### 2021-07-29 README.Rmd
Add readme

---
output: github_document
---

# pema: Penalized Meta-Analysis <!--a href='https://osf.io/zcvbs/'><img src='https://github.com/cjvanlissa/pema/raw/master/docs/pema_icon.png' align="right" height="139" /></a-->

<!-- [![CRAN status](https://www.r-pkg.org/badges/version/pema)](https://cran.r-project.org/package=pema) -->
<!-- [![CRAN RStudio mirror downloads](https://cranlogs.r-pkg.org/badges/grand-total/pema?color=blue)](https://r-pkg.org/pkg/pema) -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/cjvanlissa/pema/workflows/R-CMD-check/badge.svg)](https://github.com/cjvanlissa/pema/actions)
<!-- [![R-CMD-check](https://github.com/cjvanlissa/pema/workflows/R-CMD-check/badge.svg)](https://github.com/cjvanlissa/pema/actions) -->
<!-- [![codecov](https://codecov.io/gh/cjvanlissa/pema/branch/master/graph/badge.svg?token=7S9XKDRT4M)](https://codecov.io/gh/cjvanlissa/pema) -->
[![Contributor Covenant](https://img.shields.io/badge/Contributor%20Covenant-v2.0%20adopted-ff69b4.svg)](code_of_conduct.md)
<!-- [![CII Best Practices](https://bestpractices.coreinfrastructure.org/projects/3969/badge)](https://bestpractices.coreinfrastructure.org/projects/3969) -->
<!--[![DOI](http://joss.theoj.org/papers/10.21105/joss.00978/status.svg)](https://doi.org/10.21105/joss.00978)-->

Conduct *pe*nalized *m*eta-*a*nalysis (*"pema"*) In meta-analysis, there are
often between-study differences. These can be coded as moderator variables,
and controlled for using meta-regression. However, if the number of
moderators is large relative to the number of studies, such an analysis may
be overfitted. Penalized meta-regression is useful in these cases, because
it shrinks the regression slopes of irrelevant moderators towards zero.

<!-- ## Where do I start? -->

<!-- For most users, the recommended starting point is to [read the paper](https://osf.io/zcvbs/), currently in press in [Data Science](https://content.iospress.com/journals/data-science/Pre-press/Pre-press), -->
<!-- which introduces the pema workflow, explains the underlying tools, and illustrates how the `pema` package can be used to create a new project that follows the workflow. -->

## Installing the package

Use [R-universe](https://cjvanlissa.r-universe.dev) to install the development version of `pema`
by running the following code:

``` r
options(repos = c(
    cjvanlissa = 'https://cjvanlissa.r-universe.dev',
    CRAN = 'https://cloud.r-project.org'))

install.packages('pema')
```

## Citing pema

You can cite pema using the following citation (please use the same citation for either the package, or the paper):

> Caspar J van Lissa and Sara J van Erp (2021). pema: Penalized Meta-Analysis. R package version
0.1.0.9000. https://github.com/cjvanlissa/pema

## About this repository

This repository contains the source code for the R-package called `pema`.

## Contributing and Contact Information

We are always eager to receive user feedback and contributions to help us improve both the workflow and the software. Major contributions warrant coauthorship to the package. Please contact the lead author at [c.j.vanlissa@uu.nl](mailto:c.j.vanlissa@uu.nl), or:

  - [File a GitHub issue](https://github.com/cjvanlissa/pema) for feedback, bug reports or feature requests
  - [Make a pull request](https://github.com/cjvanlissa/pema/pulls) to contribute your code or prose

By participating in this project, you agree to abide by the [Contributor
Code of Conduct v2.0](https://www.contributor-covenant.org/). Contributions to the package must adhere to the [tidyverse style guide](https://style.tidyverse.org/). When contributing code, please add tests for that contribution to the `tests/testthat` folder, and ensure that these tests pass in the [GitHub Actions panel](https://github.com/cjvanlissa/pema/actions/workflows/R-CMD-check).

### 2021-07-30 R/brma.R
fixed data input

@@ -143,7 +143,7 @@ brma <-
     list(
       N_1 = length(unique(study)),
       M_1 = 1,
-      J_1 = 1:N,
+      J_1 = study,
       Z_1_1 = rep(1, N),
       prior_only = FALSE
     )

### 2021-08-21 simulatie_2021/Analysis Sim2021.R
Further Analysis and Clean up. EtaSq for test R2 can be found in folder 'Analysis Results'

@@ -1,7 +1,7 @@
 
-###################################
-# Predictive performance analyses #
-###################################
+##################################################
+# Predictive performance analyses - Descriptives #
+##################################################
 library(data.table)
 dat <- as.data.table(readRDS(r"(C:\Users\e_lib\OneDrive\Documents\Caspar Repositories\simulatie_2021\sim_results_2021-08-11.RData)"))
 newnames <- c('hs', 'lasso', 'mf_r', 'rma') #names of models
@@ -9,44 +9,66 @@ conditions <- c("k_train", "mean_n", "es", "tau2","alpha_mod", "moderators", "mo
 lc <- length(conditions) #length of conditions, handy for further code
 
 #subsets the data based on particular performance criterion
-#in this case train_r2
-analyzedat <- dat[ , .SD, .SDcols=c(conditions, paste0(newnames, "_train_r2"))]
+#in this case train_r2 and test_r2
+analyzedat_train <- dat[ , .SD, .SDcols=c(conditions, paste0(newnames, "_train_r2"))]
+analyzedat_test <- dat[ , .SD, .SDcols=c(conditions, paste0(newnames, "_test_r2"))]
+
 
 #converts the condition variables to factors
-analyzedat[, c(1:lc):=lapply(.SD, factor), .SDcols=c(1:7)]
+analyzedat_train[, c(1:lc):=lapply(.SD, factor), .SDcols=c(1:7)]
+analyzedat_test[, c(1:lc):=lapply(.SD, factor), .SDcols=c(1:7)]
+
 
 setwd("./simulatie_2021")
 #sink("output.txt") #makes connection with a .txt file, use it later
 #unlink('output.txt') #unlinks the connection and deletes .txt file.
 
 
-#there are missing values in the data
-apply(analyzedat, 2, function(x){sum(is.na(x))}) #17 missing values in rma_train_r2
-cases_rma_mis <- which(is.na(analyzedat$rma_train_r2)) #which cases are missing
-rma_mis <- analyzedat[cases_rma_mis,] #subset data for missing cases
-summary(rma_mis) #at first sight, I do not see an obvious pattern to why these cases are missing
+#there are missing values in the data for train
+library(mice) #load in library
+
[…]

### 2021-08-21 simulatie_2021/Analysis Sim2021.R
Just a quick test

@@ -522,7 +522,7 @@ library(xtable)
 print(xtable(coef.table), file="EtaSq_testR2.tex",sanitize.text.function=function(x){x})
 
 
-#save.image("Analysis_Data.RData")
+##save.image("Analysis_Data.RData")
 ###### TOT HIER GECHEKT ELI 2021 #####
 load("Analysis_Data.RData")
 

### 2021-08-21 simulatie_2021/Analysis Sim2021.R
quick test

@@ -158,6 +158,9 @@ library(xtable)
 print(xtable(coeftable.testr2), file="coeftable.testr2.tex",sanitize.text.function=function(x){x})
 
 
+## Vanaf hier verder ##
+
+
 ##Figure out which predictors are most important per variable
 as.numeric.factor <- function(x) {as.numeric(levels(x))[x]}
 #sink("output.txt", append = TRUE)
@@ -522,7 +525,7 @@ library(xtable)
 print(xtable(coef.table), file="EtaSq_testR2.tex",sanitize.text.function=function(x){x})
 
 
-##save.image("Analysis_Data.RData")
+#save.image("Analysis_Data.RData")
 ###### TOT HIER GECHEKT ELI 2021 #####
 load("Analysis_Data.RData")
 

### 2021-08-21 simulatie_2021/Analysis Sim2021.R
check which algorithms predicts best per condition

@@ -148,49 +148,93 @@ names(coef.table)<-c("Horseshoe", "Lasso", "Metaforest" ,"RMA")
 
 coeftable.testr2 <- coef.table
 #sink("output.txt", append = TRUE)
-#study1.coef.table.withoutmodel1
 #sink()
 
-#study1.coef.table.withoutmodel1 <- study1.coef.table.withoutmodel1[, -c(2,3, 7, 8)]
+write.csv(coef.table, file =  "EtaSq_testR2.csv")
+#sink("output.txt", append = TRUE)
+#sink()
 
 #this makes a nice table in .tex file for the coefficients
 library(xtable)
-print(xtable(coeftable.testr2), file="coeftable.testr2.tex",sanitize.text.function=function(x){x})
+print(xtable(coef.table), file="EtaSq_testR2.tex",sanitize.text.function=function(x){x})
 
 
-## Vanaf hier verder ##
+#save.image("Analysis_Data.RData")
+###### TOT HIER GECHEKT ELI 2021 #####
+load("./simulatie_2021/Analysis_Data.RData")
 
 
 ##Figure out which predictors are most important per variable
-as.numeric.factor <- function(x) {as.numeric(levels(x))[x]}
-#sink("output.txt", append = TRUE)
-lapply(coeftable.testr2, function(x){
-  tmp <- as.numeric.factor(x) #as.numeric.factor() is not an existing function
-  names(tmp)<- names(coeftable.testr2)
-  sort(tmp, decreasing = TRUE)
-})
-#sink()
-
-#functoin that sorts conditions that have highest eta to lowest
+#function that sorts conditions that have highest eta to lowest
 important_predictors <- function(df, column){
-  df.sort <- df[order(df[,column]), , drop = FALSE]
-  rnames <- rownames(df.sort)
-  vals <- sort(df.sort[,column], decreasing = TRUE)
-  memory <- c()
+  df.sort <- df[order(df[,column], decreasing = T), , drop = FALSE] #sort by particular column
+  rnames <- rownames(df.sort) #store row names in variable
+  vals <- sort(df.sort[,column], decreasing = TRUE) #store values in variable
+  condition <- c() #memory for condition names
+  value <- c() #memory for eta square values
   for(i in 1:nrow(df.sort)){
-    elem <- paste0(i, ".) ", rnames[i], "= ", vals[i])
-    memory[i] <- elem
+    condition[i] <- rnames[i]
+    value[i] <- vals[i]
   }
[…]

### 2021-09-03 paper/manuscript.Rmd
add frankenpaper.rmd

---
title             : "Select relevant moderators in meta-regression using Bayesian penalization"
shorttitle        : "Title"

author:
  - name: "Caspar J. Van Lissa"
    affiliation: "1,2"
    corresponding: yes
    address: "Padualaan 14, 3584CH Utrecht, The Netherlands"
    email: "c.j.vanlissa@uu.nl"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Writing - Original Draft Preparation
      - Writing - Review & Editing    
  - name: "Andreas M. Brandmaier"
    affiliation: "3,4"

  - name          : "Ernst-August Doelle"
    affiliation   : "1,2"
    role:
      - Writing - Review & Editing

affiliation:
  - id            : "1"
    institution   : "Wilhelm-Wundt-University"
  - id            : "2"
    institution   : "Konstanz Business School"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.

  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.

  One sentence clearly stating the **general problem** being addressed by  this particular study.

  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).

  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.

  One or two sentences to put the results into a more **general context**.

  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.

  <!-- https://tinyurl.com/ybremelq -->

keywords          : "keywords"
wordcount         : "X"

bibliography      : ["r-references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
r_refs("r-references.bib")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

Skeleton lasso/pema paper
1.) What is Meta-analysis?
2.) What is meta-regression and how does it complement meta-analysis?
	a.) Introduce Moderators
	b.) Study Heterogeneity + Random Sampling Error (and their difference)	
2.5.) Fixed vs. random effects
	a.) Shortcomings of fixed effect models
3.) Shortcomings of current meta regressions w.r.t. estimating coefficients and heterogeneity:
	a.) Small sample size / overfitting
	b.) Non-normal data
4.) Various methods to estimate heterogeneity (and coefficients)
	a.) The use of WLS and REML
5.) Intro to Frequentist linear methods/Bayesian methods and Random forests, along with their 
(dis-)advantages:
	a.) Rma: uses WLS for estimation
	b.) MetaForest (Random Effects): Uses Random Forest Algorithm
	c.) Lasso Pema: uses penalized Lasso
	d.) Horseshoe Pema: uses horseshoe priors
6.) Goal of the current study
7.) Means of attaining goal and evaluation of performance:
	a.) simulation study
	b.) algorithmic performance
	c.) design factors
	d.) Impact of design factors on algorithim performance
	e.) Hypotheses of algorithmic performances

colour coding: I colour coded the text as to know from which file the text is copied
GREEN = derived from ‘Thesis_Metaforest’
BLUE = Thesis_lasso
BLACK = internship_report
RED = Inserted myself
Short Introduction to the study
Meta-analysis is a statistical method which utilizes several tools to synthesize the data of multiple studies on the same topic, with the purpose of finding a result that is more trustworthy. What meta-analysis does is simply weighting all the observed effect sizes of the individual studies and averaging them to one summary effect. Although this explanation is a bit too simplistic, in essence this is what meta-analysis is about. Meta-analysis assigns weights to each individual study based on different assumptions which are set in advance. These weights determine to what extent an individual study takes part in the eventual summary effect. 
Nevertheless, a serious concern is heterogeneity that is included between the studies in meta-analysis, which is caused due to clinical and/or methodological diversity. Heterogeneity causes a challenge to aggregate data, but it also offers a way to find characteristics of a study or “moderators” that could have impact on the found effect size.
The process of examining the relationship between study characteristics and the effect sizes is most often done by a meta-regression (Viechtbauer & López-López, 2015). Meta-regression aims to relate the size of the effect to one or more characteristics of the studies involved. As multiple regression is used to assess the relationship between subject-level covariates and an outcome, meta-regression in meta-analysis is used to assess the relationship between study-level covariates and the effect size.
However, when performing such an analysis, a lot of moderators are measured and it may be unclear which are relevant and which are not. There are a couple of reasons to explain this: Riley, Higgins & Deeks (2011) concluded that the number of studies is oftentimes overly small. As a result of this heterogeneity cannot be inspected accurately. Also, there is an insufficiency in regard to techniques to downgrade the amount of possible moderators to a feasible number (Thompson & Higgins, 2002). This results in a large amount of moderators to be examined and a low quantity of studies. These kinds of conditions do not have a solid fit and predictive power in the classic meta-analysis approaches (van Lissa, 2017). For this obstacle there is a variable selection technique needed, that identifies moderators as strong or weak influencers of the observed effect size.
Thus, there is a need of a regularization method to curtail overfitting. LASSO (L1-norm regularization) can fulfill this role, since it has an advantage in terms of feature selection. The goal of this project is to implement L1-norm regularization in the weighted meta-regression, developing an new estimator for penalized meta-regression.
More detailed explanation of methods and theoretical concepts

Fixed vs Random effects
The two classic approaches of meta-analysis refer to fundamental different assumptions made about the underlying data. These assumptions define the weights and will also determine which methods are used for the weighting of individual studies and for the creation a summary effect.
The first approach is referred to as the as the fixed-effect model. This model assumes that each observed effect size, obtained from each individual study, is an estimate of an underlying true effect size (Hedges & Vevea, 1998). The true effect sizes are treated as, unknown, constants. The only source that causes the deviation of the observed effect from the, unknown, true effects is sampling error. Thus, for a collection of k studies, the observed effects size yi of each individual study i (for i = 1,2, . . . k) is given by:
y_i=θ+ϵ_i  						(1)
Where 𝜃 is the true effect size of each individual study i and 𝜖i follows the distribution of N(0 , vi) with vi being the sampling error or within-study variance, which is treated as a known factor.

Fixed-effects meta-analysis considers sampling error to be the only cause of variance that influences the observed effect size. Studies with a large sample size will, as a result of this, produce more precise estimations of the underlying true effect size (Schmidt, Oh & Hayes, 2009). Therefore, large sample sizes will contribute more to the weighted mean than small sample sizes. With that said, fixed-effects weights are defined by van Lissa (2017): “as the reciprocal of the effect size variances”:
			   W_i=  1/(σ_i^2 )						  (2)
	For an accurate estimate of the fixed-effects meta-analysis model, it starts with the assumption that the true effect is even in al studies. However, this assumption is implausible in plenty of meta-analysis. Especially in social sciences, the behaviour of people is extremely diverse and the contextual conditions for all humans vary to a great degree (Aronson, Wilson & Akert, 2016). A highly likely consequence is that this will lead to a huge amount of possible moderators (Caserio, 2014). Also studies that examine same or similar research questions often differ. Caused by differences in for example cultures of research populations and used methods or instruments (Neuman, 2011). Even in replication studies there are sometimes moderators that are unanticipated (Kunert, 2016). This leads very often to an eventual poor performance of the fixed-effects meta-analysis model (Snijders, 2005). 
The second model is the random-effects model. This approach makes an additional assumption, namely about the true effect sizes. Where the fixed-effect model treats the true effects as constants, the random-effect model assumes that the true effects are random and follow a distribution of their own (Hedges & Vevea, 1998). This means that variation in the observed effects (yi) in the random model incorporates not only the sampling error but also the variation of the true effect sizes (󠅵𝜏2) between the studies. In the case of the random effect model the observed effect size of yi is, given by:

y_i= θ_i+ϵ_i 						(2)
With 𝜖i ~ N(0 , vi) but, in this case 𝜃i on itself is given by:
θ_i=μ+ζ_i 						(3)
With 𝜇 being the mean of the distribution of the true effect sizes and 𝜁i following the distribution N(0 , 𝜏2) with 𝜏2 being the variance of the population of true effect sizes. It could also be explained as the variance between the individual studies. 
However, in the case of random-effects, the true effects also follow a distribution, so therefore the between study variance is also taken into account when composing the weights for the individual studies. The individual weights for the random-effect model are given by:
W_i=1/(v_i+τ ̂^2 )						(5)
In the case of the random-effect model, the within-study- and between-study variance is necessary for the calculation of the weights. It is important to note that in the calculation of the individual weights, an estimation of study heterogeneity is used (τ ̂^2). While the sampling error is known for each individual study, the true effect heterogeneity (󠅵𝜏2) remains unknown. Therefore, an estimation of the heterogeneity value needs to be made to effectively calculate the weights. This estimation of the between-study variance is thus represented by τ ̂^2.

Meta-regression
In the case of fixed- and random-effect meta-analysis, the observed effects are treated as estimations of the underlying true effect. In meta-regression the observed effects are estimated by the including the moderators. In other words, the true effect is now replaced by the moderator effects. This is expressed with the following equation, where θ_i represents the underlying true effect, xi the moderators, βi the coefficients, with p being the number of moderators:
θ_i=β_0+β_1 x_1+β_2 x_2+⋯+β_p x_p+ζ_i			(6)
When this is substituted in the original equation it will result in:
y_i=β_0+β_1 x_1+β_2 x_2+⋯+β_p x_p+ζ_i+ϵ_i			(7)
The error term 𝜁i captures the residual heterogeneity after accounting for the moderators. This term is still included because it is often the case that there still remains heterogeneity unexplained after accounting for the moderators (Thompson & Sharp, 1999). In this model the moderator effects are treated as fixed and the residual heterogeneity as random. Therefore, it is referred to as a mixed-effect meta-regression analysis model, in short, ME-MRA (Viechtbauer & López-López, 2015). To solve this ME-MRA model, both the residual heterogeneity and the moderator coefficients need to be estimated. An accurate estimation of the residual heterogeneity contributes to a better interpretation of the effect of the moderators (Panityakul, Bumrungsup & Knapp, 2013).
Estimating residual heterogeneity
The topic of estimating the residual heterogeneity is a highly discussed one (Veroniki et al., 2016; Viechtbauer & López-López, 2015; Panityakul et al., 2013). The ability of the estimators to predict the residual heterogeneity is influenced by different factors, such as the number of studies (Guolo & Varin, 2017; Panityakul et al., 2013; Hardy & Thompson, 1996) included and the sample size of the individual studies (Panityakul et al., 2013).
A third, and obvious factor, that is classified as relevant to model performance is heterogeneity among studies being meta-analysed (Kontopantelis & Reeves, 2011; Jackson & White, 2018). Coverage from models degrades when the residual heterogeneity increases, mostly when the amount of studies is small (Brockwell & Gorden, 2001). Considering that all models their performance is linked to the accuracy of the estimate. According to Sidik & Jonkman (2007), it is generally the case that the larger true between-study variance is, the more biased the estimate can be, which diminishes the performance of the method.
Methods for estimating residual heterogeneity
Numerous methods have been proposed to accurately estimate the residual heterogeneity, including the Hedges (HE), DerSimonian–Laird/Method of Moments (DL), Sidik and Jonkman (SJ), Maximum Likelihood (ML), Restricted Maximum Likelihood (REML), and Empirical Bayes (EB) method. These methods are mostly divided into two groups: closed-form or non-iterative methods and iterative methods. The main difference between these groups is that the closed form group uses a predetermined number of steps to provide an estimation for the residual heterogeneity, whereas the iterative methods run multiple iteration, as the name suggests, to converge to a solution when a specific criterion is met. It is important to note that some iterative methods do not produce a solution when they fail to converge after a predetermined amount of iteration.

In our scenario we are especially interested in an estimator which performs well under the condition of a relative low number of studies. The Restricted Maximum Likelihood (REML) seems to produce the lowest bias under this condition and is therefore preferred (Panityakul et al., 2013; Hardy & Thompson, 1996).
The REML is an iterative method. This iterative method needs a starting estimation of 𝜏2 to start, usually it gets estimated by one of the non-iterative methods (Viechtbauer & López-López, 2015). Besides the starting value of 𝜏2, it needs in every iteration an estimation of the regression coefficients of the moderators. These are typically estimated by using the Weighted Least Squares (WLS) method. This is a variation of the Ordinary Least Squares (OLS), but in the case of meta-analysis it is necessary to assess weights to the coefficients. In systematic reviews large variation in standard errors is often observed, which will result in large heteroscedasticity in the estimation of the effects (Stanley & Doucouliagos, 2017). The addition of weights is a way to adjust for this heteroscedasticity. The weights are formulated as presented in equation (5). 
The usage of a WLS method to estimate the regression coefficient may be problematic in the situation where a lot of moderators are measured without their specific effects, when the amount of studies is low and when moderators are dichotomous. The use of a least squares method will cause problems with the prediction accuracy and the model interpretability (James, Witten, Hastie, & Tibshirani, 2013). In the situation where a lot of moderators are measured and blindly included in the model, it may as well be the case that variables are included that are in fact not associated with the response. Including irrelevant variables in the model lowers the interpretability of the model (James et al., 2013). An approach is necessary that automatically excludes the variables that are irrelevant i.e. performs variable selection. As explained before, in meta-analysis it is often the case that the number of moderators closely approaches or even exceeds the number of studies included in the analysis. A least squares method will display a lot variability in the fit when the number of variables is not much smaller than the number of studies (James et al., 2013). This means that the least squares method over fits the data and loses its power to be generalizable to future observations. When the number of variables exceeds the number of studies, the least squares method fails to produce one unique estimate and the method should not be used at all. 
However, a least squares method could still be somewhat valuable in some situations. It is extremely suitable to estimate a linear relationship. In the case of dichotomous moderators, the relationship is always perfectly linear. A powerful non-linear estimation tool is in the situation of dichotomous moderators unnecessary and would not perform better at all. Whenever a non-linear relation gets fitted on data with an underlying linear relation, it will cause problems when this fit gets used for the prediction of future data. Given the various arguments, this paper provides an approach to tackle this problem of the least squares methods whilst still making use of a linear method. The weighted least squares are replaced with the so-called LASSO (least absolute shrinkage and selection operator) regression for the estimation of the regression coefficients. This algorithm shrinks or penalizes the regression coefficients and performs variable selection (James et al., 2013; Hesterberg, Choi, Meier, & Fraley, 2008).

Intro rma
The rma algorithm is part of the software-package metafor in R, which is developed by Wolfgang Viechtbauer (2010, 2019). This algorithm is specifically developed to perform a meta-analysis or met-regression. It allows to include different models, such as the fixed-, random- and mixed-effect model. It is also possible to account for moderators (Viechtbauer, 2010). The mixed-effect model, which is used is this study, requires a two-step approach to fit a meta-analytic model. First the residual heterogeneity is estimated. The package developed by Viechtbauer does provide multiple methods for the estimation of the residual heterogeneity. In this study the Restricted Maximum-likelihood is used, but this has already been discussed earlier. The second step is estimating the moderator coefficients, which is done by using the Weighted Least Squares (WLS) method. The weights are described in equation (5). The lma is a variation of the rma algorithm which is created by Caspar van Lissa. As explained before, the REML is an iterative procedure for the estimation of the residual heterogeneity. In every step of the process, instead of estimating the coefficients of the moderators by using a WLS, a weighted lasso regression is performed. Then again, the residual heterogeneity gets estimated with the rma algorithm by using the new values of the coefficients. With these new values of 𝜏2, a new weighted lasso is performed for the estimations of the coefficients. This process continuous, until the residual heterogeneity converges to a certain value.

Intro Lasso
The lasso is a technique that regularizes or constrains the coefficient estimates, better known as shrinking (James et al., 2013). It possesses the ability to reduce the regression coefficient even to a value of zero. By doing this it automatically performs variable selection. It does not seem to be immediately clear why shrinking the coefficients should be an improvement to the model. However, by shrinking the parameters, it lowers the variance of the model by increasing the bias only a little bit. In other words, the model sacrifices some of its ability to fit the current data, to greatly increase the ability to predict future data with the same fit (James et al., 2013). This is better known as the bias/variance tradeoff (Briscoe & Feldman, 2011). 
The Lasso shrinkage method is not the only shrinkage method, there do exist some others. Nevertheless, the lasso is in the case the best option. It possesses, as opposed to other methods, the ability to shrink the parameter not towards zero, but to be exactly zero (James et al., 2013; Hesterberg, Choi, Meier, & Fraley, 2008). This means that the lasso can perform variable selection, something that is specifically aimed for in this study. 
In line with other shrinkage methods the lasso makes use of a shrinkage penalty. This penalty is added in the process of the OLS calculation of the regression coefficients. The OLS method estimates the coefficients by minimizing the Residual Sum of Squares (RSS). The following equation shows how the calculation of the RSS together with the shrinkage penalty: 
RSS=∑_(i=1)^n▒〖(y_i-β_0-∑_(j=1)^p▒〖β_j x_ij )^2+λ∑_(j=1)^p▒|β_j | 〗〗			(8)
This equation shows that the shrinkage penalty consists of two variables, the tuning parameter lambda (𝜆) and the regression coefficients (𝛽). This means that, while the OLS tries to find the coefficients which explain as much variance as possible, due to the minimization of the RSS, the shrinkage penalty punishes this. Therefore, the coefficients are forced to shrink a certain amount, depending on the parameter lambda. If the lambda increases, it grows the impact of the shrinkage penalty on the RSS, with 𝜆 → ∞ shrinking all the coefficient to be zero, producing the null model. But, if the lambda is zero, the shrinkage penalty has no impact at all and it will produce the OLS estimates.

Alternative to linear model: Tree Based models
An alternative that can perform variable selection, are tree-based models. These kinds of models have numerous other advantages over linear models. Tree-based models can be used for any data type, are easy to represent visually, require little data preparation and got larger power than linear regressions when moderators exceed observations in quantity. They are also more flexible in handling moderator interactions and non-linearity. As a result of that, they are better in modelling the complicated nature of human behaviour (Earp & Trafimow, 2015). Decision trees split from the top down and group data in so-called ‘sub-nodes’, in which the data’s aspects are most homogeneous. The goal is to split to get the sub-nodes as uniform as possible, which can be until fully homogenous groups, or if a pre-specified touchstone is reached. 
Still, singletree based models have some limitations. First of all, tree models are unstable, small fluctuations that are utilized to make the model have a possibility to lead to considerable alterations in the constructions of the tree (Dwyer and Holte, 2007). Second, it has problems with seizing linearity, because it only makes ‘twofold splits’ (Steyerberg, 2019). At last, tree-based models are susceptible to overfitting (Hastie et al, 2009). 
There are also more complex tree-based models, known as random-forests, which surmount most of the disadvantages of singletree. This variant incorporates multiple decision trees, and combines results from those trees to create a single model with a more accurate estimate (Breiman, 2001). The essential idea behind is know as the ‘wisdom of crowds’, a large number of relatively uncorrelated trees operating as a group will outperform any of the individual elements. The somewhat low correlation between the models is fundamental, because uncorrelated models are able to produce ensemble predictions with a higher accuracy that any individual prediction. This is because the trees preserve each other from their own singular errors (Genuer, Poggi & Tuleau-Malot, 2010). The lower tendency to overfitting is another advantage of random forests over single trees (Bühlmann & Yu, 2002). As well as the possibility to predict cases that are not components of the bootstrap sample of the tree. This kind of measure is known as out-of-bag error, which is an approximation of the cross-validation error, and provides proper estimates of the prediction accuracy in further samples (Hastie et al., 2009). 
An alternative to explore heterogeneity in meta-analysis with a singletree-based method is MetaForest. A technique developed by van Lissa (2017), designed to overcome the lacking’s of singletrees by using random forests. MetaForest applies random-effects or fixed-effects weights to random forests.
Based on two simulation studies, van Lissa (2017) examined the performance of fixed-effects, random-effects and unweighted MetaForest
The study displayed also other advantages from random forests over singletrees. It had greater power, was able to make better predictions, gave estimates of the cross-validation error and yielded useful measures of variable importance and partial prediction plots (van Lissa, 2017). MetaForest can at the moment be considered as the best working technique to explore heterogeneity in meta-analysis.
in van Lissa (2017), that only presented estimates of τ2 based on the raw data, we saw that MetaForest had certain robustness against a low number of studies. If moderators were continuously distributed, MetaForest had sufficient power at approximately 20 studies.
However, there is an important feature to prove before we can make such an assumption. The underlying data generating models in the two simulation studies of van Lissa (2017) only included normal distributed moderators. Renouncing from normal distributions may affect the performance of the model, but since normal distribution in real-life data is more an exception than a normal state of affairs (Micceri, 1989), it is entirely possible that procedures are affected by skewness, leverage, balance etc. It is important to know how MetaForest performs in these kinds of situations.
Algorithms and simulation + goal study
The goal of the present study was to test whether a ME-MRA model with the lasso algorithm is able to outperform the ME-MRA with least squares regression. More specifically, if the lasso is able to outperform the least squares when in situation where the amount studies included in the analysis is fairly low. To test this, two different algorithms are used; one called the rma, which makes use of the WLS regression, and the lma, which makes use of a penalized lasso regression.
To test the lma and rma algorithms on the performance criteria, a simulation study is performed. A simulation of the data is preferred over the use of real data. Simulated data can be shaped to such an extent that it will have the all desired characteristics to test the performance of the algorithm. Besides that, if simulated correctly, it will not have any systematic errors or noise due to underlying models and it is more cost efficient. 
simulations are useful for evaluation of new methods like MetaForest and for the comparison with alternative methods like metaCART and the classic approaches.

Performance Criteria
The algorithms are evaluated on three different performance criteria: The algorithms’ predictive performance, their ability to estimate the residual heterogeneity and their ability to detect and select the right moderators.
The predictive performance of the algorithms is defined by how well the algorithm is able to predict future data. The algorithms have to estimate a model on a “training” dataset and then use this model to see how well it fits on a second “testing” dataset. This is operationalized as the cross-validated R_cv^2 (Van Lissa, 2017). The R_cv^2 is calculated using the fraction of variance explained by the model on the testing dataset, relative to faction of variance explained by the mean of the testing dataset. The mean of the testing dataset is the best prediction for the testing data when there is no model present (van Lissa, 2017). The calculation of R_cv^2 is expressed by the following equation:
R_cv^2=1-(∑_(i=1)^n▒〖(y_i-y ̂_i )^2 〗)/(∑_(i=1)^n▒〖(y_i-y ̅)^2 〗)					(9)
With n being the number of studies in the testing dataset, y ̂_i being the estimation for study i, and y ̅ being the mean of the training dataset. 
	The ability of the algorithms to estimate the residual heterogeneity is by simply taking the value of 𝜏2 which the algorithm produces. The true value of the residual heterogeneity is subtracted of the estimated value, solely to make the values more interpretable. This means that a correct estimation of the residual heterogeneity will be expressed by a value which exactly or close to zero. The residual heterogeneity is used as a performance criterion because it is suspected that the lma model might not always be able to predict residual heterogeneity correctly. 
	Variable selection is defined in terms of the algorithms ability to accredit positive variable importance values to relevant moderators. Variable importance measures capture the relative contribution of various moderators.

Design factors
In the simulation study, meta analytic datasets will be simulated. These datasets consist of two separate sub-datasets, a training- and a testing dataset. Both sub-datasets will have the same characteristics with the exception of the number of studies included. Certain characteristics of the sub-datasets will be manipulated to test how well the algorithms perform under certain conditions. For each combination of characteristics, or design factors, 100 datasets will be simulated. The design factors that will be manipulated are the number of studies in the training data k (22, 40 and 80), the average within-study sample size n ̅ (40, 100 and 200), the population effect size β (.2, .5 and .8) and the residual heterogeneity 𝜏2 (.01, .04 and .1). All the datasets will contain 20 moderators of which 10 are relevant and 10 are irrelevant. The moderators are binary and are randomly drawn form a Bernoulli distribution with probability p=.5, which corresponds to an equal chance of being either one or zero. The dependent variable y_i represented by a Hedges’ g. This is an estimator which takes the standardized mean difference between a treatment and control group and is commonly used in meta-analysis (Van Lissa, 2017). The true effect size θ_i  is sampled out of a normal distribution. The mean is computed by the assessing the values of the coefficients β, with the values of the moderators and with the residual heterogeneity τ^2 (Van Lissa, 2017).  This is in line with the calculation of θ_i represented in equation (6). The sampling error v_i is formed by varying the sizes of the samples of each study. The sample sizes n_i are drawn from a normal distribution with mean n ̅ and standard deviation n ̅⁄3 (Van Lissa, 2017). 
Data were simulated using the random-effects model, based on six models:
(A) Main effect of one moderator, μ_i= βx_1i 
(B) Two-way interaction, μ_i= βx_1i+ βx_2i+ βx_1i x_2i
(C) Three-way interaction, 
μ_i= βx_1i+ βx_2i+ βx_3i+ βx_1i x_2i+βx_1i x_3i+βx_2i x_3i+βx_1i x_2i x_3i
(D) Two two-way interactions, μ_i= βx_1i+ βx_2i+ βx_3i+βx_4i+βx_1i x_2i+βx_3i x_4i
(E) Non-linear, cubic relationship, μ_i= βx_1i+ βx_1i^2+βx_1i^3
(F) Exponential relationship, μ_i= βe^x1i

Impact of design factors and hypotheses
These design factors are chosen on purpose, because they are hypothesized to have an influence on the predictive performance of the algorithms. The effect of the design factors ought to be either positive or negative on the data. This means that some factor should, by increasing, make the data easier to be analyzed, or make it more difficult to analyze. The amount of studies included in the training data k has a positive influence on the variance explained by the different algorithms. This is due to the fact that there are simply more data points available to fit a model on. The lma algorithm should be superior on the low value of k over the rma algorithm. The effect size β has a positive impact on the ability of the algorithms to explain variance. It can be hypothesized that the lma performs better at lower values of β because it is better equipped to detect and select variables when even when the amount of signal is low. The residual heterogeneity τ^2 should have a negative influence on the interpretability of the data. Differences between the two algorithms could be present, but it remains unclear which would perform better. The lma might perform better when the amount of signal in the data is low or the noise is high, but it is also suspected to overestimate the amount of heterogeneity and this could worsen if the τ^2 increases. The n ̅ greatly influences the quality of the data. Higher values of within-study sample sizes reduce the sampling error. This will lead to a better prediction by the algorithms. In conclusion: higher values of k, β and n ̅ will increase the quality of the data, where higher values of  τ^2 decrease the quality of the data. The lma is suspected to perform significantly better when the quality of the data is low, especially when the amount of studies in the sample is low, with the exception of the performance of the lma on the estimation of the residual heterogeneity

Results

\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup

### 2021-09-18 paper/manuscript.Rmd
Results for predictive R2. images and tables in seperate document

@@
 RED = Inserted myself
-Short Introduction to the study
+
+#introduction
+**intro to meta-analysis**
 Meta-analysis is a statistical method which utilizes several tools to synthesize the data of multiple studies on the same topic, with the purpose of finding a result that is more trustworthy.
@@
 These weights determine to what extent an individual study takes part in the eventual summary effect.
+
 Nevertheless, a serious concern is heterogeneity that is included between the studies in meta-analysis, which is caused due to clinical and/or methodological diversity.
 Heterogeneity causes a challenge to aggregate data, but it also offers a way to find characteristics of a study or “moderators” that could have impact on the found effect size.
+
 The process of examining the relationship between study characteristics and the effect sizes is most often done by a meta-regression (Viechtbauer & López-López, 2015).
@@
 As multiple regression is used to assess the relationship between subject-level covariates and an outcome, meta-regression in meta-analysis is used to assess the relationship between study-level covariates and the effect size.
+
 However, when performing such an analysis, a lot of moderators are measured and it may be unclear which are relevant and which are not.
@@
 For this obstacle there is a variable selection technique needed, that identifies moderators as strong or weak influencers of the observed effect size.
+
 Thus, there is a need of a regularization method to curtail overfitting.
@@
 
-Fixed vs Random effects
+**Fixed vs Random effects**
 The two classic approaches of meta-analysis refer to fundamental different assumptions made about the underlying data.
 These assumptions define the weights and will also determine which methods are used for the weighting of individual studies and for the creation a summary effect.
+
 The first approach is referred to as the as the fixed-effect model.
@@
 The only source that causes the deviation of the observed effect from the, unknown, true effects is sampling error.
-Thus, for a collection of k studies, the observed effects size yi of each individual study i (for i = 1,2, .
+Thus, for a collection of k studies, the observed effects size $y_{i}$ of each individual study i (for i = 1,2, .
 .
@@
 k) is given by:
-y_i=θ+ϵ_i  						(1)
-Where 𝜃 is the true effect size of each individual study i and 𝜖i follows the distribution of N(0 , vi) with vi being the sampling error or within-study variance, which is treated as a known factor.
+
+ *$y_{i}$ = θ + $ϵ_{i}$ * 						(1)
+
+Where 𝜃 is the true effect size of each individual study i and $ϵ_{i}$ follows the distribution of N(0 , $v_{i}$) with $v_{i}$ being the sampling error or within-study variance, which is treated as a known factor.
 
@@
 With that said, fixed-effects weights are defined by van Lissa (2017): “as the reciprocal of the effect size variances”:
-			   W_i=  1/(σ_i^2 )						  (2)
+
+ *$W_{i}$=  1/($σ^2_{i}$)*						  (2)
+
 	For an accurate estimate of the fixed-effects meta-analysis model, it starts with the assumption that the true effect is even in al studies.
@@
 This leads very often to an eventual poor performance of the fixed-effects meta-analysis model (Snijders, 2005).
+
 The second model is the random-effects model.
@@
 
-y_i= θ_i+ϵ_i 						(2)
-With 𝜖i ~ N(0 , vi) but, in this case 𝜃i on itself is given by:
-θ_i=μ+ζ_i 						(3)
+ *$y_{i}$ = $θ_{i}$+$ϵ_{i}$* 						(3)
+
+With $ϵ_{i}$ ~ N(0 , $v_{i}$) but, in this case $𝜃_{i}$ on itself is given by:
+
+ *$θ_{i}$= μ + $ζ_{i}$*						(4)
+
 With 𝜇 being the mean of the distribution of the true effect sizes and 𝜁i following the distribution N(0 , 𝜏2) with 𝜏2 being the variance of the population of true effect sizes.
@@
 The individual weights for the random-effect model are given by:
+
 W_i=1/(v_i+τ ̂^2 )						(5)
@@
 
-Results
+#Results
+There were 20 cases out of 388800 that had missing values for the RMA algorithm.
+Closer inspection showed that both the cubic and exponential model each contributed 10 times to the missing values and only when 2, 3 or 6 moderators were taken up in the model.
+However, since this makes up 0.005% of the data, the missing values were chosen to be omitted from further analysis.
+
+*Predictive performance*
+Because the densities for the R2 values were either bimodal or skewed, it was chosen to use the median $R^{2}$ as the metric for predictive performance, rather than the mean.
+The spread of the data was described using the Mean Absolute Deviation [MAD], rather than the standard deviation.
+It was found that the Horseshoe, Lasso and RMA algorithm performed similarly overall, $Med_{hs}$ = 0.51, MAD = 0.36; $Med_{Lasso}$ = 0.50, MAD = 0.37; $Med_{RMA}$ = 0.50, MAD = 0.37.
+The random forest algorithm performed worst $Med_{rf}$ = 0.35, MAD = 0.38.
+
+To determine the effect of the design factors on predictive performance of all algorithms, four separate ANOVA’s was performed. The $η^{2}$ per condition per algorithm can be found in table 1.
+
+Not too surprisingly, It was found that the true effect size *β* had the largest effect on the predictive $R^{2}$ for all algorithms.
+As *β* increased, the performance of all algorithms increased as well.
+However, *β* did seem to interact with the model that was estimated, being either a linear, two-way interaction, cubic or an exponential model.
+The image of the interaction is shown in image 1.
+The major difference seems to be that for all models, except the linear, the increase of *R2* slows for every higher value for *β*.
+The steepest increase for the linear model is when *β* increases from 0.2 to 0.4.
+Also noteworthy is that the two-way interaction model seems to stagnate as the effect size goes up to 0.4 onwards, while the other models do keep increasing, although not as severely.
+There seemed to be little difference in performance between Horsehoe, Lasso and RMA, while the random forest algorithm performed worst.
+
+The second largest marginal effect was that of the estimated model.
+All algorithms performed best under the 2-way interaction model, followed by a similar performance on the cubic and exponential models.
+The linear model predicted worst performance for all algorithms.
+Horseshoe and Lasso performed best under all models, followed closely by RMA and lastly the random forest.
+Image 2 shows the relationship.
+
+There also was a moderate interaction effect between the estimated model and the amount of skewness of the data [α], especially for the Pema algorithms.
+Again, the Horseshoe and Lasso algorithms performed best, followed by RMA and MetaForest in all conditions.
+Most obvious to note is that under all model, except the linear model, the algorithms benefitted when the $R^{2}$ was estimated on more skewed data.
+The two-way interaction model performs best under all levels of *α*, but is getting caught up by the exponential and cubic model as *α* increases.
+Image 3 shows the relationship.
+
+The true residual heterogeneity $τ^{2}$ had a negative linear relationship for all algorithms on $R^{2}$.
+i.e.
+as $τ^{2}$ increases, $R^{2}$ decreased.
+The effect was slightly bigger for the Pema algorithms than for the other two.
+Still, both Horseshoe and Lasso performed best, followed by RMA and MetaForest.
+Image 4 shows the relationship.
+
+The mean sample size per study [n] also had a moderate effect, again namely for the Pema algorithms.
+For all algorithms the effect of *n* was positively linearly related to $R^{2}$ with the Pema algorithms performing best for all levels of *n*.
+Image 5 shows the relationship.
+
+An especially large effect was found for the number of studies used in the training data for MetaForest, $η^{2}$ = 0.27, while this effect was substantially smaller for RMA, $η^{2}$ = 0.11; Lasso, $η^{2}$ = 0.06 and; Horseshoe, $η^{2}$ = 0.05.
+The relationship is positively linear for all algorithms, but the slope is especially steep for MetaForest.
+Image 6 shows the relationship.
+
+Finally, the number of moderators did not have a big effect for the Pema algorithms, $η^{2}$ = 0.01 for both Horseshoe and Lasso while for RMA and Metaforest $η^{2}$ = 0.05.
+This relationship is generally negative with more moderators meaning worse performance, although a slight increase can be observed as the number of moderators increase from 6 to 7.
+The image and $η^{2}$ values indicate that the Pema algorithms seem more robust against number of moderators than RMA and MetaForest.
 

### 2021-09-22 paper/manuscript.Rmd
Results for predictive performance R2 and .rtf document containing relevant images

@@
 
- *$y_{i}$ = θ + $ϵ_{i}$ * 						(1)
+ $y_{i}$ = θ + $ϵ_{i}$						(1)
 
@@
 
- *$W_{i}$=  1/($σ^2_{i}$)*						  (2)
+ $W_{i}$=  1/($σ^2_{i}$)						  (2)
 
@@
 
- *$y_{i}$ = $θ_{i}$+$ϵ_{i}$* 						(3)
+ $y_{i}$ = $θ_{i}$+$ϵ_{i}$ 						(3)
 
@@
 
- *$θ_{i}$= μ + $ζ_{i}$*						(4)
+ $θ_{i}$= μ + $ζ_{i}$						(4)
 
@@
 #Results
-There were 20 cases out of 388800 that had missing values for the RMA algorithm.
+There were 20 cases out of 388800 that had missing values on all metrics for the RMA algorithm.
 Closer inspection showed that both the cubic and exponential model each contributed 10 times to the missing values and only when 2, 3 or 6 moderators were taken up in the model.
@@
 *Predictive performance*
-Because the densities for the R2 values were either bimodal or skewed, it was chosen to use the median $R^{2}$ as the metric for predictive performance, rather than the mean.
+Because the densities for the $R^{2}$ values were either bimodal or skewed, it was chosen to use the median $R^{2}$ as the metric for predictive performance, rather than the mean.
 The spread of the data was described using the Mean Absolute Deviation [MAD], rather than the standard deviation.
@@
 
-To determine the effect of the design factors on predictive performance of all algorithms, four separate ANOVA’s was performed. The $η^{2}$ per condition per algorithm can be found in table 1.
+To determine the effect of the design factors on predictive performance of all algorithms, four separate ANOVA’s were performed.
+The effect size $η^{2}$ per condition per algorithm, including interactions can be found in table 1.
 
-Not too surprisingly, It was found that the true effect size *β* had the largest effect on the predictive $R^{2}$ for all algorithms.
-As *β* increased, the performance of all algorithms increased as well.
-However, *β* did seem to interact with the model that was estimated, being either a linear, two-way interaction, cubic or an exponential model.
+Not too surprisingly, It was found that the true effect size $β$ had the largest effect on the predictive $R^{2}$ for all algorithms.
+As $β$ increased, the performance of all algorithms increased as well.
+However, $β$ did seem to interact with the model that was estimated, being either a linear, two-way interaction, cubic or an exponential model.
 The image of the interaction is shown in image 1.
-The major difference seems to be that for all models, except the linear, the increase of *R2* slows for every higher value for *β*.
-The steepest increase for the linear model is when *β* increases from 0.2 to 0.4.
-Also noteworthy is that the two-way interaction model seems to stagnate as the effect size goes up to 0.4 onwards, while the other models do keep increasing, although not as severely.
+For the exponential and two-way interaction model, the increase of $R^{2}$ slows for every higher value for $β$.
+The cubic model only slows the increase when the es goes from 0.5 to 0.8, while the steepest increase for the linear model is when $β$ increases from 0.2 to 0.4.
+Also noteworthy is that the two-way interaction model seems to stagnate as the effect size goes up to 0.4 and onwards, while the other models do keep increasing.
 There seemed to be little difference in performance between Horsehoe, Lasso and RMA, while the random forest algorithm performed worst.
@@
 The second largest marginal effect was that of the estimated model.
-All algorithms performed best under the 2-way interaction model, followed by a similar performance on the cubic and exponential models.
-The linear model predicted worst performance for all algorithms.
-Horseshoe and Lasso performed best under all models, followed closely by RMA and lastly the random forest.
+It seemed that all algorithms performed best under the two-way interaction model, followed by a similar performance on the cubic and exponential models.
+All algorithms seemed to perform worst for the linear model.
+There again is little difference in performance between the Pema algorithms and RMA, altough the random forest performs worst.
 Image 2 shows the relationship.
 
-There also was a moderate interaction effect between the estimated model and the amount of skewness of the data [α], especially for the Pema algorithms.
-Again, the Horseshoe and Lasso algorithms performed best, followed by RMA and MetaForest in all conditions.
-Most obvious to note is that under all model, except the linear model, the algorithms benefitted when the $R^{2}$ was estimated on more skewed data.
-The two-way interaction model performs best under all levels of *α*, but is getting caught up by the exponential and cubic model as *α* increases.
+There also was a moderate interaction effect between the estimated model and the amount of skewness of the data [$α$], especially for the Pema algorithms.
+Again, Pema and RMA algorithms performed best, followed by MetaForest in all conditions.
+Most obvious to note is that all, except the linear model seem to benefit when the $R^{2}$ was estimated on more skewed data, although the algorithms do perform worse when the model is cubic and $α$ goes from 5 to 10.
+The two-way interaction model performs best overall, but is getting caught up by the exponential and cubic model as $α$ increases.
 Image 3 shows the relationship.
 
-The true residual heterogeneity $τ^{2}$ had a negative linear relationship for all algorithms on $R^{2}$.
-i.e.
-as $τ^{2}$ increases, $R^{2}$ decreased.
-The effect was slightly bigger for the Pema algorithms than for the other two.
-Still, both Horseshoe and Lasso performed best, followed by RMA and MetaForest.
-Image 4 shows the relationship.
+The true residual heterogeneity $τ^{2}$ had a negative linear relationship for all algorithms on $R^{2}$. i.e. as $τ^{2}$ increases, $R^{2}$ decreased. Image 4 shows the relationship.
 
-The mean sample size per study [n] also had a moderate effect, again namely for the Pema algorithms.
-For all algorithms the effect of *n* was positively linearly related to $R^{2}$ with the Pema algorithms performing best for all levels of *n*.
+The mean sample size per study [$n$] also had a moderate effect.
+For all algorithms the effect of $n$ was positively linearly related to $R^{2}$ with the Pema and RMA algorithms performing best and Metaforest performing worse.
 Image 5 shows the relationship.
@@
 Finally, the number of moderators did not have a big effect for the Pema algorithms, $η^{2}$ = 0.01 for both Horseshoe and Lasso while for RMA and Metaforest $η^{2}$ = 0.05.
-This relationship is generally negative with more moderators meaning worse performance, although a slight increase can be observed as the number of moderators increase from 6 to 7.
-The image and $η^{2}$ values indicate that the Pema algorithms seem more robust against number of moderators than RMA and MetaForest.
+This relationship is generally negative with more moderators meaning worse performance, although an increase can be observed as the number of moderators increase from 4 to 6 for all algorithms except Metaforest.
+This increase in performance for Metaforest appears when the number of moderators go from 3 to 4.
+Image 7 and $η^{2}$ values indicate that the Pema algorithms seem more robust against number of moderators than RMA and MetaForest.
+
+#Estimating residual heterogeneity ($τ^{2}$)
+The ability of the algorithms to correctly estimate $τ^{2}$ was operationalized by subtracting the true value for $τ^{2}$ from the $τ^{2}$ estimated by the algorithms.
+Again, the median and MAD were used as metrics for performance.
+The RMA algorithm showed the best results, $Med_{rma}$ = 0.02, MAD = 0.06, followed by the Metaforest algorithm $Med_{mf}$ = 0.09, MAD = 0.13.
+The Pema algorithms performed worst $Med_{lasso}$ = 0.23, MAD = 0.18; $Med_{hs}$ = 0.23, MAD = 0.17.
+The finding that all medians are positive implies that all algorithms have a bigger tendency to overestimate $τ^{2}$ than underestimate it.
+
+To determine the effect of the design factors on estimated $τ^{2}$ of all algorithms, four separate ANOVA’s were performed.
+The effect size $η^{2}$ per condition per algorithm, including interactions can be found in table 2.
 

### 2021-10-07 paper/manuscript.Rmd
Images in results.rtf
Tau2, implement Latex notation and code up until now used for analysis

@@
 
-The process of examining the relationship between study characteristics and the effect sizes is most often done by a meta-regression (Viechtbauer & López-López, 2015).
+The process of examining the relationship between study characteristics and the effect sizes is most often done by a meta-regression (Viechtbauer \& López-López, 2015).
 Meta-regression aims to relate the size of the effect to one or more characteristics of the studies involved.
@@
 However, when performing such an analysis, a lot of moderators are measured and it may be unclear which are relevant and which are not.
-There are a couple of reasons to explain this: Riley, Higgins & Deeks (2011) concluded that the number of studies is oftentimes overly small.
+There are a couple of reasons to explain this: Riley, Higgins \& Deeks (2011) concluded that the number of studies is oftentimes overly small.
 As a result of this heterogeneity cannot be inspected accurately.
-Also, there is an insufficiency in regard to techniques to downgrade the amount of possible moderators to a feasible number (Thompson & Higgins, 2002).
+Also, there is an insufficiency in regard to techniques to downgrade the amount of possible moderators to a feasible number (Thompson \& Higgins, 2002).
 This results in a large amount of moderators to be examined and a low quantity of studies.
@@
 Thus, there is a need of a regularization method to curtail overfitting.
-LASSO (L1-norm regularization) can fulfill this role, since it has an advantage in terms of feature selection.
+Least Absolute Shrinkage and Selection Operator [LASSO] (L1-norm regularization) can fulfill this role, since it has an advantage in terms of feature selection.
 The goal of this project is to implement L1-norm regularization in the weighted meta-regression, developing an new estimator for penalized meta-regression.
-More detailed explanation of methods and theoretical concepts
 
@@
 The first approach is referred to as the as the fixed-effect model.
-This model assumes that each observed effect size, obtained from each individual study, is an estimate of an underlying true effect size (Hedges & Vevea, 1998).
+This model assumes that each observed effect size, obtained from each individual study, is an estimate of an underlying true effect size (Hedges \& Vevea, 1998).
 The true effect sizes are treated as, unknown, constants.
 The only source that causes the deviation of the observed effect from the, unknown, true effects is sampling error.
-Thus, for a collection of k studies, the observed effects size $y_{i}$ of each individual study i (for i = 1,2, .
+Thus, for a collection of $k$ studies, the observed effects size $y_{i}$ of each individual study $i$ (for $i$ = 1,2, .
 .
 .
-k) is given by:
+$k$) is given by:
 
- $y_{i}$ = θ + $ϵ_{i}$						(1)
+ $y_{i}$ = $\theta$ + $\varepsilon_{i}$						(1)
 
-Where 𝜃 is the true effect size of each individual study i and $ϵ_{i}$ follows the distribution of N(0 , $v_{i}$) with $v_{i}$ being the sampling error or within-study variance, which is treated as a known factor.
+Where $\theta$ is the true effect size of each individual study $i$ and $\varepsilon_{i} \sim \mathcal{N}(0,\,\sigma_{i})\,$ with $\sigma_{i}$ being the sampling error or within-study variance, which is treated as a known factor.
 
 Fixed-effects meta-analysis considers sampling error to be the only cause of variance that influences the observed effect size.
-Studies with a large sample size will, as a result of this, produce more precise estimations of the underlying true effect size (Schmidt, Oh & Hayes, 2009).
+Studies with a large sample size will, as a result of this, produce more precise estimations of the underlying true effect size (Schmidt, Oh \& Hayes, 2009).
 Therefore, large sample sizes will contribute more to the weighted mean than small sample sizes.
@@
 
- $W_{i}$=  1/($σ^2_{i}$)						  (2)
+ $W_{i} =  \frac{1}{\sigma^2_{i}}$						  (2)
 
@@
 However, this assumption is implausible in plenty of meta-analysis.
-Especially in social sciences, the behaviour of people is extremely diverse and the contextual conditions for all humans vary to a great degree (Aronson, Wilson & Akert, 2016).
+Especially in social sciences, the behaviour of people is extremely diverse and the contextual conditions for all humans vary to a great degree (Aronson, Wilson \& Akert, 2016).
 A highly likely consequence is that this will lead to a huge amount of possible moderators (Caserio, 2014).
@@
 This approach makes an additional assumption, namely about the true effect sizes.
-Where the fixed-effect model treats the true effects as constants, the random-effect model assumes that the true effects are random and follow a distribution of their own (Hedges & Vevea, 1998).
-This means that variation in the observed effects (yi) in the random model incorporates not only the sampling error but also the variation of the true effect sizes (󠅵𝜏2) between the studies.
-In the case of the random effect model the observed effect size of yi is, given by:
+Where the fixed-effect model treats the true effects as constants, the random-effect model assumes that the true effects are random and follow a distribution of their own (Hedges \& Vevea, 1998).
+This means that variation in the observed effects ($y_{i}$) in the random model incorporates not only the sampling error but also the variation of the true effect sizes $\tau^{2}$ between the studies.
+In the case of the random effect model the observed effect size of $y_{i}$ is, given by:
 
- $y_{i}$ = $θ_{i}$+$ϵ_{i}$ 						(3)
+ $y_{i} = \theta_{i}+\varepsilon_{i}$ 						(3)
 
-With $ϵ_{i}$ ~ N(0 , $v_{i}$) but, in this case $𝜃_{i}$ on itself is given by:
+With $\varepsilon_{i} \sim \mathcal{N}(0,\,\sigma_{i})\,$ but, in this case $\theta_{i}$ on itself is given by:
 
- $θ_{i}$= μ + $ζ_{i}$						(4)
+ $theta_{i} = \mu + \zeta_{i}$						(4)
 
-With 𝜇 being the mean of the distribution of the true effect sizes and 𝜁i following the distribution N(0 , 𝜏2) with 𝜏2 being the variance of the population of true effect sizes.
+With $\mu$ being the mean of the distribution of the true effect sizes and $\zeta_{i} \sim \mathcal{N}(0,\,\tau^{2})\,$ with $\tau^2$ being the variance of the population of true effect sizes.
 It could also be explained as the variance between the individual studies.
@@
 
-W_i=1/(v_i+τ ̂^2 )						(5)
+ $W_{i} =  \frac{1}{\sigma^2_{i} + \tau^{2}}$						(5)
 In the case of the random-effect model, the within-study- and between-study variance is necessary for the calculation of the weights.
-It is important to note that in the calculation of the individual weights, an estimation of study heterogeneity is used (τ ̂^2).
-While the sampling error is known for each individual study, the true effect heterogeneity (󠅵𝜏2) remains unknown.
+It is important to note that in the calculation of the individual weights, an estimation of study heterogeneity is used $\tau^{2}$.
+While the sampling error is known for each individual study, the true effect heterogeneity $\tau^{2}$ remains unknown.
 Therefore, an estimation of the heterogeneity value needs to be made to effectively calculate the weights.
-This estimation of the between-study variance is thus represented by τ ̂^2.
+This estimation of the between-study variance is thus represented by $\tau^{2}$.
 
-Meta-regression
+**Meta-regression**
 In the case of fixed- and random-effect meta-analysis, the observed effects are treated as estimations of the underlying true effect.
@@
 In other words, the true effect is now replaced by the moderator effects.
-This is expressed with the following equation, where θ_i represents the underlying true effect, xi the moderators, βi the coefficients, with p being the number of moderators:
-θ_i=β_0+β_1 x_1+β_2 x_2+⋯+β_p x_p+ζ_i			(6)
+This is expressed with the following equation, where $\theta_{i}$ represents the underlying true effect, $x_{i}$ the moderators, $\beta_{i}$ the coefficients, with $p$ being the number of moderators:
+
+$\theta_{i}=\beta_{0}+ \beta_{1}x_{1}+ \beta_{2}x_{2} + ⋯ + \beta_{p}x_{p}+ \zeta_{i}$			(6)
+
 When this is substituted in the original equation it will result in:
-y_i=β_0+β_1 x_1+β_2 x_2+⋯+β_p x_p+ζ_i+ϵ_i			(7)
-The error term 𝜁i captures the residual heterogeneity after accounting for the moderators.
-This term is still included because it is often the case that there still remains heterogeneity unexplained after accounting for the moderators (Thompson & Sharp, 1999).
+
+$y_{i}=\beta_{0}+ \beta_{1}x_{1}+ \beta_{2}x_{2} + ⋯ + \beta_{p}x_{p}+ \zeta_{i} + \varepsilon_{i}$			(7)
+
+The error term $\zeta_{i}$ captures the residual heterogeneity after accounting for the moderators.
+This term is still included because it is often the case that there still remains heterogeneity unexplained after accounting for the moderators (Thompson \& Sharp, 1999).
 In this model the moderator effects are treated as fixed and the residual heterogeneity as random.
-Therefore, it is referred to as a mixed-effect meta-regression analysis model, in short, ME-MRA (Viechtbauer & López-López, 2015).
+Therefore, it is referred to as a mixed-effect meta-regression analysis model, in short, ME-MRA (Viechtbauer \& López-López, 2015).
 To solve this ME-MRA model, both the residual heterogeneity and the moderator coefficients need to be estimated.
-An accurate estimation of the residual heterogeneity contributes to a better interpretation of the effect of the moderators (Panityakul, Bumrungsup & Knapp, 2013).
-Estimating residual heterogeneity
-The topic of estimating the residual heterogeneity is a highly discussed one (Veroniki et al., 2016; Viechtbauer & López-López, 2015; Panityakul et al., 2013).
-The ability of the estimators to predict the residual heterogeneity is influenced by different factors, such as the number of studies (Guolo & Varin, 2017; Panityakul et al., 2013; Hardy & Thompson, 1996) included and the sample size of the individual studies (Panityakul et al., 2013).
-A third, and obvious factor, that is classified as relevant to model performance is heterogeneity among studies being meta-analysed (Kontopantelis & Reeves, 2011; Jackson & White, 2018).
-Coverage from models degrades when the residual heterogeneity increases, mostly when the amount of studies is small (Brockwell & Gorden, 2001).
+An accurate estimation of the residual heterogeneity contributes to a better interpretation of the effect of the moderators (Panityakul, Bumrungsup \& Knapp, 2013).
+
+**Estimating residual heterogeneity**
+The topic of estimating the residual heterogeneity is a highly discussed one (Veroniki et al., 2016; Viechtbauer \& López-López, 2015; Panityakul et al., 2013).
+The ability of the estimators to predict the residual heterogeneity is influenced by different factors, such as the number of studies (Guolo \& Varin, 2017; Panityakul et al., 2013; Hardy \& Thompson, 1996) included and the sample size of the individual studies (Panityakul et al., 2013).
+A third, and obvious factor, that is classified as relevant to model performance is heterogeneity among studies being meta-analysed (Kontopantelis \& Reeves, 2011; Jackson \& White, 2018).
+Coverage from models degrades when the residual heterogeneity increases, mostly when the amount of studies is small (Brockwell \& Gorden, 2001).
 Considering that all models their performance is linked to the accuracy of the estimate.
-According to Sidik & Jonkman (2007), it is generally the case that the larger true between-study variance is, the more biased the estimate can be, which diminishes the performance of the method.
-Methods for estimating residual heterogeneity
+According to Sidik \& Jonkman (2007), it is generally the case that the larger true between-study variance is, the more biased the estimate can be, which diminishes the performance of the method.
+
+**Methods for estimating residual heterogeneity**
 Numerous methods have been proposed to accurately estimate the residual heterogeneity, including the Hedges (HE), DerSimonian–Laird/Method of Moments (DL), Sidik and Jonkman (SJ), Maximum Likelihood (ML), Restricted Maximum Likelihood (REML), and Empirical Bayes (EB) method.
@@
 The Restricted Maximum Likelihood (REML) seems to produce the lowest bias under this condition and is therefore preferred (Panityakul et al., 2013; Hardy & Thompson, 1996).
-The REML is an iterative method.
-This iterative method needs a starting estimation of 𝜏2 to start, usually it gets estimated by one of the non-iterative methods (Viechtbauer & López-López, 2015).
-Besides the starting value of 𝜏2, it needs in every iteration an estimation of the regression coefficients of the moderators.
+The REML is an iterative method and needs a starting estimation of $\tau^{2}$ to start, usually it gets estimated by one of the non-iterative methods (Viechtbauer \& López-López, 2015).
+Besides the starting value of $\tau^{2}$, it needs in every iteration an estimation of the regression coefficients of the moderators.
 These are typically estimated by using the Weighted Least Squares (WLS) method.
 This is a variation of the Ordinary Least Squares (OLS), but in the case of meta-analysis it is necessary to assess weights to the coefficients.
-In systematic reviews large variation in standard errors is often observed, which will result in large heteroscedasticity in the estimation of the effects (Stanley & Doucouliagos, 2017).
+In systematic reviews large variation in standard errors is often observed, which will result in large heteroscedasticity in the estimation of the effects (Stanley \& Doucouliagos, 2017).
 The addition of weights is a way to adjust for this heteroscedasticity.
 The weights are formulated as presented in equation (5).
+
 The usage of a WLS method to estimate the regression coefficient may be problematic in the situation where a lot of moderators are measured without their specific effects, when the amount of studies is low and when moderators are dichotomous.
-The use of a least squares method will cause problems with the prediction accuracy and the model interpretability (James, Witten, Hastie, & Tibshirani, 2013).
+The use of a least squares method will cause problems with the prediction accuracy and the model interpretability (James, Witten, Hastie, \& Tibshirani, 2013).
 In the situation where a lot of moderators are measured and blindly included in the model, it may as well be the case that variables are included that are in fact not associated with the response.
@@
 When the number of variables exceeds the number of studies, the least squares method fails to produce one unique estimate and the method should not be used at all.
+
 However, a least squares method could still be somewhat valuable in some situations.
@@
 Given the various arguments, this paper provides an approach to tackle this problem of the least squares methods whilst still making use of a linear method.
-The weighted least squares are replaced with the so-called LASSO (least absolute shrinkage and selection operator) regression for the estimation of the regression coefficients.
-This algorithm shrinks or penalizes the regression coefficients and performs variable selection (James et al., 2013; Hesterberg, Choi, Meier, & Fraley, 2008).
+The weighted least squares are replaced with the so-called LASSO regression for the estimation of the regression coefficients.
+This algorithm shrinks or penalizes the regression coefficients and performs variable selection (James et al., 2013; Hesterberg, Choi, Meier, \& Fraley, 2008).
 
-Intro rma
-The rma algorithm is part of the software-package metafor in R, which is developed by Wolfgang Viechtbauer (2010, 2019).
-This algorithm is specifically developed to perform a meta-analysis or met-regression.
+**Intro rma**
+The rma algorithm is part of the software-package `metafor` in `R`, which is developed by Wolfgang Viechtbauer (2010, 2019).
+This algorithm is specifically developed to perform a meta-analysis or meta-regression.
 It allows to include different models, such as the fixed-, random- and mixed-effect model.
@@
 Then again, the residual heterogeneity gets estimated with the rma algorithm by using the new values of the coefficients.
-With these new values of 𝜏2, a new weighted lasso is performed for the estimations of the coefficients.
+With these new values of $\tau^{2}$, a new weighted lasso is performed for the estimations of the coefficients.
 This process continuous, until the residual heterogeneity converges to a certain value.
 
-Intro Lasso
+**Intro Lasso**
 The lasso is a technique that regularizes or constrains the coefficient estimates, better known as shrinking (James et al., 2013).
@@
 This is better known as the bias/variance tradeoff (Briscoe & Feldman, 2011).
+
 The Lasso shrinkage method is not the only shrinkage method, there do exist some others.
 Nevertheless, the lasso is in the case the best option.
-It possesses, as opposed to other methods, the ability to shrink the parameter not towards zero, but to be exactly zero (James et al., 2013; Hesterberg, Choi, Meier, & Fraley, 2008).
+It possesses, as opposed to other methods, the ability to shrink the parameter not towards zero, but to be exactly zero (James et al., 2013; Hesterberg, Choi, Meier, \& Fraley, 2008).
 This means that the lasso can perform variable selection, something that is specifically aimed for in this study.
+
 In line with other shrinkage methods the lasso makes use of a shrinkage penalty.
@@
 The following equation shows how the calculation of the RSS together with the shrinkage penalty:
-RSS=∑_(i=1)^n▒〖(y_i-β_0-∑_(j=1)^p▒〖β_j x_ij )^2+λ∑_(j=1)^p▒|β_j | 〗〗			(8)
-This equation shows that the shrinkage penalty consists of two variables, the tuning parameter lambda (𝜆) and the regression coefficients (𝛽).
+
+$RSS=\sum_{i=1}^{n}(y_{i} - \beta_{0} - \sum_{j=1}^{p}\beta_{j}x_{ij})^2 + \lambda\sum_{j=1}^{p}|\beta_{j}|$			(8)
+
+This equation shows that the shrinkage penalty consists of two variables, the tuning parameter $\lambda$ and the regression coefficients $\beta_{j}$.
 This means that, while the OLS tries to find the coefficients which explain as much variance as possible, due to the minimization of the RSS, the shrinkage penalty punishes this.
-Therefore, the coefficients are forced to shrink a certain amount, depending on the parameter lambda.
-If the lambda increases, it grows the impact of the shrinkage penalty on the RSS, with 𝜆 → ∞ shrinking all the coefficient to be zero, producing the null model.
-But, if the lambda is zero, the shrinkage penalty has no impact at all and it will produce the OLS estimates.
+Therefore, the coefficients are forced to shrink a certain amount, depending on the parameter $\lambda$.
+If the $\lambda$ increases, it grows the impact of the shrinkage penalty on the RSS, with $\lambda \to \infty$ shrinking all the coefficient to be zero, producing the null model.
+But, if the $\lambda$ is zero, the shrinkage penalty has no impact at all and it will produce the OLS estimates.
 
-Alternative to linear model: Tree Based models
+**Alternative to linear model: Tree Based models**
 An alternative that can perform variable selection, are tree-based models.
@@
 They are also more flexible in handling moderator interactions and non-linearity.
-As a result of that, they are better in modelling the complicated nature of human behaviour (Earp & Trafimow, 2015).
+As a result of that, they are better in modelling the complicated nature of human behaviour (Earp \& Trafimow, 2015).
 Decision trees split from the top down and group data in so-called ‘sub-nodes’, in which the data’s aspects are most homogeneous.
@@
 Still, singletree based models have some limitations.
-First of all, tree models are unstable, small fluctuations that are utilized to make the model have a possibility to lead to considerable alterations in the constructions of the tree (Dwyer and Holte, 2007).
+First of all, tree models are unstable, small fluctuations that are utilized to make the model have a possibility to lead to considerable alterations in the constructions of the tree (Dwyer \& Holte, 2007).
 Second, it has problems with seizing linearity, because it only makes ‘twofold splits’ (Steyerberg, 2019).
 At last, tree-based models are susceptible to overfitting (Hastie et al, 2009).
+
 There are also more complex tree-based models, known as random-forests, which surmount most of the disadvantages of singletree.
@@
 The somewhat low correlation between the models is fundamental, because uncorrelated models are able to produce ensemble predictions with a higher accuracy that any individual prediction.
-This is because the trees preserve each other from their own singular errors (Genuer, Poggi & Tuleau-Malot, 2010).
-The lower tendency to overfitting is another advantage of random forests over single trees (Bühlmann & Yu, 2002).
+This is because the trees preserve each other from their own singular errors (Genuer, Poggi \& Tuleau-Malot, 2010).
+The lower tendency to overfitting is another advantage of random forests over single trees (Bühlmann \& Yu, 2002).
 As well as the possibility to predict cases that are not components of the bootstrap sample of the tree.
@@
 MetaForest applies random-effects or fixed-effects weights to random forests.
-Based on two simulation studies, van Lissa (2017) examined the performance of fixed-effects, random-effects and unweighted MetaForest
+Based on two simulation studies, van Lissa (2017) examined the performance of fixed-effects, random-effects and unweighted MetaForest.
+
 The study displayed also other advantages from random forests over singletrees.
@@
 MetaForest can at the moment be considered as the best working technique to explore heterogeneity in meta-analysis.
-in van Lissa (2017), that only presented estimates of τ2 based on the raw data, we saw that MetaForest had certain robustness against a low number of studies.
+In van Lissa (2017), that only presented estimates of $\tau^{2}$ based on the raw data, we saw that MetaForest had certain robustness against a low number of studies.
 If moderators were continuously distributed, MetaForest had sufficient power at approximately 20 studies.
@@
 It is important to know how MetaForest performs in these kinds of situations.
-Algorithms and simulation + goal study
+
+**Algorithms and simulation + goal study**
 The goal of the present study was to test whether a ME-MRA model with the lasso algorithm is able to outperform the ME-MRA with least squares regression.
@@
 Besides that, if simulated correctly, it will not have any systematic errors or noise due to underlying models and it is more cost efficient.
-simulations are useful for evaluation of new methods like MetaForest and for the comparison with alternative methods like metaCART and the classic approaches.
+Simulations are useful for evaluation of new methods like MetaForest and for the comparison with alternative methods like metaCART and the classic approaches.
 
-Performance Criteria
+**Performance Criteria**
 The algorithms are evaluated on three different performance criteria: The algorithms’ predictive performance, their ability to estimate the residual heterogeneity and their ability to detect and select the right moderators.
@@
 The algorithms have to estimate a model on a “training” dataset and then use this model to see how well it fits on a second “testing” dataset.
-This is operationalized as the cross-validated R_cv^2 (Van Lissa, 2017).
-The R_cv^2 is calculated using the fraction of variance explained by the model on the testing dataset, relative to faction of variance explained by the mean of the testing dataset.
+This is operationalized as the cross-validated $R_{cv}^{2}$ (Van Lissa, 2017).
+The $R_{cv}^{2}$ is calculated using the fraction of variance explained by the model on the testing dataset, relative to faction of variance explained by the mean of the testing dataset.
 The mean of the testing dataset is the best prediction for the testing data when there is no model present (van Lissa, 2017).
-The calculation of R_cv^2 is expressed by the following equation:
-R_cv^2=1-(∑_(i=1)^n▒〖(y_i-y ̂_i )^2 〗)/(∑_(i=1)^n▒〖(y_i-y ̅)^2 〗)					(9)
-With n being the number of studies in the testing dataset, y ̂_i being the estimation for study i, and y ̅ being the mean of the training dataset. 
-	The ability of the algorithms to estimate the residual heterogeneity is by simply taking the value of 𝜏2 which the algorithm produces.
+The calculation of$R_{cv}^{2}$is expressed by the following equation:
+
+$R_{cv}^{2} = 1- \frac{\sum_{i=1}^{n}(y_{i}-\hat{y}_{i})^{2}}{\sum_{i=1}^{n}(y_{i}-\bar{y}_{i})^{2}}$					(9)
+
+With $n$ being the number of studies in the testing dataset, $\hat{y}_{i}$ being the estimation for study $i$, and $\bar{y}_{i}$ being the mean of the training dataset.
+
+The ability of the algorithms to estimate the residual heterogeneity is by simply taking the value of $\tau^{2}$ which the algorithm produces.
 The true value of the residual heterogeneity is subtracted of the estimated value, solely to make the values more interpretable.
@@
 The residual heterogeneity is used as a performance criterion because it is suspected that the lma model might not always be able to predict residual heterogeneity correctly.
+
 Variable selection is defined in terms of the algorithms ability to accredit positive variable importance values to relevant moderators.
@@
 
-Design factors
+**Design factors**
 In the simulation study, meta analytic datasets will be simulated.
@@
 For each combination of characteristics, or design factors, 100 datasets will be simulated.
-The design factors that will be manipulated are the number of studies in the training data k (22, 40 and 80), the average within-study sample size n ̅ (40, 100 and 200), the population effect size β (.2, .5 and .8) and the residual heterogeneity 𝜏2 (.01, .04 and .1).
+The design factors that will be manipulated are the number of studies in the training data $k$ (22, 40 and 80), the average within-study sample size $\bar{n}$ (40, 100 and 200), the population effect size $\beta$ (.2, .5 and .8) and the residual heterogeneity $\tau^{2}$ (.01, .04 and .1).
 All the datasets will contain 20 moderators of which 10 are relevant and 10 are irrelevant.
-The moderators are binary and are randomly drawn form a Bernoulli distribution with probability p=.5, which corresponds to an equal chance of being either one or zero.
-The dependent variable y_i represented by a Hedges’ g.
+The moderators are binary and follow $\sim \mathcal{Bern}(0.5)$, which corresponds to an equal chance of being either one or zero.
+The dependent variable $y_{i}$ represented by a $Hedges’ g$.
 This is an estimator which takes the standardized mean difference between a treatment and control group and is commonly used in meta-analysis (Van Lissa, 2017).
-The true effect size θ_i  is sampled out of a normal distribution.
-The mean is computed by the assessing the values of the coefficients β, with the values of the moderators and with the residual heterogeneity τ^2 (Van Lissa, 2017).
-This is in line with the calculation of θ_i represented in equation (6).
-The sampling error v_i is formed by varying the sizes of the samples of each study.
-The sample sizes n_i are drawn from a normal distribution with mean n ̅ and standard deviation n ̅⁄3 (Van Lissa, 2017).
-Data were simulated using the random-effects model, based on six models:
-(A) Main effect of one moderator, μ_i= βx_1i 
-(B) Two-way interaction, μ_i= βx_1i+ βx_2i+ βx_1i x_2i
-(C) Three-way interaction, 
-μ_i= βx_1i+ βx_2i+ βx_3i+ βx_1i x_2i+βx_1i x_3i+βx_2i x_3i+βx_1i x_2i x_3i
-(D) Two two-way interactions, μ_i= βx_1i+ βx_2i+ βx_3i+βx_4i+βx_1i x_2i+βx_3i x_4i
-(E) Non-linear, cubic relationship, μ_i= βx_1i+ βx_1i^2+βx_1i^3
-(F) Exponential relationship, μ_i= βe^x1i
+The true effect size $\theta_{i}$  is sampled out of a normal distribution.
+The mean is computed by the assessing the values of the coefficients $\beta_{j}$, with the values of the moderators and with the residual heterogeneity $\tau^{2}$ (Van Lissa, 2017).
+This is in line with the calculation of $\theta_{i}$ represented in equation (6).
+The sampling error $\sigma^{2}_{i}$ is formed by varying the sizes of the samples of each study.
+The sample sizes $n_{i} \sim \mathcal{N}(\bar{n}, \frac{\bar{n}}{3}$ (Van Lissa, 2017).
 
-Impact of design factors and hypotheses
+Data were simulated using the random-effects model, based on four models:
+(A) Main effect of one moderator, $\mu_{i}= \beta_{1}x_{1i}$ 
+(B) Two-way interaction, $\mu_{i}= \beta_{1}x_{1i} + \beta_{2}x_{2i} + \beta_{3}x_{1i}x_{2i}$ 
+(E) Non-linear, cubic relationship, $\mu_{i}= \beta_{1}x_{1i} + \beta_{2}x_{1i}^{2} + \beta_{3}x_{1i}^{3}$ 
+(F) Exponential relationship, $\mu_{i}= \beta_{1}e^{x_{1i}}$
+
+**Impact of design factors and hypotheses**
 These design factors are chosen on purpose, because they are hypothesized to have an influence on the predictive performance of the algorithms.
@@
 This means that some factor should, by increasing, make the data easier to be analyzed, or make it more difficult to analyze.
-The amount of studies included in the training data k has a positive influence on the variance explained by the different algorithms.
+The amount of studies included in the training data $k$ has a positive influence on the variance explained by the different algorithms.
 This is due to the fact that there are simply more data points available to fit a model on.
-The lma algorithm should be superior on the low value of k over the rma algorithm.
-The effect size β has a positive impact on the ability of the algorithms to explain variance.
-It can be hypothesized that the lma performs better at lower values of β because it is better equipped to detect and select variables when even when the amount of signal is low.
-The residual heterogeneity τ^2 should have a negative influence on the interpretability of the data.
+The lma algorithm should be superior on the low value of $k$ over the rma algorithm.
+The effect size $\beta$ has a positive impact on the ability of the algorithms to explain variance.
+It can be hypothesized that the lma performs better at lower values of $\beta$ because it is better equipped to detect and select variables when even when the amount of signal is low.
+The residual heterogeneity $\tau^{2}$ should have a negative influence on the interpretability of the data.
 Differences between the two algorithms could be present, but it remains unclear which would perform better.
-The lma might perform better when the amount of signal in the data is low or the noise is high, but it is also suspected to overestimate the amount of heterogeneity and this could worsen if the τ^2 increases.
-The n ̅ greatly influences the quality of the data.
+The lma might perform better when the amount of signal in the data is low or the noise is high, but it is also suspected to overestimate the amount of heterogeneity and this could worsen if the $\tau^{2}$ increases.
+The $\bar{n}$ greatly influences the quality of the data.
 Higher values of within-study sample sizes reduce the sampling error.
 This will lead to a better prediction by the algorithms.
-In conclusion: higher values of k, β and n ̅ will increase the quality of the data, where higher values of  τ^2 decrease the quality of the data.
+In conclusion: higher values of $k$, $\beta$ and  $\bar{n}$  will increase the quality of the data, where higher values of  $\tau^{2}$ decrease the quality of the data.
 The lma is suspected to perform significantly better when the quality of the data is low, especially when the amount of studies in the sample is low, with the exception of the performance of the lma on the estimation of the residual heterogeneity
@@
 Not too surprisingly, It was found that the true effect size $β$ had the largest effect on the predictive $R^{2}$ for all algorithms.
-As $β$ increased, the performance of all algorithms increased as well.
-However, $β$ did seem to interact with the model that was estimated, being either a linear, two-way interaction, cubic or an exponential model.
+As $\beta$ increased, the performance of all algorithms increased as well.
+However, $\beta$ did seem to interact with the model that was estimated, being either a linear, two-way interaction, cubic or an exponential model.
 The image of the interaction is shown in image 1.
-For the exponential and two-way interaction model, the increase of $R^{2}$ slows for every higher value for $β$.
-The cubic model only slows the increase when the es goes from 0.5 to 0.8, while the steepest increase for the linear model is when $β$ increases from 0.2 to 0.4.
+For the exponential and two-way interaction model, the increase of $R^{2}$ slows for every higher value for $\beta$.
+The cubic model only slows the increase when the es goes from 0.5 to 0.8, while the steepest increase for the linear model is when $\beta$ increases from 0.2 to 0.4.
 Also noteworthy is that the two-way interaction model seems to stagnate as the effect size goes up to 0.4 and onwards, while the other models do keep increasing.
-There seemed to be little difference in performance between Horsehoe, Lasso and RMA, while the random forest algorithm performed worst.
+There seemed to be little difference in performance between Horsehoe, Lasso and RMA, while MetaForest performed worst.
 
@@
 All algorithms seemed to perform worst for the linear model.
-There again is little difference in performance between the Pema algorithms and RMA, altough the random forest performs worst.
+There again is little difference in performance between the Pema algorithms and RMA, altough MetaForest performs worst.
 Image 2 shows the relationship.
 
-There also was a moderate interaction effect between the estimated model and the amount of skewness of the data [$α$], especially for the Pema algorithms.
+There also was a moderate interaction effect between the estimated model and the amount of skewness of the data [$\alpha$], especially for the Pema algorithms.
 Again, Pema and RMA algorithms performed best, followed by MetaForest in all conditions.
-Most obvious to note is that all, except the linear model seem to benefit when the $R^{2}$ was estimated on more skewed data, although the algorithms do perform worse when the model is cubic and $α$ goes from 5 to 10.
-The two-way interaction model performs best overall, but is getting caught up by the exponential and cubic model as $α$ increases.
+Most obvious to note is that all, except the linear model seem to benefit when the $R^{2}$ was estimated on more skewed data, although the algorithms do perform worse when the model is cubic and $\alpha$ goes from 5 to 10.
+The two-way interaction model performs best overall, but is getting caught up by the exponential and cubic model as $\alpha$ increases.
 Image 3 shows the relationship.
 
-The true residual heterogeneity $τ^{2}$ had a negative linear relationship for all algorithms on $R^{2}$. i.e. as $τ^{2}$ increases, $R^{2}$ decreased. Image 4 shows the relationship.
+The true residual heterogeneity $\tau^{2}$ had a negative linear relationship for all algorithms on $R^{2}$. i.e. as $\tau^{2}$ increases, $R^{2}$ decreased. Image 4 shows the relationship.
 
-The mean sample size per study [$n$] also had a moderate effect.
-For all algorithms the effect of $n$ was positively linearly related to $R^{2}$ with the Pema and RMA algorithms performing best and Metaforest performing worse.
+The mean sample size per study [$\bar{n}$] also had a moderate effect.
+For all algorithms the effect of $\bar{n}$ was positively linearly related to $R^{2}$ with the Pema and RMA algorithms performing best and Metaforest performing worse.
 Image 5 shows the relationship.
 
-An especially large effect was found for the number of studies used in the training data for MetaForest, $η^{2}$ = 0.27, while this effect was substantially smaller for RMA, $η^{2}$ = 0.11; Lasso, $η^{2}$ = 0.06 and; Horseshoe, $η^{2}$ = 0.05.
+An especially large effect was found for the number of studies used in the training data for MetaForest, $\eta^{2}$ = 0.27, while this effect was substantially smaller for RMA, $\eta^{2}$ = 0.11; Lasso, $\eta^{2}$ = 0.06 and; Horseshoe, $\eta^{2}$ = 0.05.
 The relationship is positively linear for all algorithms, but the slope is especially steep for MetaForest.
@@
 
-Finally, the number of moderators did not have a big effect for the Pema algorithms, $η^{2}$ = 0.01 for both Horseshoe and Lasso while for RMA and Metaforest $η^{2}$ = 0.05.
+Finally, the number of moderators did not have a big effect for the Pema algorithms, $\eta^{2}$ = 0.01 for both Horseshoe and Lasso while for RMA and Metaforest $\eta^{2}$ = 0.05.
 This relationship is generally negative with more moderators meaning worse performance, although an increase can be observed as the number of moderators increase from 4 to 6 for all algorithms except Metaforest.
 This increase in performance for Metaforest appears when the number of moderators go from 3 to 4.
-Image 7 and $η^{2}$ values indicate that the Pema algorithms seem more robust against number of moderators than RMA and MetaForest.
+Image 7 and $\eta^{2}$ values indicate that the Pema algorithms are more robust against number of moderators than RMA and MetaForest.
 
-#Estimating residual heterogeneity ($τ^{2}$)
-The ability of the algorithms to correctly estimate $τ^{2}$ was operationalized by subtracting the true value for $τ^{2}$ from the $τ^{2}$ estimated by the algorithms.
+*Estimating residual heterogeneity* ($τ^{2}$)
+The ability of the algorithms to correctly estimate $τ^{2}$ was operationalized by subtracting the true value for $\tau^{2}$ from the $\tau^{2}$ estimated by the algorithms.
 Again, the median and MAD were used as metrics for performance.
@@
 The Pema algorithms performed worst $Med_{lasso}$ = 0.23, MAD = 0.18; $Med_{hs}$ = 0.23, MAD = 0.17.
-The finding that all medians are positive implies that all algorithms have a bigger tendency to overestimate $τ^{2}$ than underestimate it.
+The finding that all medians are positive implies that all algorithms have a bigger tendency to overestimate $\tau^{2}$ than underestimate it.
+One general comment to make is that uncertainty of the estimates generally increased as $\Delta\tau^{2}$ also increased.
+This implies that there is more variation in performance as median performance worsens.
 
-To determine the effect of the design factors on estimated $τ^{2}$ of all algorithms, four separate ANOVA’s were performed.
-The effect size $η^{2}$ per condition per algorithm, including interactions can be found in table 2.
+To determine the effect of the design factors on estimated $\tau^{2}$ of all algorithms, four separate ANOVA’s were performed.
+The effect size $\eta^{2}$ per condition per algorithm, including interactions can be found in table 2.
+
+The estimated model had one of the biggest effect on the correct estimation of $τ^{2}$.
+This is mainly because the algorithms overestimate $\tau^{2}$ quite severely when the model contains two-way interactions.
+Image 8 shows the marginal relationship of the estimated model on $\Delta\tau^{2}$ .
+It becomes more clear why this overestimation occurs when showing the interaction between the effect size and the model estimated on $\Delta\tau^{2}$ shown in image 9.
+First note the general trend which seems to be that for all models, except the linear, $\tau^{2}$ gets more overestimated the higher the true effect size is.
+This is not the case for the linear algorithm, where the effect of $\beta$ on $\Delta\tau^{2}$  seems close to zero, except for MetaForest.
+However, note the scales for the y-axes.
+While the cubic, linear and stay well within a confined interval, the algorithms severely overestimate $\tau^{2}$ when the model contains two-way interaction terms.
+Especially Metaforests overestimation is substantial when $\beta$ = 0.8 and the estimated model contains two-way interactions with $Med_{hs}$ = 2.92, $MAD$ = 2.37, although all other algorithms also have a $\Delta\tau^{2} > 1$ in these conditions.
+Interestingly, the Pema algorithms even outperform the RMA algorithm within these conditions.
+The marginal effects of $\beta$ on $\Delta\tau^{2}$  are shown in image 10.
+MetaForest seems most affected by the increase in $\beta$, but in general performs better than the Pema algorithms when $\beta$ < 0.8.
+The RMA algorithm performs best overall.
+
+The marginal effect of the skewness of the data $\alpha$ on $\Delta\tau^{2}$  seems rather minimal.
+There is a slight decrease in $\Delta\tau^{2}$  as $\alpha$ increases, but it is hardly noticeable.
+However, this decrease becomes more clear when we add the interaction with the estimated model.
+Image 12 shows the conditional relationship.
+The algorithms seem rather unaffected by $\alpha$ for the linear model, and a small general decrease in $\Delta\tau^{2}$  as $\alpha$ increases can be seen in the exponential model.
+When the cubic model is estimated however, the algorithms seem to benefit as $\alpha$ increases, while for the two-way interaction model, $\Delta\tau^{2}$  first increases as $\alpha$ increases, and afterwards decreases.
+RMA performs best, followed by Metaforest.
+The Pema algorithms perform similar, but worst.
+
+The effect of the true $\tau^{2}$ on $\Delta\tau^{2}$  also seemed rather unnoticeable for the RMA and Metaforest algorithm.
+The tendency for the Pema algorithms on the other hand, was to overestimate $\tau^{2}$ more as the true $\tau^{2}$ increased.
+Image 12 shows the marginal relationship.
+
+The effect of the number of moderators on $\Delta\tau^{2}$  was not that large either.
+A small increase in $\Delta\tau^{2}$ can be seen in the RMA and Metaforest algorithm as the number of moderators increase, which is not found for the Pema algorithms.
+However, A small note that should be made is that the Metaforest algorithm does substantially increase in $\Delta\tau^{2}$  as more moderators are added when the estimated model contains two-way interactions.
+Image 13 shows the interaction between the number of moderators and the estimated model on $\Delta\tau^{2}$ .
+
+The number of studies used in the training data $\kappa$ only had a very substantial effect for the Metaforest algorithm.
+For Metaforest, the $\Delta\tau^{2}$  decreased quite rapidly if $\kappa$ increased, especially when the two-way interaction model was estimated.
+For the other algorithms, decreasing $\kappa$ seemed to have little to know effect on correctly estimating the residual heterogeneity.
+Image 14 shows the relationship.
+
+Finally, the average number of observations in the studies did not have a substantial effect on $\Delta\tau^{2}$  Image 15 shows the marginal relationship.
+
+*Variable selection*
+**currently working on**
 

### 2021-10-07 simulatie_2021/Analysis Sim2021_2.R

@@ -1,0 +1,776 @@
+####################
+# Data exploration #
+####################
+library(data.table)
+dat <- as.data.table(readRDS(r"(C:\Users\e_lib\OneDrive\Documents\Caspar Repositories\simulatie_2021\sim_results_2021-09-08.RData)"))
+newnames <- c('hs', 'lasso', 'mf_r', 'rma') #names of models
+conditions <- c("k_train", "mean_n", "es", "tau2","alpha_mod", "moderators", "model") #conditions that vary
+lc <- length(conditions) #length of conditions, handy for further code
+dat[, c(1:lc):=lapply(.SD, factor), .SDcols=c(1:lc)]
+
+
+#there are duplicated columns which contain the same values, we can omit those
+last <- function(x) { return( x[length(x)] ) } #function to obtain last element from vector
+unique_cols <- which(!duplicated(colnames(dat)))
+dat <- dat[ , unique_cols[1]:last(unique_cols)]
+
+#Checking for missing values
+library(stringr)
+
+#first we omit the columns that almost always have missing values which are the 'sel' columns
+lashs <- str_extract(colnames(dat), pattern = "[:alpha:]+_(ci|hdi)_sel_\\d") #regex to find relevant columns for las and hs
+lashs <-lashs[!is.na(lashs)] #omit na's from returned list
+
+mfrma <- str_extract(colnames(dat), pattern = "(mf|rma)_sel_\\d") #regex for rma and mf
+mfrma <-mfrma[!is.na(mfrma)] #omit na's
+
+#create df without sel columns and subset it for rows that contain more than 1 missing
+wo_sel_cols <- colnames(dat)[!colnames(dat) %in% c(lashs, mfrma)]
+dat_no_sel <- dat[ , .SD, .SDcols=c(conditions, wo_sel_cols)] #subset data
+MD <- dat_no_sel[rowSums(is.na(dat_no_sel)) > 0, ]
+View(MD) # problem is with rma
+
+#where is the problem?
+apply(MD[, 1:lc], 2, table) #cubic and exponential model
+
+
+##################################################
+# Predictive performance analyses - R2           #
+##################################################
+
+#subsets the data based on particular performance criterion
+#in this case test and train_r2
+analyzedat_test <- dat[ , .SD, .SDcols=c(conditions, paste0(newnames, "_test_r2"))]
[…]

### 2021-10-21 paper/manuscript.Rmd
Results and script for reproduction. Images are in seperate .rtf file, but not pushed due to size (67 MB).

@@
 
-#introduction
+# introduction
 **intro to meta-analysis**
@@
 
-#Results
+# Results
 There were 20 cases out of 388800 that had missing values on all metrics for the RMA algorithm.
@@
 However, since this makes up 0.005% of the data, the missing values were chosen to be omitted from further analysis.
+Another thing is that the two-way interaction model only has results when there were either 3,4 or 7 moderators taken up, while the other models only have results when there were 2,3 or 6 moderators.
+The effects of the moderators is therefore difficult to compare between the two-way interaction and the other models.
 
 *Predictive performance*
-Because the densities for the $R^{2}$ values were either bimodal or skewed, it was chosen to use the median $R^{2}$ as the metric for predictive performance, rather than the mean.
+Because the densities for the $R^{2}$ and $MSE$ values were skewed, it was chosen to use the median as the metric for predictive performance, rather than the mean.
 The spread of the data was described using the Mean Absolute Deviation [MAD], rather than the standard deviation.
-It was found that the Horseshoe, Lasso and RMA algorithm performed similarly overall, $Med_{hs}$ = 0.51, MAD = 0.36; $Med_{Lasso}$ = 0.50, MAD = 0.37; $Med_{RMA}$ = 0.50, MAD = 0.37.
-The random forest algorithm performed worst $Med_{rf}$ = 0.35, MAD = 0.38.
+It was found that the Horseshoe, Lasso and RMA algorithm performed similarly overall, $R^2_{hs} = 0.51 \pm 0.36$, $MSE_{hs} = 0.21 \pm 0.18$ ; $R^2_{Lasso} = 0.50 \pm 0.37$, $MSE_{Lasso} = 0.21\pm 0.19$; $R^2_{RMA} = 0.50 \pm 0.37$, $MSE_{RMA} = 0.22 \pm 0.23$ .
+The random forest algorithm performed worst on $R^2$ $R^2_{rf} = 0.35 \pm 0.38$, $MSE_{rf} = 0.22 \pm 0.19$
 
-To determine the effect of the design factors on predictive performance of all algorithms, four separate ANOVA’s were performed.
+To determine the effect of the design factors on predictive performance $R^2$ of all algorithms, four separate ANOVA’s were performed.
 The effect size $η^{2}$ per condition per algorithm, including interactions can be found in table 1.
+Do note that the ANOVA's were performed with the normality assumption violated.
+The estimates serve as a guidance, rather than an non-contestable result.
 
@@
 The image of the interaction is shown in image 1.
-For the exponential and two-way interaction model, the increase of $R^{2}$ slows for every higher value for $\beta$.
-The cubic model only slows the increase when the es goes from 0.5 to 0.8, while the steepest increase for the linear model is when $\beta$ increases from 0.2 to 0.4.
-Also noteworthy is that the two-way interaction model seems to stagnate as the effect size goes up to 0.4 and onwards, while the other models do keep increasing.
+For the exponential and cubic model, the increase of $R^{2}$ slows for every higher value for $\beta$.
+The two-way interaction model only slows the increase when the es goes from 0.5 to 0.8, while the steepest increase for the linear model is when $\beta$ increases from 0.2 to 0.4.
+Also noteworthy is that the cubic model seems to stagnate as the effect size goes up to 0.4 and onwards, while the other models do keep increasing.
 There seemed to be little difference in performance between Horsehoe, Lasso and RMA, while MetaForest performed worst.
@@
 The second largest marginal effect was that of the estimated model.
-It seemed that all algorithms performed best under the two-way interaction model, followed by a similar performance on the cubic and exponential models.
+It seemed that all algorithms performed best under the cubic model, followed by a similar performance on the two-way interaction and exponential models.
 All algorithms seemed to perform worst for the linear model.
@@
 Again, Pema and RMA algorithms performed best, followed by MetaForest in all conditions.
-Most obvious to note is that all, except the linear model seem to benefit when the $R^{2}$ was estimated on more skewed data, although the algorithms do perform worse when the model is cubic and $\alpha$ goes from 5 to 10.
-The two-way interaction model performs best overall, but is getting caught up by the exponential and cubic model as $\alpha$ increases.
+Most obvious to note is that all, except the linear model seem to benefit when the $R^{2}$ was estimated on more skewed data, although the algorithms do perform worse for the interaction model and $\alpha$ goes from 5 to 10.
+The cubic model performs best overall, but is getting caught up by the exponential and interactoin model as $\alpha$ increases.
 Image 3 shows the relationship.
@@
 The mean sample size per study [$\bar{n}$] also had a moderate effect.
-For all algorithms the effect of $\bar{n}$ was positively linearly related to $R^{2}$ with the Pema and RMA algorithms performing best and Metaforest performing worse.
+For all algorithms the effect of $\bar{n}$ was positively linearly related to $R^{2}$ with the Pema and RMA algorithms performing best and Metaforest performing worst.
 Image 5 shows the relationship.
@@
 Again, the median and MAD were used as metrics for performance.
-The RMA algorithm showed the best results, $Med_{rma}$ = 0.02, MAD = 0.06, followed by the Metaforest algorithm $Med_{mf}$ = 0.09, MAD = 0.13.
-The Pema algorithms performed worst $Med_{lasso}$ = 0.23, MAD = 0.18; $Med_{hs}$ = 0.23, MAD = 0.17.
+The RMA algorithm showed the best results, $\Delta\tau^2_{RMA} = 0.02 \pm 0.06$, followed by the Metaforest algorithm $\Delta\tau^2_{MF} = 0.09 \pm 0.13$.
+The Pema algorithms performed worst $\Delta\tau^2_{Lasso} = 0.23 \pm 0.18$; $\Delta\tau^2_{hs} = 0.23 \pm 0.17$.
 The finding that all medians are positive implies that all algorithms have a bigger tendency to overestimate $\tau^{2}$ than underestimate it.
-One general comment to make is that uncertainty of the estimates generally increased as $\Delta\tau^{2}$ also increased.
+One comment to make is that uncertainty of the estimates generally increased as $\Delta\tau^{2}$ also increased.
 This implies that there is more variation in performance as median performance worsens.
@@
 The effect size $\eta^{2}$ per condition per algorithm, including interactions can be found in table 2.
+Again, the assumption of normality was violated.
 
 The estimated model had one of the biggest effect on the correct estimation of $τ^{2}$.
-This is mainly because the algorithms overestimate $\tau^{2}$ quite severely when the model contains two-way interactions.
+This is mainly because the algorithms overestimate $\tau^{2}$ quite severely when the model contains cubic relationships.
 Image 8 shows the marginal relationship of the estimated model on $\Delta\tau^{2}$ .
@@
 However, note the scales for the y-axes.
-While the cubic, linear and stay well within a confined interval, the algorithms severely overestimate $\tau^{2}$ when the model contains two-way interaction terms.
-Especially Metaforests overestimation is substantial when $\beta$ = 0.8 and the estimated model contains two-way interactions with $Med_{hs}$ = 2.92, $MAD$ = 2.37, although all other algorithms also have a $\Delta\tau^{2} > 1$ in these conditions.
+While the interaction, linear and stay well within a confined interval, the algorithms severely overestimate $\tau^{2}$ when the model contains cubic terms.
+Especially Metaforests overestimation is substantial when $\beta$ = 0.8 and the estimated model is cubic with $\Delta\tau^{2}_{MF} = 2.92 \pm 2.37$, although all other algorithms also have a $\Delta\tau^{2} > 1$ in these conditions.
 Interestingly, the Pema algorithms even outperform the RMA algorithm within these conditions.
@@
 The algorithms seem rather unaffected by $\alpha$ for the linear model, and a small general decrease in $\Delta\tau^{2}$  as $\alpha$ increases can be seen in the exponential model.
-When the cubic model is estimated however, the algorithms seem to benefit as $\alpha$ increases, while for the two-way interaction model, $\Delta\tau^{2}$  first increases as $\alpha$ increases, and afterwards decreases.
+When the interaction model is estimated however, the algorithms seem to benefit as $\alpha$ increases, while for the cubic model, $\Delta\tau^{2}$  first increases as $\alpha$ increases, and afterwards decreases.
 RMA performs best, followed by Metaforest.
@@
 A small increase in $\Delta\tau^{2}$ can be seen in the RMA and Metaforest algorithm as the number of moderators increase, which is not found for the Pema algorithms.
-However, A small note that should be made is that the Metaforest algorithm does substantially increase in $\Delta\tau^{2}$  as more moderators are added when the estimated model contains two-way interactions.
+However, A small note that should be made is that the Metaforest algorithm does substantially increase in $\Delta\tau^{2}$  as more moderators are added when the estimated model is cubic.
 Image 13 shows the interaction between the number of moderators and the estimated model on $\Delta\tau^{2}$ .
 
-The number of studies used in the training data $\kappa$ only had a very substantial effect for the Metaforest algorithm.
-For Metaforest, the $\Delta\tau^{2}$  decreased quite rapidly if $\kappa$ increased, especially when the two-way interaction model was estimated.
-For the other algorithms, decreasing $\kappa$ seemed to have little to know effect on correctly estimating the residual heterogeneity.
+The number of studies used in the training data $\kappa$ only had a substantial effect for the Metaforest algorithm.
+For Metaforest, the $\Delta\tau^{2}$  decreased quite rapidly if $\kappa$ increased, especially when the cubic model was estimated.
+For the other algorithms, decreasing $\kappa$ seemed to have little to no effect on correctly estimating the residual heterogeneity.
 Image 14 shows the relationship.
@@
 *Variable selection*
-**currently working on**
+To determine the extent to which the algorithms could perform correct variable selection, the proportion true positives [TP] and true negatives [TN] were calculated.
+There were no differences in variables selected by Highest Density Intervals or Confidence Intervals for both Lasso and Horshoe and so for both algorithm it did not matter whether the Highest Density Interval or Confidence Interval were analyzed.
+The mean proportions along with the standard deviations on TP and TN are provided.
+It was found that Metaforest had the highest proportion true positives: $TP_{mf} = 0.98 \pm 0.15$, closely followed by RMA: $TP_{RMA} = 0.96 \pm 0.21$.
+Horshoe performed slightly better than Lasso;  $TP_{hs} = 0.91 \pm 0.29$; $TP_{Lasso} = 0.89 \pm 0.31$.
+As for TN, it was found that the pema algorithms performed best: $TN_{hs} = 0.93 \pm 0.16$, $TN_{Lasso} = 0.93 \pm 0.17$, followed by RMA: $TN_{RMA} = 0.89 \pm 0.20$.
+MF performed worst by a large margin: $TN_{mf} = 0.50 \pm 0.35$
+Perfomance on TP and TN were very high for all algorithms, with all mean proportions exceeding .89.
+One exception was the performance on TN for MetaForest, which mean was 0.50.
+This implies that MetaForest had issues excluding irrelevant moderators from the models.
+Plots were inspected to determine the effects of the design factors on the proportions.
+Something different to note is that there seem to be little marginal effects of the design factors on TN, while TP is more affected.
+It implies that the algorithms are more robust in excluding irrelevant moderators than in including relevant moderators.
+
+Firstly, $\kappa$ only had a marginal positive effect on TP.
+As $\kappa$ increased, TP also increased.
+This implies that the ability for all algorithms to attribute positive relevance to relevant moderators increased as the number of studies in the training dataset increased.
+MetaForest had the highest TP, followed by RMA and lastly Horshoe and Lasso.
+The increase in TP for higher values of $\kappa$ was steeper for the pema algorithms, however.
+There also seemed to exist an interaction of $\kappa$ with the estimated model.
+For the linear and interaction model, the relationship of $\kappa$ seemed relatively linear.
+At $\kappa = 20$ the TP was relatively low for the algorithms, compared to the cubic model where TP starts at .98 and converges to 1 as $\kappa$ increased.
+This latter relationship was also found for the exponential model, although the TP at $\kappa = 20$ was slighlty lower.
+Image 16 shows the interaction.
+
+The mean observations per study had a roughly positive linear relationship with TP for all algorithms.
+MetaForest performed best, followed by RMA, while Horseshoe and Lasso performed worst.
+Image 17 shows the relationship.
+
+The true effect size $\beta$ had an interaction effect with the model estimated on TN.
+Only for the interaction model, TN decreased as $\beta$ increased, For the other models, TN remained stable.
+This could be because the interaction model was only fitted when there were 3,4 or 7 moderators, while for the other models, only 2,3 or 6 moderators were used.
+Image 18 shows the relationship.
+The effect of $\beta$ on TP was positive; as $\beta$ increased, TP increased too.
+
+The true $\tau^2$ had a negative effect on TP, while skewness parameter $\alpha$ seemed to have little effect of both TP and TN. Image 19 shows the marginal relationship of $\tau^2$ on TP.
+
+Finally, there seemed to be an effect of number of moderators on TN only for the interaction model.
+The TN increased as the number of moderators did.
+Image 20 shows the relationship.
+The relationship was reversed for TP and was found for all algorithms, i.e.
+TP decreased as the number of moderators increased.
 

### 2021-10-21 simulatie_2021/Analysis Sim2021.R

@@ -1,760 +1,0 @@
-
-##################################################
-# Predictive performance analyses - Descriptives #
-##################################################
-library(data.table)
-dat <- as.data.table(readRDS(r"(C:\Users\e_lib\OneDrive\Documents\Caspar Repositories\simulatie_2021\sim_results_2021-08-11.RData)"))
-newnames <- c('hs', 'lasso', 'mf_r', 'rma') #names of models
-conditions <- c("k_train", "mean_n", "es", "tau2","alpha_mod", "moderators", "model") #conditions that vary
-lc <- length(conditions) #length of conditions, handy for further code
-
-#subsets the data based on particular performance criterion
-#in this case train_r2 and test_r2
-analyzedat_train <- dat[ , .SD, .SDcols=c(conditions, paste0(newnames, "_train_r2"))]
-analyzedat_test <- dat[ , .SD, .SDcols=c(conditions, paste0(newnames, "_test_r2"))]
-
-#converts the condition variables to factors
-analyzedat_train[, c(1:lc):=lapply(.SD, factor), .SDcols=c(1:7)]
-analyzedat_test[, c(1:lc):=lapply(.SD, factor), .SDcols=c(1:7)]
-
-setwd("./simulatie_2021")
-#sink("output.txt") #makes connection with a .txt file, use it later
-#unlink('output.txt') #unlinks the connection and deletes .txt file.
-
-
-#there are missing values in the data for train
-library(mice) #load in library
-
-#show where missings are and prodivde summary of the dataset to check for patterns
-misdat_pat <- function(df){
-  varmis <- (apply(df, 2, function(x){sum(is.na(x))})) #shows where missings are
-  cases_mis <- which(is.na(df)) #which cases are missing
-  missdat <- df[cases_rma_mis,] #subset data for missing cases
-  varmis_pat <- summary(missdat)
-  mispat <- md.pattern(missdat, plot = T) #shows where missings are and how many
-  return(list(variables_missing = varmis, pattern = varmis_pat))
-}
-
-misdat_pat(analyzedat_train) #17 missing in rma_train r2
-misdat_pat(analyzedat_test) #the same for the test data
-
-
[…]

### 2021-10-21 simulatie_2021/Analysis Sim2021_2.R

@@ -1,12 +1,20 @@
 ####################
 # Data exploration #
 ####################
-library(data.table)
+dependencies <- c('data.table', 'tidyverse', 'stringr', 'ggplot2')
+lapply(dependencies, function(x) library(x, character.only = T))
 dat <- as.data.table(readRDS(r"(C:\Users\e_lib\OneDrive\Documents\Caspar Repositories\simulatie_2021\sim_results_2021-09-08.RData)"))
-newnames <- c('hs', 'lasso', 'mf_r', 'rma') #names of models
+
+# load in needed functions
+source('./simulatie_2021/Analysis_functions.R') #created functions used for analysis
+
+#some data preprocessing
+newnames <- c('hs', 'lasso', 'mf_r', 'rma') #names of algorithms
 conditions <- c("k_train", "mean_n", "es", "tau2","alpha_mod", "moderators", "model") #conditions that vary
 lc <- length(conditions) #length of conditions, handy for further code
-dat[, c(1:lc):=lapply(.SD, factor), .SDcols=c(1:lc)]
+dat[, c(1:lc):=lapply(.SD, factor), .SDcols=c(1:lc)] #convert to factor
+dat$model <- as.factor(dat$model)
+levels(dat$model) <- c('exponential', 'linear', 'cubic', 'Twoway_interaction') #rename to more understandable levels
 
 
 #there are duplicated columns which contain the same values, we can omit those
@@ -15,27 +23,35 @@ unique_cols <- which(!duplicated(colnames(dat)))
 dat <- dat[ , unique_cols[1]:last(unique_cols)]
 
 #Checking for missing values
-library(stringr)
-
-#first we omit the columns that almost always have missing values which are the 'sel' columns
-lashs <- str_extract(colnames(dat), pattern = "[:alpha:]+_(ci|hdi)_sel_\\d") #regex to find relevant columns for las and hs
-lashs <-lashs[!is.na(lashs)] #omit na's from returned list
-
-mfrma <- str_extract(colnames(dat), pattern = "(mf|rma)_sel_\\d") #regex for rma and mf
-mfrma <-mfrma[!is.na(mfrma)] #omit na's
+#first we omit the columns that should contain missing values which are the 'sel' columns
+lashs <- colnames(dat)[grep(pattern = "_(ci|hdi)_sel_\\d", colnames(dat))]
+mfrma <- colnames(dat)[grep(pattern = "(mf|rma)_sel_\\d", colnames(dat))]
 
[…]

### 2021-10-21 simulatie_2021/Analysis_functions.R

@@ -1,0 +1,196 @@
+#creates traceplots for metrics
+Traceplot <- function(test, train, param, alg){
+  plot(x = 1:length(test), y = test, type = 'n', main = paste('Traceplot Test and Train', param , ' for', alg), xlab = 'iterations', ylab = paste('values for ', param)) #empty plot with correct dimensions for the traced values
+  lines(x = 1:length(test),  y = test, col = 'red') #superimpose traced values for testing r2
+  lines(x= 1: length(train), y = train, col = 'blue') #superimpose traced values for training r2
+  legend('bottomleft', c('Train R2', 'Test R2'), lty = 1, col = c('blue', 'red'), bg = 'white', cex = 0.75) #add informative legend
+}
+
+
+#creates densities for metric
+plotdens <- function(df){
+  df <- as.data.frame(df)
+  for(column in (lc+1):ncol(df)){ #plot densities for all algorithms
+    plot(density(df[,column]),
+         main = paste0('histogram of ', colnames(df)[column])
+         #xlim = c(-30,1)
+    )
+  }
+}
+
+#Check for significant moderators using eta squared
+EtaSq<-function (x)
+{
+  anovaResults <- summary.aov(x)[[1]]
+  anovaResultsNames <- rownames(anovaResults)
+  SS <- anovaResults[,2] #SS effects and residuals
+  k <- length(SS) - 1  # Number of factors
+  ssResid <- SS[k + 1]  # Sum of Squares Residual
+  ssTot <- sum(SS)  # Sum of Squares Total
+  SS <- SS[1:k] # takes only the effect SS
+  anovaResultsNames <- anovaResultsNames[1:k]
+  etaSquared <- SS/ssTot # Should be the same as R^2 values
+  partialEtaSquared <- SS/(SS + ssResid)
+  res <- cbind(etaSquared, partialEtaSquared)
+  colnames(res) <- c("Eta^2", "Partial Eta^2")
+  rownames(res) <- anovaResultsNames
+  return(res)
+}
+
+#functions for plotting marginal and conditional effects of design factors for algorithms
+plot_marginal_mean <- function(condition, df, lonames, metric){
+  condition <- as.name(condition)
+  hs <- as.name(lonames[1])
+  las <- as.name(lonames[2])
+  mf <- as.name(lonames[3])
+  rma <- as.name(lonames[4])
+
+  cond <- df %>%
[…]

### 2021-11-03 paper/manuscript.Rmd
fix latex

@@
 
-$\theta_{i}=\beta_{0}+ \beta_{1}x_{1}+ \beta_{2}x_{2} + ⋯ + \beta_{p}x_{p}+ \zeta_{i}$			(6)
+$\theta_{i}=\beta_{0}+ \beta_{1}x_{1}+ \beta_{2}x_{2} + \ldots + \beta_{p}x_{p}+ \zeta_{i}$			(6)
 
@@
 
-$y_{i}=\beta_{0}+ \beta_{1}x_{1}+ \beta_{2}x_{2} + ⋯ + \beta_{p}x_{p}+ \zeta_{i} + \varepsilon_{i}$			(7)
+$y_{i}=\beta_{0}+ \beta_{1}x_{1}+ \beta_{2}x_{2} + \ldots + \beta_{p}x_{p}+ \zeta_{i} + \varepsilon_{i}$			(7)
 
@@
 To determine the effect of the design factors on predictive performance $R^2$ of all algorithms, four separate ANOVA’s were performed.
-The effect size $η^{2}$ per condition per algorithm, including interactions can be found in table 1.
+The effect size $\eta^{2}$ per condition per algorithm, including interactions can be found in table 1.
 Do note that the ANOVA's were performed with the normality assumption violated.
@@
 
-Not too surprisingly, It was found that the true effect size $β$ had the largest effect on the predictive $R^{2}$ for all algorithms.
+Not too surprisingly, It was found that the true effect size $\beta$ had the largest effect on the predictive $R^{2}$ for all algorithms.
 As $\beta$ increased, the performance of all algorithms increased as well.
@@
 
-*Estimating residual heterogeneity* ($τ^{2}$)
-The ability of the algorithms to correctly estimate $τ^{2}$ was operationalized by subtracting the true value for $\tau^{2}$ from the $\tau^{2}$ estimated by the algorithms.
+*Estimating residual heterogeneity* ($\tau^{2}$)
+The ability of the algorithms to correctly estimate $\tau^{2}$ was operationalized by subtracting the true value for $\tau^{2}$ from the $\tau^{2}$ estimated by the algorithms.
 Again, the median and MAD were used as metrics for performance.
@@
 
-The estimated model had one of the biggest effect on the correct estimation of $τ^{2}$.
+The estimated model had one of the biggest effect on the correct estimation of $\tau^{2}$.
 This is mainly because the algorithms overestimate $\tau^{2}$ quite severely when the model contains cubic relationships.

### 2021-11-04 paper/manuscript.Rmd
rewrite part of intro

@@
 # introduction
-**intro to meta-analysis**
-Meta-analysis is a statistical method which utilizes several tools to synthesize the data of multiple studies on the same topic, with the purpose of finding a result that is more trustworthy.
-What meta-analysis does is simply weighting all the observed effect sizes of the individual studies and averaging them to one summary effect.
-Although this explanation is a bit too simplistic, in essence this is what meta-analysis is about.
-Meta-analysis assigns weights to each individual study based on different assumptions which are set in advance.
-These weights determine to what extent an individual study takes part in the eventual summary effect.
 
-Nevertheless, a serious concern is heterogeneity that is included between the studies in meta-analysis, which is caused due to clinical and/or methodological diversity.
-Heterogeneity causes a challenge to aggregate data, but it also offers a way to find characteristics of a study or “moderators” that could have impact on the found effect size.
+Meta-analysis is the practice of aggregating effect sizes from multiple similar studies.
+In its simplest form, a summary effect is computed as a weighted average of the observed effect sizes. 
+The weight assigned to each effect size is based on certain assumptions,
+and determines how influential it is in calculating the summary effect.
+For example, the *fixed effect* model assumes that all observed effect sizes reflect one underlying true population effect size.
+This assumption may be reasonable for close replication studies [@higgins_re-evaluation_2009, fabrigar_conceptualizing_2016, maxwell_is_2015]. 
+The *random effects* model, by contrast, assumes that population effect sizes follow a normal distribution.
+Each observed effect size provides information about the mean and standard deviation of this distribution of population effect sizes.
+This assumption is appropriate when studies are conceptually similar and differences between them are random [@higgins_re-evaluation_2009, fabrigar_conceptualizing_2016, maxwell_is_2015].
 
-The process of examining the relationship between study characteristics and the effect sizes is most often done by a meta-regression (Viechtbauer \& López-López, 2015).
-Meta-regression aims to relate the size of the effect to one or more characteristics of the studies involved.
-As multiple regression is used to assess the relationship between subject-level covariates and an outcome, meta-regression in meta-analysis is used to assess the relationship between study-level covariates and the effect size.
+Aside from random heterogeneity in effect sizes, quantifiable between-study differences may introduce systematic heterogeneity.
+Such between-study differences are known as "moderators".
+For example, if studies have been replicated in Europe and the Americas, this difference can be captured by a binary moderator called "continent".
+Alternatively, if studies have used different dosages of the same drug, this may be captured by a continuous moderator called "dosage".
+Systematic heterogeneity in the observed effect sizes can be accounted for using *meta-regression* (Viechtbauer \& López-López, 2015).
+This technique provides estimates of the effect of one or more study characteristics on the overall effect size,
+as well as of the overall effect size and residual heterogeneity after controlling for their influence.
 
-However, when performing such an analysis, a lot of moderators are measured and it may be unclear which are relevant and which are not.
-There are a couple of reasons to explain this: Riley, Higgins \& Deeks (2011) concluded that the number of studies is oftentimes overly small.
-As a result of this heterogeneity cannot be inspected accurately.
-Also, there is an insufficiency in regard to techniques to downgrade the amount of possible moderators to a feasible number (Thompson \& Higgins, 2002).
-This results in a large amount of moderators to be examined and a low quantity of studies.
-These kinds of conditions do not have a solid fit and predictive power in the classic meta-analysis approaches (van Lissa, 2017).
-For this obstacle there is a variable selection technique needed, that identifies moderators as strong or weak influencers of the observed effect size.
+Meta-analysis is often used to summarize existing bodies of literature.
+In such situations, the number of moderators is often relatively high because similar research questions have been studied in different laboratories,
+using different methods, instruments, and samples.
+Each of these between-study differences could be coded as a moderator, and some of these moderators may explain systematic heterogeneity.
+
+It is often not known beforehand which moderators are relevant and which are not.
+This introduces a methodological challenge,
+because the number of studies in meta-analyses is typically small (Riley, Higgins \& Deeks, 2011),
+resulting in low power to identify relevant moderators (Thompson \& Higgins, 2002).
+There is thus a need for a technique that can perform variable selection in meta-analysis, and which is relatively robust to small sample sizes.
+
+$$
+\begin{aligned}
+y_i &= \theta_i + \epsilon_i &\text{where } \epsilon_i \sim N(0, \sigma^2_i)\\ % \text{ and } 
+%\theta_1 &= \theta_2 \dots = \theta_k
+\end{aligned}
+$$
+
+., and methods have been developed to account for their influence.
+However, extant approaches lack the power to assess more than a handful of known moderators, or to investigate interactions between moderators, and non-linear effects.
+Heterogeneity between studies thus presents a non-trivial challenge to data aggregation using classic meta-analytic methods.
+At the same time, it also offers an unexploited opportunity to learn which differences between studies have an impact on the effect size found, if adequate exploratory techniques can be developed.
 

### 2021-11-06 paper/manuscript.Rmd
Update Manuscript Results

@@
 # Results
-There were 20 cases out of 388800 that had missing values on all metrics for the RMA algorithm.
-Closer inspection showed that both the cubic and exponential model each contributed 10 times to the missing values and only when 2, 3 or 6 moderators were taken up in the model.
-However, since this makes up 0.005% of the data, the missing values were chosen to be omitted from further analysis.
-Another thing is that the two-way interaction model only has results when there were either 3,4 or 7 moderators taken up, while the other models only have results when there were 2,3 or 6 moderators.
-The effects of the moderators is therefore difficult to compare between the two-way interaction and the other models.
+There were 3888 condition combinations and for each of those the algorithms ran 100 times, leaving 388800 cases to analyze.
+Out of those, 20 cases had missing values on all metrics for the RMA algorithm.
+Closer inspection showed that both the cubic and exponential model each contributed ten times to the missing values and only when 2, 3 or 6 moderators were taken up in the model.
+However, since these 20 cases make up only 0.005% of the data, the missing values were chosen to be omitted from further analysis.
+Another observation is that the two-way interaction model only had results when there were either 3,4 or 7 moderators taken up, while the other models only had results when there were 2,3 or 6 moderators.
+It is therefor more challenging to compare and interpret the effect the moderators had on the performance criteria between the two-way interaction and the other models.
 
-*Predictive performance*
-Because the densities for the $R^{2}$ and $MSE$ values were skewed, it was chosen to use the median as the metric for predictive performance, rather than the mean.
-The spread of the data was described using the Mean Absolute Deviation [MAD], rather than the standard deviation.
-It was found that the Horseshoe, Lasso and RMA algorithm performed similarly overall, $R^2_{hs} = 0.51 \pm 0.36$, $MSE_{hs} = 0.21 \pm 0.18$ ; $R^2_{Lasso} = 0.50 \pm 0.37$, $MSE_{Lasso} = 0.21\pm 0.19$; $R^2_{RMA} = 0.50 \pm 0.37$, $MSE_{RMA} = 0.22 \pm 0.23$ .
-The random forest algorithm performed worst on $R^2$ $R^2_{rf} = 0.35 \pm 0.38$, $MSE_{rf} = 0.22 \pm 0.19$
+## Predictive performance
+Predictive performance was operationalized by calculating the $R^2_{test}$ and $MSE_{test}$ for every combination of design factors, in further test denoted as $R^2$ and $MSE$ respectively.
+The densities for the $R^{2}_{test}$ and $MSE_{test}$ values were skewed however, which is why it was chosen to use the median $R^2$ as the metric for predictive performance, rather than the mean.
+The spread of the metrics was described using the Mean Absolute Deviation [MAD], rather than the standard deviation.
+It was found that the Horseshoe, Lasso and RMA algorithm performed similarly overall, $R^2_{Hs} = 0.51 \pm 0.36$, $MSE_{Hs} = 0.21 \pm 0.18$ ; $R^2_{Lasso} = 0.50 \pm 0.37$, $MSE_{Lasso} = 0.21\pm 0.19$; $R^2_{RMA} = 0.50 \pm 0.37$, $MSE_{RMA} = 0.22 \pm 0.23$ .
+The MetaForest algorithm performed worst on $R^2$: $R^2_{Mf} = 0.35 \pm 0.38$, $MSE_{Mf} = 0.22 \pm 0.19$
 
-To determine the effect of the design factors on predictive performance $R^2$ of all algorithms, four separate ANOVA’s were performed.
-The effect size $\eta^{2}$ per condition per algorithm, including interactions can be found in table 1.
+To determine the effect of the design factors on $R^2$ for all algorithms, four separate ANOVA’s were performed, one per algorithm.
+The effect size $\eta^{2}$ per condition per algorithm, including for all two-way interactions can be found in table 1.
 Do note that the ANOVA's were performed with the normality assumption violated.
-The estimates serve as a guidance, rather than an non-contestable result.
+The estimates serve mostly as a guidance, rather than an absolute result.
 
-Not too surprisingly, It was found that the true effect size $\beta$ had the largest effect on the predictive $R^{2}$ for all algorithms.
+Not too surprisingly, It was found that the true effect size $\beta$ had the largest effect on $R^{2}$ for all algorithms.
 As $\beta$ increased, the performance of all algorithms increased as well.
-However, $\beta$ did seem to interact with the model that was estimated, being either a linear, two-way interaction, cubic or an exponential model.
+However, $\beta$ did interact with the model that was estimated, being either a linear, two-way interaction, cubic or an exponential model.
 The image of the interaction is shown in image 1.
-For the exponential and cubic model, the increase of $R^{2}$ slows for every higher value for $\beta$.
-The two-way interaction model only slows the increase when the es goes from 0.5 to 0.8, while the steepest increase for the linear model is when $\beta$ increases from 0.2 to 0.4.
-Also noteworthy is that the cubic model seems to stagnate as the effect size goes up to 0.4 and onwards, while the other models do keep increasing.
-There seemed to be little difference in performance between Horsehoe, Lasso and RMA, while MetaForest performed worst.
+When the exponential and cubic model were estimated, the increase of $R^{2}$ slows for every higher value of $\beta$.
+For the estimation of the two-way interaction model the increase only slowed when $\beta$ goes from 0.5 to 0.8, while the steepest increase for the linear model estimation is when $\beta$ increases from 0.2 to 0.5.
+Also noteworthy is that $R^2$ stagnates during estimation of the cubic model as $\beta$ goes up to 0.5 and onwards, while the other models do keep increasing.
+There was little difference in median $R^2$ between Horsehoe, Lasso and RMA, while MetaForest performed worst.
 
 The second largest marginal effect was that of the estimated model.
-It seemed that all algorithms performed best under the cubic model, followed by a similar performance on the two-way interaction and exponential models.
-All algorithms seemed to perform worst for the linear model.
-There again is little difference in performance between the Pema algorithms and RMA, altough MetaForest performs worst.
+All algorithms had the highest $R^2$ under the cubic model, followed by a similar performance on the two-way interaction and exponential models.
+All algorithms performed worst for the linear model.
+There again was little difference in performance between the Pema algorithms and RMA, altough MetaForest performed worst.
 Image 2 shows the relationship.
 
-There also was a moderate interaction effect between the estimated model and the amount of skewness of the data [$\alpha$], especially for the Pema algorithms.
+There also was a moderate interaction effect between the estimated model and the amount of skewness of the input data $\alpha$, especially for the Pema algorithms.
 Again, Pema and RMA algorithms performed best, followed by MetaForest in all conditions.
-Most obvious to note is that all, except the linear model seem to benefit when the $R^{2}$ was estimated on more skewed data, although the algorithms do perform worse for the interaction model and $\alpha$ goes from 5 to 10.
-The cubic model performs best overall, but is getting caught up by the exponential and interactoin model as $\alpha$ increases.
+Most obvious to note is that all algorithms, except for when the linear model was estimated, generally performed better on more skewed data, although the algorithms did perform worse during estimation of the two-way interaction model and as $\alpha$ goes from 5 to 10.
+Overall performance was best during estimation of the cubic model, but the performance difference between estimated models decreased as $\alpha$ increased.
 Image 3 shows the relationship.
 
-The true residual heterogeneity $\tau^{2}$ had a negative linear relationship for all algorithms on $R^{2}$. i.e. as $\tau^{2}$ increases, $R^{2}$ decreased. Image 4 shows the relationship.
+The true residual heterogeneity $\tau^{2}$ had a negative linear relationship for all algorithms on $R^{2}$. That is, as $\tau^{2}$ increased, $R^{2}$ decreased. Image 4 shows the relationship.
 
-The mean sample size per study [$\bar{n}$] also had a moderate effect.
-For all algorithms the effect of $\bar{n}$ was positively linearly related to $R^{2}$ with the Pema and RMA algorithms performing best and Metaforest performing worst.
+The mean sample size per study $\bar{n}$ also had a moderate effect.
+For all algorithms the effect of $\bar{n}$ was positively linearly related with $R^{2}$.
+Again, the Pema and RMA algorithms performed better than MetaForest.
 Image 5 shows the relationship.
 
-An especially large effect was found for the number of studies used in the training data for MetaForest, $\eta^{2}$ = 0.27, while this effect was substantially smaller for RMA, $\eta^{2}$ = 0.11; Lasso, $\eta^{2}$ = 0.06 and; Horseshoe, $\eta^{2}$ = 0.05.
+An especially large effect was found for the number of studies used in the training data $\kappa$ for MetaForest, $\eta^{2} = 0.27$, while this effect was substantially smaller for RMA, $\eta^{2} = 0.11$; Lasso, $\eta^{2} = 0.06$ and; Horseshoe, $\eta^{2} = 0.05$.
 The relationship is positively linear for all algorithms, but the slope is especially steep for MetaForest.
@@
 
-Finally, the number of moderators did not have a big effect for the Pema algorithms, $\eta^{2}$ = 0.01 for both Horseshoe and Lasso while for RMA and Metaforest $\eta^{2}$ = 0.05.
-This relationship is generally negative with more moderators meaning worse performance, although an increase can be observed as the number of moderators increase from 4 to 6 for all algorithms except Metaforest.
-This increase in performance for Metaforest appears when the number of moderators go from 3 to 4.
-Image 7 and $\eta^{2}$ values indicate that the Pema algorithms are more robust against number of moderators than RMA and MetaForest.
+Finally, the number of moderators did not have a big effect for the Pema algorithms: $\eta^{2} = 0.01$ while for RMA and MetaForest $\eta^{2} = 0.05$.
+The relationship is shown in image 7.
+The relationship is generally negative with more moderators meaning worse performance, although an increase can be observed as the number of moderators increase from 4 to 6 for all algorithms except MetaForest.
+This increase in performance for MetaForest appears when the number of moderators go from 3 to 4.
 
-*Estimating residual heterogeneity* ($\tau^{2}$)
+## Estimating residual heterogeneity
 The ability of the algorithms to correctly estimate $\tau^{2}$ was operationalized by subtracting the true value for $\tau^{2}$ from the $\tau^{2}$ estimated by the algorithms.
-Again, the median and MAD were used as metrics for performance.
-The RMA algorithm showed the best results, $\Delta\tau^2_{RMA} = 0.02 \pm 0.06$, followed by the Metaforest algorithm $\Delta\tau^2_{MF} = 0.09 \pm 0.13$.
-The Pema algorithms performed worst $\Delta\tau^2_{Lasso} = 0.23 \pm 0.18$; $\Delta\tau^2_{hs} = 0.23 \pm 0.17$.
+Again, the median and Mean Absolute Deviation were used as metrics for performance.
+The RMA algorithm showed the best results, $\Delta\tau^2_{RMA} = 0.02 \pm 0.06$, followed by the MetaForest algorithm $\Delta\tau^2_{Mf} = 0.09 \pm 0.13$.
+The Pema algorithms performed worst $\Delta\tau^2_{Lasso} = 0.23 \pm 0.18$; $\Delta\tau^2_{Hs} = 0.23 \pm 0.17$.
 The finding that all medians are positive implies that all algorithms have a bigger tendency to overestimate $\tau^{2}$ than underestimate it.
 One comment to make is that uncertainty of the estimates generally increased as $\Delta\tau^{2}$ also increased.
-This implies that there is more variation in performance as median performance worsens.
+This implies that there was more variation in performance as median performance worsened.
 
-To determine the effect of the design factors on estimated $\tau^{2}$ of all algorithms, four separate ANOVA’s were performed.
-The effect size $\eta^{2}$ per condition per algorithm, including interactions can be found in table 2.
+To determine the effect of the design factors on $\Delta\tau^{2}$ for all algorithms, four separate ANOVA’s were performed.
+The effect size $\eta^{2}$ per condition per algorithm, including $\eta^2$ for all two-way interactions can be found in table 2.
 Again, the assumption of normality was violated.
 
-The estimated model had one of the biggest effect on the correct estimation of $\tau^{2}$.
-This is mainly because the algorithms overestimate $\tau^{2}$ quite severely when the model contains cubic relationships.
+The biggest predictor on the correct estimation of $\tau^{2}$ was the estimated model.
+This was mainly because the algorithms overestimated $\tau^{2}$ most when the model contained cubic terms.
 Image 8 shows the marginal relationship of the estimated model on $\Delta\tau^{2}$ .
-It becomes more clear why this overestimation occurs when showing the interaction between the effect size and the model estimated on $\Delta\tau^{2}$ shown in image 9.
-First note the general trend which seems to be that for all models, except the linear, $\tau^{2}$ gets more overestimated the higher the true effect size is.
-This is not the case for the linear algorithm, where the effect of $\beta$ on $\Delta\tau^{2}$  seems close to zero, except for MetaForest.
+It becomes more clear why this overestimation occurred when showing the interaction between $\beta$ and the model estimated on $\Delta\tau^{2}$, shown in image 9.
+First note the general trend that during estimation of all models $\tau^{2}$ got more overestimated as $\beta$ increased, except during estimation of the linear model, where the effect of $\beta$ on $\Delta\tau^{2}$ was close to zero, except for MetaForest.
 However, note the scales for the y-axes.
-While the interaction, linear and stay well within a confined interval, the algorithms severely overestimate $\tau^{2}$ when the model contains cubic terms.
-Especially Metaforests overestimation is substantial when $\beta$ = 0.8 and the estimated model is cubic with $\Delta\tau^{2}_{MF} = 2.92 \pm 2.37$, although all other algorithms also have a $\Delta\tau^{2} > 1$ in these conditions.
-Interestingly, the Pema algorithms even outperform the RMA algorithm within these conditions.
+While estimating the two-way interaction, linear and exponential model, $\Delta\tau^2$ stayed well within a confined interval.
+However, the algorithms severely overestimated $\tau^{2}$ when the model contained cubic terms.
+Especially MetaForest overestimated $\tau^{2}$ substantially when $\beta = 0.8$ and the estimated model is cubic: $\Delta\tau^{2}_{MF} = 2.92 \pm 2.37$.
+The other algorithms also had a $\Delta\tau^{2} > 1$ in these conditions, but the results were not as severe.
+Interestingly, the Pema algorithms even outperformed the RMA algorithm in these conditions.
+
 The marginal effects of $\beta$ on $\Delta\tau^{2}$  are shown in image 10.
-MetaForest seems most affected by the increase in $\beta$, but in general performs better than the Pema algorithms when $\beta$ < 0.8.
-The RMA algorithm performs best overall.
+MetaForest was most affected by the increase in $\beta$, but in general performed better than the Pema algorithms when $\beta < 0.8$.
+The RMA algorithm performed best overall.
 
-The marginal effect of the skewness of the data $\alpha$ on $\Delta\tau^{2}$  seems rather minimal.
-There is a slight decrease in $\Delta\tau^{2}$  as $\alpha$ increases, but it is hardly noticeable.
-However, this decrease becomes more clear when we add the interaction with the estimated model.
-Image 12 shows the conditional relationship.
-The algorithms seem rather unaffected by $\alpha$ for the linear model, and a small general decrease in $\Delta\tau^{2}$  as $\alpha$ increases can be seen in the exponential model.
-When the interaction model is estimated however, the algorithms seem to benefit as $\alpha$ increases, while for the cubic model, $\Delta\tau^{2}$  first increases as $\alpha$ increases, and afterwards decreases.
-RMA performs best, followed by Metaforest.
-The Pema algorithms perform similar, but worst.
+The marginal effect of $\alpha$ on $\Delta\tau^{2}$ was rather minimal, altough there was a slight decrease in $\Delta\tau^{2}$ as $\alpha$ increased.
+However, the decrease is more explicit when the interaction of $\alpha$ with the estimated model is added.
+Image 11 shows this interaction.
+The algorithms were rather unaffected by $\alpha$ for the linear model, and a small decrease in $\Delta\tau^{2}$ as $\alpha$ increased can be seen in the exponential model.
+When the two-way interaction model is estimated however, the algorithms benefitted as $\alpha$ increased, while for the cubic model, $\Delta\tau^{2}$ first increased as $\alpha$ increased from 0 to 2, but decreased as $\alpha$ increased from 2 to 10.
+RMA performed best, followed by MetaForest.
+The Pema algorithms performed similarly, but worst.
 
-The effect of the true $\tau^{2}$ on $\Delta\tau^{2}$  also seemed rather unnoticeable for the RMA and Metaforest algorithm.
+The effect of the true $\tau^{2}$ on $\Delta\tau^{2}$ was rather unnoticeable for the RMA and MetaForest algorithms.
 The tendency for the Pema algorithms on the other hand, was to overestimate $\tau^{2}$ more as the true $\tau^{2}$ increased.
@@
 The effect of the number of moderators on $\Delta\tau^{2}$  was not that large either.
-A small increase in $\Delta\tau^{2}$ can be seen in the RMA and Metaforest algorithm as the number of moderators increase, which is not found for the Pema algorithms.
-However, A small note that should be made is that the Metaforest algorithm does substantially increase in $\Delta\tau^{2}$  as more moderators are added when the estimated model is cubic.
-Image 13 shows the interaction between the number of moderators and the estimated model on $\Delta\tau^{2}$ .
+A small increase in $\Delta\tau^{2}$ can be seen in the RMA and MetaForest algorithm as the number of moderators increased, which was not found for the Pema algorithms.
+However, A small note is that MetaForest did substantially increase in $\Delta\tau^{2}$ as more moderators were added and the estimated model is cubic.
+Image 13 shows the interaction between the number of moderators and the estimated model.
 
-The number of studies used in the training data $\kappa$ only had a substantial effect for the Metaforest algorithm.
-For Metaforest, the $\Delta\tau^{2}$  decreased quite rapidly if $\kappa$ increased, especially when the cubic model was estimated.
-For the other algorithms, decreasing $\kappa$ seemed to have little to no effect on correctly estimating the residual heterogeneity.
+$\kappa$ only had a substantial effect for MetaForest; the $\Delta\tau^{2}$  decreased quite rapidly if $\kappa$ increased, especially when the cubic model was estimated.
+For the other algorithms, decreasing $\kappa$ had little to no effect on correctly estimating the residual heterogeneity.
 Image 14 shows the relationship.
 
-Finally, the average number of observations in the studies did not have a substantial effect on $\Delta\tau^{2}$  Image 15 shows the marginal relationship.
+Finally, the average number of observations in the studies did not have a substantial effect on $\Delta\tau^{2}$. Image 15 shows the marginal relationship.
 
-*Variable selection*
-To determine the extent to which the algorithms could perform correct variable selection, the proportion true positives [TP] and true negatives [TN] were calculated.
-There were no differences in variables selected by Highest Density Intervals or Confidence Intervals for both Lasso and Horshoe and so for both algorithm it did not matter whether the Highest Density Interval or Confidence Interval were analyzed.
-The mean proportions along with the standard deviations on TP and TN are provided.
-It was found that Metaforest had the highest proportion true positives: $TP_{mf} = 0.98 \pm 0.15$, closely followed by RMA: $TP_{RMA} = 0.96 \pm 0.21$.
-Horshoe performed slightly better than Lasso;  $TP_{hs} = 0.91 \pm 0.29$; $TP_{Lasso} = 0.89 \pm 0.31$.
-As for TN, it was found that the pema algorithms performed best: $TN_{hs} = 0.93 \pm 0.16$, $TN_{Lasso} = 0.93 \pm 0.17$, followed by RMA: $TN_{RMA} = 0.89 \pm 0.20$.
-MF performed worst by a large margin: $TN_{mf} = 0.50 \pm 0.35$
-Perfomance on TP and TN were very high for all algorithms, with all mean proportions exceeding .89.
-One exception was the performance on TN for MetaForest, which mean was 0.50.
+## Variable selection
+To determine the extent to which the algorithms could perform variable selection correctly, the proportion true positives [$TP$] and true negatives [$TN$] were calculated.
+The $TP$ and $TN$ reflect how well the algorithms accredit importance to relevant moderators and discredit importance to irrelevant moderators respectively.
+It should be noted that $TP$ could only take on values 1 or 0 per simulated iteration, because in all models where $\beta > 0$, only one moderator was simulated to be relevant.
+As $\beta$ increased, the already relevant moderator increased in relevance, rather than spreading the relevance over the other moderators.
+$TN$ had a bigger range and could take on values dependent on how many moderators were taken up in the model.
+E.g.
+when $\beta = 0$ and $n_{mods} = n$, $n+1$ different proportions were possible, $\frac{0}{n}$ up until $\frac{n}{n}$.
+
+There were no differences in variables selected by Highest Density Intervals or Confidence Intervals for both Lasso and Horshoe and so for both algorithms it did not matter which interval type was analyzed.
+It was found that MetaForest had the highest proportion true positives: $TP_{Mf} = 0.98$, closely followed by RMA: $TP_{RMA} = 0.96$.
+Horshoe performed slightly better than Lasso;  $TP_{Hs} = 0.91$; $TP_{Lasso} = 0.89$.
+As for $TN$, it was found that the pema algorithms performed best: $TN_{Hs} \ \text{and} \ TN_{Lasso} = 0.93$, followed by RMA: $TN_{RMA} = 0.89 \pm 0.20$.
+MetaForest performed worst by a large margin: $TN_{Mf} = 0.50$.
+The Mean Absolute Deviation for all algorithms on both $TP$ and $TN$ was 0, except for MetaForests performance on $TN$, where the Mean Absolute Deviation was 0.44.
+
+Perfomance on $TP$ and $TN$ were very high for all algorithms, with all mean proportions, except MetaForests performance on $TN$, exceeding .89.
 This implies that MetaForest had issues excluding irrelevant moderators from the models.
 Plots were inspected to determine the effects of the design factors on the proportions.
-Something different to note is that there seem to be little marginal effects of the design factors on TN, while TP is more affected.
-It implies that the algorithms are more robust in excluding irrelevant moderators than in including relevant moderators.
+While inspecting the plots, there were found to be little marginal effects of the design factors on $TN$, while $TP$ was more affected.
 
-Firstly, $\kappa$ only had a marginal positive effect on TP.
-As $\kappa$ increased, TP also increased.
-This implies that the ability for all algorithms to attribute positive relevance to relevant moderators increased as the number of studies in the training dataset increased.
-MetaForest had the highest TP, followed by RMA and lastly Horshoe and Lasso.
-The increase in TP for higher values of $\kappa$ was steeper for the pema algorithms, however.
-There also seemed to exist an interaction of $\kappa$ with the estimated model.
-For the linear and interaction model, the relationship of $\kappa$ seemed relatively linear.
-At $\kappa = 20$ the TP was relatively low for the algorithms, compared to the cubic model where TP starts at .98 and converges to 1 as $\kappa$ increased.
-This latter relationship was also found for the exponential model, although the TP at $\kappa = 20$ was slighlty lower.
-Image 16 shows the interaction.
+Firstly, $\kappa$ only had a marginal positive effect on $TP$.
+As $\kappa$ increased, $TP$ also increased.
+MetaForest had the highest $TP$, followed by RMA and, lastly, Horsehoe and Lasso.
+The increase in $TP$ for higher values of $\kappa$ was steeper for the Pema algorithms, however.
+There was also an interaction of $\kappa$ with the estimated model shown in image 16.
+During estimation of the linear and two-way interaction model, the relationship of $\kappa$ looked relatively linear.
+At $\kappa = 20$ the $TP$ was relatively low for the algorithms, compared to the cubic model where $TP$ starts at .98 and converges to 1 as $\kappa$ increased.
+This latter relationship was also found for the exponential model, although the $TP$ at $\kappa = 20$ was lower.
 
-The mean observations per study had a roughly positive linear relationship with TP for all algorithms.
+$\bar{n}$ had a positive and roughly linear relationship with $TP$ for all algorithms.
 MetaForest performed best, followed by RMA, while Horseshoe and Lasso performed worst.
@@
 
-The true effect size $\beta$ had an interaction effect with the model estimated on TN.
-Only for the interaction model, TN decreased as $\beta$ increased, For the other models, TN remained stable.
+$\beta$ had an interaction effect with the model estimated on $TN$.
+Only during estimation of the two-way interaction model, $TN$ decreased as $\beta$ increased, For the other models, $TN$ remained stable.
 This could be because the interaction model was only fitted when there were 3,4 or 7 moderators, while for the other models, only 2,3 or 6 moderators were used.
 Image 18 shows the relationship.
-The effect of $\beta$ on TP was positive; as $\beta$ increased, TP increased too.
+The effect of $\beta$ on $TP$ was positive; as $\beta$ increased, $TP$ increased too.
 
-The true $\tau^2$ had a negative effect on TP, while skewness parameter $\alpha$ seemed to have little effect of both TP and TN. Image 19 shows the marginal relationship of $\tau^2$ on TP.
+The true $\tau^2$ had a negative effect on $TP$, while $\alpha$ seemed to have little effect on both $TP$ and $TN$. Image 19 shows the marginal relationship of $\tau^2$ on $TP$.
 
-Finally, there seemed to be an effect of number of moderators on TN only for the interaction model.
-The TN increased as the number of moderators did.
-Image 20 shows the relationship.
-The relationship was reversed for TP and was found for all algorithms, i.e.
-TP decreased as the number of moderators increased.
+Finally, there seemed to be an effect of number of moderators on $TN$, but only for the two-way interaction model.
+The $TN$ increased as the number of moderators did.
+Image 20 shows the interaction.
+This relationship was reversed for $TP$ and was found for all algorithms, i.e.
+$TP$ decreased as the number of moderators increased.
+
+# Discussion
 

### 2021-11-06 paper/manuscript.Rmd
Update Results Manuscript

@@
 All algorithms performed worst for the linear model.
-There again was little difference in performance between the Pema algorithms and RMA, altough MetaForest performed worst.
+There again was little difference in performance between the Pema algorithms and RMA, although MetaForest performed worst.
 Image 2 shows the relationship.
@@
 
-The marginal effect of $\alpha$ on $\Delta\tau^{2}$ was rather minimal, altough there was a slight decrease in $\Delta\tau^{2}$ as $\alpha$ increased.
+The marginal effect of $\alpha$ on $\Delta\tau^{2}$ was rather minimal, although there was a slight decrease in $\Delta\tau^{2}$ as $\alpha$ increased.
 However, the decrease is more explicit when the interaction of $\alpha$ with the estimated model is added.
@@
 
-Finally, there seemed to be an effect of number of moderators on $TN$, but only for the two-way interaction model.
+Finally, there was an effect of number of moderators on $TN$, but only for the two-way interaction model.
 The $TN$ increased as the number of moderators did.

### 2021-11-14 paper/manuscript.Rmd
Update results, add images

@@
 # Results
-There were 3888 condition combinations and for each of those the algorithms ran 100 times, leaving 388800 cases to analyze.
-Out of those, 20 cases had missing values on all metrics for the RMA algorithm.
+There were 3888 condition combinations in total.
+The algorithms ran on 100 different datasets on each of those, leaving 388800 cases to analyze.
+There were 20 of those cases for which the RMA algorithm had missing values on all metrics.
 Closer inspection showed that both the cubic and exponential model each contributed ten times to the missing values and only when 2, 3 or 6 moderators were taken up in the model.
-However, since these 20 cases make up only 0.005% of the data, the missing values were chosen to be omitted from further analysis.
-Another observation is that the two-way interaction model only had results when there were either 3,4 or 7 moderators taken up, while the other models only had results when there were 2,3 or 6 moderators.
+However, since the missing cases make up only 0.005% of the data, the cases were chosen to be omitted from further analysis entirely.
+Another observation is that the two-way interaction model only had results when the number of moderators in the model was either 3, 4 or 7, while the other models only had results when there were 2, 3 or 6 moderators.
 It is therefor more challenging to compare and interpret the effect the moderators had on the performance criteria between the two-way interaction and the other models.
@@
 
-To determine the effect of the design factors on $R^2$ for all algorithms, four separate ANOVA’s were performed, one per algorithm.
+To determine the effect of the design factors on $R^2$ for all algorithms, four separate ANOVA’s were performed; one per algorithm.
 The effect size $\eta^{2}$ per condition per algorithm, including for all two-way interactions can be found in table 1.
@@
 However, $\beta$ did interact with the model that was estimated, being either a linear, two-way interaction, cubic or an exponential model.
-The image of the interaction is shown in image 1.
-When the exponential and cubic model were estimated, the increase of $R^{2}$ slows for every higher value of $\beta$.
-For the estimation of the two-way interaction model the increase only slowed when $\beta$ goes from 0.5 to 0.8, while the steepest increase for the linear model estimation is when $\beta$ increases from 0.2 to 0.5.
-Also noteworthy is that $R^2$ stagnates during estimation of the cubic model as $\beta$ goes up to 0.5 and onwards, while the other models do keep increasing.
+A graphical representation of the interaction is shown in image 1.
+When the exponential and cubic model were estimated, the increase of $R^{2}$ slowed for every higher value of $\beta$.
+For the estimation of the two-way interaction model the increase only slowed when $\beta$ went from 0.5 to 0.8, while the steepest increase for the linear model estimation was when $\beta$ increased from 0.2 to 0.5.
+Also noteworthy is that $R^2$ stagnated during estimation of the cubic model as $\beta$ went up to 0.5, while for the other models $R^2$ did keep increasing.
 There was little difference in median $R^2$ between Horsehoe, Lasso and RMA, while MetaForest performed worst.
@@
 There again was little difference in performance between the Pema algorithms and RMA, although MetaForest performed worst.
-Image 2 shows the relationship.
+Image 2A shows the relationship.
 
@@
 Again, Pema and RMA algorithms performed best, followed by MetaForest in all conditions.
-Most obvious to note is that all algorithms, except for when the linear model was estimated, generally performed better on more skewed data, although the algorithms did perform worse during estimation of the two-way interaction model and as $\alpha$ goes from 5 to 10.
+Most obvious to note is that all algorithms, except for when the linear model was estimated, generally performed better on more skewed data, although the algorithms did perform worse during estimation of the two-way interaction model when $\alpha$ went from 5 to 10.
 Overall performance was best during estimation of the cubic model, but the performance difference between estimated models decreased as $\alpha$ increased.
@@
 
-The true residual heterogeneity $\tau^{2}$ had a negative linear relationship for all algorithms on $R^{2}$. That is, as $\tau^{2}$ increased, $R^{2}$ decreased. Image 4 shows the relationship.
+The true residual heterogeneity $\tau^{2}$ had a negative linear relationship for all algorithms on $R^{2}$. That is, as $\tau^{2}$ increased, $R^{2}$ decreased. Image 2B shows the relationship.
 
@@
 Again, the Pema and RMA algorithms performed better than MetaForest.
-Image 5 shows the relationship.
+Image 2C shows the relationship.
 
-An especially large effect was found for the number of studies used in the training data $\kappa$ for MetaForest, $\eta^{2} = 0.27$, while this effect was substantially smaller for RMA, $\eta^{2} = 0.11$; Lasso, $\eta^{2} = 0.06$ and; Horseshoe, $\eta^{2} = 0.05$.
+An especially large effect was found for the number of studies used in the training data $\kappa$ for MetaForest, while this effect was substantially smaller for RMA, Lasso and Horseshoe.
 The relationship is positively linear for all algorithms, but the slope is especially steep for MetaForest.
-Image 6 shows the relationship.
+Image 2D shows the relationship.
 
-Finally, the number of moderators did not have a big effect for the Pema algorithms: $\eta^{2} = 0.01$ while for RMA and MetaForest $\eta^{2} = 0.05$.
+Finally, the number of moderators did not have a big effect for the Pema algorithms, while for RMA and MetaForest the effect was more noticeable.
 The relationship is shown in image 7.
@@
 This was mainly because the algorithms overestimated $\tau^{2}$ most when the model contained cubic terms.
-Image 8 shows the marginal relationship of the estimated model on $\Delta\tau^{2}$ .
-It becomes more clear why this overestimation occurred when showing the interaction between $\beta$ and the model estimated on $\Delta\tau^{2}$, shown in image 9.
+Image 5A shows the marginal relationship of the estimated model on $\Delta\tau^{2}$ .
+It becomes more clear why this overestimation occurred when showing the interaction between $\beta$ and the model estimated on $\Delta\tau^{2}$, shown in image 6.
 First note the general trend that during estimation of all models $\tau^{2}$ got more overestimated as $\beta$ increased, except during estimation of the linear model, where the effect of $\beta$ on $\Delta\tau^{2}$ was close to zero, except for MetaForest.
@@
 
-The marginal effects of $\beta$ on $\Delta\tau^{2}$  are shown in image 10.
-MetaForest was most affected by the increase in $\beta$, but in general performed better than the Pema algorithms when $\beta < 0.8$.
+The marginal effects of $\beta$ on $\Delta\tau^{2}$ are shown in image 5B.
+MetaForest was affected most by the increase in $\beta$, but in general performed better than the Pema algorithms when $\beta < 0.8$.
 The RMA algorithm performed best overall.
@@
 However, the decrease is more explicit when the interaction of $\alpha$ with the estimated model is added.
-Image 11 shows this interaction.
+Image 7 shows this interaction.
 The algorithms were rather unaffected by $\alpha$ for the linear model, and a small decrease in $\Delta\tau^{2}$ as $\alpha$ increased can be seen in the exponential model.
-When the two-way interaction model is estimated however, the algorithms benefitted as $\alpha$ increased, while for the cubic model, $\Delta\tau^{2}$ first increased as $\alpha$ increased from 0 to 2, but decreased as $\alpha$ increased from 2 to 10.
+When the two-way interaction model was estimated however, the algorithms benefitted as $\alpha$ increased, while for the cubic model, $\Delta\tau^{2}$ first increased as $\alpha$ increased from 0 to 2, but decreased as $\alpha$ increased from 2 to 10.
 RMA performed best, followed by MetaForest.
@@
 The tendency for the Pema algorithms on the other hand, was to overestimate $\tau^{2}$ more as the true $\tau^{2}$ increased.
-Image 12 shows the marginal relationship.
+Image 5C shows the marginal relationship.
 
 The effect of the number of moderators on $\Delta\tau^{2}$  was not that large either.
-A small increase in $\Delta\tau^{2}$ can be seen in the RMA and MetaForest algorithm as the number of moderators increased, which was not found for the Pema algorithms.
+A small increase in $\Delta\tau^{2}$ can be seen in the RMA and MetaForest algorithm as the number of moderators increased which was not found for the Pema algorithms.
 However, A small note is that MetaForest did substantially increase in $\Delta\tau^{2}$ as more moderators were added and the estimated model is cubic.
-Image 13 shows the interaction between the number of moderators and the estimated model.
+Image 8 shows the interaction between the number of moderators and the estimated model.
 
@@
 For the other algorithms, decreasing $\kappa$ had little to no effect on correctly estimating the residual heterogeneity.
-Image 14 shows the relationship.
+Image 9 shows the interaction of $\kappa$ with the estimated model.
 
-Finally, the average number of observations in the studies did not have a substantial effect on $\Delta\tau^{2}$. Image 15 shows the marginal relationship.
+Finally, the average number of observations in the studies did not have a substantial effect on $\Delta\tau^{2}$. Image 5D shows the marginal relationship.
 
@@
 Horshoe performed slightly better than Lasso;  $TP_{Hs} = 0.91$; $TP_{Lasso} = 0.89$.
-As for $TN$, it was found that the pema algorithms performed best: $TN_{Hs} \ \text{and} \ TN_{Lasso} = 0.93$, followed by RMA: $TN_{RMA} = 0.89 \pm 0.20$.
+As for $TN$, it was found that the pema algorithms performed best: $TN_{Hs} \ \text{and} \ TN_{Lasso} = 0.93$, followed by RMA: $TN_{RMA} = 0.89$.
 MetaForest performed worst by a large margin: $TN_{Mf} = 0.50$.
@@
 
-Firstly, $\kappa$ only had a marginal positive effect on $TP$.
+Firstly, $\kappa$ only had a positive effect on $TP$.
 As $\kappa$ increased, $TP$ also increased.
@@
 The increase in $TP$ for higher values of $\kappa$ was steeper for the Pema algorithms, however.
-There was also an interaction of $\kappa$ with the estimated model shown in image 16.
+There was also an interaction of $\kappa$ with the estimated model shown in image 10.
 During estimation of the linear and two-way interaction model, the relationship of $\kappa$ looked relatively linear.
@@
 MetaForest performed best, followed by RMA, while Horseshoe and Lasso performed worst.
-Image 17 shows the relationship.
+Image 11A shows the relationship.
 
@@
 This could be because the interaction model was only fitted when there were 3,4 or 7 moderators, while for the other models, only 2,3 or 6 moderators were used.
-Image 18 shows the relationship.
+Image 12 shows the relationship.
 The effect of $\beta$ on $TP$ was positive; as $\beta$ increased, $TP$ increased too.
 
-The true $\tau^2$ had a negative effect on $TP$, while $\alpha$ seemed to have little effect on both $TP$ and $TN$. Image 19 shows the marginal relationship of $\tau^2$ on $TP$.
+The true $\tau^2$ had a negative effect on $TP$, while $\alpha$ seemed to have little effect on both $TP$ and $TN$. Image 11B shows the marginal relationship of $\tau^2$ on $TP$.
 
@@
 The $TN$ increased as the number of moderators did.
-Image 20 shows the interaction.
-This relationship was reversed for $TP$ and was found for all algorithms, i.e.
+Image 13 shows the interaction.
+This relationship was reversed for $TP$ and was found during estimation of all models, i.e.
 $TP$ decreased as the number of moderators increased.
+Image 14 shows the relationship.
 

### 2021-11-14 simulatie_2021/Analysis_functions.R

@@ -38,7 +38,7 @@ EtaSq<-function (x)
 }
 
 #functions for plotting marginal and conditional effects of design factors for algorithms
-plot_marginal_mean <- function(condition, df, lonames, metric){
+plot_marginal_mean <- function(condition, df, lonames, metric, pointsize = 5, linesize = 2){
   condition <- as.name(condition)
   hs <- as.name(lonames[1])
   las <- as.name(lonames[2])
@@ -54,8 +54,8 @@ plot_marginal_mean <- function(condition, df, lonames, metric){
     pivot_longer(cols = !all_of(condition), names_to = 'alg', values_to = metric)
 
   ggplot(data = cond, aes(x = !!condition,y = !!as.name(metric), linetype = alg, group = alg, shape = alg)) +
-    geom_line(size = 1, ) +
-    geom_point(size = 2.5) +
+    geom_line(size = linesize, ) +
+    geom_point(size = pointsize) +
     theme_classic(base_size = 25)
 }
 
@@ -82,7 +82,7 @@ plot_interaction_mean <- function(condition, intcond, df, lonames, metric){
     theme_classic(base_size = 25)
 }
 
-plot_marginal_median <- function(condition, df, lonames, metric){
+plot_marginal_median <- function(condition, df, lonames, metric, pointsize = 5, linesize = 1.5){
   condition <- as.name(condition)
   hs <- as.name(lonames[1])
   las <- as.name(lonames[2])
@@ -98,8 +98,8 @@ plot_marginal_median <- function(condition, df, lonames, metric){
     pivot_longer(cols = !all_of(condition), names_to = 'alg', values_to = metric)
 
   ggplot(data = cond, aes(x = !!condition,y = !!as.name(metric), linetype = alg, group = alg, shape = alg)) +
-    geom_line(size = 1, ) +
-    geom_point(size = 2.5) +
+    geom_line(size = linesize, ) +
+    geom_point(size = pointsize) +
     theme_classic(base_size = 25)
 }
 

### 2021-11-24 paper/manuscript.Rmd
rewrite part of intro

--- 2021-11-06 paper/manuscript.Rmd
@@
 
-# introduction
+# Introduction
 
@@
 
-Meta-analysis is often used to summarize existing bodies of literature.
+In applied research, meta-analysis is often used to summarize existing bodies of literature.
 In such situations, the number of moderators is often relatively high because similar research questions have been studied in different laboratories,
@@
 
-It is often not known beforehand which moderators are relevant and which are not.
-This introduces a methodological challenge,
-because the number of studies in meta-analyses is typically small (Riley, Higgins \& Deeks, 2011),
-resulting in low power to identify relevant moderators (Thompson \& Higgins, 2002).
-There is thus a need for a technique that can perform variable selection in meta-analysis, and which is relatively robust to small sample sizes.
+It is theoretically possible to account for the influence of multiple moderators using meta-regression.
+However, like any regression-based approach, meta-regression requires a relatively high number of cases (studies) per parameter obtain sufficient power to examine heterogeneity.
+In practice the number of available studies is often low (Riley, Higgins, & Deeks, 2011).
+This necessitates *variable selection*: the selection of a smaller subset of relevant moderators from a larger number of candidate moderators.
 
-$$
+One way to perform variable selection is by relying on theory.
+However, theories at the individual level of analysis do not necessarily generalize to the study level of analysis.
+Using theories at the individual level for moderator selection at the study level amounts to committing the ecological fallacy: generalizing inferences across levels of analysis [@jargowskyEcologicalFallacy2004].
+The so-called *decline effect* illustrates this problem.
+It is a phenomenon whereby effect sizes in a particular tranche of the literature seem to diminish over time [@schoolerUnpublishedResultsHide2011].
+The decline effect has been attributed to i.a. regression to the mean:
+A finding initially draws attention from the research community because an anomalously large effect size has been published, and subsequent replications find smaller effect sizes.
+The decline effect would cause the variable "year of publication" to be a relevant moderator of effect size - even if it is orthogonal to the outcome of interest within each study.
+<!--A second example that might illustrate this problem is a study that concluded that American college students' empathy had decreased over time, based on meta-analysis of 72 samples collected between 1979 and 2009.-->
+
+An alternative solution is to rely on statistical methods for variable selection [see @hastieElementsStatisticalLearning2009].
+This paper introduces *penalized meta-regression* (implemented in the R-package `pema`),
+an algorithm that performs variable selection by shrinking the regression weight for irrelevant moderators towards zero.
+<!--
+Thus, there is a need of a regularization method to curtail overfitting.
+Least Absolute Shrinkage and Selection Operator [LASSO] (L1-norm regularization) can fulfill this role, since it has an advantage in terms of feature selection.
+The goal of this project is to implement L1-norm regularization in the weighted meta-regression, developing an new estimator for penalized meta-regression.
+This dilemma could be resolved by an exploratory technique that can identify relevant moderators in meta-analysis,
+and which is relatively robust to small sample sizes.
+-->
+
+## Statistical underpinnings
+
+To understand how the proposed `pema` algorithm estimates the relevant parameters and performs variable selection, it is instructional to first review the statistical underpinnings of the aforementioned classic approaches to meta-analysis.
+First is the fixed-effect model, which assumes that each observed effect size $T_i$ is an estimate of an underlying true effect size $\Theta$ [@hedgesFixedRandomeffectsModels1998].
+The only cause of variability in observed effect sizes is presumed to be effect size-specific sampling variance $v_i$.
+Thus, for a collection of $k$ studies, the observed effects sizes of individual studies $i$ (for $i$ = 1,2, . . . $k$) are given by:
+
+\begin{align}
+T_i &= \Theta + \epsilon_i\\
+\text{where } \epsilon_i &\sim N(0, v_i)
+\end{align}
+
+Typically, the variance $v_i$ is treated as known, and computed as the square of the standard error of the effect size.
+<!--
 \begin{aligned}
@@
 %\theta_1 &= \theta_2 \dots = \theta_k
-\end{aligned}
+\end{aligned}-->
+Under the fixed effect model, the estimated population effect size  $\hat{\theta}$ is obtained by computing a weighted average of the observed effect sizes.
+If sampling error is assumed to be the only source of variance in observed effect size,
+then it follows that studies with smaller standard errors estimate the underlying true effect size more precisely<!--(Schmidt, Oh \& Hayes, 2009)-->.
+The fixed-effect weights are thus simply the reciprocal of the sampling variance, $w_{i} =  \frac{1}{v_i}$.
+The weigted average is then:
+
+$$
+\hat{\theta} = \frac{\sum_{i=1}^k w_iT_i}{\sum_{i=1}^k w_i}
 $$
 
-., and methods have been developed to account for their influence.
-However, extant approaches lack the power to assess more than a handful of known moderators, or to investigate interactions between moderators, and non-linear effects.
-Heterogeneity between studies thus presents a non-trivial challenge to data aggregation using classic meta-analytic methods.
-At the same time, it also offers an unexploited opportunity to learn which differences between studies have an impact on the effect size found, if adequate exploratory techniques can be developed.
-
-Thus, there is a need of a regularization method to curtail overfitting.
-Least Absolute Shrinkage and Selection Operator [LASSO] (L1-norm regularization) can fulfill this role, since it has an advantage in terms of feature selection.
-The goal of this project is to implement L1-norm regularization in the weighted meta-regression, developing an new estimator for penalized meta-regression.
-
-**Fixed vs Random effects**
-The two classic approaches of meta-analysis refer to fundamental different assumptions made about the underlying data.
-These assumptions define the weights and will also determine which methods are used for the weighting of individual studies and for the creation a summary effect.
-
-The first approach is referred to as the as the fixed-effect model.
-This model assumes that each observed effect size, obtained from each individual study, is an estimate of an underlying true effect size (Hedges \& Vevea, 1998).
-The true effect sizes are treated as, unknown, constants.
-The only source that causes the deviation of the observed effect from the, unknown, true effects is sampling error.
-Thus, for a collection of $k$ studies, the observed effects size $y_{i}$ of each individual study $i$ (for $i$ = 1,2, .
-.
-.
-$k$) is given by:
-
- $y_{i}$ = $\theta$ + $\varepsilon_{i}$						(1)
-
-Where $\theta$ is the true effect size of each individual study $i$ and $\varepsilon_{i} \sim \mathcal{N}(0,\,\sigma_{i})\,$ with $\sigma_{i}$ being the sampling error or within-study variance, which is treated as a known factor.
-
-Fixed-effects meta-analysis considers sampling error to be the only cause of variance that influences the observed effect size.
-Studies with a large sample size will, as a result of this, produce more precise estimations of the underlying true effect size (Schmidt, Oh \& Hayes, 2009).
-Therefore, large sample sizes will contribute more to the weighted mean than small sample sizes.
-With that said, fixed-effects weights are defined by van Lissa (2017): “as the reciprocal of the effect size variances”:
-
- $W_{i} =  \frac{1}{\sigma^2_{i}}$						  (2)
-
-For an accurate estimate of the fixed-effects meta-analysis model, it starts with the assumption that the true effect is even in al studies.
-However, this assumption is implausible in plenty of meta-analysis.
-Especially in social sciences, the behaviour of people is extremely diverse and the contextual conditions for all humans vary to a great degree (Aronson, Wilson \& Akert, 2016).
-A highly likely consequence is that this will lead to a huge amount of possible moderators (Caserio, 2014).
-Also studies that examine same or similar research questions often differ.
+<!--A highly likely consequence is that this will lead to a huge amount of possible moderators (Caserio, 2014).
 Caused by differences in for example cultures of research populations and used methods or instruments (Neuman, 2011).
@@
 This leads very often to an eventual poor performance of the fixed-effects meta-analysis model (Snijders, 2005).
+-->
 
@@
 This estimation of the between-study variance is thus represented by $\tau^{2}$.
+
+$$
+\begin{aligned}
+y_i &= \theta_i + \epsilon_i &\text{where } \epsilon_i \sim N(0, \sigma^2_i)\\ % \text{ and } 
+%\theta_1 &= \theta_2 \dots = \theta_k
+\end{aligned}
+$$
 
@@
 # Results
-There were 3888 condition combinations and for each of those the algorithms ran 100 times, leaving 388800 cases to analyze.
-Out of those, 20 cases had missing values on all metrics for the RMA algorithm.
-Closer inspection showed that both the cubic and exponential model each contributed ten times to the missing values and only when 2, 3 or 6 moderators were taken up in the model.
-However, since these 20 cases make up only 0.005% of the data, the missing values were chosen to be omitted from further analysis.
-Another observation is that the two-way interaction model only had results when there were either 3,4 or 7 moderators taken up, while the other models only had results when there were 2,3 or 6 moderators.
-It is therefor more challenging to compare and interpret the effect the moderators had on the performance criteria between the two-way interaction and the other models.
+There were 20 cases out of 388800 that had missing values on all metrics for the RMA algorithm.
+Closer inspection showed that both the cubic and exponential model each contributed 10 times to the missing values and only when 2, 3 or 6 moderators were taken up in the model.
+However, since this makes up 0.005% of the data, the missing values were chosen to be omitted from further analysis.
+Another thing is that the two-way interaction model only has results when there were either 3,4 or 7 moderators taken up, while the other models only have results when there were 2,3 or 6 moderators.
+The effects of the moderators is therefore difficult to compare between the two-way interaction and the other models.
 
-## Predictive performance
-Predictive performance was operationalized by calculating the $R^2_{test}$ and $MSE_{test}$ for every combination of design factors, in further test denoted as $R^2$ and $MSE$ respectively.
-The densities for the $R^{2}_{test}$ and $MSE_{test}$ values were skewed however, which is why it was chosen to use the median $R^2$ as the metric for predictive performance, rather than the mean.
-The spread of the metrics was described using the Mean Absolute Deviation [MAD], rather than the standard deviation.
-It was found that the Horseshoe, Lasso and RMA algorithm performed similarly overall, $R^2_{Hs} = 0.51 \pm 0.36$, $MSE_{Hs} = 0.21 \pm 0.18$ ; $R^2_{Lasso} = 0.50 \pm 0.37$, $MSE_{Lasso} = 0.21\pm 0.19$; $R^2_{RMA} = 0.50 \pm 0.37$, $MSE_{RMA} = 0.22 \pm 0.23$ .
-The MetaForest algorithm performed worst on $R^2$: $R^2_{Mf} = 0.35 \pm 0.38$, $MSE_{Mf} = 0.22 \pm 0.19$
+*Predictive performance*
+Because the densities for the $R^{2}$ and $MSE$ values were skewed, it was chosen to use the median as the metric for predictive performance, rather than the mean.
+The spread of the data was described using the Mean Absolute Deviation [MAD], rather than the standard deviation.
+It was found that the Horseshoe, Lasso and RMA algorithm performed similarly overall, $R^2_{hs} = 0.51 \pm 0.36$, $MSE_{hs} = 0.21 \pm 0.18$ ; $R^2_{Lasso} = 0.50 \pm 0.37$, $MSE_{Lasso} = 0.21\pm 0.19$; $R^2_{RMA} = 0.50 \pm 0.37$, $MSE_{RMA} = 0.22 \pm 0.23$ .
+The random forest algorithm performed worst on $R^2$ $R^2_{rf} = 0.35 \pm 0.38$, $MSE_{rf} = 0.22 \pm 0.19$
 
-To determine the effect of the design factors on $R^2$ for all algorithms, four separate ANOVA’s were performed, one per algorithm.
-The effect size $\eta^{2}$ per condition per algorithm, including for all two-way interactions can be found in table 1.
+To determine the effect of the design factors on predictive performance $R^2$ of all algorithms, four separate ANOVA’s were performed.
+The effect size $\eta^{2}$ per condition per algorithm, including interactions can be found in table 1.
 Do note that the ANOVA's were performed with the normality assumption violated.
-The estimates serve mostly as a guidance, rather than an absolute result.
+The estimates serve as a guidance, rather than an non-contestable result.
 
-Not too surprisingly, It was found that the true effect size $\beta$ had the largest effect on $R^{2}$ for all algorithms.
+Not too surprisingly, It was found that the true effect size $\beta$ had the largest effect on the predictive $R^{2}$ for all algorithms.
 As $\beta$ increased, the performance of all algorithms increased as well.
-However, $\beta$ did interact with the model that was estimated, being either a linear, two-way interaction, cubic or an exponential model.
+However, $\beta$ did seem to interact with the model that was estimated, being either a linear, two-way interaction, cubic or an exponential model.
 The image of the interaction is shown in image 1.
-When the exponential and cubic model were estimated, the increase of $R^{2}$ slows for every higher value of $\beta$.
-For the estimation of the two-way interaction model the increase only slowed when $\beta$ goes from 0.5 to 0.8, while the steepest increase for the linear model estimation is when $\beta$ increases from 0.2 to 0.5.
-Also noteworthy is that $R^2$ stagnates during estimation of the cubic model as $\beta$ goes up to 0.5 and onwards, while the other models do keep increasing.
-There was little difference in median $R^2$ between Horsehoe, Lasso and RMA, while MetaForest performed worst.
+For the exponential and cubic model, the increase of $R^{2}$ slows for every higher value for $\beta$.
+The two-way interaction model only slows the increase when the es goes from 0.5 to 0.8, while the steepest increase for the linear model is when $\beta$ increases from 0.2 to 0.4.
+Also noteworthy is that the cubic model seems to stagnate as the effect size goes up to 0.4 and onwards, while the other models do keep increasing.
+There seemed to be little difference in performance between Horsehoe, Lasso and RMA, while MetaForest performed worst.
 
 The second largest marginal effect was that of the estimated model.
-All algorithms had the highest $R^2$ under the cubic model, followed by a similar performance on the two-way interaction and exponential models.
-All algorithms performed worst for the linear model.
-There again was little difference in performance between the Pema algorithms and RMA, although MetaForest performed worst.
+It seemed that all algorithms performed best under the cubic model, followed by a similar performance on the two-way interaction and exponential models.
+All algorithms seemed to perform worst for the linear model.
+There again is little difference in performance between the Pema algorithms and RMA, altough MetaForest performs worst.
 Image 2 shows the relationship.
 
-There also was a moderate interaction effect between the estimated model and the amount of skewness of the input data $\alpha$, especially for the Pema algorithms.
+There also was a moderate interaction effect between the estimated model and the amount of skewness of the data [$\alpha$], especially for the Pema algorithms.
 Again, Pema and RMA algorithms performed best, followed by MetaForest in all conditions.
-Most obvious to note is that all algorithms, except for when the linear model was estimated, generally performed better on more skewed data, although the algorithms did perform worse during estimation of the two-way interaction model and as $\alpha$ goes from 5 to 10.
-Overall performance was best during estimation of the cubic model, but the performance difference between estimated models decreased as $\alpha$ increased.
+Most obvious to note is that all, except the linear model seem to benefit when the $R^{2}$ was estimated on more skewed data, although the algorithms do perform worse for the interaction model and $\alpha$ goes from 5 to 10.
+The cubic model performs best overall, but is getting caught up by the exponential and interactoin model as $\alpha$ increases.
 Image 3 shows the relationship.
 
-The true residual heterogeneity $\tau^{2}$ had a negative linear relationship for all algorithms on $R^{2}$. That is, as $\tau^{2}$ increased, $R^{2}$ decreased. Image 4 shows the relationship.
+The true residual heterogeneity $\tau^{2}$ had a negative linear relationship for all algorithms on $R^{2}$. i.e. as $\tau^{2}$ increases, $R^{2}$ decreased. Image 4 shows the relationship.
 
-The mean sample size per study $\bar{n}$ also had a moderate effect.
-For all algorithms the effect of $\bar{n}$ was positively linearly related with $R^{2}$.
-Again, the Pema and RMA algorithms performed better than MetaForest.
+The mean sample size per study [$\bar{n}$] also had a moderate effect.
+For all algorithms the effect of $\bar{n}$ was positively linearly related to $R^{2}$ with the Pema and RMA algorithms performing best and Metaforest performing worst.
 Image 5 shows the relationship.
 
-An especially large effect was found for the number of studies used in the training data $\kappa$ for MetaForest, $\eta^{2} = 0.27$, while this effect was substantially smaller for RMA, $\eta^{2} = 0.11$; Lasso, $\eta^{2} = 0.06$ and; Horseshoe, $\eta^{2} = 0.05$.
+An especially large effect was found for the number of studies used in the training data for MetaForest, $\eta^{2}$ = 0.27, while this effect was substantially smaller for RMA, $\eta^{2}$ = 0.11; Lasso, $\eta^{2}$ = 0.06 and; Horseshoe, $\eta^{2}$ = 0.05.
 The relationship is positively linear for all algorithms, but the slope is especially steep for MetaForest.
@@
 
-Finally, the number of moderators did not have a big effect for the Pema algorithms: $\eta^{2} = 0.01$ while for RMA and MetaForest $\eta^{2} = 0.05$.
-The relationship is shown in image 7.
-The relationship is generally negative with more moderators meaning worse performance, although an increase can be observed as the number of moderators increase from 4 to 6 for all algorithms except MetaForest.
-This increase in performance for MetaForest appears when the number of moderators go from 3 to 4.
+Finally, the number of moderators did not have a big effect for the Pema algorithms, $\eta^{2}$ = 0.01 for both Horseshoe and Lasso while for RMA and Metaforest $\eta^{2}$ = 0.05.
+This relationship is generally negative with more moderators meaning worse performance, although an increase can be observed as the number of moderators increase from 4 to 6 for all algorithms except Metaforest.
+This increase in performance for Metaforest appears when the number of moderators go from 3 to 4.
+Image 7 and $\eta^{2}$ values indicate that the Pema algorithms are more robust against number of moderators than RMA and MetaForest.
 
-## Estimating residual heterogeneity
+*Estimating residual heterogeneity* ($\tau^{2}$)
 The ability of the algorithms to correctly estimate $\tau^{2}$ was operationalized by subtracting the true value for $\tau^{2}$ from the $\tau^{2}$ estimated by the algorithms.
-Again, the median and Mean Absolute Deviation were used as metrics for performance.
-The RMA algorithm showed the best results, $\Delta\tau^2_{RMA} = 0.02 \pm 0.06$, followed by the MetaForest algorithm $\Delta\tau^2_{Mf} = 0.09 \pm 0.13$.
-The Pema algorithms performed worst $\Delta\tau^2_{Lasso} = 0.23 \pm 0.18$; $\Delta\tau^2_{Hs} = 0.23 \pm 0.17$.
+Again, the median and MAD were used as metrics for performance.
+The RMA algorithm showed the best results, $\Delta\tau^2_{RMA} = 0.02 \pm 0.06$, followed by the Metaforest algorithm $\Delta\tau^2_{MF} = 0.09 \pm 0.13$.
+The Pema algorithms performed worst $\Delta\tau^2_{Lasso} = 0.23 \pm 0.18$; $\Delta\tau^2_{hs} = 0.23 \pm 0.17$.
 The finding that all medians are positive implies that all algorithms have a bigger tendency to overestimate $\tau^{2}$ than underestimate it.
 One comment to make is that uncertainty of the estimates generally increased as $\Delta\tau^{2}$ also increased.
-This implies that there was more variation in performance as median performance worsened.
+This implies that there is more variation in performance as median performance worsens.
 
-To determine the effect of the design factors on $\Delta\tau^{2}$ for all algorithms, four separate ANOVA’s were performed.
-The effect size $\eta^{2}$ per condition per algorithm, including $\eta^2$ for all two-way interactions can be found in table 2.
+To determine the effect of the design factors on estimated $\tau^{2}$ of all algorithms, four separate ANOVA’s were performed.
+The effect size $\eta^{2}$ per condition per algorithm, including interactions can be found in table 2.
 Again, the assumption of normality was violated.
 
-The biggest predictor on the correct estimation of $\tau^{2}$ was the estimated model.
-This was mainly because the algorithms overestimated $\tau^{2}$ most when the model contained cubic terms.
+The estimated model had one of the biggest effect on the correct estimation of $\tau^{2}$.
+This is mainly because the algorithms overestimate $\tau^{2}$ quite severely when the model contains cubic relationships.
 Image 8 shows the marginal relationship of the estimated model on $\Delta\tau^{2}$ .
-It becomes more clear why this overestimation occurred when showing the interaction between $\beta$ and the model estimated on $\Delta\tau^{2}$, shown in image 9.
-First note the general trend that during estimation of all models $\tau^{2}$ got more overestimated as $\beta$ increased, except during estimation of the linear model, where the effect of $\beta$ on $\Delta\tau^{2}$ was close to zero, except for MetaForest.
+It becomes more clear why this overestimation occurs when showing the interaction between the effect size and the model estimated on $\Delta\tau^{2}$ shown in image 9.
+First note the general trend which seems to be that for all models, except the linear, $\tau^{2}$ gets more overestimated the higher the true effect size is.
+This is not the case for the linear algorithm, where the effect of $\beta$ on $\Delta\tau^{2}$  seems close to zero, except for MetaForest.
 However, note the scales for the y-axes.
-While estimating the two-way interaction, linear and exponential model, $\Delta\tau^2$ stayed well within a confined interval.
-However, the algorithms severely overestimated $\tau^{2}$ when the model contained cubic terms.
-Especially MetaForest overestimated $\tau^{2}$ substantially when $\beta = 0.8$ and the estimated model is cubic: $\Delta\tau^{2}_{MF} = 2.92 \pm 2.37$.
-The other algorithms also had a $\Delta\tau^{2} > 1$ in these conditions, but the results were not as severe.
-Interestingly, the Pema algorithms even outperformed the RMA algorithm in these conditions.
+While the interaction, linear and stay well within a confined interval, the algorithms severely overestimate $\tau^{2}$ when the model contains cubic terms.
+Especially Metaforests overestimation is substantial when $\beta$ = 0.8 and the estimated model is cubic with $\Delta\tau^{2}_{MF} = 2.92 \pm 2.37$, although all other algorithms also have a $\Delta\tau^{2} > 1$ in these conditions.
+Interestingly, the Pema algorithms even outperform the RMA algorithm within these conditions.
+The marginal effects of $\beta$ on $\Delta\tau^{2}$  are shown in image 10.
+MetaForest seems most affected by the increase in $\beta$, but in general performs better than the Pema algorithms when $\beta$ < 0.8.
+The RMA algorithm performs best overall.
 
-The marginal effects of $\beta$ on $\Delta\tau^{2}$  are shown in image 10.
-MetaForest was most affected by the increase in $\beta$, but in general performed better than the Pema algorithms when $\beta < 0.8$.
-The RMA algorithm performed best overall.
+The marginal effect of the skewness of the data $\alpha$ on $\Delta\tau^{2}$  seems rather minimal.
+There is a slight decrease in $\Delta\tau^{2}$  as $\alpha$ increases, but it is hardly noticeable.
+However, this decrease becomes more clear when we add the interaction with the estimated model.
+Image 12 shows the conditional relationship.
+The algorithms seem rather unaffected by $\alpha$ for the linear model, and a small general decrease in $\Delta\tau^{2}$  as $\alpha$ increases can be seen in the exponential model.
+When the interaction model is estimated however, the algorithms seem to benefit as $\alpha$ increases, while for the cubic model, $\Delta\tau^{2}$  first increases as $\alpha$ increases, and afterwards decreases.
+RMA performs best, followed by Metaforest.
+The Pema algorithms perform similar, but worst.
 
-The marginal effect of $\alpha$ on $\Delta\tau^{2}$ was rather minimal, although there was a slight decrease in $\Delta\tau^{2}$ as $\alpha$ increased.
-However, the decrease is more explicit when the interaction of $\alpha$ with the estimated model is added.
-Image 11 shows this interaction.
-The algorithms were rather unaffected by $\alpha$ for the linear model, and a small decrease in $\Delta\tau^{2}$ as $\alpha$ increased can be seen in the exponential model.
-When the two-way interaction model is estimated however, the algorithms benefitted as $\alpha$ increased, while for the cubic model, $\Delta\tau^{2}$ first increased as $\alpha$ increased from 0 to 2, but decreased as $\alpha$ increased from 2 to 10.
-RMA performed best, followed by MetaForest.
-The Pema algorithms performed similarly, but worst.
-
-The effect of the true $\tau^{2}$ on $\Delta\tau^{2}$ was rather unnoticeable for the RMA and MetaForest algorithms.
+The effect of the true $\tau^{2}$ on $\Delta\tau^{2}$  also seemed rather unnoticeable for the RMA and Metaforest algorithm.
 The tendency for the Pema algorithms on the other hand, was to overestimate $\tau^{2}$ more as the true $\tau^{2}$ increased.
@@
 The effect of the number of moderators on $\Delta\tau^{2}$  was not that large either.
-A small increase in $\Delta\tau^{2}$ can be seen in the RMA and MetaForest algorithm as the number of moderators increased, which was not found for the Pema algorithms.
-However, A small note is that MetaForest did substantially increase in $\Delta\tau^{2}$ as more moderators were added and the estimated model is cubic.
-Image 13 shows the interaction between the number of moderators and the estimated model.
+A small increase in $\Delta\tau^{2}$ can be seen in the RMA and Metaforest algorithm as the number of moderators increase, which is not found for the Pema algorithms.
+However, A small note that should be made is that the Metaforest algorithm does substantially increase in $\Delta\tau^{2}$  as more moderators are added when the estimated model is cubic.
+Image 13 shows the interaction between the number of moderators and the estimated model on $\Delta\tau^{2}$ .
 
-$\kappa$ only had a substantial effect for MetaForest; the $\Delta\tau^{2}$  decreased quite rapidly if $\kappa$ increased, especially when the cubic model was estimated.
-For the other algorithms, decreasing $\kappa$ had little to no effect on correctly estimating the residual heterogeneity.
+The number of studies used in the training data $\kappa$ only had a substantial effect for the Metaforest algorithm.
+For Metaforest, the $\Delta\tau^{2}$  decreased quite rapidly if $\kappa$ increased, especially when the cubic model was estimated.
+For the other algorithms, decreasing $\kappa$ seemed to have little to no effect on correctly estimating the residual heterogeneity.
 Image 14 shows the relationship.
 
-Finally, the average number of observations in the studies did not have a substantial effect on $\Delta\tau^{2}$. Image 15 shows the marginal relationship.
+Finally, the average number of observations in the studies did not have a substantial effect on $\Delta\tau^{2}$  Image 15 shows the marginal relationship.
 
-## Variable selection
-To determine the extent to which the algorithms could perform variable selection correctly, the proportion true positives [$TP$] and true negatives [$TN$] were calculated.
-The $TP$ and $TN$ reflect how well the algorithms accredit importance to relevant moderators and discredit importance to irrelevant moderators respectively.
-It should be noted that $TP$ could only take on values 1 or 0 per simulated iteration, because in all models where $\beta > 0$, only one moderator was simulated to be relevant.
-As $\beta$ increased, the already relevant moderator increased in relevance, rather than spreading the relevance over the other moderators.
-$TN$ had a bigger range and could take on values dependent on how many moderators were taken up in the model.
-E.g.
-when $\beta = 0$ and $n_{mods} = n$, $n+1$ different proportions were possible, $\frac{0}{n}$ up until $\frac{n}{n}$.
-
-There were no differences in variables selected by Highest Density Intervals or Confidence Intervals for both Lasso and Horshoe and so for both algorithms it did not matter which interval type was analyzed.
-It was found that MetaForest had the highest proportion true positives: $TP_{Mf} = 0.98$, closely followed by RMA: $TP_{RMA} = 0.96$.
-Horshoe performed slightly better than Lasso;  $TP_{Hs} = 0.91$; $TP_{Lasso} = 0.89$.
-As for $TN$, it was found that the pema algorithms performed best: $TN_{Hs} \ \text{and} \ TN_{Lasso} = 0.93$, followed by RMA: $TN_{RMA} = 0.89 \pm 0.20$.
-MetaForest performed worst by a large margin: $TN_{Mf} = 0.50$.
-The Mean Absolute Deviation for all algorithms on both $TP$ and $TN$ was 0, except for MetaForests performance on $TN$, where the Mean Absolute Deviation was 0.44.
-
-Perfomance on $TP$ and $TN$ were very high for all algorithms, with all mean proportions, except MetaForests performance on $TN$, exceeding .89.
+*Variable selection*
+To determine the extent to which the algorithms could perform correct variable selection, the proportion true positives [TP] and true negatives [TN] were calculated.
+There were no differences in variables selected by Highest Density Intervals or Confidence Intervals for both Lasso and Horshoe and so for both algorithm it did not matter whether the Highest Density Interval or Confidence Interval were analyzed.
+The mean proportions along with the standard deviations on TP and TN are provided.
+It was found that Metaforest had the highest proportion true positives: $TP_{mf} = 0.98 \pm 0.15$, closely followed by RMA: $TP_{RMA} = 0.96 \pm 0.21$.
+Horshoe performed slightly better than Lasso;  $TP_{hs} = 0.91 \pm 0.29$; $TP_{Lasso} = 0.89 \pm 0.31$.
+As for TN, it was found that the pema algorithms performed best: $TN_{hs} = 0.93 \pm 0.16$, $TN_{Lasso} = 0.93 \pm 0.17$, followed by RMA: $TN_{RMA} = 0.89 \pm 0.20$.
+MF performed worst by a large margin: $TN_{mf} = 0.50 \pm 0.35$
+Perfomance on TP and TN were very high for all algorithms, with all mean proportions exceeding .89.
+One exception was the performance on TN for MetaForest, which mean was 0.50.
 This implies that MetaForest had issues excluding irrelevant moderators from the models.
 Plots were inspected to determine the effects of the design factors on the proportions.
-While inspecting the plots, there were found to be little marginal effects of the design factors on $TN$, while $TP$ was more affected.
+Something different to note is that there seem to be little marginal effects of the design factors on TN, while TP is more affected.
+It implies that the algorithms are more robust in excluding irrelevant moderators than in including relevant moderators.
 
-Firstly, $\kappa$ only had a marginal positive effect on $TP$.
-As $\kappa$ increased, $TP$ also increased.
-MetaForest had the highest $TP$, followed by RMA and, lastly, Horsehoe and Lasso.
-The increase in $TP$ for higher values of $\kappa$ was steeper for the Pema algorithms, however.
-There was also an interaction of $\kappa$ with the estimated model shown in image 16.
-During estimation of the linear and two-way interaction model, the relationship of $\kappa$ looked relatively linear.
-At $\kappa = 20$ the $TP$ was relatively low for the algorithms, compared to the cubic model where $TP$ starts at .98 and converges to 1 as $\kappa$ increased.
-This latter relationship was also found for the exponential model, although the $TP$ at $\kappa = 20$ was lower.
+Firstly, $\kappa$ only had a marginal positive effect on TP.
+As $\kappa$ increased, TP also increased.
+This implies that the ability for all algorithms to attribute positive relevance to relevant moderators increased as the number of studies in the training dataset increased.
+MetaForest had the highest TP, followed by RMA and lastly Horshoe and Lasso.
+The increase in TP for higher values of $\kappa$ was steeper for the pema algorithms, however.
+There also seemed to exist an interaction of $\kappa$ with the estimated model.
+For the linear and interaction model, the relationship of $\kappa$ seemed relatively linear.
+At $\kappa = 20$ the TP was relatively low for the algorithms, compared to the cubic model where TP starts at .98 and converges to 1 as $\kappa$ increased.
+This latter relationship was also found for the exponential model, although the TP at $\kappa = 20$ was slighlty lower.
+Image 16 shows the interaction.
 
-$\bar{n}$ had a positive and roughly linear relationship with $TP$ for all algorithms.
+The mean observations per study had a roughly positive linear relationship with TP for all algorithms.
 MetaForest performed best, followed by RMA, while Horseshoe and Lasso performed worst.
@@
 
-$\beta$ had an interaction effect with the model estimated on $TN$.
-Only during estimation of the two-way interaction model, $TN$ decreased as $\beta$ increased, For the other models, $TN$ remained stable.
+The true effect size $\beta$ had an interaction effect with the model estimated on TN.
+Only for the interaction model, TN decreased as $\beta$ increased, For the other models, TN remained stable.
 This could be because the interaction model was only fitted when there were 3,4 or 7 moderators, while for the other models, only 2,3 or 6 moderators were used.
 Image 18 shows the relationship.
-The effect of $\beta$ on $TP$ was positive; as $\beta$ increased, $TP$ increased too.
+The effect of $\beta$ on TP was positive; as $\beta$ increased, TP increased too.
 
-The true $\tau^2$ had a negative effect on $TP$, while $\alpha$ seemed to have little effect on both $TP$ and $TN$. Image 19 shows the marginal relationship of $\tau^2$ on $TP$.
+The true $\tau^2$ had a negative effect on TP, while skewness parameter $\alpha$ seemed to have little effect of both TP and TN. Image 19 shows the marginal relationship of $\tau^2$ on TP.
 
-Finally, there was an effect of number of moderators on $TN$, but only for the two-way interaction model.
-The $TN$ increased as the number of moderators did.
-Image 20 shows the interaction.
-This relationship was reversed for $TP$ and was found for all algorithms, i.e.
-$TP$ decreased as the number of moderators increased.
-
-# Discussion
+Finally, there seemed to be an effect of number of moderators on TN only for the interaction model.
+The TN increased as the number of moderators did.
+Image 20 shows the relationship.
+The relationship was reversed for TP and was found for all algorithms, i.e.
+TP decreased as the number of moderators increased.
 

### 2021-12-04 paper/manuscript.Rmd
update 2021-12-04 11:46:32

@@
 title             : "Select relevant moderators in meta-regression using Bayesian penalization"
-shorttitle        : "Title"
+shorttitle        : "BAYESIAN REGULARIZED META-ANALYSIS"
 
@@
       - Writing - Original Draft Preparation
-      - Writing - Review & Editing    
-  - name: "Andreas M. Brandmaier"
-    affiliation: "3,4"
-
-  - name          : "Ernst-August Doelle"
-    affiliation   : "1,2"
+      - Programming front-end
+  - name: "Sara van Erp"
+    affiliation: "1"
     role:
-      - Writing - Review & Editing
-
+      - Writing - Contributions and feedback
+      - Programming back-end
 affiliation:
   - id            : "1"
-    institution   : "Wilhelm-Wundt-University"
+    institution   : "Utrecht University, dept. Methodology & Statistics"
   - id            : "2"
-    institution   : "Konstanz Business School"
+    institution   : "Open Science Community Utrecht"
 
@@
 
+<!--
 Skeleton lasso/pema paper
@@
 # Introduction
+-->
 
-Meta-analysis is the practice of aggregating effect sizes from multiple similar studies.
-In its simplest form, a summary effect is computed as a weighted average of the observed effect sizes. 
-The weight assigned to each effect size is based on certain assumptions,
-and determines how influential it is in calculating the summary effect.
-For example, the *fixed effect* model assumes that all observed effect sizes reflect one underlying true population effect size.
-This assumption may be reasonable for close replication studies [@higgins_re-evaluation_2009, fabrigar_conceptualizing_2016, maxwell_is_2015]. 
+Meta-analysis is a quantitative form of evidence synthesis,
+whereby effect sizes from multiple similar studies are aggregated.
+In its simplest form, this aggregation consists of the computation of a summary effect as a weighted average of the observed effect sizes.
+This average is weighted to account for the fact that some observed effect sizes are assumed to be more informative about the underlying population effect.
+Each effect size is assigned a weight that determines how influential it is in calculating the summary effect.
+This weight is based on specific assumptions;
+for example, the *fixed effect* model assumes that all observed effect sizes reflect one underlying true population effect size.
+This assumption is well-suited to the situation where effect sizes from close replication studies are meta-analyzed [@higgins_re-evaluation_2009, fabrigar_conceptualizing_2016, maxwell_is_2015]. 
 The *random effects* model, by contrast, assumes that population effect sizes follow a normal distribution.
 Each observed effect size provides information about the mean and standard deviation of this distribution of population effect sizes.
-This assumption is appropriate when studies are conceptually similar and differences between them are random [@higgins_re-evaluation_2009, fabrigar_conceptualizing_2016, maxwell_is_2015].
+This assumption is more appropriate when studies are conceptually similar and differences between them are random [@higgins_re-evaluation_2009, fabrigar_conceptualizing_2016, maxwell_is_2015].
 
-Aside from random heterogeneity in effect sizes, quantifiable between-study differences may introduce systematic heterogeneity.
+Not all heterogeneity in effect sizes is random, however.
+Quantifiable between-study differences may introduce systematic heterogeneity.
 Such between-study differences are known as "moderators".
@@
 
-In applied research, meta-analysis is often used to summarize existing bodies of literature.
+One common application of meta-analysis is to summarize existing bodies of literature.
 In such situations, the number of moderators is often relatively high because similar research questions have been studied in different laboratories,
@@
 However, like any regression-based approach, meta-regression requires a relatively high number of cases (studies) per parameter obtain sufficient power to examine heterogeneity.
-In practice the number of available studies is often low (Riley, Higgins, & Deeks, 2011).
-This necessitates *variable selection*: the selection of a smaller subset of relevant moderators from a larger number of candidate moderators.
+In practice the number of available studies is often too low to examine heterogeneity reliably (Riley, Higgins, & Deeks, 2011).
+At the same time, there are many potential sources of heterogeneity,
+as similar research questions are studied in different laboratories, using different methods,
+instruments, and samples.
+This leads to a problem known as the "curse of dimensionality": the number of candidate moderators is large relative to the number of cases in the data.
+Such cases do not fit comfortably into the
+classic meta-analysis paradigm, which, like any regression-based approach, requires a
+high number of cases per parameter. 
+Between-studies thus presents a non-trivial challenge to data aggregation
+using classic meta-analytic methods.
+At the same time, it also offers an unexploited
+opportunity to learn which differences between studies have an impact on the effect size
+found, if adequate exploratory techniques can be developed.
 
+Addressing the curse of dimensionality necessitates *variable selection*:
+the selection of a smaller subset of relevant moderators from a larger number of candidate moderators.
 One way to perform variable selection is by relying on theory.
-However, theories at the individual level of analysis do not necessarily generalize to the study level of analysis.
+However, in many fields of science, theories exist at the individual level of analysis (e.g., in social science, at the level of individual people).
+These theories do not necessarily generalize to the study level of analysis.
 Using theories at the individual level for moderator selection at the study level amounts to committing the ecological fallacy: generalizing inferences across levels of analysis [@jargowskyEcologicalFallacy2004].
-The so-called *decline effect* illustrates this problem.
+To illustrate what theory at the study level of analysis might look like, 
+consider the so-called *decline effect*.
 It is a phenomenon whereby effect sizes in a particular tranche of the literature seem to diminish over time [@schoolerUnpublishedResultsHide2011].
-The decline effect has been attributed to i.a. regression to the mean:
+It has been theorized that the decline effect can been attributed to regression to the mean:
 A finding initially draws attention from the research community because an anomalously large effect size has been published, and subsequent replications find smaller effect sizes.
-The decline effect would cause the variable "year of publication" to be a relevant moderator of effect size - even if it is orthogonal to the outcome of interest within each study.
+Based on the decline effect, we might thus expect the variable "year of publication" to be a relevant moderator of study effect sizes.
+Note that this prediction is valid even if year is orthogonal to the outcome of interest within each study.
+Until more theory about the drivers of between-study heterogeneity is developed,
+however, this approach will have limited utility for variable selection.
 <!--A second example that might illustrate this problem is a study that concluded that American college students' empathy had decreased over time, based on meta-analysis of 72 samples collected between 1979 and 2009.-->
 
-An alternative solution is to rely on statistical methods for variable selection [see @hastieElementsStatisticalLearning2009].
-This paper introduces *penalized meta-regression* (implemented in the R-package `pema`),
-an algorithm that performs variable selection by shrinking the regression weight for irrelevant moderators towards zero.
+An alternative solution is to rely on statistical methods for variable selection.
+This is a focal issue in the discipline of machine learning [@hastieElementsStatisticalLearning2009].
+One technique that facilitates variable selection is *regularization*:
+shrinking model parameters towards zero, such that only larger parameters remain.
+Although this technique biases the parameter estimates,
+it also reduces their variance, which has the advantage of producing more generalizable results that make better predictions for new data [see @hastieElementsStatisticalLearning2009].
+This paper introduces *Bayesian regularized meta-regression* (BRMA),
+an algorithm that uses Bayesian estimation with regularizing priors to perform variable selection in meta-analysis.
+The algorithm is implemented in the function `brma()` in the R-package `pema`.
 <!--
@@
 Least Absolute Shrinkage and Selection Operator [LASSO] (L1-norm regularization) can fulfill this role, since it has an advantage in terms of feature selection.
-The goal of this project is to implement L1-norm regularization in the weighted meta-regression, developing an new estimator for penalized meta-regression.
+The goal of this project is to implement L1-norm regularization in the weighted meta-regression, developing an new estimator for regularized meta-regression.
 This dilemma could be resolved by an exploratory technique that can identify relevant moderators in meta-analysis,
@@
 -->
+<!--Such shrinkage is advantageous because it performs variable selection and results in a sparse model.
+Sparse models are easier to interpret, as fewer non-zero effects remain.
+Regularization also provides a solution to the curse of dimensionality; unlike standard regression models, it can provide identified models even if the number of moderators exceeds the number of cases.-->
+<!--By doing this it automatically performs variable selection.
+It does not seem to be immediately clear why shrinking the coefficients should be an improvement to the model.
+However, by shrinking the parameters, it lowers the variance of the model by increasing the bias only a little bit.
+In other words, the model sacrifices some of its ability to fit the current data, to greatly increase the ability to predict future data with the same fit (James et al., 2013).
+This is better known as the bias/variance tradeoff (Briscoe & Feldman, 2011).-->
 
@@
 
-To understand how the proposed `pema` algorithm estimates the relevant parameters and performs variable selection, it is instructional to first review the statistical underpinnings of the aforementioned classic approaches to meta-analysis.
+To understand how BRMA estimates the relevant parameters and performs variable selection, it is instructional to first review the statistical underpinnings of the aforementioned classic approaches to meta-analysis.
 First is the fixed-effect model, which assumes that each observed effect size $T_i$ is an estimate of an underlying true effect size $\Theta$ [@hedgesFixedRandomeffectsModels1998].
-The only cause of variability in observed effect sizes is presumed to be effect size-specific sampling variance $v_i$.
+The only cause of heterogeneity in observed effect sizes is presumed to be effect size-specific sampling variance, $v_i$, which is treated as known, and computed as the square of the standard error of the effect size.
 Thus, for a collection of $k$ studies, the observed effects sizes of individual studies $i$ (for $i$ = 1,2, . . . $k$) are given by:
@@
 
-Typically, the variance $v_i$ is treated as known, and computed as the square of the standard error of the effect size.
 <!--
@@
 \end{aligned}-->
+
 Under the fixed effect model, the estimated population effect size  $\hat{\theta}$ is obtained by computing a weighted average of the observed effect sizes.
@@
 The fixed-effect weights are thus simply the reciprocal of the sampling variance, $w_{i} =  \frac{1}{v_i}$.
-The weigted average is then:
+The estimate of the true effect is a weighted average across observed effect sizes:
 
-$$
+\begin{equation}
 \hat{\theta} = \frac{\sum_{i=1}^k w_iT_i}{\sum_{i=1}^k w_i}
-$$
-
+\end{equation}
+-->
 <!--A highly likely consequence is that this will lead to a huge amount of possible moderators (Caserio, 2014).
@@
 
-The second model is the random-effects model.
-This approach makes an additional assumption, namely about the true effect sizes.
-Where the fixed-effect model treats the true effects as constants, the random-effect model assumes that the true effects are random and follow a distribution of their own (Hedges \& Vevea, 1998).
-This means that variation in the observed effects ($y_{i}$) in the random model incorporates not only the sampling error but also the variation of the true effect sizes $\tau^{2}$ between the studies.
-In the case of the random effect model the observed effect size of $y_{i}$ is, given by:
+Whereas the fixed-effect model assumes that only one true population effect exists,
+the random-effects model assumes that true effects may vary for unknown reasons,
+and thus follow a (normal) distribution of their own (Hedges \& Vevea, 1998).
+This heterogeneity of the true effects is represented by their variance, $\tau^{2}$.
+The random effect model thus assumes that the heterogeneity in observed effects can be decomposed into sampling error and between-studies heterogeneity, resulting in the following equation for the observed effect sizes:
 
- $y_{i} = \theta_{i}+\varepsilon_{i}$ 						(3)
+\begin{align}
+T_i &= \Theta + \zeta_{i} + \epsilon_i\\
+\text{where } \zeta_i &\sim N(0, \tau^2)\\
+\text{and } \epsilon_i &\sim N(0, v_i)
+\end{align}
 
-With $\varepsilon_{i} \sim \mathcal{N}(0,\,\sigma_{i})\,$ but, in this case $\theta_{i}$ on itself is given by:
+In this model, $\Theta$ is the mean of the distribution of true effect sizes, and $\tau^2$ is its variance, which can be interpreted as the variance between studies.
 
- $theta_{i} = \mu + \zeta_{i}$						(4)
+If the true effect sizes follow a distribution, 
+then even less precise studies (with larger sampling errors) may provide some information about this distribution.
+Like fixed-effect weights, random effects weights are still influenced by sampling error, but this influence is attenuated by the estimated variance of the true effect sizes. 
+The random-effects weights are thus given by $w_{i} =  \frac{1}{v_i + \hat{\tau}^2}$.
+It is important to note that,
+whereas the sampling error for each individual effect size is treated as known,
+between-study heterogeneity $\tau^{2}$ must be estimated.
+This estimate is represented by $\hat{\tau}^{2}$.
 
-With $\mu$ being the mean of the distribution of the true effect sizes and $\zeta_{i} \sim \mathcal{N}(0,\,\tau^{2})\,$ with $\tau^2$ being the variance of the population of true effect sizes.
-It could also be explained as the variance between the individual studies.
-However, in the case of random-effects, the true effects also follow a distribution, so therefore the between study variance is also taken into account when composing the weights for the individual studies.
-The individual weights for the random-effect model are given by:
+### Meta-regression
 
- $W_{i} =  \frac{1}{\sigma^2_{i} + \tau^{2}}$						(5)
-In the case of the random-effect model, the within-study- and between-study variance is necessary for the calculation of the weights.
-It is important to note that in the calculation of the individual weights, an estimation of study heterogeneity is used $\tau^{2}$.
-While the sampling error is known for each individual study, the true effect heterogeneity $\tau^{2}$ remains unknown.
-Therefore, an estimation of the heterogeneity value needs to be made to effectively calculate the weights.
-This estimation of the between-study variance is thus represented by $\tau^{2}$.
+The random effects model assumes that causes of heterogeneity in the true effect sizes are unknown, and that their influence is random.
+Oftentimes, however, there are systematic sources of heterogeneity in true effect sizes.
+These between-study differences can be coded as moderators, and their influence can be estimated and controlled for using meta-regression.
+Meta-regression with $p$ moderators can be expressed with the following equation, where $x_{1\ldots p}$ represent the moderators, and $\beta_{1\ldots p}$ the regression coefficients:
 
-$$
-\begin{aligned}
-y_i &= \theta_i + \epsilon_i &\text{where } \epsilon_i \sim N(0, \sigma^2_i)\\ % \text{ and } 
-%\theta_1 &= \theta_2 \dots = \theta_k
-\end{aligned}
-$$
+\begin{align}
+T_i &= \beta_{0}+ \beta_{1}x_{1}+ \beta_{2}x_{2} + \ldots + \beta_{p}x_{p} + \zeta_{i} + \epsilon_i\\
+\end{align}
 
-**Meta-regression**
-In the case of fixed- and random-effect meta-analysis, the observed effects are treated as estimations of the underlying true effect.
-In meta-regression the observed effects are estimated by the including the moderators.
-In other words, the true effect is now replaced by the moderator effects.
-This is expressed with the following equation, where $\theta_{i}$ represents the underlying true effect, $x_{i}$ the moderators, $\beta_{i}$ the coefficients, with $p$ being the number of moderators:
+Note that $\beta_0$ represents the intercept of the distribution of true effect sizes after controlling for the moderators
+and the error term $\zeta_{i}$ represents residual between-studies heterogeneity.
+This term is still included because unexplained heterogeneity often remains after accounting for the moderators (Thompson \& Sharp, 1999).
+This is a mixed-effects model; the intercept and effects of moderators are treated as fixed and the residual heterogeneity as random (Viechtbauer \& López-López, 2015).
 
-$\theta_{i}=\beta_{0}+ \beta_{1}x_{1}+ \beta_{2}x_{2} + \ldots + \beta_{p}x_{p}+ \zeta_{i}$			(6)
+<!--
+An accurate estimation of the residual heterogeneity contributes to a better interpretation of the effect of the moderators (Panityakul, Bumrungsup \& Knapp, 2013).-->
 
-When this is substituted in the original equation it will result in:
-
-$y_{i}=\beta_{0}+ \beta_{1}x_{1}+ \beta_{2}x_{2} + \ldots + \beta_{p}x_{p}+ \zeta_{i} + \varepsilon_{i}$			(7)
-
-The error term $\zeta_{i}$ captures the residual heterogeneity after accounting for the moderators.
-This term is still included because it is often the case that there still remains heterogeneity unexplained after accounting for the moderators (Thompson \& Sharp, 1999).
-In this model the moderator effects are treated as fixed and the residual heterogeneity as random.
-Therefore, it is referred to as a mixed-effect meta-regression analysis model, in short, ME-MRA (Viechtbauer \& López-López, 2015).
-To solve this ME-MRA model, both the residual heterogeneity and the moderator coefficients need to be estimated.
-An accurate estimation of the residual heterogeneity contributes to a better interpretation of the effect of the moderators (Panityakul, Bumrungsup \& Knapp, 2013).
-
-**Estimating residual heterogeneity**
-The topic of estimating the residual heterogeneity is a highly discussed one (Veroniki et al., 2016; Viechtbauer \& López-López, 2015; Panityakul et al., 2013).
+To solve this model, the regression coefficients and residual heterogeneity must be estimated simultaneously.
+<!--The topic of estimating the residual heterogeneity is a highly discussed one (Veroniki et al., 2016; Viechtbauer \& López-López, 2015; Panityakul et al., 2013).
 The ability of the estimators to predict the residual heterogeneity is influenced by different factors, such as the number of studies (Guolo \& Varin, 2017; Panityakul et al., 2013; Hardy \& Thompson, 1996) included and the sample size of the individual studies (Panityakul et al., 2013).
@@
 Considering that all models their performance is linked to the accuracy of the estimate.
-According to Sidik \& Jonkman (2007), it is generally the case that the larger true between-study variance is, the more biased the estimate can be, which diminishes the performance of the method.
-
-**Methods for estimating residual heterogeneity**
-Numerous methods have been proposed to accurately estimate the residual heterogeneity, including the Hedges (HE), DerSimonian–Laird/Method of Moments (DL), Sidik and Jonkman (SJ), Maximum Likelihood (ML), Restricted Maximum Likelihood (REML), and Empirical Bayes (EB) method.
+According to Sidik \& Jonkman (2007), it is generally the case that the larger true between-study variance is, the more biased the estimate can be, which diminishes the performance of the method.-->
+Numerous methods have been proposed to estimate meta-regression models, the most commonly used of which is restricted maximum likelihood (REML).
+REML is an iterative method, meaning it performs the same calculations repeatedly, updating the estimated regression coefficients and residual heterogeneity until these estimates stabilize.
+<!--, including the Hedges (HE), DerSimonian–Laird/Method of Moments (DL), Sidik and Jonkman (SJ), Maximum Likelihood (ML), Restricted Maximum Likelihood (REML), and Empirical Bayes (EB) method.
 These methods are mostly divided into two groups: closed-form or non-iterative methods and iterative methods.
 The main difference between these groups is that the closed form group uses a predetermined number of steps to provide an estimation for the residual heterogeneity, whereas the iterative methods run multiple iteration, as the name suggests, to converge to a solution when a specific criterion is met.
-It is important to note that some iterative methods do not produce a solution when they fail to converge after a predetermined amount of iteration.
-
-In our scenario we are especially interested in an estimator which performs well under the condition of a relative low number of studies.
-The Restricted Maximum Likelihood (REML) seems to produce the lowest bias under this condition and is therefore preferred (Panityakul et al., 2013; Hardy & Thompson, 1996).
-The REML is an iterative method and needs a starting estimation of $\tau^{2}$ to start, usually it gets estimated by one of the non-iterative methods (Viechtbauer \& López-López, 2015).
+It is important to note that some iterative methods do not produce a solution when they fail to converge after a predetermined amount of iteration.-->
+In contrast to a regularized analysis technique, this estimator produces low bias, which means that the average value of the estimated regression coefficients and residual heterogeneity is close to their true values (Panityakul et al., 2013; Hardy & Thompson, 1996).
+<!--It needs a starting estimation of $\tau^{2}$, which is usually estimated by one of the non-iterative methods (Viechtbauer \& López-López, 2015).
 Besides the starting value of $\tau^{2}$, it needs in every iteration an estimation of the regression coefficients of the moderators.
@@
 The addition of weights is a way to adjust for this heteroscedasticity.
-The weights are formulated as presented in equation (5).
-
+The weights are formulated as presented in equation (5).-->
+<!--
 The usage of a WLS method to estimate the regression coefficient may be problematic in the situation where a lot of moderators are measured without their specific effects, when the amount of studies is low and when moderators are dichotomous.
@@
 The weighted least squares are replaced with the so-called LASSO regression for the estimation of the regression coefficients.
-This algorithm shrinks or penalizes the regression coefficients and performs variable selection (James et al., 2013; Hesterberg, Choi, Meier, \& Fraley, 2008).
+This algorithm shrinks or penalizes the regression coefficients and performs variable selection (James et al., 2013; Hesterberg, Choi, Meier, \& Fraley, 2008).-->
 
-**Intro rma**
-The rma algorithm is part of the software-package `metafor` in `R`, which is developed by Wolfgang Viechtbauer (2010, 2019).
-This algorithm is specifically developed to perform a meta-analysis or meta-regression.
-It allows to include different models, such as the fixed-, random- and mixed-effect model.
-It is also possible to account for moderators (Viechtbauer, 2010).
-The mixed-effect model, which is used is this study, requires a two-step approach to fit a meta-analytic model.
-First the residual heterogeneity is estimated.
-The package developed by Viechtbauer does provide multiple methods for the estimation of the residual heterogeneity.
-In this study the Restricted Maximum-likelihood is used, but this has already been discussed earlier.
-The second step is estimating the moderator coefficients, which is done by using the Weighted Least Squares (WLS) method.
-The weights are described in equation (5).
-The lma is a variation of the rma algorithm which is created by Caspar van Lissa.
-As explained before, the REML is an iterative procedure for the estimation of the residual heterogeneity.
-In every step of the process, instead of estimating the coefficients of the moderators by using a WLS, a weighted lasso regression is performed.
-Then again, the residual heterogeneity gets estimated with the rma algorithm by using the new values of the coefficients.
-With these new values of $\tau^{2}$, a new weighted lasso is performed for the estimations of the coefficients.
-This process continuous, until the residual heterogeneity converges to a certain value.
+### Regularized regression
 
-**Intro Lasso**
-The lasso is a technique that regularizes or constrains the coefficient estimates, better known as shrinking (James et al., 2013).
-It possesses the ability to reduce the regression coefficient even to a value of zero.
-By doing this it automatically performs variable selection.
-It does not seem to be immediately clear why shrinking the coefficients should be an improvement to the model.
-However, by shrinking the parameters, it lowers the variance of the model by increasing the bias only a little bit.
-In other words, the model sacrifices some of its ability to fit the current data, to greatly increase the ability to predict future data with the same fit (James et al., 2013).
-This is better known as the bias/variance tradeoff (Briscoe & Feldman, 2011).
+Regularized regression biases parameter estimates towards zero by including a shrinkage penalty in the estimation process.
+Before examining the Bayesian case, we will explain the principle using frequentist OLS regression as an example.
+OLS regression estimates the model parameters by minimizing the Residual Sum of Squares (RSS) of the dependent variable, which is given by:
 
-The Lasso shrinkage method is not the only shrinkage method, there do exist some others.
+$$
+RSS=\sum_{i=1}^{n}(y_{i} - \beta_{0} - \sum_{j=1}^{p}\beta_{j}x_{ij})^2
+$$
+The resulting parameter estimates are those that give the best predictions of the dependent variable in the present dataset.
+Penalized regression, by contrast, adds a penalty term to the quantity to be minimized.
+One commonly used penalty is the L1-norm of the regression coefficients, or LASSO penalty,
+which corresponds to the sum of their absolute values.
+This gives the penalized residual sum of squares:
+
+$$
+PRSS= RSS + \lambda \sum_{j=1}^{p}|\beta_{j}|
+$$
+
+Where $\lambda$ is a tuning parameter that determines how influential the penalty term will be.
+If $\lambda$ is zero, the shrinkage penalty has no impact at all and the penalized regression will produce the OLS estimates.
+If $\lambda \to \infty$, all coefficient shrink towards zero, producing the null model.
+<!--Another commonly used penalty is the L2-norm of the coefficients, or ridge penalty,
+which corresponds to the sum of their squared values: $\sum_{j=1}^{p}\beta_{j}^2$.-->
+Because the penalty term is a function of the regression coefficients,
+the optimizer has an incentive to keep the regression coefficients as small as possible.
+<!--The LASSO penalty has the unique property of shrinking some coefficients to be exactly zero,
+but the ridge penalty does not do so, as -->
+Note that theLASSO penalty is but one example of a shrinkage penalty; other penalties exist, with some unique properties.
+
+<!--The Lasso shrinkage method is not the only shrinkage method, there do exist some others.
 Nevertheless, the lasso is in the case the best option.
@@
 This means that the lasso can perform variable selection, something that is specifically aimed for in this study.
+-->
 
-In line with other shrinkage methods the lasso makes use of a shrinkage penalty.
-This penalty is added in the process of the OLS calculation of the regression coefficients.
-The OLS method estimates the coefficients by minimizing the Residual Sum of Squares (RSS).
-The following equation shows how the calculation of the RSS together with the shrinkage penalty:
-
-$RSS=\sum_{i=1}^{n}(y_{i} - \beta_{0} - \sum_{j=1}^{p}\beta_{j}x_{ij})^2 + \lambda\sum_{j=1}^{p}|\beta_{j}|$			(8)
-
-This equation shows that the shrinkage penalty consists of two variables, the tuning parameter $\lambda$ and the regression coefficients $\beta_{j}$.
-This means that, while the OLS tries to find the coefficients which explain as much variance as possible, due to the minimization of the RSS, the shrinkage penalty punishes this.
-Therefore, the coefficients are forced to shrink a certain amount, depending on the parameter $\lambda$.
-If the $\lambda$ increases, it grows the impact of the shrinkage penalty on the RSS, with $\lambda \to \infty$ shrinking all the coefficient to be zero, producing the null model.
-But, if the $\lambda$ is zero, the shrinkage penalty has no impact at all and it will produce the OLS estimates.
-
+<!--
 **Alternative to linear model: Tree Based models**
@@
 Renouncing from normal distributions may affect the performance of the model, but since normal distribution in real-life data is more an exception than a normal state of affairs (Micceri, 1989), it is entirely possible that procedures are affected by skewness, leverage, balance etc.
-It is important to know how MetaForest performs in these kinds of situations.
+It is important to know how MetaForest performs in these kinds of situations.-->
 
-**Algorithms and simulation + goal study**
-The goal of the present study was to test whether a ME-MRA model with the lasso algorithm is able to outperform the ME-MRA with least squares regression.
-More specifically, if the lasso is able to outperform the least squares when in situation where the amount studies included in the analysis is fairly low.
-To test this, two different algorithms are used; one called the rma, which makes use of the WLS regression, and the lma, which makes use of a penalized lasso regression.
-To test the lma and rma algorithms on the performance criteria, a simulation study is performed.
-A simulation of the data is preferred over the use of real data.
-Simulated data can be shaped to such an extent that it will have the all desired characteristics to test the performance of the algorithm.
-Besides that, if simulated correctly, it will not have any systematic errors or noise due to underlying models and it is more cost efficient.
-Simulations are useful for evaluation of new methods like MetaForest and for the comparison with alternative methods like metaCART and the classic approaches.
+### Bayesian estimation
 
-**Performance Criteria**
-The algorithms are evaluated on three different performance criteria: The algorithms’ predictive performance, their ability to estimate the residual heterogeneity and their ability to detect and select the right moderators.
-The predictive performance of the algorithms is defined by how well the algorithm is able to predict future data.
-The algorithms have to estimate a model on a “training” dataset and then use this model to see how well it fits on a second “testing” dataset.
-This is operationalized as the cross-validated $R_{cv}^{2}$ (Van Lissa, 2017).
-The $R_{cv}^{2}$ is calculated using the fraction of variance explained by the model on the testing dataset, relative to faction of variance explained by the mean of the testing dataset.
-The mean of the testing dataset is the best prediction for the testing data when there is no model present (van Lissa, 2017).
-The calculation of$R_{cv}^{2}$is expressed by the following equation:
+<!--To solve this model, the moderator coefficients and the residual heterogeneity must be estimated simulataneously.
+<!--The topic of estimating the residual heterogeneity is a highly discussed one (Veroniki et al., 2016; Viechtbauer \& López-López, 2015; Panityakul et al., 2013).
+The ability of the estimators to predict the residual heterogeneity is influenced by different factors, such as the number of studies (Guolo \& Varin, 2017; Panityakul et al., 2013; Hardy \& Thompson, 1996) included and the sample size of the individual studies (Panityakul et al., 2013).
+A third, and obvious factor, that is classified as relevant to model performance is heterogeneity among studies being meta-analysed (Kontopantelis \& Reeves, 2011; Jackson \& White, 2018).
+Coverage from models degrades when the residual heterogeneity increases, mostly when the amount of studies is small (Brockwell \& Gorden, 2001).
+Considering that all models their performance is linked to the accuracy of the estimate.
+According to Sidik \& Jonkman (2007), it is generally the case that the larger true between-study variance is, the more biased the estimate can be, which diminishes the performance of the method.-->
+<!--Numerous methods have been proposed to accurately estimate the residual heterogeneity, including the Hedges (HE), DerSimonian–Laird/Method of Moments (DL), Sidik and Jonkman (SJ), Maximum Likelihood (ML), Restricted Maximum Likelihood (REML), and Empirical Bayes (EB) method.
+These methods are mostly divided into two groups: closed-form or non-iterative methods and iterative methods.
+The main difference between these groups is that the closed form group uses a predetermined number of steps to provide an estimation for the residual heterogeneity, whereas the iterative methods run multiple iteration, as the name suggests, to converge to a solution when a specific criterion is met.
+It is important to note that some iterative methods do not produce a solution when they fail to converge after a predetermined amount of iteration.
 
-$R_{cv}^{2} = 1- \frac{\sum_{i=1}^{n}(y_{i}-\hat{y}_{i})^{2}}{\sum_{i=1}^{n}(y_{i}-\bar{y}_{i})^{2}}$					(9)
+In our scenario we are especially interested in an estimator which performs well under the condition of a relative low number of studies.
+The Restricted Maximum Likelihood (REML) seems to produce the lowest bias under this condition and is therefore preferred (Panityakul et al., 2013; Hardy & Thompson, 1996).
+The REML is an iterative method and needs a starting estimation of $\tau^{2}$ to start, usually it gets estimated by one of the non-iterative methods (Viechtbauer \& López-López, 2015).
+Besides the starting value of $\tau^{2}$, it needs in every iteration an estimation of the regression coefficients of the moderators.
+These are typically estimated by using the Weighted Least Squares (WLS) method.
+This is a variation of the Ordinary Least Squares (OLS), but in the case of meta-analysis it is necessary to assess weights to the coefficients.
+In systematic reviews large variation in standard errors is often observed, which will result in large heteroscedasticity in the estimation of the effects (Stanley \& Doucouliagos, 2017).
+The addition of weights is a way to adjust for this heteroscedasticity.
+The weights are formulated as presented in equation (5).
 
-With $n$ being the number of studies in the testing dataset, $\hat{y}_{i}$ being the estimation for study $i$, and $\bar{y}_{i}$ being the mean of the training dataset.
+The usage of a WLS method to estimate the regression coefficient may be problematic in the situation where a lot of moderators are measured without their specific effects, when the amount of studies is low and when moderators are dichotomous.
+The use of a least squares method will cause problems with the prediction accuracy and the model interpretability (James, Witten, Hastie, \& Tibshirani, 2013).
+In the situation where a lot of moderators are measured and blindly included in the model, it may as well be the case that variables are included that are in fact not associated with the response.
+Including irrelevant variables in the model lowers the interpretability of the model (James et al., 2013).
+An approach is necessary that automatically excludes the variables that are irrelevant i.e.
+performs variable selection.
+As explained before, in meta-analysis it is often the case that the number of moderators closely approaches or even exceeds the number of studies included in the analysis.
+A least squares method will display a lot variability in the fit when the number of variables is not much smaller than the number of studies (James et al., 2013).
+This means that the least squares method over fits the data and loses its power to be generalizable to future observations.
+When the number of variables exceeds the number of studies, the least squares method fails to produce one unique estimate and the method should not be used at all.
 
-The ability of the algorithms to estimate the residual heterogeneity is by simply taking the value of $\tau^{2}$ which the algorithm produces.
-The true value of the residual heterogeneity is subtracted of the estimated value, solely to make the values more interpretable.
-This means that a correct estimation of the residual heterogeneity will be expressed by a value which exactly or close to zero.
-The residual heterogeneity is used as a performance criterion because it is suspected that the lma model might not always be able to predict residual heterogeneity correctly.
+However, a least squares method could still be somewhat valuable in some situations.
+It is extremely suitable to estimate a linear relationship.
+In the case of dichotomous moderators, the relationship is always perfectly linear.
+A powerful non-linear estimation tool is in the situation of dichotomous moderators unnecessary and would not perform better at all.
+Whenever a non-linear relation gets fitted on data with an underlying linear relation, it will cause problems when this fit gets used for the prediction of future data.
+Given the various arguments, this paper provides an approach to tackle this problem of the least squares methods whilst still making use of a linear method.
+The weighted least squares are replaced with the so-called LASSO regression for the estimation of the regression coefficients.
+This algorithm shrinks or penalizes the regression coefficients and performs variable selection (James et al., 2013; Hesterberg, Choi, Meier, \& Fraley, 2008).
+-->
 
-Variable selection is defined in terms of the algorithms ability to accredit positive variable importance values to relevant moderators.
-Variable importance measures capture the relative contribution of various moderators.
+<!--
+**Intro rma**
+The rma algorithm is part of the software-package `metafor` in `R`, which is developed by Wolfgang Viechtbauer (2010, 2019).
+This algorithm is specifically developed to perform a meta-analysis or meta-regression.
+It allows to include different models, such as the fixed-, random- and mixed-effect model.
+It is also possible to account for moderators (Viechtbauer, 2010).
+The mixed-effect model, which is used is this study, requires a two-step approach to fit a meta-analytic model.
+First the residual heterogeneity is estimated.
+The package developed by Viechtbauer does provide multiple methods for the estimation of the residual heterogeneity.
+In this study the Restricted Maximum-likelihood is used, but this has already been discussed earlier.
+The second step is estimating the moderator coefficients, which is done by using the Weighted Least Squares (WLS) method.
+The weights are described in equation (5).
+The lma is a variation of the rma algorithm which is created by Caspar van Lissa.
+As explained before, the REML is an iterative procedure for the estimation of the residual heterogeneity.
+In every step of the process, instead of estimating the coefficients of the moderators by using a WLS, a weighted lasso regression is performed.
+Then again, the residual heterogeneity gets estimated with the rma algorithm by using the new values of the coefficients.
+With these new values of $\tau^{2}$, a new weighted lasso is performed for the estimations of the coefficients.
+This process continuous, until the residual heterogeneity converges to a certain value.
+-->
 
-**Design factors**
-In the simulation study, meta analytic datasets will be simulated.
-These datasets consist of two separate sub-datasets, a training- and a testing dataset.
-Both sub-datasets will have the same characteristics with the exception of the number of studies included.
-Certain characteristics of the sub-datasets will be manipulated to test how well the algorithms perform under certain conditions.
-For each combination of characteristics, or design factors, 100 datasets will be simulated.
-The design factors that will be manipulated are the number of studies in the training data $k$ (22, 40 and 80), the average within-study sample size $\bar{n}$ (40, 100 and 200), the population effect size $\beta$ (.2, .5 and .8) and the residual heterogeneity $\tau^{2}$ (.01, .04 and .1).
-All the datasets will contain 20 moderators of which 10 are relevant and 10 are irrelevant.
-The moderators are binary and follow $\sim \mathcal{Bern}(0.5)$, which corresponds to an equal chance of being either one or zero.
-The dependent variable $y_{i}$ represented by a $Hedges’ g$.
-This is an estimator which takes the standardized mean difference between a treatment and control group and is commonly used in meta-analysis (Van Lissa, 2017).
-The true effect size $\theta_{i}$  is sampled out of a normal distribution.
-The mean is computed by the assessing the values of the coefficients $\beta_{j}$, with the values of the moderators and with the residual heterogeneity $\tau^{2}$ (Van Lissa, 2017).
-This is in line with the calculation of $\theta_{i}$ represented in equation (6).
-The sampling error $\sigma^{2}_{i}$ is formed by varying the sizes of the samples of each study.
-The sample sizes $n_{i} \sim \mathcal{N}(\bar{n}, \frac{\bar{n}}{3}$ (Van Lissa, 2017).
+# Simulation study
 
-Data were simulated using the random-effects model, based on four models:
-(A) Main effect of one moderator, $\mu_{i}= \beta_{1}x_{1i}$ 
-(B) Two-way interaction, $\mu_{i}= \beta_{1}x_{1i} + \beta_{2}x_{2i} + \beta_{3}x_{1i}x_{2i}$ 
-(E) Non-linear, cubic relationship, $\mu_{i}= \beta_{1}x_{1i} + \beta_{2}x_{1i}^{2} + \beta_{3}x_{1i}^{3}$ 
-(F) Exponential relationship, $\mu_{i}= \beta_{1}e^{x_{1i}}$
+The present study set out to validate the BRMA algorithm using a simulation study.
+As a benchmark for comparison, we used restricted maximum likelihood meta-regression,
+which is the standard in the field.
+The algorithms are evaluated on three different criteria:
+The algorithms' predictive performance in new data, 
+<!-- examining its predictive performance in new data, its sensitivity and specificity in variable selection, and its bias and variance in recovering population parameters. -->
+their ability to perform variable selection,
+and their ability to recover population parameters.
 
-**Impact of design factors and hypotheses**
-These design factors are chosen on purpose, because they are hypothesized to have an influence on the predictive performance of the algorithms.
-The effect of the design factors ought to be either positive or negative on the data.
-This means that some factor should, by increasing, make the data easier to be analyzed, or make it more difficult to analyze.
-The amount of studies included in the training data $k$ has a positive influence on the variance explained by the different algorithms.
-This is due to the fact that there are simply more data points available to fit a model on.
-The lma algorithm should be superior on the low value of $k$ over the rma algorithm.
-The effect size $\beta$ has a positive impact on the ability of the algorithms to explain variance.
-It can be hypothesized that the lma performs better at lower values of $\beta$ because it is better equipped to detect and select variables when even when the amount of signal is low.
-The residual heterogeneity $\tau^{2}$ should have a negative influence on the interpretability of the data.
-Differences between the two algorithms could be present, but it remains unclear which would perform better.
-The lma might perform better when the amount of signal in the data is low or the noise is high, but it is also suspected to overestimate the amount of heterogeneity and this could worsen if the $\tau^{2}$ increases.
-The $\bar{n}$ greatly influences the quality of the data.
-Higher values of within-study sample sizes reduce the sampling error.
-This will lead to a better prediction by the algorithms.
-In conclusion: higher values of $k$, $\beta$ and  $\bar{n}$  will increase the quality of the data, where higher values of  $\tau^{2}$ decrease the quality of the data.
-The lma is suspected to perform significantly better when the quality of the data is low, especially when the amount of studies in the sample is low, with the exception of the performance of the lma on the estimation of the residual heterogeneity
+## Performance indicators
+
+Predictive performance reflects how well the algorithm is able to predict data not used to estimate the model parameters, in other words, it indicates the generalizability of the model.
+To compute it, for each iteration of the simulation both a training dataset and a testing dataset are generated.
+The model is estimated on the training data, which has a varying number of cases according to the simulation conditions.
+Predictive performance is then operationalized as the explained variance in the testing data, $R^2_{test}$.
+The testing data has 100 cases in all simulation conditions.
+The $R^2_{test}$ reflects the fraction of variance in the testing data explained by the model,
+relative to the variance explained by the mean of the training data.
+For a predictive performance measure, it is necessary to use the mean of the training data, as the mean of the testing is a descriptive statistic of that sample.
+The resulting metric $R_{test}^{2}$ is expressed by the following equation:
+
+$$
+R_{cv}^{2} = 1- \frac{\sum_{i=1}^{k}(y_{i-test}-\hat{y}_{i-test})^{2}}{\sum_{i=1}^{k}(y_{i-test}-\bar{y}_{train})^{2}}
+$$
+
+With $k$ being the number of studies in the testing dataset, $\hat{y}_{i-test}$ being the predicted effect size for study $i$, and $\bar{y}_{train}$ being the mean of the training dataset.
+
+The algorithms' ability to perform variable selection was evaluated by three indices: sensitivity, specificity, and the fraction of the product over the sum (FPS).
+These indices are based on proportions computed across replications within each condition.
+Sensitivity $P$ is the ability to select true positives, or the probability that a variable is selected, $S = 1$, given that it has a non-zero population effect: $P = p(S = 1||\beta| >0)$.
+Specificity is the ability to identify true negatives, or the probability that a variable is not selected given that it has a zero population effect: $N = p(S = 0|\beta  = 0)$.
+It is possible for a poorly-fitted model to score highly on specificity by predicting all null effects while detecting no true positives.
+Therefore, we additionally computed a the fraction of the product over the sum (FPS) as an overall performance criterion, which is given by $FPS=  2(\frac{P*N}{P+N})$.
+
+The ability to recover population parameters $\beta$ and $\tau^2$ was examined in terms of bias and variance of these estimates.
+The bias is given by the mean deviation of the estimate from the population value,
+and the variance is given by the variance of this deviation.
+
+## Design factors
+
+The simulation conditions consist of all unique combinations of the following design factors: the number of studies in the training data $k \in (22, 40, 80)$, average within-study sample size $\bar{n} \in (40, 100, 200)$, the population effect size of relevant moderators $\beta \in (.2, .5, .8)$, the number of standard normally distributed moderators $p \in (2, 3, 6)$, and residual heterogeneity $\tau^{2} \in (.01, .04, .1)$.
+The true effect size was simulated using two models:
+one with a main effect of one moderator, $T_{i}= \beta x_{1i} + \epsilon_i$, and one with a non-linear, cubic effect of one moderator, $T_{i}= \beta x_{1i} + \beta x_{1i}^{2} + \beta x_{1i}^{3} + \epsilon_i$,
+where $\epsilon_i \sim N(0, \tau^2)$.
+The observed effect size $y_i$ was then simulated as a standardized mean difference (SMD),
+sampled from a non-central t-distribution.
+For all simulation conditions, 100 datasets were generated.
 
 # Results
+
 There were 3888 condition combinations in total.

### 2021-12-05 paper/manuscript.Rmd
first results

@@
 library("papaja")
+library(tidySEM)
+library(kableExtra)
 r_refs("r-references.bib")
+out <- readRDS("output.RData")
 ```
@@
 
-The simulation conditions consist of all unique combinations of the following design factors: the number of studies in the training data $k \in (22, 40, 80)$, average within-study sample size $\bar{n} \in (40, 100, 200)$, the population effect size of relevant moderators $\beta \in (.2, .5, .8)$, the number of standard normally distributed moderators $p \in (2, 3, 6)$, and residual heterogeneity $\tau^{2} \in (.01, .04, .1)$.
+The simulation conditions consist of all unique combinations of the following design factors: the number of studies in the training data $k \in (22, 40, 80)$, average within-study sample size $\bar{n} \in (40, 100, 200)$, the population effect size of relevant moderators $\beta \in (0, .2, .5, .8)$, the number of skewed normally distributed moderators $p \in (2, 3, 6)$, and residual heterogeneity $\tau^{2} \in (.01, .04, .1)$.
+The scale parameters of the skewed normal moderators were selected from $\omega \in (0, 2, 10)$, where $\omega = 0$ corresponds to a standard normal distribution.
 The true effect size was simulated using two models:
-one with a main effect of one moderator, $T_{i}= \beta x_{1i} + \epsilon_i$, and one with a non-linear, cubic effect of one moderator, $T_{i}= \beta x_{1i} + \beta x_{1i}^{2} + \beta x_{1i}^{3} + \epsilon_i$,
+one with a linear effect of one moderator, $T_{i}= \beta x_{1i} + \epsilon_i$, and one with a non-linear (cubic) effect of one moderator, $T_{i}= \beta x_{1i} + \beta x_{1i}^{2} + \beta x_{1i}^{3} + \epsilon_i$,
 where $\epsilon_i \sim N(0, \tau^2)$.
@@
 sampled from a non-central t-distribution.
+The design factors combined to produce `r out$conditions` unique conditions.
 For all simulation conditions, 100 datasets were generated. 
+<!-- x = rnorm(1000) -->
+<!-- func <- function(x, b){b*x+(b*(x^2))+(b*(x^3))} -->
+<!-- dat <- data.frame(x = x, -->
+<!--                   y = c(func(x, .2), func(x, .5), func(x, .8)), -->
+<!--                   es = rep(c(".2", ".5", ".8"), each = 1000)) -->
 
+<!-- ggplot(dat, aes(x, y, color = es))+geom_smooth() -->
 # Results
 
-There were 3888 condition combinations in total.
-The algorithms ran on 100 different datasets on each of those, leaving 388800 cases to analyze.
-There were 20 of those cases for which the RMA algorithm had missing values on all metrics.
-Closer inspection showed that both the cubic and exponential model each contributed ten times to the missing values and only when 2, 3 or 6 moderators were taken up in the model.
-However, since the missing cases make up only 0.005% of the data, the cases were chosen to be omitted from further analysis entirely.
-Another observation is that the two-way interaction model only had results when the number of moderators in the model was either 3, 4 or 7, while the other models only had results when there were 2, 3 or 6 moderators.
-It is therefor more challenging to compare and interpret the effect the moderators had on the performance criteria between the two-way interaction and the other models.
+The RMA algorithm failed to converge for `r out$missing` replications, all of which were characterized by low number of cases ($k \leq 40$) and high effect sizes $\beta \geq .5$.
+These cases were omitted from further analysis.
 
 ## Predictive performance
-Predictive performance was operationalized by calculating the $R^2_{test}$ and $MSE_{test}$ for every combination of design factors, in further test denoted as $R^2$ and $MSE$ respectively.
-The densities for the $R^{2}_{test}$ and $MSE_{test}$ values were skewed however, which is why it was chosen to use the median $R^2$ as the metric for predictive performance, rather than the mean.
-The spread of the metrics was described using the Mean Absolute Deviation [MAD], rather than the standard deviation.
-It was found that the Horseshoe, Lasso and RMA algorithm performed similarly overall, $R^2_{Hs} = 0.51 \pm 0.36$, $MSE_{Hs} = 0.21 \pm 0.18$ ; $R^2_{Lasso} = 0.50 \pm 0.37$, $MSE_{Lasso} = 0.21\pm 0.19$; $R^2_{RMA} = 0.50 \pm 0.37$, $MSE_{RMA} = 0.22 \pm 0.23$ .
-The MetaForest algorithm performed worst on $R^2$: $R^2_{Mf} = 0.35 \pm 0.38$, $MSE_{Mf} = 0.22 \pm 0.19$
+```{r}
+out <- readRDS("output.RData")
+```
 
-To determine the effect of the design factors on $R^2$ for all algorithms, four separate ANOVA’s were performed; one per algorithm.
-The effect size $\eta^{2}$ per condition per algorithm, including for all two-way interactions can be found in table 1.
-Do note that the ANOVA's were performed with the normality assumption violated.
-The estimates serve mostly as a guidance, rather than an absolute result.
+Results indicated that the overall $R^2_{test}$ was highest for BRMA with a Horseshoe prior and lowest for RMA, see \@ref(tab:tabr2).
+This difference was driven in part by the fact that explained variance was somewhat higher for the BRMA models when the true effect was not null, and by the fact that RMA had larger negative explained variance when the true effect was equal to zero (i.e., there was no effect to detect).
 
-Not too surprisingly, It was found that the true effect size $\beta$ had the largest effect on $R^{2}$ for all algorithms.
-As $\beta$ increased, the performance of all algorithms increased as well.
-However, $\beta$ did interact with the model that was estimated, being either a linear, two-way interaction, cubic or an exponential model.
-A graphical representation of the interaction is shown in image 1.
-When the exponential and cubic model were estimated, the increase of $R^{2}$ slowed for every higher value of $\beta$.
-For the estimation of the two-way interaction model the increase only slowed when $\beta$ went from 0.5 to 0.8, while the steepest increase for the linear model estimation was when $\beta$ increased from 0.2 to 0.5.
-Also noteworthy is that $R^2$ stagnated during estimation of the cubic model as $\beta$ went up to 0.5, while for the other models $R^2$ did keep increasing.
-There was little difference in median $R^2$ between Horsehoe, Lasso and RMA, while MetaForest performed worst.
+```{r tabr2, results= "asis"}
+tab <- read.csv("r2.csv")[1:7][c(1, 2,5,3,6,4,7)]
+#[, c(seq(1, 9, by = 3), seq(2, 9, by = 3),
+#                                                                  seq(3, 9, by = 3))]
+names(tab)[1] <- ""
+names(tab) <- gsub(".", " ", names(tab), fixed = T)
+names(tab)[grepl("Mean", names(tab))] <- paste0(names(tab)[grepl("Mean", names(tab))], "}$")
+names(tab) <- gsub("Mean R2", "$\\bar{R^2}_{", names(tab), fixed = T)
+names(tab) <- gsub("SD R2.*", "$SD$", names(tab))
+names(tab) <- gsub("CI.*", "$CI_{95}$", names(tab))
+kbl(tab[, ], caption = "Mean and SD of predictive R2 for BRMA with a horseshoe (HS) and LASSO prior, and for RMA, for models with a true effect (ES != 0) and without (ES = 0).", digits = 2, row.names = FALSE, escape = FALSE, booktabs = TRUE, col.names = gsub("\\.\\d", "", names(tab)))
 
-The second largest marginal effect was that of the estimated model.
-All algorithms had the highest $R^2$ under the cubic model, followed by a similar performance on the two-way interaction and exponential models.
-All algorithms performed worst for the linear model.
-There again was little difference in performance between the Pema algorithms and RMA, although MetaForest performed worst.
-Image 2A shows the relationship.
+```
 
-There also was a moderate interaction effect between the estimated model and the amount of skewness of the input data $\alpha$, especially for the Pema algorithms.
-Again, Pema and RMA algorithms performed best, followed by MetaForest in all conditions.
-Most obvious to note is that all algorithms, except for when the linear model was estimated, generally performed better on more skewed data, although the algorithms did perform worse during estimation of the two-way interaction model when $\alpha$ went from 5 to 10.
-Overall performance was best during estimation of the cubic model, but the performance difference between estimated models decreased as $\alpha$ increased.
-Image 3 shows the relationship.
+To determine the effect of the design factors on $R^2_{test}$, ANOVA’s were performed; one per algorithm.
+Note that p-values are likely not informative due to the large sample size and violation of the assumptions of normality and homoscedasticity.
+The results should thus be interpreted as descriptive, not inferential, statistics.
+Table \@ref(tab:tabr2eta) reports the effect size  $\eta^{2}$ of main effects and two-way interactions between simulation conditions.
+As many effects of design factors were monotonously positive or negative for all algorithms,
+we provide an overview of the interpretation of those effects in the Table.
+Interpretation was less straightforward for a number of interactions;
+for these, the median $R^2_{test}$ is graphed in Figure \@ref(fig:figanova).
 
-The true residual heterogeneity $\tau^{2}$ had a negative linear relationship for all algorithms on $R^{2}$. That is, as $\tau^{2}$ increased, $R^{2}$ decreased. Image 2B shows the relationship.
+```{r tabr2eta, results= "asis", eval = TRUE}
+tabanova <- readRDS("anova.RData")
+#tabanova$condition <- gsub("alpha", "omega", tabanova$condition, fixed = T)
+#tabanova$condition <- gsub("$mean{n}$", "$n$", tabanova$condition, fixed = T)
+tabanova$Factor <- gsub("\\$(omega|beta|tau)", "\\$\\\\\\1", tabanova$Factor)
+tabanova$HS.vs..LASSO <- NULL
+tabanova <- tabanova[, c(ncol(tabanova), 2:(ncol(tabanova)-1))]
+# kbl(tabanova, caption = "Effect size of design factors and their two-way interactions on R2 the different algorithms, and of the difference between algorithms.
+The comparison between HS and LASSO was zero in the second decimal for all conditions.
+Interpretation indicates whether the effect was uniformly positive or negative (for interactions, the effect of the second design factor in the interaction) for all algorithms.", digits = 2, row.names = FALSE, escape = FALSE, booktabs = TRUE, col.names = gsub("(?<!vs)\\.", " ", names(tabanova), perl = TRUE)) |>
+#   kable_styling(latex_options = c("scale_down"))
+apa_table(tabanova, caption = "Effect size of design factors and their two-way interactions on R2 the different algorithms, and of the difference between algorithms.
+The comparison between HS and LASSO was zero in the second decimal for all conditions.
+Interpretation indicates whether the effect was uniformly positive or negative (for interactions, the effect of the second design factor in the interaction) for all algorithms.", digits = 2, escape = FALSE, col.names = gsub("(?<!vs)\\.", " ", names(tabanova), perl = TRUE), longtable = TRUE)
+```
 
-The mean sample size per study $\bar{n}$ also had a moderate effect.
-For all algorithms the effect of $\bar{n}$ was positively linearly related with $R^{2}$.
-Again, the Pema and RMA algorithms performed better than MetaForest.
-Image 2C shows the relationship.
+```{r figanova, fig.cap="Predictive R2 for HS (circle, solid line), LASSO(triangle, dotted line) and RMA (square, dashed line) for interactions.
+One design factor is displayed in different panels, the other on the x-axis."}
+knitr::include_graphics("other_effects.png")
+```
 
-An especially large effect was found for the number of studies used in the training data $\kappa$ for MetaForest, while this effect was substantially smaller for RMA, Lasso and Horseshoe.
-The relationship is positively linear for all algorithms, but the slope is especially steep for MetaForest.
-Image 2D shows the relationship.
+To establish difference in predictive performance between the three algorithms,
+the interactions of algorithm (HS vs. LASSO, HS vs. RMA and LASSO vs. RMA) were estimated.
+The $\eta^2$ of these differences between algorithms are also displayed in Table \@ref(tab:tabr2eta).
+Note that $\eta^2$ for the comparison between HS and LASSO was zero in the second decimal for all conditions; thus, this comparison was omitted from the Table.
+Results show that the largest differences between algorithms were due to the effect size $\beta$, number of cases in the training data $k$, and the number of irrelevant moderators $M$.
+The effect of these factors by algorithm is displayed in Figure \@ref(fig:figmaindif).
+Evidently, predictive performance increased most for the HS algorithm when the effect size increased above zero.
+As noted previously, predictive performance of RMA was most negative (negative explained variance) when the effect size was zero.
+The HS algorithm furthermore had the consistently highest predictive performance regardless of number of cases in the training data or number of irrelevant moderators, and was relatively less affected by increases in the number of training cases (panel b) or in the number of irrelevant moderators (panel c).
+Similarly, the HS algorithm furthermore had the consistently highest predictive performance regardless of number of cases in the training data, and thus also increased less when the number of training cases increased (panel b).
+Conversely, RMA had relatively poor predictive performance on average, and was more responsive to increases in the number of training cases and irrelevant moderators.
 
-Finally, the number of moderators did not have a big effect for the Pema algorithms, while for RMA and MetaForest the effect was more noticeable.
+```{r figmaindif, fig.cap="Predictive R2 for design factors with largest differences in predictive performance across the HS (circle, solid line), LASSO(triangle, dotted line) and RMA (square, dashed line) algorithms."}
+knitr::include_graphics("main_diff.png")
+```
+
+<!-- Results show that the true effect size $\beta$ had the largest marginal effect on $R^{2}$ for all algorithms. -->
+<!-- As $\beta$ increased, each algorithm's performance increased as well. -->
+<!-- Predictably, the effect of $\beta$ interacted with the model used to simulate data. -->
+<!-- Compared to the linear model, $R^{2}_{test}$ for the cubic model showed diminishing increases with $\beta$. -->
+<!-- The third largest marginal effect was that of the simulation model. -->
+<!-- All algorithms had higher $R^2_{test}$ under the cubic model than under the linear model, which makes sense because $\beta$ had an additional effect through the polynomials of the relevant moderator.
+-->
+<!-- There was an interaction between the model and the amount of skewness of the predictor variable $\omega$: -->
+<!-- For all algorithms, the association between skewness and $R^2_{test}$ was negative for the linear model, and positive for the cubic model. -->
+<!-- <!-- Figure \@ref(fig:skewness) shows the relationship. --> -->
+<!-- The residual heterogeneity $\tau^{2}$ had a negative linear relationship with $R^{2}_{test}$ for all algorithms. -->
+<!-- The mean sample size per study $\bar{n}$ also had a moderate effect for all algorithms, indicating that a greater number of participants within studies was positively linearly related with $R^{2}_{test}$.
+-->
+<!-- Similarly, the number of studies in the training data $k$ was positively related with $R^{2}_{test}$. -->
+
+<!-- Finally, the number of moderators did not have a big effect for the Pema algorithms, while for RMA and MetaForest the effect was more noticeable.
 The relationship is shown in image 7.
@@
 This increase in performance for MetaForest appears when the number of moderators go from 3 to 4.
+-->
 

### 2021-12-05 simulatie_2021/Analysis Sim2021_2.R

@@ -3,7 +3,7 @@
 ####################
 dependencies <- c('data.table', 'tidyverse', 'stringr', 'ggplot2')
 lapply(dependencies, function(x) library(x, character.only = T))
-dat <- as.data.table(readRDS(r"(C:\Users\e_lib\OneDrive\Documents\Caspar Repositories\PEMA\simulatie_2021\sim_results_2021-09-08.RData)"))
+dat <- as.data.table(readRDS("simulatie_2021/results/sim_results_2021-09-08.RData"))
 
 # load in needed functions
 source('./simulatie_2021/Analysis_functions.R') #created functions used for analysis

### 2021-12-05 simulatie_2021/Analysis Sim2021_3.R

@@ -1,0 +1,482 @@
+####################
+# Data exploration #
+####################
+library(latex2exp)
+library(cowplot)
+out <- list()
+dependencies <- c('data.table', 'tidyverse', 'stringr', 'ggplot2')
+lapply(dependencies, function(x) library(x, character.only = T))
+dat <- as.data.table(readRDS("simulatie_2021/results/sim_results_2021-09-08.RData"))
+dat <- dat[dat$model %in% c("es * x[, 1]", "es * x[, 1] + es * (x[, 1] ^ 2) + es * (x[, 1] ^ 3)"),]
+dat[, grep("^mf", names(dat)) := NULL]
+
+# load in needed functions
+source('./simulatie_2021/Analysis_functions.R') #created functions used for analysis
+
+#some data preprocessing
+newnames <- c('hs', 'lasso', 'rma') #names of algorithms
+conditions <- c("k_train", "mean_n", "es", "tau2","alpha_mod", "moderators", "model") #conditions that vary
+lc <- length(conditions) #length of conditions, handy for further code
+dat[, (conditions):=lapply(.SD, factor), .SDcols=conditions] #convert to factor
+levels(dat$model) <- c('linear', 'cubic') #rename to more understandable levels
+
+#there are duplicated columns which contain the same values, we can omit those
+last <- function(x) { return( x[length(x)] ) } #function to obtain last element from vector
+unique_cols <- which(!duplicated(colnames(dat)))
+dat <- dat[ , unique_cols[1]:last(unique_cols)]
+
+#Checking for missing values
+#first we omit the columns that should contain missing values which are the 'sel' columns
+lashs <- colnames(dat)[grep(pattern = "_(ci|hdi)_sel_\\d", colnames(dat))]
+mfrma <- colnames(dat)[grep(pattern = "(mf|rma)_sel_\\d", colnames(dat))]
+
+#create df without sel columns and subset it for rows that contain more than 1 missing
+wo_sel_cols <- colnames(dat)[!colnames(dat) %in% c(lashs, mfrma)]
+dat_no_sel <- dat[ , .SD, .SDcols=c(conditions, wo_sel_cols)] #subset data
+MD <- dat_no_sel[rowSums(is.na(dat_no_sel)) > 0, ]
+out$missing <- sum(MD$model == "cubic")
+#View(MD) # issue is with rma
+
[…]

### 2021-12-05 simulatie_2021/Analysis_functions.R

@@ -86,44 +86,41 @@ plot_marginal_median <- function(condition, df, lonames, metric, pointsize = 5, 
   condition <- as.name(condition)
   hs <- as.name(lonames[1])
   las <- as.name(lonames[2])
-  mf <- as.name(lonames[3])
-  rma <- as.name(lonames[4])
+  rma <- as.name(lonames[3])
 
   cond <- df %>%
     group_by(!!condition)%>%
     summarise(Horseshoe = median(!!hs),
               Lasso = median(!!las),
-              Metaforest = median(!!mf),
               RMA = median(!!rma)) %>%
     pivot_longer(cols = !all_of(condition), names_to = 'alg', values_to = metric)
 
   ggplot(data = cond, aes(x = !!condition,y = !!as.name(metric), linetype = alg, group = alg, shape = alg)) +
     geom_line(size = linesize, ) +
     geom_point(size = pointsize) +
-    theme_classic(base_size = 25)
+    theme_bw(base_size = 25)
 }
+
 
 plot_interaction_median <- function(condition, intcond, df, lonames, metric){
   condition <- as.name(condition)
   intcond <- as.name(intcond)
   hs <- as.name(lonames[1])
   las <- as.name(lonames[2])
-  mf <- as.name(lonames[3])
-  rma <- as.name(lonames[4])
+   rma <- as.name(lonames[3])
 
   cond <- df %>%
     group_by(!!condition, !!intcond)%>%
     summarise(Horseshoe = median(!!hs),
               Lasso = median(!!las),
-              Metaforest = median(!!mf),
               RMA = median(!!rma)) %>%
-    pivot_longer(cols = c(Horseshoe, Lasso, Metaforest, RMA), names_to = 'alg', values_to = metric)
+    pivot_longer(cols = c(Horseshoe, Lasso, RMA), names_to = 'alg', values_to = metric)
 
   ggplot(data = cond, aes(x = !!condition,y = !!as.name(metric), linetype = alg, group = alg, shape = alg)) +
     geom_line(size = 1, ) +
     geom_point(size = 2.5) +
-    facet_wrap(~cond[[intcond]], scales = 'free') +
-    theme_classic(base_size = 25)
+    facet_wrap(~cond[[intcond]]) +
+    theme_bw(base_size = 25) + theme(legend.position = "none")
 }
 
 

### 2021-12-08 paper/manuscript.Rmd
first paper draft

@@
 abstract: |
-  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
+  Todo
 
-  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
-
-  One sentence clearly stating the **general problem** being addressed by  this particular study.
-
-  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
-
-  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
-
-  One or two sentences to put the results into a more **general context**.
-
-  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
-
-  <!-- https://tinyurl.com/ybremelq -->
-
-keywords          : "keywords"
-wordcount         : "X"
+keywords          : "meta-analysis, machine learning, bayesian, lasso, regularized"
+wordcount         : "5356"
 
@@
 which is the standard in the field.
-The algorithms are evaluated on three different criteria:
-The algorithms' predictive performance in new data, 
+We evaluated the algorithms' predictive performance in new data, 
 <!-- examining its predictive performance in new data, its sensitivity and specificity in variable selection, and its bias and variance in recovering population parameters. -->
-their ability to perform variable selection,
+<!-- their ability to perform variable selection, -->
 and their ability to recover population parameters. 
+Our research questions are whether BRMA offers a performance advantage over RMA in terms of any of these indicators;
+under what conditions BRMA does not offer an advantage,
+and which prior (horseshoe versus LASSO) is to be preferred.
 
@@
 
-The algorithms' ability to perform variable selection was evaluated by three indices: sensitivity, specificity, and the fraction of the product over the sum (FPS).
-These indices are based on proportions computed across replications within each condition.
+The algorithms' ability to perform variable selection was evaluated by sensitivity and specificity.
 Sensitivity $P$ is the ability to select true positives, or the probability that a variable is selected, $S = 1$, given that it has a non-zero population effect: $P = p(S = 1||\beta| >0)$.
 Specificity is the ability to identify true negatives, or the probability that a variable is not selected given that it has a zero population effect: $N = p(S = 0|\beta  = 0)$.
-It is possible for a poorly-fitted model to score highly on specificity by predicting all null effects while detecting no true positives.
-Therefore, we additionally computed a the fraction of the product over the sum (FPS) as an overall performance criterion, which is given by $FPS=  2(\frac{P*N}{P+N})$.
 
@@
 
-The simulation conditions consist of all unique combinations of the following design factors: the number of studies in the training data $k \in (22, 40, 80)$, average within-study sample size $\bar{n} \in (40, 100, 200)$, the population effect size of relevant moderators $\beta \in (0, .2, .5, .8)$, the number of skewed normally distributed moderators $p \in (2, 3, 6)$, and residual heterogeneity $\tau^{2} \in (.01, .04, .1)$.
-The scale parameters of the skewed normal moderators were selected from $\omega \in (0, 2, 10)$, where $\omega = 0$ corresponds to a standard normal distribution.
-The true effect size was simulated using two models:
+To examine performance in a range of realistic meta-analysis scenarios,
+several design factors were manipulated:
+The number of studies in the training data $k \in (20, 40, 100)$, the average within-study sample size $\bar{n} \in (40, 80, 160)$, the population effect size of relevant moderators $\beta \in (0, .2, .5, .8)$, the number of moderators $p \in (2, 3, 6)$, and residual heterogeneity $\tau^{2} \in (.01, .04, .1)$.
+According to a review of 705 published psychological meta-analyses (Van Erp et al., 2017),
+these values of $\tau^2$ fall within the range observed in practice.
+Note that both BRMA and RMA assume linear effects.
+To test the robustness of the algorithms to violations of this assumption, true effect sizes were simulated using two models:
 one with a linear effect of one moderator, $T_{i}= \beta x_{1i} + \epsilon_i$, and one with a non-linear (cubic) effect of one moderator, $T_{i}= \beta x_{1i} + \beta x_{1i}^{2} + \beta x_{1i}^{3} + \epsilon_i$,
 where $\epsilon_i \sim N(0, \tau^2)$.
-The observed effect size $y_i$ was then simulated as a standardized mean difference (SMD),
+The algorithms further assume normality of residuals.
+To examine robustness of the algorithms to violations of this assumption,
+moderator variables were simulated as skewed normal moderators, with scale parameter $\omega \in (0, 2, 10)$, where $\omega = 0$ corresponds to the standard normal distribution.
+The design factors combined to produce `r out$conditions` unique conditions.
+For all simulation conditions, 100 data sets were generated. 
+In each data set, the observed effect size $y_i$ was simulated as a standardized mean difference (SMD),
 sampled from a non-central t-distribution.
-The design factors combined to produce `r out$conditions` unique conditions.
-For all simulation conditions, 100 datasets were generated. 
+
 <!-- x = rnorm(1000) -->
@@
 out <- readRDS("output.RData")
+whichhi <- prop.table(out$which_highest)
 ```
 
+Within data sets, the BRMA with a horseshoe prior had the highest predictive performance `r round(whichhi[1]*100)`% of the time, followed by RMA, `r round(whichhi[3]*100)`%, and finally BRMA with a LASSO prior, `r round(whichhi[2]*100)`%.
 Results indicated that the overall $R^2_{test}$ was highest for BRMA with a Horseshoe prior and lowest for RMA, see \@ref(tab:tabr2).
@@
 
-To determine the effect of the design factors on $R^2_{test}$, ANOVA’s were performed; one per algorithm.
+The effect of the design factors on $R^2_{test}$ was evaluated using ANOVAs.
 Note that p-values are likely not informative due to the large sample size and violation of the assumptions of normality and homoscedasticity.
-The results should thus be interpreted as descriptive, not inferential, statistics.
-Table \@ref(tab:tabr2eta) reports the effect size  $\eta^{2}$ of main effects and two-way interactions between simulation conditions.
-As many effects of design factors were monotonously positive or negative for all algorithms,
-we provide an overview of the interpretation of those effects in the Table.
-Interpretation was less straightforward for a number of interactions;
-for these, the median $R^2_{test}$ is graphed in Figure \@ref(fig:figanova).
+The results should therefore be interpreted as descriptive, not inferential, statistics.
+Table \@ref(tab:tabr2eta) reports the effect size $\eta^{2}$ of simulation conditions on $R^2_{test}$.
+<!-- for main effects and two-way interactions between simulation conditions. -->
+<!-- , -->
+<!-- we provide an overview of the interpretation of those effects in the Table. -->
+<!-- For interaction effects, we report whether the interaction was spreading -->
+<!-- Interpretation was less straightforward for a number of interactions; -->
+<!-- for these, the median $R^2_{test}$ is graphed in Figure \@ref(fig:figanova). -->
 
@@
 tabanova <- readRDS("anova.RData")
+tabanova <- tabanova[!grepl(":", tabanova$condition), ]
+tabanova$Interpretation[!tabanova$Interpretation %in% c("positive", "negative", "other")] <- NA
 #tabanova$condition <- gsub("alpha", "omega", tabanova$condition, fixed = T)
@@
 tabanova$Factor <- gsub("\\$(omega|beta|tau)", "\\$\\\\\\1", tabanova$Factor)
-tabanova$HS.vs..LASSO <- NULL
+#tabanova$HS.vs..LASSO <- NULL
 tabanova <- tabanova[, c(ncol(tabanova), 2:(ncol(tabanova)-1))]
@@
 #   kable_styling(latex_options = c("scale_down"))
-apa_table(tabanova, caption = "Effect size of design factors and their two-way interactions on R2 the different algorithms, and of the difference between algorithms.
-The comparison between HS and LASSO was zero in the second decimal for all conditions.
-Interpretation indicates whether the effect was uniformly positive or negative (for interactions, the effect of the second design factor in the interaction) for all algorithms.", digits = 2, escape = FALSE, col.names = gsub("(?<!vs)\\.", " ", names(tabanova), perl = TRUE), longtable = TRUE)
+#tabanova <- tabanova[!grepl(":", tabanova$condition, fixed = T), ]
+apa_table(tabanova, caption = "Effect size of design factors on predictive R2 of the different algorithms, and of the difference between algorithms.
+Interpretation indicates whether a main effect was uniformly positive or negative across all algorithms.", digits = 2, escape = FALSE, col.names = gsub("(?<!vs)\\.", " ", names(tabanova), perl = TRUE))#, longtable = TRUE)
+# Interpretation for main effects indicates whether the effect was uniformly positive or negative or other, and for interactions, whether it is a spreading or crossover interaction.
+```
+```{r figr2, fig.cap="Predictive R2 for BRMA with horseshoe (HS) and LASSO prior, and RMA. Plots are sorted by largest performance difference between BRMA and RMA."}
+knitr::include_graphics("r2.png")
 ```
@@
 ```{r figanova, fig.cap="Predictive R2 for HS (circle, solid line), LASSO(triangle, dotted line) and RMA (square, dashed line) for interactions.
-One design factor is displayed in different panels, the other on the x-axis."}
+One design factor is displayed in different panels, the other on the x-axis.", eval = FALSE}
 knitr::include_graphics("other_effects.png")
@@
 
-To establish difference in predictive performance between the three algorithms,
-the interactions of algorithm (HS vs. LASSO, HS vs. RMA and LASSO vs. RMA) were estimated.
+To test our research questions, we computed interactions of algorithm (HS vs. LASSO, HS vs. RMA and LASSO vs. RMA) with the other design factors.
 The $\eta^2$ of these differences between algorithms are also displayed in Table \@ref(tab:tabr2eta).
 Note that $\eta^2$ for the comparison between HS and LASSO was zero in the second decimal for all conditions; thus, this comparison was omitted from the Table.
-Results show that the largest differences between algorithms were due to the effect size $\beta$, number of cases in the training data $k$, and the number of irrelevant moderators $M$.
-The effect of these factors by algorithm is displayed in Figure \@ref(fig:figmaindif).
+The effect of design factors by algorithm is displayed in Figure \@ref(fig:figr2); these plots have been ranked from largest difference between BRMA and RMA to smallest.
+Results indicate that the largest differences between algorithms were due to the effect size $\beta$, number of irrelevant moderators $M$, and the number of cases in the training data $k$.
 Evidently, predictive performance increased most for the HS algorithm when the effect size increased above zero.
 As noted previously, predictive performance of RMA was most negative (negative explained variance) when the effect size was zero.
-The HS algorithm furthermore had the consistently highest predictive performance regardless of number of cases in the training data or number of irrelevant moderators, and was relatively less affected by increases in the number of training cases (panel b) or in the number of irrelevant moderators (panel c).
-Similarly, the HS algorithm furthermore had the consistently highest predictive performance regardless of number of cases in the training data, and thus also increased less when the number of training cases increased (panel b).
+The HS algorithm furthermore had the consistently highest predictive performance regardless of number of irrelevant moderators or number of cases in the training data, and was relatively less affected by increases in the number of irrelevant moderators (panel b) or in the number of training cases (panel c).
+Similarly, the HS algorithm furthermore had the consistently highest predictive performance regardless of number of cases in the training data, and thus also increased less when the number of training cases increased (panel c).
 Conversely, RMA had relatively poor predictive performance on average, and was more responsive to increases in the number of training cases and irrelevant moderators.
 
-```{r figmaindif, fig.cap="Predictive R2 for design factors with largest differences in predictive performance across the HS (circle, solid line), LASSO(triangle, dotted line) and RMA (square, dashed line) algorithms."}
+```{r figmaindif, fig.cap="Predictive R2 for design factors with largest differences in predictive performance across the HS (circle, solid line), LASSO(triangle, dotted line) and RMA (square, dashed line) algorithms.", eval = FALSE}
 knitr::include_graphics("main_diff.png")
@@
 
-## Estimating residual heterogeneity
-The ability of the algorithms to correctly estimate $\tau^{2}$ was operationalized by subtracting the true value for $\tau^{2}$ from the $\tau^{2}$ estimated by the algorithms.
-Again, the median and Mean Absolute Deviation were used as metrics for performance.
-The RMA algorithm showed the best results, $\Delta\tau^2_{RMA} = 0.02 \pm 0.06$, followed by the MetaForest algorithm $\Delta\tau^2_{Mf} = 0.09 \pm 0.13$.
-The Pema algorithms performed worst $\Delta\tau^2_{Lasso} = 0.23 \pm 0.18$; $\Delta\tau^2_{Hs} = 0.23 \pm 0.17$.
-The finding that all medians are positive implies that all algorithms have a bigger tendency to overestimate $\tau^{2}$ than underestimate it.
-One comment to make is that uncertainty of the estimates generally increased as $\Delta\tau^{2}$ also increased.
-This implies that there was more variation in performance as median performance worsened.
+## Variable selection
+```{r}
+selprob <- out$selection
+colnames(selprob) <- c("HS", "LASSO", "RMA")
+truepos <- paste0(sapply(order(selprob[1,], decreasing = TRUE), function(i)paste0("$P_{", colnames(selprob)[i], "}", report(selprob[1,i]), "$")), collapse = ", ")
+trueneg <- paste0(sapply(order(selprob[2,], decreasing = TRUE), function(i)paste0("$N_{", colnames(selprob)[i], "}", report(selprob[2,i]), "$")), collapse = ", ")
+proboveral <- colMeans(selprob)
+proboveral <- paste0(sapply(order(proboveral, decreasing = TRUE), function(i)paste0("$Acc_{", colnames(selprob)[i], "}", report(proboveral[i]), "$")), collapse = ", ")
+```
 
-To determine the effect of the design factors on $\Delta\tau^{2}$ for all algorithms, four separate ANOVA’s were performed.
-The effect size $\eta^{2}$ per condition per algorithm, including $\eta^2$ for all two-way interactions can be found in table 2.
-Again, the assumption of normality was violated.
+To determine the extent to which the algorithms could perform variable selection correctly, the sensitivity to true positives $P$ and specificity to true negatives $N$ were calculated.
+Only simulation conditions with $\beta > 0$ were used, such that the effect of the first moderator was always positive in the population and could be used to calculate $P$,
+and the effect of the second moderator was always zero in the population and could be used to calculate $N$.
 
-The biggest predictor on the correct estimation of $\tau^{2}$ was the estimated model.
-This was mainly because the algorithms overestimated $\tau^{2}$ most when the model contained cubic terms.
-Image 5A shows the marginal relationship of the estimated model on $\Delta\tau^{2}$ .
-It becomes more clear why this overestimation occurred when showing the interaction between $\beta$ and the model estimated on $\Delta\tau^{2}$, shown in image 6.
+As the regularized algorithms shrink all coefficients towards zero, it is unsurprising that sensitivity was highest for the un-regularized algorithm RMA, followed by HS and LASSO, `r truepos`.
+By contrast, specificity was higher for the regularized algorithms, `r trueneg`.
+Overall accuracy reflects the trade off between sensitivity and specificity.
+As the baserate of true positives and true negatives is equal in this simulation, overall accuracy is simply given by $Acc = (P+N)/2$.
+Results showed that overall accuracy was approximately equal for RMA and HS, and was lower for LASSO, `r proboveral`.
+
+Cramer's V, an effect size for categorical variables, was used to examine the effect of design factors on sensitivity (Table \@ref(tab:tabcramerp), Figure \@ref(fig:figsensitivity)) and specificity (Table \@ref(tab:tabcramern), Figure \@ref(fig:figspecificity)).
+We also computed this effect size for the difference between algorithms in the number of true positives by design factor.
+
+```{r tabcramerp, results= "asis", eval = TRUE}
+tabselect <- readRDS("selected.RData")
+rownames(tabselect) <- NULL
+names(tabselect) <- gsub("(?<!vs)\\.", " ", names(tabselect), perl = TRUE)
+apa_table(tabselect, caption = "Effect size (Cramer's V) of design factors, and of the difference between algorithms, on sensitivity (P).", digits = 2, escape = FALSE)#, longtable = TRUE)
+# Interpretation for main effects indicates whether the effect was uniformly positive or negative or other, and for interactions, whether it is a spreading or crossover interaction.
+```
+```{r figsensitivity, fig.cap="Sensitivity by design factors for the HS (circle, solid line), LASSO(triangle, dotted line) and RMA (square, dashed line) algorithms."}
+knitr::include_graphics("sensitivity.png")
+```
+```{r tabcramern, results= "asis", eval = TRUE}
+tabselectn <- readRDS("notselected.RData")
+rownames(tabselectn) <- NULL
+names(tabselectn) = gsub("(?<!vs)\\.", " ", names(tabselectn), perl = TRUE)
+apa_table(tabselectn, caption = "Effect size (Cramer's V) of design factors, and of the difference between algorithms, on specificity (N).", digits = 2, escape = FALSE)#, longtable = TRUE)
+```
+```{r figspecificity, fig.cap="Specificity by design factors for the HS (circle, solid line), LASSO(triangle, dotted line) and RMA (square, dashed line) algorithms."}
+knitr::include_graphics("specificity.png")
+```
+
+Differences in sensitivity between the algorithms were near-zero for HS and LASSO.
+The difference between the two BRMA algorithms and RMA were largest for the design factor effect size $\beta$, followed by the model and number of studies $k$.
+Across all design factors, RMA had the highest sensitivity, followed by HS and then LASSO.
+
+For specificity, differences in sensitivity between HS and LASSO were largest for the number of noise moderators $M$, followed by the effect size $\beta$, number of studies $k$, and residual heterogeneity $\tau^2$.
+The difference between the two BRMA algorithms and RMA were largest for the design factor number of studies $k$, followed by the model, the number of noise moderators $M$, and the effect size $\beta$.
+Across all design factors, HS had the highest specificity, followed by LASSO and then RMA.
+Also note that the association between design factors and specificity was not monotonously positive or negative across algorithms.
+Instead, some design factors had opposite effects for the two BRMA algorithms versus RMA.
+For instance, a larger number of studies $k$ had a negative effect on specificity for the BRMA algorithms, but a positive effect for RMA - within the context that RMA had lower specificity on average.
+Conversely, a greater number of noise moderators $M$ had a positive effect on specificity for BRMA, but a negative effect for RMA.
+
+## Ability to recover population parameters
+
+The ability to recover population parameters $\beta$ and $\tau^2$ was examined in terms of bias and variance of these estimates.
+If the value of the regression coefficient as estimated by one of the algorithms is $\hat{b}$,
+then the bias $B$ and variance $V$ of this estimate can be computed as the mean and variance of the difference between $\hat{b}$ and $\beta$ across simulation conditions, respectively.
+
+Across all simulation conditions, HS had the lowest bias for $\tau^2$, $B_{HS} `r report(out[["tau2_bias"]][["hs_tau2"]])`$, 
+followed by RMA, $B_{RMA} `r report(out[["tau2_bias"]][["rma_tau2"]])`$,
+and then LASSO, $B_{LASSO} `r report(out[["tau2_bias"]][["lasso_tau2"]])`$.
+Note that all algorithms yielded positively biased estimates. 
+The LASSO estimates of $\tau^2$ had the lowest variance, $V_{LASSO} `r report(out[["tau2_variance"]][["lasso_tau2"]])`$, 
+followed by HS, $V_{HS} `r report(out[["tau2_variance"]][["hs_tau2"]])`$,
+and then RMA, $B_{RMA} `r report(out[["tau2_variance"]][["rma_tau2"]])`$.
+
+The effect of the design factors on the bias in $\tau^2$ was evaluated using ANOVAs.
+Table \@ref(tab:tabtau2) reports the effect size $\eta^{2}$ of simulation conditions on $\hat{t^2}-\tau^2$.
+The design factors $\beta$ and model had the largest effect on bias in estimated $\tau^{2}$ for all algorithms.
+No differences between algorithms in the effect of design factors were observed.
+
+```{r tabtau2, results= "asis", eval = TRUE}
+tabtau <- readRDS("table_tau2.RData")
+tabtau$Factor <- gsub("\\$(omega|beta|tau)", "\\$\\\\\\1", tabtau$Factor)
+tabtau <- tabtau[, c(ncol(tabtau), 2:(ncol(tabtau)-1))]
+apa_table(tabtau, caption = "Effect size of design factors on bias in tau squared for the different algorithms, and of the difference between algorithms.", digits = 2, escape = FALSE, col.names = gsub("(?<!vs)\\.", " ", names(tabtau), perl = TRUE))
+```
+
+For the estimated regression coefficient, HS had the greatest (negative) bias across simulation conditions, $B_{HS} `r report(out[["beta_bias"]][["hs_beta1"]])`$, 
+followed by LASSO, $B_{LASSO} `r report(out[["beta_bias"]][["lasso_beta1"]])`$,
+and then RMA, $B_{RMA} `r report(out[["beta_bias"]][["rma_beta1"]])`$.
+Note that all algorithms - including RMA - provided, on average, negatively biased estimates. 
+Across simulation conditions, HS had the lowest variance, $V_{HS} `r report(out[["beta_variance"]][["hs_beta1"]])`$, 
+followed by LASSO, $B_{LASSO} `r report(out[["beta_variance"]][["lasso_beta1"]])`$,
+and then RMA, $B_{RMA} `r report(out[["beta_variance"]][["rma_beta1"]])`$.
+
+The effect of the design factors on the bias in estimated $\beta$ was evaluated using ANOVAs.
+Table \@ref(tab:tabbeta) reports the effect size $\eta^{2}$ of simulation conditions on $\hat{b}-\beta$.
+The skewness of moderator variables had the largest effect on bias in estimated $\beta$ for all algorithms.
+Note, however, that this is likely due to the fact that the data simulated with a cubic model are analyzed with a linear model, and thus,  
+was the estimated model. This was mainly because the algorithms overestimated $\tau^{2}$ most when the model contained cubic terms.
+No differences between algorithms in the effect of design factors were observed.
+
+```{r tabbeta, results= "asis", eval = TRUE}
+tabbeta <- readRDS("table_beta.RData")
+tabbeta$Factor <- gsub("\\$(omega|beta|beta)", "\\$\\\\\\1", tabbeta$Factor)
+tabbeta <- tabbeta[, c(ncol(tabbeta), 2:(ncol(tabbeta)-1))]
+apa_table(tabbeta, caption = "Effect size of design factors on bias in beta squared for the different algorithms, and of the difference between algorithms.", digits = 2, escape = FALSE, col.names = gsub("(?<!vs)\\.", " ", names(tabbeta), perl = TRUE))
+```
+
+# Discussion
+
+This simulation study validated the performance of two versions of the new BRMA algorithm, relative to state-of-the-art meta-regression (RMA).
+Our analyses examined the algorithms' predictive performance, which is a measure of generalizability,
+their ability to perform variable selection,
+and their ability to recover population parameters.
+Our research questions were whether BRMA offers a performance advantage over RMA in terms of any of these indicators;
+under what conditions BRMA does not offer an advantage,
+and which prior (horseshoe versus LASSO) is to be preferred.
+
+Results indicated that the BRMA algorithms had higher predictive performance than RMA in the presence of relevant moderators.
+In the absence of relevant moderators, RMA produced overfit models; in other words, its models generalized poorly to new data.
+The predictive performance of the BRMA algorithms also suffered less than that of RMA in the presence of more irrelevant moderators.
+The BRMA algorithms were also more efficient, in the sense that they achieved greater predictive performance when the number of studies in the training data was low.
+Across all conditions, BRMA with a horseshoe prior achieved the highest average predictive performance, and within each data set, BRMA with a horseshoe prior most often had the best predictive performance (in `r round(whichhi[1]*100)`% of replications).
+This provides strong evidence that BRMA with a horseshoe prior is generally preferable when the goal is to obtain findings that generalize to new data.
+
+With regard to variable selection, results indicated that the penalized BRMA algorithms had lower sensitivity: they were less able to select relevant moderators than the un-penalized RMA algorithm.
+Conversely, the BRMA algorithms had better specificity: they were better able to reject irrelevant moderators than RMA.
+These results are unsurprising because the BRMA algorithms shrink all regression coefficients towards zero.
+This diminishes their ability to detect true effects and aids their ability to reject irrelevant moderators.
+Importantly, the overall accuracy was approximately equal for RMA and BRMA with a horseshoe prior.
+This means that the total number of Type I and Type II errors will be approximately the same when choosing between these two methods - but there is a tradeoff between sensitivity and specificity.
+Applied researchers must consider whether sensitivity or specificity is more important in the context of their research.
+When meta-analyzing a heterogeneous body of literature, with many between-study differences that could be coded as moderators, BRMA may be preferred due to its greater ability to retain only relevant moderators.
+Conversely, when meta-analyzing a highly curated body of literature with a small number of theoretically relevant moderators, un-penalized RMA might be preferred.
+
+With regard to the algorithms' ability to recover population effect sizes of moderators,
+we observed that BRMA with a horseshoe prior had the greatest bias towards zero across simulation conditions, followed by LASSO, and then RMA.
+Note that all algorithms provided, on average, negatively biased estimated.
+The variance of the estimates followed the opposite pattern.
+This unsurprising result illustrates the bias-variance trade-off in penalized regression.
+The greater predictive performance of the BRMA algorithms is a direct consequence off this trade-off.
+
+We further observed that BRMA with a horseshoe prior had the lowest bias when estimating residual heterogeneity.
+The BRMA algorithms also had lower variance than RMA when estimating residual heterogeneity.
+This suggests that the penalized regression coefficients do not compromise the estimation of residual heterogeneity.
+Future research might investigate under what conditions residual heterogeneity is estimated more accurately in a penalized model than in an un-penalized model.
+Together, these results suggest that BRMA has superior predictive performance and specificity, and provides relatively unbiased estimates of residual heterogeneity, relative to RMA.
+
+# Strengths and future directions
+
+The present paper has several strengths.
+First, we included a wide range of simulation conditions, including conditions that violated the assumptions of linearity and normality.
+Across all conditions, BRMA displayed superior predictive performance and specificity compared to RMA.
+Another strength is that the present simulation study used realistic estimates of $\tau^2$,
+based on data from 705 published psychological meta-analyses (Van Erp et al., 2017).
+Another strength is that we made the BRMA algorithms available in a FAIR (Findable, Accessible, Interoperable and Reusable) format by publishing an R package on the "Comprehensive R Archive Network".
+Thanks to the use of compiled code, the BRMA algorithm is computationally relatively inexpensive.
+
+Several limitations remain to be addressed in future research, however.
+One limitation is that, by necessity, computational resources and journal space limit the number of conditions that could be considered in the simulation study.
+To facilitate further exploration and follow-up research,
+we have made all simulation data and analysis code for the present study available online.
+This code also enables researchers to conduct Monte Carlo power analyses for applied research.
+Another limitation is that the present study did not examine the effect of multicolinear predictors.
+Regularizing estimators typically have an advantage over OLS regression in the presence of multicolinearity;
+future research ought to examine whether this also applies to BRMA.
+
+A final limitation is that the present study did not examine the effect of dependent data (e.g., multiple effect sizes per study).
+In principle, the BRMA algorithm can accommodate dependent data by means of three-level multilevel analysis.
+To our knowledge, there are no theoretical reasons to expect that dependent data would result in a different pattern of findings than we found for independent data, but future research is required to ascertain this.
+
+Another direction for future research is the specification of different priors, aside from the horseshoe and LASSO priors that were examined in this study.
+To facilitate such research, we provide a generalized BRMA function which is not compiled, and can be fully customized with user-specified priors.
+The downside of this flexible function is that it is not compiled, and requires the user to set up a compilation toolchain.
+Compiling the function thus requires some technological sophistication and is more computationally costly.
+
+Alghough the use of Bayesian estimation has several advantages, one major downside is that Bayesian models are not directly comparable with frequentist models.
+Another disadvantage is that Bayesian estimation is typically more computationally expensive than frequentist estimation.
+One future direction of research is thus to develop a frequentist estimator for regularized meta-regression.
+
+## Recommendations for applied research
+
+BRMA aims to address the challenge that arises when meta-analysing heterogeneous bodies of literature, with few studies relative to the number of moderators.
+BRMA can be used to identify relevant moderators when it is not known beforehand which moderators are responsible for between-studies differences in observed effect sizes.
+To facilitate adoption of this method in applied research, we have published the function `brma()` in the R package `pema`.
+Here, we offer several recommendations for its use.
+The first recommendation precedes analysis, and relates to
+the design of the meta-analysis.
+When the search for moderators is exploratory,
+researchers ought to be inclusive, but focus on moderators that are expected to be
+relevant, including theoretically relevant moderators, as well as moderators pertaining
+to the sample, methods, instruments, study quality, and publication type.
+In our experience, many applied researchers code such study characteristics anyway, but omit
+them from their analyses for lack of statistical power.
+Moderators can be continuous or categorical, in which case they should be dummy-coded.
+Missing data must be accounted for.
+The best way to do so is by retrieving the missing information, by contacting authors or comparing different publications on the same data.
+If missing data remains, users can either use a single imputation method (for example, a non-parametric imputation method like missForest),
+or manually aggregate the results across multiple imputations.
+The effect sizes and their variances must be computed using suitable methods;
+note that many such methods are available in the R package `metafor` (Viechtbauer et al.,, 2010).
+With regard to data analysis, we recommend the use of a horseshoe prior by default,
+because it demonstrated the best predictive performance and most attractive trade-off between sensitivity and specificity in our simulations.
+
+When reporting results, researchers should substantiate their decision to explore heterogeneity on both subjective and objective grounds.
+The former can be achieved by simply ascertaining that the body of literature
+to be meta-analyzed appears to be heterogeneous;
+the same rationale commonly used to support the use of random-effects meta-analysis (Higgins et al., 2009).
+The latter can be accomplished by conducting a random-effects meta-analysis without any moderators,
+and reporting the estimated $\tau^2$.
+Note that significant heterogeneity does not constitute
+sufficient grounds, for deciding to explore ignore heterogeneity, for two reasons:
+Firstly, because data-driven decisions render any analysis (partly) exploratory, and increase the risk of results that generalize poorly (i.e., are overfit).
+The second reason is that tests for heterogeneity are often underpowered when the number of studies is low, and overpowered when it is high, thus limiting their usefulness (see Higgins & Thompson, 2002).
+As when conducting RMA meta-analysis, researchers should report both the estimated effect of moderators and residual heterogeneity.
+Regression coefficients can be interpreted as usual, but it is recommended that researchers acknowledge that they are biased towards zero.
+If all moderators are centered, the model intercept can be interpreted as the overall effect size at average levels of the moderators.
+Note that, as BRMA is a Bayesian method, credible intervals or highest posterior density intervals should be used for inference, instead of p-values.
+The null hypothesis is rejected if such intervals exclude zero.
+As both types of intervals performed identically in the present study,
+we suggest using credible intervals, which are computationally less expensive.
+**SARA: Wel of niet nog OLS RMA doen met enkel de significante predictoren van de BRMA?**
+
+Finally, with regards to publication, we highly recommend sharing the data and
+syntax for the meta-analysis publicly; for example, by making the entire paper reproducible using the Workflow for Reproducible Code in Science (WORCS; REF).
+Transparency allows readers and reviewers to verify that methods were correctly applied, and try alternative analyses.
+Particularly when using a new method like BRMA, this transparency is likely to inspire confidence in the results.
+Secondly, the results of a meta-analysis can be used to obtain predictions for the expected effect size of a new study on the same topic, given specific design characteristics.
+This prediction can be used to conduct power analysis for future research.
+To this end, researchers can simply enter their planned
+design (or several alternative designs) as new lines of data, using the codebook of the
+original meta-analysis, and use the published BRMA model to calculate the
+predicted effect size for a study with these specifications.
+
+# Conclusion
+
+The present research has demonstrated that BRMA is a powerful tool for
+exploring heterogeneity in meta-analysis, with a number of advantages over classic RMA.
+BRMA had better predictive performance than RMA, which indicates that results from BRMA analysis generalize better to new data.
+This predictive performance advantage was especially pronounced when training data were as small as 20 studies, suggesting that BRMA is suitable as a small sample solution.
+This is an appealing quality, because many meta-analyses have small sample sizes.
+BRMA further has greater specificity in rejecting irrelevant moderators from a larger set of potential candidates, while keeping overall variable selection accuracy approximately constant to RMA.
+Although the estimated regression coefficients are biased towards zero by design,
+the estimated residual heterogeneity did not show evidence of bias in our simulation.
+A final advantage of BRMA over other variable selection methods for meta-analysis is that it is an extension of the linear model.
+Most applied researchers are familiar with the linear model, and it can easily accommodate predictor variables of any measurement level, interaction terms, and non-linear effects.
+Adoption of this new method may be further facilitated by the availability of the user-friendly R package `pema`.
+
+<!-- indicated that the BRMA algorithms had higher predictive performance than RMA in the presence of relevant moderators. -->
+<!-- In the absence of relevant moderators, RMA produced overfit models; in other words, its models generalized poorly to new data. -->
+<!-- The predictive performance of the BRMA algorithms also suffered less than that of RMA in the presence of more irrelevant moderators. -->
+<!-- The BRMA algorithms were also more efficient, in the sense that they achieved greater predictive performance when the number of studies in the training data was low. -->
+<!-- Across all conditions, BRMA with a horseshoe prior achieved the highest average predictive performance, and within each data set, BRMA with a horseshoe prior most often had the best predictive performance (in `r round(whichhi[1]*100)`% of replications).
+-->
+<!-- This provides strong evidence that BRMA with a horseshoe prior is generally preferable when the goal is to obtain findings that generalize to new data. -->
+
+<!-- 6.
 First note the general trend that during estimation of all models $\tau^{2}$ got more overestimated as $\beta$ increased, except during estimation of the linear model, where the effect of $\beta$ on $\Delta\tau^{2}$ was close to zero, except for MetaForest.
@@
 Interestingly, the Pema algorithms even outperformed the RMA algorithm in these conditions.
+-->
 
-The marginal effects of $\beta$ on $\Delta\tau^{2}$ are shown in image 5B.
+<!-- The marginal effects of $\beta$ on $\Delta\tau^{2}$ are shown in image 5B.
 MetaForest was affected most by the increase in $\beta$, but in general performed better than the Pema algorithms when $\beta < 0.8$.
 The RMA algorithm performed best overall.
+-->
 
-The marginal effect of $\alpha$ on $\Delta\tau^{2}$ was rather minimal, although there was a slight decrease in $\Delta\tau^{2}$ as $\alpha$ increased.
+<!-- The marginal effect of $\alpha$ on $\Delta\tau^{2}$ was rather minimal, although there was a slight decrease in $\Delta\tau^{2}$ as $\alpha$ increased.
 However, the decrease is more explicit when the interaction of $\alpha$ with the estimated model is added.
@@
 The Pema algorithms performed similarly, but worst.
+-->
 
-The effect of the true $\tau^{2}$ on $\Delta\tau^{2}$ was rather unnoticeable for the RMA and MetaForest algorithms.
+<!-- The effect of the true $\tau^{2}$ on $\Delta\tau^{2}$ was rather unnoticeable for the RMA and MetaForest algorithms.
 The tendency for the Pema algorithms on the other hand, was to overestimate $\tau^{2}$ more as the true $\tau^{2}$ increased.
 Image 5C shows the marginal relationship.
+-->
 
-The effect of the number of moderators on $\Delta\tau^{2}$  was not that large either.
+<!-- The effect of the number of moderators on $\Delta\tau^{2}$  was not that large either.
 A small increase in $\Delta\tau^{2}$ can be seen in the RMA and MetaForest algorithm as the number of moderators increased which was not found for the Pema algorithms.
@@
 Image 8 shows the interaction between the number of moderators and the estimated model.
+-->
 
-$\kappa$ only had a substantial effect for MetaForest; the $\Delta\tau^{2}$  decreased quite rapidly if $\kappa$ increased, especially when the cubic model was estimated.
+<!-- $\kappa$ only had a substantial effect for MetaForest; the $\Delta\tau^{2}$  decreased quite rapidly if $\kappa$ increased, especially when the cubic model was estimated.
 For the other algorithms, decreasing $\kappa$ had little to no effect on correctly estimating the residual heterogeneity.
 Image 9 shows the interaction of $\kappa$ with the estimated model.
+-->
 
-Finally, the average number of observations in the studies did not have a substantial effect on $\Delta\tau^{2}$. Image 5D shows the marginal relationship.
-
-## Variable selection
-To determine the extent to which the algorithms could perform variable selection correctly, the proportion true positives [$TP$] and true negatives [$TN$] were calculated.
-The $TP$ and $TN$ reflect how well the algorithms accredit importance to relevant moderators and discredit importance to irrelevant moderators respectively.
-It should be noted that $TP$ could only take on values 1 or 0 per simulated iteration, because in all models where $\beta > 0$, only one moderator was simulated to be relevant.
-As $\beta$ increased, the already relevant moderator increased in relevance, rather than spreading the relevance over the other moderators.
-$TN$ had a bigger range and could take on values dependent on how many moderators were taken up in the model.
-E.g.
-when $\beta = 0$ and $n_{mods} = n$, $n+1$ different proportions were possible, $\frac{0}{n}$ up until $\frac{n}{n}$.
-
-There were no differences in variables selected by Highest Density Intervals or Confidence Intervals for both Lasso and Horshoe and so for both algorithms it did not matter which interval type was analyzed.
-It was found that MetaForest had the highest proportion true positives: $TP_{Mf} = 0.98$, closely followed by RMA: $TP_{RMA} = 0.96$.
-Horshoe performed slightly better than Lasso;  $TP_{Hs} = 0.91$; $TP_{Lasso} = 0.89$.
-As for $TN$, it was found that the pema algorithms performed best: $TN_{Hs} \ \text{and} \ TN_{Lasso} = 0.93$, followed by RMA: $TN_{RMA} = 0.89$.
-MetaForest performed worst by a large margin: $TN_{Mf} = 0.50$.
-The Mean Absolute Deviation for all algorithms on both $TP$ and $TN$ was 0, except for MetaForests performance on $TN$, where the Mean Absolute Deviation was 0.44.
-
-Perfomance on $TP$ and $TN$ were very high for all algorithms, with all mean proportions, except MetaForests performance on $TN$, exceeding .89.
-This implies that MetaForest had issues excluding irrelevant moderators from the models.
-Plots were inspected to determine the effects of the design factors on the proportions.
-While inspecting the plots, there were found to be little marginal effects of the design factors on $TN$, while $TP$ was more affected.
-
-Firstly, $\kappa$ only had a positive effect on $TP$.
-As $\kappa$ increased, $TP$ also increased.
-MetaForest had the highest $TP$, followed by RMA and, lastly, Horsehoe and Lasso.
-The increase in $TP$ for higher values of $\kappa$ was steeper for the Pema algorithms, however.
-There was also an interaction of $\kappa$ with the estimated model shown in image 10.
-During estimation of the linear and two-way interaction model, the relationship of $\kappa$ looked relatively linear.
-At $\kappa = 20$ the $TP$ was relatively low for the algorithms, compared to the cubic model where $TP$ starts at .98 and converges to 1 as $\kappa$ increased.
-This latter relationship was also found for the exponential model, although the $TP$ at $\kappa = 20$ was lower.
-
-$\bar{n}$ had a positive and roughly linear relationship with $TP$ for all algorithms.
-MetaForest performed best, followed by RMA, while Horseshoe and Lasso performed worst.
-Image 11A shows the relationship.
-
-$\beta$ had an interaction effect with the model estimated on $TN$.
-Only during estimation of the two-way interaction model, $TN$ decreased as $\beta$ increased, For the other models, $TN$ remained stable.
-This could be because the interaction model was only fitted when there were 3,4 or 7 moderators, while for the other models, only 2,3 or 6 moderators were used.
-Image 12 shows the relationship.
-The effect of $\beta$ on $TP$ was positive; as $\beta$ increased, $TP$ increased too.
-
-The true $\tau^2$ had a negative effect on $TP$, while $\alpha$ seemed to have little effect on both $TP$ and $TN$. Image 11B shows the marginal relationship of $\tau^2$ on $TP$.
-
-Finally, there was an effect of number of moderators on $TN$, but only for the two-way interaction model.
-The $TN$ increased as the number of moderators did.
-Image 13 shows the interaction.
-This relationship was reversed for $TP$ and was found during estimation of all models, i.e.
-$TP$ decreased as the number of moderators increased.
-Image 14 shows the relationship.
-
-# Discussion
+<!-- Finally, the average number of observations in the studies did not have a substantial effect on $\Delta\tau^{2}$. Image 5D shows the marginal relationship. -->
 

### 2021-12-08 simulatie_2021/Analysis Sim2021_3.R

@@ -3,51 +3,40 @@
 ####################
 library(latex2exp)
 library(cowplot)
+library(data.table)
+library(ggplot2)
+library(tidySEM)
+library(rcompanion)
+# load in needed functions
+source('./simulatie_2021/Analysis_functions.R') #created functions used for analysis
+
 out <- list()
-dependencies <- c('data.table', 'tidyverse', 'stringr', 'ggplot2')
-lapply(dependencies, function(x) library(x, character.only = T))
+
 dat <- as.data.table(readRDS("simulatie_2021/results/sim_results_2021-09-08.RData"))
 dat <- dat[dat$model %in% c("es * x[, 1]", "es * x[, 1] + es * (x[, 1] ^ 2) + es * (x[, 1] ^ 3)"),]
 dat[, grep("^mf", names(dat)) := NULL]
 
-# load in needed functions
-source('./simulatie_2021/Analysis_functions.R') #created functions used for analysis
 
 #some data preprocessing
 newnames <- c('hs', 'lasso', 'rma') #names of algorithms
 conditions <- c("k_train", "mean_n", "es", "tau2","alpha_mod", "moderators", "model") #conditions that vary
 lc <- length(conditions) #length of conditions, handy for further code
-dat[, (conditions):=lapply(.SD, factor), .SDcols=conditions] #convert to factor
+dat[, (conditions):=lapply(.SD, ordered), .SDcols=conditions] #convert to factor
 levels(dat$model) <- c('linear', 'cubic') #rename to more understandable levels
 
 #there are duplicated columns which contain the same values, we can omit those
-last <- function(x) { return( x[length(x)] ) } #function to obtain last element from vector
 unique_cols <- which(!duplicated(colnames(dat)))
-dat <- dat[ , unique_cols[1]:last(unique_cols)]
+dat <- dat[ , unique_cols[1]:tail(unique_cols, 1)]
 
-#Checking for missing values
-#first we omit the columns that should contain missing values which are the 'sel' columns
-lashs <- colnames(dat)[grep(pattern = "_(ci|hdi)_sel_\\d", colnames(dat))]
-mfrma <- colnames(dat)[grep(pattern = "(mf|rma)_sel_\\d", colnames(dat))]
-
-#create df without sel columns and subset it for rows that contain more than 1 missing
[…]

### 2021-12-08 simulatie_2021/Analysis_functions.R

@@ -1,3 +1,29 @@
+renamefactors <- function(x){
+  out <- gsub("moderators", "M", x, fixed = T) #this changes 'moderators' to M
+  out <- gsub("tau2", "$\\tau^2$", out, fixed = T) #nothing
+  out <-gsub("es", "$\\beta$", out, fixed = T) #changes 'es'to '$beta$ but I do not know why
+  out<-gsub("mean_n", "$n$", out, fixed = T) #nothing
+  out<-gsub("model", "Model ", out, fixed = T) #capitalizes 'model'
+  out<-gsub("k_train", "$k$ ", out, fixed = T)
+  out<-gsub("alpha_mod", "$\\omega$ ", out, fixed = T)
+  out
+}
+
+interpret <- function(x){
+  thelng <- (length(x)-1)
+  if(is.na(x[1])) return(NA)
+  x <- sum(sign(diff(x)))
+  if(x == thelng){
+    return("positive")
+  }
+  if(-1*x == thelng){
+    return("negative")
+  }
+  return("other")
+}
+
+
+
 #creates traceplots for metrics
 Traceplot <- function(test, train, param, alg){
   plot(x = 1:length(test), y = test, type = 'n', main = paste('Traceplot Test and Train', param , ' for', alg), xlab = 'iterations', ylab = paste('values for ', param)) #empty plot with correct dimensions for the traced values
@@ -100,6 +126,8 @@ plot_marginal_median <- function(condition, df, lonames, metric, pointsize = 5, 
     geom_point(size = pointsize) +
     theme_bw(base_size = 25)
 }
+
+
 
 
 plot_interaction_median <- function(condition, intcond, df, lonames, metric){

### 2021-12-08 R/as_stan.R
start work on methods

@@ -1,0 +1,33 @@
+#' Convert an object to stanfit
+#'
+#' Create a `stanfit` object from an object for which a method exists,
+#' so that all methods for `stanfit` objects can be used.
+#' @param x An object for which a method exists.
+#' @param ... Arguments passed to or from other methods.
+#' @return An object of class `stanfit`.
+#' @export
+#' @examples
+#' stanfit <- "a"
+#' class(stanfit) <- "stanfit"
+#' brmaobject <- list(fit = stanfit)
+#' class(brmaobject) <- "brma"
+#' converted <- as.stan(brmaobject)
+#' @importFrom stats rbinom rnorm rt
+#' @importFrom sn rsn
+as.stan <- function(x, ...){
+  UseMethod("as.stan", x)
+}
+
+#' @method as.stan brma
+#' @export
+as.stan.brma <- function(x, ...){
+  if(is.null(x[["fit"]])) stop("Could not coerce object to class 'stanfit'.")
+  if(!inherits(x[["fit"]], "stanfit")) stop("Could not coerce object to class 'stanfit'.")
+  out <- x[["fit"]]
+  as_atts <- names(x)[!names(x) %in% c("fit")]
+  for(thisatt in as_atts){
+    attr(out, which = thisatt) <- x[[thisatt]]
+  }
+  attr(out, which = "type") <- "brma"
+  return(out)
+}

### 2021-12-08 R/brma.R

@@ -169,6 +169,8 @@ brma <-
                 Y = Y)
     if(!is.null(vi_column)) fit$vi_column <- vi_column
     if(!is.null(study_column)) fit$study_column <- study_column
+    if(!is.null(vi)) fit$vi <- vi
+    if(!is.null(study)) fit$study <- study
     class(fit) <- c("brma", class(fit))
     return(fit)
   }

### 2021-12-08 R/methods.R

@@ -1,6 +1,115 @@
-#' @S3method print brma
-print.brma <- function(x, ...){
-  cl <- match.call()
-  cl[["x"]] <- x[["model"]]
-  eval.parent(cl)
+#' @importFrom utils getFromNamespace
+# .invcalc <- getFromNamespace(".invcalc", "metafor")
+# .tr  <- getFromNamespace(".tr", "metafor")
+#' @method summary brma
+#' @export
+summary.brma <- function(object, ...){
+  sums <- summary(object$fit)$summary
+  keepthese <- c(which(rownames(sums) == "Intercept"),
+                 which(startsWith(rownames(sums), "b[")),
+                 which(rownames(sums) == "sd_1[1]"))
+  sums <- sums[keepthese, , drop = FALSE]
+
+
+  sdpar <- match("sd_1[1]", sim$fnames_oi)
+  sim <- object$fit@sim
+  tau2 <- .extract_samples(sim, sdpar)^2
+  addrow <- sums["sd_1[1]",]
+  addrow[c("mean", "sd", "2.5%", "25%", "50%", "75%", "97.5%")] <-
+    c(mean(tau2), sd(tau2), quantile(tau2, c(.025, .25, .5, .75,.975)))
+  addrow["se_mean"] <- addrow["sd"]/sqrt(addrow[["n_eff"]])
+  tau <- unlist(lapply(object$fit@sim$samples, `[[`, "sd_1[1]"))
+  sums <- rbind(sums, tau2 = addrow)
+  rownames(sums)[2:(ncol(object$X))] <- colnames(object$X)[-1]
+  rownames(sums)[rownames(sums) == "sd_1[1]"] <- "tau"
+  tau2 <- unname(addrow["mean"])
+  rma_res <- rma(yi = object$Y, vi = object$vi)
+  Wi <- 1 / vi
+  yi <- object$Y
+  k <- length(object$Y)
+  tau2_before <-
+    max(0, (sum(Wi * (yi - (
+      sum(Wi * yi) / sum(Wi)
+    )) ^ 2) - (k - 1)) / (sum(Wi) - (sum(Wi ^ 2) / sum(Wi))))
+
+  R2 <- max(0, 100 * (tau2_before-tau2)/tau2_before)
+  I2 <- 100 * tau2/(vt + tau2)
+  H2 <- tau2/vt + 1
+  out <- list(
+    coefficients = sums,
+    tau2 = tau2,
+    I2 = I2,
[…]

### 2021-12-08 paper/regsem.R

@@ -1,0 +1,36 @@
+library(metafor)
+library(metaSEM)
+
+::meta()
+
+### calculate log risk ratios and corresponding sampling variances
+dat <- escalc(measure="RR", ai=tpos, bi=tneg, ci=cpos, di=cneg, data=dat.bcg)
+
+### fit a random-effects model using the log risk ratios and variances as input
+### note: method="REML" is the default, so one could leave this out
+rma(yi, vi, data=dat, method="REML")
+
+tmp <- meta(y = dat[, "yi", drop = FALSE], v = dat[, "vi", drop = FALSE])
+summary(mxRun(tmp$mx.model))
+tmp$mx.model$Inter$values
+
+X <- model.matrix(~. , dat[c("year", "alloc")])[, -1]
+
+tmp <- meta(y = dat[, "yi", drop = FALSE], v = dat[, "vi", drop = FALSE], x = X, run= TRUE)
+summary(mxTryHard(mxRun(tmp$mx.model)))
+tmp$mx.model$Inter$values
+
+tmp$
+
+summary(tmp)
+
+# install.packages("devtools")
+devtools::install_github("trbrick/mxregsem")
+
+install.packages("regsem")
+library(regsem)
+library(mxregsem)
+?mxRegularizeLASSO
+mxregsem::mxRegularizeLASSO()
+tmp <- OpenMx::mxModel(tmp$mx.model, mxregsem::mxRegularizeLASSO(what = paste0("Slope1_", 1:3), name = NULL))
+fit1 <- regsem(tmp$mx.model, lambda=0.05, type="lasso")

### 2021-12-08 tests/testthat/pema_confint.R

@@ -1,0 +1,16 @@
+df <- simulate_smd(k_train = 500)$training
+fit <- brma(yi~., data = df, iter = 100, seed = 30)
+
+CI95 <- summary(fit$fit)$summary
+CI95 <- CI95[paste0("betas[", 1:(ncol(fit$X)-1), "]"), c("2.5%", "97.5%")]
+selected <- apply(CI95, 1, function(x){ !(sum(sign(x)) == 0)})
+
+test_that("ci selects relevant vars", {
+  expect_true(selected[1])
+  expect_true(all(!selected[-1]))
+})
+#hpdi <- bayestestR::hdi(fit$fit, parameters = "betas")
+#hpdi <- cbind(hpdi$CI_low, hpdi$CI_high)
+#selected <- apply(CI95, 1, function(x){ !(sum(sign(x)) == 0)})
+fitrma <- rma(df$yi, df$vi)
+res <- rma(object$Y, object$vi, mods = object$X[, -1])

### 2021-12-08 tests/testthat/pema_runs.R

@@ -1,0 +1,16 @@
+library(metafor)
+df <- dat.baskerville2012
+df$vi <- df$se^2
+df[["se"]] <- NULL
+df$yi <- df$smd
+df[["smd"]] <- NULL
+mods <- c("year", "score", "fumonths", "retention", "outcomes", "duration", "meetings", "hours")
+df <- df[c("yi", "vi", mods)]
+df <- missRanger::missRanger(df)
+
+res <- tryCatch({
+  pema::brma(yi ~. , df)
+  }, error = function(e){NULL})
+test_that("pema runs", {
+  expect_true(!is.null(res))
+})

### 2021-12-10 README.Rmd
update 2021-12-10 17:54:22

@@
 
-You can cite pema using the following citation (please use the same citation for either the package, or the paper):
+The `pema` validation paper is currently in preprint stage.
+The code and results of the validation study are publicly available.
+You can cite `pema` using the following citation (please use the same citation for either the package, or the paper); consider updating that citation once the preprint is published:
 
-> Caspar J van Lissa and Sara J van Erp (2021). pema: Penalized Meta-Analysis. R package version
-0.1.0.9000. https://github.com/cjvanlissa/pema
+> Van Lissa, C. J., & van Erp, S. (2021, December 9). Select relevant moderators using Bayesian regularized meta-regression. Retrieved from psyarxiv.com/6phs5
 

### 2021-12-10 paper/manuscript.Rmd
update 2021-12-10 17:54:22

@@
 ---
-title             : "Select relevant moderators in meta-regression using Bayesian penalization"
-shorttitle        : "BAYESIAN REGULARIZED META-ANALYSIS"
+title             : "Select relevant moderators using Bayesian regularized meta-regression"
+shorttitle        : "BAYESIAN REGULARIZED META-REGRESSION"
 
@@
 abstract: |
-  Todo
+  When analyzing a heterogeneous body of literature, there may be many
+  potentially relevant between-studies differences. These differences can be
+  coded as moderators, and accounted for using meta-regression. However, many
+  applied meta-analyses lack the power to adequately account for multiple
+  moderators, as the number of studies on any given topic is often low. The
+  present study introduces Bayesian Regularized Meta-Analysis (BRMA), an
+  exploratory algorithm that can select relevant moderators from a larger number
+  of candidates. This approach is suitable when heterogeneity is suspected, but
+  it is not known which moderators most strongly inﬂuence the observed effect
+  size. We present a simulation study to validate the performance of BRMA
+  relative to state-of-the-art meta-regression (RMA). Results indicated that
+  BRMA compared favorably to RMA on three metrics: predictive performance,
+  which is a measure of the generalizability of results, the ability to reject
+  irrelevant moderators, and the ability to recover population parameters with
+  low bias. BRMA had slightly lower ability to detect true effects of relevant
+  moderators, but the overall proportion of Type I and Type II errors was
+  equivalent to RMA. Furthermore, BRMA regression coefficients were slightly
+  biased towards zero (by design), but its estimates of residual heterogeneity
+  were unbiased. BRMA performed well with as few as 20 studies in the training
+  data, suggesting its suitability as a small sample solution. We discuss how
+  applied researchers can use BRMA to explorate between-studies heterogeneity
+  in meta-analysis.
 

### 2021-12-10 R/brma.R

@@ -30,6 +30,7 @@
 #  the model statement. Defaults to .5.
 # @param chains A positive integer specifying the number of Markov chains.
 # Defaults to 4.
+#' @param mute_stan Logical, indicating whether mute all 'Stan' output or not.
 #' @param ... Additional arguments passed on to [rstan::sampling()].
 #' Use this, e.g., to override default arguments of that function.
 #' @details Penalization of the regression coefficients occurs either via the
@@ -97,7 +98,14 @@
 #' doi:10.1214/17-ejs1337si
 #' @export
 #' @examples
-#' print("Make me")
+#' data("fukkink_lont")
+#' df <- fukkink_lont[c(1:5, 40:45), c("yi", "vi", "Integrated", "Trainee_Age")]
+#' suppressWarnings({res <- brma(yi~., data = df, iter = 10)})
+#' @importMethodsFrom rstan summary
+#' @importFrom stats model.matrix na.omit quantile sd
+#' @importFrom RcppParallel RcppParallelLibs CxxFlags
+# The line above is just to avoid CRAN warnings that RcppParallel is not
+# imported from, despite RcppParallel being a necessary dependency of rstan.
 brma <-
   function(formula,
            data,
@@ -108,29 +116,36 @@ brma <-
            prior = switch(method,
                           "lasso" = c(df = 1, scale = 1),
                           "hs" = c(df = 1, df_global = 1, df_slab = 4, scale_global = 1, scale_slab = 1, par_ratio = NULL)),
+           mute_stan = TRUE,
            ...) {
+    # Bookkeeping for columns that should not be in X or Y
     vi_column <- NULL
     study_column <- NULL
+    if(inherits(vi, "character")){
+      vi_column <- vi
+      vi <- data[[vi]]
+      data[[vi_column]] <- NULL
+    }
+    if(is.null(study)){
+      study <- 1:nrow(data)
+    } else {
+      if(inherits(study, "character")){
+        study_column <- study
+        study <- data[[study]]
+        data[[study_column]] <- NULL
+      }
+    }
+    # Make model matrix
     mf <- match.call(expand.dots = FALSE)
-    mf <- mf[c(1L, match(c("formula", "data", "subset", "na.action"), names(mf), 0L))]
[…]

### 2021-12-10 R/maxap.R

@@ -1,0 +1,102 @@
+#' @title Maximum a posteriori parameter estimate
+#' @description Find the parameter estimate with the highest posterior
+#' probability density given a vector of samples.
+#' @param x Numeric vector.
+#' @param dens Optional object of class `density`. Defaults to `NULL`.
+#' @param ... Arguments passed to \code{\link[stats]{density}}
+#' @return Atomic numeric vector.
+#' @examples
+#' maxap(c(1,2,3,4,5))
+#' @export
+#' @importFrom stats density
+maxap <- function(x, dens = NULL, ...) {
+  rangex <- range(x)
+  if(is.null(dens)) dens <- density(x, bw = "SJ", from = rangex[1], to = rangex[2], ...)
+  dens$x[which.max(dens$y)]
+}
+
+#
+# highest_alpha <- function(alpha, df, x.min, x.max, ...) {
+#   p <- function(h) {
+#     g <- function(x) {y <- df(x); ifelse(y > h, y, 0)}
+#     integrate(g, x.min, x.max, ...)$value - alpha
+#   }
+#   uniroot(p, c(x.min, x.max), tol=1e-12)$root
+# }
+# as.pdf <- function(x, y, ...) {
+#   f <- approxfun(x, y, method="linear", yleft=0, yright=0, rule=2)
+#   const <- integrate(f, min(x), max(x), ...)$value
+#   approxfun(x, y/const, method="linear", yleft=0, yright=0, rule=2)
+# }
+# highest_alpha(.95, as.pdf(dens$x, dens$y), rangex[1], rangex[2])
+# bayestestR::hdi(x)
+#
+# hpdi <- function(x, ci = 0.95, dens = NULL, ...) {
+#   x <- unname(sort.int(x, method = "quick"))
+#   if(is.null(dens)) dens <- density(x, bw = "SJ", from = rangex[1], to = rangex[2], ...)
+#   pointdens <- approx(dens$x, dens$y, xout = x)
+#   best <- 0
+#   for(lb in 1:(length(x) - 1)){
+#     for (ub in (lb + 1) : length(x)){
+#       mass = sum(diff(x[lb : ub]) * dens$y[dens$x > x[lb] & dens$x <= x[ub]])
+#       if (mass >= ci && mass / (x[ub] - x[lb]) > best){
+#         best = mass / (x[ub] - x[lb])
+#         lb.best = lb
+#         ub.best = ub
+#       }
+#     }
+#   }
+#
+#   c(x[lb.best], x[ub.best])}
+#
+#
+#
[…]

### 2021-12-10 R/methods_predict.R

@@ -1,0 +1,61 @@
+#' @method predict brma
+#' @export
+predict.brma <- function(object, newdata, type = c("mean", "median", "samples"), ...){
+  if (missing(newdata) || is.null(newdata)) {
+    X <- object$X
+  } else {
+    if(isTRUE(all(colnames(object$X) %in% colnames(newdata)))){
+      X <- newdata[, colnames(object$X), drop = FALSE]
+    } else {
+      X <- try({
+        form <- object$formula
+        form[2] <- NULL
+        if(object$vi_column %in% names(newdata)) newdata[[object$vi_column]] <- NULL
+        if(object$study_column %in% names(newdata)) newdata[[object$study_column]] <- NULL
+        # Make model matrix
+        mf <- call("model.frame")
+        #mf <- mf[c(1L, match(c("formula", "subset", "na.action"), names(mf), 0L))]
+        mf[["formula"]] <- form
+        mf[["data"]] <- newdata
+        mf$drop.unused.levels <- FALSE
+        mf <- eval(mf, parent.frame())
+        #X <- mf[, -1, drop = FALSE]
+        #mt <- attr(mf, "terms")
+        mt <- object$terms
+        model.matrix(mt, mf)
+      })
+      if(inherits(X, "try-error")) stop("Could not construct a valid model.frame from argument 'newdata'.")
+    }
+  }
+  switch(type[1],
+         "mean" = .pred_brma_summary(object, X, parcol = "mean"),
+         "median" = .pred_brma_summary(object, X, parcol = "50%"),
+         "samples" = .pred_brma_samples(object, X))
+}
+
+
+
+.pred_brma_samples <- function(object, X, ...){
+  sums <- summary(object$fit)$summary
+  sim <- object$fit@sim
+  keepthese <- c(which(sim$fnames_oi == "sd_1[1]"),
+                 which(sim$fnames_oi == "Intercept"),
+                 grep("^b\\[\\d+\\]$", sim$fnames_oi))
+
+  sums <- sums[keepthese, , drop = FALSE]
+
+  samps <- sapply(keepthese, .extract_samples, sim = sim)
+  preds <- apply(samps[, -1], 1, function(thisrow){ rowSums(X %*% diag(thisrow)) })
+  attr(preds, "tau") <- samps[,1]
+  class(preds) <- c("brma_preds", class(preds))
+  return(preds)
+}
+
+.pred_brma_summary <- function(object, X, parcol, ...){
[…]

### 2021-12-10 R/methods_print_summary.R

@@ -4,47 +4,40 @@
 #' @method summary brma
 #' @export
 summary.brma <- function(object, ...){
-  sums <- summary(object$fit)$summary
-  keepthese <- c(which(rownames(sums) == "Intercept"),
-                 which(startsWith(rownames(sums), "b[")),
-                 which(rownames(sums) == "sd_1[1]"))
-  sums <- sums[keepthese, , drop = FALSE]
-
-
-  sdpar <- match("sd_1[1]", sim$fnames_oi)
-  sim <- object$fit@sim
-  tau2 <- .extract_samples(sim, sdpar)^2
-  addrow <- sums["sd_1[1]",]
-  addrow[c("mean", "sd", "2.5%", "25%", "50%", "75%", "97.5%")] <-
-    c(mean(tau2), sd(tau2), quantile(tau2, c(.025, .25, .5, .75,.975)))
-  addrow["se_mean"] <- addrow["sd"]/sqrt(addrow[["n_eff"]])
-  tau <- unlist(lapply(object$fit@sim$samples, `[[`, "sd_1[1]"))
-  sums <- rbind(sums, tau2 = addrow)
-  rownames(sums)[2:(ncol(object$X))] <- colnames(object$X)[-1]
-  rownames(sums)[rownames(sums) == "sd_1[1]"] <- "tau"
-  tau2 <- unname(addrow["mean"])
-  rma_res <- rma(yi = object$Y, vi = object$vi)
-  Wi <- 1 / vi
-  yi <- object$Y
-  k <- length(object$Y)
-  tau2_before <-
-    max(0, (sum(Wi * (yi - (
-      sum(Wi * yi) / sum(Wi)
-    )) ^ 2) - (k - 1)) / (sum(Wi) - (sum(Wi ^ 2) / sum(Wi))))
-
-  R2 <- max(0, 100 * (tau2_before-tau2)/tau2_before)
-  I2 <- 100 * tau2/(vt + tau2)
-  H2 <- tau2/vt + 1
-  out <- list(
-    coefficients = sums,
-    tau2 = tau2,
-    I2 = I2,
-    H2 = H2,
-    R2 = R2,
-    k = k,
-    method = object$fit@stan_args[[1]]$method,
-    algorithm = object$fit@stan_args[[1]]$algorithm
-  )
+  # sums <- summary(object$fit)$summary
+  # keepthese <- c(which(rownames(sums) == "Intercept"),
+  #                which(startsWith(rownames(sums), "b[")),
[…]

### 2021-12-10 tests/testthat/pema_confint.R

@@ -1,16 +1,0 @@
-df <- simulate_smd(k_train = 500)$training
-fit <- brma(yi~., data = df, iter = 100, seed = 30)
-
-CI95 <- summary(fit$fit)$summary
-CI95 <- CI95[paste0("betas[", 1:(ncol(fit$X)-1), "]"), c("2.5%", "97.5%")]
-selected <- apply(CI95, 1, function(x){ !(sum(sign(x)) == 0)})
-
-test_that("ci selects relevant vars", {
-  expect_true(selected[1])
-  expect_true(all(!selected[-1]))
-})
-#hpdi <- bayestestR::hdi(fit$fit, parameters = "betas")
-#hpdi <- cbind(hpdi$CI_low, hpdi$CI_high)
-#selected <- apply(CI95, 1, function(x){ !(sum(sign(x)) == 0)})
-fitrma <- rma(df$yi, df$vi)
-res <- rma(object$Y, object$vi, mods = object$X[, -1])

### 2021-12-10 tests/testthat/pema_runs.R

@@ -1,16 +1,0 @@
-library(metafor)
-df <- dat.baskerville2012
-df$vi <- df$se^2
-df[["se"]] <- NULL
-df$yi <- df$smd
-df[["smd"]] <- NULL
-mods <- c("year", "score", "fumonths", "retention", "outcomes", "duration", "meetings", "hours")
-df <- df[c("yi", "vi", mods)]
-df <- missRanger::missRanger(df)
-
-res <- tryCatch({
-  pema::brma(yi ~. , df)
-  }, error = function(e){NULL})
-test_that("pema runs", {
-  expect_true(!is.null(res))
-})

### 2021-12-10 R/brma.R
update rstan

@@ -98,9 +98,9 @@
 #' doi:10.1214/17-ejs1337si
 #' @export
 #' @examples
-#' data("fukkink_lont")
-#' df <- fukkink_lont[c(1:5, 40:45), c("yi", "vi", "Integrated", "Trainee_Age")]
-#' suppressWarnings({res <- brma(yi~., data = df, iter = 10)})
+#' data("curry")
+#' df <- curry[c(1:5, 50:55), c("d", "vi", "sex", "age", "donorcode")]
+#' suppressWarnings({res <- brma(d~., data = df, iter = 10)})
 #' @importMethodsFrom rstan summary
 #' @importFrom stats model.matrix na.omit quantile sd
 #' @importFrom RcppParallel RcppParallelLibs CxxFlags

### 2021-12-10 R/curry.R

@@ -26,14 +26,11 @@
 #' @docType data
 #' @keywords datasets
 #' @name curry
-#' @usage data(curry)
+#' @usage data("curry")
 #' @references Curry, O. S., Rowland, L. A., Van Lissa, C. J., Zlotowitz, S.,
 #' McAlaney, J., & Whitehouse, H. (2018). Happy to help? A systematic review and
 #' meta-analysis of the effects of performing acts of kindness on the well-being
 #' of the actor. Journal of Experimental Social Psychology, 76, 320-329.
-#' \href{https://doi.org/10.1016/j.ecresq.2007.04.005}{
-#' doi:10.1016/j.jesp.2018.02.014}
-#' @source \href{https://doi.org/10.1016/j.jesp.2018.02.014}{
-#' doi:10.1016/j.jesp.2018.02.014}
+#' \doi{10.1016/j.ecresq.2007.04.005}
 #' @format A data.frame with 56 rows and 18 columns.
 NULL

### 2021-12-10 R/fukkink_lont.R

@@ -1,50 +1,0 @@
-#' Does training matter? A meta-analysis of caregiver training studies
-#'
-#' A review of 17 experimental studies published between 1980 and 2005 on the
-#' effect of specialized training on the competency of caregivers in childcare.
-#'
-#' \tabular{lll}{
-#'    \strong{id_exp} \tab \code{integer} \tab Unique identifier of the study\cr
-#'    \strong{yi} \tab \code{numeric} \tab Standardized mean difference between the control group and\cr
-#'    \strong{vi} \tab \code{numeric} \tab Variance of the effect size\cr
-#'    \strong{Journal} \tab \code{factor} \tab Publication type (scientific journal or other publications)\cr
-#'    \strong{Setting} \tab \code{factor} \tab Setting (center-based care or family daycare)\cr
-#'    \strong{Integrated} \tab \code{factor} \tab Whether the training was integrated into childcare practice\cr
-#'    \strong{Supervision} \tab \code{factor} \tab Whether supervision was part of the training\cr
-#'    \strong{Scope} \tab \code{factor} \tab Scope of the training (narrow or broad)\cr
-#'    \strong{Location} \tab \code{factor} \tab Location of the training (one-site or multi-site)\cr
-#'    \strong{Curriculum} \tab \code{factor} \tab Fixed curriculum\cr
-#'    \strong{Control} \tab \code{factor} \tab Alternative treatment for control group\cr
-#'    \strong{Assignment} \tab \code{factor} \tab Random assignment or matching (at the level of the individual caregiver or childcare center)\cr
-#'    \strong{Train_Knowledge} \tab \code{factor} \tab Explicit focus on knowledge\cr
-#'    \strong{Train_Skills} \tab \code{factor} \tab Explicit focus on skills\cr
-#'    \strong{Train_Attitude} \tab \code{factor} \tab Explicit focus on attitude\cr
-#'    \strong{Video} \tab \code{factor} \tab Use of video feedback\cr
-#'    \strong{Design} \tab \code{factor} \tab Single group, or two-group experimental design\cr
-#'    \strong{Pre_Post} \tab \code{factor} \tab Pretest/posttest design (yes/no)\cr
-#'    \strong{Blind} \tab \code{factor} \tab Was a blinding procedure used?\cr
[…]

### 2021-12-11 R/brma.R
fix curry documentation

@@ -36,7 +36,7 @@
 #' @details Penalization of the regression coefficients occurs either via the
 #' lasso (Park & Casella, 2008) or the regularized horseshoe
 #' (Piironen & Vehtari, 2017) prior. The implementation of both priors is based
-#' on the [brms::brms-package] package.
+#' on the \code{\link[brms]{brms}} package.
 #' \describe{
 #'   \item{lasso}{ The Bayesian equivalent of the lasso penalty is obtained when
 #'   placing independent Laplace (i.e., double exponential) priors on the

### 2021-12-11 R/curry.R

@@ -3,6 +3,7 @@
 #' A systematic review and meta-analysis of the effects of performing acts of
 #' kindness on the well-being of the actor.
 #'
+#' @format A data.frame with 56 rows and 18 columns.
 #' \tabular{lll}{
 #'    \strong{study_id} \tab \code{factor} \tab Unique identifier of the study\cr
 #'    \strong{effect_id} \tab \code{integer} \tab Unique identifier of the effect size\cr
@@ -32,5 +33,5 @@
 #' meta-analysis of the effects of performing acts of kindness on the well-being
 #' of the actor. Journal of Experimental Social Psychology, 76, 320-329.
 #' \doi{10.1016/j.ecresq.2007.04.005}
-#' @format A data.frame with 56 rows and 18 columns.
-NULL
+#' @source \doi{10.1016/j.ecresq.2007.04.005}
+"curry"

### 2021-12-11 README.Rmd
add pkgdown

@@
 <!-- [![codecov](https://codecov.io/gh/cjvanlissa/pema/branch/master/graph/badge.svg?token=7S9XKDRT4M)](https://codecov.io/gh/cjvanlissa/pema) -->
-[![Contributor Covenant](https://img.shields.io/badge/Contributor%20Covenant-v2.0%20adopted-ff69b4.svg)](code_of_conduct.md)
+[![Contributor Covenant](https://img.shields.io/badge/Contributor%20Covenant-v2.0%20adopted-ff69b4.svg)](https://www.contributor-covenant.org/version/2/0/code_of_conduct.html)
 <!-- [![CII Best Practices](https://bestpractices.coreinfrastructure.org/projects/3969/badge)](https://bestpractices.coreinfrastructure.org/projects/3969) -->

### 2021-12-11 R/bonapersona.R

@@ -1,0 +1,19 @@
+#' The behavioral phenotype of early life adversity
+#'
+#' This meta-analysis of rodent studies examined whether early life adversity
+#' (ELA) alters cognitive performance in several domains.
+#' The data include over 400 independent experiments, involving approximately
+#' 8600 animals.
+#'
+#' @format A data.frame with 734 rows and 65 columns.
+#' @docType data
+#' @keywords datasets
+#' @name bonapersona
+#' @usage data("bonapersona")
+#' @references Bonapersona, V., Kentrop, J., Van Lissa, C. J., van der Veen,
+#' R., Joels, M., & Sarabdjitsingh, R. A. (2019).
+#' The behavioral phenotype of early life adversity: A 3-level meta-analysis of
+#' rodent studies. Neuroscience & Biobehavioral Reviews, 102, 299–307.
+#' \doi{10.1016/j.neubiorev.2019.04.021}
+#' @source \url{https://osf.io/ra947/}
+"bonapersona"

### 2021-12-11 R/brma.R

@@ -104,6 +104,7 @@
 #' @importMethodsFrom rstan summary
 #' @importFrom stats model.matrix na.omit quantile sd
 #' @importFrom RcppParallel RcppParallelLibs CxxFlags
+#' @importFrom rstantools bayes_R2
 # The line above is just to avoid CRAN warnings that RcppParallel is not
 # imported from, despite RcppParallel being a necessary dependency of rstan.
 brma <-

### 2021-12-11 R/methods_predict.R

@@ -10,8 +10,12 @@ predict.brma <- function(object, newdata, type = c("mean", "median", "samples"),
       X <- try({
         form <- object$formula
         form[2] <- NULL
-        if(object$vi_column %in% names(newdata)) newdata[[object$vi_column]] <- NULL
-        if(object$study_column %in% names(newdata)) newdata[[object$study_column]] <- NULL
+        if(!is.null(object[["vi_column"]])){
+          if(object$vi_column %in% names(newdata)) newdata[[object$vi_column]] <- NULL
+        }
+        if(!is.null(object[["study_column"]])){
+          if(object$study_column %in% names(newdata)) newdata[[object$study_column]] <- NULL
+        }
         # Make model matrix
         mf <- call("model.frame")
         #mf <- mf[c(1L, match(c("formula", "subset", "na.action"), names(mf), 0L))]

### 2021-12-11 tests/testthat/test-methods.R

@@ -1,0 +1,45 @@
+data("bonapersona")
+df <- bonapersona
+df <- df[, c("species", "origin", "sex", "ageWeek", "model", "yi", "vi")]
+df <- na.omit(df)
+
+suppressWarnings({res <- brma(yi~., method = "lasso", data = df, iter = 100)})
+sms <- summary(res)
+
+test_that("summary method works", {
+  expect_true(all(c("coefficients", "tau2", "R2", "k", "method", "algorithm") %in% names(sms)))
+})
+
+test_that("print method works", {
+  tmp <- capture.output(print(sms))
+  expect_true(any(startsWith(tmp, "BRMA")))
+  expect_true(any(startsWith(tmp, "Intercept")))
+})
+
+test_that("predict method works", {
+  preds <- predict(res)
+  expect_true(inherits(preds, "numeric"))
+  expect_true(length(preds) == nrow(df))
+})
+
+test_that("predict method works with samples", {
+  preds <- predict(res, type = "samples")
+  expect_true(inherits(preds, "matrix"))
+  expect_true(nrow(preds) == nrow(df))
+  expect_true(ncol(preds) == 200)
+})
+
+test_that("predict method works with newdata", {
+  nd <- df[1:10, ]
+  preds <- predict(res, newdata = nd)
+  expect_true(inherits(preds, "numeric"))
+  expect_true(length(preds) == nrow(nd))
+})
+
+test_that("predict method works with samples", {
+  nd <- df[1:10, ]
+  preds <- predict(res, newdata = nd, type = "samples")
+  expect_true(inherits(preds, "matrix"))
+  expect_true(nrow(preds) == nrow(nd))
+  expect_true(ncol(preds) == 200)
+})

### 2021-12-11 tests/testthat/test-methods.R
try to fix tests

@@ -1,4 +1,4 @@
-data("bonapersona")
+library(pema)
 df <- bonapersona
 df <- df[, c("species", "origin", "sex", "ageWeek", "model", "yi", "vi")]
 df <- na.omit(df)

### 2021-12-11 tests/testthat/test-methods.R
try to fix again

@@ -1,5 +1,5 @@
 library(pema)
-df <- bonapersona
+df <- pema::bonapersona
 df <- df[, c("species", "origin", "sex", "ageWeek", "model", "yi", "vi")]
 df <- na.omit(df)
 

### 2021-12-12 R/bonapersona.R
add cran-comments.md

@@ -1,4 +1,4 @@
-#' The behavioral phenotype of early life adversity
+#' Data from 'The behavioral phenotype of early life adversity'
 #'
 #' This meta-analysis of rodent studies examined whether early life adversity
 #' (ELA) alters cognitive performance in several domains.

### 2021-12-12 R/brma.R

@@ -35,8 +35,7 @@
 #' Use this, e.g., to override default arguments of that function.
 #' @details Penalization of the regression coefficients occurs either via the
 #' lasso (Park & Casella, 2008) or the regularized horseshoe
-#' (Piironen & Vehtari, 2017) prior. The implementation of both priors is based
-#' on the \code{\link[brms]{brms}} package.
+#' (Piironen & Vehtari, 2017) prior.
 #' \describe{
 #'   \item{lasso}{ The Bayesian equivalent of the lasso penalty is obtained when
 #'   placing independent Laplace (i.e., double exponential) priors on the

### 2021-12-12 R/curry.R

@@ -1,4 +1,4 @@
-#' Happy to Help?
+#' Data from 'Happy to Help?'
 #'
 #' A systematic review and meta-analysis of the effects of performing acts of
 #' kindness on the well-being of the actor.

### 2021-12-12 R/brma.R
update 2021-12-12 08:27:51

@@ -3,7 +3,7 @@
 #' This function uses Bayesian estimation via the \code{stan} function
 #' [rstan::sampling] to fit a meta-analytic mixed-effects model with
 #' moderators. A lasso or horseshoe prior is used to shrink the regression
-#' coefficients of irrrelevant moderators towards zero. See Details.
+#' coefficients of irrelevant moderators towards zero. See Details.
 #' @param formula An object of class `formula` (or one that can be coerced to
 #' that class), see \code{\link[stats]{lm}}.
 #' @param data Optional data.frame containing the variables in the model, see
@@ -87,14 +87,15 @@
 #' }
 #' @references
 #' Park, T., & Casella, G. (2008). The Bayesian Lasso. Journal of the American
-#' Statistical Association, 103(482), 681–686. doi:10.1198/016214508000000337
+#' Statistical Association, 103(482), 681–686. \doi{10.1198/016214508000000337}
 #'
-#' Carvalho, C. M., Polson, N. G., & Scott, J. G. (2010). The horseshoe estimator
-#' for sparse signals. Biometrika, 97(2), 465–480. doi:10.1093/biomet/asq017
+#' Carvalho, C. M., Polson, N. G., & Scott, J. G. (2010). The horseshoe
+#' estimator for sparse signals. Biometrika, 97(2), 465–480.
+#' \doi{10.1093/biomet/asq017}
 #'
-#' Piironen, J., & Vehtari, A. (2017). Sparsity information and regularization in
-#' the horseshoe and other shrinkage priors. Electronic Journal of Statistics, 11(2).
-#' doi:10.1214/17-ejs1337si
+#' Piironen, J., & Vehtari, A. (2017). Sparsity information and regularization
+#' in the horseshoe and other shrinkage priors. Electronic Journal of
+#' Statistics, 11(2). \doi{10.1214/17-ejs1337si}
 #' @export
 #' @examples
 #' data("curry")

### 2021-12-12 R/pema-package.R

@@ -12,6 +12,7 @@
 #' @importFrom rstan sampling
 #'
 #' @references
-#' Stan Development Team (NA). RStan: the R interface to Stan. R package version 2.26.2. https://mc-stan.org
+#' Stan Development Team (NA). RStan: the R interface to Stan. R package version
+#' 2.26.2. \url{https://mc-stan.org}
 #'
 NULL

### 2021-12-12 R/simulate_smd.R

@@ -11,29 +11,29 @@
 #' @param k_test Atomic integer. The number of studies in the testing dataset.
 #' Defaults to 100.
 #' @param mean_n Atomic integer. The mean sample size of each simulated study in
-#' the meta-analytic dataset. Defaults to 40. For each simulated study, the
+#' the meta-analytic dataset. Defaults to `40`. For each simulated study, the
 #' sample size n is randomly drawn from a normal distribution with mean mean_n,
 #' and sd mean_n/3.
 #' @param es Atomic numeric vector. The effect size, also known as beta, used in
-#'  the model statement. Defaults to .5.
+#'  the model statement. Defaults to `.5`.
 #' @param tau2 Atomic numeric vector. The residual heterogeneity. For a range of
 #'  realistic values encountered in psychological research, see Van Erp,
-#'  Verhagen, Grasman, & Wagenmakers, 2017. Defaults to 0.04.
+#'  Verhagen, Grasman, & Wagenmakers, 2017. Defaults to `0.04`.
 #' @param alpha Vector of slant parameters, passed to [sn::rsn].
 #' @param moderators Atomic integer. The number of moderators to simulate for
 #' each study. Make sure that the number of moderators to be simulated is at
 #' least as large as the number of moderators referred to in the model
-#' parameter. Internally, the matrix of moderators is referred to as "x".
+#' parameter. Internally, the matrix of moderators is referred to as `"x"`.
 #' Defaults to 5.
 #' @param distribution Atomic character. The distribution of the moderators.
-#' Can be set to either "normal" or "bernoulli". Defaults to "normal".
+#' Can be set to either `"normal"` or `"bernoulli"`. Defaults to `"normal"`.
 #' @param model Expression. An expression to specify the model from which to
-#' simulate the mean true effect size, mu. This formula may use the terms "es"
-#' (referring to the es parameter of the call to simulate_smd), and "x\[, \]"
+#' simulate the mean true effect size, mu. This formula may use the terms `"es"`
+#' (referring to the es parameter of the call to simulate_smd), and `"x\[, \]"`
 #' (referring to the matrix of moderators, x). Thus, to specify that the mean
 #' effect size, mu, is a function of the effect size and the first moderator,
 #' one would pass the value \code{model = "es * x\[ , 1\]"}.
-#' Defaults to "es * x\[ , 1\]".
+#' Defaults to `"es * x\[ , 1\]"`.
 #' @return List of length 4. The "training" element of this list is a data.frame
[…]

### 2021-12-12 R/bonapersona.R
try to pass bonapersona test

@@ -4,11 +4,9 @@
 #' (ELA) alters cognitive performance in several domains.
 #' The data include over 400 independent experiments, involving approximately
 #' 8600 animals.
-#'
-#' @format A data.frame with 734 rows and 65 columns.
 #' @docType data
 #' @keywords datasets
-#' @name bonapersona
+#' @format A data.frame with 734 rows and 65 columns.
 #' @usage data("bonapersona")
 #' @references Bonapersona, V., Kentrop, J., Van Lissa, C. J., van der Veen,
 #' R., Joels, M., & Sarabdjitsingh, R. A. (2019).

### 2021-12-12 tests/testthat/test-methods.R

@@ -1,5 +1,5 @@
 library(pema)
-df <- pema::bonapersona
+df <- bonapersona
 df <- df[, c("species", "origin", "sex", "ageWeek", "model", "yi", "vi")]
 df <- na.omit(df)
 

### 2021-12-12 R/bonapersona.R
update 2021-12-12 11:01:43

@@ -4,14 +4,10 @@
 #' (ELA) alters cognitive performance in several domains.
 #' The data include over 400 independent experiments, involving approximately
 #' 8600 animals.
-#' @docType data
-#' @keywords datasets
 #' @format A data.frame with 734 rows and 65 columns.
-#' @usage data("bonapersona")
 #' @references Bonapersona, V., Kentrop, J., Van Lissa, C. J., van der Veen,
 #' R., Joels, M., & Sarabdjitsingh, R. A. (2019).
 #' The behavioral phenotype of early life adversity: A 3-level meta-analysis of
 #' rodent studies. Neuroscience & Biobehavioral Reviews, 102, 299–307.
 #' \doi{10.1016/j.neubiorev.2019.04.021}
-#' @source \url{https://osf.io/ra947/}
 "bonapersona"

### 2021-12-12 R/brma.R

@@ -95,7 +95,7 @@
 #'
 #' Piironen, J., & Vehtari, A. (2017). Sparsity information and regularization
 #' in the horseshoe and other shrinkage priors. Electronic Journal of
-#' Statistics, 11(2). \doi{10.1214/17-ejs1337si}
+#' Statistics, 11(2). \url{https://projecteuclid.org/journals/electronic-journal-of-statistics/volume-11/issue-2/Sparsity-information-and-regularization-in-the-horseshoe-and-other-shrinkage/10.1214/17-EJS1337SI.pdf}
 #' @export
 #' @examples
 #' data("curry")

### 2021-12-12 R/curry.R

@@ -24,14 +24,9 @@
 #'    \strong{outcomedv} \tab \code{character} \tab What was the outcome, or dependent variable, of the study?\cr
 #'    \strong{outcomecode} \tab \code{factor} \tab What was the outcome, or dependent variable, of the study? Categorized into Happiness, Life Satisfaction, PN Affect (positive or negative), and Other
 #' }
-#' @docType data
-#' @keywords datasets
-#' @name curry
-#' @usage data("curry")
 #' @references Curry, O. S., Rowland, L. A., Van Lissa, C. J., Zlotowitz, S.,
 #' McAlaney, J., & Whitehouse, H. (2018). Happy to help? A systematic review and
 #' meta-analysis of the effects of performing acts of kindness on the well-being
 #' of the actor. Journal of Experimental Social Psychology, 76, 320-329.
 #' \doi{10.1016/j.ecresq.2007.04.005}
-#' @source \doi{10.1016/j.ecresq.2007.04.005}
 "curry"

### 2021-12-20 R/brma.R
fix methods

@@ -20,18 +20,6 @@
 #' @param method Character, indicating the type of regularizing prior to use.
 #' Supports one of \code{c("lasso", "hs")}, see Details. Defaults to
 #' \code{"lasso"}.
-#' @param standardize Logical, indicating whether or not to standardize the
-#' predictors (defaults to \code{TRUE}, which is recommended so that shrinking
-#' affects all parameters similarly.
-#' @param prior Numeric vector, specifying the prior to use. Note that the
-#' different \code{method}s require this vector to contain specific named
-#' elements.
-# @param iter A positive integer specifying the number of iterations for each
-# chain (including warmup). Defaults to 2000.
-#  the model statement. Defaults to .5.
-# @param chains A positive integer specifying the number of Markov chains.
-# Defaults to 4.
-#' @param mute_stan Logical, indicating whether mute all 'Stan' output or not.
 #' @param standardize Either a logical argument or a list. If `standardize` is
 #' logical, it controls whether all predictors are standardized prior to
 #' analysis or not. Parameter estimates are restored to the predictors' original
@@ -42,8 +30,17 @@
 #' , mean(X2), mean(X...)), scale = c(sd(X1), sd(X2), sd(X...)))`. It is used
 #' only to restore parameter estimates to the original scale of the predictors.
 #' This is useful, e.g., to standardize continuous and dichotomous variables
-#' separately. Note that when predictors are not standardized, they may be
-#' differentially affected by the shrinkage prior.
+#' separately. Defaults to \code{TRUE}, which is recommended so that shrinking
+#' affects all parameters similarly.
+#' @param prior Numeric vector, specifying the prior to use. Note that the
+#' different \code{method}s require this vector to contain specific named
+#' elements.
+# @param iter A positive integer specifying the number of iterations for each
+# chain (including warmup). Defaults to 2000.
+#  the model statement. Defaults to .5.
+# @param chains A positive integer specifying the number of Markov chains.
+# Defaults to 4.
+#' @param mute_stan Logical, indicating whether mute all 'Stan' output or not.
 # @param prior_only Logical, indicating whether to sample from the prior
[…]

### 2021-12-20 R/methods_print_summary.R

@@ -35,7 +35,7 @@ summary.brma <- function(object, ...){
   # R2 <- max(0, 100 * (tau2_before-tau2)/tau2_before)
   # I2 <- 100 * tau2/(vt + tau2)
   # H2 <- tau2/vt + 1
-  out <- object[na.omit(match(c("coefficients", "tau2", "I2", "H2", "R2", "k"), names(object)))]
+  out <- object[na.omit(match(c("coefficients", "tau2", "I2", "H2", "R2", "k", "study_column", "study"), names(object)))]
   out$method <- object$fit@stan_args[[1]]$method
   out$algorithm <- object$fit@stan_args[[1]]$algorithm
   class(out) <- c("brma_sum", class(out))
@@ -63,8 +63,14 @@ print.brma <- function(x, ...){
 #' @export
 print.brma_sum <- function(x, digits = 2, ...){
   #res$tau2/unaccounted
-  cat("BRMA mixed-effects model (k = ", x$k, "), method: ", x$algorithm, " ", x$method, "\n", sep = "")
-  cat("tau^2: ", formatC(x$tau2, digits = digits, format = "f"), " (SE = ", formatC(x$coefficients["tau2", 2], digits = digits, format = "f"),")\n\n", sep = "")
+  cat("BRMA ", c("three-level ", "")[is.null(x[["study_column"]])+1], "mixed-effects model (k = ", x$k, "), method: ", x$algorithm, " ", x$method, "\n", sep = "")
+  taus <- x$coefficients[startsWith(rownames(x$coefficients), "tau2"), c("mean", "se_mean"), drop = FALSE]
+  if(nrow(taus) == 1){
+    cat("tau^2 (n = ", x$k, "): ", formatC(taus[1,1], digits = digits, format = "f"), " (SE = ", formatC(taus[1,2], digits = digits, format = "f"),")\n\n", sep = "")
+  } else {
+    cat("tau^2 (n = ", x$k, "): ", formatC(taus["tau2_w",1], digits = digits, format = "f"), " (SE = ", formatC(taus["tau2_w",2], digits = digits, format = "f"),")\n", sep = "")
+    cat("tau^2 between ", x$study_column, " (k = ", length(unique(x$study)), "): ", formatC(taus["tau2_b",1], digits = digits, format = "f"), " (SE = ", formatC(taus["tau2_b",2], digits = digits, format = "f"),")\n\n", sep = "")
+  }
[…]

### 2021-12-20 src/stanExports_horseshoe_MA.h

@@ -33,7 +33,7 @@ static int current_statement_begin__;
 stan::io::program_reader prog_reader__() {
     stan::io::program_reader reader;
     reader.add_event(0, 0, "start", "model_horseshoe_MA");
-    reader.add_event(100, 98, "end", "model_horseshoe_MA");
+    reader.add_event(91, 89, "end", "model_horseshoe_MA");
     return reader;
 }
 template <typename T0__, typename T1__, typename T2__, typename T3__>
@@ -106,8 +106,6 @@ private:
         std::vector<int> J_1;
         vector_d Z_1_1;
         int prior_only;
-        int Kc;
-        matrix_d Xc;
         vector_d means_X;
         vector_d sds_X;
 public:
@@ -268,63 +266,48 @@ public:
             vals_i__ = context__.vals_i("prior_only");
             pos__ = 0;
             prior_only = vals_i__[pos__++];
-            // initialize transformed data variables
-            current_statement_begin__ = 41;
-            Kc = int(0);
-            stan::math::fill(Kc, std::numeric_limits<int>::min());
-            stan::math::assign(Kc,(K - 1));
-            current_statement_begin__ = 42;
-            validate_non_negative_index("Xc", "N", N);
-            validate_non_negative_index("Xc", "Kc", Kc);
-            Xc = Eigen::Matrix<double, Eigen::Dynamic, Eigen::Dynamic>(N, Kc);
-            stan::math::fill(Xc, DUMMY_VAR__);
-            current_statement_begin__ = 43;
-            validate_non_negative_index("means_X", "Kc", Kc);
-            means_X = Eigen::Matrix<double, Eigen::Dynamic, 1>(Kc);
-            stan::math::fill(means_X, DUMMY_VAR__);
-            current_statement_begin__ = 44;
-            validate_non_negative_index("sds_X", "Kc", Kc);
-            sds_X = Eigen::Matrix<double, Eigen::Dynamic, 1>(Kc);
-            stan::math::fill(sds_X, DUMMY_VAR__);
-            // execute transformed data statements
-            current_statement_begin__ = 45;
-            for (int i = 2; i <= K; ++i) {
-                current_statement_begin__ = 46;
-                stan::model::assign(means_X, 
-                            stan::model::cons_list(stan::model::index_uni((i - 1)), stan::model::nil_index_list()), 
[…]

### 2021-12-20 src/stanExports_horseshoe_MA_ml.h

@@ -33,7 +33,7 @@ static int current_statement_begin__;
 stan::io::program_reader prog_reader__() {
     stan::io::program_reader reader;
     reader.add_event(0, 0, "start", "model_horseshoe_MA_ml");
-    reader.add_event(117, 115, "end", "model_horseshoe_MA_ml");
+    reader.add_event(108, 106, "end", "model_horseshoe_MA_ml");
     return reader;
 }
 template <typename T0__, typename T1__, typename T2__, typename T3__>
@@ -110,8 +110,6 @@ private:
         std::vector<int> J_2;
         vector_d Z_2_1;
         int prior_only;
-        int Kc;
-        matrix_d Xc;
         vector_d means_X;
         vector_d sds_X;
 public:
@@ -310,70 +308,55 @@ public:
             vals_i__ = context__.vals_i("prior_only");
             pos__ = 0;
             prior_only = vals_i__[pos__++];
-            // initialize transformed data variables
-            current_statement_begin__ = 47;
-            Kc = int(0);
-            stan::math::fill(Kc, std::numeric_limits<int>::min());
-            stan::math::assign(Kc,(K - 1));
-            current_statement_begin__ = 48;
-            validate_non_negative_index("Xc", "N", N);
-            validate_non_negative_index("Xc", "Kc", Kc);
-            Xc = Eigen::Matrix<double, Eigen::Dynamic, Eigen::Dynamic>(N, Kc);
-            stan::math::fill(Xc, DUMMY_VAR__);
-            current_statement_begin__ = 49;
-            validate_non_negative_index("means_X", "Kc", Kc);
-            means_X = Eigen::Matrix<double, Eigen::Dynamic, 1>(Kc);
-            stan::math::fill(means_X, DUMMY_VAR__);
-            current_statement_begin__ = 50;
-            validate_non_negative_index("sds_X", "Kc", Kc);
-            sds_X = Eigen::Matrix<double, Eigen::Dynamic, 1>(Kc);
-            stan::math::fill(sds_X, DUMMY_VAR__);
-            // execute transformed data statements
-            current_statement_begin__ = 51;
-            for (int i = 2; i <= K; ++i) {
-                current_statement_begin__ = 52;
-                stan::model::assign(means_X, 
-                            stan::model::cons_list(stan::model::index_uni((i - 1)), stan::model::nil_index_list()), 
[…]

### 2021-12-20 src/stanExports_horseshoe_MA_ml_noint.h

@@ -33,7 +33,7 @@ static int current_statement_begin__;
 stan::io::program_reader prog_reader__() {
     stan::io::program_reader reader;
     reader.add_event(0, 0, "start", "model_horseshoe_MA_ml_noint");
-    reader.add_event(102, 100, "end", "model_horseshoe_MA_ml_noint");
+    reader.add_event(105, 103, "end", "model_horseshoe_MA_ml_noint");
     return reader;
 }
 template <typename T0__, typename T1__, typename T2__, typename T3__>
@@ -110,6 +110,8 @@ private:
         std::vector<int> J_2;
         vector_d Z_2_1;
         int prior_only;
+        vector_d means_X;
+        vector_d sds_X;
 public:
     model_horseshoe_MA_ml_noint(stan::io::var_context& context__,
         std::ostream* pstream__ = 0)
@@ -306,35 +308,55 @@ public:
             vals_i__ = context__.vals_i("prior_only");
             pos__ = 0;
             prior_only = vals_i__[pos__++];
+            current_statement_begin__ = 45;
+            validate_non_negative_index("means_X", "K", K);
+            context__.validate_dims("data initialization", "means_X", "vector_d", context__.to_vec(K));
+            means_X = Eigen::Matrix<double, Eigen::Dynamic, 1>(K);
+            vals_r__ = context__.vals_r("means_X");
+            pos__ = 0;
+            size_t means_X_j_1_max__ = K;
+            for (size_t j_1__ = 0; j_1__ < means_X_j_1_max__; ++j_1__) {
+                means_X(j_1__) = vals_r__[pos__++];
+            }
+            current_statement_begin__ = 46;
+            validate_non_negative_index("sds_X", "K", K);
+            context__.validate_dims("data initialization", "sds_X", "vector_d", context__.to_vec(K));
+            sds_X = Eigen::Matrix<double, Eigen::Dynamic, 1>(K);
+            vals_r__ = context__.vals_r("sds_X");
+            pos__ = 0;
+            size_t sds_X_j_1_max__ = K;
+            for (size_t j_1__ = 0; j_1__ < sds_X_j_1_max__; ++j_1__) {
+                sds_X(j_1__) = vals_r__[pos__++];
+            }
             // initialize transformed data variables
             // execute transformed data statements
             // validate transformed data
             // validate, set parameter ranges
             num_params_r__ = 0U;
             param_ranges_i__.clear();
-            current_statement_begin__ = 48;
[…]

### 2021-12-20 src/stanExports_horseshoe_MA_noint.h

@@ -33,7 +33,7 @@ static int current_statement_begin__;
 stan::io::program_reader prog_reader__() {
     stan::io::program_reader reader;
     reader.add_event(0, 0, "start", "model_horseshoe_MA_noint");
-    reader.add_event(85, 83, "end", "model_horseshoe_MA_noint");
+    reader.add_event(88, 86, "end", "model_horseshoe_MA_noint");
     return reader;
 }
 template <typename T0__, typename T1__, typename T2__, typename T3__>
@@ -106,6 +106,8 @@ private:
         std::vector<int> J_1;
         vector_d Z_1_1;
         int prior_only;
+        vector_d means_X;
+        vector_d sds_X;
 public:
     model_horseshoe_MA_noint(stan::io::var_context& context__,
         std::ostream* pstream__ = 0)
@@ -264,26 +266,46 @@ public:
             vals_i__ = context__.vals_i("prior_only");
             pos__ = 0;
             prior_only = vals_i__[pos__++];
+            current_statement_begin__ = 39;
+            validate_non_negative_index("means_X", "K", K);
+            context__.validate_dims("data initialization", "means_X", "vector_d", context__.to_vec(K));
+            means_X = Eigen::Matrix<double, Eigen::Dynamic, 1>(K);
+            vals_r__ = context__.vals_r("means_X");
+            pos__ = 0;
+            size_t means_X_j_1_max__ = K;
+            for (size_t j_1__ = 0; j_1__ < means_X_j_1_max__; ++j_1__) {
+                means_X(j_1__) = vals_r__[pos__++];
+            }
+            current_statement_begin__ = 40;
+            validate_non_negative_index("sds_X", "K", K);
+            context__.validate_dims("data initialization", "sds_X", "vector_d", context__.to_vec(K));
+            sds_X = Eigen::Matrix<double, Eigen::Dynamic, 1>(K);
+            vals_r__ = context__.vals_r("sds_X");
+            pos__ = 0;
+            size_t sds_X_j_1_max__ = K;
+            for (size_t j_1__ = 0; j_1__ < sds_X_j_1_max__; ++j_1__) {
+                sds_X(j_1__) = vals_r__[pos__++];
+            }
             // initialize transformed data variables
             // execute transformed data statements
             // validate transformed data
             // validate, set parameter ranges
             num_params_r__ = 0U;
             param_ranges_i__.clear();
-            current_statement_begin__ = 43;
+            current_statement_begin__ = 45;
[…]

### 2021-12-20 src/stanExports_lasso_MA.h

@@ -33,7 +33,7 @@ static int current_statement_begin__;
 stan::io::program_reader prog_reader__() {
     stan::io::program_reader reader;
     reader.add_event(0, 0, "start", "model_lasso_MA");
-    reader.add_event(72, 70, "end", "model_lasso_MA");
+    reader.add_event(62, 60, "end", "model_lasso_MA");
     return reader;
 }
 #include <stan_meta_header.hpp>
@@ -52,9 +52,6 @@ private:
         std::vector<int> J_1;
         vector_d Z_1_1;
         int prior_only;
-        vector_d se2;
-        int Kc;
-        matrix_d Xc;
         vector_d means_X;
         vector_d sds_X;
 public:
@@ -194,65 +191,43 @@ public:
             vals_i__ = context__.vals_i("prior_only");
             pos__ = 0;
             prior_only = vals_i__[pos__++];
-            // initialize transformed data variables
-            current_statement_begin__ = 22;
-            validate_non_negative_index("se2", "N", N);
-            se2 = Eigen::Matrix<double, Eigen::Dynamic, 1>(N);
-            stan::math::fill(se2, DUMMY_VAR__);
-            stan::math::assign(se2,square(se));
-            current_statement_begin__ = 23;
-            Kc = int(0);
-            stan::math::fill(Kc, std::numeric_limits<int>::min());
-            stan::math::assign(Kc,(K - 1));
-            current_statement_begin__ = 24;
-            validate_non_negative_index("Xc", "N", N);
-            validate_non_negative_index("Xc", "Kc", Kc);
-            Xc = Eigen::Matrix<double, Eigen::Dynamic, Eigen::Dynamic>(N, Kc);
-            stan::math::fill(Xc, DUMMY_VAR__);
-            current_statement_begin__ = 25;
-            validate_non_negative_index("means_X", "Kc", Kc);
-            means_X = Eigen::Matrix<double, Eigen::Dynamic, 1>(Kc);
-            stan::math::fill(means_X, DUMMY_VAR__);
-            current_statement_begin__ = 26;
-            validate_non_negative_index("sds_X", "Kc", Kc);
-            sds_X = Eigen::Matrix<double, Eigen::Dynamic, 1>(Kc);
-            stan::math::fill(sds_X, DUMMY_VAR__);
-            // execute transformed data statements
-            current_statement_begin__ = 27;
-            for (int i = 2; i <= K; ++i) {
-                current_statement_begin__ = 28;
[…]

### 2021-12-20 src/stanExports_lasso_MA_ml.h

@@ -33,7 +33,7 @@ static int current_statement_begin__;
 stan::io::program_reader prog_reader__() {
     stan::io::program_reader reader;
     reader.add_event(0, 0, "start", "model_lasso_MA_ml");
-    reader.add_event(101, 99, "end", "model_lasso_MA_ml");
+    reader.add_event(92, 90, "end", "model_lasso_MA_ml");
     return reader;
 }
 template <typename T0__, typename T1__, typename T2__, typename T3__>
@@ -107,8 +107,6 @@ private:
         std::vector<int> J_2;
         vector_d Z_2_1;
         int prior_only;
-        int Kc;
-        matrix_d Xc;
         vector_d means_X;
         vector_d sds_X;
 public:
@@ -286,65 +284,50 @@ public:
             vals_i__ = context__.vals_i("prior_only");
             pos__ = 0;
             prior_only = vals_i__[pos__++];
-            // initialize transformed data variables
-            current_statement_begin__ = 44;
-            Kc = int(0);
-            stan::math::fill(Kc, std::numeric_limits<int>::min());
-            stan::math::assign(Kc,(K - 1));
-            current_statement_begin__ = 45;
-            validate_non_negative_index("Xc", "N", N);
-            validate_non_negative_index("Xc", "Kc", Kc);
-            Xc = Eigen::Matrix<double, Eigen::Dynamic, Eigen::Dynamic>(N, Kc);
-            stan::math::fill(Xc, DUMMY_VAR__);
-            current_statement_begin__ = 46;
-            validate_non_negative_index("means_X", "Kc", Kc);
-            means_X = Eigen::Matrix<double, Eigen::Dynamic, 1>(Kc);
-            stan::math::fill(means_X, DUMMY_VAR__);
-            current_statement_begin__ = 47;
-            validate_non_negative_index("sds_X", "Kc", Kc);
-            sds_X = Eigen::Matrix<double, Eigen::Dynamic, 1>(Kc);
-            stan::math::fill(sds_X, DUMMY_VAR__);
-            // execute transformed data statements
-            current_statement_begin__ = 48;
-            for (int i = 2; i <= K; ++i) {
-                current_statement_begin__ = 49;
-                stan::model::assign(means_X, 
-                            stan::model::cons_list(stan::model::index_uni((i - 1)), stan::model::nil_index_list()), 
[…]

### 2021-12-20 src/stanExports_lasso_MA_ml_noint.h

@@ -33,7 +33,7 @@ static int current_statement_begin__;
 stan::io::program_reader prog_reader__() {
     stan::io::program_reader reader;
     reader.add_event(0, 0, "start", "model_lasso_MA_ml_noint");
-    reader.add_event(85, 83, "end", "model_lasso_MA_ml_noint");
+    reader.add_event(88, 86, "end", "model_lasso_MA_ml_noint");
     return reader;
 }
 template <typename T0__, typename T1__, typename T2__, typename T3__>
@@ -107,6 +107,8 @@ private:
         std::vector<int> J_2;
         vector_d Z_2_1;
         int prior_only;
+        vector_d means_X;
+        vector_d sds_X;
 public:
     model_lasso_MA_ml_noint(stan::io::var_context& context__,
         std::ostream* pstream__ = 0)
@@ -282,28 +284,48 @@ public:
             vals_i__ = context__.vals_i("prior_only");
             pos__ = 0;
             prior_only = vals_i__[pos__++];
+            current_statement_begin__ = 42;
+            validate_non_negative_index("means_X", "K", K);
+            context__.validate_dims("data initialization", "means_X", "vector_d", context__.to_vec(K));
+            means_X = Eigen::Matrix<double, Eigen::Dynamic, 1>(K);
+            vals_r__ = context__.vals_r("means_X");
+            pos__ = 0;
+            size_t means_X_j_1_max__ = K;
+            for (size_t j_1__ = 0; j_1__ < means_X_j_1_max__; ++j_1__) {
+                means_X(j_1__) = vals_r__[pos__++];
+            }
+            current_statement_begin__ = 43;
+            validate_non_negative_index("sds_X", "K", K);
+            context__.validate_dims("data initialization", "sds_X", "vector_d", context__.to_vec(K));
+            sds_X = Eigen::Matrix<double, Eigen::Dynamic, 1>(K);
+            vals_r__ = context__.vals_r("sds_X");
+            pos__ = 0;
+            size_t sds_X_j_1_max__ = K;
+            for (size_t j_1__ = 0; j_1__ < sds_X_j_1_max__; ++j_1__) {
+                sds_X(j_1__) = vals_r__[pos__++];
+            }
             // initialize transformed data variables
             // execute transformed data statements
             // validate transformed data
             // validate, set parameter ranges
             num_params_r__ = 0U;
             param_ranges_i__.clear();
-            current_statement_begin__ = 44;
-            validate_non_negative_index("betas", "K", K);
-            num_params_r__ += K;
[…]

### 2021-12-20 src/stanExports_lasso_MA_noint.h

@@ -33,7 +33,7 @@ static int current_statement_begin__;
 stan::io::program_reader prog_reader__() {
     stan::io::program_reader reader;
     reader.add_event(0, 0, "start", "model_lasso_MA_noint");
-    reader.add_event(56, 54, "end", "model_lasso_MA_noint");
+    reader.add_event(59, 57, "end", "model_lasso_MA_noint");
     return reader;
 }
 #include <stan_meta_header.hpp>
@@ -52,6 +52,8 @@ private:
         std::vector<int> J_1;
         vector_d Z_1_1;
         int prior_only;
+        vector_d means_X;
+        vector_d sds_X;
 public:
     model_lasso_MA_noint(stan::io::var_context& context__,
         std::ostream* pstream__ = 0)
@@ -189,21 +191,41 @@ public:
             vals_i__ = context__.vals_i("prior_only");
             pos__ = 0;
             prior_only = vals_i__[pos__++];
+            current_statement_begin__ = 20;
+            validate_non_negative_index("means_X", "K", K);
+            context__.validate_dims("data initialization", "means_X", "vector_d", context__.to_vec(K));
+            means_X = Eigen::Matrix<double, Eigen::Dynamic, 1>(K);
+            vals_r__ = context__.vals_r("means_X");
+            pos__ = 0;
+            size_t means_X_j_1_max__ = K;
+            for (size_t j_1__ = 0; j_1__ < means_X_j_1_max__; ++j_1__) {
+                means_X(j_1__) = vals_r__[pos__++];
+            }
+            current_statement_begin__ = 21;
+            validate_non_negative_index("sds_X", "K", K);
+            context__.validate_dims("data initialization", "sds_X", "vector_d", context__.to_vec(K));
+            sds_X = Eigen::Matrix<double, Eigen::Dynamic, 1>(K);
+            vals_r__ = context__.vals_r("sds_X");
+            pos__ = 0;
+            size_t sds_X_j_1_max__ = K;
+            for (size_t j_1__ = 0; j_1__ < sds_X_j_1_max__; ++j_1__) {
+                sds_X(j_1__) = vals_r__[pos__++];
+            }
             // initialize transformed data variables
             // execute transformed data statements
             // validate transformed data
             // validate, set parameter ranges
             num_params_r__ = 0U;
             param_ranges_i__.clear();
-            current_statement_begin__ = 22;
-            validate_non_negative_index("betas", "K", K);
-            num_params_r__ += K;
[…]

### 2021-12-20 R/brma.R
fix intercept

@@ -199,6 +199,8 @@ brma.formula <-
     if(all(X[,1] == 1)){
       intercept <- TRUE
       X <- X[, -1]
+    } else {
+      intercept <- FALSE
     }
     if(!inherits(standardize, c("logical", "list"))) stop("Argument 'standardize' must be either logical (TRUE/FALSE) or a list with two elements: list(center = c(mean(X1), mean(X2), mean(X...)), scale = c(sd(X1), sd(X2), sd(X...))).")
     if(is.logical(standardize)){

### 2021-12-21 paper/manuscript.Rmd
comments/additions paper

@@
   data, suggesting its suitability as a small sample solution. We discuss how
-  applied researchers can use BRMA to explorate between-studies heterogeneity
+  applied researchers can use BRMA to explore between-studies heterogeneity
   in meta-analysis.
 
-keywords          : "meta-analysis, machine learning, bayesian, lasso, regularized"
+keywords          : "meta-analysis, machine learning, bayesian, lasso, horseshoe, regularized"
 wordcount         : "5356"
@@
 It is theoretically possible to account for the influence of multiple moderators using meta-regression.
-However, like any regression-based approach, meta-regression requires a relatively high number of cases (studies) per parameter obtain sufficient power to examine heterogeneity.
+However, like any regression-based approach, meta-regression requires a relatively high number of cases (studies) per parameter to obtain sufficient power to examine heterogeneity.
 In practice the number of available studies is often too low to examine heterogeneity reliably (Riley, Higgins, & Deeks, 2011).
@@
 This leads to a problem known as the "curse of dimensionality": the number of candidate moderators is large relative to the number of cases in the data.
-Such cases do not fit comfortably into the
-classic meta-analysis paradigm, which, like any regression-based approach, requires a
-high number of cases per parameter. 
-Between-studies thus presents a non-trivial challenge to data aggregation
+Between-studies differences thus present a non-trivial challenge to data aggregation
 using classic meta-analytic methods.
@@
 Using theories at the individual level for moderator selection at the study level amounts to committing the ecological fallacy: generalizing inferences across levels of analysis [@jargowskyEcologicalFallacy2004].
-To illustrate what theory at the study level of analysis might look like, 
+To illustrate what a theory at the study level of analysis might look like, 
 consider the so-called *decline effect*.
 It is a phenomenon whereby effect sizes in a particular tranche of the literature seem to diminish over time [@schoolerUnpublishedResultsHide2011].
-It has been theorized that the decline effect can been attributed to regression to the mean:
+It has been theorized that the decline effect can be attributed to regression to the mean:
 A finding initially draws attention from the research community because an anomalously large effect size has been published, and subsequent replications find smaller effect sizes.
@@
 Under the fixed effect model, the estimated population effect size  $\hat{\theta}$ is obtained by computing a weighted average of the observed effect sizes.
-If sampling error is assumed to be the only source of variance in observed effect size,
+If sampling error is assumed to be the only source of variance in the observed effect size,
 then it follows that studies with smaller standard errors estimate the underlying true effect size more precisely<!--(Schmidt, Oh \& Hayes, 2009)-->.
@@
 It is important to note that,
-whereas the sampling error for each individual effect size is treated as known,
+whereas the sampling error for each individual effect size is treated as known, the
 between-study heterogeneity $\tau^{2}$ must be estimated.
@@
 
-The random effects model assumes that causes of heterogeneity in the true effect sizes are unknown, and that their influence is random.
+The random-effects model assumes that causes of heterogeneity in the true effect sizes are unknown, and that their influence is random.
 Oftentimes, however, there are systematic sources of heterogeneity in true effect sizes.
@@
 In contrast to a regularized analysis technique, this estimator produces low bias, which means that the average value of the estimated regression coefficients and residual heterogeneity is close to their true values (Panityakul et al., 2013; Hardy & Thompson, 1996).
+However, due to the bias-variance tradeoff, this bias comes at the cost of high variance, meaning that the results might not generalize to a new sample.
+Regularization can offer a solution to this problem.
 <!--It needs a starting estimation of $\tau^{2}$, which is usually estimated by one of the non-iterative methods (Viechtbauer \& López-López, 2015).
@@
 The resulting parameter estimates are those that give the best predictions of the dependent variable in the present dataset.
-Penalized regression, by contrast, adds a penalty term to the quantity to be minimized.
-One commonly used penalty is the L1-norm of the regression coefficients, or LASSO penalty,
+Penalized regression, by contrast, adds a penalty term to the RSS.
+One commonly used penalty is the L1-norm of the regression coefficients, or LASSO penalty (Tibshirani, 1996),
 which corresponds to the sum of their absolute values.
@@
 If $\lambda$ is zero, the shrinkage penalty has no impact at all and the penalized regression will produce the OLS estimates.
-If $\lambda \to \infty$, all coefficient shrink towards zero, producing the null model.
+If $\lambda \to \infty$, all coefficients shrink towards zero, producing the null model.
 <!--Another commonly used penalty is the L2-norm of the coefficients, or ridge penalty,
 which corresponds to the sum of their squared values: $\sum_{j=1}^{p}\beta_{j}^2$.-->
-Because the penalty term is a function of the regression coefficients,
-the optimizer has an incentive to keep the regression coefficients as small as possible.
+Generally, cross-validation is used to find the optimal value for the penalty parameter $\lambda$.
 <!--The LASSO penalty has the unique property of shrinking some coefficients to be exactly zero,
 but the ridge penalty does not do so, as -->
-Note that theLASSO penalty is but one example of a shrinkage penalty; other penalties exist, with some unique properties.
+Note that the LASSO penalty is but one example of a shrinkage penalty; other penalties exist.
 
@@
 ### Bayesian estimation
+
+Instead of using a penalty to shrink regression coefficients towards zero, it is possible to use a Bayesian prior distribution to achieve a similar result.
+Whereas classical, frequentist estimation methods rely solely on the data at hand, Bayesian estimation methods require the specification of a prior distribution.
+The prior distribution is a probability distribution that reflects the prior knowledge or beliefs that the researcher has before collecting the data.
+The prior is combined with the likelihood of the data to form the posterior distribution.
+In the context of regularization, the prior distribution is specified such that it reflects the prior belief that not all regression coefficients are substantial enough to be included in the model.
+
+Many different prior distributions exist that have specific properties that enable them to shrink small regression coefficients towards zero, while keeping substantial coefficients large (van Erp, Oberski & Mulder, 2019).
+Some prior distributions have been shown to result in exactly the same solutions as classical, frequentist penalties, such as the LASSO.
+Specifically, placing independent Laplace (i.e., double exponential) priors on the regression coefficients results in posterior modes that are equal to the lasso estimates (Park and Casella, 2008).
+In addition, many prior distributions have been developed and investigated specifically for the purpose of providing good shrinkage properties, meaning that the prior pulls small regression coefficients towards zero, without exerting any influence on substantial regression coefficients.
+A popular prior in this regard is the horseshoe prior (Carvalho et al.
+2010).
+An advantage of the horseshoe prior compared to the lasso is the fact that it has heavier tails.
+As a result, it will not shrink and therefore bias substantial coefficients as much as the LASSO prior with its lighter tails.
+
+### Implementation
+The brma function uses Stan (Stan development team) to fit the models.
+Stan is a probabilistic programming language that uses a Hamiltonian Monte Carlo algorithm to sample from the posterior distribution.
+When running a Bayesian analysis in Stan it is important to ensure that the algorithm has converged to the posterior distribution in order for the results to be trusted.
+Stan offers automatic warnings and errors if this might not be the case.
+
+Currently, the brma function supports two priors: the LASSO and the regularized horseshoe. We have precompiled the models with these two priors using brms (brms ref).
+
+The LASSO prior is implemented as follows:
+
+$$
+\beta_{j} \sim \text{double exponential}(0, \frac{s}{lambda})
+$$
+
+and requires the specification of a global scale parameter $s$ and an inverse-tuning parameter $\lambda$.
+By default, the global scale is set to 1 and the inverse-tuning parameter is given a chi-square prior with degrees of freedom equal to 1.
+
+For the horseshoe prior, we use an extension proposed by Piironen and Vehtari (2017) called the regularized horseshoe:
+
+$$
+\beta_{j} \sim \text{normal}(0, \tilde{\tau}_j^2\lambda) \text{, with } \tilde{\tau}_j^2 = \frac{c^2 \tau_j^2}{c^2 + \lambda^2 \tau_j^2} \\
+\lambda \sim \text{half-t}(\nu_1, 0, \lambda^2_0) \\
+\tau_j \sim \text{half-t}(\nu_2, 0, 1) \\
+c^2 \sim \text{inverse-gamma}(\frac{\nu_3}{2}, \frac{\nu_3 s^2}{2})
+$$
+
+This extension is more numerically stable in certain cases.
+In addition, it allows the user to explicitly include prior information regarding the number of relevant moderators by setting the argument par_ratio to the ratio of the expected number of non-zero coefficients to the expected number of zero coefficients.
+If this information is not available, the user should specify scale_global ($\lambda^2_0$) which affects the overall shrinkage of the prior, with smaller values resulting in more shrinkage (default = 1).
+In addition, the regularized horseshoe has two degrees of freedom parameters ($\nu_1$ and $\nu_2$) which default to 1.
+Increasing the degrees of freedom parameters results in a prior with lighter tails, which is strictly no longer a horseshoe prior.
+However, the lighter tails might be needed in certain cases to attain convergence.
+The regularized horseshoe differs from the horseshoe in the specification of a finite "slab".
+This ensures at least some regularization of large coefficients and as a consequence, more stable results.
+This slab is governed by a degrees of freedom parameter ($\nu_3$, set to 4) and a scale parameter ($s$, set to 1).
+
+We have chosen all default settings for the hyperparameters such that the values are reasonable in most applications.
+However, in a Bayesian analysis it is good practice to perform a prior sensitivity analysis in which different hyperparameters are chosen and the model is rerun to see if this leads to different results.
+
+Unlike the classical frequentist lasso, Bayesian regularized estimation cannot estimate coefficients to be exactly equal to zero.
+Therefore, some approach is needed to select variables post-estimation.
+the brma funciton currently uses credible intervals (the Bayesian counterpart of confidence intervals) to do so, with a moderator being selected if the 95% credible interval excludes zero.
 
@@
 under what conditions BRMA does not offer an advantage,
-and which prior (horseshoe versus LASSO) is to be preferred.
+and which prior (regularized horseshoe versus LASSO) is to be preferred.
 
@@
 relative to the variance explained by the mean of the training data.
-For a predictive performance measure, it is necessary to use the mean of the training data, as the mean of the testing is a descriptive statistic of that sample.
+For a predictive performance measure, it is necessary to use the mean of the training data, as the mean of the testing set is a descriptive statistic of that sample.
+**ik vind deze zin niet heel duidelijk**
 The resulting metric $R_{test}^{2}$ is expressed by the following equation:
@@
 $$
-R_{cv}^{2} = 1- \frac{\sum_{i=1}^{k}(y_{i-test}-\hat{y}_{i-test})^{2}}{\sum_{i=1}^{k}(y_{i-test}-\bar{y}_{train})^{2}}
+R_{test}^{2} = 1- \frac{\sum_{i=1}^{k}(y_{i-test}-\hat{y}_{i-test})^{2}}{\sum_{i=1}^{k}(y_{i-test}-\bar{y}_{train})^{2}}
 $$
@@
 The number of studies in the training data $k \in (20, 40, 100)$, the average within-study sample size $\bar{n} \in (40, 80, 160)$, the population effect size of relevant moderators $\beta \in (0, .2, .5, .8)$, the number of moderators $p \in (2, 3, 6)$, and residual heterogeneity $\tau^{2} \in (.01, .04, .1)$.
+**het aantal moderatoren is redelijk laag; ik zou vooral nog voordelen van brma verwachten met meer moderatoren maar is dat realistisch in de praktijk?
+Zo ja, dan is het iets om te noemen in de discussie**
 According to a review of 705 published psychological meta-analyses (Van Erp et al., 2017),
@@
 These cases were omitted from further analysis.
+**was er volledige convergence voor brma in alle replicaties? Dat heb ik zelf namelijk nog nooit meegemaakt.**
 
@@
 Within data sets, the BRMA with a horseshoe prior had the highest predictive performance `r round(whichhi[1]*100)`% of the time, followed by RMA, `r round(whichhi[3]*100)`%, and finally BRMA with a LASSO prior, `r round(whichhi[2]*100)`%.
-Results indicated that the overall $R^2_{test}$ was highest for BRMA with a Horseshoe prior and lowest for RMA, see \@ref(tab:tabr2).
-This difference was driven in part by the fact that explained variance was somewhat higher for the BRMA models when the true effect was not null, and by the fact that RMA had larger negative explained variance when the true effect was equal to zero (i.e., there was no effect to detect).
+Results indicated that the overall $R^2_{test}$ was highest for BRMA with a horseshoe prior and lowest for RMA, see \@ref(tab:tabr2).
+This difference was driven in part by the fact that explained variance was somewhat higher for the BRMA models when the true effect was not null **moet zijn null?**, and by the fact that RMA had larger negative explained variance when the true effect was equal to zero **moet zijn not equal to zero?** (i.e., there was no effect to detect).**deze statements lijken niet overeen te komen met de tabel**
 
@@
 Conversely, RMA had relatively poor predictive performance on average, and was more responsive to increases in the number of training cases and irrelevant moderators.
+However, differences between the algorithms were generally small.
 
@@
 Note, however, that this is likely due to the fact that the data simulated with a cubic model are analyzed with a linear model, and thus,  
-was the estimated model. This was mainly because the algorithms overestimated $\tau^{2}$ most when the model contained cubic terms.
+was the estimated model.
+**met brma zouden we de kwadratische en kubieke termen mee kunnen nemen en penalizen in het model.
+Misschien noemen als optie?** This was mainly because the algorithms overestimated $\tau^{2}$ most when the model contained cubic terms.
 No differences between algorithms in the effect of design factors were observed.
@@
 This provides strong evidence that BRMA with a horseshoe prior is generally preferable when the goal is to obtain findings that generalize to new data.
+**In mijn ogen waren de verschillen in performance niet heel groot, dus ik vraag me af of het nu niet iets te sterk is opgeschreven.
+Maar jij bent meer bezig geweest met de simulatie, dus mogelijk zie ik iets over het hoofd.**
 
@@
 This code also enables researchers to conduct Monte Carlo power analyses for applied research.
-Another limitation is that the present study did not examine the effect of multicolinear predictors.
-Regularizing estimators typically have an advantage over OLS regression in the presence of multicolinearity;
+Another limitation is that the present study did not examine the effect of multicollinear predictors.
+Regularizing estimators typically have an advantage over OLS regression in the presence of multicollinearity;
 future research ought to examine whether this also applies to BRMA.
@@
 One future direction of research is thus to develop a frequentist estimator for regularized meta-regression.
+Additionally, the current implementation relies on 95% credible intervals to select relevant moderators.
+However, these marginal credible intervals can behave differently compared to the joint credible intervals (Piironen, Betancourt, Simpson & Vehtari, 2017).
+A second future direction of research is therefore to implement more advanced selection procedures, such as projection predictive variable selection (Piironen & Vehtari, 2016).
 
@@
 we suggest using credible intervals, which are computationally less expensive.
-**SARA: Wel of niet nog OLS RMA doen met enkel de significante predictoren van de BRMA?**
+**SARA: Wel of niet nog OLS RMA doen met enkel de significante predictoren van de BRMA?** **nee**
 

### 2021-12-21 paper/manuscript.Rmd
updated references

@@
 Penalized regression, by contrast, adds a penalty term to the RSS.
-One commonly used penalty is the L1-norm of the regression coefficients, or LASSO penalty (Tibshirani, 1996),
+One commonly used penalty is the L1-norm of the regression coefficients, or LASSO penalty ([@tibshirani1996]),
 which corresponds to the sum of their absolute values.
@@
 
-Many different prior distributions exist that have specific properties that enable them to shrink small regression coefficients towards zero, while keeping substantial coefficients large (van Erp, Oberski & Mulder, 2019).
+Many different prior distributions exist that have specific properties that enable them to shrink small regression coefficients towards zero, while keeping substantial coefficients large ([@vanErpOberskiMulder2019]).
 Some prior distributions have been shown to result in exactly the same solutions as classical, frequentist penalties, such as the LASSO.
-Specifically, placing independent Laplace (i.e., double exponential) priors on the regression coefficients results in posterior modes that are equal to the lasso estimates (Park and Casella, 2008).
+Specifically, placing independent Laplace (i.e., double exponential) priors on the regression coefficients results in posterior modes that are equal to the lasso estimates ([@ParkCasella2008]).
 In addition, many prior distributions have been developed and investigated specifically for the purpose of providing good shrinkage properties, meaning that the prior pulls small regression coefficients towards zero, without exerting any influence on substantial regression coefficients.
-A popular prior in this regard is the horseshoe prior (Carvalho et al.
-2010).
+A popular prior in this regard is the horseshoe prior ([@CarvalhoPolsonScott2010]).
 An advantage of the horseshoe prior compared to the lasso is the fact that it has heavier tails.
@@
 ### Implementation
-The brma function uses Stan (Stan development team) to fit the models.
+The brma function uses Stan ([@StanManual]) to fit the models.
 Stan is a probabilistic programming language that uses a Hamiltonian Monte Carlo algorithm to sample from the posterior distribution.
@@
 
-Currently, the brma function supports two priors: the LASSO and the regularized horseshoe. We have precompiled the models with these two priors using brms (brms ref).
+Currently, the brma function supports two priors: the LASSO and the regularized horseshoe. We have precompiled the models with these two priors using brms ([@brms]).
 
@@
 
-For the horseshoe prior, we use an extension proposed by Piironen and Vehtari (2017) called the regularized horseshoe:
+For the horseshoe prior, we use an extension proposed by [@PiironenVehtari2017b] called the regularized horseshoe:
 
@@
 Additionally, the current implementation relies on 95% credible intervals to select relevant moderators.
-However, these marginal credible intervals can behave differently compared to the joint credible intervals (Piironen, Betancourt, Simpson & Vehtari, 2017).
-A second future direction of research is therefore to implement more advanced selection procedures, such as projection predictive variable selection (Piironen & Vehtari, 2016).
+However, these marginal credible intervals can behave differently compared to the joint credible intervals ([@PiironenEtal2017]).
+A second future direction of research is therefore to implement more advanced selection procedures, such as projection predictive variable selection ([@PiironenVehtari2017a]).
 

### 2021-12-22 R/brma.R
Fix multilevel and documentation

@@ -153,6 +153,7 @@ brma <- function(x, ...){
 
 #' @method brma formula
 #' @export
+#' @rdname brma
 brma.formula <-
   function(formula,
            data,
@@ -176,7 +177,7 @@ brma.formula <-
       data[[vi_column]] <- NULL
     }
     if(is.null(study)){
-      study <- 1:nrow(data)
+      study <- 1
     } else {
       if(inherits(study, "character")){
         if(!study %in% names(data)) stop("Argument 'study' is not a column of 'data'.")
@@ -232,6 +233,7 @@ brma.formula <-
 
 #' @method brma default
 #' @export
+#' @rdname brma
 brma.default <-
   function(Y,
            X,
@@ -270,6 +272,9 @@ brma.default <-
     }
     # Check if standardize is valid
     if(!length(standardize) == 2) stop("Argument 'standardize' must be a list with two elements: list(center = c(mean(X1), mean(X2), mean(X...)), scale = c(sd(X1), sd(X2), sd(X...))).")
+    if(!(length(standardize[[1]] == ncol(X) & length(standardize[[2]] == ncol(X))))){
+      stop("Both elements of argument 'standardize' must be as long as the number of predictors.")
+    }
     Xunscale <- do.call(unscale, c(list(x = X), standardize))
     names(standardize) <- c("means_X", "sds_X")
     # Prepare standat for study-level data

### 2021-12-22 paper/manuscript.Rmd

@@
 This leads to a problem known as the "curse of dimensionality": the number of candidate moderators is large relative to the number of cases in the data.
+Such cases do not fit comfortably into the
+classic meta-analysis paradigm, which, like any regression-based approach, requires a
+high number of cases per parameter. 
 Between-studies differences thus present a non-trivial challenge to data aggregation
@@
 It is important to note that some iterative methods do not produce a solution when they fail to converge after a predetermined amount of iteration.-->
-In contrast to a regularized analysis technique, this estimator produces low bias, which means that the average value of the estimated regression coefficients and residual heterogeneity is close to their true values (Panityakul et al., 2013; Hardy & Thompson, 1996).
-However, due to the bias-variance tradeoff, this bias comes at the cost of high variance, meaning that the results might not generalize to a new sample.
-Regularization can offer a solution to this problem.
+This estimator has low bias, which means that the average value of the estimated regression coefficients and residual heterogeneity is close to their true values (Panityakul et al., 2013; Hardy & Thompson, 1996).
+However, this bias comes at the cost of higher variance, which means that the estimated values of a population parameter vary more from one sample to the next. 
+In practice, an estimator with higher variance generalizes less well to new data.
+This phenomenon is known as the *bias-variance tradeoff*.
+Regularization increases bias to reduce variance, and thus produces more generalizable estimates.
 <!--It needs a starting estimation of $\tau^{2}$, which is usually estimated by one of the non-iterative methods (Viechtbauer \& López-López, 2015).
@@
 
-Where $\lambda$ is a tuning parameter that determines how influential the penalty term will be.
+Because the penalty term is a function of the regression coefficients,
+the optimizer is incentivized to keep the regression coefficients as small as possible.
+In this equation, $\lambda$ is a tuning parameter that determines how influential the penalty term will be.
 If $\lambda$ is zero, the shrinkage penalty has no impact at all and the penalized regression will produce the OLS estimates.
@@
 Results indicated that the overall $R^2_{test}$ was highest for BRMA with a horseshoe prior and lowest for RMA, see \@ref(tab:tabr2).
-This difference was driven in part by the fact that explained variance was somewhat higher for the BRMA models when the true effect was not null **moet zijn null?**, and by the fact that RMA had larger negative explained variance when the true effect was equal to zero **moet zijn not equal to zero?** (i.e., there was no effect to detect).**deze statements lijken niet overeen te komen met de tabel**
+This difference was driven in part by the fact that explained variance was somewhat higher for the BRMA models when the true effect was non-zero (i.e., in the presence of a population effect),
+and by the fact that RMA had larger negative explained variance when the true effect was equal to zero (i.e., there was no population effect to detect).
 
@@
 Conversely, RMA had relatively poor predictive performance on average, and was more responsive to increases in the number of training cases and irrelevant moderators.
-However, differences between the algorithms were generally small.
+<!--However, differences between the algorithms were generally small.
+CJ: Niet mee eens; de verschillen zijn misschien klein in termen van de substantieve interpretatie van R2, maar de grootte van dat verschil hangt af van de gebruikte simulatie condities.
+Je kan dus een groter verschil aantonen als je daarmee gaat spelen, en een situatie opzoekt die ongunstiger is voor RMA.
+Belangrijker is dat we uberhaupt een consequent voordeel van BRMA over RMA aantonen-->
 
@@
 we suggest using credible intervals, which are computationally less expensive.
-**SARA: Wel of niet nog OLS RMA doen met enkel de significante predictoren van de BRMA?** **nee**
 

### 2021-12-23 paper/manuscript.Rmd
Improve manuscript after Sara's additions

@@
 
-bibliography      : ["r-references.bib"]
+bibliography      : ["r-references.bib", "references.bib", "sara-references.bib"]
 
@@
 for example, the *fixed effect* model assumes that all observed effect sizes reflect one underlying true population effect size.
-This assumption is well-suited to the situation where effect sizes from close replication studies are meta-analyzed [@higgins_re-evaluation_2009, fabrigar_conceptualizing_2016, maxwell_is_2015]. 
+This assumption is well-suited to the situation where effect sizes from close replication studies are meta-analyzed [@higginsReevaluationRandomeffectsMetaanalysis2009, fabrigar_conceptualizing_2016, maxwell_is_2015].
 The *random effects* model, by contrast, assumes that population effect sizes follow a normal distribution.
 Each observed effect size provides information about the mean and standard deviation of this distribution of population effect sizes.
-This assumption is more appropriate when studies are conceptually similar and differences between them are random [@higgins_re-evaluation_2009, fabrigar_conceptualizing_2016, maxwell_is_2015].
+This assumption is more appropriate when studies are conceptually similar and differences between them are random [@higginsReevaluationRandomeffectsMetaanalysis2009, fabrigar_conceptualizing_2016, maxwell_is_2015].
 
@@
 Penalized regression, by contrast, adds a penalty term to the RSS.
-One commonly used penalty is the L1-norm of the regression coefficients, or LASSO penalty ([@tibshirani1996]),
+One commonly used penalty is the L1-norm of the regression coefficients, or LASSO penalty ([@hastieElementsStatisticalLearning2009]),
 which corresponds to the sum of their absolute values.
@@
 
+### Standardization
+
+Lasso regression puts constraints on the size of the coefficients associated to each variable.
+However, this value will depend on the magnitude of each variable.
+It is therefore necessary to center and reduce, or standardize, the variables.
+
+The result of centering the variables means that there is no longer an intercept. This applies equally to ridge regression, by the way.
+
 ### Bayesian estimation
@@
 ### Implementation
-The brma function uses Stan ([@StanManual]) to fit the models.
-Stan is a probabilistic programming language that uses a Hamiltonian Monte Carlo algorithm to sample from the posterior distribution.
-When running a Bayesian analysis in Stan it is important to ensure that the algorithm has converged to the posterior distribution in order for the results to be trusted.
-Stan offers automatic warnings and errors if this might not be the case.
-
-Currently, the brma function supports two priors: the LASSO and the regularized horseshoe. We have precompiled the models with these two priors using brms ([@brms]).
-
+
+Bayesian penalized meta-analysis is implemented in the function `brma()` in the R-package `pema`.
+For estimation, it depends on Stan, a probabilistic programming language that uses Hamiltonian Monte Carlo to sample from the posterior distribution ([@StanManual]).
+Being written in C++, Stan is computationally efficient, but models must be compiled prior to estimation.
+This results in substantial computational overhead.
+To avoid this overhead, `pema` uses pre-compiled models corresponding to random-effects and three-level meta-regression, with and without an intercept.
+Future updates may bring additional models.
+At the time of writing, `brma()` supports two priors: the LASSO and the regularized horseshoe.
 The LASSO prior is implemented as follows:
+<!-- CJ: Sara, kan jij checken of La de juiste notatie is voor de Laplace prior? -->
 
 $$
-\beta_{j} \sim \text{double exponential}(0, \frac{s}{lambda})
+\beta_{j} \sim \text{La}(0, \frac{s}{\lambda})
 $$
-
-and requires the specification of a global scale parameter $s$ and an inverse-tuning parameter $\lambda$.
-By default, the global scale is set to 1 and the inverse-tuning parameter is given a chi-square prior with degrees of freedom equal to 1.
-
-For the horseshoe prior, we use an extension proposed by [@PiironenVehtari2017b] called the regularized horseshoe:
+where $s$ is a global scale parameter, and $\lambda$ is an inverse-tuning parameter.
+By default in `brma()`, the global scale parameter is set to 1,
+and the inverse-tuning parameter is given a $\chi^2$ prior with 1 degree of freedom.
+Its value is thus optimized during model estimation.
+
+The implementation of the horseshoe prior is based on the regularized horseshoe proposed by @PiironenVehtari2017b:
+<!-- CJ: Sara, Kan jij checken wat de juiste notatie is voor "half-t"? -->
 
 $$
-\beta_{j} \sim \text{normal}(0, \tilde{\tau}_j^2\lambda) \text{, with } \tilde{\tau}_j^2 = \frac{c^2 \tau_j^2}{c^2 + \lambda^2 \tau_j^2} \\
-\lambda \sim \text{half-t}(\nu_1, 0, \lambda^2_0) \\
-\tau_j \sim \text{half-t}(\nu_2, 0, 1) \\
-c^2 \sim \text{inverse-gamma}(\frac{\nu_3}{2}, \frac{\nu_3 s^2}{2})
+\begin{aligned}
+\beta_{j} &\sim N(0, \tilde{\tau}_j^2\lambda) \text{, with } \tilde{\tau}_j^2 = \frac{c^2 \tau_j^2}{c^2 + \lambda^2 \tau_j^2}\\
+\lambda &\sim \text{half-t}(\nu_1, 0, \lambda^2_0)\\
+\tau_j &\sim \text{half-t}(\nu_2, 0, 1)\\
+c^2 &\sim \Gamma^{-1}(\frac{\nu_3}{2}, \frac{\nu_3 s^2}{2})
+\end{aligned}
 $$
-
-This extension is more numerically stable in certain cases.
-In addition, it allows the user to explicitly include prior information regarding the number of relevant moderators by setting the argument par_ratio to the ratio of the expected number of non-zero coefficients to the expected number of zero coefficients.
-If this information is not available, the user should specify scale_global ($\lambda^2_0$) which affects the overall shrinkage of the prior, with smaller values resulting in more shrinkage (default = 1).
-In addition, the regularized horseshoe has two degrees of freedom parameters ($\nu_1$ and $\nu_2$) which default to 1.
-Increasing the degrees of freedom parameters results in a prior with lighter tails, which is strictly no longer a horseshoe prior.
-However, the lighter tails might be needed in certain cases to attain convergence.
-The regularized horseshoe differs from the horseshoe in the specification of a finite "slab".
-This ensures at least some regularization of large coefficients and as a consequence, more stable results.
+This extension of the horseshoe is more numerically stable in certain cases.
+In addition, it allows the user to explicitly include prior information regarding the expected number of relevant moderators by setting the argument par_ratio to the ratio of the expected number of non-zero coefficients to the expected number of zero coefficients.
+<!-- CJ: Je spreekt hier over het argument par_ratio van de functie in Stan.
+Maar hier in de tekst verwacht ik uitleg over de formule.
+Zien we par_ratio terug in die formule?-->
+In this formula, $\lambda^2_0$ is a global scale parameter that affects the overall shrinkage of the prior, with smaller values resulting in more shrinkage. The default value in `brma()` is 1. 
+The thickness of the tails is controlled by two degrees of freedom parameters, $\nu_1$ and $\nu_2$, which default to 1 in `brma()`.
+Increasing these degrees of freedom parameters results in a prior with lighter tails,
+which is strictly no longer a horseshoe prior.
+However, in certain cases<!-- Sara, wat voor cases?--> these lighter tails can aid model convergence. 
+The regularized horseshoe differs from the standard horseshoe in the specification of a finite "slab". This slab ensures at least some regularization of large coefficients and as a consequence,
+more stable results.
 This slab is governed by a degrees of freedom parameter ($\nu_3$, set to 4) and a scale parameter ($s$, set to 1).
-
-We have chosen all default settings for the hyperparameters such that the values are reasonable in most applications.
+<!--Sara, eigenlijk is het niet helemaal duidelijk wat al deze nummers doen.
+Kunnen we een interactieve plot maken waarmee gebruikers kunnen zien hoe aanpassingen de vorm van de prior beinvloeden?-->
+
+Default settings for these hyperparameters in `brma()` were chosen such that the values are reasonable in most applications.
 However, in a Bayesian analysis it is good practice to perform a prior sensitivity analysis in which different hyperparameters are chosen and the model is rerun to see if this leads to different results.
-
-Unlike the classical frequentist lasso, Bayesian regularized estimation cannot estimate coefficients to be exactly equal to zero.
-Therefore, some approach is needed to select variables post-estimation.
-the brma funciton currently uses credible intervals (the Bayesian counterpart of confidence intervals) to do so, with a moderator being selected if the 95% credible interval excludes zero.
+This is particularly important when the sample is small, as the prior is more influential in this case.
+
+Unlike the frequentist LASSO algorithm, Bayesian regularized estimation cannot set coefficients to be exactly equal to zero.
+Therefore, variables must be selected post-estimation.
+One way to do so is by the use of probability intervals, the Bayesian counterpart of confidence intervals, with a moderator being selected if, for example, a 95% interval excludes zero.
+The present study considers two types of intervals:
+The credible interval, which is obtained by taking the 2.5% and 97.5% quantiles of the samples of the posterior, and the highest posterior density interval, which is the narrowest possible interval that contains 95% of the probability mass.
 
@@
 <!--                   es = rep(c(".2", ".5", ".8"), each = 1000)) -->
-
 <!-- ggplot(dat, aes(x, y, color = es))+geom_smooth() -->
+
 # Results
 
-The RMA algorithm failed to converge for `r out$missing` replications, all of which were characterized by low number of cases ($k \leq 40$) and high effect sizes $\beta \geq .5$.
+Any iterative algorithm is susceptible to convergence problems.
+In such cases, the BRMA algorithms provide warning messages,
+but still return samples from the posterior.
+We were thus able to use all iterations of the BRMA algorithms,
+although some of these may have failed to converge and thus have poor performance.
+The RMA algorithm failed to converge more regularly, however, in which case the process terminates with an error.
+To handle these contingencies, we automated some of the steps recommended [on the `metafor` website](https://www.metafor-project.org/doku.php/tips:convergence_problems_rma).
+Despite this, `r out$missing` replications of the RMA algorithm still failed to converge.
+All of these were characterized by low number of cases ($k \leq 40$) and high effect sizes $\beta \geq .5$.
 These cases were omitted from further analysis.
-**was er volledige convergence voor brma in alle replicaties? Dat heb ik zelf namelijk nog nooit meegemaakt.**
 
@@
 was the estimated model.
-**met brma zouden we de kwadratische en kubieke termen mee kunnen nemen en penalizen in het model.
-Misschien noemen als optie?** This was mainly because the algorithms overestimated $\tau^{2}$ most when the model contained cubic terms.
+This was mainly because the algorithms overestimated $\tau^{2}$ most when the model contained cubic terms.
 No differences between algorithms in the effect of design factors were observed.
@@
 Across all conditions, BRMA with a horseshoe prior achieved the highest average predictive performance, and within each data set, BRMA with a horseshoe prior most often had the best predictive performance (in `r round(whichhi[1]*100)`% of replications).
-This provides strong evidence that BRMA with a horseshoe prior is generally preferable when the goal is to obtain findings that generalize to new data.
-**In mijn ogen waren de verschillen in performance niet heel groot, dus ik vraag me af of het nu niet iets te sterk is opgeschreven.
-Maar jij bent meer bezig geweest met de simulatie, dus mogelijk zie ik iets over het hoofd.**
+Based on these findings, we would recommend using BRMA with a horseshoe prior when the goal is to obtain findings that generalize to new data.
+<!-- **In mijn ogen waren de verschillen in performance niet heel groot, dus ik vraag me af of het nu niet iets te sterk is opgeschreven.
+Maar jij bent meer bezig geweest met de simulatie, dus mogelijk zie ik iets over het hoofd.** -->
 
@@
 Together, these results suggest that BRMA has superior predictive performance and specificity, and provides relatively unbiased estimates of residual heterogeneity, relative to RMA.
+
+We examined the effect of several violations of model assumptions, including simulating data from a cubic model, and then analyzing these data with a linear model.
+In applied research, it is often not known what the true shape of the association between a moderator and effect size is.
+Thus, model mis-specification is likely to occur.
+One advantage of BRMA is that it can accommodate more moderators than RMA and has superior specificity.
+This allows researchers to specify a more flexible model to account for potential misspecification, with less concern for overfitting and non-convergence.
+For example, researchers could add polynomials of continuous variables with suspected non-linear effects, or interactions between predictors.
 
@@
 
+When estimating the model, it is important to ascertain that the algorithm has converged before interpreting the results.
+Stan, the computational back-end of `brma()`, should return warnings and errors if there are indicationsof non-convergence.
+<!-- Sara, wat kan men nog meer doen om convergence te checken?
+Iets met trace plots?
+Alle standaard plots voor stan-model objecten zijn beschikbaar, dankzij de functie `as.stan()`.
+Misschien kan je wat tips geven hier?
+-->
+
 When reporting results, researchers should substantiate their decision to explore heterogeneity on both subjective and objective grounds.
@@
 
+BRMA may not be the best solution for every situation.
+Several trade-offs must be made to decide what method is most appropriate.
+Firstly, the fact that BRMA has high predictive performance compared to RMA suggests that it is a particularly suitable technique when a researcher intends to obtain results that will generalize beyond the sample at hand, and is willing to accept some bias in parameter estimates.
+Conversely, RMA might be more suitable when the goal is to describe the sample at hand in an unbiased manner, with less concern for generalizability to future studies.
+Secondly, the fact that BRMA has high specificity compared to RMA suggests that it is a suitable technique when a researcher seeks to eliminate irrelevant moderators at the cost of increasing the Type II error rate.
+Conversely, RMA might be more suitable when the researcher seeks to identify relevant moderators, at the cost of increasing the Type I error rate.
+If many moderators have been coded, and many of them are expected to be irrelevant, then BRMA may thus be prererable.
+Thirdly, there may be pragmatic reasons for preferring BRMA over RMA.
+For example, if a dataset is small, or the number of moderators is high relative to the number of cases,
+RMA models may prove to be empirically under-identified.
+This can be indicated by convergence problems.
+In such cases, Bayesian estimation may converge on a solution where frequentist estimation does not [@kohliFittingLinearLinearPiecewise2015].
+Similarly, BRMA may perform better in the presence of multicolinearity among predictors,
+which can be examined using the function `vif()` in the R-package `metafor`.
+Values exceeding 5 are cause for concern.
+Multicolinearity increases the variance of regression coefficients.
+BRMA may have an advantage here, because the regularizing priors restrict variance.
+If multicolinearity is observed, researchers might thus prefer BRMA over RMA.
+
 # Conclusion

### 2021-12-23 R/brma.R

@@ -176,14 +176,16 @@ brma.formula <-
       vi <- data[[vi]]
       data[[vi_column]] <- NULL
     }
-    if(is.null(study)){
-      study <- 1
-    } else {
+    if(!is.null(study)){
       if(inherits(study, "character")){
         if(!study %in% names(data)) stop("Argument 'study' is not a column of 'data'.")
         study_column <- study
-        study <- data[[study]]
+        cl[["study"]] <- data[[study]]
         data[[study_column]] <- NULL
+      } else {
+        if(!length(study) == nrow(data)){
+          stop("Argument 'study' must be a character string referencing a column in 'data', or a vector of study IDs with length equal to the number of rows in 'data'.")
+        }
       }
     }
     # Make model matrix
@@ -220,7 +222,6 @@ brma.formula <-
     cl[["Y"]] <- Y
     cl[["X"]] <- X
     cl[["vi"]] <- vi
-    cl[["study"]] <- study
     cl[["prior"]] <- prior
     cl[["mute_stan"]] <- mute_stan
     cl[["standardize"]] <- standardize
@@ -238,7 +239,7 @@ brma.default <-
   function(Y,
            X,
            vi,
-           study,
+           study = NULL,
            prior,
            mute_stan = TRUE,
            standardize,

### 2021-12-23 R/plot_prior.R

@@ -1,0 +1,10 @@
+plot_prior <- function(method = c("hs", "lasso"),
+                       prior = switch(method,
+                                      "lasso" = c(df = 1, scale = 1),
+                                      "hs" = c(df = 1, df_global = 1, df_slab = 4, scale_global = 1, scale_slab = 1, par_ratio = NULL)),
+                       iter = 1000){
+  smpls <- suppressWarnings(sampling(object = pema:::stanmodels[[c("lasso_prior", "hs_prior")[(method[1] == "hs")+1]]], data = as.list(prior), chains = 1, iter = 10000, warmup = 0, show_messages = FALSE, verbose = FALSE, refresh = 0))
+  plot(density(smpls@sim$samples[[1]]$b), main = c("Lasso prior", "Horseshoe prior")[(method == "hs")+1],
+       xlab = paste0("Samples: ", iter, ", ", paste0(names(prior), " = ", prior, collapse = ", ")),
+       xlim = c(-5, 5))
+}

### 2021-12-23 R/stanmodels.R

@@ -1,17 +1,19 @@
 # Generated by rstantools.  Do not edit by hand.
 
 # names of stan models
-stanmodels <- c("horseshoe_MA", "horseshoe_MA_ml", "horseshoe_MA_ml_noint", "horseshoe_MA_noint", "lasso_MA", "lasso_MA_ml", "lasso_MA_ml_noint", "lasso_MA_noint")
+stanmodels <- c("horseshoe_MA", "horseshoe_MA_ml", "horseshoe_MA_ml_noint", "horseshoe_MA_noint", "hs_prior", "lasso_MA", "lasso_MA_ml", "lasso_MA_ml_noint", "lasso_MA_noint", "lasso_prior")
 
 # load each stan module
 Rcpp::loadModule("stan_fit4horseshoe_MA_mod", what = TRUE)
 Rcpp::loadModule("stan_fit4horseshoe_MA_ml_mod", what = TRUE)
 Rcpp::loadModule("stan_fit4horseshoe_MA_ml_noint_mod", what = TRUE)
 Rcpp::loadModule("stan_fit4horseshoe_MA_noint_mod", what = TRUE)
+Rcpp::loadModule("stan_fit4hs_prior_mod", what = TRUE)
 Rcpp::loadModule("stan_fit4lasso_MA_mod", what = TRUE)
 Rcpp::loadModule("stan_fit4lasso_MA_ml_mod", what = TRUE)
 Rcpp::loadModule("stan_fit4lasso_MA_ml_noint_mod", what = TRUE)
 Rcpp::loadModule("stan_fit4lasso_MA_noint_mod", what = TRUE)
+Rcpp::loadModule("stan_fit4lasso_prior_mod", what = TRUE)
 
 # instantiate each stanmodel object
 stanmodels <- sapply(stanmodels, function(model_name) {

### 2021-12-23 src/RcppExports.cpp

@@ -16,20 +16,24 @@ RcppExport SEXP _rcpp_module_boot_stan_fit4horseshoe_MA_mod();
 RcppExport SEXP _rcpp_module_boot_stan_fit4horseshoe_MA_ml_mod();
 RcppExport SEXP _rcpp_module_boot_stan_fit4horseshoe_MA_ml_noint_mod();
 RcppExport SEXP _rcpp_module_boot_stan_fit4horseshoe_MA_noint_mod();
+RcppExport SEXP _rcpp_module_boot_stan_fit4hs_prior_mod();
 RcppExport SEXP _rcpp_module_boot_stan_fit4lasso_MA_mod();
 RcppExport SEXP _rcpp_module_boot_stan_fit4lasso_MA_ml_mod();
 RcppExport SEXP _rcpp_module_boot_stan_fit4lasso_MA_ml_noint_mod();
 RcppExport SEXP _rcpp_module_boot_stan_fit4lasso_MA_noint_mod();
+RcppExport SEXP _rcpp_module_boot_stan_fit4lasso_prior_mod();
 
 static const R_CallMethodDef CallEntries[] = {
     {"_rcpp_module_boot_stan_fit4horseshoe_MA_mod", (DL_FUNC) &_rcpp_module_boot_stan_fit4horseshoe_MA_mod, 0},
     {"_rcpp_module_boot_stan_fit4horseshoe_MA_ml_mod", (DL_FUNC) &_rcpp_module_boot_stan_fit4horseshoe_MA_ml_mod, 0},
     {"_rcpp_module_boot_stan_fit4horseshoe_MA_ml_noint_mod", (DL_FUNC) &_rcpp_module_boot_stan_fit4horseshoe_MA_ml_noint_mod, 0},
     {"_rcpp_module_boot_stan_fit4horseshoe_MA_noint_mod", (DL_FUNC) &_rcpp_module_boot_stan_fit4horseshoe_MA_noint_mod, 0},
+    {"_rcpp_module_boot_stan_fit4hs_prior_mod", (DL_FUNC) &_rcpp_module_boot_stan_fit4hs_prior_mod, 0},
     {"_rcpp_module_boot_stan_fit4lasso_MA_mod", (DL_FUNC) &_rcpp_module_boot_stan_fit4lasso_MA_mod, 0},
[…]

### 2021-12-23 R/plot_prior.R
add prior plots

@@ -8,3 +8,45 @@ plot_prior <- function(method = c("hs", "lasso"),
        xlab = paste0("Samples: ", iter, ", ", paste0(names(prior), " = ", prior, collapse = ", ")),
        xlim = c(-5, 5))
 }
+
+## Plotting the shrinkage priors in pema
+library(ggplot2)
+library(tidyr)
+library(rmutil)
+library(LaplacesDemon)
+
+set.seed(23122021)
+
+ndraws <- 1e+05
+
+## lasso
+lasso <- rmutil::rlaplace(ndraws, m=0, s=0.5)
+
+## regularized horseshoe
+reg.hs <- rep(NA, ndraws)
+for(i in 1:ndraws){
+  c2 <- LaplacesDemon::rinvgamma(1, shape=0.5, scale=1)
+  lambda <- LaplacesDemon::rhalfcauchy(1, scale=1)
+  tau <- LaplacesDemon::rhalfcauchy(1, scale=1)
+  lambda2_tilde <- c2 * lambda^2/(c2 + tau^2*lambda^2)
+  reg.hs[i] <- rnorm(1, 0, sqrt(tau^2*lambda2_tilde))
+}
+
+## plot
+df.comb <- data.frame(lasso, reg.hs)
+df.long <- gather(df.comb, Prior, value) # long format
+df.long$Prior <- factor(df.long$Prior)
+levels(df.long$Prior) <- list("Lasso"="lasso", "Horseshoe"="reg.hs")
+
+p1 <- ggplot(df.long, aes(x = value, linetype = Prior)) +
+  stat_density(geom = "line", position = "identity") +
+  scale_linetype_manual(values = c(1, 2))
+p1
+
+# xlim removes values outside the range, coord_cartesian does not, but behaves strange sometimes
+# solution: restrict range with xlim first & then use coord-cartesian
+p2 <- ggplot(df.long, aes(x = value, linetype = Prior)) +
+  stat_density(geom = "line", position = "identity") +
+  scale_linetype_manual(values = c(1, 2)) +
+  xlim(-10,10) + coord_cartesian(xlim=c(-5,5))
+p2

### 2021-12-23 paper/manuscript.Rmd
draft paragraphs about standardization and intercepts

@@
 
-### Standardization
-
-Lasso regression puts constraints on the size of the coefficients associated to each variable.
+### Standardizing predictors
+
+<!-- Eli? -->
+<!-- Staclexchange: Lasso regression puts constraints on the size of the coefficients associated to each variable.
 However, this value will depend on the magnitude of each variable.
 It is therefore necessary to center and reduce, or standardize, the variables.
-
-The result of centering the variables means that there is no longer an intercept. This applies equally to ridge regression, by the way.
+-->
+<!-- * Eli, kan jij het algemene principe van standardization hier uitleggen, met een paar referenties?
+In de volgende paragraaf over intercepts moet ook nog een referentie, over wel/niet standaardizeren van dummies.-->
+<!-- * In BRMA werk het als volgt: -->
+<!--     + By default, all variables are normalized. -->
+<!--     + The penalized model (without an intercept) is estimated on the normalized data -->
+<!--     + The intercept is then restored to the original scale by applying  -->
+<!--     $b_0 = b_{0z} - \mathbf{b}_z\frac{\bar{\mathbf{x}}}{\mathbf{s}_x}$ -->
+<!--     Where b_0 is the intercept, b_0z is the intercept for the normalized predictors, b_z is the vector of regression coefficients for the normalized predictors, bar x is the vector of means of X, and s_x is the vector of standard deviations of x -->
+<!--     + The regression coefficients are restored to the original scale by applying  -->
+<!--     $\mathbf{b} = \mathbf{b}_z\mathbf{s}_x$ -->
+<!-- * Leg vervolgens uit dat mensen dummies misschien niet willen standaardizeren -->
+<!-- * Gebruikers kunnen de default standaardization overschrijven door een aantal van de variabelen handmatig te standaardizeren, en de vector met means en vector met SDs handmatig mee te geven via het argument `standardize = list(center = meanvec, scale = sdvec)`.
+Als ze een bepaalde variabele NIET willen standaardizeren moeten ze voor die variabele mean= 0 en sd= 1 meegeven.
+-->
+
+### Intercepts
+
+The standard linear model estimates an intercept, which reflects the expected value of the outcome when all predictors are equal to zero, and regression coefficients for the effect of moderators.
+In some cases, it may be desirable to omit the intercept.
+For example, if an analysis contains categorical predictors,
+these can be encoded as dummy variables, with values $x \in \{0, 1\}$.
+For a variable with $c$ categories, the number of dummy variables must be equal to $c-1$;
+the omitted category functions as a reference category, and its expected value is represented by the model intercept $b_0$.
+This so-called *regression specification* of a model may be useful when there is a meaningful reference category.
+For example, imagine a study on the effectiveness of interventions for specific phobia with two types of interventions: An industry-standard intervention, and a more recently developed one.
+In this case, it might make sense to code the industry standard intervention as the reference category,
+and dummy-code the new contender.
+The model will then estimate whether the new contended has an effect size significantly lower or higher than the industry standard.
+In other cases, there may not be a straightforward reference category.
+For example, imagine a study on the effectiveness of one intervention for specific phobia in two continents.
+In such cases, the average effect in both continents may be estimated by omitting the intercept, and including all $c$ dummy variables.
+This so-called *ANOVA specification* of a model estimates a mean for all dummy-coded categories.
+In BRMA, as in other R functions, one can use ANOVA specification by explicitly removing the intercept from the model formula; for example, if `yi` is the effect size and $C$ a categorical moderator, regression specification with $c-1$ dummies is specified as `yi ~ C`, and ANOVA specification with $c$ dummies is specified as `yi ~ -1 + C`.
+The appropriate standardization of dummy variables in penalized regression analyses is a topic of ongoing debate.
+Suffice it to say that, for greater interpretability, users may want the freedom to leave dummy variables unstandardized.
+This is possible in `brma()` by ...
 

### 2021-12-23 paper/manuscript.Rmd
quietstart [ci skip]

@@
 
-  Enter author note here.
+  Author contributions: CvL conceived of the method; wrote simulation, analysis,
+  and package code; and drafted the manuscript. SE implemented the method in
+  stan and contributed package code; contributed paragraphs and revised the
+  manuscript. EC wrote manuscript outline and contributed paragraphs; curated
+  existing lab notes; conducted literature research; performed initial analyses.
 

### 2021-12-23 R/brma.R

@@ -87,11 +87,11 @@
 #'   prior on the global shrinkage parameter \code{scale_global} defaults to 1
 #'   and can be decreased to achieve more shrinkage. Moreover, if prior
 #'   information regarding the number of relevant moderators is available, it is
-#'   recommended to include this information via the \code{par_rel} argument
-#'   by setting it to the expected number of relevant moderators. When \code{par_rel} is
-#'   specified, \code{scale_global} is ignored and instead based on the
-#'   available prior information. Contrary to the horseshoe prior, the
-#'   regularized horseshoe applies additional regularization on large
+#'   recommended to include this information via the \code{relevant_pars}
+#'   argument by setting it to the expected number of relevant moderators. When
+#'   \code{relevant_pars} is specified, \code{scale_global} is ignored and
+#'   instead based on the available prior information. Contrary to the horseshoe
+#'   prior, the regularized horseshoe applies additional regularization on large
 #'   coefficients which is governed by a Student's t prior with a
 #'   \code{scale_slab} defaulting to 2 and \code{df_slab} defaulting to 4.
 #'   This additional regularization ensures at least some shrinkage of large
@@ -128,11 +128,7 @@
 #'   tau2         # Numeric, estimated tau2
 #'   R2           # Numeric, estimated heterogeneity explained by the moderators
 #'   k            # Numeric, number of effect sizes
-#'   vi_column    # Optional, name of the column in the original data
-#'                # corresponding to vi
 #'   study        # Numeric vector with study id numbers
-#'   study_column # Optional, name of the column in the original data
-#'                # corresponding to study
 #' )
 #' ```
 #' @export
@@ -162,7 +158,7 @@ brma.formula <-
            standardize = TRUE,
            prior = switch(method,
                           "lasso" = c(df = 1, scale = 1),
-                          "hs" = c(df = 1, df_global = 1, df_slab = 4, scale_global = 1, scale_slab = 1, par_rel = NULL)),
+                          "hs" = c(df = 1, df_global = 1, df_slab = 4, scale_global = 1, scale_slab = 1, relevant_pars = NULL)),
            mute_stan = TRUE,
            #prior_only = FALSE,
            ...) {
@@ -255,10 +251,13 @@ brma.default <-
     }
     # Check validity of prior
     method <- "invalid"
[…]

### 2021-12-23 R/plot_prior.R

@@ -9,44 +9,44 @@ plot_prior <- function(method = c("hs", "lasso"),
        xlim = c(-5, 5))
 }
 
-## Plotting the shrinkage priors in pema
-library(ggplot2)
-library(tidyr)
-library(rmutil)
-library(LaplacesDemon)
-
-set.seed(23122021)
-
-ndraws <- 1e+05
-
-## lasso
-lasso <- rmutil::rlaplace(ndraws, m=0, s=0.5)
-
-## regularized horseshoe
-reg.hs <- rep(NA, ndraws)
-for(i in 1:ndraws){
-  c2 <- LaplacesDemon::rinvgamma(1, shape=0.5, scale=1)
-  lambda <- LaplacesDemon::rhalfcauchy(1, scale=1)
-  tau <- LaplacesDemon::rhalfcauchy(1, scale=1)
-  lambda2_tilde <- c2 * lambda^2/(c2 + tau^2*lambda^2)
-  reg.hs[i] <- rnorm(1, 0, sqrt(tau^2*lambda2_tilde))
-}
-
-## plot
-df.comb <- data.frame(lasso, reg.hs)
-df.long <- gather(df.comb, Prior, value) # long format
-df.long$Prior <- factor(df.long$Prior)
-levels(df.long$Prior) <- list("Lasso"="lasso", "Horseshoe"="reg.hs")
-
-p1 <- ggplot(df.long, aes(x = value, linetype = Prior)) +
-  stat_density(geom = "line", position = "identity") +
-  scale_linetype_manual(values = c(1, 2))
-p1
-
-# xlim removes values outside the range, coord_cartesian does not, but behaves strange sometimes
-# solution: restrict range with xlim first & then use coord-cartesian
-p2 <- ggplot(df.long, aes(x = value, linetype = Prior)) +
-  stat_density(geom = "line", position = "identity") +
-  scale_linetype_manual(values = c(1, 2)) +
-  xlim(-10,10) + coord_cartesian(xlim=c(-5,5))
-p2
+# ## Plotting the shrinkage priors in pema
+# library(ggplot2)
+# library(tidyr)
+# library(rmutil)
+# library(LaplacesDemon)
+#
+# set.seed(23122021)
+#
+# ndraws <- 1e+05
+#
+# ## lasso
+# lasso <- rmutil::rlaplace(ndraws, m=0, s=0.5)
+#
+# ## regularized horseshoe
+# reg.hs <- rep(NA, ndraws)
[…]

### 2021-12-24 paper/manuscript.Rmd
start standardization

@@
       - Programming back-end
+  - name: "Eli-Boaz Clapper"
+    affiliation: "1"
 affiliation:
@@
 
+In Lasso regression it is often preferred to equalize the scales of the predictors (REF).
+This is because $\lambda$, the regularization parameter, constrains the absolute magnitude of the coefficients that are dependent on the scales of the predictors.
+This leads to Lasso unfairly penalizing large coefficients that do not necessarily reflect importance (REF).
+Equalizing scales is usually done by setting the mean of all predictors to 0 and their variance to 1, a procedure known as standardization.
+This procedure transforms all elements in a predictor vector to Z-scores as follows:
+$\boldsymbol{Z} = \frac{\boldsymbol{X} - \mu_\boldsymbol{X}}{\sigma_\boldsymbol{X}}$
+where $\boldsymbol{X}$ is the vector of the predictor, $\mu_\boldsymbol{X}$ is its mean and $\sigma_\boldsymbol{X}$ is its standard deviation.
+
 ### Intercepts

### 2022-01-06 paper/manuscript.Rmd
update standardization

--- 2021-12-23 paper/manuscript.Rmd
@@
   - name: "Sara van Erp"
+    affiliation: "1"
+    role:
+      - Writing - Contributions and feedback
+      - Programming back-end
+  - name: "Eli-Boaz Clapper"
     affiliation: "1"
@@
 
-bibliography      : ["r-references.bib", "references.bib", "sara-references.bib"]
+bibliography      : ["r-references.bib", "references.bib", "sara-references.bib", "eli-references.bib"]
 
@@
 <!-- Eli? -->
-<!-- Staclexchange: Lasso regression puts constraints on the size of the coefficients associated to each variable.
-However, this value will depend on the magnitude of each variable.
-It is therefore necessary to center and reduce, or standardize, the variables.
--->
 <!-- * Eli, kan jij het algemene principe van standardization hier uitleggen, met een paar referenties?
@@
 -->
+
+Lasso often requires the scales of the predictors to be equalized ([@tibshirani1996]).
+This is because $\lambda$, the regularization parameter, penalizes the absolute magnitude of the coefficients that are dependent on the scales of the predictors.
+This leads to the Lasso unfairly penalizing larger coefficients that do not necessarily reflect importance (REF).
+For example, in the case of 2 or more equally important predictors, the coefficient of the predictor with the largest scale will be shrunk most.
+
+To equalize predictor scales, an often-used technique is standardization.
+Standardization sets the mean of all predictors to 0 and their variance to 1.
+It does so by transforming all cases in the predictor space $\boldsymbol{X}$ to Z-scores as follows:
+$$
+\mathbf{Z_{i}} = \frac{\mathbf{X}_i- \bar{\mathbf{X}}}{\mathbf{s_X}}
+$$
+where $\mathbf{X}$ is the matrix of predictors, $\bar{\mathbf{X}}$ is a vector of predictor means and $\mathbf{s_X}$ is a vector of standard deviations of the predictors.
+In BRMA, the predictors are standardized by default, on which the model is estimated.
+The function returns the estimated parameters in their original scales.
+This is achieved for the intercept by applying:
+$$
+b_0 = b_{0Z} - \mathbf{b}_Z\frac{\bar{\mathbf{X}}}{\mathbf{s}_X} \\
+$$
+where $b_0$ is the intercept, $b_{0Z}$ is the intercept for the normalized predictors and $\mathbf{b_Z}$ is the vector of regression coefficients for the normalized predictors.
+The regression coefficients are returned in their original scale by applying:
+$$
+\mathbf{b_X} = \frac{\mathbf{b_Z}}{\mathbf{s_X}}
+$$
+
+In the case of binary/dummy predictors,
+
+```{r}
+library(pema)
+?brma()
+X <- sample(0:1, 50, replace = T)
+scale(X)
+sd(X)
+Y <- rep(1, 50)
+sd(Y)
+
+```
 

### 2022-01-08 paper/manuscript.Rmd
standardize dummies

@@
 
-Lasso often requires the scales of the predictors to be equalized ([@tibshirani1996]).
-This is because $\lambda$, the regularization parameter, penalizes the absolute magnitude of the coefficients that are dependent on the scales of the predictors.
-This leads to the Lasso unfairly penalizing larger coefficients that do not necessarily reflect importance (REF).
+Penalized regression analyses often require the scales of the predictors to be equalized ([@tibshirani1996; @lee2015note]).
+This is because $\lambda$, the regularization parameter, penalizes the magnitude of the coefficients that are dependent on the scales of the predictors.
+This leads to the unfair penalization of larger coefficients that do not necessarily reflect importance ([@zou2006adaptive]).
 For example, in the case of 2 or more equally important predictors, the coefficient of the predictor with the largest scale will be shrunk most.
 
-To equalize predictor scales, an often-used technique is standardization.
+To equalize predictor scales, an often-used technique is standardization ([@gelman2008scaling]).
 Standardization sets the mean of all predictors to 0 and their variance to 1.
-It does so by transforming all cases in the predictor space $\boldsymbol{X}$ to Z-scores as follows:
-$$
-\mathbf{Z_{i}} = \frac{\mathbf{X}_i- \bar{\mathbf{X}}}{\mathbf{s_X}}
+It does so by transforming all observations in the predictor space $\boldsymbol{X}$ to Z-scores as follows:
+
+$$
+\mathbf{Z} = \frac{\mathbf{X}- \bar{\mathbf{X}}}{\mathbf{s_X}}
 $$
 where $\mathbf{X}$ is the matrix of predictors, $\bar{\mathbf{X}}$ is a vector of predictor means and $\mathbf{s_X}$ is a vector of standard deviations of the predictors.
-In BRMA, the predictors are standardized by default, on which the model is estimated.
-The function returns the estimated parameters in their original scales.
+`brma()` standardizes the predictors by default, on which the model is estimated.
+The function returns the estimated parameters back in their original scales.
 This is achieved for the intercept by applying:
+
 $$
@@
 The regression coefficients are returned in their original scale by applying:
+
 $$
@@
 
-In the case of binary/dummy predictors,
-
-```{r}
-library(pema)
-?brma()
-X <- sample(0:1, 50, replace = T)
-scale(X)
-sd(X)
-Y <- rep(1, 50)
-sd(Y)
-
-```
+There is some debate regarding the standardization of binary/dummy predictors in penalized regression ([@lee2015note]).
+Some suggest to always standardize dummy variables ([@tibshirani1997lasso]).
+However, standardizing binary predictors increases the absolute maximum values the predictor can take on which in some cases can make it more sensitive to the penalty function ([@harrell2001regression]).
+
+In any case, the default standardization option in `brma()` can be overwritten entirely by setting `standardize = False`.
+`brma()` also allows the user to standardize only some of the predictors.
+This is done by constructing a vector of means and a vector of standard deviations.
+These vectors contain the means and standard deviations of the predictors in their original scales, except for the predictors that **should not** be standardized.
+For the latter, a mean of 0 and a standard deviation of 1 must be passed.
+The predictors that need to be standardized should then be standardized manually.
+Finally, the mean and standard deviation vectors are passed to the `standardize` argument as follows: `standardize = list(center = MeanVector, scale = SdVector)`.
 

### 2022-01-09 paper/manuscript.Rmd
update standardization

@@
 This is because $\lambda$, the regularization parameter, penalizes the magnitude of the coefficients that are dependent on the scales of the predictors.
-This leads to the unfair penalization of larger coefficients that do not necessarily reflect importance ([@zou2006adaptive]).
-For example, in the case of 2 or more equally important predictors, the coefficient of the predictor with the largest scale will be shrunk most.
+This can lead to the unfair penalization of larger coefficients that do not necessarily reflect importance ([@zou2006adaptive]).
+To clarify, a regression parameter $\beta$ can be interpreted as the amount outcome $Y$ increases as predictor $X$ increases with 1 unit.
+This means that as $X$ is reduced by a factor of 10, its regression coefficient is increased by a factor of 10.
+So suppose the desire to predict running speed by a person`s height.
+If height is measured in kilometers, than a one unit increase in height, which is a one kilometer increase, will likely lead to a drastic increase in running speed.
+In penalized regression techniques, this high value for $\beta$ would then dominate the cost function, leaving coefficients of other predictors unregularized.
 
 To equalize predictor scales, an often-used technique is standardization ([@gelman2008scaling]).
-Standardization sets the mean of all predictors to 0 and their variance to 1.
+Standardization sets the mean of all predictors to 0 and their standard deviation to 1.
 It does so by transforming all observations in the predictor space $\boldsymbol{X}$ to Z-scores as follows:
@@
 Some suggest to always standardize dummy variables ([@tibshirani1997lasso]).
-However, standardizing binary predictors increases the absolute maximum values the predictor can take on which in some cases can make it more sensitive to the penalty function ([@harrell2001regression]).
+However, standardizing binary predictors increases the absolute maximum values the predictor can take on which in some cases can make its coefficient more sensitive to the penalty function ([@harrell2001regression]).
 

### 2022-01-09 paper/manuscript.Rmd
minor update

@@
 
-To equalize predictor scales, an often-used technique is standardization ([@gelman2008scaling]).
+Thus, to equalize predictor scales, a widely used technique is standardization ([@gelman2008scaling]).
 Standardization sets the mean of all predictors to 0 and their standard deviation to 1.
-It does so by transforming all observations in the predictor space $\boldsymbol{X}$ to Z-scores as follows:
+It does so by transforming all observations in the predictor space $\mathbf{X}$ to Z-scores as follows:
 
@@
 $$
-where $\mathbf{X}$ is the matrix of predictors, $\bar{\mathbf{X}}$ is a vector of predictor means and $\mathbf{s_X}$ is a vector of standard deviations of the predictors.
+where $\bar{\mathbf{X}}$ is a vector of predictor means and $\mathbf{s_X}$ is a vector of standard deviations of the predictors.
 `brma()` standardizes the predictors by default, on which the model is estimated.

### 2022-01-10 paper/manuscript.Rmd
minor commit

@@
 This can lead to the unfair penalization of larger coefficients that do not necessarily reflect importance ([@zou2006adaptive]).
-To clarify, a regression parameter $\beta$ can be interpreted as the amount outcome $Y$ increases as predictor $X$ increases with 1 unit.
-This means that as $X$ is reduced by a factor of 10, its regression coefficient is increased by a factor of 10.
+To clarify, a regression parameter $\beta$ can be interpreted as the amount outcome $\mathbf{Y}$ increases as predictor $\mathbf{X}$ increases with 1 unit.
+This means that as $\mathbf{X}$ is reduced by a factor of 10, its regression coefficient is increased by a factor of 10.
 So suppose the desire to predict running speed by a person`s height.
 If height is measured in kilometers, than a one unit increase in height, which is a one kilometer increase, will likely lead to a drastic increase in running speed.
-In penalized regression techniques, this high value for $\beta$ would then dominate the cost function, leaving coefficients of other predictors unregularized.
+In penalized regression techniques, this high value for $\beta$ would then dominate the penalty function, leaving coefficients of other predictors unregularized.
 
@@
 Standardization sets the mean of all predictors to 0 and their standard deviation to 1.
-It does so by transforming all observations in the predictor space $\mathbf{X}$ to Z-scores as follows:
+It does so by Z-transforming all predictors as follows:
 
@@
 where $\bar{\mathbf{X}}$ is a vector of predictor means and $\mathbf{s_X}$ is a vector of standard deviations of the predictors.
-`brma()` standardizes the predictors by default, on which the model is estimated.
+`brma()` standardizes the predictors by default on which the model is estimated.
 The function returns the estimated parameters back in their original scales.
@@
 $$
-where $b_0$ is the intercept, $b_{0Z}$ is the intercept for the normalized predictors and $\mathbf{b_Z}$ is the vector of regression coefficients for the normalized predictors.
+where $b_0$ is the intercept, $b_{0Z}$ is the intercept for the standardized predictors and $\mathbf{b_Z}$ is the vector of regression coefficients for the standardized predictors.
 The regression coefficients are returned in their original scale by applying:

### 2022-01-25 paper/manuscript.Rmd
Standardization Attempt 2
Second attempt at writing the piece on standardization.

@@
 
-Penalized regression analyses often require the scales of the predictors to be equalized ([@tibshirani1996; @lee2015note]).
+Penalized regression analyses often require the scales of the predictors to be equalized ([@tibshirani1996]).
 This is because $\lambda$, the regularization parameter, penalizes the magnitude of the coefficients that are dependent on the scales of the predictors.
-This can lead to the unfair penalization of larger coefficients that do not necessarily reflect importance ([@zou2006adaptive]).
+This can lead to the unfair penalization of larger coefficients that do not necessarily reflect importance ([@lee2015note]).
 To clarify, a regression parameter $\beta$ can be interpreted as the amount outcome $\mathbf{Y}$ increases as predictor $\mathbf{X}$ increases with 1 unit.
@@
 
-Thus, to equalize predictor scales, a widely used technique is standardization ([@gelman2008scaling]).
+To equalize predictor scales, a widely used technique is standardization ([@gelman2008scaling]).
 Standardization sets the mean of all predictors to 0 and their standard deviation to 1.
@@
 `brma()` standardizes the predictors by default on which the model is estimated.
-The function returns the estimated parameters back in their original scales.
+The function returns the estimated parameters back to their original scales.
 This is achieved for the intercept by applying:
@@
 where $b_0$ is the intercept, $b_{0Z}$ is the intercept for the standardized predictors and $\mathbf{b_Z}$ is the vector of regression coefficients for the standardized predictors.
-The regression coefficients are returned in their original scale by applying:
+The regression coefficients are returned to their original scale by applying:
 
@@
 
-There is some debate regarding the standardization of binary/dummy predictors in penalized regression ([@lee2015note]).
-Some suggest to always standardize dummy variables ([@tibshirani1997lasso]).
-However, standardizing binary predictors increases the absolute maximum values the predictor can take on which in some cases can make its coefficient more sensitive to the penalty function ([@harrell2001regression]).
-
-In any case, the default standardization option in `brma()` can be overwritten entirely by setting `standardize = False`.
+It is not always necessary or desirable to standardize predictors, however.
+The most straightforward instance is when predictors are already standardized or on the same scale for different reasons.
+In these cases standardization does not make scales more equal, nor the penalization more fair.
+
+Also, if the desire is to directly compare current research outcomes with prior research outcomes that did not standardize predictors, standardization in the current research would make penalization unequal across studies.
+
+Finally, standardization should be thought over when dealing with binary/dummy predictors ([@alkharusi2012categorical]).
+Some suggest to always standardize binary predictors ([@tibshirani1997lasso]).
+This makes that, irrespective of initial scaling, the binary predictor will be on the same scale as the continuous standardized predictors ([@gelman2008scaling]).
+However, standardizing binary predictors may decrease model interpretability ([@wissmann2007role]).
+Consider a regression problem including only a binary predictor $X$ that takes on values 0 and 1 predicting outcome $Y$.
+The intercept represents $\mathbb{E}(Y | X = 0)$ and the regression coefficient represents $\mathbb{E}(Y | X = 1)$, or the difference in means on $Y$ between conditions ([@alkharusi2012categorical]).
+By standardizing binary predictors, they lose 0 as a value to take on and both the intercept and its regression coefficient have no clear interpretation anymore, especially in multivariate cases ([@wissmann2007role]).
+
+Also note that there are multiple coding schemes for categorical predictors in penalized regression, but that the coding choice can affect model accuracy and interpretation ([@chiquet2016coding; @detmer2020note]).
+The standard option is to dummy code categorical predictors and standardize the dummies afterwards, dependent on considerations mentioned above.
+
+For all cases where standardization is undesired, the default standardization option in `brma()` can be overwritten entirely by setting `standardize = False`.
 `brma()` also allows the user to standardize only some of the predictors.
-This is done by constructing a vector of means and a vector of standard deviations.
-These vectors contain the means and standard deviations of the predictors in their original scales, except for the predictors that **should not** be standardized.
+This is done by constructing a vector of means and a vector of standard deviations of the predictors in their original scales, except for the predictors that **should not** be standardized.
 For the latter, a mean of 0 and a standard deviation of 1 must be passed.

### 2022-02-28 R/plot_prior.R
update 2022-02-28 11:42:53

@@ -1,9 +1,25 @@
+#' @title Plot Prior Distribution
+#' @description Plots the kernal density function of samples from a prior
+#' distribution with parameters defined in `prior`.
+#' @param method Character string, indicating which prior to sample from.
+#' Default: first element of `c("hs", "lasso")`.
+#' @param prior Numeric vector, specifying the prior to use. See [pema::brma]
+#' for more details.
+#' @param iter A positive integer specifying the number of iterations to sample.
+#' Default: 1000
+#' @return NULL, function is called for its side-effect of plotting to the
+#' graphics device.
+#' @examples
+#' plot_prior("lasso", iter = 10)
+#' @rdname plot_prior
+#' @importFrom rstan sampling
+#' @export
 plot_prior <- function(method = c("hs", "lasso"),
                        prior = switch(method,
                                       "lasso" = c(df = 1, scale = 1),
                                       "hs" = c(df = 1, df_global = 1, df_slab = 4, scale_global = 1, scale_slab = 1, par_ratio = NULL)),
                        iter = 1000){
-  smpls <- suppressWarnings(sampling(object = pema:::stanmodels[[c("lasso_prior", "hs_prior")[(method[1] == "hs")+1]]], data = as.list(prior), chains = 1, iter = 10000, warmup = 0, show_messages = FALSE, verbose = FALSE, refresh = 0))
+  smpls <- suppressWarnings(sampling(object = stanmodels[[c("lasso_prior", "hs_prior")[(method[1] == "hs")+1]]], data = as.list(prior), chains = 1, iter = iter, warmup = 0, show_messages = FALSE, verbose = FALSE, refresh = 0))
   plot(density(smpls@sim$samples[[1]]$b), main = c("Lasso prior", "Horseshoe prior")[(method == "hs")+1],
        xlab = paste0("Samples: ", iter, ", ", paste0(names(prior), " = ", prior, collapse = ", ")),
        xlim = c(-5, 5))

### 2022-02-28 paper/manuscript.Rmd
Revisions to eli's writing

--- 2022-01-10 paper/manuscript.Rmd
@@
       - Writing - Original Draft Preparation
-      - Programming front-end
+      - Programming front- and back-end
   - name: "Sara van Erp"
@@
       - Writing - Contributions and feedback
-      - Programming back-end
+      - Preliminary analyses
 affiliation:
@@
 
-Penalized regression analyses often require the scales of the predictors to be equalized ([@tibshirani1996; @lee2015note]).
-This is because $\lambda$, the regularization parameter, penalizes the magnitude of the coefficients that are dependent on the scales of the predictors.
-This can lead to the unfair penalization of larger coefficients that do not necessarily reflect importance ([@zou2006adaptive]).
-To clarify, a regression parameter $\beta$ can be interpreted as the amount outcome $\mathbf{Y}$ increases as predictor $\mathbf{X}$ increases with 1 unit.
-This means that as $\mathbf{X}$ is reduced by a factor of 10, its regression coefficient is increased by a factor of 10.
-So suppose the desire to predict running speed by a person`s height.
-If height is measured in kilometers, than a one unit increase in height, which is a one kilometer increase, will likely lead to a drastic increase in running speed.
-In penalized regression techniques, this high value for $\beta$ would then dominate the penalty function, leaving coefficients of other predictors unregularized.
-
-Thus, to equalize predictor scales, a widely used technique is standardization ([@gelman2008scaling]).
-Standardization sets the mean of all predictors to 0 and their standard deviation to 1.
-It does so by Z-transforming all predictors as follows:
+Penalized regression analyses typically require the scales of predictors to be equivalent ([@tibshirani1996]).
+This is because the regularization penalizes coefficients without regard for their scale.
+If variable scales differ, this can lead to an imbalanced penalization of coefficients that does not reflect differences in variable importance ([@lee2015note]).
+To clarify, a regression parameter $\beta$ can be interpreted as the expected increase in outcome $\mathbf{Y}$ for a one unit increase in predictor $\mathbf{X}$.
+If the scale of predictor $\mathbf{X}$ is increased by a factor 10, its regression coefficient is reduced by a factor 10.
+Standardization is a widely used method for equalizing predictor scales ([@gelman2008scaling]).
+It sets the mean of all predictors to 0 and their standard deviation to 1 by Z-transforming all predictors as follows:
 
@@
 where $\bar{\mathbf{X}}$ is a vector of predictor means and $\mathbf{s_X}$ is a vector of standard deviations of the predictors.
-`brma()` standardizes the predictors by default on which the model is estimated.
-The function returns the estimated parameters back in their original scales.
+By default, `brma()` standardizes the predictors on which the model is estimated.
+The function returns the estimated parameters back to their original scales.
 This is achieved for the intercept by applying:
@@
 
-There is some debate regarding the standardization of binary/dummy predictors in penalized regression ([@lee2015note]).
-Some suggest to always standardize dummy variables ([@tibshirani1997lasso]).
-However, standardizing binary predictors increases the absolute maximum values the predictor can take on which in some cases can make its coefficient more sensitive to the penalty function ([@harrell2001regression]).
-
-In any case, the default standardization option in `brma()` can be overwritten entirely by setting `standardize = False`.
-`brma()` also allows the user to standardize only some of the predictors.
-This is done by constructing a vector of means and a vector of standard deviations.
-These vectors contain the means and standard deviations of the predictors in their original scales, except for the predictors that **should not** be standardized.
-For the latter, a mean of 0 and a standard deviation of 1 must be passed.
-The predictors that need to be standardized should then be standardized manually.
-Finally, the mean and standard deviation vectors are passed to the `standardize` argument as follows: `standardize = list(center = MeanVector, scale = SdVector)`.
+It is not always necessary or desirable to standardize predictors, however.
+For example, if predictors are already standardized or on a unified scale for different reasons.
+In these cases standardization does not make scales more equal, nor the penalization more fair, and the default standardization in `brma()` can be disabled.
+<!--Alternatively, if the goal of a study is to compare results to prior findings based on unstandardized predictors, standardization would make penalization unequal across studies.-->
+
+There are additional considerations regarding standardization of binary and dummy predictors ([@alkharusi2012categorical]).
+Some suggest to always standardize binary predictors ([@tibshirani1997lasso]).
+This makes that, irrespective of initial scaling, the binary predictor will be on the same scale as the continuous standardized predictors ([@gelman2008scaling]).
+However, standardizing binary predictors may decrease model interpretability ([@wissmann2007role]).
+To illustrate this point, consider bivariate regression with a single binary predictor $X$ that takes on values 0 and 1 predicting outcome $Y$.
+The intercept represents the expected value of $Y$ when $X == 0$, and the regression coefficient represents the difference in the expected value of $Y$ between the two conditions ([@alkharusi2012categorical]).
+By standardizing this binary predictor, the reference value is no longer zero, and both the intercept and its regression coefficient have no clear interpretation anymore, especially in multivariate cases ([@wissmann2007role]).
+
+Multiple coding schemes for categorical predictors exist that are equivalent in OLS regression.
+In penalized regression, however, the choice of coding might affect model fit and interpretation ([@chiquet2016coding; @detmer2020note]).<!--ELI: weet je dit zeker?
+Ik heb nu gezegd "might" affect model fit and interpretation, omdat ik het niet zeker weet.
+Kan jij checken en als het inderdaad zo is, hier "does affect" van maken?
+-->
+In `brma()`, the default is to use dummy coding for categorical predictors and standardize the dummies.
+Users may specify alternative solutions, keeping in mind the aforementions considerations.
+
+There are two ways to circumvent the default standardization in `brma()`.
+The first is to disable standardization entirely, analyzing predictors in their original scale,
+by setting `standardize = FALSE`.
+Alternatively, `brma()` allows custom standardization.
+To use this option, first manually standardize (some of) the predictors.
+Then, when calling `brma()`, pass a vector of means and a vector of standard deviations to restore the coefficients to the predictors' original scale.
+This can be accomplished using the argument `standardize = list(center = meanvector, scale = sdvector)`.
+For predictors that **should not** be standardized, a mean of 0 and a standard deviation of 1 must be passed; this will leave the coefficient in question unaffected.
 

### 2022-03-04 paper/manuscript.Rmd

@@
 Multiple coding schemes for categorical predictors exist that are equivalent in OLS regression.
-In penalized regression, however, the choice of coding might affect model fit and interpretation ([@chiquet2016coding; @detmer2020note]).<!--ELI: weet je dit zeker?
-Ik heb nu gezegd "might" affect model fit and interpretation, omdat ik het niet zeker weet.
-Kan jij checken en als het inderdaad zo is, hier "does affect" van maken?
--->
+In penalized regression, however, the choice of coding does affect model fit and interpretation ([@chiquet2016coding; @detmer2020note]).
+Although this paper does not cover such considerations, a more elaborate discussion on how coding schemes affect model accuracy and interpretability in penalized regression can be found in @chiquet2016coding and @detmer2020note.
+
 In `brma()`, the default is to use dummy coding for categorical predictors and standardize the dummies.
-Users may specify alternative solutions, keeping in mind the aforementions considerations.
+Users may specify alternative solutions, keeping in mind the aforementioned considerations.
 

### 2022-03-17 paper/manuscript.Rmd
checked manuscript and replied to comments

@@
 $$
-The resulting parameter estimates are those that give the best predictions of the dependent variable in the present dataset.
+The resulting parameter estimates are those that give the best predictions of the dependent variable in the present data set.
 Penalized regression, by contrast, adds a penalty term to the RSS.
@@
 and dummy-code the new contender.
-The model will then estimate whether the new contended has an effect size significantly lower or higher than the industry standard.
+The model will then estimate whether the newly developed intervention has an effect size significantly lower or higher than the industry standard.
 In other cases, there may not be a straightforward reference category.
@@
 In BRMA, as in other R functions, one can use ANOVA specification by explicitly removing the intercept from the model formula; for example, if `yi` is the effect size and $C$ a categorical moderator, regression specification with $c-1$ dummies is specified as `yi ~ C`, and ANOVA specification with $c$ dummies is specified as `yi ~ -1 + C`.
+<!-- This part seems a repetition from the info on standardization of dummies above?: 
 The appropriate standardization of dummy variables in penalized regression analyses is a topic of ongoing debate.
@@
 This is possible in `brma()` by ... 
+-->
 
@@
 Some prior distributions have been shown to result in exactly the same solutions as classical, frequentist penalties, such as the LASSO.
-Specifically, placing independent Laplace (i.e., double exponential) priors on the regression coefficients results in posterior modes that are equal to the lasso estimates ([@ParkCasella2008]).
+Specifically, placing independent double exponential (i.e., Laplace) priors on the regression coefficients can result in posterior modes that are equal to the classical LASSO estimates ([@ParkCasella2008]).
 In addition, many prior distributions have been developed and investigated specifically for the purpose of providing good shrinkage properties, meaning that the prior pulls small regression coefficients towards zero, without exerting any influence on substantial regression coefficients.
@@
 The LASSO prior is implemented as follows:
-<!-- CJ: Sara, kan jij checken of La de juiste notatie is voor de Laplace prior? -->
-
-$$
-\beta_{j} \sim \text{La}(0, \frac{s}{\lambda})
-$$
-where $s$ is a global scale parameter, and $\lambda$ is an inverse-tuning parameter.
+<!-- CJ: Sara, kan jij checken of La de juiste notatie is voor de Laplace prior? 
+SvE: ik heb er DE van gemaakt voor double exponential, aangezien dat de aanduiding is die ook in Stan en de Stan manual wordt gebruikt.
+-->
+
+$$
+\beta_{j} \sim \text{DE}(0, \frac{s}{\lambda})
+$$
+where DE denotes the double exponential distribution with a location equal to 0 and a scale determined by a global scale parameter $s$ and an inverse-tuning parameter $\lambda$.
 By default in `brma()`, the global scale parameter is set to 1,
@@
 \beta_{j} &\sim N(0, \tilde{\tau}_j^2\lambda) \text{, with } \tilde{\tau}_j^2 = \frac{c^2 \tau_j^2}{c^2 + \lambda^2 \tau_j^2}\\
-\lambda &\sim \text{half-t}(\nu_1, 0, \lambda^2_0)\\
-\tau_j &\sim \text{half-t}(\nu_2, 0, 1)\\
+\lambda &\sim \text{student-}t^+(\nu_1, 0, \lambda^2_0)\\
+\tau_j &\sim \text{student-}t^+(\nu_2, 0, 1)\\
 c^2 &\sim \Gamma^{-1}(\frac{\nu_3}{2}, \frac{\nu_3 s^2}{2})
@@
 $$
+where N denotes the normal distribution, student-$t^+$ denotes the half-t distribution and $\Gamma^{-1}$ denotes the inverse Gamma distribution.
 This extension of the horseshoe is more numerically stable in certain cases.
-In addition, it allows the user to explicitly include prior information regarding the expected number of relevant moderators by setting the argument par_ratio to the ratio of the expected number of non-zero coefficients to the expected number of zero coefficients.
 <!-- CJ: Je spreekt hier over het argument par_ratio van de functie in Stan.
 Maar hier in de tekst verwacht ik uitleg over de formule.
-Zien we par_ratio terug in die formule?-->
-In this formula, $\lambda^2_0$ is a global scale parameter that affects the overall shrinkage of the prior, with smaller values resulting in more shrinkage. The default value in `brma()` is 1. 
+Zien we par_ratio terug in die formule?; SvE: ik heb dit hieronder nu extra uitgelegd -->
+In this formula, $\lambda^2_0$ is a global scale parameter that affects the overall shrinkage of the prior, with smaller values resulting in more shrinkage.
+The default value in `brma()` is 1.
+However, if prior information regarding the number of relevant moderators is available, it is best to include this information by setting $\lambda^2_0 = \frac{p_0}{p-p_0}{\frac{\sigma}{\sqrt{n}}$, where $p_0$ represents the number of relevant moderators, $p$ the total number of moderators, $\sigma$ is the residual standard deviation and $n$ equals the number of observations.
+This can be done by setting the argument `relevant_pars` equal to the expected number of relevant moderators.
+<!-- SvE: nu twijfel ik toch weer of dit helemaal goed gaat.
+sigma is in ons model namelijk op 0 gezet en wordt hier dus niet in meegenomen.
+Klopt het dat de residual SD 0 moet zijn in dit model?
+De rest van de global scale wordt berekend buiten het Stan model om in de brma functie zelf.
+-->
 The thickness of the tails is controlled by two degrees of freedom parameters, $\nu_1$ and $\nu_2$, which default to 1 in `brma()`.
@@
 which is strictly no longer a horseshoe prior.
-However, in certain cases<!-- Sara, wat voor cases?--> these lighter tails can aid model convergence. 
+However, in cases where the model is weakly identified, for example when there are more moderators than observations, these lighter tails can aid model convergence. 
 The regularized horseshoe differs from the standard horseshoe in the specification of a finite "slab". This slab ensures at least some regularization of large coefficients and as a consequence,
@@
 <!--Sara, eigenlijk is het niet helemaal duidelijk wat al deze nummers doen.
-Kunnen we een interactieve plot maken waarmee gebruikers kunnen zien hoe aanpassingen de vorm van de prior beinvloeden?-->
+Kunnen we een interactieve plot maken waarmee gebruikers kunnen zien hoe aanpassingen de vorm van de prior beinvloeden?; SvE: ik heb een prototype shiny app gemaakt.-->
 
@@
 For a predictive performance measure, it is necessary to use the mean of the training data, as the mean of the testing set is a descriptive statistic of that sample.
-**ik vind deze zin niet heel duidelijk**
+**ik vind deze zin niet heel duidelijk** <!-- SvE: dit was nog een eerdere comment van mij (toen ik nog niet wist hoe ik echt kon commenten binnen Rmarkdown :) ) -->
 The resulting metric $R_{test}^{2}$ is expressed by the following equation:
@@
 **het aantal moderatoren is redelijk laag; ik zou vooral nog voordelen van brma verwachten met meer moderatoren maar is dat realistisch in de praktijk?
-Zo ja, dan is het iets om te noemen in de discussie**
+Zo ja, dan is het iets om te noemen in de discussie** <!-- hier ook nog een eerdere comment.
+Mocht je een keer een toepassing tegenkomen met echt veel moderatoren, kan het interessant zijn hier nog een kleine simulatie op te baseren.
+Een voorbeeld kan zijn een set van moderatoren die de kwaliteit van studies proberen te vatten zoals we laatst hebben besproken -->
 According to a review of 705 published psychological meta-analyses (Van Erp et al., 2017),
@@
 The effect sizes and their variances must be computed using suitable methods;
-note that many such methods are available in the R package `metafor` (Viechtbauer et al.,, 2010).
+note that many such methods are available in the R package `metafor` (Viechtbauer et al., 2010).
 With regard to data analysis, we recommend the use of a horseshoe prior by default,
@@
 When estimating the model, it is important to ascertain that the algorithm has converged before interpreting the results.
-Stan, the computational back-end of `brma()`, should return warnings and errors if there are indicationsof non-convergence.
+Stan, the computational back-end of `brma()`, should return warnings and errors if there are indications of non-convergence.
 <!-- Sara, wat kan men nog meer doen om convergence te checken?
@@
 Alle standaard plots voor stan-model objecten zijn beschikbaar, dankzij de functie `as.stan()`.
-Misschien kan je wat tips geven hier?
+Misschien kan je wat tips geven hier?; SvE: ik zal dit verwerken in de toepassing.
 -->

### 2022-03-18 paper/manuscript.Rmd
add shiny_prior and sample_prior

@@
 The LASSO prior is implemented as follows:
-<!-- CJ: Sara, kan jij checken of La de juiste notatie is voor de Laplace prior? 
-SvE: ik heb er DE van gemaakt voor double exponential, aangezien dat de aanduiding is die ook in Stan en de Stan manual wordt gebruikt.
--->
 
@@
 The implementation of the horseshoe prior is based on the regularized horseshoe proposed by @PiironenVehtari2017b:
-<!-- CJ: Sara, Kan jij checken wat de juiste notatie is voor "half-t"? -->
 
@@
 This extension of the horseshoe is more numerically stable in certain cases.
-<!-- CJ: Je spreekt hier over het argument par_ratio van de functie in Stan.
-Maar hier in de tekst verwacht ik uitleg over de formule.
-Zien we par_ratio terug in die formule?; SvE: ik heb dit hieronder nu extra uitgelegd -->
 In this formula, $\lambda^2_0$ is a global scale parameter that affects the overall shrinkage of the prior, with smaller values resulting in more shrinkage.
@@
 This slab is governed by a degrees of freedom parameter ($\nu_3$, set to 4) and a scale parameter ($s$, set to 1).
-<!--Sara, eigenlijk is het niet helemaal duidelijk wat al deze nummers doen.
-Kunnen we een interactieve plot maken waarmee gebruikers kunnen zien hoe aanpassingen de vorm van de prior beinvloeden?; SvE: ik heb een prototype shiny app gemaakt.-->
 
@@
 The $R^2_{test}$ reflects the fraction of variance in the testing data explained by the model,
-relative to the variance explained by the mean of the training data.
-For a predictive performance measure, it is necessary to use the mean of the training data, as the mean of the testing set is a descriptive statistic of that sample.
-**ik vind deze zin niet heel duidelijk** <!-- SvE: dit was nog een eerdere comment van mij (toen ik nog niet wist hoe ik echt kon commenten binnen Rmarkdown :) ) -->
+relative to the mean.
+Note that the mean of the training data, not of the testing data, is used as a benchmark.
 The resulting metric $R_{test}^{2}$ is expressed by the following equation:
@@
 The number of studies in the training data $k \in (20, 40, 100)$, the average within-study sample size $\bar{n} \in (40, 80, 160)$, the population effect size of relevant moderators $\beta \in (0, .2, .5, .8)$, the number of moderators $p \in (2, 3, 6)$, and residual heterogeneity $\tau^{2} \in (.01, .04, .1)$.
-**het aantal moderatoren is redelijk laag; ik zou vooral nog voordelen van brma verwachten met meer moderatoren maar is dat realistisch in de praktijk?
-Zo ja, dan is het iets om te noemen in de discussie** <!-- hier ook nog een eerdere comment.
+<!-- **het aantal moderatoren is redelijk laag; ik zou vooral nog voordelen van brma verwachten met meer moderatoren maar is dat realistisch in de praktijk?
+Zo ja, dan is het iets om te noemen in de discussie** hier ook nog een eerdere comment.
 Mocht je een keer een toepassing tegenkomen met echt veel moderatoren, kan het interessant zijn hier nog een kleine simulatie op te baseren.

### 2022-03-18 R/plot_prior.R

@@ -1,6 +1,7 @@
-#' @title Plot Prior Distribution
-#' @description Plots the kernal density function of samples from a prior
-#' distribution with parameters defined in `prior`.
+#' @title Sample from the Prior Distribution
+#' @description Samples from a prior
+#' distribution with parameters defined in `prior`. The result can be plotted
+#' using the \code{\link{plot}} function.
 #' @param method Character string, indicating which prior to sample from.
 #' Default: first element of `c("hs", "lasso")`.
 #' @param prior Numeric vector, specifying the prior to use. See [pema::brma]
@@ -10,18 +11,27 @@
 #' @return NULL, function is called for its side-effect of plotting to the
 #' graphics device.
 #' @examples
-#' plot_prior("lasso", iter = 10)
-#' @rdname plot_prior
+#' sample_prior("lasso", iter = 10)
+#' @rdname sample_prior
 #' @importFrom rstan sampling
 #' @export
-plot_prior <- function(method = c("hs", "lasso"),
+sample_prior <- function(method = c("hs", "lasso"),
                        prior = switch(method,
                                       "lasso" = c(df = 1, scale = 1),
                                       "hs" = c(df = 1, df_global = 1, df_slab = 4, scale_global = 1, scale_slab = 1, par_ratio = NULL)),
                        iter = 1000){
-  smpls <- suppressWarnings(sampling(object = stanmodels[[c("lasso_prior", "hs_prior")[(method[1] == "hs")+1]]], data = as.list(prior), chains = 1, iter = iter, warmup = 0, show_messages = FALSE, verbose = FALSE, refresh = 0))
-  plot(density(smpls@sim$samples[[1]]$b), main = c("Lasso prior", "Horseshoe prior")[(method == "hs")+1],
-       xlab = paste0("Samples: ", iter, ", ", paste0(names(prior), " = ", prior, collapse = ", ")),
+  out <- as.list(match.call()[-1])
+  out[["samples"]] <- suppressWarnings(sampling(object = stanmodels[[c("lasso_prior", "hs_prior")[(method[1] == "hs")+1]]], data = as.list(prior), chains = 1, iter = iter, warmup = 0, show_messages = FALSE, verbose = FALSE, refresh = 0))
+  if(is.null(out[["iter"]])) out[["iter"]] <- iter
+  class(out) <- c("brma_prior", class(out))
+  out
+}
+
[…]

### 2022-03-18 R/shiny_prior.R

@@ -1,0 +1,150 @@
+library(shiny)
+library(LaplacesDemon)
+library(ggplot2)
+
+ui <- fluidPage(
+
+  titlePanel("BRMA prior visualization"),
+
+  sidebarLayout(
+
+    sidebarPanel(
+      htmlOutput("general"),
+      br(),
+      numericInput("ndraws",
+                   "Number of draws from the prior",
+                   value = 1000),
+      selectInput("priortype", "Prior",
+                  list("hs", "lasso")),
+      conditionalPanel(
+        condition = "input.priortype == 'hs'",
+        numericInput("hs_df",
+                     "df",
+                     value = 1),
+        numericInput("hs_df_global",
+                     "df_global",
+                     value = 1),
+        numericInput("hs_df_slab",
+                     "df_slab",
+                     value = 4),
+        numericInput("hs_scale_global",
+                     "scale_global",
+                     value = 1),
+        numericInput("hs_scale_slab",
+                     "hs_scale_slab",
+                     value = 1)
+      ),
+      conditionalPanel(
+        condition = "input.priortype == 'lasso'",
+        numericInput("lasso_df",
+                     "df",
+                     value = 1),
+        numericInput("lasso_scale",
+                     "scale",
+                     value = 1)
+      ),
+      actionButton("update_plot", "Add to plot"),
+      uiOutput("ui_removelist"),
+      uiOutput("ui_removebutton")
+    ),
+
+    mainPanel(
+      plotOutput("prior_plot"),
+      uiOutput("prior_list")
+    )
+  )
+)
+
+# Define server logic
+server <- function(input, output) {
+  reactives <- reactiveValues()
+  reactives[["priors"]] <- list()
+  reactives[["prior_names"]] <- vector("character")
+  reactives[["prior_deets"]] <- list()
+  reactives[["counter"]] <- 0
+  observeEvent(input$update_plot, {
+    priorargs <- switch(input$priortype,
+                        "hs" = c(df = input$hs_df,
+                                 df_global = input$hs_df_global,
+                                 df_slab = input$hs_df_slab,
+                                 scale_global = input$hs_scale_global,
+                                 scale_slab = input$hs_scale_slab),
[…]

### 2022-04-07 paper/application.Rmd

---
title: "pema application"
author: "Sara van Erp"
date: "3/30/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Packages
First, load in the necessary packages. In addition, if you are running the model locally on a multicore machine, you can set `options(mc.cores = 4)`. This ensures the different MCMC chains will be run in parallel, making estimation faster.

```{r}
library(pema)
options(mc.cores = 4)
library(tidyverse)
library(fastDummies)
```

## Data

In this application, we will work with the bonapersona data (Bonapersona et al., 2019). The data and codebook can be found [here](https://zenodo.org/record/2540657#.XEGPP2ko9aR). First, we read in the data and make sure all relevant variables are of the correct type.

Q1 Caspar: de data lijkt nog niet beschikbaar in de laatste versie van het package?

```{r data}
bonapersona <- read.csv2("./pema_application/MAB_data.csv")
summary(bonapersona)
bonapersona$yi <- as.numeric(bonapersona$yi)
bonapersona$vi <- as.numeric(bonapersona$vi)
bonapersona$bias <- as.numeric(bonapersona$bias)
```
For this application, we use the same 26 moderators as in Bonapersona et al. (2019; see Figure 3A for an overview). We select these moderators and create dummy variables for all categorical moderators.

```{r dummies}
datsel <- bonapersona %>% 
  select(yi, vi, author, mTimeLength, year, model, ageWeek, testAuthorGrouped,
         strainGrouped, bias, species, domain, mLDGrouped, waterTcate, 
         origin, mCageGrouped, seqGeneration, baseline, blindExp,
         retentionGrouped, hit2Grouped, outBlind, sex, housing,
         testLDGrouped, freezingType, blindRand, control, mControlGrouped)

# Recode categorical moderators
catmod <- c("model", "testAuthorGrouped", "strainGrouped", "species", "domain", "mLDGrouped", "waterTcate", "origin", 
            "mCageGrouped", "seqGeneration", "baseline", "blindExp", "retentionGrouped", "hit2Grouped",
            "outBlind", "sex", "housing", "testLDGrouped", "freezingType", "blindRand", "control", "mControlGrouped")
datdum <- dummy_cols(datsel, 
                     select_columns = catmod,
                     remove_first_dummy = TRUE,
                     remove_selected_columns = TRUE) 
```

## Two-level model
First, for simplicity, we run a two-level model ignoring the fact that certain effect sizes come from the same study.

```{r}
dat2l <- datdum %>%
  select(-author)
```

### Two-level model with the lasso prior
We start with running a penalized meta-analysis using the lasso prior. Compared to the horseshoe prior, the lasso is easier to use because it has only two hyperparameters to set. However, the lighter tails of the lasso can result in large coefficients being shrunken too much towards zero thereby leading to potentially more bias compared to the regularized horseshoe prior.

For the lasso prior, we need to specify the degrees of freedom `df` and the `scale`. Both default to 1. The degrees of freedom determines the chi-square prior that is specified for the inverse-tuning parameter. Increasing the degrees of freedom will allow larger values for the inverse-tuning parameter, leading to less shrinkage. Increasing the scale parameter will also result in less shrinkage. The influence of these hyperparameters can be visualized through the implemented shiny app, which can be called via `shiny_prior()`.

Q2 Caspar: `standardize = TRUE` resulteert in NAs waardoor Stan een error geeft. Weet jij hoe dit kan? Daarnaast moeten we misschien een meer informatieve waarschuwing geven in het algemeen als er NAs in de data zitten?

```{r}
# Manually standardize the continuous moderators, because `standardize = TRUE` does not work for some reason
dat2l <- dat2l %>%
  mutate(year = scale(year)) %>%
  mutate(ageWeek = scale(ageWeek)) %>%
  mutate(bias = scale(bias))
```

```{r lasso, cache = TRUE}
fit.lasso <- brma(yi ~ .,
            data = dat2l,
            vi = "vi",
            method = "lasso",
            standardize = FALSE,
            prior = c(df = 1, scale = 1),
            mute_stan = FALSE)
```

#### Assessing convergence and interpreting the results
We can request the results using the `summary` function. Before we interpret the results, we need to ensure that the MCMC chains have converged to the posterior distribution. Two helpful diagnostics provided in the summary are the number of effective posterior samples `n_eff` and the potential scale reduction factor `Rhat`. `n_eff` is an estimate of the number of independent samples from the posterior. Ideally, the ratio `n_eff` to total samples is as close to 1 as possible. `Rhat` compares the between- and within-chain estimates and is ideally close to 1 (indicating the chains have mixed well). Should any values for `n_eff` or `Rhat` be far from these ideal values, you can try increasing the number of iterations through the `iter` argument. By default, the `brma` function runs four MCMC chains with 2000 iterations each, half of which is discarded as burn-in. As a result, a total of 4000 iterations is available on which posterior summaries are based. If this does not help, non-convergence might indicate a problem with the model specification.

```{r}
options(max.print = 10000)
summary(fit.lasso)
```

If we are satisfied with the convergence, we can continue looking at the posterior summary statistics. The `summary` function provides the posterior mean estimate for the effect of each moderator. Since Bayesian penalization does not automatically shrink estimates exactly to zero, some additional criterion is needed to determine which moderators should be selected in the model. Currently, this is done using the 95% credible intervals, with a moderator being selected if zero is excluded in this interval. In the `summary` this is denoted by an asterisk for that moderator. In this model, the only significant moderator is the dummy variable for sex. All other coefficients are not significant after being shrunken towards zero by the lasso prior.

Q3 Caspar: Deze resultaten lijken niet overeen te komen met die uit het originele paper waar metaforest is gebruikt. Daar lijkt sex namelijk niet zo'n belangrijke moderator (gebaseerd op figuur 3A). Ik weet alleen niet genoeg van metaforest om te bepalen of dit problematisch is of logisch te verklaren door de onderliggende methode.

### Two-level model with the horseshoe prior
Next, we look into the regularized horseshoe prior. The horseshoe prior has five hyperparameters that can be set. Three parameters are degrees of freedom parameters which influence the tails of the distributions in the prior. Generally, it is not needed to specify different values for these hyperparameters. Here, we focus instead on the global scale parameter and the scale of the slab.

```{r hs, cache = TRUE}
# use the default settings
fit.hs1 <- brma(yi ~ .,
               data = dat2l,
               vi = "vi",
               method = "hs",
               standardize = FALSE,
               prior = c(df = 1, df_global = 1, df_slab = 4, scale_global = 1, scale_slab = 1, relevant_pars = NULL),
               mute_stan = FALSE)

# reduce the global scale
fit.hs2 <- brma(yi ~ .,
                data = dat2l,
                vi = "vi",
                method = "hs",
                standardize = FALSE,
                prior = c(df = 1, df_global = 1, df_slab = 4, scale_global = 0.1, scale_slab = 1, relevant_pars = NULL),
                mute_stan = FALSE)

# increase the scale of the slab
fit.hs3 <- brma(yi ~ .,
                data = dat2l,
                vi = "vi",
                method = "hs",
                standardize = FALSE,
                prior = c(df = 1, df_global = 1, df_slab = 4, scale_global = 1, scale_slab = 5, relevant_pars = NULL),
                mute_stan = FALSE)

```

Note that the horseshoe prior results in some divergent transitions. This can be an indication of non-convergence. However, these divergences arise often when using the horseshoe prior and as long as there are not too many of them, the results can still be used.

Next, we plot the posterior mean estimates for a selection of moderators for the different priors.

```{r}
df.fun <- function(fit, prior){
  plotdat <- data.frame(fit$coefficients)
  plotdat$par <- rownames(plotdat)
  plotdat$Prior <- prior
  return(plotdat)
}

df0 <- df.fun(fit.lasso, prior = "lasso")
df1 <- df.fun(fit.hs1, prior = "hs default")
df2 <- df.fun(fit.hs2, prior = "hs reduced global scale")
df3 <- df.fun(fit.hs3, prior = "hs increased slab scale")

df <- rbind.data.frame(df0, df1, df2, df3)

# select pars with highest posterior mean estimates 
parsel <- df1 %>%
  arrange(desc(abs(`mean`))) %>%
  select(par) %>%
  filter(!par == "tau2")

dfsub <- df %>%
  filter(par %in% parsel$par[1:10] )

pd <- 0.5

ggplot(dfsub, aes(x=mean, y=par, group = Prior)) + 
  geom_errorbar(aes(xmin=X2.5., xmax=X97.5., colour = Prior), width=.1, position = position_dodge(width = pd)) +
  geom_point(aes(colour = Prior), position = position_dodge(width = pd)) +
  theme_bw() + xlab("Posterior mean") + ylab("")
```

We can see that, in general, the different priors give quite similar results in this application. A notable exception is the estimate for the dummy variable `testAuthorGrouped_stepDownAvoidance` which is much smaller for the lasso compared to the horseshoe specification. This indicates that the lasso can shrink large coefficients more towards zero whereas the horseshoe is better at keeping them large.

## Three-level model
Finally, we can also take into account the fact that some effect sizes might come from the same study by fitting a three-level model as follows:

```{r 3level, cache = TRUE}
fit.3l <- brma(yi ~ .,
               data = datdum,
               vi = "vi",
               study = "author",
               method = "lasso",
               standardize = FALSE,
               prior = c(df = 1, scale = 1),
               mute_stan = FALSE)
```

### 2022-04-07 paper/application.Rmd
application

@@
 knitr::opts_chunk$set(echo = TRUE)
+run_everything = FALSE
 ```
@@
 ## Packages
+
 First, load in the necessary packages.
@@
 library(fastDummies)
+library(tidySEM)
+library(DT)
 ```
@@
 
-Q1 Caspar: de data lijkt nog niet beschikbaar in de laatste versie van het package?
+```{r data}
+tab_desc <- descriptives(bonapersona)[c("name", "type", "n", "unique", "mean", "sd", "v")]
+DT::datatable(tab_desc) %>%
+  formatRound(columns=c("mean", "sd", "v"), digits = 2)
+```
 
-```{r data}
-bonapersona <- read.csv2("./pema_application/MAB_data.csv")
-summary(bonapersona)
-bonapersona$yi <- as.numeric(bonapersona$yi)
-bonapersona$vi <- as.numeric(bonapersona$vi)
-bonapersona$bias <- as.numeric(bonapersona$bias)
+## Impute missings
+
+```{r}
+bonapersona$ageWeek[is.na(bonapersona$ageWeek)] <- median(bonapersona$ageWeek, na.rm = TRUE)
 ```
-For this application, we use the same 26 moderators as in Bonapersona et al.
-(2019; see Figure 3A for an overview).
-We select these moderators and create dummy variables for all categorical moderators.
+
+## Moderators
+
+For this application, we use a smaller selection of moderators than in Bonapersona et al. (2019; see Figure 3A for an overview).
 
@@
 datsel <- bonapersona %>% 
-  select(yi, vi, author, mTimeLength, year, model, ageWeek, testAuthorGrouped,
-         strainGrouped, bias, species, domain, mLDGrouped, waterTcate, 
-         origin, mCageGrouped, seqGeneration, baseline, blindExp,
-         retentionGrouped, hit2Grouped, outBlind, sex, housing,
-         testLDGrouped, freezingType, blindRand, control, mControlGrouped)
-
-# Recode categorical moderators
-catmod <- c("model", "testAuthorGrouped", "strainGrouped", "species", "domain", "mLDGrouped", "waterTcate", "origin", 
-            "mCageGrouped", "seqGeneration", "baseline", "blindExp", "retentionGrouped", "hit2Grouped",
-            "outBlind", "sex", "housing", "testLDGrouped", "freezingType", "blindRand", "control", "mControlGrouped")
-datdum <- dummy_cols(datsel, 
-                     select_columns = catmod,
-                     remove_first_dummy = TRUE,
-                     remove_selected_columns = TRUE) 
+  select(yi, vi, author, mTimeLength, year, model, ageWeek, strainGrouped, bias, species, domain, sex) 
 ```
@@
 ## Two-level model
+
 First, for simplicity, we run a two-level model ignoring the fact that certain effect sizes come from the same study.
@@
 ```{r}
-dat2l <- datdum %>%
+dat2l <- datsel %>%
   select(-author)
@@
 ### Two-level model with the lasso prior
+
 We start with running a penalized meta-analysis using the lasso prior.
@@
 
-Q2 Caspar: `standardize = TRUE` resulteert in NAs waardoor Stan een error geeft.
-Weet jij hoe dit kan?
-Daarnaast moeten we misschien een meer informatieve waarschuwing geven in het algemeen als er NAs in de data zitten?
-
-```{r}
-# Manually standardize the continuous moderators, because `standardize = TRUE` does not work for some reason
-dat2l <- dat2l %>%
-  mutate(year = scale(year)) %>%
-  mutate(ageWeek = scale(ageWeek)) %>%
-  mutate(bias = scale(bias))
-```
-
-```{r lasso, cache = TRUE}
-fit.lasso <- brma(yi ~ .,
+```{r, echo = TRUE, eval = F}
+fit_lasso <- brma(yi ~ .,
                   data = dat2l,
@@
                   method = "lasso",
-            standardize = FALSE,
                   prior = c(df = 1, scale = 1),
@@
 ```
+```{r, echo = FALSE, eval = TRUE}
+if(run_everything){
+  fit_lasso <- brma(yi ~ .,
+                    data = dat2l,
+                    vi = "vi",
+                    method = "lasso",
+                    prior = c(df = 1, scale = 1),
+                    mute_stan = FALSE)
+  saveRDS(fit_lasso, "fitlasso.RData")
+}
+fit_lasso <- readRDS("fitlasso.RData")
+```
 
 #### Assessing convergence and interpreting the results
+
 We can request the results using the `summary` function.
@@
 
-```{r}
-options(max.print = 10000)
-summary(fit.lasso)
+```{r, eval = TRUE}
+sum <- summary(fit_lasso)
+DT::datatable(sum$coefficients[, c("mean", "sd", "2.5%", "97.5%", "n_eff", "Rhat")]) %>%
+  formatRound(columns=c("mean", "sd", "2.5%", "97.5%", "n_eff", "Rhat"), digits = 2)
 ```
@@
 
-Q3 Caspar: Deze resultaten lijken niet overeen te komen met die uit het originele paper waar metaforest is gebruikt.
-Daar lijkt sex namelijk niet zo'n belangrijke moderator (gebaseerd op figuur 3A).
-Ik weet alleen niet genoeg van metaforest om te bepalen of dit problematisch is of logisch te verklaren door de onderliggende methode.
+Also note the summary statistics for `tau2`, the (unexplained) residual between-studies heterogeneity.
+The 95% credible interval for this coefficient excludes zero, indicating that there is a non-zero amount of unexplained heterogeneity.
+It is customary to express this heterogeneity in terms of $I^2$, the percentage of variation across studies that is due to heterogeneity rather than chance (Higgins and Thompson, 2002; Higgins et al., 2003).
+The helper function `I2()` computes the posterior distribution of $I^2$ based on the MCMC draws of `tau2`:
+
+```{r}
+I2(fit_lasso)
+```
 
 ### Two-level model with the horseshoe prior
+
 Next, we look into the regularized horseshoe prior.
@@
 
-```{r hs, cache = TRUE}
+```{r hs, echo = TRUE, eval = F}
 # use the default settings
-fit.hs1 <- brma(yi ~ .,
+fit_hs1 <- brma(yi ~ .,
                 data = dat2l,
@@
                 method = "hs",
-               standardize = FALSE,
                 prior = c(df = 1, df_global = 1, df_slab = 4, scale_global = 1, scale_slab = 1, relevant_pars = NULL),
@@
 # reduce the global scale
-fit.hs2 <- brma(yi ~ .,
+fit_hs2 <- brma(yi ~ .,
                 data = dat2l,
@@
                 method = "hs",
-                standardize = FALSE,
                 prior = c(df = 1, df_global = 1, df_slab = 4, scale_global = 0.1, scale_slab = 1, relevant_pars = NULL),
@@
 # increase the scale of the slab
-fit.hs3 <- brma(yi ~ .,
+fit_hs3 <- brma(yi ~ .,
                 data = dat2l,
@@
                 method = "hs",
-                standardize = FALSE,
                 prior = c(df = 1, df_global = 1, df_slab = 4, scale_global = 1, scale_slab = 5, relevant_pars = NULL),
@@
 
+```{r, echo = FALSE, eval = TRUE}
+if(run_everything){
+  # use the default settings
+  fit_hs1 <- brma(yi ~ .,
+                  data = dat2l,
+                  vi = "vi",
+                  method = "hs",
+                  prior = c(df = 1, df_global = 1, df_slab = 4, scale_global = 1, scale_slab = 1, relevant_pars = NULL),
+                  mute_stan = FALSE)
+
+  # reduce the global scale
+  fit_hs2 <- brma(yi ~ .,
+                  data = dat2l,
+                  vi = "vi",
+                  method = "hs",
+                  prior = c(df = 1, df_global = 1, df_slab = 4, scale_global = 0.1, scale_slab = 1, relevant_pars = NULL),
+                  mute_stan = FALSE)
+
+  # increase the scale of the slab
+  fit_hs3 <- brma(yi ~ .,
+                  data = dat2l,
+                  vi = "vi",
+                  method = "hs",
+                  prior = c(df = 1, df_global = 1, df_slab = 4, scale_global = 1, scale_slab = 5, relevant_pars = NULL),
+                  mute_stan = FALSE)
+  saveRDS(fit_hs1, "fit_hs1.RData")
+  saveRDS(fit_hs2, "fit_hs2.RData")
+  saveRDS(fit_hs3, "fit_hs3.RData")
+}
+fit_hs1 <- readRDS("fit_hs1.RData")
+fit_hs2 <- readRDS("fit_hs2.RData")
+fit_hs3 <- readRDS("fit_hs3.RData")
+```
+
 Note that the horseshoe prior results in some divergent transitions.
 This can be an indication of non-convergence.
-However, these divergences arise often when using the horseshoe prior and as long as there are not too many of them, the results can still be used.
+However, these divergences arise often when using the horseshoe prior and as long as there are not too many of them, the results can still be used.<!-- CJ Reference?
+-->
 
@@
 
-```{r}
-df.fun <- function(fit, prior){
+```{r, eval = F}
+make_plotdat <- function(fit, prior){
   plotdat <- data.frame(fit$coefficients)
@@
 
-df0 <- df.fun(fit.lasso, prior = "lasso")
-df1 <- df.fun(fit.hs1, prior = "hs default")
-df2 <- df.fun(fit.hs2, prior = "hs reduced global scale")
-df3 <- df.fun(fit.hs3, prior = "hs increased slab scale")
+df0 <- make_plotdat(fit_lasso, prior = "lasso")
+df1 <- make_plotdat(fit_hs1, prior = "hs default")
+df2 <- make_plotdat(fit_hs2, prior = "hs reduced global scale")
+df3 <- make_plotdat(fit_hs3, prior = "hs increased slab scale")
 
@@
   select(par) %>%
-  filter(!par == "tau2")
+  filter(!par %in% c("Intercept", "tau2"))
 
@@
   geom_point(aes(colour = Prior), position = position_dodge(width = pd)) +
+  geom_vline(xintercept = 0) +
   theme_bw() + xlab("Posterior mean") + ylab("")
@@
 ## Three-level model
+
 Finally, we can also take into account the fact that some effect sizes might come from the same study by fitting a three-level model as follows:
 
-```{r 3level, cache = TRUE}
-fit.3l <- brma(yi ~ .,
-               data = datdum,
+```{r, echo = TRUE, eval = F}
+fit_3l <- brma(yi ~ .,
+               data = datsel,
                vi = "vi",
@@
 ```
+```{r, eval = TRUE, echo = F}
+if(run_everything){
+  fit_3l <- brma(yi ~ .,
+                 data = datsel,
+                 vi = "vi",
+                 study = "author",
+                 method = "lasso",
+                 prior = c(df = 1, scale = 1),
+                 mute_stan = FALSE)
+  saveRDS(fit_3l, "fit_3l.RData")
+}
+fit_3l <- readRDS("fit_3l.RData")
+```
+
+## Standardization
+
+It is possible to override the default standardization, which standardizes all variables (including dummies).
+To do so, first manually standardize any variables that must be standardized.
+Then, in the call to `brma()`, provide a named list with elements `list(center = ..., scale = ...)`.
+For variables that are **not** to be standardized, use `center = 0, scale = 1`.
+This retains their original scale.
+For variables that are to be standardized, use their original `center` and `scale` to restore the coefficients to their original scale.
+
+In the example below, we standardize a continuous predictor, but we do not standardize the dummies:
+
+```{r echo = FALSE, eval = TRUE}
+
+if(run_everything){
+  moderators <- model.matrix(yi~ageWeek + strainGrouped, data = datsel)[, -1]
+  scale_age <- scale(moderators[,1])
+  stdz <- list(center = c(attr(scale_age, "scaled:center"), rep(0, length(levels(datsel$strainGrouped))-1)),
+               scale = c(attr(scale_age, "scaled:scale"),   rep(1, length(levels(datsel$strainGrouped))-1)))
+  moderators <- data.frame(datsel[c("yi", "vi", "author")], moderators)
+  fit_std <- brma(yi ~ .,
+                  data = moderators,
+                  vi = "vi",
+                  study = "author",
+                  method = "lasso",
+                  prior = c(df = 1, scale = 1),
+                  standardize = stdz,
+                  mute_stan = FALSE)
+  saveRDS(fit_std, "fit_std.RData")
+}
+fit_std <- readRDS("fit_std.RData")
+
+```
+
+```{r echo = TRUE, eval = FALSE}
+moderators <- model.matrix(yi~ageWeek + strainGrouped, data = datsel)[, -1]
+scale_age <- scale(moderators[,1])
+stdz <- list(center = c(attr(scale_age, "scaled:center"), rep(0, length(levels(datsel$strainGrouped))-1)),
+             scale = c(attr(scale_age, "scaled:scale"),   rep(1, length(levels(datsel$strainGrouped))-1)))
+moderators <- data.frame(datsel[c("yi", "vi", "author")], moderators)
+fit_std <- brma(yi ~ .,
+                data = moderators,
+                vi = "vi",
+                study = "author",
+                method = "lasso",
+                prior = c(df = 1, scale = 1),
+                standardize = stdz,
+                mute_stan = FALSE)
+
+```
+
+Note that, in this example, only `ageWeek` is standardized; the remaining (dummy) variables are untouched.
+The object `stdz` provides the original center and scale for `ageWeek`, which allows `brma()` to properly rescale the coefficient for this moderator.
+As the center and scale for all remaining (dummy) variables are 0 and 1, these coefficients are **not** rescaled.
+See the `pema` paper for a discussion of standardization and further references.

### 2022-04-07 R/I2.R

@@ -16,6 +16,8 @@ I2 <- function(x, ...){
   UseMethod("I2", x)
 }
 
+#' @method I2 brma
+#' @export
 I2.brma <- function(x, ...){
 
   fit <- x$fit

### 2022-04-07 R/shiny_prior.R

@@ -1,5 +1,4 @@
 library(shiny)
-library(LaplacesDemon)
 library(ggplot2)
 
 ui <- fluidPage(

### 2022-04-07 R/I2.R
fix test results

@@ -22,7 +22,7 @@ I2.brma <- function(x, ...){
 
   fit <- x$fit
   taus <- sapply(grep("^tau2", rownames(x$coefficients), value = TRUE), function(p){
-    pema:::.extract_samples(fit@sim, par = p)
+    .extract_samples(fit@sim, par = p)
   })
 
   W <- diag(1/x$vi)
@@ -35,6 +35,8 @@ I2.brma <- function(x, ...){
   I2(I2mat)
 }
 
+#' @method I2 default
+#' @export
 I2.default <- function(x, ...){
   cbind(
     mean = colMeans(x),

### 2022-04-07 R/brma.R

@@ -214,8 +214,8 @@ brma.formula <-
 
     cl[names(cl) %in% c("formula", "data", "method")] <- NULL
     cl[[1L]] <- quote(brma)
-    cl[["Y"]] <- Y
-    cl[["X"]] <- X
+    cl[["x"]] <- X
+    cl[["y"]] <- Y
     cl[["vi"]] <- vi
     cl[["prior"]] <- prior
     cl[["mute_stan"]] <- mute_stan
@@ -231,8 +231,8 @@ brma.formula <-
 #' @export
 #' @rdname brma
 brma.default <-
-  function(Y,
-           X,
+  function(x,
+           y,
            vi,
            study = NULL,
            prior,
@@ -241,6 +241,8 @@ brma.default <-
            intercept,
            #prior_only = FALSE,
            ...) {
+    X <- x
+    Y <- y
     dots <- list(...)
     outputdots <- match(c("formula", "vi_column", "study_column"), names(dots), nomatch = 0L)
     if(any(outputdots > 0)){

### 2022-04-20 paper/manuscript.Rmd

@@
 
+# Applied example
+In this application, we will work with the bonapersona data (@BonapersonaEtal2019) which is available in the `pema` package.In this study, over 400 rodent experiments where meta-analysed to investigate the effects of early life adversity on cognitive performance.
+The study includes over 30 potential moderators.
+Here, we select a small random subset of moderators to illustrate the regularized horseshoe prior.
+We focus specifically on how to choose the different hyperparameters of the regularized horseshoe prior.
+
+<!-- Caspar: misschien is het handig om de data binnen het package aan te passen zodat de eerste stappen hieronder niet nodig zijn?
+Wil je daarnaast de code voor de toepassing ook nog in een apart bestand of wil je de snippets laten zien binnen het paper?
+-->
+
+```{r exdata, eval = TRUE}
+# Load the relevant packages
+library(pema)
+library(fastDummies)
+library(bayesplot)
+
+#  Data prep
+summary(bonapersona)
+bonapersona$yi <- as.numeric(bonapersona$yi)
+bonapersona$vi <- as.numeric(bonapersona$vi)
+bonapersona$bias <- as.numeric(bonapersona$bias)
+
+# Use a small random subset of moderators
+datsel <- bonapersona %>% 
+  select(yi, vi, mTimeLength, year, model, ageWeek)
+
+# First recode categorical moderators
+catmod <- c("model")
+datdum <- dummy_cols(datsel, 
+                     select_columns = catmod,
+                     remove_first_dummy = TRUE,
+                     remove_selected_columns = TRUE) 
+```
+
+## Visualizing the prior
+In any Bayesian analysis, it is a good idea to visualize the prior.
+One way to do so is through the shiny app that is implemented in the `pema` package.
+This app can be launched with the following command: `shiny_prior()` and provides the user the opportunity to plot draws from the prior distribution given specific values for the hyperparameters.
+It can be seen that increasing `scale_global` or `hs_scale_slab` will lead to a prior that is more spread out and will therefore pull coefficients less heavily towards zero.
+The degrees of freedom parameters influence the heaviness of the tails with higher values leading to thinner tails.
+Generally, it is not needed to adapt these hyperparameters and so we will only consider the default values.
+
+A second way to gain insight into the prior distribution is by plotting the implied prior on the effective number of nonzero coefficients given specific hyperparameters.
+One advantage of the regularized horseshoe prior is its ability to include prior information on the number of nonzero coefficients.
+This can be done by setting the `relevant_pars` argument to the expected number of relevant moderators, which will determine the `scale_global` hyperparameter setting.
+If no prior information is given via the `relevant_pars` argument, the `scale_global` is fixed to 1.
+In this application, we have a total of 7 possible moderators, including the dummy variables for the categorical moderator "model".
+We can visualize the implied prior on the number of nonzero coefficients for different values of `relevant_pars`: p0 = 1; p0 = 3; p0 = 6; or p0 = NA, in which case no prior information is given and `scale_global`= 1.
+
+<!-- Caspar: zou het mogelijk zijn om dit nog als functie in te bouwen in het package? Het benodigde stan model staat nu bij de andere stan modellen.
+-->
+
+```{r exprior, eval = TRUE}
+mod <- stan_model("./prior_meff.stan")
+meff_prior_fun <- function(priorinfo = TRUE, p0){
+  D <- ncol(datdum) - 2
+  n <-  nrow(datdum)
+  sigma <- 1
+
+  vars <- apply(datdum, 2, var)[-c(1:2)]
+
+  if(priorinfo == TRUE){
+    tausq0 <-  p0/(D-p0)*(sigma/sqrt(n))
+  } else if(priorinfo == FALSE){
+    p0 <- NA
+    tausq0 <- 1
+  }
+
+  dat <- list(tausq0 = tausq0,
+              D = D,
+              n = n,
+              sigma = sigma, # fixed to 1 in the current implementation; alternative would be to scale to tau
+              s2 = vars)
+  fit <- sampling(mod, data = dat, iter = 4000)
+  draws <- as.matrix(fit)
+  df <- cbind.data.frame("p0" = paste0("p0 = ", p0),
+                         "draws" = draws[, "meff"])
+  return(df)
+}
+
+df1 <- meff_prior_fun(priorinfo = FALSE)
+df2 <- meff_prior_fun(priorinfo = TRUE, p0 = 1)
+df3 <- meff_prior_fun(priorinfo = TRUE, p0 = 3)
+df4 <- meff_prior_fun(priorinfo = TRUE, p0 = 6)
+df <- rbind.data.frame(df1, df2, df3, df4)
+
+# plot
+ggplot(df, aes(x=draws)) + 
+  geom_histogram() +
+  facet_wrap(~p0) +
+ theme_bw() + 
+  xlab("Effective number of nonzero coefficients") + 
+  ylab("") +
+  theme(axis.text.y = element_blank(),
+        axis.ticks.y = element_blank())
+```
+
+It is clear that the implied prior on the number of nonzero coefficients follows the prior information it has been given, with more mass on a small number of relevant moderators if that is expected a priori (p0 = 1) and more mass on a larger number of relevant moderators if that is expected a priori (p0 = 6).
+Interestingly, when no prior information is provided (p0 = NA), the default `global_scale` setting of 1 implies a relatively large number of nonzero coefficients, which is important to keep in mind when using this default setting.
+
+## Regularized meta-analysis with the horseshoe prior
+Next, we run the model using the default hyperparameter settings.
+
+<!-- Caspar: in de originele toepassing met 26 moderatoren kreeg ik een foutmelding als ik probeerde te standaardizeren via de brma functie zelf, maar nu doet ie het wel.
+Misschien iets om nog even naar te kijken hoe dat precies komt?
+-->
+
+```{r exmodel1, eval = TRUE}
+fit.hs1 <- brma(yi ~ .,
+                data = datdum,
+                vi = "vi",
+                method = "hs",
+                standardize = TRUE,
+                prior = c(df = 1, df_global = 1, df_slab = 4, scale_global = 1, scale_slab = 1, relevant_pars = NULL),
+                mute_stan = FALSE)
+```
+
+### Convergence
+By setting `mute_stan = FALSE` we can see how far the sampling procedure is and we obtain all messages from Stan, the computational back-end of `brma()`.
+This is important to assess convergence of the sampler to the posterior distribution.
+Various numeric and visual diagnostics exist to assess convergence.
+If any serious convergence issues occur, Stan will provide warning messages.
+One warning message often seen with the horseshoe prior is that of divergent transitions after warmup.
+Divergent transitions can result in biased estimates, but if the number of divergences is small and the other convergence diagnostics do not indicate any issues, the posterior distribution is often good enough to safely interpret the results.
+In some cases, the number of divergences can be reduced by increasing the values for the degrees of freedom parameters.
+
+In this case, the default settings result in 111 divergent transitions.
+Increasing both `df_global` and `df_slab` to 5 results in slightly less divergences but does not have any substantial influence on the results.
+
+```{r exmodel2, eval = TRUE}
+fit.hs2 <- brma(yi ~ .,
+                data = datdum,
+                vi = "vi",
+                method = "hs",
+                standardize = TRUE,
+                prior = c(df = 5, df_global = 5, df_slab = 4, scale_global = 1, scale_slab = 1, relevant_pars = NULL),
+                mute_stan = FALSE)
+```
+
+Traceplots can be created for each parameter to visualize the MCMC draws, for example using the `bayesplot` package.
+Ideally, these traceplots look like 'fat caterpillars' with the different MCMC chains mixing together.
+Note that there are many auxiliary parameters used for the regularized horseshoe prior.
+No information on these parameters is returned in the `brma` fitobject, however, once the fitobject is transformed into a Stan object for plotting, these parameters are included.
+
+```{r extrace, eval = TRUE}
+fit <- as.stan(fit.hs1)
+posterior <- as.array(fit)
+pars <- dimnames(posterior)$parameters
+parsel <- c("Intercept", pars[grep("betas", pars)], "tau2")
+mcmc_trace(posterior, pars = parsel)
+```
+
+Additionally, convergence can be checked manually by asking for the summary of the fitobject:
+
+```{r exsumm, eval = TRUE}
+summary(fit.hs1)
+```
+
+The column `Rhat` provides information on the split $\hat{R}$, a version of the potential scale reduction factor (PSRF; @GelmanRubin1992).
+`Rhat` values close to 1 indicate convergence.
+In addition, the column `n_eff` provides information on the number of effective MCMC samples, which should be high relative to the total number of samples.
+These diagnostics can be easily visualized using the `bayesplot` package.
+
+```{r exrhat, eval = TRUE}
+rhats <- rhat(fit)
+mcmc_rhat(rhats[names(rhats) %in% parsel])
+```
+
+```{r exeffn, eval = TRUE}
+ratios_neff <- neff_ratio(fit)
+mcmc_neff(ratios_neff[names(ratios_neff) %in% parsel])
+```
+
+All `Rhat` values are close to 0, indicating convergence.
+The ratios of effective number of MCMC samples to total number of MCMC samples are on the low side.
+An often used heuristic is to consider ratios smaller than 0.1 as problematic.
+Even though this is not the case here, it might still be a good idea to increase the number of MCMC iterations.
+
+### Results
+We can request the results using the `summary()` function, which provides the posterior mean estimate for the effect of each moderator.
+Since Bayesian penalization does not automatically shrink estimates exactly to zero, some additional criterion is needed to determine which moderators should be selected in the model.
+Currently, this is done using the 95% credible intervals, with a moderator being selected if zero is excluded in this interval.
+In the `summary` this is denoted by an asterisk for that moderator.
+In this model, there are no moderators for which the 95% CI excludes 0.
+The results can also be visualized.
+
+```{r exres, eval = TRUE}
+summary(fit.hs1)
+
+# plot
+df <- as.data.frame(summary(fit.hs1)[[1]])
+df$par <- rownames(df)
+plotdat <- filter(df, !par %in% c("Intercept", "tau2"))
+ggplot(plotdat, aes(x = mean, y = par)) +
+  geom_point() +
+  geom_errorbar(aes(xmin = `2.5%`, xmax = `97.5%`), width = 0.1) +
+  theme_bw() + xlab("Posterior mean") + ylab("")
+```
+
+## Prior sensitivity
+Finally, we run the model with different prior hyperparameters to assess the sensitivity of the results to the chosen values of the hyperparameters.
+Specifically, we focus on different settings for the expected number of relevant moderators `relevant_pars`.
+
+```{r expriorsens, eval = TRUE}
+fit.hs3 <- brma(yi ~ .,
+                data = datdum,
+                vi = "vi",
+                method = "hs",
+                standardize = FALSE,
+                prior = c(df = 1, df_global = 1, df_slab = 4, scale_global = 1, scale_slab = 1, relevant_pars = 1),
+                mute_stan = FALSE)
+
+fit.hs4 <- brma(yi ~ .,
+                data = datdum,
+                vi = "vi",
+                method = "hs",
+                standardize = FALSE,
+                prior = c(df = 1, df_global = 1, df_slab = 4, scale_global = 1, scale_slab = 1, relevant_pars = 3),
+                mute_stan = FALSE)
+
+fit.hs5 <- brma(yi ~ .,
+                data = datdum,
+                vi = "vi",
+                method = "hs",
+                standardize = FALSE,
+                prior = c(df = 1, df_global = 1, df_slab = 4, scale_global = 1, scale_slab = 1, relevant_pars = 6),
+                mute_stan = FALSE)
+
+# plot
+df.fun <- function(fit, prior){
+  plotdat <- data.frame(fit$coefficients)
+  plotdat$par <- rownames(plotdat)
+  plotdat$Prior <- prior
+  return(plotdat)
+}
+
+df1 <- df.fun(fit.hs1, prior = "hs default")
+df3 <- df.fun(fit.hs3, prior = "hs with p0 = 1")
+df4 <- df.fun(fit.hs4, prior = "hs with p0 = 3")
+df5 <- df.fun(fit.hs5, prior = "hs with p0 = 6")
+
+df <- rbind.data.frame(df1, df3, df4, df5)
+df$par <- as.factor(df$par)
+plotdat <- filter(df, !par %in% c("Intercept", "tau2"))
+
+pd <- 0.5
+
+ggplot(plotdat, aes(x=mean, y=par, group = Prior)) + 
+  geom_errorbar(aes(xmin=X2.5., xmax=X97.5., colour = Prior), width=.1, position = position_dodge(width = pd)) +
+  geom_point(aes(colour = Prior), position = position_dodge(width = pd)) +
+  theme_bw() + xlab("Posterior mean") + ylab("")
+```
+
+When running the models with prior information regarding the number of relevant moderators, it becomes clear that there are convergence issues.
+The number of divergent transitions is very high and the maximum treedepth is often exceeded.
+For the model with `relevant_pars` = 1, these convergence issues are also reflected in high `rhat` values.
+When comparing the results, it is clear that the horseshoe specifications that include prior information shrink coefficients more towards zero compared to the default setting.
+This is a consequence of the fact that these settings imply more prior mass on smaller numbers of relevant moderators, as was shown previously.
+However, in this situation, this high shrinkage results in convergence issues so these results should not be fully trusted but are only shown for the purpose of illustration.
+In our experience, the default prior settings are suitable for most applications, but conducting a prior sensitivity analysis as well as prior visualizations before running the analysis can help users to better understand the prior and its influence on the results.
+
 # Discussion
 
-This simulation study validated the performance of two versions of the new BRMA algorithm, relative to state-of-the-art meta-regression (RMA).
+This study presented a novel algorithm to select relevant moderators that can explain heterogeneity in meta-analyses, using Bayesian shrinkage priors. 
+The simulation study validated the performance of two versions of the new BRMA algorithm, relative to state-of-the-art meta-regression (RMA).
 Our analyses examined the algorithms' predictive performance, which is a measure of generalizability,
@@
 This code also enables researchers to conduct Monte Carlo power analyses for applied research.
-Another limitation is that the present study did not examine the effect of multicollinear predictors.
+
+A second limitation is that the present study did not examine the effect of multicollinear predictors.
 Regularizing estimators typically have an advantage over OLS regression in the presence of multicollinearity;
@@
 
-A final limitation is that the present study did not examine the effect of dependent data (e.g., multiple effect sizes per study).
+A third limitation is that the present study did not examine the effect of dependent data (e.g., multiple effect sizes per study).
 In principle, the BRMA algorithm can accommodate dependent data by means of three-level multilevel analysis.
 To our knowledge, there are no theoretical reasons to expect that dependent data would result in a different pattern of findings than we found for independent data, but future research is required to ascertain this.
+
+A final limitation of the current implementation is that it relies on 95% credible intervals to select relevant moderators.
+However, these marginal credible intervals can behave differently compared to the joint credible intervals ([@PiironenEtal2017]).
+A future direction of research is therefore to implement more advanced selection procedures, such as projection predictive variable selection ([@PiironenVehtari2017a]).
 
@@
 One future direction of research is thus to develop a frequentist estimator for regularized meta-regression.
-Additionally, the current implementation relies on 95% credible intervals to select relevant moderators.
-However, these marginal credible intervals can behave differently compared to the joint credible intervals ([@PiironenEtal2017]).
-A second future direction of research is therefore to implement more advanced selection procedures, such as projection predictive variable selection ([@PiironenVehtari2017a]).
 
@@
 
-Finally, with regards to publication, we highly recommend sharing the data and
+Finally, with regard to publication, we highly recommend sharing the data and
 syntax for the meta-analysis publicly; for example, by making the entire paper reproducible using the Workflow for Reproducible Code in Science (WORCS; REF).
@@
 In such cases, Bayesian estimation may converge on a solution where frequentist estimation does not [@kohliFittingLinearLinearPiecewise2015].
-Similarly, BRMA may perform better in the presence of multicolinearity among predictors,
+Similarly, BRMA may perform better in the presence of multicollinearity among predictors,
 which can be examined using the function `vif()` in the R-package `metafor`.
 Values exceeding 5 are cause for concern.
-Multicolinearity increases the variance of regression coefficients.
+Multicollinearity increases the variance of regression coefficients.
 BRMA may have an advantage here, because the regularizing priors restrict variance.
-If multicolinearity is observed, researchers might thus prefer BRMA over RMA.
+If multicollinearity is observed, researchers might thus prefer BRMA over RMA.
 

### 2022-04-20 paper/manuscript.Rmd
simplify applied example

--- 2022-03-18 paper/manuscript.Rmd
@@
 ```{r setup, include = FALSE}
+run_everything = FALSE
 library("papaja")
@@
 
+# Applied example
+
+In this application, we will work with the `pema::bonapersona` data [@BonapersonaEtal2019].
+This meta-analysis of over 400 experiments investigated the effects of early life adversity on cognitive performance in rodents.
+This example uses a small subset of the more than 30 moderators.
+<!-- We focus specifically on how to choose the different hyperparameters of the regularized horseshoe prior. -->
+
+```{r exdata, eval = TRUE}
+# Set random seed
+set.seed(1)
+# Load relevant packages
+library(pema)
+library(tidySEM)
+library(ggplot2)
+library(bayesplot)
+
+# Select data to analyze
+df <- bonapersona[ , c("yi", "vi", "mTimeLength", "year", "model", "ageWeek")] 
+# Impute missings
+df$ageWeek[is.na(df$ageWeek)] <- median(df$ageWeek, na.rm = TRUE)
+```
+
+## Visualizing the prior
+
+Our simulation study shows good performance with default hyperparameters.
+However, experienced users may want to customize the prior.
+Visualizing the prior can be helpful in this process.
+This is accomplished using the interactive application visualization application available through `shiny_prior()`.
+The user can plot the prior distributions resulting from different sets of hyperparameters and compare them.
+Increasing the values of the scale parameters (`scale_global` and `hs_scale_slab`) results in a more spread out prior, which applies less regularization.
+Increasing the degrees of freedom (`df_global` and `df_slab`) results in thinner tails, which applies more regularization.
+<!-- One advantage of the regularized horseshoe prior is its ability to define the prior in terms of the expected number of nonzero coefficients, using the argument `relevant_pars`. -->
+<!-- This argument in turn influences the other hyperparameters. -->
+<!-- We can also plot the implied prior on the effective number of nonzero coefficients given specific hyperparameters. -->
+<!-- In this application, we have a total of 7 possible moderators, including the dummy variables for the categorical moderator "model".
+We can visualize the implied prior on the number of nonzero coefficients for different values of `relevant_pars`: p0 = 1; p0 = 3; p0 = 6; or p0 = NA, in which case no prior information is given and `scale_global`= 1.
+-->
+
+```{r exprior, eval = FALSE, include = FALSE}
+mod <- stan_model("../inst/stan/prior_meff.stan")
+datdum <- data.frame(model.matrix(~., df)[, -1])
+meff_prior_fun <- function(priorinfo = TRUE, p0){
+  D <- ncol(datdum) - 2
+  n <-  nrow(datdum)
+  sigma <- 1
+
+  vars <- apply(datdum, 2, var)[-c(1:2)]
+
+  if(priorinfo == TRUE){
+    tausq0 <-  p0/(D-p0)*(sigma/sqrt(n))
+  } else if(priorinfo == FALSE){
+    p0 <- NA
+    tausq0 <- 1
+  }
+
+  dat <- list(tausq0 = tausq0,
+              D = D,
+              n = n,
+              sigma = sigma, # fixed to 1 in the current implementation; alternative would be to scale to tau
+              s2 = vars)
+  fit <- sampling(mod, data = dat, iter = 4000)
+  draws <- as.matrix(fit)
+  df <- cbind.data.frame("p0" = paste0("p0 = ", p0),
+                         "draws" = draws[, "meff"])
+  return(df)
+}
+
+df1 <- meff_prior_fun(priorinfo = FALSE)
+df2 <- meff_prior_fun(priorinfo = TRUE, p0 = 1)
+df3 <- meff_prior_fun(priorinfo = TRUE, p0 = 3)
+df4 <- meff_prior_fun(priorinfo = TRUE, p0 = 6)
+df <- rbind.data.frame(df1, df2, df3, df4)
+
+# plot
+ggplot(df, aes(x=draws)) + 
+  geom_histogram() +
+  facet_wrap(~p0) +
+ theme_bw() + 
+  xlab("Effective number of nonzero coefficients") + 
+  ylab("") +
+  theme(axis.text.y = element_blank(),
+        axis.ticks.y = element_blank())
+```
+<!-- It is clear that the implied prior on the number of nonzero coefficients follows the prior information it has been given, with more mass on a small number of relevant moderators if that is expected a priori (p0 = 1) and more mass on a larger number of relevant moderators if that is expected a priori (p0 = 6).
+Interestingly, when no prior information is provided (p0 = NA), the default `global_scale` setting of 1 implies a relatively large number of nonzero coefficients, which is important to keep in mind when using this default setting.
+-->
+
+In this example, we will estimate the model using default settings, which includes a horseshoe prior with default hyperparameters.
+To see the default values, open the function documentation using `?brma`.
+
+```{r exmodel1, echo = TRUE, eval = FALSE}
+fit_hs1 <- brma(yi ~ ., data = df, vi = "vi")
+```
+```{r, echo = FALSE, eval = run_everything}
+fit_hs1 <- brma(yi ~ ., data = df, vi = "vi")
+saveRDS(fit_hs1, "fit_hs1.RData")
+```
+```{r, echo = FALSE, eval = TRUE}
+fit_hs1 <- readRDS("fit_hs1.RData")
+```
+
+Note the warning message about divergent transitions, which may indicate problems with model convergence.
+This warning is generated by `Stan`, the computational back-end of `brma()`.
+Divergent transitions can result in biased estimates. 
+However, if the number of divergences is small and there are no further indications of non-convergence,
+the posterior distribution is often good enough to safely interpret the results.
+In some cases, this problem may be resolved by increasing the values for the degrees of freedom parameters.
+Note that increasing both `df_global` and `df_slab` to 5 results in fewer divergences,
+but does not otherwise influence the substantive interpretation of the results:
+
+```{r exmodel2, eval = FALSE, echo = TRUE}
+fit_hs2 <- brma(yi ~ .,
+                data = df,
+                vi = "vi",
+                prior = c(df = 5, df_global = 5, df_slab = 4, scale_global = 1, scale_slab = 1, relevant_pars = NULL))
+```
+```{r, echo = FALSE, eval = run_everything}
+fit_hs2 <- brma(yi ~ .,
+                data = df,
+                vi = "vi",
+                prior = c(df = 5, df_global = 5, df_slab = 4, scale_global = 1, scale_slab = 1, relevant_pars = NULL))
+saveRDS(fit_hs2, "fit_hs2.RData")
+```
+```{r, echo = FALSE, eval = TRUE}
+fit_hs2 <- readRDS("fit_hs2.RData")
+```
+
+In general, it is prudent to assess model convergence.
+Various numeric and visual diagnostics exist, for example, in the R-package `rstan`.
+These functions can be used by converting a `brma` object to a `stanfit` object, using the function `pema::as.stan()`:
+
+```{r}
+fit_stan <- as.stan(fit_hs1)
+check_hmc_diagnostics(fit_stan)
+```
+
+Additionally, traceplots can be created for each parameter to visualize the MCMC draws using the `bayesplot` R-package.
+The traceplots of a converged model look like "fat caterpillars", with the different MCMC chains mixing together: 
+<!-- Note that there are many auxiliary parameters used for the regularized horseshoe prior.
+No information on these parameters is returned in the `brma` fitobject, however, once the fitobject is transformed into a Stan object for plotting, these parameters are included.
+-->
+
+```{r extrace, eval = FALSE, echo = TRUE}
+mcmc_trace(fit_stan, pars = c("Intercept", "year"))
+```
+```{r, eval = run_everything, echo = FALSE}
+p <- mcmc_trace(fit_stan, pars = c("Intercept", "year"))
+ggsave("traceplot.png", p, device = "png", width = 4, height = 3, dpi = 300, scale = 1.5)
+```
+```{r, eval = TRUE, echo = FALSE}
+knitr::include_graphics("traceplot.png")
+```
+
+Convergence can also be checked by examining for the summary of the model object.
+The column `Rhat` provides information on the split $\hat{R}$, a version of the potential scale reduction factor (PSRF; @GelmanRubin1992).
+Values close to 1 indicate convergence.
+In addition, the column `n_eff` provides information on the number of effective (independent) MCMC samples, which should be high relative to the total number of samples (in this case, 4000):
+
+```{r exsumm, eval = TRUE}
+summary(fit_hs1)
+```
+All `Rhat` values are close to 1, indicating convergence.
+The effective number of MCMC samples is relatively small compared to the total number of MCMC samples.
+An often used heuristic is to consider ratios smaller than 0.1 as problematic.
+Even though this is not the case here, consider increasing the number of MCMC iterations.
+<!-- These diagnostics can be easily visualized using the `bayesplot` package: -->
+
+```{r exrhat, eval = FALSE, echo = FALSE}
+rhats <- rhat(fit)
+mcmc_rhat(rhats[names(rhats) %in% parsel])
+```
+
+```{r exeffn, eval = FALSE, echo = FALSE}
+ratios_neff <- neff_ratio(fit)
+mcmc_neff(ratios_neff[names(ratios_neff) %in% parsel])
+```
+
+<!-- ### Results -->
+
+The `summary()` function also provides summary statistics for the model parameters.
+For each parameter, the posterior mean, standard deviation, and quantiles are reported by default (the 50% quantile is the median).
+To perform inference, consider using the posterior median and 95% credible interval (2.5% - 97.5%).
+Since Bayesian penalization does not automatically shrink estimates exactly to zero,
+we retained moderators when the 95% credible interval excluded zero in the simulation study.
+The `summary()` flags such parameters with an asterisk.
+If the model is converted using `as.stan()`, the results can also be visualized using standard `rstan` functions.
+In this example, we conclude that there are no moderators for which the 95% CI excludes zero.
+
+```{r exres, eval = FALSE}
+plot(fit_stan, pars = rownames(coef(fit_hs1))[2:8])
+```
+```{r, eval = run_everything, echo = FALSE}
+p <- plot(fit_stan, pars = rownames(coef(fit_hs1))[2:8])
+ggsave("plot_es.png", p, device = "png", width = 4, height = 3, dpi = 300, scale = 1.5)
+```
+```{r, eval = TRUE, echo = FALSE}
+knitr::include_graphics("plot_es.png")
+```
+
+<!-- ## Prior sensitivity -->
+
+<!-- To assess the sensitivity of the results to the chosen values of the hyperparameters, -->
+<!-- one can run the model with a different prior. -->
+<!-- In this example, we vary the expected number of relevant moderators `relevant_pars`.  -->
+
+```{r expriorsens, eval = FALSE, echo = FALSE}
+fit_hs3 <- brma(yi ~ .,
+                data = datdum,
+                vi = "vi",
+                method = "hs",
+                standardize = FALSE,
+                prior = c(df = 1, df_global = 1, df_slab = 4, scale_global = 1, scale_slab = 1, relevant_pars = 1),
+                mute_stan = FALSE)
+
+fit_hs4 <- brma(yi ~ .,
+                data = datdum,
+                vi = "vi",
+                method = "hs",
+                standardize = FALSE,
+                prior = c(df = 1, df_global = 1, df_slab = 4, scale_global = 1, scale_slab = 1, relevant_pars = 3),
+                mute_stan = FALSE)
+
+fit_hs5 <- brma(yi ~ .,
+                data = datdum,
+                vi = "vi",
+                method = "hs",
+                standardize = FALSE,
+                prior = c(df = 1, df_global = 1, df_slab = 4, scale_global = 1, scale_slab = 1, relevant_pars = 6),
+                mute_stan = FALSE)
+
+# plot
+df.fun <- function(fit, prior){
+  plotdat <- data.frame(fit$coefficients)
+  plotdat$par <- rownames(plotdat)
+  plotdat$Prior <- prior
+  return(plotdat)
+}
+
+df1 <- df.fun(fit_hs1, prior = "hs default")
+df3 <- df.fun(fit_hs3, prior = "hs with p0 = 1")
+df4 <- df.fun(fit_hs4, prior = "hs with p0 = 3")
+df5 <- df.fun(fit_hs5, prior = "hs with p0 = 6")
+
+df <- rbind.data.frame(df1, df3, df4, df5)
+df$par <- as.factor(df$par)
+plotdat <- filter(df, !par %in% c("Intercept", "tau2"))
+
+pd <- 0.5
+
+ggplot(plotdat, aes(x=mean, y=par, group = Prior)) + 
+  geom_errorbar(aes(xmin=X2.5., xmax=X97.5., colour = Prior), width=.1, position = position_dodge(width = pd)) +
+  geom_point(aes(colour = Prior), position = position_dodge(width = pd)) +
+  theme_bw() + xlab("Posterior mean") + ylab("")
+```
+
+<!-- When running the models with prior information regarding the number of relevant moderators, it becomes clear that there are convergence issues.
+The number of divergent transitions is very high and the maximum treedepth is often exceeded.
+For the model with `relevant_pars` = 1, these convergence issues are also reflected in high `rhat` values.
+-->
+<!-- When comparing the results, it is clear that the horseshoe specifications that include prior information shrink coefficients more towards zero compared to the default setting.
+This is a consequence of the fact that these settings imply more prior mass on smaller numbers of relevant moderators, as was shown previously.
+However, in this situation, this high shrinkage results in convergence issues so these results should not be fully trusted but are only shown for the purpose of illustration.
+In our experience, the default prior settings are suitable for most applications, but conducting a prior sensitivity analysis as well as prior visualizations before running the analysis can help users to better understand the prior and its influence on the results.
+-->
+
 # Discussion
 
-This simulation study validated the performance of two versions of the new BRMA algorithm, relative to state-of-the-art meta-regression (RMA).
+This study presented a novel algorithm to select relevant moderators that can explain heterogeneity in meta-analyses, using Bayesian shrinkage priors. 
+The simulation study validated the performance of two versions of the new BRMA algorithm, relative to state-of-the-art meta-regression (RMA).
 Our analyses examined the algorithms' predictive performance, which is a measure of generalizability,

### 2022-04-20 R/as_stan.R

@@ -28,6 +28,46 @@ as.stan.brma <- function(x, ...){
   for(thisatt in as_atts){
     attr(out, which = thisatt) <- x[[thisatt]]
   }
+
+  # Try to replace all betas with true parameter names
+  renm <- rownames(x$coefficients)
+  renm <- renm[!renm %in% c("Intercept", "tau2", "tau2_w", "tau2_b")]
+  names(renm) <- paste0("betas[", 1:x$fit@par_dims$betas, "]")
+
+  oldposition <- which(names(out@sim$samples[[1]]) %in% names(renm))
+  oldnames <- names(out@sim$samples[[1]])[oldposition]
+  newnames <- unname(renm[oldnames])
+
+  for(thischain in seq_along(out@sim$samples)){
+    names(out@sim$samples[[thischain]])[oldposition] <- newnames
+  }
+
+  isbetas <- which(out@sim$pars_oi == "betas")
+  out@sim$pars_oi <- append(out@sim$pars_oi, newnames, after = isbetas)
+  out@sim$pars_oi <- out@sim$pars_oi[-isbetas]
+
+  out@model_pars <- append(out@model_pars, newnames, after = isbetas)
+  out@model_pars <- out@model_pars[-isbetas]
+
+  out@sim$fnames_oi[oldposition] <- newnames
+
+  appendthis <- replicate(length(newnames), {vector(mode = "numeric")})
+  names(appendthis) <- newnames
+
+  out@sim$dims_oi <- append(out@sim$dims_oi, appendthis, after = isbetas)
+  out@sim$dims_oi <- out@sim$dims_oi[-isbetas]
+
+  out@par_dims <- append(out@par_dims, appendthis, after = isbetas)
+  out@par_dims <- out@par_dims[-isbetas]
+
+  for(thischain in seq_along(out@inits)){
+    appendthis <- as.list(out@inits[[thischain]][["betas"]])
+    names(appendthis) <- newnames
+    out@inits[[thischain]] <- append(out@inits[[thischain]], appendthis, after = isbetas)
+    out@inits[[thischain]][["betas"]] <- NULL
+  }
+
   attr(out, which = "type") <- "brma"
   return(out)
 }
+

### 2022-04-20 R/brma.R

@@ -227,6 +227,11 @@ brma.formula <-
     eval.parent(cl)
 }
 
+#' @param x An k x m numeric matrix, where k is the number of effect sizes and m
+#' is the number of moderators.
+#' @param y A numeric vector of k effect sizes.
+#' @param y Logical, indicating whether or not an intercept should be included
+#' in the model.
 #' @method brma default
 #' @export
 #' @rdname brma

### 2022-04-22 paper/manuscript.Rmd
final check and removed typos

@@
 De rest van de global scale wordt berekend buiten het Stan model om in de brma functie zelf.
--->
+Dit is ondertussen gecheckt en in de huidige implementatie is sigma op 1 gezet, wat de meest voor de hand liggende adhoc manier is.
+Uitgebreider onderzoek is nodig om te kijken of scaling naar tau beter zou kunnen zijn.
+Overigens is dit enkel relevant als er prior info wordt meegenomen via relevant_pars -->
 The thickness of the tails is controlled by two degrees of freedom parameters, $\nu_1$ and $\nu_2$, which default to 1 in `brma()`.
@@
 Visualizing the prior can be helpful in this process.
-This is accomplished using the interactive application visualization application available through `shiny_prior()`.
+This is accomplished using the interactive visualization application available through `shiny_prior()`.
 The user can plot the prior distributions resulting from different sets of hyperparameters and compare them.
-Increasing the values of the scale parameters (`scale_global` and `hs_scale_slab`) results in a more spread out prior, which applies less regularization.
+For the regularized horseshoe, increasing the values of the scale parameters (`scale_global` and `hs_scale_slab`) results in a more spread out prior, which applies less regularization.
 Increasing the degrees of freedom (`df_global` and `df_slab`) results in thinner tails, which applies more regularization.
@@
 
-In this example, we will estimate the model using default settings, which includes a horseshoe prior with default hyperparameters.
+In this example, we will estimate the model using the default settings, which implies a horseshoe prior with default hyperparameters.
 To see the default values, open the function documentation using `?brma`.
@@
 
-Convergence can also be checked by examining for the summary of the model object.
+Convergence can also be checked by examining the summary of the model object.
 The column `Rhat` provides information on the split $\hat{R}$, a version of the potential scale reduction factor (PSRF; @GelmanRubin1992).
@@
 we observed that BRMA with a horseshoe prior had the greatest bias towards zero across simulation conditions, followed by LASSO, and then RMA.
-Note that all algorithms provided, on average, negatively biased estimated.
+Note that all algorithms provided, on average, negatively biased estimates.
 The variance of the estimates followed the opposite pattern.
 This unsurprising result illustrates the bias-variance trade-off in penalized regression.
-The greater predictive performance of the BRMA algorithms is a direct consequence off this trade-off.
+The greater predictive performance of the BRMA algorithms is a direct consequence of this trade-off.
 
@@
 In applied research, it is often not known what the true shape of the association between a moderator and effect size is.
-Thus, model mis-specification is likely to occur.
+Thus, model misspecification is likely to occur.
 One advantage of BRMA is that it can accommodate more moderators than RMA and has superior specificity.
@@
 
-Alghough the use of Bayesian estimation has several advantages, one major downside is that Bayesian models are not directly comparable with frequentist models.
+Although the use of Bayesian estimation has several advantages, one major downside is that Bayesian models are not directly comparable with frequentist models.
 Another disadvantage is that Bayesian estimation is typically more computationally expensive than frequentist estimation.
@@
 
-BRMA aims to address the challenge that arises when meta-analysing heterogeneous bodies of literature, with few studies relative to the number of moderators.
+BRMA aims to address the challenge that arises when meta-analyzing heterogeneous bodies of literature, with few studies relative to the number of moderators.
 BRMA can be used to identify relevant moderators when it is not known beforehand which moderators are responsible for between-studies differences in observed effect sizes.
@@
 because it demonstrated the best predictive performance and most attractive trade-off between sensitivity and specificity in our simulations.
+Visualizations of the prior distribution can be helpful to understand the influence of choosing specific hyperparameters and a prior sensitivity analysis after estimation can further aid this understanding.
 
@@
 syntax for the meta-analysis publicly; for example, by making the entire paper reproducible using the Workflow for Reproducible Code in Science (WORCS; REF).
+<!--Caspar: hier mist nog een ref.
+Ik krijg errors als ik alles probeer te knitten, dus weet niet of alle andere referenties correct worden weergegeven.
+-->
 Transparency allows readers and reviewers to verify that methods were correctly applied, and try alternative analyses.
@@
 # Conclusion 
+<!-- Ik weet niet hoe we zitten qua woordenlimiet, maar als er gekort moet worden zou deze laatste conclusie sectie er wat mij betreft uit kunnen. Is vooral herhaling van wat eerder al is genoemd. -->
 

### 2022-04-22 paper/manuscript.Rmd
Update software and paper

--- 2022-04-20 paper/manuscript.Rmd
@@
       - Conceptualization
-      - Writing - Original Draft Preparation
-      - Programming front- and back-end
+      - Formal Analysis
+      - Funding acquisition
+      - Methodology
+      - Project administration
+      - Software
+      - Supervision
+      - Writing – original draft
+      - Writing – review & editing
   - name: "Sara van Erp"
@@
     role:
-      - Writing - Contributions and feedback
-      - Programming back-end
+      - Methodology
+      - Software
+      - Writing – original draft
+      - Writing – review & editing
   - name: "Eli-Boaz Clapper"
@@
     role:
-      - Writing - Contributions and feedback
-      - Preliminary analyses
+      - Formal Analysis
+      - Writing – original draft
+      - Writing – review & editing
 affiliation:
@@
 authornote: |
-  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
-
-  Author contributions: CvL conceived of the method; wrote simulation, analysis,
-  and package code; and drafted the manuscript. SE implemented the method in
-  stan and contributed package code; contributed paragraphs and revised the
-  manuscript. EC wrote manuscript outline and contributed paragraphs; curated
-  existing lab notes; conducted literature research; performed initial analyses.
+  This is a preprint paper, generated from Git Commit # `r substr(gert::git_commit_id(),1,7)`. This work was funded by a NWO Veni Grant (NWO Grant Number VI.Veni.191G.090), awarded to the lead author.
 
@@
 
-bibliography      : ["r-references.bib", "references.bib", "sara-references.bib", "eli-references.bib"]
+bibliography      : ["r-references.bib", "references.bib",
+                     "sara-references.bib", "eli-references.bib"]
 
@@
 classoption       : "man"
+knit: worcs::cite_essential
 output            : papaja::apa6_pdf
@@
 ```{r setup, include = FALSE}
-run_everything = FALSE
+run_everything <- FALSE
 library("papaja")
@@
 set.seed(42)
-knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
+knitr::opts_chunk$set(cache.extra = knitr::rand_seed, warning = FALSE)
 ```
@@
 whereby effect sizes from multiple similar studies are aggregated.
-In its simplest form, this aggregation consists of the computation of a summary effect as a weighted average of the observed effect sizes.
-This average is weighted to account for the fact that some observed effect sizes are assumed to be more informative about the underlying population effect.
-Each effect size is assigned a weight that determines how influential it is in calculating the summary effect.
-This weight is based on specific assumptions;
-for example, the *fixed effect* model assumes that all observed effect sizes reflect one underlying true population effect size.
-This assumption is well-suited to the situation where effect sizes from close replication studies are meta-analyzed [@higginsReevaluationRandomeffectsMetaanalysis2009, fabrigar_conceptualizing_2016, maxwell_is_2015].
+In its simplest form, this aggregation consists of a weighted average of the observed effect sizes.
+Weighting accounts for the fact that some observed effect sizes are assumed to be more informative about the underlying population effect.
+<!-- Each effect size is assigned a weight that determines how influential it is in calculating the summary effect. -->
+The weights are based on specific assumptions;
+for example, the *fixed effect* model assumes that all observed effect sizes reflect one underlying true population effect.
+This assumption is well-suited to the situation where effect sizes from close replication studies are meta-analyzed [@higginsReevaluationRandomeffectsMetaanalysis2009; @@fabrigarConceptualizingEvaluatingReplication2016; @@maxwellPsychologySufferingReplication2015].
 The *random effects* model, by contrast, assumes that population effect sizes follow a normal distribution.
 Each observed effect size provides information about the mean and standard deviation of this distribution of population effect sizes.
-This assumption is more appropriate when studies are conceptually similar and differences between them are random [@higginsReevaluationRandomeffectsMetaanalysis2009, fabrigar_conceptualizing_2016, maxwell_is_2015].
+This assumption is more appropriate when studies are conceptually similar and differences between them are random [@higginsReevaluationRandomeffectsMetaanalysis2009; @@fabrigarConceptualizingEvaluatingReplication2016; @@maxwellPsychologySufferingReplication2015].
 
@@
 Such between-study differences are known as "moderators".
-For example, if studies have been replicated in Europe and the Americas, this difference can be captured by a binary moderator called "continent".
+For example, if studies have been replicated in Europe and the Americas, this difference could be captured by a binary moderator called "continent".
 Alternatively, if studies have used different dosages of the same drug, this may be captured by a continuous moderator called "dosage".
-Systematic heterogeneity in the observed effect sizes can be accounted for using *meta-regression* (Viechtbauer \& López-López, 2015).
+Systematic heterogeneity in the observed effect sizes can be accounted for using *meta-regression* [see @lopez-lopezEstimationPredictivePower2014].
 This technique provides estimates of the effect of one or more study characteristics on the overall effect size,
@@
 
-It is theoretically possible to account for the influence of multiple moderators using meta-regression.
+The influence of multiple moderators can be accounted for using meta-regression.
 However, like any regression-based approach, meta-regression requires a relatively high number of cases (studies) per parameter to obtain sufficient power to examine heterogeneity.
-In practice the number of available studies is often too low to examine heterogeneity reliably (Riley, Higgins, & Deeks, 2011).
+In applied meta-analyses, the number of available studies is often too low to examine heterogeneity reliably [@rileyInterpretationRandomEffects2011].
 At the same time, there are many potential sources of heterogeneity,
@@
 This leads to a problem known as the "curse of dimensionality": the number of candidate moderators is large relative to the number of cases in the data.
-Such cases do not fit comfortably into the
-classic meta-analysis paradigm, which, like any regression-based approach, requires a
-high number of cases per parameter. 
-Between-studies differences thus present a non-trivial challenge to data aggregation
+<!-- This poses a challenge in the -->
+<!-- classic meta-analysis paradigm, which, like any regression-based approach, requires a -->
+<!-- high number of cases per parameter.  -->
+Between-studies differences present a non-trivial challenge to data aggregation
 using classic meta-analytic methods.
-At the same time, it also offers an unexploited
+At the same time, they also provide an unexploited
 opportunity to learn which differences between studies have an impact on the effect size
-found, if adequate exploratory techniques can be developed.
-
-Addressing the curse of dimensionality necessitates *variable selection*:
+found, if adequate exploratory techniques are used.
+
+Addressing this curse of dimensionality necessitates *variable selection*:
 the selection of a smaller subset of relevant moderators from a larger number of candidate moderators.
@@
 This is a focal issue in the discipline of machine learning [@hastieElementsStatisticalLearning2009].
-One technique that facilitates variable selection is *regularization*:
-shrinking model parameters towards zero, such that only larger parameters remain.
-Although this technique biases the parameter estimates,
-it also reduces their variance, which has the advantage of producing more generalizable results that make better predictions for new data [see @hastieElementsStatisticalLearning2009].
-This paper introduces *Bayesian regularized meta-regression* (BRMA),
+There is precedent for the use of machine learning to perform variable selection in meta-analysis [@vanlissaSmallSampleMetaanalyses2020].
+This work used the *random forest* algorithm; a non-parametric approach that largely ignores irrelevant moderators.
+One limitation of random forests is that non-parametric models are harder to interpret,
+particularly for a readership that is accustomed to linear models,
+where the effect of each predictor is described by a single parameter.
+An alternative method for variable selection that can be used in linear models is *regularization*:
+shrinking model parameters towards zero, such that irrelevant moderators are eliminated.
+The present paper introduces *Bayesian regularized meta-regression* (BRMA),
 an algorithm that uses Bayesian estimation with regularizing priors to perform variable selection in meta-analysis.
@@
 \end{equation}
--->
+
 <!--A highly likely consequence is that this will lead to a huge amount of possible moderators (Caserio, 2014).
@@
 the random-effects model assumes that true effects may vary for unknown reasons,
-and thus follow a (normal) distribution of their own (Hedges \& Vevea, 1998).
+and thus follow a (normal) distribution of their own [@hedgesFixedRandomeffectsModels1998].
 This heterogeneity of the true effects is represented by their variance, $\tau^{2}$.
-The random effect model thus assumes that the heterogeneity in observed effects can be decomposed into sampling error and between-studies heterogeneity, resulting in the following equation for the observed effect sizes:
+The random effects model thus assumes that the heterogeneity in observed effects can be decomposed into sampling error and between-studies heterogeneity, resulting in the following equation for the observed effect sizes:
 
@@
 and the error term $\zeta_{i}$ represents residual between-studies heterogeneity.
-This term is still included because unexplained heterogeneity often remains after accounting for the moderators (Thompson \& Sharp, 1999).
-This is a mixed-effects model; the intercept and effects of moderators are treated as fixed and the residual heterogeneity as random (Viechtbauer \& López-López, 2015).
+This term is included because unexplained heterogeneity often remains after accounting for the moderators.
+This is a mixed-effects model; the intercept and effects of moderators are treated as fixed and the residual heterogeneity as random [@lopez-lopezEstimationPredictivePower2014].
 
@@
 It is important to note that some iterative methods do not produce a solution when they fail to converge after a predetermined amount of iteration.-->
-This estimator has low bias, which means that the average value of the estimated regression coefficients and residual heterogeneity is close to their true values (Panityakul et al., 2013; Hardy & Thompson, 1996).
+This estimator has low bias, which means that the average value of the estimated regression coefficients and residual heterogeneity is close to their true values [@panityakulEstimatingResidualHeterogeneity2013].
+<!-- ; (Panityakul et al., 2013; Hardy & Thompson, 1996). -->
 However, this bias comes at the cost of higher variance, which means that the estimated values of a population parameter vary more from one sample to the next. 
 In practice, an estimator with higher variance generalizes less well to new data.
-This phenomenon is known as the *bias-variance tradeoff*.
-Regularization increases bias to reduce variance, and thus produces more generalizable estimates.
+This phenomenon is known as the *bias-variance trade-off*.
+Regularization increases bias to reduce variance.
+A disadvantage of this trade-off is that model parameters can no longer be interpreted as straightforwardly as OLS regression coefficients.
+An advantage is that the resulting model is more generalizable and makes better predictions for new data [see @hastieElementsStatisticalLearning2009].
+
 <!--It needs a starting estimation of $\tau^{2}$, which is usually estimated by one of the non-iterative methods (Viechtbauer \& López-López, 2015).
@@
 
-Regularized regression biases parameter estimates towards zero by including a shrinkage penalty in the estimation process.
-Before examining the Bayesian case, we will explain the principle using frequentist OLS regression as an example.
+Regularized regression biases parameter estimates towards zero.
+Before examining the Bayesian case, we will explain the general principle of regularization in frequentist regression.
 OLS regression estimates the model parameters by minimizing the Residual Sum of Squares (RSS) of the dependent variable, which is given by:
@@
 Penalized regression, by contrast, adds a penalty term to the RSS.
-One commonly used penalty is the L1-norm of the regression coefficients, or LASSO penalty ([@hastieElementsStatisticalLearning2009]),
+One commonly used penalty is the L1-norm of the regression coefficients, or LASSO penalty [@hastieElementsStatisticalLearning2009],
 which corresponds to the sum of their absolute values.
@@
 In this equation, $\lambda$ is a tuning parameter that determines how influential the penalty term will be.
-If $\lambda$ is zero, the shrinkage penalty has no impact at all and the penalized regression will produce the OLS estimates.
+If $\lambda$ is zero, the shrinkage penalty has no impact and the penalized regression will produce the OLS estimates.
 If $\lambda \to \infty$, all coefficients shrink towards zero, producing the null model.
@@
 
-### Standardizing predictors
-
-<!-- Eli? -->
-<!-- * Eli, kan jij het algemene principe van standardization hier uitleggen, met een paar referenties?
-In de volgende paragraaf over intercepts moet ook nog een referentie, over wel/niet standaardizeren van dummies.-->
-<!-- * In BRMA werk het als volgt: -->
-<!--     + By default, all variables are normalized. -->
-<!--     + The penalized model (without an intercept) is estimated on the normalized data -->
-<!--     + The intercept is then restored to the original scale by applying  -->
-<!--     $b_0 = b_{0z} - \mathbf{b}_z\frac{\bar{\mathbf{x}}}{\mathbf{s}_x}$ -->
-<!--     Where b_0 is the intercept, b_0z is the intercept for the normalized predictors, b_z is the vector of     regression coefficients for the normalized predictors, bar x is the vector of means of X, and s_x is the vector of standard deviations of x -->
-<!--     + The regression coefficients are restored to the original scale by applying  -->
-<!--     $\mathbf{b} = \mathbf{b}_z\mathbf{s}_x$ -->
-<!-- * Leg vervolgens uit dat mensen dummies misschien niet willen standaardizeren -->
-<!-- * Gebruikers kunnen de default standaardization overschrijven door een aantal van de variabelen handmatig te standaardizeren, en de vector met means en vector met SDs handmatig mee te geven via het argument `standardize = list(center = meanvec, scale = sdvec)`.
-Als ze een bepaalde variabele NIET willen standaardizeren moeten ze voor die variabele mean= 0 en sd= 1 meegeven.
--->
-
-Penalized regression analyses typically require the scales of predictors to be equivalent ([@tibshirani1996]).
-This is because the regularization penalizes coefficients without regard for their scale.
-If variable scales differ, this can lead to an imbalanced penalization of coefficients that does not reflect differences in variable importance ([@lee2015note]).
-To clarify, a regression parameter $\beta$ can be interpreted as the expected increase in outcome $\mathbf{Y}$ for a one unit increase in predictor $\mathbf{X}$.
-If the scale of predictor $\mathbf{X}$ is increased by a factor 10, its regression coefficient is reduced by a factor 10.
-Standardization is a widely used method for equalizing predictor scales ([@gelman2008scaling]).
-It sets the mean of all predictors to 0 and their standard deviation to 1 by Z-transforming all predictors as follows:
-
-$$
-\mathbf{Z} = \frac{\mathbf{X}- \bar{\mathbf{X}}}{\mathbf{s_X}}
-$$
-where $\bar{\mathbf{X}}$ is a vector of predictor means and $\mathbf{s_X}$ is a vector of standard deviations of the predictors.
-By default, `brma()` standardizes the predictors on which the model is estimated.
-The function returns the estimated parameters back to their original scales.
-This is achieved for the intercept by applying:
-
-$$
-b_0 = b_{0Z} - \mathbf{b}_Z\frac{\bar{\mathbf{X}}}{\mathbf{s}_X} \\
-$$
-where $b_0$ is the intercept, $b_{0Z}$ is the intercept for the standardized predictors and $\mathbf{b_Z}$ is the vector of regression coefficients for the standardized predictors.
-The regression coefficients are returned to their original scale by applying:
-
-$$
-\mathbf{b_X} = \frac{\mathbf{b_Z}}{\mathbf{s_X}}
-$$
-
-It is not always necessary or desirable to standardize predictors, however.
-For example, if predictors are already standardized or on a unified scale for different reasons.
-In these cases standardization does not make scales more equal, nor the penalization more fair, and the default standardization in `brma()` can be disabled.
-<!--Alternatively, if the goal of a study is to compare results to prior findings based on unstandardized predictors, standardization would make penalization unequal across studies.-->
-
-There are additional considerations regarding standardization of binary and dummy predictors ([@alkharusi2012categorical]).
-Some suggest to always standardize binary predictors ([@tibshirani1997lasso]).
-This makes that, irrespective of initial scaling, the binary predictor will be on the same scale as the continuous standardized predictors ([@gelman2008scaling]).
-However, standardizing binary predictors may decrease model interpretability ([@wissmann2007role]).
-To illustrate this point, consider bivariate regression with a single binary predictor $X$ that takes on values 0 and 1 predicting outcome $Y$.
-The intercept represents the expected value of $Y$ when $X == 0$, and the regression coefficient represents the difference in the expected value of $Y$ between the two conditions ([@alkharusi2012categorical]).
-By standardizing this binary predictor, the reference value is no longer zero, and both the intercept and its regression coefficient have no clear interpretation anymore, especially in multivariate cases ([@wissmann2007role]).
-
-Multiple coding schemes for categorical predictors exist that are equivalent in OLS regression.
-In penalized regression, however, the choice of coding does affect model fit and interpretation ([@chiquet2016coding; @detmer2020note]).
-Although this paper does not cover such considerations, a more elaborate discussion on how coding schemes affect model accuracy and interpretability in penalized regression can be found in @chiquet2016coding and @detmer2020note.
-
-In `brma()`, the default is to use dummy coding for categorical predictors and standardize the dummies.
-Users may specify alternative solutions, keeping in mind the aforementioned considerations.
-
-There are two ways to circumvent the default standardization in `brma()`.
-The first is to disable standardization entirely, analyzing predictors in their original scale,
-by setting `standardize = FALSE`.
-Alternatively, `brma()` allows custom standardization.
-To use this option, first manually standardize (some of) the predictors.
-Then, when calling `brma()`, pass a vector of means and a vector of standard deviations to restore the coefficients to the predictors' original scale.
-This can be accomplished using the argument `standardize = list(center = meanvector, scale = sdvector)`.
-For predictors that **should not** be standardized, a mean of 0 and a standard deviation of 1 must be passed; this will leave the coefficient in question unaffected.
-
-### Intercepts
-
-The standard linear model estimates an intercept, which reflects the expected value of the outcome when all predictors are equal to zero, and regression coefficients for the effect of moderators.
-In some cases, it may be desirable to omit the intercept.
-For example, if an analysis contains categorical predictors,
-these can be encoded as dummy variables, with values $x \in \{0, 1\}$.
-For a variable with $c$ categories, the number of dummy variables must be equal to $c-1$;
-the omitted category functions as a reference category, and its expected value is represented by the model intercept $b_0$.
-This so-called *regression specification* of a model may be useful when there is a meaningful reference category.
-For example, imagine a study on the effectiveness of interventions for specific phobia with two types of interventions: An industry-standard intervention, and a more recently developed one.
-In this case, it might make sense to code the industry standard intervention as the reference category,
-and dummy-code the new contender.
-The model will then estimate whether the newly developed intervention has an effect size significantly lower or higher than the industry standard.
-In other cases, there may not be a straightforward reference category.
-For example, imagine a study on the effectiveness of one intervention for specific phobia in two continents.
-In such cases, the average effect in both continents may be estimated by omitting the intercept, and including all $c$ dummy variables.
-This so-called *ANOVA specification* of a model estimates a mean for all dummy-coded categories.
-In BRMA, as in other R functions, one can use ANOVA specification by explicitly removing the intercept from the model formula; for example, if `yi` is the effect size and $C$ a categorical moderator, regression specification with $c-1$ dummies is specified as `yi ~ C`, and ANOVA specification with $c$ dummies is specified as `yi ~ -1 + C`.
-<!-- This part seems a repetition from the info on standardization of dummies above?: 
-The appropriate standardization of dummy variables in penalized regression analyses is a topic of ongoing debate.
-Suffice it to say that, for greater interpretability, users may want the freedom to leave dummy variables unstandardized.
-This is possible in `brma()` by ... 
--->
-
 ### Bayesian estimation
 
-Instead of using a penalty to shrink regression coefficients towards zero, it is possible to use a Bayesian prior distribution to achieve a similar result.
-Whereas classical, frequentist estimation methods rely solely on the data at hand, Bayesian estimation methods require the specification of a prior distribution.
-The prior distribution is a probability distribution that reflects the prior knowledge or beliefs that the researcher has before collecting the data.
-The prior is combined with the likelihood of the data to form the posterior distribution.
-In the context of regularization, the prior distribution is specified such that it reflects the prior belief that not all regression coefficients are substantial enough to be included in the model.
-
-Many different prior distributions exist that have specific properties that enable them to shrink small regression coefficients towards zero, while keeping substantial coefficients large ([@vanErpOberskiMulder2019]).
-Some prior distributions have been shown to result in exactly the same solutions as classical, frequentist penalties, such as the LASSO.
-Specifically, placing independent double exponential (i.e., Laplace) priors on the regression coefficients can result in posterior modes that are equal to the classical LASSO estimates ([@ParkCasella2008]).
-In addition, many prior distributions have been developed and investigated specifically for the purpose of providing good shrinkage properties, meaning that the prior pulls small regression coefficients towards zero, without exerting any influence on substantial regression coefficients.
-A popular prior in this regard is the horseshoe prior ([@CarvalhoPolsonScott2010]).
-An advantage of the horseshoe prior compared to the lasso is the fact that it has heavier tails.
-As a result, it will not shrink and therefore bias substantial coefficients as much as the LASSO prior with its lighter tails.
+One alternative to the use of a shrinkage penalty is Bayesian estimation with a regularizing prior.
+Whereas classical, frequentist estimation relies solely on the data at hand,
+Bayesian estimation combines information from the data with a *prior distribution*.
+The prior distribution is a probability distribution that reflects expectations about likely parameter values.
+This prior is updated with the likelihood of the data to form a posterior distribution,
+which reflects expectations about likely parameter values after having seen the data.
+
+A regularizing prior distribution reflects the expectation that not all regression coefficients are substantial enough to be included in the model.
+There are many different regularizing prior distributions [@vanErpOberskiMulder2019].
+Some of these result in exactly the same solutions as frequentist penalized methods.
+For example, applying an independent double exponential (i.e., Laplace) prior to regression coefficients results in posterior modes that are equal to the classical LASSO estimates [@ParkCasella2008].
+Other distributions have been developed specifically for the purpose of providing good shrinkage properties,
+meaning that the prior pulls small regression coefficients towards zero,
+while leaving larger regression coefficients mostly unaffected. 
+A popular prior in this regard is the horseshoe prior [@CarvalhoPolsonScott2010].
+It has heavier tails than the LASSO prior,
+which means that it does not shrink (and therefore bias) substantial coefficients as much.
 
@@
 Bayesian penalized meta-analysis is implemented in the function `brma()` in the R-package `pema`.
-For estimation, it depends on Stan, a probabilistic programming language that uses Hamiltonian Monte Carlo to sample from the posterior distribution ([@StanManual]).
+For estimation, it depends on Stan, a probabilistic programming language that uses Hamiltonian Monte Carlo to sample from the posterior distribution [@StanManual].
 Being written in C++, Stan is computationally efficient, but models must be compiled prior to estimation.
@@
 The implementation of the horseshoe prior is based on the regularized horseshoe proposed by @PiironenVehtari2017b:
-
 $$
@@
 The default value in `brma()` is 1.
-However, if prior information regarding the number of relevant moderators is available, it is best to include this information by setting $\lambda^2_0 = \frac{p_0}{p-p_0}{\frac{\sigma}{\sqrt{n}}$, where $p_0$ represents the number of relevant moderators, $p$ the total number of moderators, $\sigma$ is the residual standard deviation and $n$ equals the number of observations.
-This can be done by setting the argument `relevant_pars` equal to the expected number of relevant moderators.
+However, if prior information regarding the number of relevant moderators is available,
+it is best to include this information.
+This is accomplished by setting $\lambda^2_0 = \frac{p_0}{p-p_0}{\frac{\sigma}{\sqrt{n}}}$, where $p_0$ represents the number of relevant moderators, $p$ the total number of moderators, $\sigma$ is the residual standard deviation and $n$ equals the number of observations.
+An alternative, user-friendly way to accomplish this is by setting the argument `relevant_pars` equal to the expected number of relevant moderators. 
 <!-- SvE: nu twijfel ik toch weer of dit helemaal goed gaat.
@@
 Increasing these degrees of freedom parameters results in a prior with lighter tails,
-which is strictly no longer a horseshoe prior.
+which is, strictly speaking, no longer a horseshoe prior.
 However, in cases where the model is weakly identified, for example when there are more moderators than observations, these lighter tails can aid model convergence. 
-The regularized horseshoe differs from the standard horseshoe in the specification of a finite "slab". This slab ensures at least some regularization of large coefficients and as a consequence,
+The regularized horseshoe differs from the standard horseshoe in the specification of a finite "slab".
+This slab ensures at least some regularization of large coefficients and as a consequence,
 more stable results.
@@
 Default settings for these hyperparameters in `brma()` were chosen such that the values are reasonable in most applications.
-However, in a Bayesian analysis it is good practice to perform a prior sensitivity analysis in which different hyperparameters are chosen and the model is rerun to see if this leads to different results.
+However, it is good practice to perform a prior sensitivity analysis to compare the effect of different hyperparameters on the model results. 
 This is particularly important when the sample is small, as the prior is more influential in this case.
 
-Unlike the frequentist LASSO algorithm, Bayesian regularized estimation cannot set coefficients to be exactly equal to zero.
+Unlike the frequentist LASSO algorithm, Bayesian regularized estimation does not shrink coefficients to be exactly equal to zero.
 Therefore, variables must be selected post-estimation.
@@
 The present study considers two types of intervals:
-The credible interval, which is obtained by taking the 2.5% and 97.5% quantiles of the samples of the posterior, and the highest posterior density interval, which is the narrowest possible interval that contains 95% of the probability mass.
+The credible interval, which is obtained by taking the 2.5% and 97.5% quantiles of the posterior distribution, and the highest posterior density interval,
+which is the narrowest possible interval that contains 95% of the probability mass.
 
@@
 
+### Standardizing predictors
+
+<!-- Eli? -->
+<!-- * Eli, kan jij het algemene principe van standardization hier uitleggen, met een paar referenties?
+In de volgende paragraaf over intercepts moet ook nog een referentie, over wel/niet standaardizeren van dummies.-->
+<!-- * In BRMA werk het als volgt: -->
+<!--     + By default, all variables are normalized. -->
+<!--     + The penalized model (without an intercept) is estimated on the normalized data -->
+<!--     + The intercept is then restored to the original scale by applying  -->
+<!--     $b_0 = b_{0z} - \mathbf{b}_z\frac{\bar{\mathbf{x}}}{\mathbf{s}_x}$ -->
+<!--     Where b_0 is the intercept, b_0z is the intercept for the normalized predictors, b_z is the vector of     regression coefficients for the normalized predictors, bar x is the vector of means of X, and s_x is the vector of standard deviations of x -->
+<!--     + The regression coefficients are restored to the original scale by applying  -->
+<!--     $\mathbf{b} = \mathbf{b}_z\mathbf{s}_x$ -->
+<!-- * Leg vervolgens uit dat mensen dummies misschien niet willen standaardizeren -->
+<!-- * Gebruikers kunnen de default standaardization overschrijven door een aantal van de variabelen handmatig te standaardizeren, en de vector met means en vector met SDs handmatig mee te geven via het argument `standardize = list(center = meanvec, scale = sdvec)`.
+Als ze een bepaalde variabele NIET willen standaardizeren moeten ze voor die variabele mean= 0 en sd= 1 meegeven.
+-->
+
+Penalized regression analyses typically require the scales of predictors to be equivalent [@tibshirani1996].
+This is because the regularization penalizes coefficients without regard for their scale.
+If variable scales differ, this can lead to an imbalanced penalization of coefficients that does not reflect differences in variable importance [@lee2015note].
+To clarify, a regression parameter $\beta$ can be interpreted as the expected increase in outcome $y$ for a one unit increase in predictor $x$.
+If the scale of predictor $x$ is increased by a factor 10, its regression coefficient is reduced by a factor 10.
+Standardization is a widely used method for equalizing predictor scales,
+in which the mean of all predictors is set to 0 and their standard deviation is set to 1 [@gelman2008scaling].
+By default, this type of standardization is used in the `brma()` function.
+The estimated parameters are restored to their original scales.
+For the intercept, the transformation is:
+
+$$
+b_0 = b_{0Z} - \mathbf{b}_Z\frac{\bar{\mathbf{x}}}{\mathbf{s}_X}
+$$
+where $b_0$ is the intercept, $b_{0Z}$ is the intercept for the standardized predictors,
+$\mathbf{\bar{x}}$ and $\mathbf{s}_{x}$ are the vectors of predictor means and variances,
+and $\mathbf{b_Z}$ is the vector of regression coefficients for the standardized predictors.
+The regression coefficients are returned to their original scale by applying:
+
+$$
+\mathbf{b}_x = \frac{\mathbf{b}_z}{\mathbf{s}_x}
+$$
+It is not always necessary or desirable to standardize predictors, however.
+For example, if predictors are already standardized or on a unified scale for different reasons.
+In these cases standardization does not make scales more equal, nor the penalization more fair, and the default standardization in `brma()` can be disabled.
+<!--Alternatively, if the goal of a study is to compare results to prior findings based on unstandardized predictors, standardization would make penalization unequal across studies.-->
+
+There are additional considerations regarding standardization of binary and dummy predictors [@alkharusi2012categorical].
+Some suggest to always standardize binary predictors [@tibshirani1997lasso].
+This makes that, irrespective of initial scaling, the binary predictor will be on the same scale as the continuous standardized predictors [@gelman2008scaling].
+However, standardizing binary predictors may decrease model interpretability [@wissmann2007role].
+To illustrate this point, consider bivariate regression with a single binary predictor $x$ that takes on values 0 and 1 predicting outcome $y$.
+The intercept represents the expected value of $y$ when $x == 0$, and the regression coefficient represents the difference in the expected value of $y$ between the two conditions [@alkharusi2012categorical].
+By standardizing this binary predictor, the reference value is no longer zero, and both the intercept and its regression coefficient have no clear interpretation anymore, especially in multivariate cases [@wissmann2007role].
+
+The default in `brma()` is to use dummy coding for categorical predictors and standardize the dummies.
+Other coding schemes for categorical predictors exist that are equivalent in OLS regression.
+In penalized regression, by contrast, the choice of coding does affect model fit and interpretation due to the introduction of bias [@chiquet2016coding; @detmer2020note].
+Although the `brma()` function allows users to specify alternative coding schemes and standardization options,
+be advised that these decisions do affect model accuracy and interpretability in penalized regression [see @chiquet2016coding; @detmer2020note].
+
+There are two ways to circumvent the default standardization in `brma()`.
+The first is to disable standardization entirely, analyzing predictors in their original scale,
+by setting `standardize = FALSE`.
+Alternatively, `brma()` allows custom standardization.
+To use this option, first manually standardize (some of) the predictors.
+Then, when calling `brma()`, pass a vector of means and a vector of standard deviations to restore the coefficients to the predictors' original scale.
+This can be accomplished using the argument `standardize = list(center = meanvector, scale = sdvector)`.
+For predictors that **should not** be standardized, pass a mean of 0 and a standard deviation of 1;
+this leaves the coefficient in question unaffected.
+
+### Intercepts
+
+The standard linear model estimates an intercept, which reflects the expected value of the outcome when all predictors are equal to zero, and regression coefficients for the effect of moderators.
+In some cases, it may be desirable to omit the intercept.
+For example, if an analysis contains categorical predictors,
+these can be encoded as dummy variables, with values $x \in \{0, 1\}$.
+For a variable with $c$ categories, the number of dummy variables must be equal to $c-1$;
+the omitted category functions as a reference category, and its expected value is represented by the model intercept $b_0$.
+This so-called *regression specification* of a model may be useful when there is a meaningful reference category.
+For example, imagine a study on the effectiveness of interventions for specific phobia with two interventions: Treatment as usual, and a novel intervention.
+In this case, it might make sense to code treatment as usual as the reference category,
+and dummy-code the new contender.
+The model will then estimate whether the newly developed intervention has an effect size significantly lower or higher than the industry standard.
+In other cases, there may not be a straightforward reference category.
+For example, imagine a study on the effectiveness of one intervention for specific phobia in two continents.
+In such cases, the average effect in both continents may be estimated by omitting the intercept, and including all $c$ dummy variables.
+This so-called *ANOVA specification* of a model estimates a mean for all dummy-coded categories.
+In BRMA, as in other R functions, one can use ANOVA specification by explicitly removing the intercept from the model formula; for example, if `yi` is the effect size and $C$ a categorical moderator, regression specification with $c-1$ dummies is specified as `yi ~ C`, and ANOVA specification with $c$ dummies is specified as `yi ~ -1 + C`.
+<!-- This part seems a repetition from the info on standardization of dummies above?: 
+The appropriate standardization of dummy variables in penalized regression analyses is a topic of ongoing debate.
+Suffice it to say that, for greater interpretability, users may want the freedom to leave dummy variables unstandardized.
+This is possible in `brma()` by ... 
+-->
+
 # Simulation study
@@
 and their ability to recover population parameters. 
-Our research questions are whether BRMA offers a performance advantage over RMA in terms of any of these indicators;
-under what conditions BRMA does not offer an advantage,
+Our research questions are whether BRMA offers a performance advantage over RMA in terms of any of these indicators,
 and which prior (regularized horseshoe versus LASSO) is to be preferred.
@@
 In each data set, the observed effect size $y_i$ was simulated as a standardized mean difference (SMD),
-sampled from a non-central t-distribution.
+sampled from a non-central $t$-distribution.
 
@@
 We were thus able to use all iterations of the BRMA algorithms,
-although some of these may have failed to converge and thus have poor performance.
-The RMA algorithm failed to converge more regularly, however, in which case the process terminates with an error.
-To handle these contingencies, we automated some of the steps recommended [on the `metafor` website](https://www.metafor-project.org/doku.php/tips:convergence_problems_rma).
-Despite this, `r out$missing` replications of the RMA algorithm still failed to converge.
+although there may be some that failed to converge, which will likely have poor performance.
+When the RMA algorithm fails to converge, however, it terminates with an error.
+To handle this contingency, we automated some of the steps recommended [on the `metafor` website](https://www.metafor-project.org/doku.php/tips:convergence_problems_rma).
+Nevertheless, `r out$missing` replications of the RMA algorithm failed to converge.
 All of these were characterized by low number of cases ($k \leq 40$) and high effect sizes $\beta \geq .5$.
@@
 The HS algorithm furthermore had the consistently highest predictive performance regardless of number of irrelevant moderators or number of cases in the training data, and was relatively less affected by increases in the number of irrelevant moderators (panel b) or in the number of training cases (panel c).
-Similarly, the HS algorithm furthermore had the consistently highest predictive performance regardless of number of cases in the training data, and thus also increased less when the number of training cases increased (panel c).
+<!-- Similarly, the HS algorithm furthermore had the consistently highest predictive performance regardless of number of cases in the training data, and thus also increased less when the number of training cases increased (panel c).
+-->
 Conversely, RMA had relatively poor predictive performance on average, and was more responsive to increases in the number of training cases and irrelevant moderators.
@@
 <!-- For all algorithms, the association between skewness and $R^2_{test}$ was negative for the linear model, and positive for the cubic model. -->
-<!-- <!-- Figure \@ref(fig:skewness) shows the relationship. --> -->
+<!-- <!-- Figure \@ref(fig:skewness) shows the relationship. -->
 <!-- The residual heterogeneity $\tau^{2}$ had a negative linear relationship with $R^{2}_{test}$ for all algorithms. -->
@@
 and the effect of the second moderator was always zero in the population and could be used to calculate $N$.
+Additionally, overall accuracy can be computed, which reflects the trade off between sensitivity and specificity.
+As the base rate of true positives and true negatives is equal in this simulation, overall accuracy is simply given by $Acc = (P+N)/2$.
 
@@
 By contrast, specificity was higher for the regularized algorithms, `r trueneg`.
-Overall accuracy reflects the trade off between sensitivity and specificity.
-As the baserate of true positives and true negatives is equal in this simulation, overall accuracy is simply given by $Acc = (P+N)/2$.
-Results showed that overall accuracy was approximately equal for RMA and HS, and was lower for LASSO, `r proboveral`.
+Overall accuracy was approximately equal for RMA and HS, and was lower for LASSO, `r proboveral`.
 
@@
 We also computed this effect size for the difference between algorithms in the number of true positives by design factor.
-
 ```{r tabcramerp, results= "asis", eval = TRUE}
@@
 ```
-
 Differences in sensitivity between the algorithms were near-zero for HS and LASSO.
@@
 then the bias $B$ and variance $V$ of this estimate can be computed as the mean and variance of the difference between $\hat{b}$ and $\beta$ across simulation conditions, respectively.
-
 Across all simulation conditions, HS had the lowest bias for $\tau^2$, $B_{HS} `r report(out[["tau2_bias"]][["hs_tau2"]])`$, 
@@
 and then RMA, $B_{RMA} `r report(out[["tau2_variance"]][["rma_tau2"]])`$.
-
 The effect of the design factors on the bias in $\tau^2$ was evaluated using ANOVAs.
@@
 Note that all algorithms - including RMA - provided, on average, negatively biased estimates. 
-Across simulation conditions, HS had the lowest variance, $V_{HS} `r report(out[["beta_variance"]][["hs_beta1"]])`$, 
-followed by LASSO, $B_{LASSO} `r report(out[["beta_variance"]][["lasso_beta1"]])`$,
+Across simulation conditions, HS had the lowest variance, $V_{HS} `r report(out[["beta_variance"]][["hs_beta1"]])`$, followed by LASSO, $B_{LASSO} `r report(out[["beta_variance"]][["lasso_beta1"]])`$,
 and then RMA, $B_{RMA} `r report(out[["beta_variance"]][["rma_beta1"]])`$.
-
 The effect of the design factors on the bias in estimated $\beta$ was evaluated using ANOVAs.
@@
 This example uses a small subset of the more than 30 moderators.
+See the `pema` package documentation (help and vignettes) for further examples.
 <!-- We focus specifically on how to choose the different hyperparameters of the regularized horseshoe prior. -->
@@
 ```{r exdata, eval = TRUE}
-# Set random seed
-set.seed(1)
 # Load relevant packages
 library(pema)
-library(tidySEM)
-library(ggplot2)
-library(bayesplot)
-
 # Select data to analyze
@@
 ```
-
-## Visualizing the prior
 
@@
 ```{r exmodel1, echo = TRUE, eval = FALSE}
-fit_hs1 <- brma(yi ~ ., data = df, vi = "vi")
+fit <- brma(yi ~ ., data = df, vi = "vi")
 ```
 ```{r, echo = FALSE, eval = run_everything}
-fit_hs1 <- brma(yi ~ ., data = df, vi = "vi")
-saveRDS(fit_hs1, "fit_hs1.RData")
+fit <- brma(yi ~ ., data = df, vi = "vi")
+saveRDS(fit, "fit.RData")
 ```
 ```{r, echo = FALSE, eval = TRUE}
-fit_hs1 <- readRDS("fit_hs1.RData")
-```
-
-Note the warning message about divergent transitions, which may indicate problems with model convergence.
-This warning is generated by `Stan`, the computational back-end of `brma()`.
+fit <- readRDS("fit.RData")
+```
+
+By running `summary(fit)`, we obtain the posterior mean, standard deviation, and quantiles of the model parameters (see Table \@ref(tab:tabsumex)).
+To perform inference, consider using the posterior median (50% quantile) and 95% credible interval (2.5% - 97.5%).
+<!-- In the simulation study, -->
+<!-- we retained moderators when the 95% credible interval excluded zero, -->
+<!-- Since Bayesian penalization does not automatically shrink estimates exactly to zero. -->
+Parameters whose 95% credible interval excludes zero are marked with an asterisk.
+In this example, however, there are no moderators for which the 95\% CI excludes zero.
+
+```{r, echo = FALSE, eval = FALSE}
+summary(fit)
+```
+```{r tabsumex, eval = TRUE, echo = FALSE, results = "asis"}
+tab <- summary(fit)$coefficients[1:8, c("mean", "sd", "2.5%", "50%", "97.5%", "n_eff", "Rhat")]
+papaja::apa_table(tab, caption = "Summary of model parameters for the applied example.")
+```
+Many additional convenience functions exist for `rstan` models,
+which become available by converting a `brma` model object to a `stanfit` object,
+using the function `as.stan(fit)`.
+This makes it possible to plot the model parameters instead of tabulating them,
+using the `plot()` function.
+For example, one can obtain posterior density plots for parameters using `plot(as.stan(fit), plotfun = "dens", pars = c("Intercept", "year"))`.
+
+```{r exres, eval = FALSE, echo = FALSE}
+fit_stan <- as.stan(fit)
+plot(fit_stan, pars = rownames(coef(fit))[2:8])
+```
+```{r, eval = run_everything, echo = FALSE}
+fit_stan <- as.stan(fit)
+p <- plot(fit_stan, pars = rownames(coef(fit))[2:8])
+ggsave("plot_es.png", p, device = "png", width = 4, height = 3, dpi = 300, scale = 1.5)
+```
+```{r, eval = FALSE, echo = FALSE, fig.cap="Visual presentation of model parameters for the applied example."}
+knitr::include_graphics("plot_es.png")
+```
+
+It is good practice to assess model convergence.
+For example, the analysis above returns a warning about "divergent transitions".
+Converting to a `stanfit` object also facilitates convergence diagnostics;
+for example, using the function `check_hmc_diagnostics(as.stan(fit))`.
+Additionally, the MCMC draws can be visualized using `traceplot(as.stan(fit), pars = c("Intercept", "year"))`.
+The traces of a converged model look like "fat caterpillars",
+with the different MCMC chains mixing together.
+<!-- Note that there are many auxiliary parameters used for the regularized horseshoe prior.
+No information on these parameters is returned in the `brma` fitobject, however, once the fitobject is transformed into a Stan object for plotting, these parameters are included.
+-->
+
+```{r extrace, eval = FALSE, echo = FALSE}
+traceplot(fit_stan, pars = c("Intercept", "year"))
+```
+```{r, eval = FALSE, echo = FALSE}
+p <- traceplot(fit_stan, pars = c("Intercept", "year"))
+ggsave("traceplot.png", p, device = "png", width = 4, height = 2.5, dpi = 300, scale = 1.5)
+```
+```{r, eval = FALSE, echo = FALSE, fig.cap="Trace plot for the applied example."}
+knitr::include_graphics("traceplot.png")
+```
+
+The model summary also offers convergence diagnostics.
+For example, the column `Rhat` provides information on the split $\hat{R}$,
+a version of the potential scale reduction factor [PSRF, @GelmanRubin1992].
+Values close to 1 indicate convergence.
+In addition, the column `n_eff` provides information on the number of effective (independent) MCMC samples, which should be high relative to the total number of samples (in this case, 4000).
+In this example, all `Rhat` values are close to 1.
+The effective number of MCMC samples is relatively small compared to the total number of MCMC samples.
+An often used heuristic is to consider ratios smaller than 0.1 as problematic.
+<!-- Even though this is not the case here, consider increasing the number of MCMC iterations. -->
+<!-- These diagnostics can be easily visualized using the `bayesplot` package: -->
+Both statistics indicate convergence in this example.
+
+As mentioned before, this analysis results in a warning message about divergent transitions.
 Divergent transitions can result in biased estimates.
-However, if the number of divergences is small and there are no further indications of non-convergence,
-the posterior distribution is often good enough to safely interpret the results.
-In some cases, this problem may be resolved by increasing the values for the degrees of freedom parameters.
-Note that increasing both `df_global` and `df_slab` to 5 results in fewer divergences,
-but does not otherwise influence the substantive interpretation of the results:
-
-```{r exmodel2, eval = FALSE, echo = TRUE}
-fit_hs2 <- brma(yi ~ .,
+However, the posterior distribution is often good enough to safely interpret the results if the number of divergences is small and there are no further indications of non-convergence.
+In some cases, divergent transitions may be resolved by increasing the degrees of freedom of the prior.
+Increasing both `df_global` and `df_slab` to 5 results in fewer divergences for this example,
+but does not otherwise influence the substantive interpretation of the results.
+It is prudent to perform similar sensitivity analyses to determine whether results are robust to different priors.
+
+```{r exmodel2, eval = FALSE, echo = F}
+fit2 <- brma(yi ~ .,
+             data = df,
+             vi = "vi",
+             prior = c(df = 5, df_global = 5, df_slab = 4,
+                       scale_global = 1, scale_slab = 1,
+                       relevant_pars = NULL))
+```
+```{r, echo = FALSE, eval = FALSE}
+fit2 <- brma(yi ~ .,
                 data = df,
@@
                 prior = c(df = 5, df_global = 5, df_slab = 4, scale_global = 1, scale_slab = 1, relevant_pars = NULL))
-```
-```{r, echo = FALSE, eval = run_everything}
-fit_hs2 <- brma(yi ~ .,
-                data = df,
-                vi = "vi",
-                prior = c(df = 5, df_global = 5, df_slab = 4, scale_global = 1, scale_slab = 1, relevant_pars = NULL))
-saveRDS(fit_hs2, "fit_hs2.RData")
-```
-```{r, echo = FALSE, eval = TRUE}
-fit_hs2 <- readRDS("fit_hs2.RData")
-```
-
-In general, it is prudent to assess model convergence.
-Various numeric and visual diagnostics exist, for example, in the R-package `rstan`.
-These functions can be used by converting a `brma` object to a `stanfit` object, using the function `pema::as.stan()`:
-
-```{r}
-fit_stan <- as.stan(fit_hs1)
-check_hmc_diagnostics(fit_stan)
-```
-
-Additionally, traceplots can be created for each parameter to visualize the MCMC draws using the `bayesplot` R-package.
-The traceplots of a converged model look like "fat caterpillars", with the different MCMC chains mixing together: 
-<!-- Note that there are many auxiliary parameters used for the regularized horseshoe prior.
-No information on these parameters is returned in the `brma` fitobject, however, once the fitobject is transformed into a Stan object for plotting, these parameters are included.
--->
-
-```{r extrace, eval = FALSE, echo = TRUE}
-mcmc_trace(fit_stan, pars = c("Intercept", "year"))
-```
-```{r, eval = run_everything, echo = FALSE}
-p <- mcmc_trace(fit_stan, pars = c("Intercept", "year"))
-ggsave("traceplot.png", p, device = "png", width = 4, height = 3, dpi = 300, scale = 1.5)
-```
-```{r, eval = TRUE, echo = FALSE}
-knitr::include_graphics("traceplot.png")
-```
-
-Convergence can also be checked by examining for the summary of the model object.
-The column `Rhat` provides information on the split $\hat{R}$, a version of the potential scale reduction factor (PSRF; @GelmanRubin1992).
-Values close to 1 indicate convergence.
-In addition, the column `n_eff` provides information on the number of effective (independent) MCMC samples, which should be high relative to the total number of samples (in this case, 4000):
-
-```{r exsumm, eval = TRUE}
-summary(fit_hs1)
-```
-All `Rhat` values are close to 1, indicating convergence.
-The effective number of MCMC samples is relatively small compared to the total number of MCMC samples.
-An often used heuristic is to consider ratios smaller than 0.1 as problematic.
-Even though this is not the case here, consider increasing the number of MCMC iterations.
-<!-- These diagnostics can be easily visualized using the `bayesplot` package: -->
+saveRDS(fit2, "fit2.RData")
+```
+```{r, echo = FALSE, eval = FALSE}
+fit2 <- readRDS("fit2.RData")
+```
 
@@
 
-The `summary()` function also provides summary statistics for the model parameters.
-For each parameter, the posterior mean, standard deviation, and quantiles are reported by default (the 50% quantile is the median).
-To perform inference, consider using the posterior median and 95% credible interval (2.5% - 97.5%).
-Since Bayesian penalization does not automatically shrink estimates exactly to zero,
-we retained moderators when the 95% credible interval excluded zero in the simulation study.
-The `summary()` flags such parameters with an asterisk.
-If the model is converted using `as.stan()`, the results can also be visualized using standard `rstan` functions.
-In this example, we conclude that there are no moderators for which the 95% CI excludes zero.
-
-```{r exres, eval = FALSE}
-plot(fit_stan, pars = rownames(coef(fit_hs1))[2:8])
-```
-```{r, eval = run_everything, echo = FALSE}
-p <- plot(fit_stan, pars = rownames(coef(fit_hs1))[2:8])
-ggsave("plot_es.png", p, device = "png", width = 4, height = 3, dpi = 300, scale = 1.5)
-```
-```{r, eval = TRUE, echo = FALSE}
-knitr::include_graphics("plot_es.png")
-```
-
 <!-- ## Prior sensitivity -->
@@
 ```{r expriorsens, eval = FALSE, echo = FALSE}
-fit_hs3 <- brma(yi ~ .,
+fit3 <- brma(yi ~ .,
                 data = datdum,
@@
 
-fit_hs4 <- brma(yi ~ .,
+fit4 <- brma(yi ~ .,
                 data = datdum,
@@
 
-fit_hs5 <- brma(yi ~ .,
+fit5 <- brma(yi ~ .,
                 data = datdum,
@@
 
-df1 <- df.fun(fit_hs1, prior = "hs default")
-df3 <- df.fun(fit_hs3, prior = "hs with p0 = 1")
-df4 <- df.fun(fit_hs4, prior = "hs with p0 = 3")
-df5 <- df.fun(fit_hs5, prior = "hs with p0 = 6")
+df1 <- df.fun(fit, prior = "hs default")
+df3 <- df.fun(fit3, prior = "hs with p0 = 1")
+df4 <- df.fun(fit4, prior = "hs with p0 = 3")
+df5 <- df.fun(fit5, prior = "hs with p0 = 6")
 
@@
 and their ability to recover population parameters.
-Our research questions were whether BRMA offers a performance advantage over RMA in terms of any of these indicators;
-under what conditions BRMA does not offer an advantage,
+Our research questions were whether BRMA offers a performance advantage over RMA in terms of any of these indicators,
 and which prior (horseshoe versus LASSO) is to be preferred.
@@
 
-With regard to variable selection, results indicated that the penalized BRMA algorithms had lower sensitivity: they were less able to select relevant moderators than the un-penalized RMA algorithm.
+With regard to variable selection, results indicated that the penalized BRMA algorithms had lower sensitivity: they were less able to select relevant moderators than RMA.
 Conversely, the BRMA algorithms had better specificity: they were better able to reject irrelevant moderators than RMA.
@@
 This diminishes their ability to detect true effects and aids their ability to reject irrelevant moderators.
-Importantly, the overall accuracy was approximately equal for RMA and BRMA with a horseshoe prior.
+Importantly however, the overall accuracy was approximately equal for RMA and BRMA with a horseshoe prior.
 This means that the total number of Type I and Type II errors will be approximately the same when choosing between these two methods - but there is a tradeoff between sensitivity and specificity.
@@
 we observed that BRMA with a horseshoe prior had the greatest bias towards zero across simulation conditions, followed by LASSO, and then RMA.
-Note that all algorithms provided, on average, negatively biased estimated.
+Note that all algorithms provided, on average, negatively biased estimates.
 The variance of the estimates followed the opposite pattern.
-This unsurprising result illustrates the bias-variance trade-off in penalized regression.
-The greater predictive performance of the BRMA algorithms is a direct consequence off this trade-off.
-
-We further observed that BRMA with a horseshoe prior had the lowest bias when estimating residual heterogeneity.
-The BRMA algorithms also had lower variance than RMA when estimating residual heterogeneity.
+This illustrates the bias-variance trade-off,
+of which the BRMA algorithms' greater predictive performance is a direct consequence.
+
+With regard to residual heterogeneity, we observed that BRMA with a horseshoe prior had the lowest bias.
+The BRMA algorithms also had lower variance.
 This suggests that the penalized regression coefficients do not compromise the estimation of residual heterogeneity.
-Future research might investigate under what conditions residual heterogeneity is estimated more accurately in a penalized model than in an un-penalized model.
+Future research might investigate under what conditions residual heterogeneity is estimated more accurately in a penalized model than in an unpenalized model.
 Together, these results suggest that BRMA has superior predictive performance and specificity, and provides relatively unbiased estimates of residual heterogeneity, relative to RMA.
 
-We examined the effect of several violations of model assumptions, including simulating data from a cubic model, and then analyzing these data with a linear model.
+We examined the effect of several violations of model assumptions, including simulating data from a cubic model.
 In applied research, it is often not known what the true shape of the association between a moderator and effect size is.
-Thus, model mis-specification is likely to occur.
+Thus, model misspecification is likely to occur.
 One advantage of BRMA is that it can accommodate more moderators than RMA and has superior specificity.
-This allows researchers to specify a more flexible model to account for potential misspecification, with less concern for overfitting and non-convergence.
+This allows researchers to specify a more flexible model to account for potential misspecification, with less concern for overfitting and nonconvergence.
 For example, researchers could add polynomials of continuous variables with suspected non-linear effects, or interactions between predictors.
-
-# Strengths and future directions
+If nothing is known about the shape of the associations between moderators and effect size,
+non-parametric methods like random forest meta-analysis may be preferable over linear models [@vanlissaSmallSampleMetaanalyses2020].
+
+## Strengths and future directions
 
@@
 based on data from 705 published psychological meta-analyses (Van Erp et al., 2017).
-Another strength is that we made the BRMA algorithms available in a FAIR (Findable, Accessible, Interoperable and Reusable) format by publishing an R package on the "Comprehensive R Archive Network".
+Another strength is that the BRMA algorithms have been made available in a FAIR (Findable, Accessible, Interoperable and Reusable) repository: an R-package published on the "Comprehensive R Archive Network".
 Thanks to the use of compiled code, the BRMA algorithm is computationally relatively inexpensive.
@@
 we have made all simulation data and analysis code for the present study available online.
-This code also enables researchers to conduct Monte Carlo power analyses for applied research.
-
+This code can also be used to conduct Monte Carlo power analyses for applied research.
 A second limitation is that the present study did not examine the effect of multicollinear predictors.
 Regularizing estimators typically have an advantage over OLS regression in the presence of multicollinearity;
-future research ought to examine whether this also applies to BRMA.
-
+future research ought to examine whether this advantage extends to BRMA.
 A third limitation is that the present study did not examine the effect of dependent data (e.g., multiple effect sizes per study).
-In principle, the BRMA algorithm can accommodate dependent data by means of three-level multilevel analysis.
-To our knowledge, there are no theoretical reasons to expect that dependent data would result in a different pattern of findings than we found for independent data, but future research is required to ascertain this.
-
+The BRMA algorithm can accommodate dependent data by means of three-level multilevel analysis.
+To our knowledge, there are no reasons to expect that dependent data would result in a different pattern of findings than we found for independent data, but future research is required to ascertain this.
 A final limitation of the current implementation is that it relies on 95% credible intervals to select relevant moderators.
-However, these marginal credible intervals can behave differently compared to the joint credible intervals ([@PiironenEtal2017]).
-A future direction of research is therefore to implement more advanced selection procedures, such as projection predictive variable selection ([@PiironenVehtari2017a]).
-
-Another direction for future research is the specification of different priors, aside from the horseshoe and LASSO priors that were examined in this study.
-To facilitate such research, we provide a generalized BRMA function which is not compiled, and can be fully customized with user-specified priors.
-The downside of this flexible function is that it is not compiled, and requires the user to set up a compilation toolchain.
-Compiling the function thus requires some technological sophistication and is more computationally costly.
-
-Alghough the use of Bayesian estimation has several advantages, one major downside is that Bayesian models are not directly comparable with frequentist models.
-Another disadvantage is that Bayesian estimation is typically more computationally expensive than frequentist estimation.
+However, these marginal credible intervals can behave differently compared to the joint credible intervals [@PiironenEtal2017].
+A future direction of research is therefore to implement more advanced selection procedures, such as projective predictive variable selection [@PiironenVehtari2017a].
+Another direction for future research is the specification of different priors,
+aside from the horseshoe and LASSO priors that were examined in this study.
+<!-- To facilitate such research, we provide a generalized BRMA function which is not compiled, and can be fully customized with user-specified priors. -->
+<!-- The downside of this flexible function is that it is not compiled, and requires the user to set up a compilation toolchain. -->
+<!-- Compiling the function thus requires some technological sophistication and is more computationally costly. -->
+<!-- Although the use of Bayesian estimation has several advantages, one major downside is that Bayesian models are not directly comparable with frequentist models. -->
+A final disadvantage is that Bayesian estimation is typically more computationally expensive than frequentist estimation.
 One future direction of research is thus to develop a frequentist estimator for regularized meta-regression.
@@
 them from their analyses for lack of statistical power.
-Moderators can be continuous or categorical, in which case they should be dummy-coded.
+Moderators can be continuous or categorical.
 Missing data must be accounted for.
@@
 If missing data remains, users can either use a single imputation method (for example, a non-parametric imputation method like missForest),
-or manually aggregate the results across multiple imputations.
+or use multiple imputation and provide a list of multiply imputed data to the `data` argument.
 The effect sizes and their variances must be computed using suitable methods;
@@
 Finally, with regard to publication, we highly recommend sharing the data and
-syntax for the meta-analysis publicly; for example, by making the entire paper reproducible using the Workflow for Reproducible Code in Science (WORCS; REF).
+syntax for the meta-analysis publicly; for example, by making the entire paper reproducible using the Workflow for Reproducible Code in Science [WORCS, @vanlissaWORCSWorkflowOpen2020].
 Transparency allows readers and reviewers to verify that methods were correctly applied, and try alternative analyses.

### 2022-04-22 R/brma.R

@@ -7,8 +7,9 @@
 #' See Details.
 #' @param formula An object of class `formula` (or one that can be coerced to
 #' that class), see \code{\link[stats]{lm}}.
-#' @param data Optional data.frame containing the variables in the model, see
-#' \code{\link[stats]{lm}}.
+#' @param data Either a `data.frame` containing the variables in the model,
+#' see \code{\link[stats]{lm}}, or a `list` of multiple imputed `data.frame`s,
+#' or an object returned by \code{\link[mice]{mice}}.
 #' @param vi Character. Name of the column in the \code{data} that
 #' contains the variances of the effect sizes. This column will be removed from
 #' the data prior to analysis. Defaults to \code{"vi"}.
@@ -163,6 +164,16 @@ brma.formula <-
            #prior_only = FALSE,
            ...) {
     cl <- match.call()
+    # Check if data is multiply imputed
+    if(inherits(data, "mids")){
+      data <- mice::complete(data, action = "all")
+    }
+    if(inherits(data, "list") & !inherits(data, "data.frame")){
+      cl[["data"]] <- data
+      return(brma_imp(cl = cl))
+    }
+    # Check for complete data
+    if(anyNA(data)) stop("The function brma() requires complete data.")
     # Bookkeeping for columns that should not be in X or Y
     vi_column <- NULL
     study_column <- NULL
@@ -230,7 +241,7 @@ brma.formula <-
 #' @param x An k x m numeric matrix, where k is the number of effect sizes and m
 #' is the number of moderators.
 #' @param y A numeric vector of k effect sizes.
-#' @param y Logical, indicating whether or not an intercept should be included
+#' @param intercept Logical, indicating whether or not an intercept should be included
 #' in the model.
 #' @method brma default
 #' @export
@@ -248,6 +259,9 @@ brma.default <-
            ...) {
     X <- x
     Y <- y
+    # Check for complete data
+    if(anyNA(X) | anyNA(Y)) stop("The function brma() requires complete data.")
+
     dots <- list(...)
[…]

### 2022-04-22 R/stanmodels.R

@@ -1,7 +1,7 @@
 # Generated by rstantools.  Do not edit by hand.
 
 # names of stan models
-stanmodels <- c("horseshoe_MA", "horseshoe_MA_ml", "horseshoe_MA_ml_noint", "horseshoe_MA_noint", "hs_prior", "lasso_MA", "lasso_MA_ml", "lasso_MA_ml_noint", "lasso_MA_noint", "lasso_prior")
+stanmodels <- c("horseshoe_MA", "horseshoe_MA_ml", "horseshoe_MA_ml_noint", "horseshoe_MA_noint", "hs_prior", "lasso_MA", "lasso_MA_ml", "lasso_MA_ml_noint", "lasso_MA_noint", "lasso_prior", "prior_meff")
 
 # load each stan module
 Rcpp::loadModule("stan_fit4horseshoe_MA_mod", what = TRUE)
@@ -14,6 +14,7 @@ Rcpp::loadModule("stan_fit4lasso_MA_ml_mod", what = TRUE)
 Rcpp::loadModule("stan_fit4lasso_MA_ml_noint_mod", what = TRUE)
 Rcpp::loadModule("stan_fit4lasso_MA_noint_mod", what = TRUE)
 Rcpp::loadModule("stan_fit4lasso_prior_mod", what = TRUE)
+Rcpp::loadModule("stan_fit4prior_meff_mod", what = TRUE)
 
 # instantiate each stanmodel object
 stanmodels <- sapply(stanmodels, function(model_name) {

### 2022-04-22 src/RcppExports.cpp
Stop tracking

@@ -1,43 +1,0 @@
-// Generated by using Rcpp::compileAttributes() -> do not edit by hand
-// Generator token: 10BE3573-1514-4C36-9D1C-5A225CD40393
-
-#include <RcppEigen.h>
-#include <Rcpp.h>
-
-using namespace Rcpp;
-
-#ifdef RCPP_USE_GLOBAL_ROSTREAM
-Rcpp::Rostream<true>&  Rcpp::Rcout = Rcpp::Rcpp_cout_get();
-Rcpp::Rostream<false>& Rcpp::Rcerr = Rcpp::Rcpp_cerr_get();
-#endif
-
-
-RcppExport SEXP _rcpp_module_boot_stan_fit4horseshoe_MA_mod();
-RcppExport SEXP _rcpp_module_boot_stan_fit4horseshoe_MA_ml_mod();
-RcppExport SEXP _rcpp_module_boot_stan_fit4horseshoe_MA_ml_noint_mod();
-RcppExport SEXP _rcpp_module_boot_stan_fit4horseshoe_MA_noint_mod();
-RcppExport SEXP _rcpp_module_boot_stan_fit4hs_prior_mod();
-RcppExport SEXP _rcpp_module_boot_stan_fit4lasso_MA_mod();
-RcppExport SEXP _rcpp_module_boot_stan_fit4lasso_MA_ml_mod();
-RcppExport SEXP _rcpp_module_boot_stan_fit4lasso_MA_ml_noint_mod();
-RcppExport SEXP _rcpp_module_boot_stan_fit4lasso_MA_noint_mod();
-RcppExport SEXP _rcpp_module_boot_stan_fit4lasso_prior_mod();
-
-static const R_CallMethodDef CallEntries[] = {
-    {"_rcpp_module_boot_stan_fit4horseshoe_MA_mod", (DL_FUNC) &_rcpp_module_boot_stan_fit4horseshoe_MA_mod, 0},
-    {"_rcpp_module_boot_stan_fit4horseshoe_MA_ml_mod", (DL_FUNC) &_rcpp_module_boot_stan_fit4horseshoe_MA_ml_mod, 0},
-    {"_rcpp_module_boot_stan_fit4horseshoe_MA_ml_noint_mod", (DL_FUNC) &_rcpp_module_boot_stan_fit4horseshoe_MA_ml_noint_mod, 0},
[…]

### 2022-04-22 R/as_stan.R
update 2022-04-22 16:07:01

@@ -9,9 +9,9 @@
 #' @examples
 #' stanfit <- "a"
 #' class(stanfit) <- "stanfit"
-#' brmaobject <- list(fit = stanfit)
-#' class(brmaobject) <- "brma"
-#' converted <- as.stan(brmaobject)
+# brmaobject <- list(fit = stanfit)
+# class(brmaobject) <- "brma"
+#' converted <- as.stan(stanfit)
 #' @importFrom stats rbinom rnorm rt
 #' @importFrom sn rsn
 as.stan <- function(x, ...){
@@ -71,3 +71,14 @@ as.stan.brma <- function(x, ...){
   return(out)
 }
 
+#' @method as.stan default
+#' @export
+as.stan.default <- function(x, ...){
+  if(inherits(x, "stanfit")){
+    return(x)
+  } else {
+    message("Could not coerce to 'stanfit'.")
+    return(NULL)
+  }
+
+}

### 2022-04-23 paper/manuscript.Rmd
Submitted to RSM

@@
   present study introduces Bayesian Regularized Meta-Analysis (BRMA), an
-  exploratory algorithm that can select relevant moderators from a larger number
-  of candidates. This approach is suitable when heterogeneity is suspected, but
+  algorithm that performs variable selection to identify relevant moderators
+  from a larger number of candidates.
+  This approach is suitable when heterogeneity is suspected, but
   it is not known which moderators most strongly inﬂuence the observed effect
@@
   relative to state-of-the-art meta-regression (RMA). Results indicated that
-  BRMA compared favorably to RMA on three metrics: predictive performance,
-  which is a measure of the generalizability of results, the ability to reject
-  irrelevant moderators, and the ability to recover population parameters with
+  BRMA compared favorably to RMA on three metrics: predictive performance (a
+  measure of generalizability), the ability to reject irrelevant moderators,
+  and the ability to recover population parameters with
   low bias. BRMA had slightly lower ability to detect true effects of relevant
   moderators, but the overall proportion of Type I and Type II errors was
-  equivalent to RMA. Furthermore, BRMA regression coefficients were slightly
+  equivalent to RMA. BRMA regression coefficients were slightly
   biased towards zero (by design), but its estimates of residual heterogeneity
@@
 for example, the *fixed effect* model assumes that all observed effect sizes reflect one underlying true population effect.
-This assumption is well-suited to the situation where effect sizes from close replication studies are meta-analyzed [@higginsReevaluationRandomeffectsMetaanalysis2009; @@fabrigarConceptualizingEvaluatingReplication2016; @@maxwellPsychologySufferingReplication2015].
+This assumption is well-suited to the situation where effect sizes from close replication studies are meta-analyzed [@higginsReevaluationRandomeffectsMetaanalysis2009]. 
 The *random effects* model, by contrast, assumes that population effect sizes follow a normal distribution.
 Each observed effect size provides information about the mean and standard deviation of this distribution of population effect sizes.
-This assumption is more appropriate when studies are conceptually similar and differences between them are random [@higginsReevaluationRandomeffectsMetaanalysis2009; @@fabrigarConceptualizingEvaluatingReplication2016; @@maxwellPsychologySufferingReplication2015].
+This assumption is more appropriate when studies are conceptually similar and differences between them are random [@higginsReevaluationRandomeffectsMetaanalysis2009].
 
@@
 and which prior (regularized horseshoe versus LASSO) is to be preferred.
+All analysis code is available in a version-controlled repository at <https://github.com/cjvanlissa/pema>.
 
@@
 
-In this example, we will estimate the model using default settings, which includes a horseshoe prior with default hyperparameters.
+As no prior is specified, this example uses a horseshoe prior with default hyperparameters.
 To see the default values, open the function documentation using `?brma`.
@@
 By running `summary(fit)`, we obtain the posterior mean, standard deviation, and quantiles of the model parameters (see Table \@ref(tab:tabsumex)).
-To perform inference, consider using the posterior median (50% quantile) and 95% credible interval (2.5% - 97.5%).
+Use the posterior mean or median (50% quantile) and 95% credible interval (2.5% - 97.5%) to perform inference on model parameters.
 <!-- In the simulation study, -->
@@
 Parameters whose 95% credible interval excludes zero are marked with an asterisk.
+Note that Bayesian analyses do not use the frequentist notion of significance.
+Instead, we say that there is a 95% probability that the true population parameter lies within the interval,
+given the prior and observed data.
 In this example, however, there are no moderators for which the 95\% CI excludes zero.
@@
 The best way to do so is by retrieving the missing information, by contacting authors or comparing different publications on the same data.
-If missing data remains, users can either use a single imputation method (for example, a non-parametric imputation method like missForest),
-or use multiple imputation and provide a list of multiply imputed data to the `data` argument.
+If missing data remains, users can either use a single imputation method
+or supply multiple imputed data to the `data` argument (see function documentation).
 The effect sizes and their variances must be computed using suitable methods;
-note that many such methods are available in the R package `metafor` (Viechtbauer et al., 2010).
+note that many such methods are available in the R package `metafor` [@viechtbauerConductingMetaanalysesMetafor2010].
 With regard to data analysis, we recommend the use of a horseshoe prior by default,
 because it demonstrated the best predictive performance and most attractive trade-off between sensitivity and specificity in our simulations.
-
 When estimating the model, it is important to ascertain that the algorithm has converged before interpreting the results.
-Stan, the computational back-end of `brma()`, should return warnings and errors if there are indications of non-convergence.
-<!-- Sara, wat kan men nog meer doen om convergence te checken?
-Iets met trace plots?
-Alle standaard plots voor stan-model objecten zijn beschikbaar, dankzij de functie `as.stan()`.
-Misschien kan je wat tips geven hier?; SvE: ik zal dit verwerken in de toepassing.
--->
+Stan, the computational back-end of `brma()`, returns warnings and errors if there are any indications of non-convergence.
+Additionally, users can obtain trace plots as described in the illustrative example.
 
@@
 
-Finally, with regard to publication, we highly recommend sharing the data and
-syntax for the meta-analysis publicly; for example, by making the entire paper reproducible using the Workflow for Reproducible Code in Science [WORCS, @vanlissaWORCSWorkflowOpen2020].
-Transparency allows readers and reviewers to verify that methods were correctly applied, and try alternative analyses.
-Particularly when using a new method like BRMA, this transparency is likely to inspire confidence in the results.
-Secondly, the results of a meta-analysis can be used to obtain predictions for the expected effect size of a new study on the same topic, given specific design characteristics.
+Finally, with regard to publication, we highly recommend making the data and code for the meta-analysis publicly available.
+One way to do this is by creating a reproducible research repository,
+for example, using the Workflow for Reproducible Code in Science [WORCS, @vanlissaWORCSWorkflowOpen2020].
+Transparency allows readers and reviewers to verify that methods were correctly applied,
+which should inspire greater confidence in the results.
+Others can easily perform sensitivity analyses by changing the analysis code.
+Sharing data allows the meta-analysis to be updated in the future,
+which increases the reuse value of the data.
+Finally, sharing the model object (or code to reproduce it) allows others to obtain predictions for the expected effect size of a new study on the same topic.
 This prediction can be used to conduct power analysis for future research.
@@
 BRMA may not be the best solution for every situation.
-Several trade-offs must be made to decide what method is most appropriate.
-Firstly, the fact that BRMA has high predictive performance compared to RMA suggests that it is a particularly suitable technique when a researcher intends to obtain results that will generalize beyond the sample at hand, and is willing to accept some bias in parameter estimates.
-Conversely, RMA might be more suitable when the goal is to describe the sample at hand in an unbiased manner, with less concern for generalizability to future studies.
-Secondly, the fact that BRMA has high specificity compared to RMA suggests that it is a suitable technique when a researcher seeks to eliminate irrelevant moderators at the cost of increasing the Type II error rate.
+Several trade-offs must be considered to decide what method is most appropriate.
+Firstly, the fact that BRMA has high predictive performance compared to RMA suggests that it is particularly suitable when a researcher intends to obtain results that will generalize beyond the sample at hand,
+and is willing to accept some bias in parameter estimates.
+Conversely, RMA might be more suitable when the goal is to describe the sample at hand in an unbiased manner,
+with less concern for generalizability to future studies.
+Secondly, the fact that BRMA has high specificity compared to RMA suggests that it is more suitable when a researcher seeks to eliminate irrelevant moderators at the cost of increasing the Type II error rate.
 Conversely, RMA might be more suitable when the researcher seeks to identify relevant moderators, at the cost of increasing the Type I error rate.
-If many moderators have been coded, and many of them are expected to be irrelevant, then BRMA may thus be prererable.
+If many moderators have been coded, and many of them are expected to be irrelevant, then BRMA may thus be preferable.
 Thirdly, there may be pragmatic reasons for preferring BRMA over RMA.
 For example, if a dataset is small, or the number of moderators is high relative to the number of cases,
-RMA models may prove to be empirically under-identified.
+RMA models may be empirically under-identified.
 This can be indicated by convergence problems.
@@
 BRMA had better predictive performance than RMA, which indicates that results from BRMA analysis generalize better to new data.
-This predictive performance advantage was especially pronounced when training data were as small as 20 studies, suggesting that BRMA is suitable as a small sample solution.
-This is an appealing quality, because many meta-analyses have small sample sizes.
-BRMA further has greater specificity in rejecting irrelevant moderators from a larger set of potential candidates, while keeping overall variable selection accuracy approximately constant to RMA.
+This predictive performance advantage was especially pronounced when training data were as small as 20 studies.
+This is appealing because many meta-analyses have small sample sizes.
+BRMA further has greater specificity in rejecting irrelevant moderators from a larger set of potential candidates, while maintaining an overall variable selection accuracy equivalent to RMA.
 Although the estimated regression coefficients are biased towards zero by design,
@@
 \newpage
+# Highlights
+
+* Many applied meta-analyses concern heterogeneous bodies of literature, with many between-studies differences (moderators).
+* Simultaneously, meta-analytic samples are often small. There is thus limited statistical power to account for moderators.
+* The present study introduces Bayesian Regularized Meta-Analysis (BRMA), an algorithm that applies regularization to identify relevant moderators from a larger number of candidates.
+* The algorithm is made available in a user-friendly R-package, `pema`, which is published on CRAN.
+* Readers across fields can use this method to account for between-studies heterogeneity in meta-analysis, without concern that models may be underfit or underpowered.
+
+\newpage
 

### 2022-04-23 R/brma.R

@@ -386,6 +386,8 @@ brma_imp <- function(cl){
   foroutput[["X"]] <- lapply(out,`[[`, "X")
   foroutput[["Y"]] <- lapply(out,`[[`, "Y")
   foroutput[["vi"]] <- lapply(out,`[[`, "vi")
+  # Check if all Y is the same; if so, compute tau2 and R2 over all chains.
+  # If not, take mean of tau2s and R2s
   foroutput[["tau2"]] <- mean(sapply(out,`[[`, "tau2"))
   foroutput[["R2"]] <- mean(sapply(out,`[[`, "R2"))
   if(!is.null(foroutput[["study"]])) foroutput[["study"]] <- lapply(out,`[[`, "study")
@@ -413,9 +415,7 @@ calc_r2 <- function(tau2, vi, Y, N){
     max(0, (sum(Wi * (Y - (
       sum(Wi * Y) / sum(Wi)
     )) ^ 2) - (N - 1)) / (sum(Wi) - (sum(Wi ^ 2) / sum(Wi))))
-
-  R2 <- max(0, 100 * (tau2_before-tau2)/tau2_before)
-  return(c(tau2, R2))
+  return(max(0, 100 * (tau2_before-tau2)/tau2_before))
 }
 
 stanfit_to_brma <- function(fit, coefficients, X, Y, vi, tau2, R2, k, ...){

### 2022-07-13 README.Rmd
prepare for CRAN submission

--- 2021-12-10 README.Rmd
@@
 
-<!-- [![CRAN status](https://www.r-pkg.org/badges/version/pema)](https://cran.r-project.org/package=pema) -->
-<!-- [![CRAN RStudio mirror downloads](https://cranlogs.r-pkg.org/badges/grand-total/pema?color=blue)](https://r-pkg.org/pkg/pema) -->
+[![CRAN status](https://www.r-pkg.org/badges/version/pema)](https://CRAN.R-project.org/package=pema)
+[![CRAN RStudio mirror downloads](https://cranlogs.r-pkg.org/badges/grand-total/pema?color=blue)](https://r-pkg.org/pkg/pema)
 [![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
@@
 
-Use [R-universe](https://cjvanlissa.r-universe.dev) to install the development version of `pema`
+Use [CRAN](https://CRAN.R-project.org/package=pema) to install the latest release of `pema`:
+
+```
+install.packages("pema")
+```
+
+Alternatively, use [R-universe](https://cjvanlissa.r-universe.dev) to install the development version of `pema`
 by running the following code:

### 2022-11-10 paper/manuscript.Rmd
prepare for CRAN submission
Update abstract, table ref

@@
   applied meta-analyses lack the power to adequately account for multiple
-  moderators, as the number of studies on any given topic is often low. The
-  present study introduces Bayesian Regularized Meta-Analysis (BRMA), an
-  algorithm that performs variable selection to identify relevant moderators
-  from a larger number of candidates.
-  This approach is suitable when heterogeneity is suspected, but
-  it is not known which moderators most strongly inﬂuence the observed effect
-  size. We present a simulation study to validate the performance of BRMA
-  relative to state-of-the-art meta-regression (RMA). Results indicated that
-  BRMA compared favorably to RMA on three metrics: predictive performance (a
-  measure of generalizability), the ability to reject irrelevant moderators,
+  moderators, as the number of studies on any given topic is often low.
+  [The present study introduces Bayesian Regularized Meta-Analysis (BRMA),
+  which uses regularizing (LASSO or horseshoe) priors to shrink small
+  regression coefficients towards zero]{#lassoabstract}, thereby selecting relevant
+  moderators from a larger number of candidates.
+  This approach is suitable when heterogeneity is suspected,
+  but it is not known which moderators most strongly inﬂuence the
+  observed effect size.
+  We present a simulation study to validate the performance of BRMA
+  relative to state-of-the-art random effects meta-analysis using REML   (RMA).
+  Results indicated that BRMA compared favorably to RMA on three metrics:
+  predictive performance (a measure of generalizability),
+  the ability to reject irrelevant moderators,
   and the ability to recover population parameters with
-  low bias. BRMA had slightly lower ability to detect true effects of relevant
+  low bias.
+  BRMA had slightly lower ability to detect true effects of relevant
   moderators, but the overall proportion of Type I and Type II errors was
@@
 
-The present study set out to validate the BRMA algorithm using a simulation study.
+The present simulation study set out to validate the BRMA algorithm.
 As a benchmark for comparison, we used restricted maximum likelihood meta-regression,
@@
 Within data sets, the BRMA with a horseshoe prior had the highest predictive performance `r round(whichhi[1]*100)`% of the time, followed by RMA, `r round(whichhi[3]*100)`%, and finally BRMA with a LASSO prior, `r round(whichhi[2]*100)`%.
-Results indicated that the overall $R^2_{test}$ was highest for BRMA with a horseshoe prior and lowest for RMA, see \@ref(tab:tabr2).
+Results indicated that the overall $R^2_{test}$ was highest for BRMA with a horseshoe prior and lowest for RMA, see Table \@ref(tab:tabr2).
 This difference was driven in part by the fact that explained variance was somewhat higher for the BRMA models when the true effect was non-zero (i.e., in the presence of a population effect),

### 2022-11-10 paper/action_letter.Rmd
Create action letter

---
title       : "Selecting relevant moderators with Bayesian regularized meta-regression"
authors     : "masked"
journal     : "Research Synthesis Methods"
editor      : "Pigott"
manuscript  : "RSM-04-2022-0056"
class       : "draft"
bibliography      : ["r-references.bib", "references.bib",
                     "sara-references.bib", "eli-references.bib"]
output      : papaja::revision_letter_pdf
---

```{r, message=FALSE, warning=FALSE}
library(revise)
man <- read_manuscript("manuscript.Rmd")
```

Dear Dr. `r rmarkdown::metadata$editor`,

Thank you for considering our manuscript for publication in _`r rmarkdown::metadata$journal`_.
We appreciate the thorough and critical comments you solicited,
which helped strengthen the argumentation, clarify the structure, and add nuance.
We have attempted to address all comments as thoroughly as possible.
All changes are explained below.
We hope that you will find the quality of the work to be sufficiently improved.

Yours sincerely,

the authors

# Associate Editor {-}

\RC{The authors introduce their implementation of a regularisation approach for estimation and variable selection in meta-regression, which seems a timely contribution given the danger of overfitting. Some more detail or elaboration would be helpful in some places.}

\RC{please consider whether the title is appropriate, or whether (something like) "Selecting..." or "Selection of..." might be better.}

We appreciate the suggestion and have changed the title to:

*Selecting relevant moderators with Bayesian regularized meta-regression*

\RC{in abstract and Introduction, please consider being more concrete here: it might be good to mention here already that this is about penalisation/LASSO/horseshoe priors in order to give the reader a better idea.}

We appreciate the suggestion and have made the requested change. The Abstract now reads:

`r get_manuscript("lassoabstract")`

In the Introduction, we now write:

REF

\RC{on p.16 (Section "design factors"):
what were the total numbers of variables (or "noise moderators")?}

\RC{regarding the 3rd comment by Reviewer 1: in the context of variable selection, the so-called "penalized complexity priors" (here: exponential priors for the heterogeneity standard deviation) might play a role.}

# Reviewer 1

\RC{The manuscript provides an interesting approach based on regularization to selection of covariates in meta-regression, when the number of covariates is relevant. The Authors focus on a Bayesian strategy.
Although I found the topic interesting, the study needs some additional investigations and the text needs to be substantially modified in order to provide a clear and exhaustive picture of the proposal.
My comments and questions are listed below.}

\RC{The introduction is too long in terms of explanation of the meta-regression and selection of covariates problems, with many repetitions. For example, end of page 4 and beginning of page 5 include many repetitions about between-study heterogeneity. Other parts, instead, require a substantially deeper explanation. }

\RC{Which theories useful for variable selection do you refer to in page 5 ? The description is extremely vague.}

\RC{The topic of the study is variable selection from a Bayesian point of view: but the description is so short. Just a few lines about the novelty of the paper in page 6, with no clear description of the proposal and with the reference to pema package without even the explanation of the name of the package.}

\RC{Statistical underpinnings: Again, I found a lot of repetitions in the text.}

\RC{Probably, in (1) you mean \theta and not \Theta? As you have \theta int the text. Why do you use theta and not beta, as you do for the meta-regression model in (7)? The notation would be simplified and would be more consistent.}

\RC{The sentence in lines 132-133 is not clear.}

\RC{line 147: probably the explanation of the error term should be anticipated where the error term appears for the first time.}

\RC{line 152: “to estimate this model “ has a preferable statistical sound than “to solve this model”}

\RC{lines 163- 166 describe some features of regularization….but regularization is introduced later, from line 167.}

\RC{Regularized regression + Bayesian estimation
I found both the sections very short and lacking of many details.}

\RC{what about the existing literature using lasso for meta-regression?}

\RC{In addition, I expected some references about the theory of LASSO given the relevance of the instrument in the literature.}

\RC{line 183-184: “other penalties exist”: ok, so discuss about, indicate advantages and disadvantages of the other solutions; why do you not focus on them in the study? If you do not, just explain why.}

\RC{Bayesian estimation: I think that some additional methodological details and additional explanations about priors and their comparison to the classical LASSO would help the reader.}

\RC{Why details relevant for the Bayesian estimation are included in the “Implementation” section? I mean lasso prior and horseshoe prior, that is, details useful to understand the methodology.}

\RC{Can you comment about the choice of the numerical values in the priors at the end of page 11?}

\RC{line 221: “this extension”: which one?}

\RC{line 225: “This is accomplished by..” Why?}

\RC{line 240: “values are reasonable in most applications” Why? Can you prove this?}

\RC{lines 244-251 seems to be pertinent to the methodology of the proposal not to implementation.}

\RC{More in general, I do not like to see a mixture of methodology and R code. I think I would be more useful for  the reader to have sections describing the proposed approach and the underlying methodology (something that is not present at the emano) and then having an appendix about the code. }

\RC{line 278: “x==0” could be substituted by “x is equal to 0” as this is a text, not a source code.}

\RC{Intercept.
I don’t think it is so relevant to deserve a section. Why not inserting a line in the section devoted to the code?}

\RC{Performance indicators, Design factors, Predictive performance
* You split the data in training set and test set, for each iteration. So, how do you account for the variability associated to the choice of the test set (as done for example in cross-validation)?}

\RC{I’m surprised by the large number fo linea devoted to the explanation of such a basic indicator like R2. In addition, it is well known to be optimistic, and thus the adjusted version I usually preferable. Why don’t you evaluate the method using other indicators, such as the adjusted r2, AIC, or BIC?}

\RC{line 344: I suppose you mean the estimate of sensitivity and specificity.}

\RC{line 368: 100 datasets only? Probably, there is a typo, as 100 is the number of datasets included in the test set, if I’m not wrong. In any case, 100 is a very low number of replicates for a simulation study, I suggest to increase at least to the common value equal to 1,000.}

\RC{line 385: do you mean “Table” 1?}

\RC{line 405: “the” most negative?}

\RC{lines 449-452 are not necessary as bias and variance are known concepts. However, in Tables I can see only bias, and not information about variance.}

\RC{lines 469-470: there is a white space}

\RC{Could you please avoid writing pema::bonapersona and use instead dataset titled bonapersona in the R pema package? This is not a list of lines code, but a text.}

\RC{you have 440 experiments in the dataset: do you mean 440 study included in the meta-regression? If so, the number is much. Larger than the scenarios evaluated in the simulations.}

\RC{Finally, There are many typos and inconsistencies throughout the text (e.g., data set and dataset, random effect and randoms-effects, …).}

# Reviewer 2

\RC{Comments to the Author
The authors investigated selection of moderators for the meta-regression, which is especially useful to explain the sources of heterogeneity between trials. They proposed the use of regularizing priors for meta-regression within a Bayesian framework. They shared publicly available R package "pema" which relies on rstan, which helps practitioners to use the proposed methods. I think the contribution of the paper and R package is important. However, I have some comments.}

## Major points

\RC{1) I think it is important to note some limitations of meta-regression. For example, the use of moderators might "break" the randomization, when the studies analyzed are randomized controlled trials. This is because it is not possible to randomize patients to one moderator, see Thompson and Higgins (2002) section 3 for further discussion of limitations of meta-regression of clinical trials.}

\RC{2) Important references are missing, in which the use of regularization or penalization approaches for the meta-analysis were investigated, although not the same purpose as in the current paper. For example, in Chung et al (2013) regularizing prior was used for the heterogeneity parameter to avoid boundary estimates, and in Günhan et al (2020) regularizing priors were used for the heterogeneity parameter and treatment effect parameter to deal with data sparsity. Finally and most importantly, Röver et al (2021) reviewed different use of regularizing priors and provided some guidance. Note that in the mentioned references, the term of weakly informative priors are used instead of regularizing priors (also see an earlier reference by Gelman (2006) in a hierarchical model context). Mention of these publications and relationship to the present paper can help the reader.}

\RC{3) An important part of Bayesian random-effects meta-analysis is the specification of the prior for the heterogeneity parameter tau. Can you include more specifications on the prior choice for tau and influence of the choice to the results (if there is any).}

\RC{4) In the abstract and in the main text, it states "We present a simulation study to validate the performance of BRMA relative to state-of-the-art meta-regression (RMA)". What does RMA refer to here, is it "Random effect Meta-Analysis using REML"? If yes, I think the term random-effect meta-analysis (or meta-regression) using RMLE is more clear than state-of-the-art meta-analysis (or meta-regression).}

## Minor points

\RC{Line 385: "see 1": I think Table is missing}

Thank you; we have corrected this.

# References
1) Thompson SG, Higgins JPT. How should meta-regression analyses be undertaken and interpreted?. Stat Med. 2002;21:1559-1573.
2) Chung Y, Rabe-Hesketh S, Choi IH. Avoiding zero between-study variance estimates in random-effects meta-analysis. Stat Med. 2013;32(23):4071-4089.
3) Günhan, BK, Röver, C, Friede, T. Random-effects meta-analysis of few studies involving rare events. Res Syn Meth. 2020; 11: 74– 90. https://doi.org/10.1002/jrsm.1370
4) Röver, C, Bender, R, Dias, S, et al. On weakly informative prior distributions for the heterogeneity parameter in Bayesian random-effects meta-analysis. Res Syn Meth. 2021; 12: 448– 474. https://doi.org/10.1002/jrsm.1475
5) Gelman A. Prior distributions for variance parameters in hierarchical models. Bayesian Anal. 2006;1(3):515-534. https://doi.org/10.1214/06-BA117A.

\newpage

# References

::: {#refs custom-style="Bibliography"}
:::

### 2022-11-10 paper/manuscript.Rmd
Update

@@
   in meta-analysis.
+  The method is implemented in the R-package 
+  `pema` (penalized meta-analysis) and in the free open source statistical software package JASP.
 
@@
 an algorithm that uses Bayesian estimation with regularizing priors to perform variable selection in meta-analysis.
-The algorithm is implemented in the function `brma()` in the R-package `pema`.
+Regularizing priors assign a high probability mass to near-zero values,
+which keeps small regression coefficients close to zero, resulting in a sparse solution.
+This manuscript discusses two shrinkage priors,
+the LASSO and horseshoe prior.
 <!--

### 2022-11-19 paper/action_letter.Rmd
update 2022-11-19 10:59:30

@@
 library(revise)
-man <- read_manuscript("manuscript.Rmd")
+read_manuscript("manuscript.Rmd")
 ```
@@
 
-`r get_manuscript("lassoabstract")`
+`r get_revision("lassoabstract")`
 
@@
 
+We see now that we did not report clearly enough how many design factors there were and what they were.
+Apparently, it was also not sufficiently clear that "noise moderators" are not the same as "design factors".
+To address this comment and avoid confusion, we have rewritten this paragraph as follows:
+
+`r get_revision("designfactors")`
+
 \RC{regarding the 3rd comment by Reviewer 1: in the context of variable selection, the so-called "penalized complexity priors" (here: exponential priors for the heterogeneity standard deviation) might play a role.}
+
+REF
 
@@
 
+We thank the Reviewer for their constructive comments, which substantially helped improve the quality of the manuscript.
+We have tried to address them all in turn, as detailed below.
+
 \RC{The introduction is too long in terms of explanation of the meta-regression and selection of covariates problems, with many repetitions.
 For example, end of page 4 and beginning of page 5 include many repetitions about between-study heterogeneity.
-Other parts, instead, require a substantially deeper explanation.
-}
+Other parts, instead, require a substantially deeper explanation.}
 
@@
 
-\RC{Probably, in (1) you mean \theta and not \Theta?
-As you have \theta int the text.
+\RC{Probably, in (1) you mean $\theta$ and not $\Theta$?
+As you have $\theta$ int the text.
 Why do you use theta and not beta, as you do for the meta-regression model in (7)?
@@
 \RC{line 278: “x==0” could be substituted by “x is equal to 0” as this is a text, not a source code.}
+
+We have made the suggested change.
 
@@
 
+We thank the Reviewer for suggesting these references, which had eluded our literature search.
+
+We agree that the use of weakly informative priors for heterogeneity parameters was insufficiently discussed in the previous version of our manuscript, and have now added a paragraph on that topic (see our response to the next comment).
+
+However, it is important to note that the use of weakly informative priors (WIP) for heterogeneity parameters serves a categorically different purpose than the use of regularizing priors for regression coefficients - even if the term "regularization" has been used for both in prior literature.
+The purpose of WIP for heterogeneity parameters is to aid model convergence and avoid boundary estimates.
+The purpose of regularizing priors for regression coefficients is to perform variable selection.
+We believe that the newly added paragraph sufficiently clarifies these distinct uses of "regularization" (see response to next comment).
+
+Thank you for pointing out these relevant references.
+We have included the reference to Chung et al.
+(2013), Gelman (2006) and Rover et al.
+(2021) in the new section on the prior for $\tau$ (see the next comment).
+In addition we have added the following section on page ...
+to be more explicit about the terminology of different types of priors:
+
+Suggest to add this paragraph in the section on Bayesian estimation after "which reflects expectations about likely parameter values after having seen the data." Note: if included, this should be updated in the text from a previous comment to reviewer 1 as well.
+Also here it is relevant whether we use "regularizing" or "shrinkage" priors and should mention the definite choice explicitly.
+
+"As a result, the posterior distribution is a compromise between the likelihood of the data and the prior distribution.
+The influence of either the data or the prior is determined by the sample size as well as the informativeness of the prior distribution.
+The larger the sample size, the more influential the likelihood of the data will be.
+Similarly, as the prior distribution becomes more informative, i.e., more peaked, it will exert more influence on the results.
+Priors can thus be placed on a continuum from "non-informative" to "highly informative".
+Weakly informative or regularizing priors are often used in situations when there is some prior information available, for example regarding the boundaries of the parameter space or, as is the case here, regarding the existence of parameters equal to zero.
+Throughout this manuscript, we will use the term "shrinkage prior" to refer to the weakly informative or regularizing prior that holds the prior knowledge that some coefficients are equal to zero and should therefore be shrunken towards zero."
+
 \RC{3) An important part of Bayesian random-effects meta-analysis is the specification of the prior for the heterogeneity parameter tau.
 Can you include more specifications on the prior choice for tau and influence of the choice to the results (if there is any).}
+
+We agree with the Reviewer that the prior specification for the heterogeneity parameter $tau$ is important and should be addressed in the text.
+To address this comment, we have included the following paragraph in the revision:
+
+`r get_revision("tauprior")`
+
+Chung Y, Rabe-Hesketh S, Choi IH. Avoiding zero between-study variance estimates in random-effects meta-analysis. Stat Med. 2013;32(23):4071-4089.
+
+Gelman A.
+Prior distributions for variance parameters in hierarchical models.
+Bayesian Anal.
+2006;1(3):515-534. [https://doi.org/10.1214/06-BA117A](https://doi.org/10.1214/06-BA117A "https://doi.org/10.1214/06-BA117A").
+
+Gronau, Q.
+F., Van Erp, S., Heck, D.
+W., Cesario, J., Jonas, K.
+J., & Wagenmakers, E.
+J.
+(2017).
+A Bayesian model-averaged meta-analysis of the power pose effect with informed and default priors: The case of felt power. _Comprehensive Results in Social Psychology_, _2_(1), 123-138.
+
+Röver, C, Bender, R, Dias, S, et al.
+On weakly informative prior distributions for the heterogeneity parameter in Bayesian random-effects meta-analysis.
+Res Syn Meth.
+2021; 12: 448– 474. [https://doi.org/10.1002/jrsm.1475](https://doi.org/10.1002/jrsm.1475 "https://doi.org/10.1002/jrsm.1475")
 
@@
 If yes, I think the term random-effect meta-analysis (or meta-regression) using RMLE is more clear than state-of-the-art meta-analysis (or meta-regression).}
+
+We have made the suggested correction. Both in the Abstract and in the text, the first time we introduce RMA, we introduce it as "random effects meta-analysis using restricted maximum likelihood".
 

### 2022-11-19 paper/manuscript.Rmd
update 2022-11-19 10:59:30

@@
 for example, the *fixed effect* model assumes that all observed effect sizes reflect one underlying true population effect.
-This assumption is well-suited to the situation where effect sizes from close replication studies are meta-analyzed [@higginsReevaluationRandomeffectsMetaanalysis2009]. 
+This assumption is appropriate when meta-analyzing effect sizes from close replication studies [@higginsReevaluationRandomeffectsMetaanalysis2009]. 
 The *random effects* model, by contrast, assumes that population effect sizes follow a normal distribution.
-Each observed effect size provides information about the mean and standard deviation of this distribution of population effect sizes.
-This assumption is more appropriate when studies are conceptually similar and differences between them are random [@higginsReevaluationRandomeffectsMetaanalysis2009].
-
-Not all heterogeneity in effect sizes is random, however.
-Quantifiable between-study differences may introduce systematic heterogeneity.
-Such between-study differences are known as "moderators".
-For example, if studies have been replicated in Europe and the Americas, this difference could be captured by a binary moderator called "continent".
-Alternatively, if studies have used different dosages of the same drug, this may be captured by a continuous moderator called "dosage".
-Systematic heterogeneity in the observed effect sizes can be accounted for using *meta-regression* [see @lopez-lopezEstimationPredictivePower2014].
-This technique provides estimates of the effect of one or more study characteristics on the overall effect size,
-as well as of the overall effect size and residual heterogeneity after controlling for their influence.
-
-One common application of meta-analysis is to summarize existing bodies of literature.
-In such situations, the number of moderators is often relatively high because similar research questions have been studied in different laboratories,
-using different methods, instruments, and samples.
-Each of these between-study differences could be coded as a moderator, and some of these moderators may explain systematic heterogeneity.
-
-The influence of multiple moderators can be accounted for using meta-regression.
-However, like any regression-based approach, meta-regression requires a relatively high number of cases (studies) per parameter to obtain sufficient power to examine heterogeneity.
-In applied meta-analyses, the number of available studies is often too low to examine heterogeneity reliably [@rileyInterpretationRandomEffects2011].
-At the same time, there are many potential sources of heterogeneity,
-as similar research questions are studied in different laboratories, using different methods,
-instruments, and samples.
-This leads to a problem known as the "curse of dimensionality": the number of candidate moderators is large relative to the number of cases in the data.
+<!-- Each observed effect size provides information about the mean and standard deviation of this distribution. -->
+This assumption is more appropriate when studies are conceptually similar but vary in small random ways that introduce heterogeneity in effect sizes [@higginsReevaluationRandomeffectsMetaanalysis2009].
+
+Heterogeneity in effect sizes is not always random, however.
+When similar research questions are studied by different labs, in different populations, using different study designs, measurement instruments, and methods - those between-study differences may introduce *systematic heterogeneity*.
+Suspected causes of systematic heterogeneity can either be used as exclusion criteria,
+or accounted for using *meta-regression* [see @lopez-lopezEstimationPredictivePower2014].
+Meta-regression estimates the effect of study characteristics on effect size,
+and provides an estimate of the overall effect size and residual heterogeneity after controlling for their influence.
+For example, if studies have been replicated in Europe and the Americas,
+one could either exclude studies from Europe from further analysis,
+or code a binary moderator variable called "continent".
+One could then estimate the average effect size across both continents.
+Similarly, if studies have examined the effect of a drug at different dosages,
+one could code dosage as a continuous moderator, and control for its influence - thus estimating the overall effect size at average dosages.
+
+A common application of meta-analysis is to summarize existing bodies of literature.
+In such situations, there are many potentially relevant between-study differences that could be coded as moderators.
+Although meta-regression can accommodate multiple moderators,
+like any regression-based approach, it requires a relatively high number of cases (studies) per parameter to obtain sufficient statistical power.
+In applied meta-analyses, the number of available studies is often too low to obtain sufficient power [@rileyInterpretationRandomEffects2011],
+or even so low that the model is not identified [@akaikeNewLookStatistical1974].
+This problem is known as the "curse of dimensionality".
 <!-- This poses a challenge in the -->
@@
 <!-- high number of cases per parameter.  -->
-Between-studies differences present a non-trivial challenge to data aggregation
-using classic meta-analytic methods.
+Between-studies differences thus pose a non-trivial challenge to classic meta-analytic methods.
 At the same time, they also provide an unexploited
-opportunity to learn which differences between studies have an impact on the effect size
+opportunity to learn which factors impact the effect size
 found, if adequate exploratory techniques are used.
 
-Addressing this curse of dimensionality necessitates *variable selection*:
-the selection of a smaller subset of relevant moderators from a larger number of candidate moderators.
-One way to perform variable selection is by relying on theory.
-However, in many fields of science, theories exist at the individual level of analysis (e.g., in social science, at the level of individual people).
-These theories do not necessarily generalize to the study level of analysis.
-Using theories at the individual level for moderator selection at the study level amounts to committing the ecological fallacy: generalizing inferences across levels of analysis [@jargowskyEcologicalFallacy2004].
+The curse of dimensionality can be overcome using *variable selection*:
+identifying a smaller subset of relevant moderators from a larger number of candidate moderators [@hastieElementsStatisticalLearning2009].
+One way to perform variable selection is by relying on theory, and selecting only moderators that should theoretically have an impact on effect size.
+Note, however, that theories at the individual level of analysis do not necessarily generalize to the study level of analysis.
+In the social sciences, for example, many theories describe phenomena at the level of individual people.
+Using such theories for variable selection at the study level amounts to committing the ecological fallacy: generalizing inferences across levels of analysis [@jargowskyEcologicalFallacy2004].
 To illustrate what a theory at the study level of analysis might look like, 
@@
 There is precedent for the use of machine learning to perform variable selection in meta-analysis [@vanlissaSmallSampleMetaanalyses2020].
-This work used the *random forest* algorithm; a non-parametric approach that largely ignores irrelevant moderators.
+This prior work used the non-parametric *random forest* algorithm.
 One limitation of random forests is that non-parametric models are harder to interpret,
-particularly for a readership that is accustomed to linear models,
-where the effect of each predictor is described by a single parameter.
-An alternative method for variable selection that can be used in linear models is *regularization*:
-shrinking model parameters towards zero, such that irrelevant moderators are eliminated.
+particularly when the readership is accustomed to linear models that describe the effect of each moderator with a single parameter.
+
+Regularization is a method for variable selection that can be applied in linear models.
+It effectively shrinks small model parameters towards zero,
+such that irrelevant moderators are eliminated.
 The present paper introduces *Bayesian regularized meta-regression* (BRMA),
@@
 
-To understand how BRMA estimates the relevant parameters and performs variable selection, it is instructional to first review the statistical underpinnings of the aforementioned classic approaches to meta-analysis.
-First is the fixed-effect model, which assumes that each observed effect size $T_i$ is an estimate of an underlying true effect size $\Theta$ [@hedgesFixedRandomeffectsModels1998].
-The only cause of heterogeneity in observed effect sizes is presumed to be effect size-specific sampling variance, $v_i$, which is treated as known, and computed as the square of the standard error of the effect size.
-Thus, for a collection of $k$ studies, the observed effects sizes of individual studies $i$ (for $i$ = 1,2, . . . $k$) are given by:
+To understand how BRMA estimates the relevant parameters and performs variable selection,
+it is instructional to first review the statistical underpinnings of classical meta-analysis.
+As mentioned before, the fixed effect model assumes that each observed effect size $T_i$ is an estimate of an underlying true effect size $\Theta$ [@hedgesFixedRandomeffectsModels1998].
+The only cause of heterogeneity in observed effect sizes is presumed to be sampling error, $v_i$, which is treated as known, and computed as the square of the standard error of the effect size.
+Thus, for a collection of $k$ studies,
+the observed effects sizes of individual studies $i$ (for $i \in [1,2, \ldots k]$) are given by:
 
@@
 
-<!--
-\begin{aligned}
-y_i &= \theta_i + \epsilon_i &\text{where } \epsilon_i \sim N(0, \sigma^2_i)\\ % \text{ and } 
-%\theta_1 &= \theta_2 \dots = \theta_k
-\end{aligned}-->
-
-Under the fixed effect model, the estimated population effect size  $\hat{\theta}$ is obtained by computing a weighted average of the observed effect sizes.
-If sampling error is assumed to be the only source of variance in the observed effect size,
-then it follows that studies with smaller standard errors estimate the underlying true effect size more precisely<!--(Schmidt, Oh \& Hayes, 2009)-->.
-The fixed-effect weights are thus simply the reciprocal of the sampling variance, $w_{i} =  \frac{1}{v_i}$.
+The estimated population effect size $\hat{\theta}$ is then a weighted average of the observed effect sizes.
+The assumption that sampling error is the only source of variance in observed effect sizes implies that studies with smaller standard errors estimate the underlying true effect size more precisely and should accrue more weight.
+Therefore, fixed effect weights are simply the reciprocal of the sampling variance, $w_{i} =  \frac{1}{v_i}$.
 The estimate of the true effect is a weighted average across observed effect sizes:
@@
 Even in replication studies there are sometimes moderators that are unanticipated (Kunert, 2016).
-This leads very often to an eventual poor performance of the fixed-effects meta-analysis model (Snijders, 2005).
--->
-
-Whereas the fixed-effect model assumes that only one true population effect exists,
-the random-effects model assumes that true effects may vary for unknown reasons,
-and thus follow a (normal) distribution of their own [@hedgesFixedRandomeffectsModels1998].
-This heterogeneity of the true effects is represented by their variance, $\tau^{2}$.
-The random effects model thus assumes that the heterogeneity in observed effects can be decomposed into sampling error and between-studies heterogeneity, resulting in the following equation for the observed effect sizes:
+This leads very often to an eventual poor performance of the fixed effects meta-analysis model (Snijders, 2005).
+-->
+
+The random effects model assumes that, in addition to sampling error, true effects may vary for random reasons,
+and thus follow a (normal) distribution with mean $\Theta$ and variance $\tau^{2}$ [@hedgesFixedRandomeffectsModels1998].
+The observed effect sizes are thus given by:
 
@@
 
-In this model, $\Theta$ is the mean of the distribution of true effect sizes, and $\tau^2$ is its variance, which can be interpreted as the variance between studies.
-
-If the true effect sizes follow a distribution, 
-then even less precise studies (with larger sampling errors) may provide some information about this distribution.
-Like fixed-effect weights, random effects weights are still influenced by sampling error, but this influence is attenuated by the estimated variance of the true effect sizes. 
-The random-effects weights are thus given by $w_{i} =  \frac{1}{v_i + \hat{\tau}^2}$.
-It is important to note that,
-whereas the sampling error for each individual effect size is treated as known, the
-between-study heterogeneity $\tau^{2}$ must be estimated.
+As in the fixed effect model,
+studies with smaller sampling errors are assigned more weight.
+However, to account for the fact that all studies now provide some information about different regions of the distribution of true effect sizes,
+the weights are attenuated in proportion to the spread of that distribution.
+The random effects weights are thus given by $w_{i} =  \frac{1}{v_i + \hat{\tau}^2}$.
+Whereas sampling error is still treated as known,
+the between-study heterogeneity $\tau^{2}$ must be estimated.
 This estimate is represented by $\hat{\tau}^{2}$.
 
-### Meta-regression
-
-The random-effects model assumes that causes of heterogeneity in the true effect sizes are unknown, and that their influence is random.
-Oftentimes, however, there are systematic sources of heterogeneity in true effect sizes.
-These between-study differences can be coded as moderators, and their influence can be estimated and controlled for using meta-regression.
-Meta-regression with $p$ moderators can be expressed with the following equation, where $x_{1\ldots p}$ represent the moderators, and $\beta_{1\ldots p}$ the regression coefficients:
+Meta-regression extends the random effects model to account for systematic sources of heterogeneity, which are coded as moderators.
+The equation below describes a model with $p$ moderators, where $x_{1\ldots p}$ represent the moderators, and $\beta_{1\ldots p}$ their regression coefficients.
+Note that $\beta_0$ represents the intercept of the distribution of true effect sizes after controlling for the moderators
+and the error term $\zeta_{i}$ represents residual unexplained between-studies heterogeneity.
+This is a mixed-effects model; the intercept and effects of moderators are treated as fixed and the residual heterogeneity as random [@lopez-lopezEstimationPredictivePower2014]:
 
@@
 
-Note that $\beta_0$ represents the intercept of the distribution of true effect sizes after controlling for the moderators
-and the error term $\zeta_{i}$ represents residual between-studies heterogeneity.
-This term is included because unexplained heterogeneity often remains after accounting for the moderators.
-This is a mixed-effects model; the intercept and effects of moderators are treated as fixed and the residual heterogeneity as random [@lopez-lopezEstimationPredictivePower2014].
-
-<!--
-An accurate estimation of the residual heterogeneity contributes to a better interpretation of the effect of the moderators (Panityakul, Bumrungsup \& Knapp, 2013).-->
-
-To solve this model, the regression coefficients and residual heterogeneity must be estimated simultaneously.
 <!--The topic of estimating the residual heterogeneity is a highly discussed one (Veroniki et al., 2016; Viechtbauer \& López-López, 2015; Panityakul et al., 2013).
@@
 According to Sidik \& Jonkman (2007), it is generally the case that the larger true between-study variance is, the more biased the estimate can be, which diminishes the performance of the method.-->
-Numerous methods have been proposed to estimate meta-regression models, the most commonly used of which is restricted maximum likelihood (REML).
-REML is an iterative method, meaning it performs the same calculations repeatedly, updating the estimated regression coefficients and residual heterogeneity until these estimates stabilize.
+The parameters of this model are the regression coefficients and residual heterogeneity.
+Numerous methods have been proposed to estimate meta-regression models,
+the most common of which is restricted maximum likelihood (REML).
+REML is an iterative method, which means that it repeatedly performs the same calculations and updates the estimated parameters until their estimates stabilize.
 <!--, including the Hedges (HE), DerSimonian–Laird/Method of Moments (DL), Sidik and Jonkman (SJ), Maximum Likelihood (ML), Restricted Maximum Likelihood (REML), and Empirical Bayes (EB) method.
@@
 It is important to note that some iterative methods do not produce a solution when they fail to converge after a predetermined amount of iteration.-->
-This estimator has low bias, which means that the average value of the estimated regression coefficients and residual heterogeneity is close to their true values [@panityakulEstimatingResidualHeterogeneity2013].
+This estimator has low bias, which means that the average values of the parameters are close to their true values [@panityakulEstimatingResidualHeterogeneity2013].
 <!-- ; (Panityakul et al., 2013; Hardy & Thompson, 1996). -->
 However, this bias comes at the cost of higher variance, which means that the estimated values of a population parameter vary more from one sample to the next. 
-In practice, an estimator with higher variance generalizes less well to new data.
+An estimator with low bias and high variance produces results that generalize less well to new data than an estimator with high bias and low variance.
 This phenomenon is known as the *bias-variance trade-off*.
@@
 
-Regularized regression biases parameter estimates towards zero.
-Before examining the Bayesian case, we will explain the general principle of regularization in frequentist regression.
-OLS regression estimates the model parameters by minimizing the Residual Sum of Squares (RSS) of the dependent variable, which is given by:
+Ordinary least squares regression (OLS) estimates the model parameters by minimizing the Residual Sum of Squares (RSS) of the dependent variable.
+The resulting parameter estimates perfectly describe linear relations in the present data set, but generalize less well to new data:
 
@@
 $$
-The resulting parameter estimates are those that give the best predictions of the dependent variable in the present data set.
-Penalized regression, by contrast, adds a penalty term to the RSS.
-One commonly used penalty is the L1-norm of the regression coefficients, or LASSO penalty [@hastieElementsStatisticalLearning2009],
-which corresponds to the sum of their absolute values.
-This gives the penalized residual sum of squares:
+
+Regularized regression biases parameter estimates towards zero by adding a penalty term to the RSS.
+As an example, we will discuss the most common penalty: the sum of the absolute regression coefficients, also known as the the L1- or LASSO penalty [@hastieElementsStatisticalLearning2009].
+Note that other penalties exist.
+As the LASSO penalty is a function of the regression coefficients, it increases when they get bigger.
+This incentivizes the optimizer to keep the regression coefficients as small as possible.
+Note that the amount of regularization can be controlled by multiplying the penalty by a tuning parameter, $\lambda$.
+If $\lambda$ is zero, the shrinkage penalty has no impact.
+If $\lambda \to \infty$,
+all coefficients shrink towards zero, producing the null model.
+<!--Another commonly used penalty is the L2-norm of the coefficients, or ridge penalty,
+which corresponds to the sum of their squared values: $\sum_{j=1}^{p}\beta_{j}^2$.-->
+Cross-validation is often used to find the optimal value for the penalty parameter $\lambda$.
+<!--The LASSO penalty has the unique property of shrinking some coefficients to be exactly zero,
+but the ridge penalty does not do so, as -->
+The LASSO penalized residual sum of squares is given by:
 
@@
 $$
-
-Because the penalty term is a function of the regression coefficients,
-the optimizer is incentivized to keep the regression coefficients as small as possible.
-In this equation, $\lambda$ is a tuning parameter that determines how influential the penalty term will be.
-If $\lambda$ is zero, the shrinkage penalty has no impact and the penalized regression will produce the OLS estimates.
-If $\lambda \to \infty$, all coefficients shrink towards zero, producing the null model.
-<!--Another commonly used penalty is the L2-norm of the coefficients, or ridge penalty,
-which corresponds to the sum of their squared values: $\sum_{j=1}^{p}\beta_{j}^2$.-->
-Generally, cross-validation is used to find the optimal value for the penalty parameter $\lambda$.
-<!--The LASSO penalty has the unique property of shrinking some coefficients to be exactly zero,
-but the ridge penalty does not do so, as -->
-Note that the LASSO penalty is but one example of a shrinkage penalty; other penalties exist.
 
@@
 -->
-
 <!--
@@
 A technique developed by van Lissa (2017), designed to overcome the lacking’s of singletrees by using random forests.
-MetaForest applies random-effects or fixed-effects weights to random forests.
-Based on two simulation studies, van Lissa (2017) examined the performance of fixed-effects, random-effects and unweighted MetaForest.
+MetaForest applies random effects or fixed effects weights to random forests.
+Based on two simulation studies, van Lissa (2017) examined the performance of fixed effects, random effects and unweighted MetaForest.
 
@@
 
-One alternative to the use of a shrinkage penalty is Bayesian estimation with a regularizing prior.
-Whereas classical, frequentist estimation relies solely on the data at hand,
+An alternative to the use of a shrinkage penalty is Bayesian estimation with a regularizing prior.
 Bayesian estimation combines information from the data with a *prior distribution*.
-The prior distribution is a probability distribution that reflects expectations about likely parameter values.
-This prior is updated with the likelihood of the data to form a posterior distribution,
-which reflects expectations about likely parameter values after having seen the data.
-
-A regularizing prior distribution reflects the expectation that not all regression coefficients are substantial enough to be included in the model.
+The prior distribution assigns a-priori probability to different parameter values.
+Likely parameter values have a high probability density, and unlikely parameter values have a low probability density.
+The aforementioned (frequentist) approaches, by contrast, treat every possible parameter value as equally plausible.
+The prior distribution is updated with the likelihood of the data to form a posterior distribution,
+which reflects expectations about likely parameter values after having seen the data [for an extensive introduction, see @mcelreathStatisticalRethinkingBayesian2020].
+
+A regularizing prior distribution shrinks small coefficients towards zero by assigning high probability mass to near-zero values.
 There are many different regularizing prior distributions [@vanErpOberskiMulder2019].
-Some of these result in exactly the same solutions as frequentist penalized methods.
-For example, applying an independent double exponential (i.e., Laplace) prior to regression coefficients results in posterior modes that are equal to the classical LASSO estimates [@ParkCasella2008].
-Other distributions have been developed specifically for the purpose of providing good shrinkage properties,
-meaning that the prior pulls small regression coefficients towards zero,
-while leaving larger regression coefficients mostly unaffected. 
-A popular prior in this regard is the horseshoe prior [@CarvalhoPolsonScott2010].
+Some of these regularizing priors are analogous to specific frequentist methods.
+For example, a double exponential prior (hereafter: LASSO prior) results in posterior distributions whose modes are identical to the estimates from LASSO-penalized regression [@ParkCasella2008].
+
+A limitation of the LASSO prior is that it introduces substantial bias in non-zero regression coefficients.
+To overcome this limitation, regularizing priors with better shrinkage properties have been developed.
+These priors still pull small regression coefficients towards zero,
+but exert less bias on larger regression coefficients.
+One example is the horseshoe prior [@CarvalhoPolsonScott2010].
 It has heavier tails than the LASSO prior,
@@
 
-### Implementation
-
-Bayesian penalized meta-analysis is implemented in the function `brma()` in the R-package `pema`.
-For estimation, it depends on Stan, a probabilistic programming language that uses Hamiltonian Monte Carlo to sample from the posterior distribution [@StanManual].
-Being written in C++, Stan is computationally efficient, but models must be compiled prior to estimation.
-This results in substantial computational overhead.
-To avoid this overhead, `pema` uses pre-compiled models corresponding to random-effects and three-level meta-regression, with and without an intercept.
-Future updates may bring additional models.
-At the time of writing, `brma()` supports two priors: the LASSO and the regularized horseshoe.
-The LASSO prior is implemented as follows:
-
+The BRMA method introduced here offers both LASSO and horseshoe priors.
+The LASSO prior is given by:
 $$
@@
 where DE denotes the double exponential distribution with a location equal to 0 and a scale determined by a global scale parameter $s$ and an inverse-tuning parameter $\lambda$.
-By default in `brma()`, the global scale parameter is set to 1,
-and the inverse-tuning parameter is given a $\chi^2$ prior with 1 degree of freedom.
+In the present study, the global scale parameter is set to 1,
+and the inverse-tuning parameter is assigned a $\chi^2$ prior distribution with 1 degree of freedom.
 Its value is thus optimized during model estimation.
 
-The implementation of the horseshoe prior is based on the regularized horseshoe proposed by @PiironenVehtari2017b:
+The regularizing horseshoe prior was proposed by @PiironenVehtari2017b and is given by:
 $$
@@
 $$
-where N denotes the normal distribution, student-$t^+$ denotes the half-t distribution and $\Gamma^{-1}$ denotes the inverse Gamma distribution. 
-This extension of the horseshoe is more numerically stable in certain cases.
+where $N$ denotes the normal distribution, student-$t^+$ denotes the half-t distribution and $\Gamma^{-1}$ denotes the inverse Gamma distribution. 
 In this formula, $\lambda^2_0$ is a global scale parameter that affects the overall shrinkage of the prior, with smaller values resulting in more shrinkage.
-The default value in `brma()` is 1.
-However, if prior information regarding the number of relevant moderators is available,
+In the present study, we assume a default value of $\lambda^2_0 = 1$.
+However, if prior information regarding the expected number of relevant moderators is available,
 it is best to include this information.
-This is accomplished by setting $\lambda^2_0 = \frac{p_0}{p-p_0}{\frac{\sigma}{\sqrt{n}}}$, where $p_0$ represents the number of relevant moderators, $p$ the total number of moderators, $\sigma$ is the residual standard deviation and $n$ equals the number of observations.
-An alternative, user-friendly way to accomplish this is by setting the argument `relevant_pars` equal to the expected number of relevant moderators. 
+This is accomplished by setting $\lambda^2_0 = \frac{p_0}{p-p_0}{\frac{\sigma}{\sqrt{n}}}$, where $p_0$ represents the expected number of relevant moderators, $p$ the total number of moderators, $\sigma$ is the residual standard deviation and $n$ equals the number of observations.
 <!-- SvE: nu twijfel ik toch weer of dit helemaal goed gaat.
@@
 -->
-The thickness of the tails is controlled by two degrees of freedom parameters, $\nu_1$ and $\nu_2$, which default to 1 in `brma()`.
+The thickness of the tails is controlled by two degrees of freedom parameters, $\nu_1$ and $\nu_2$.
+In this study, we assume default values of 1 for these parameters.
 Increasing these degrees of freedom parameters results in a prior with lighter tails,
@@
 However, in cases where the model is weakly identified, for example when there are more moderators than observations, these lighter tails can aid model convergence. 
-The regularized horseshoe differs from the standard horseshoe in the specification of a finite "slab".
+The regularizing horseshoe differs from the standard horseshoe in the specification of a finite "slab".
 This slab ensures at least some regularization of large coefficients and as a consequence,
@@
 This slab is governed by a degrees of freedom parameter ($\nu_3$, set to 4) and a scale parameter ($s$, set to 1).
-
-Default settings for these hyperparameters in `brma()` were chosen such that the values are reasonable in most applications.
-However, it is good practice to perform a prior sensitivity analysis to compare the effect of different hyperparameters on the model results. 
+This extension ensures greater numerical stability of the results.
+
+The default settings discussed above are reasonable in most applications.
+However, it is good practice to perform sensitivity analysis to determine how sensitive the model results are to different prior specifications. 
 This is particularly important when the sample is small, as the prior is more influential in this case.
+
+<span id = "tauprior">
+The choice of prior distributions is an important decision in any Bayesian analysis.
+This also applies to the heterogeneity parameters.
+In the case of random effects meta-regression,
+the only heterogeneity parameter is the between-studies variance, $\tau^2$.
+In the case of three-level multilevel meta-regression,
+there is a within-study and between-studies variance.
+
+A crucial challenge with heterogeneity parameters in meta-regression is that the number of observations at the within- and between-study level is often small.
+This can result in poor model convergence [@roverWeaklyInformativePrior2021],
+or boundary estimates at zero [@chungAvoidingZeroBetweenstudy2013].
+A well-known advantage of Bayesian meta-analysis is that it can overcome these challenges by using weakly informative priors, which guide the estimator towards plausible values for the heterogeneity parameters.
+There is less consensus, however, about which priors are best for this purpose [@roverWeaklyInformativePrior2021].
+By default, `brma()` uses a prior that was specifically developed for multilevel heterogeneity parameters
+[@gelmanPriorDistributionsVariance2006]:
+the half-Student's t distribution with large variance, $df = 3, scale = 2.5$.
+Note that other suitable weakly informative priors have been discussed in the literature, but have not (yet) been implemented in `brma()`, such as the Wishart prior [@chungWeaklyInformativePrior2015], but has not been implemented in `brma()`.
+There has also been increasing interest in the use of informative priors for heterogeneity parameters when information about their values is available [@thompsonGroupspecificPriorDistribution2020].
+The use of informative priors is out of scope for BRMA, however, as BRMA takes a pragmatic approach to Bayesian analysis, using weakly informative priors to aid convergence for heterogeneity parameters,
+and regularizing priors to perform variable selection for regression coefficients.
+If researchers do wish to construct alternative prior specifications, they may want to develop a custom model in `rstan` instead [@rstan].
+</span>
 
@@
 Penalized regression analyses typically require the scales of predictors to be equivalent [@tibshirani1996].
-This is because the regularization penalizes coefficients without regard for their scale.
-If variable scales differ, this can lead to an imbalanced penalization of coefficients that does not reflect differences in variable importance [@lee2015note].
+This is because regularization penalizes coefficients equally, without regard for their scale.
+If variables are on different scales,
+this can lead to uneven penalization of coefficients in which
+variables with smaller standard deviations are biased more strongly towards zero [@lee2015note].
 To clarify, a regression parameter $\beta$ can be interpreted as the expected increase in outcome $y$ for a one unit increase in predictor $x$.
@@
 in which the mean of all predictors is set to 0 and their standard deviation is set to 1 [@gelman2008scaling].
-By default, this type of standardization is used in the `brma()` function.
-The estimated parameters are restored to their original scales.
+This type of standardization is also used by default in BRMA.
+
+After standardization, the estimated parameters can be restored to their original scales.
 For the intercept, the transformation is:
-
 $$
@@
 The regression coefficients are returned to their original scale by applying:
-
 $$
@@
 $$
-It is not always necessary or desirable to standardize predictors, however.
-For example, if predictors are already standardized or on a unified scale for different reasons.
-In these cases standardization does not make scales more equal, nor the penalization more fair, and the default standardization in `brma()` can be disabled.
+Note that standardization is not always necessary or desirable.
+If predictors are already on equivalent scales,
+standardization does not make scales more equal, nor the penalization more fair
 <!--Alternatively, if the goal of a study is to compare results to prior findings based on unstandardized predictors, standardization would make penalization unequal across studies.-->
 
-There are additional considerations regarding standardization of binary and dummy predictors [@alkharusi2012categorical].
-Some suggest to always standardize binary predictors [@tibshirani1997lasso].
-This makes that, irrespective of initial scaling, the binary predictor will be on the same scale as the continuous standardized predictors [@gelman2008scaling].
-However, standardizing binary predictors may decrease model interpretability [@wissmann2007role].
-To illustrate this point, consider bivariate regression with a single binary predictor $x$ that takes on values 0 and 1 predicting outcome $y$.
-The intercept represents the expected value of $y$ when $x == 0$, and the regression coefficient represents the difference in the expected value of $y$ between the two conditions [@alkharusi2012categorical].
-By standardizing this binary predictor, the reference value is no longer zero, and both the intercept and its regression coefficient have no clear interpretation anymore, especially in multivariate cases [@wissmann2007role].
-
-The default in `brma()` is to use dummy coding for categorical predictors and standardize the dummies.
-Other coding schemes for categorical predictors exist that are equivalent in OLS regression.
-In penalized regression, by contrast, the choice of coding does affect model fit and interpretation due to the introduction of bias [@chiquet2016coding; @detmer2020note].
-Although the `brma()` function allows users to specify alternative coding schemes and standardization options,
-be advised that these decisions do affect model accuracy and interpretability in penalized regression [see @chiquet2016coding; @detmer2020note].
-
-There are two ways to circumvent the default standardization in `brma()`.
-The first is to disable standardization entirely, analyzing predictors in their original scale,
-by setting `standardize = FALSE`.
-Alternatively, `brma()` allows custom standardization.
-To use this option, first manually standardize (some of) the predictors.
-Then, when calling `brma()`, pass a vector of means and a vector of standard deviations to restore the coefficients to the predictors' original scale.
-This can be accomplished using the argument `standardize = list(center = meanvector, scale = sdvector)`.
-For predictors that **should not** be standardized, pass a mean of 0 and a standard deviation of 1;
-this leaves the coefficient in question unaffected.
+There are additional considerations regarding standardization of categorical predictors [@alkharusi2012categorical].
+As binary predictors can be straightforwardly included as predictors in linear models,
+the most common way to represent categorical predictors is by choosing one response option as reference category,
+and creating binary dummy variables to represent other response categories.
+If these dummies are not standardized,
+they might be unevenly penalized, as explained before.
+However, standardizing dummy variables compromises the interpretability of their regression coefficients [@tibshiraniLassoMethodVariable1997; @wissmann2007role].
+To illustrate this challenge, consider bivariate regression with a single binary predictor $x$ that takes on values 0 and 1 predicting outcome $y$.
+The intercept represents the expected value of $y$ when $x$ is equal to zero, and the regression coefficient represents the difference in the expected value of $y$ between the two conditions [@alkharusi2012categorical].
+By standardizing this binary predictor, the reference value is no longer zero, and both the intercept and its regression coefficient have no clear interpretation anymore.
+Extending this example to the multivariate case further complicates the problem [@wissmann2007role].
+
+The appropriate solution depends on the research goals;
+if the primary goal is variable selection,
+then the dummies should be standardized.
+However, if the primary goal is interpretation of the coefficients,
+they should not be [@gelman2008scaling].
+A related challenge is that, whereas various coding schemes for categorical predictors are equivalent in OLS regression, this is not the case in penalized regression.
+The choice of coding affects model fit and interpretation of the coefficients [@chiquet2016coding; @detmer2020note].
 
@@
 This so-called *ANOVA specification* of a model estimates a mean for all dummy-coded categories.
-In BRMA, as in other R functions, one can use ANOVA specification by explicitly removing the intercept from the model formula; for example, if `yi` is the effect size and $C$ a categorical moderator, regression specification with $c-1$ dummies is specified as `yi ~ C`, and ANOVA specification with $c$ dummies is specified as `yi ~ -1 + C`.
+
 <!-- This part seems a repetition from the info on standardization of dummies above?: 
@@
 -->
+
+## Implementation
+
+We implemented BRMA in the function `brma()` in the statistical programming language R [@R-base],
+in the package `pema`, short for *pe*nalized *m*eta *a*nalysis.
+The `brma()` function aims to make Bayesian regularized regression readily available via a user-friendly interface.
+R-users can install the package from CRAN, by running `install.packages("pema")`.
+Non-R-users can use BRMA via the "Penalized Meta-Analysis" extension of JASP [@JASP2022],
+a free open source statistical software package with a graphical user interface, see Figure \@ref(fig:figjasp).
+
+```{r figjasp, fig.cap="Using BRMA via the JASP software package." }
+knitr::include_graphics("jasp.png")
+```
+
+For estimation, `brma()` depends on Stan, a probabilistic programming language that uses Hamiltonian Monte Carlo to sample from the posterior distribution [@StanManual].
+Stan is written in C++, and thus computationally efficient, but custom models must be compiled prior to estimation.
+This results in substantial computational overhead,
+and installing a toolchain to compile models requires some technical sophistication.
+To avoid this overhead, `pema` uses pre-compiled stock models with opinionated default options.
+At the time of writing, these include random effects and three-level meta-regression with and without an intercept.
+R-users can refer to the package documentation to see what options are available at the time of reading by running `?pema::brma`.
+Researchers who wish to construct a model that is currently out of scope of `brma()` are referred to `rstan` instead [@rstan].
+As a starting point, the `rstan` source code for the stock models included with `pema` is available in `pema:::stanmodels`.
+We welcome contributions of additional models.
+
+The function `brma()` has two main interfaces:
+a formula interface, corresponding to base-R functions like `lm()`,
+in which the user provides a model `formula` that references variables in a `data` argument.
+The second interface is more amenable to machine learning applications,
+and accepts an `x` matrix of predictors and a `y` vector of effect sizes.
+Additionally, `brma()` has an argument `vi`, which refers to the effect size variances,
+and `study`, which (optionally) refers to a clustering variable for three-level meta-regression.
+Both of these arguments accept either the name of a column in `data`, or a numeric vector.
+
+As mentioned before, the R-implementation of BRMA has several options that can be customized.
+The most important option relates to the choice of priors f the regression coefficients.
+At the time of writing, `brma()` supports two priors for regression coefficients: the LASSO and the regularized horseshoe.
+A prior is selected using the `method` argument;
+the `prior` argument is used to specify custom values for the prior hyperparameters (see Statistical underpinnings).
+The lasso prior uses Laplace priors, whose scale is determined by the `scale` parameter multiplied with a scale parameter,
+which in turn is assigned a chi-square prior distribution with `df` degrees of freedom.
+Increasing `df` allows for larger values for the inverse-tuning parameter, leading to less shrinkage.
+
+The horseshoe prior has several shrinkage parameters,
+all assigned Student's t prior distributions with parameters `df` and `scale`.
+The `df` parameter controls the thickness of the tails,
+with higher values corresponding to thinner tails, which assign less probability mass to extreme values.
+The `scale` parameter controls how wide the prior is;
+smaller values assign most probability mass to values near zero, thus resulting in more regularization.
+The parameters `df` and `scale` are local shrinkage parameters, enabling flexible shrinkage of separate regression coefficients.
+Parameters `df_global` and `scale_global` control global shrinkage that influences all coefficients similarly.
+The regularized horseshoe applies additional regularization to very large coefficients,
+which is governed by parameters `df_slab` and `scale_slab`.
+This additional regularization ensures at least some shrinkage of large coefficients to avoid any sampling problems.
+When prior information regarding the expected number of relevant moderators is available,
+this information can be incorporated via the `relevant_pars` argument.
+The `scale_global` argument is then ignored and instead calculated based on `relevant_pars`.
+
+Another important decision is whether or not to standardize parameters.
+By default, `brma()` standardizes the predictor matrix,
+and restores model coefficients to their original scale,
+as explained in Statistical underpinnings.
+There are two ways to circumvent this default standardization.
+The first is to disable standardization entirely, analyzing predictors in their original scale,
+by setting `standardize = FALSE`.
+Alternatively, `brma()` allows custom standardization.
+To use this option, first manually standardize (some of) the predictors.
+Then, when calling `brma()`, provide the means (`means`) and standard deviations (`sds`) that should be used to restore coefficients to the predictors' original scale.
+This can be accomplished using the argument `standardize = list(center = means, scale = sds)`.
+This approach can also be used to select predictors that **should not** be standardized:
+For these predictors,
+simply pass a mean of 0 and a standard deviation of 1;
+this leaves the coefficient in question unaffected.
 
@@
 and their ability to recover population parameters. 
-Our research questions are whether BRMA offers a performance advantage over RMA in terms of any of these indicators,
+Our research questions are whether BRMA offers a performance advantage over state-of-the-art random effects meta-analysis using restricted maximum likelihood [RMA, @viechtbauerConductingMetaanalysesMetafor2010] in terms of any of these indicators,
 and which prior (regularized horseshoe versus LASSO) is to be preferred.
@@
 
-To examine performance in a range of realistic meta-analysis scenarios,
-several design factors were manipulated:
-The number of studies in the training data $k \in (20, 40, 100)$, the average within-study sample size $\bar{n} \in (40, 80, 160)$, the population effect size of relevant moderators $\beta \in (0, .2, .5, .8)$, the number of moderators $p \in (2, 3, 6)$, and residual heterogeneity $\tau^{2} \in (.01, .04, .1)$.
+<span id = "designfactors">To examine performance in a range of realistic meta-analysis scenarios,
+seven design factors were manipulated:
+First, we manipulated the number of studies in the training data $k \in (20, 40, 100)$. 
+Second, the average within-study sample size $\bar{n} \in (40, 80, 160)$. 
+Third, 
+true effect sizes were simulated according to two models:
+one with a linear effect of one moderator, $T_{i}= \beta x_{1i} + \epsilon_i$, and one with a non-linear (cubic) effect of one moderator, $T_{i}= \beta x_{1i} + \beta x_{1i}^{2} + \beta x_{1i}^{3} + \epsilon_i$,
+where $\epsilon_i \sim N(0, \tau^2)$.
+As both BRMA and RMA assume linear effects,
+simulating data from a non-linear model allows us to examine how robust the different methods are to violations of this assumption.
+The fourth design factor was the population effect size $\beta$ in the aforementioned models, with $\beta \in (0, .2, .5, .8)$. 
+Fifth, we manipulated the residual heterogeneity $\tau^2$ in the aforementioned models, with $\tau^{2} \in (.01, .04, .1)$.
+According to a review of 705 published psychological meta-analyses (Van Erp et al., 2017),
+these values of $\tau^2$ fall within the range observed in practice.
+Sixth, we varied the number of moderators not associated with the effect size $M \in (1, 2, 5)$.
+These are the moderators that ought to be shrunk to zero by BRMA.
+Note that the total number of moderators is $M+1$,
+as one moderator is used to compute the true effect size (see the third design factor).
+Finally, moderator variables were simulated as skewed normal moderators, with scale parameter $\omega \in (0, 2, 10)$, where $\omega = 0$ corresponds to the standard normal distribution.</span>
+All unique combinations of these design factors produced `r out$conditions` unique conditions.
+For each simulation condition, 100 data sets were generated.
+In each data set, the observed effect size $y_i$ was simulated as a standardized mean difference (SMD),
+sampled from a non-central $t$-distribution.
+
 <!-- **het aantal moderatoren is redelijk laag; ik zou vooral nog voordelen van brma verwachten met meer moderatoren maar is dat realistisch in de praktijk?
@@
 Een voorbeeld kan zijn een set van moderatoren die de kwaliteit van studies proberen te vatten zoals we laatst hebben besproken -->
-According to a review of 705 published psychological meta-analyses (Van Erp et al., 2017),
-these values of $\tau^2$ fall within the range observed in practice.
-Note that both BRMA and RMA assume linear effects.
-To test the robustness of the algorithms to violations of this assumption, true effect sizes were simulated using two models:
-one with a linear effect of one moderator, $T_{i}= \beta x_{1i} + \epsilon_i$, and one with a non-linear (cubic) effect of one moderator, $T_{i}= \beta x_{1i} + \beta x_{1i}^{2} + \beta x_{1i}^{3} + \epsilon_i$,
-where $\epsilon_i \sim N(0, \tau^2)$.
-The algorithms further assume normality of residuals.
-To examine robustness of the algorithms to violations of this assumption,
-moderator variables were simulated as skewed normal moderators, with scale parameter $\omega \in (0, 2, 10)$, where $\omega = 0$ corresponds to the standard normal distribution.
-The design factors combined to produce `r out$conditions` unique conditions.
-For all simulation conditions, 100 data sets were generated. 
-In each data set, the observed effect size $y_i$ was simulated as a standardized mean difference (SMD),
-sampled from a non-central $t$-distribution.
 
@@
 to be meta-analyzed appears to be heterogeneous;
-the same rationale commonly used to support the use of random-effects meta-analysis (Higgins et al., 2009).
-The latter can be accomplished by conducting a random-effects meta-analysis without any moderators,
+the same rationale commonly used to support the use of random effects meta-analysis (Higgins et al., 2009).
+The latter can be accomplished by conducting a random effects meta-analysis without any moderators,
 and reporting the estimated $\tau^2$.

### 2022-11-23 paper/action_letter.Rmd
add supplemental tables

@@
 bibliography      : ["r-references.bib", "references.bib",
-                     "sara-references.bib", "eli-references.bib"]
+                     "sara-references.bib", "eli-references.bib", "metaforest.bib"]
 output      : papaja::revision_letter_pdf
@@
 
+In addressing all comments below, we have added detail and elaboration in many places. We hope that this addresses this comment.
+
 \RC{please consider whether the title is appropriate, or whether (something like) "Selecting..." or "Selection of..." might be better.}
@@
 
-We appreciate the suggestion and have made the requested change. The Abstract now reads:
+To address this comment and others,
+we have restructured the Introduction to be more to the point.
+We still provide the same background information in a more abbreviated form at a later point.
+With regard to the specific request to mention penalisation/LASSO/horseshoe priors in the Abstract and Introduction, we have made the following changes. The Abstract now reads:
 
@@
 
-In the Introduction, we now write:
+The Introduction now states:
 
-REF
+`r get_revision("lassointroduction")`
 
@@
 
-REF
+To address the 3d comment by Reviewer 2, we have included the following paragraph in the revision:
+
+`r get_revision("tauprior")`
 
@@
 
+To address this comment and others,
+we have restructured the Introduction to be more to the point.
+We still provide the same background information in a more abbreviated form at a later point.
+We have elaborated on all the points that were raised by the Reviewers (see our responses to the other comments).
+
 \RC{Which theories useful for variable selection do you refer to in page 5 ? The description is extremely vague.}
+
+We have attempted to clarify this section by invoking an additional reference and rewriting it as follows:
+
+`r get_revision("theory")`
 
@@
 
+To address this comment, we have made the following changes:
+
+1) We have rewritten the opening paragraph to clearly state the problem addressed in this paper, and the proposed solution:
+
+`r get_revision("openingparagraph")`
+
+\WorkInProgress
+
 \RC{Statistical underpinnings: Again, I found a lot of repetitions in the text.}
+
+\WorkInProgress
 
@@
 
+We have made the suggested change and now use the intercept $\beta_0$ in place of $\Theta$. We have also simplified the notation of the estimated population effect to $\hat{\beta_0}$.
+
 \RC{The sentence in lines 132-133 is not clear.}
+
+\WorkInProgress
 
@@
 
+\WorkInProgress
+
 \RC{line 152: “to estimate this model “ has a preferable statistical sound than “to solve this model”}
 
+\WorkInProgress
+
 \RC{lines 163- 166 describe some features of regularization….but regularization is introduced later, from line 167.}
+
+\WorkInProgress
 
@@
 
+\WorkInProgress
+
 \RC{what about the existing literature using lasso for meta-regression?}
 
+\WorkInProgress
+
 \RC{In addition, I expected some references about the theory of LASSO given the relevance of the instrument in the literature.}
+
+\WorkInProgress
 
@@
 
+\WorkInProgress
+
 \RC{Bayesian estimation: I think that some additional methodological details and additional explanations about priors and their comparison to the classical LASSO would help the reader.}
+
+As requested, we have added this information. These sections now read:
+
+`r get_revision("morepriors")`
+
+<!-- Second, the frequentist LASSO shrinks some coefficients to be exactly zero, thereby performing automatic variable selection.  -->
+<!-- This is not the case for its Bayesian counterpart, which always provides a continuous posterior probability distribution. -->
+<!-- Variable selection is then performed by determining which parameters have a high probability density assigned to near-zero values. -->
+<!-- Third, classical penalized regression approaches rely on optimization while the Bayesian framework generally relies on Markov Chain Monte Carlo (MCMC) sampling to obtain the posterior distribution.
+As a result, Bayesian estimation tends to be slower compared to classical estimation.
+-->
 
@@
 
+We agree with the Reviewer that this information would be better positioned in another section.
+To address this comment, we have restructured the paper; the information about priors is now incorporated into the *Bayesian estimation* section, and the *Implementation* section now exclusively relates to the `pema` R-package.
+
 \RC{Can you comment about the choice of the numerical values in the priors at the end of page 11?}
+
+\WorkInProgress
 
@@
 
+We intended to explain that the regularizing horseshoe prior is an extension of the (normal) horseshoe prior. This was insufficiently clear.
+To address this comment, we have written the following section:
+
+`r get_revision("horseshoe")`
+
 \RC{line 225: “This is accomplished by..” Why?}
+
+We have rephrased this so that it is clearer that the formula explains how this is achieved. The section now reads:
+
+`r get_revision("expectedmods")`
 
@@
 
+We thank the Reviewer for pointing out that this statement raises more questions than it answers.
+To address this Reviewer comment, we have moved this statement to the Discussion and slightly rephrased it to clarify that it is supported by the results of the present study.
+It now reads:
+
+`r get_revision("sensitivityanalysis")`
+
 \RC{lines 244-251 seems to be pertinent to the methodology of the proposal not to implementation.}
 
+We agree with the Reviewer that the writing in this section was too methodological.
+To address this comment, we have made two changes: This paragraph has been moved to the section on Bayesian estimation, and we have rewritten it as follows:
+
+`r get_revision("intervals")`
+
 \RC{More in general, I do not like to see a mixture of methodology and R code.
-I think I would be more useful for  the reader to have sections describing the proposed approach and the underlying methodology (something that is not present at the emano) and then having an appendix about the code.
-}
+I think I would be more useful for  the reader to have sections describing the proposed approach and the underlying methodology (something that is not present at the emano) and then having an appendix about the code.}
+
+To address this comment, we have made a stricter separation between methodology and code. 
+All references to code are now relegated to the Implementation section.
+
+We do believe that there are advantages to having code in the paper and not in an appendix, as the intended readership for this paper consists of those who wish to conduct a Bayesian regularized meta-analysis.
+We hope that the current approach is an acceptable compromise.
 
@@
 
+This section is important because omitting the intercept from the model has very different implications for penalized Bayesian meta-regression than for frequentist models (where the model is equivalent, regardless of whether the intercept is included or not).
+
+To clarify this, we have rewritten this section to focus on the implications of including or excluding the intercept.
+The line explaining *how* to include or exclude the intercept has been moved to the Implementation paragraph, consistent with the Reviewer's request to relegate code to a separate section:
+
+`get_revision("intercept")`
+
 \RC{Performance indicators, Design factors, Predictive performance
 * You split the data in training set and test set, for each iteration. So, how do you account for the variability associated to the choice of the test set (as done for example in cross-validation)?}
+
+We respectfully believe that this comment is based on a misunderstanding of the procedure.
+We do not split a finite sample into a training and testing set - 
+we simulate data for both sets from the same known data generating model.
+Each sample from this model is independent and identically distributed (IID).
+The distinction between training and testing is thus arbitrary.
+This is different from real data analyses, where the available dataset is finite, and training and testing data are drawn from that finite dataset - thus violating the assumption of IID.
+
+In a real dataset, if one case has very unusual values (i.e., an outlier),
+the model could be biased if this case ends up in the training data, and the performance metrics could be biased if this case ends up in the testing data.
+In our simulation study, outliers have exactly equal probabilities of appearing in the training or testing data - and as we are not sampling from a finite dataset, the probability of having an outlier in the training data is independent from having one in the testing data.
+
+Their effect on the estimated parameters is known as "Monte Carlo error" and averages out across replications of the simulation.
 
@@
 
+We respectfully feel that it is important to define how we operationalized each outcome metric, and why we use it.
+Unfortunately, we now realize that our explanation was not sufficiently clear.
+To address this comment, we have rewritten the explanation of our outcome metric, $R^2_{test}$.
+We hope that this revised explanation clarifies that this is **not** the basic indicator R2, but rather, a different type of R2 that is suitable for assessing overfitting:
+
+`r get_revision("rsquared")`
+
+Additionally,
+the reason we do not use AIC or BIC is because these are comparative fit indices, only suitable for comparing a set of models; we have only a single model and AIC or BIC do not speak to the absolute fit of a single model.
+
+The reason we do not use adjusted $R^2$ is because it is an approximation of $R^2_{test}$ but calculated on the training sample data.
+Since we simulate data from a known true model,
+we do not need to *estimate* $R^2_{test}$ - we can *calculate* it directly, based on a new sample.
+
 \RC{line 344: I suppose you mean the estimate of sensitivity and specificity.}
+
+We have rephrased this as suggested.
 
@@
 
+As these simulations are very computationally demanding,
+and increasing the number of replications adds only marginal accuracy gains, we did indeed use 100 replications.
+However, as per the Reviewer's request, we have increased this to 1000.
+
 \RC{line 385: do you mean “Table” 1?}
+
+Thank you for pointing out this omission; we have corrected it.
 
@@
 
-\RC{lines 449-452 are not necessary as bias and variance are known concepts. However, in Tables I can see only bias, and not information about variance.}
+We corrected this, and slightly rephrased the sentence for clarity.
+
+\RC{lines 449-452 are not necessary as bias and variance are known concepts.}
+
+We respectfully feel that it is prudent to define how all outcome metrics are operationalized.
+Even though the general concepts of bias and variance may be known to most readers,
+we cannot assume that they will know exactly how these are calculated in the context of this simulation study - particularly for the broad readership of a journal like Research Synthesis Methods.
+See also our response to the comment about defining $R^2_{test}$
+
+\RC{However, in Tables I can see only bias, and not information about variance.}
+
+This is correct; we had not reported these statistics for two reasons:
+
+1.
+Unlike bias, they must be computed on aggregate across replications of each simulation condition.
+This results in a strange situation where each condition has only one outcome value.
+But it is probably fine to interpret these effect sizes as descriptive statistics.
+2. The differences between algorithms in variance of $\tau^2$ were negligible. We did not want to devote two tables to, essentially, a matrix of zeroes.
+
+To address this comment, we now describe the results in the text, and provide the requested tables as online Supplements.
 
@@
 
+We thank the Reviewer for pointing this out;
+a fragment of a sentance was cut here.
+We restored the original text.
+
 \RC{Could you please avoid writing pema::bonapersona and use instead dataset titled bonapersona in the R pema package? This is not a list of lines code, but a text.}
+
+We have done as requested.
 
@@
 
+This observation is correct, but this is not a problem. 
+The method is validated for up to 100 studies,
+so it should also be valid for >100 studies,
+as a larger sample size gives more power.
+
+The reason we used these data is because we were able to secure permission from the original author to include them in the R-package.
+This means we can make the examples reproducible, requiring only the `pema` package.
+We feel that it adds a lot to the paper to present a reproducible real-data example based on a novel dataset.
+To address this comment,
+we now acknowledge in the text that this sample is relatively large compared to the sample sizes of the simulation study:
+
+\WorkInProgress
+
 \RC{Finally, There are many typos and inconsistencies throughout the text (e.g., data set and dataset, random effect and randoms-effects, …).}
+
+\WorkInProgress
 
@@
 
+We thank the Reviewer for their encouraging words and thought-provoking comments, which we feel have helped improve the quality of the manuscript.
+
 ## Major points
@@
 This is because it is not possible to randomize patients to one moderator, see Thompson and Higgins (2002) section 3 for further discussion of limitations of meta-regression of clinical trials.}
+
+\WorkInProgress
 
@@
 Throughout this manuscript, we will use the term "shrinkage prior" to refer to the weakly informative or regularizing prior that holds the prior knowledge that some coefficients are equal to zero and should therefore be shrunken towards zero."
+
+\WorkInProgress
 

### 2022-11-23 paper/manuscript.Rmd
add supplemental tables

@@
 abstract: |
-  When analyzing a heterogeneous body of literature, there may be many
-  potentially relevant between-studies differences. These differences can be
-  coded as moderators, and accounted for using meta-regression. However, many
-  applied meta-analyses lack the power to adequately account for multiple
-  moderators, as the number of studies on any given topic is often low.
-  [The present study introduces Bayesian Regularized Meta-Analysis (BRMA),
-  which uses regularizing (LASSO or horseshoe) priors to shrink small
-  regression coefficients towards zero]{#lassoabstract}, thereby selecting relevant
-  moderators from a larger number of candidates.
-  This approach is suitable when heterogeneity is suspected,
-  but it is not known which moderators most strongly inﬂuence the
-  observed effect size.
-  We present a simulation study to validate the performance of BRMA
-  relative to state-of-the-art random effects meta-analysis using REML (RMA).
-  Results indicated that BRMA compared favorably to RMA on three metrics:
-  predictive performance (a measure of generalizability),
-  the ability to reject irrelevant moderators,
-  and the ability to recover population parameters with
-  low bias.
-  BRMA had slightly lower ability to detect true effects of relevant
-  moderators, but the overall proportion of Type I and Type II errors was
-  equivalent to RMA. BRMA regression coefficients were slightly
-  biased towards zero (by design), but its estimates of residual heterogeneity
-  were unbiased. BRMA performed well with as few as 20 studies in the training
-  data, suggesting its suitability as a small sample solution. We discuss how
-  applied researchers can use BRMA to explore between-studies heterogeneity
-  in meta-analysis.
-  The method is implemented in the R-package 
-  `pema` (penalized meta-analysis) and in the free open source statistical software package JASP.
-
-keywords          : "meta-analysis, machine learning, bayesian, lasso, horseshoe, regularized"
+  When meta-analyzing heterogeneous bodies of literature,
+  meta-regression can be used to account for potentially relevant between-studies differences.
+  A key challenge is that the number of these potential moderators is often high
+  relative to the number of studies.
+  This introduces a risk of overfitting and finding spurious results.
+  To overcome this challenge,
+  [we introduce Bayesian Regularized Meta-Analysis (BRMA),
+  which selects relevant moderators from a larger set of candidates
+  by shrinking small regression coefficients towards zero
+  with regularizing (LASSO or horseshoe) priors.]{#lassoabstract}
+  This method is suitable when there are many potential moderators,
+  but it is not known beforehand which of them are relevant.
+  A simulation study compared BRMA against state-of-the-art random effects
+  meta-regression using restricted maximum likelihood (RMA).
+  Results indicated that BRMA outperformed RMA on three metrics:
+  BRMA had superior predictive performance, which means that the results
+  generalized better;
+  BRMA was better at rejecting irrelevant moderators,
+  and worse at detecting true effects of relevant
+  moderators,
+  but the overall proportion of Type I and Type II errors was
+  equivalent to RMA.
+  BRMA regression coefficients were slightly biased towards zero (by design),
+  but its residual heterogeneity estimates were less biased than those of RMA.
+  BRMA performed well with as few as 20 studies,
+  suggesting its suitability as a small sample solution. 
+  We present free open source software implementations in the R-package `pema` (for penalized meta-analysis)
+  and in the stand-alone statistical program JASP.
+  An applied example demonstrates the use of the R-package.
+
+keywords          : "meta-analysis, machine learning, regularization, bayesian, lasso, horseshoe"
 wordcount         : "5356"
@@
 bibliography      : ["r-references.bib", "references.bib",
-                     "sara-references.bib", "eli-references.bib"]
+                     "sara-references.bib", "eli-references.bib", "metaforest.bib"]
 
@@
 output            : papaja::apa6_pdf
+header-includes:
+  - \raggedbottom
 ---
@@
 
-Meta-analysis is a quantitative form of evidence synthesis,
-whereby effect sizes from multiple similar studies are aggregated.
-In its simplest form, this aggregation consists of a weighted average of the observed effect sizes.
-Weighting accounts for the fact that some observed effect sizes are assumed to be more informative about the underlying population effect.
-<!-- Each effect size is assigned a weight that determines how influential it is in calculating the summary effect. -->
-The weights are based on specific assumptions;
-for example, the *fixed effect* model assumes that all observed effect sizes reflect one underlying true population effect.
-This assumption is appropriate when meta-analyzing effect sizes from close replication studies [@higginsReevaluationRandomeffectsMetaanalysis2009]. 
-The *random effects* model, by contrast, assumes that population effect sizes follow a normal distribution.
-<!-- Each observed effect size provides information about the mean and standard deviation of this distribution. -->
-This assumption is more appropriate when studies are conceptually similar but vary in small random ways that introduce heterogeneity in effect sizes [@higginsReevaluationRandomeffectsMetaanalysis2009].
-
-Heterogeneity in effect sizes is not always random, however.
-When similar research questions are studied by different labs, in different populations, using different study designs, measurement instruments, and methods - those between-study differences may introduce *systematic heterogeneity*.
+<span id = "openingparagraph">A common application of meta-analysis is to summarize existing bodies of literature.
+A crucial challenge is that there is often substantial heterogeneity between studies,
+because similar research questions are studied in different labs,
+sampling from different populations,
+and using different study designs, instruments, and methods.
+Any of those between-studies differences can introduce *systematic heterogeneity* in observed effect sizes.
 Suspected causes of systematic heterogeneity can either be used as exclusion criteria,
-or accounted for using *meta-regression* [see @lopez-lopezEstimationPredictivePower2014].
-Meta-regression estimates the effect of study characteristics on effect size,
-and provides an estimate of the overall effect size and residual heterogeneity after controlling for their influence.
-For example, if studies have been replicated in Europe and the Americas,
-one could either exclude studies from Europe from further analysis,
-or code a binary moderator variable called "continent".
-One could then estimate the average effect size across both continents.
-Similarly, if studies have examined the effect of a drug at different dosages,
-one could code dosage as a continuous moderator, and control for its influence - thus estimating the overall effect size at average dosages.
-
-A common application of meta-analysis is to summarize existing bodies of literature.
-In such situations, there are many potentially relevant between-study differences that could be coded as moderators.
-Although meta-regression can accommodate multiple moderators,
-like any regression-based approach, it requires a relatively high number of cases (studies) per parameter to obtain sufficient statistical power.
-In applied meta-analyses, the number of available studies is often too low to obtain sufficient power [@rileyInterpretationRandomEffects2011],
-or even so low that the model is not identified [@akaikeNewLookStatistical1974].
-This problem is known as the "curse of dimensionality".
-<!-- This poses a challenge in the -->
-<!-- classic meta-analysis paradigm, which, like any regression-based approach, requires a -->
-<!-- high number of cases per parameter.  -->
-Between-studies differences thus pose a non-trivial challenge to classic meta-analytic methods.
-At the same time, they also provide an unexploited
-opportunity to learn which factors impact the effect size
-found, if adequate exploratory techniques are used.
-
-The curse of dimensionality can be overcome using *variable selection*:
-identifying a smaller subset of relevant moderators from a larger number of candidate moderators [@hastieElementsStatisticalLearning2009].
-One way to perform variable selection is by relying on theory, and selecting only moderators that should theoretically have an impact on effect size.
-Note, however, that theories at the individual level of analysis do not necessarily generalize to the study level of analysis.
-In the social sciences, for example, many theories describe phenomena at the level of individual people.
-Using such theories for variable selection at the study level amounts to committing the ecological fallacy: generalizing inferences across levels of analysis [@jargowskyEcologicalFallacy2004].
-To illustrate what a theory at the study level of analysis might look like, 
-consider the so-called *decline effect*.
-It is a phenomenon whereby effect sizes in a particular tranche of the literature seem to diminish over time [@schoolerUnpublishedResultsHide2011].
-It has been theorized that the decline effect can be attributed to regression to the mean:
-A finding initially draws attention from the research community because an anomalously large effect size has been published, and subsequent replications find smaller effect sizes.
-Based on the decline effect, we might thus expect the variable "year of publication" to be a relevant moderator of study effect sizes.
-Note that this prediction is valid even if year is orthogonal to the outcome of interest within each study.
-Until more theory about the drivers of between-study heterogeneity is developed,
-however, this approach will have limited utility for variable selection.
-<!--A second example that might illustrate this problem is a study that concluded that American college students' empathy had decreased over time, based on meta-analysis of 72 samples collected between 1979 and 2009.-->
+or controlled for using *meta-regression* [see @lopez-lopezEstimationPredictivePower2014].
+The latter approach provides an opportunity to learn which factors impact the effect size
+found.
+However, a limitation of meta-regression is that it requires a relatively high number of cases (studies) per parameter to obtain sufficient statistical power.
+In applied meta-analyses, the number of available studies is often low [@rileyInterpretationRandomEffects2011].
+This introduces a risk of overfitting,
+which results in uninterpretable model parameters [@hastieElementsStatisticalLearning2009].
+In extreme cases, the ratio of cases to parameters can be so low that the model is not (empirically) identified,
+resulting in non-convergence [@akaikeNewLookStatistical1974].
+Accounting for between-studies heterogeneity thus poses a non-trivial challenge to classic meta-analytic methods.
+The present study introduces a novel method that overcomes this challenge by imposing Bayesian regularizing (LASSO and horseshoe) priors on the regression coefficients.
+These priors shrink the effect of irrelevant predictors towards zero while leaving important predictors relatively unaffected.
+The result is a sparse model with fewer non-zero parameters,
+which benefits model convergence, reduces overfitting, and helps identify relevant between-study differences.
+</span>
+
+## Variable selection
+
+The "curse of dimensionality" refers to the aforementioned problems that arise when the number of moderators is high relative to the number of cases [@hastieElementsStatisticalLearning2009].
+It can be overcome by performing *variable selection*:
+identifying a smaller subset of relevant moderators from the larger set of candidate moderators [@hastieElementsStatisticalLearning2009].
+<span id = "theory">One way to perform variable selection is by relying on theory,
+and selecting only moderators that should theoretically have an impact on effect size.
+An important caveat is that theories that describe phenomena at the level of individual units of analysis do not necessarily generalize to the study level.
+Using such theories for variable selection amounts to committing the ecological fallacy:
+generalizing inferences across levels of analysis [@jargowskyEcologicalFallacy2004].
+The implications of the ecological fallacy for interpreting the *results* of meta-regression have been discussed elsewhere [@bakerUnderstandingHeterogeneityMetaanalysis2009]:
+For example, meta-regression may find a significant positive effect of average sample age on treatment efficacy,
+even if age is uncorrelated with treatment effect within each study.
+A similar problem arises when using individual level theory to select study level moderators:
+If theory states that an individual's age influences their susceptibility to treatment,
+that does not imply that average sample age will be a relevant moderator of study-level treatment effect in meta-regression.
+For an example of study level theory,
+consider the *decline effect*:
+effect sizes in any given tranche of the literature tend to diminish over time [@schoolerUnpublishedResultsHide2011].
+When, by coincidence, a large effect is found, it initially draws attention from the research community.
+Subsequent replications then find smaller effects due to regression to the mean.
+Based on the decline effect, we might hypothesize "year of publication" to be a relevant moderator of study effect sizes.
+At present, few such study level theories about the drivers of heterogeneity exist, and until they are developed,
+theory has limited utility for variable selection.</span>
 
@@
 There is precedent for the use of machine learning to perform variable selection in meta-analysis [@vanlissaSmallSampleMetaanalyses2020].
-This prior work used the non-parametric *random forest* algorithm.
+This prior work used the non-parametric *random forest* algorithm to perform variable selection.
 One limitation of random forests is that non-parametric models are harder to interpret,
@@
 
-Regularization is a method for variable selection that can be applied in linear models.
-It effectively shrinks small model parameters towards zero,
+In linear models, variable selection can be accomplished via a statistical method called  *regularization*.
+Regularization shrinks small model parameters towards zero,
 such that irrelevant moderators are eliminated.
-The present paper introduces *Bayesian regularized meta-regression* (BRMA),
-an algorithm that uses Bayesian estimation with regularizing priors to perform variable selection in meta-analysis.
-Regularizing priors assign a high probability mass to near-zero values,
-which keeps small regression coefficients close to zero, resulting in a sparse solution.
+Different approaches to regularization exist [@hastieElementsStatisticalLearning2009].
+<span id = "lassointroduction">The present paper introduces *Bayesian Regularized Meta-Regression* (BRMA),
+an algorithm that uses Bayesian regularizing priors to perform variable selection in meta-analysis.
+Regularizing priors assign a high probability density to near-zero values,
+which shrinks small regression coefficients towards zero, thus resulting in a sparse solution.
 This manuscript discusses two shrinkage priors,
-the LASSO and horseshoe prior.
-<!--
-Thus, there is a need of a regularization method to curtail overfitting.
-Least Absolute Shrinkage and Selection Operator [LASSO] (L1-norm regularization) can fulfill this role, since it has an advantage in terms of feature selection.
-The goal of this project is to implement L1-norm regularization in the weighted meta-regression, developing an new estimator for regularized meta-regression.
-This dilemma could be resolved by an exploratory technique that can identify relevant moderators in meta-analysis,
-and which is relatively robust to small sample sizes.
--->
-<!--Such shrinkage is advantageous because it performs variable selection and results in a sparse model.
-Sparse models are easier to interpret, as fewer non-zero effects remain.
-Regularization also provides a solution to the curse of dimensionality; unlike standard regression models, it can provide identified models even if the number of moderators exceeds the number of cases.-->
-<!--By doing this it automatically performs variable selection.
-It does not seem to be immediately clear why shrinking the coefficients should be an improvement to the model.
-However, by shrinking the parameters, it lowers the variance of the model by increasing the bias only a little bit.
-In other words, the model sacrifices some of its ability to fit the current data, to greatly increase the ability to predict future data with the same fit (James et al., 2013).
-This is better known as the bias/variance tradeoff (Briscoe & Feldman, 2011).-->
+the LASSO and horseshoe prior.</span>
 
@@
 it is instructional to first review the statistical underpinnings of classical meta-analysis.
-As mentioned before, the fixed effect model assumes that each observed effect size $T_i$ is an estimate of an underlying true effect size $\Theta$ [@hedgesFixedRandomeffectsModels1998].
+In its simplest form, meta-analysis amounts to computing a weighted average of the effect sizes.
+Each effect size is assigned a weight that determines how influential it is in calculating the summary effect.
+The weights are based on specific assumptions.
+For example, the *fixed effect* model assumes
+that each observed effect size $T_i$ is an estimate of an underlying true population effect size $\beta_0$ [@hedgesFixedRandomeffectsModels1998].
+This assumption is appropriate when meta-analyzing close replication studies [@higginsReevaluationRandomeffectsMetaanalysis2009].
 The only cause of heterogeneity in observed effect sizes is presumed to be sampling error, $v_i$, which is treated as known, and computed as the square of the standard error of the effect size.
@@
 the observed effects sizes of individual studies $i$ (for $i \in [1,2, \ldots k]$) are given by:
-
 \begin{align}
-T_i &= \Theta + \epsilon_i\\
+T_i &= \beta_0 + \epsilon_i\\
 \text{where } \epsilon_i &\sim N(0, v_i)
 \end{align}
-
-The estimated population effect size $\hat{\theta}$ is then a weighted average of the observed effect sizes.
+The estimated population effect size $\hat{\beta_0}$ is then a weighted average of the observed effect sizes.
 The assumption that sampling error is the only source of variance in observed effect sizes implies that studies with smaller standard errors estimate the underlying true effect size more precisely and should accrue more weight.
@@
 The estimate of the true effect is a weighted average across observed effect sizes:
-
 \begin{equation}
-\hat{\theta} = \frac{\sum_{i=1}^k w_iT_i}{\sum_{i=1}^k w_i}
+\hat{\beta_0} = \frac{\sum_{i=1}^k w_iT_i}{\sum_{i=1}^k w_i}
 \end{equation}
 
-<!--A highly likely consequence is that this will lead to a huge amount of possible moderators (Caserio, 2014).
-Caused by differences in for example cultures of research populations and used methods or instruments (Neuman, 2011).
-Even in replication studies there are sometimes moderators that are unanticipated (Kunert, 2016).
-This leads very often to an eventual poor performance of the fixed effects meta-analysis model (Snijders, 2005).
--->
-
-The random effects model assumes that, in addition to sampling error, true effects may vary for random reasons,
-and thus follow a (normal) distribution with mean $\Theta$ and variance $\tau^{2}$ [@hedgesFixedRandomeffectsModels1998].
+The *random effects* model, by contrast, assumes that,
+in addition to sampling error, true effects vary for random reasons,
+and thus follow a normal distribution with mean $\beta_0$ and variance $\tau^{2}$ [@hedgesFixedRandomeffectsModels1998].
+This assumption is appropriate when studies are conceptually similar but differ in small random ways [@higginsReevaluationRandomeffectsMetaanalysis2009]. 
 The observed effect sizes are thus given by:
-
 \begin{align}
-T_i &= \Theta + \zeta_{i} + \epsilon_i\\
+T_i &= \beta_0 + \zeta_{i} + \epsilon_i\\
 \text{where } \zeta_i &\sim N(0, \tau^2)\\
@@
 \end{align}
-
 As in the fixed effect model,
@@
 
-Meta-regression extends the random effects model to account for systematic sources of heterogeneity, which are coded as moderators.
-The equation below describes a model with $p$ moderators, where $x_{1\ldots p}$ represent the moderators, and $\beta_{1\ldots p}$ their regression coefficients.
+Between-studies heterogeneity is not always random, however.
+Meta-regression extends the random effects model to account for systematic sources of heterogeneity,
+which are coded as moderators.
+It estimates the effect of moderators on effect size,
+and provides an estimate of the overall effect size and residual heterogeneity after controlling for their influence.
+For example, if studies have been conducted in Europe and the Americas,
+one could code a binary moderator variable called "continent".
+Using meta-regression, one can then estimate either the continent-specific effect size,
+or control for the difference between continents when estimating the overall average effect size.
+Similarly, if studies have examined the effect of a drug at different dosages,
+one could code dosage as a continuous moderator and estimate the overall effect size at average dosages,
+or at a specific dosage.
+The equation below describes a general model for $p$ moderators,
+where $x_{1\ldots p}$ represent the moderator variables,
+and $\beta_{1\ldots p}$ their regression coefficients.
 Note that $\beta_0$ represents the intercept of the distribution of true effect sizes after controlling for the moderators
@@
 This is a mixed-effects model; the intercept and effects of moderators are treated as fixed and the residual heterogeneity as random [@lopez-lopezEstimationPredictivePower2014]:
-
 \begin{align}
@@
 According to Sidik \& Jonkman (2007), it is generally the case that the larger true between-study variance is, the more biased the estimate can be, which diminishes the performance of the method.-->
-The parameters of this model are the regression coefficients and residual heterogeneity.
 Numerous methods have been proposed to estimate meta-regression models,
-the most common of which is restricted maximum likelihood (REML).
+the most common of which is restricted maximum likelihood [REML, @pattersonRecoveryInterblockInformation1971].
 REML is an iterative method, which means that it repeatedly performs the same calculations and updates the estimated parameters until their estimates stabilize.
-<!--, including the Hedges (HE), DerSimonian–Laird/Method of Moments (DL), Sidik and Jonkman (SJ), Maximum Likelihood (ML), Restricted Maximum Likelihood (REML), and Empirical Bayes (EB) method.
-These methods are mostly divided into two groups: closed-form or non-iterative methods and iterative methods.
-The main difference between these groups is that the closed form group uses a predetermined number of steps to provide an estimation for the residual heterogeneity, whereas the iterative methods run multiple iteration, as the name suggests, to converge to a solution when a specific criterion is met.
-It is important to note that some iterative methods do not produce a solution when they fail to converge after a predetermined amount of iteration.-->
 This estimator has low bias, which means that the average values of the parameters are close to their true values [@panityakulEstimatingResidualHeterogeneity2013].
-<!-- ; (Panityakul et al., 2013; Hardy & Thompson, 1996). -->
 However, this bias comes at the cost of higher variance, which means that the estimated values of a population parameter vary more from one sample to the next. 
@@
 
-<!--It needs a starting estimation of $\tau^{2}$, which is usually estimated by one of the non-iterative methods (Viechtbauer \& López-López, 2015).
-Besides the starting value of $\tau^{2}$, it needs in every iteration an estimation of the regression coefficients of the moderators.
-These are typically estimated by using the Weighted Least Squares (WLS) method.
-This is a variation of the Ordinary Least Squares (OLS), but in the case of meta-analysis it is necessary to assess weights to the coefficients.
-In systematic reviews large variation in standard errors is often observed, which will result in large heteroscedasticity in the estimation of the effects (Stanley \& Doucouliagos, 2017).
-The addition of weights is a way to adjust for this heteroscedasticity.
-The weights are formulated as presented in equation (5).-->
-<!--
-The usage of a WLS method to estimate the regression coefficient may be problematic in the situation where a lot of moderators are measured without their specific effects, when the amount of studies is low and when moderators are dichotomous.
-The use of a least squares method will cause problems with the prediction accuracy and the model interpretability (James, Witten, Hastie, \& Tibshirani, 2013).
-In the situation where a lot of moderators are measured and blindly included in the model, it may as well be the case that variables are included that are in fact not associated with the response.
-Including irrelevant variables in the model lowers the interpretability of the model (James et al., 2013).
-An approach is necessary that automatically excludes the variables that are irrelevant i.e.
-performs variable selection.
-As explained before, in meta-analysis it is often the case that the number of moderators closely approaches or even exceeds the number of studies included in the analysis.
-A least squares method will display a lot variability in the fit when the number of variables is not much smaller than the number of studies (James et al., 2013).
-This means that the least squares method over fits the data and loses its power to be generalizable to future observations.
-When the number of variables exceeds the number of studies, the least squares method fails to produce one unique estimate and the method should not be used at all.
-
-However, a least squares method could still be somewhat valuable in some situations.
-It is extremely suitable to estimate a linear relationship.
-In the case of dichotomous moderators, the relationship is always perfectly linear.
-A powerful non-linear estimation tool is in the situation of dichotomous moderators unnecessary and would not perform better at all.
-Whenever a non-linear relation gets fitted on data with an underlying linear relation, it will cause problems when this fit gets used for the prediction of future data.
-Given the various arguments, this paper provides an approach to tackle this problem of the least squares methods whilst still making use of a linear method.
-The weighted least squares are replaced with the so-called LASSO regression for the estimation of the regression coefficients.
-This algorithm shrinks or penalizes the regression coefficients and performs variable selection (James et al., 2013; Hesterberg, Choi, Meier, \& Fraley, 2008).-->
-
 ### Regularized regression
@@
 The resulting parameter estimates perfectly describe linear relations in the present data set, but generalize less well to new data:
-
 $$
@@
 $$
-
 Regularized regression biases parameter estimates towards zero by adding a penalty term to the RSS.
@@
 If $\lambda$ is zero, the shrinkage penalty has no impact.
-If $\lambda \to \infty$,
-all coefficients shrink towards zero, producing the null model.
-<!--Another commonly used penalty is the L2-norm of the coefficients, or ridge penalty,
-which corresponds to the sum of their squared values: $\sum_{j=1}^{p}\beta_{j}^2$.-->
+As $\lambda$ increases,
+all coefficients shrink towards zero, ultimately producing the null model.
 Cross-validation is often used to find the optimal value for the penalty parameter $\lambda$.
-<!--The LASSO penalty has the unique property of shrinking some coefficients to be exactly zero,
-but the ridge penalty does not do so, as -->
 The LASSO penalized residual sum of squares is given by:
-
 $$
@@
 
-<!--The Lasso shrinkage method is not the only shrinkage method, there do exist some others.
-Nevertheless, the lasso is in the case the best option.
-It possesses, as opposed to other methods, the ability to shrink the parameter not towards zero, but to be exactly zero (James et al., 2013; Hesterberg, Choi, Meier, \& Fraley, 2008).
-This means that the lasso can perform variable selection, something that is specifically aimed for in this study.
--->
-<!--
-**Alternative to linear model: Tree Based models**
-An alternative that can perform variable selection, are tree-based models.
-These kinds of models have numerous other advantages over linear models.
-Tree-based models can be used for any data type, are easy to represent visually, require little data preparation and got larger power than linear regressions when moderators exceed observations in quantity.
-They are also more flexible in handling moderator interactions and non-linearity.
-As a result of that, they are better in modelling the complicated nature of human behaviour (Earp \& Trafimow, 2015).
-Decision trees split from the top down and group data in so-called ‘sub-nodes’, in which the data’s aspects are most homogeneous.
-The goal is to split to get the sub-nodes as uniform as possible, which can be until fully homogenous groups, or if a pre-specified touchstone is reached.
-Still, singletree based models have some limitations.
-First of all, tree models are unstable, small fluctuations that are utilized to make the model have a possibility to lead to considerable alterations in the constructions of the tree (Dwyer \& Holte, 2007).
-Second, it has problems with seizing linearity, because it only makes ‘twofold splits’ (Steyerberg, 2019).
-At last, tree-based models are susceptible to overfitting (Hastie et al, 2009).
-
-There are also more complex tree-based models, known as random-forests, which surmount most of the disadvantages of singletree.
-This variant incorporates multiple decision trees, and combines results from those trees to create a single model with a more accurate estimate (Breiman, 2001).
-The essential idea behind is know as the ‘wisdom of crowds’, a large number of relatively uncorrelated trees operating as a group will outperform any of the individual elements.
-The somewhat low correlation between the models is fundamental, because uncorrelated models are able to produce ensemble predictions with a higher accuracy that any individual prediction.
-This is because the trees preserve each other from their own singular errors (Genuer, Poggi \& Tuleau-Malot, 2010).
-The lower tendency to overfitting is another advantage of random forests over single trees (Bühlmann \& Yu, 2002).
-As well as the possibility to predict cases that are not components of the bootstrap sample of the tree.
-This kind of measure is known as out-of-bag error, which is an approximation of the cross-validation error, and provides proper estimates of the prediction accuracy in further samples (Hastie et al., 2009).
-An alternative to explore heterogeneity in meta-analysis with a singletree-based method is MetaForest.
-A technique developed by van Lissa (2017), designed to overcome the lacking’s of singletrees by using random forests.
-MetaForest applies random effects or fixed effects weights to random forests.
-Based on two simulation studies, van Lissa (2017) examined the performance of fixed effects, random effects and unweighted MetaForest.
-
-The study displayed also other advantages from random forests over singletrees.
-It had greater power, was able to make better predictions, gave estimates of the cross-validation error and yielded useful measures of variable importance and partial prediction plots (van Lissa, 2017).
-MetaForest can at the moment be considered as the best working technique to explore heterogeneity in meta-analysis.
-In van Lissa (2017), that only presented estimates of $\tau^{2}$ based on the raw data, we saw that MetaForest had certain robustness against a low number of studies.
-If moderators were continuously distributed, MetaForest had sufficient power at approximately 20 studies.
-However, there is an important feature to prove before we can make such an assumption.
-The underlying data generating models in the two simulation studies of van Lissa (2017) only included normal distributed moderators.
-Renouncing from normal distributions may affect the performance of the model, but since normal distribution in real-life data is more an exception than a normal state of affairs (Micceri, 1989), it is entirely possible that procedures are affected by skewness, leverage, balance etc.
-It is important to know how MetaForest performs in these kinds of situations.-->
-
 ### Bayesian estimation
 
-An alternative to the use of a shrinkage penalty is Bayesian estimation with a regularizing prior.
-Bayesian estimation combines information from the data with a *prior distribution*.
-The prior distribution assigns a-priori probability to different parameter values.
+<span id = "morepriors">An alternative to the use of a shrinkage penalty is Bayesian estimation with a regularizing prior.
+Whereas the aforementioned (frequentist) approaches treat every possible parameter value as equally plausible,
+Bayesian estimation combines information from the data with a *prior distribution* that assigns a-priori probability to different parameter values.
 Likely parameter values have a high probability density, and unlikely parameter values have a low probability density.
-The aforementioned (frequentist) approaches, by contrast, treat every possible parameter value as equally plausible.
 The prior distribution is updated with the likelihood of the data to form a posterior distribution,
@@
 For example, a double exponential prior (hereafter: LASSO prior) results in posterior distributions whose modes are identical to the estimates from LASSO-penalized regression [@ParkCasella2008].
-
-A limitation of the LASSO prior is that it introduces substantial bias in non-zero regression coefficients.
+There are some notable differences between the frequentist LASSO penalty and its Bayesian counterpart, the LASSO prior.
+First, the frequentist LASSO penalty has a tuning parameter $\lambda$, whose value is usually chosen via cross-validation.
+In the Bayesian approach, an analogous role is fulfilled by a hyperparameter of the shrinkage prior.
+Instead of using cross-validation, the value of this hyperparameter can be estimated from the data.
+
+<span id = "horseshoe">One limitation of the LASSO prior is that it biases all regression coefficients towards zero - for relevant as well as irrelevant moderators.
 To overcome this limitation, regularizing priors with better shrinkage properties have been developed.
@@
 which means that it does not shrink (and therefore bias) substantial coefficients as much.
-
-The BRMA method introduced here offers both LASSO and horseshoe priors.
+One remaining limitation of the horseshoe prior is that it is difficult to specify a prior that ensures a sufficiently sparse solution.
+The regularizing horseshoe was introduced to overcome this limitation;
+it uses information about the expected number of parameters to determine an appropriate shrinkage prior  [@PiironenVehtari2017b].</span></span>
+
+The BRMA method introduced here offers both LASSO and regularizing horseshoe priors.
 The LASSO prior is given by:
@@
 
-The regularizing horseshoe prior was proposed by @PiironenVehtari2017b and is given by:
+The regularizing horseshoe prior [@PiironenVehtari2017b] is given by:
 $$
@@
 In the present study, we assume a default value of $\lambda^2_0 = 1$.
-However, if prior information regarding the expected number of relevant moderators is available,
-it is best to include this information.
-This is accomplished by setting $\lambda^2_0 = \frac{p_0}{p-p_0}{\frac{\sigma}{\sqrt{n}}}$, where $p_0$ represents the expected number of relevant moderators, $p$ the total number of moderators, $\sigma$ is the residual standard deviation and $n$ equals the number of observations.
+
+<span id = "expectedmods">An attractive property of this shrinkage prior is that it can incorporate prior information regarding the expected number of relevant moderators.
+This is accomplished by having the scale of the global shrinkage parameter $\lambda^2_0$ depend on the expected number of relevant moderators $p_0$.
+The shrinkage parameter is then given by $\lambda^2_0 = \frac{p_0}{p-p_0}{\frac{\sigma}{\sqrt{n}}}$, where $p$ represents the total number of moderators, $\sigma$ is the residual standard deviation and $n$ equals the number of observations.</span>
 <!-- SvE: nu twijfel ik toch weer of dit helemaal goed gaat.
@@
 However, in cases where the model is weakly identified, for example when there are more moderators than observations, these lighter tails can aid model convergence. 
-The regularizing horseshoe differs from the standard horseshoe in the specification of a finite "slab".
+<span id = "thisextension">The regularizing horseshoe differs from the standard horseshoe by the addition of a finite "slab", which is governed by a degrees of freedom parameter ($\nu_3$, set to 4) and a scale parameter ($s$, set to 1).
 This slab ensures at least some regularization of large coefficients and as a consequence,
-more stable results.
-This slab is governed by a degrees of freedom parameter ($\nu_3$, set to 4) and a scale parameter ($s$, set to 1).
-This extension ensures greater numerical stability of the results.
-
-The default settings discussed above are reasonable in most applications.
-However, it is good practice to perform sensitivity analysis to determine how sensitive the model results are to different prior specifications. 
-This is particularly important when the sample is small, as the prior is more influential in this case.
+results in greater numerical stability of the model parameters.</span>
 
@@
 there is a within-study and between-studies variance.
-
 A crucial challenge with heterogeneity parameters in meta-regression is that the number of observations at the within- and between-study level is often small.
@@
 A well-known advantage of Bayesian meta-analysis is that it can overcome these challenges by using weakly informative priors, which guide the estimator towards plausible values for the heterogeneity parameters.
-There is less consensus, however, about which priors are best for this purpose [@roverWeaklyInformativePrior2021].
-By default, `brma()` uses a prior that was specifically developed for multilevel heterogeneity parameters
+There is less consensus, however, about which priors are most suitable for this purpose [@roverWeaklyInformativePrior2021].
+BRMA uses a prior specifically developed for multilevel heterogeneity parameters
 [@gelmanPriorDistributionsVariance2006]:
 the half-Student's t distribution with large variance, $df = 3, scale = 2.5$.
-Note that other suitable weakly informative priors have been discussed in the literature, but have not (yet) been implemented in `brma()`, such as the Wishart prior [@chungWeaklyInformativePrior2015], but has not been implemented in `brma()`.
-There has also been increasing interest in the use of informative priors for heterogeneity parameters when information about their values is available [@thompsonGroupspecificPriorDistribution2020].
-The use of informative priors is out of scope for BRMA, however, as BRMA takes a pragmatic approach to Bayesian analysis, using weakly informative priors to aid convergence for heterogeneity parameters,
+Note that other relevant weakly informative priors have been discussed in the literature,
+such as the Wishart prior [@chungWeaklyInformativePrior2015].
+There has also been increasing interest in the use of informative priors for heterogeneity parameters,
+which incorporate substantive knowledge about plausible parameter values [@thompsonGroupspecificPriorDistribution2020].
+Informative priors exert substantial influence on the parameter estimates.
+They thus differ from weakly informative priors,
+which merely guide the estimator towards possible values (e.g., by excluding negative values for the variance),
+or restrict it to plausible values to aid model convergence.
+BRMA takes a pragmatic approach to Bayesian analysis,
+using weakly informative priors to aid convergence for heterogeneity parameters,
 and regularizing priors to perform variable selection for regression coefficients.
+The use of informative priors is out of scope for BRMA.
 If researchers do wish to construct alternative prior specifications, they may want to develop a custom model in `rstan` instead [@rstan].
@@
 
-Unlike the frequentist LASSO algorithm, Bayesian regularized estimation does not shrink coefficients to be exactly equal to zero.
-Therefore, variables must be selected post-estimation.
-One way to do so is by the use of probability intervals, the Bayesian counterpart of confidence intervals, with a moderator being selected if, for example, a 95% interval excludes zero.
-The present study considers two types of intervals:
-The credible interval, which is obtained by taking the 2.5% and 97.5% quantiles of the posterior distribution, and the highest posterior density interval,
-which is the narrowest possible interval that contains 95% of the probability mass.
+<span id = "intervals">The frequentist LASSO algorithm shrinks coefficients to be exactly equal to zero, and thus inherently performs variable selection.
+Other approaches to regularization - frequentist or Bayesian - lack this property.
+However, an advantage of the Bayesian approach is that its posterior distributions lend itself to exact inference.
+One can use probability intervals to determine which population effects are likely non-zero;
+for example, by selecting moderators whose 95% interval excludes zero.
+Two commonly used Bayesian probability intervals are the credible interval and the highest posterior density interval [@mcelreathStatisticalRethinkingBayesian2020].
+The credible interval (CI) is the Bayesian counterpart of a confidence interval,
+and it is obtained by taking the 2.5% and 97.5% quantiles of the posterior distribution.
+The highest posterior density interval (HDPI) is the narrowest possible interval that contains 95% of the probability mass [@kruschkeChapter12Bayesian2015].
+When the posterior distribution is symmetrical,
+the CI and HDPI are the same.
+However, when the posterior is skewed,
+the HPDI has the advantage that all parameter values within the interval have a higher posterior probability density than values outside the interval.
+This suggests that the HPDI might be superior for performing inference on residual heterogeneity parameters, which have a skewed posterior distribution by definition.
+For inference on regression coefficients, the choice of interval is likely less crucial.</span>
 
@@
 in which the mean of all predictors is set to 0 and their standard deviation is set to 1 [@gelman2008scaling].
-This type of standardization is also used by default in BRMA.
+BRMA performs standardization by default.
 
@@
 If predictors are already on equivalent scales,
-standardization does not make scales more equal, nor the penalization more fair
+standardization does not make scales more equal, nor the penalization more fair.
 <!--Alternatively, if the goal of a study is to compare results to prior findings based on unstandardized predictors, standardization would make penalization unequal across studies.-->
@@
 
-The standard linear model estimates an intercept, which reflects the expected value of the outcome when all predictors are equal to zero, and regression coefficients for the effect of moderators.
-In some cases, it may be desirable to omit the intercept.
-For example, if an analysis contains categorical predictors,
-these can be encoded as dummy variables, with values $x \in \{0, 1\}$.
-For a variable with $c$ categories, the number of dummy variables must be equal to $c-1$;
-the omitted category functions as a reference category, and its expected value is represented by the model intercept $b_0$.
-This so-called *regression specification* of a model may be useful when there is a meaningful reference category.
+<span id = "intercept">The general linear model used in BRMA typically includes an intercept,
+which reflects the expected value of the outcome when all predictors are equal to zero, and regression coefficients for the effect of moderators.
+If the analysis contains categorical predictors, it may be desirable to omit this intercept.
+To understand why, first consider the model with an intercept.
+Standard practice is to encode category membership with dummy variables, with values $x \in \{0, 1\}$.
+For a variable with $c$ categories, the number of dummy variables is equal to $c-1$.
+The omitted category functions as a reference category, and its expected value is represented by the model intercept $b_0$.
+The regression coefficients of the dummy variables, $b_{1\ldots c}$, indicate the difference between the expected values of the reference category and of the category represented by the dummy.
+This so-called *regression specification* is useful when there is a meaningful reference category.
 For example, imagine a study on the effectiveness of interventions for specific phobia with two interventions: Treatment as usual, and a novel intervention.
-In this case, it might make sense to code treatment as usual as the reference category,
+In this case, it makes sense to code treatment as usual as the reference category,
 and dummy-code the new contender.
-The model will then estimate whether the newly developed intervention has an effect size significantly lower or higher than the industry standard.
+The intercept $b_0$ then represents the effect size of treatment as usual,
+and the effect of the dummy $b_1$ indicates whether the newly developed intervention has a significantly different effect size from treatment as usual.
 In other cases, there may not be a straightforward reference category.
 For example, imagine a study on the effectiveness of one intervention for specific phobia in two continents.
-In such cases, the average effect in both continents may be estimated by omitting the intercept, and including all $c$ dummy variables.
+In this case, it makes more sense to estimate the average effect in both continents - in other words, to conduct a multi-group analysis.
+This is achieved by removing the intercept, and including all $c$ dummy variables.
 This so-called *ANOVA specification* of a model estimates a mean for all dummy-coded categories.
-
-<!-- This part seems a repetition from the info on standardization of dummies above?: 
-The appropriate standardization of dummy variables in penalized regression analyses is a topic of ongoing debate.
-Suffice it to say that, for greater interpretability, users may want the freedom to leave dummy variables unstandardized.
-This is possible in `brma()` by ... 
--->
+In the context of standard linear regression, the regression specification and ANOVA specification are equivalent.
+This is not the case in regularized regression, however, because shrinkage may affect the intercept differently from the dummy variables.
+Consequently, a reasoned choice must be made about whether to include an intercept or not.</span>
 
@@
 We implemented BRMA in the function `brma()` in the statistical programming language R [@R-base],
-in the package `pema`, short for *pe*nalized *m*eta *a*nalysis.
+in the package `pema`, short for *pe*nalized *m*eta *a*nalysis [@R-pema].
 The `brma()` function aims to make Bayesian regularized regression readily available via a user-friendly interface.
 R-users can install the package from CRAN, by running `install.packages("pema")`.
-Non-R-users can use BRMA via the "Penalized Meta-Analysis" extension of JASP [@JASP2022],
-a free open source statistical software package with a graphical user interface, see Figure \@ref(fig:figjasp).
+Non-R-users can use BRMA via a graphical user interface by selecting the menu option "Penalized Meta-Analysis" in the free, open source statistical program JASP [@JASP2022], see Figure \@ref(fig:figjasp).
 
@@
 Stan is written in C++, and thus computationally efficient, but custom models must be compiled prior to estimation.
-This results in substantial computational overhead,
-and installing a toolchain to compile models requires some technical sophistication.
-To avoid this overhead, `pema` uses pre-compiled stock models with opinionated default options.
+Installing a toolchain to compile models requires some technical sophistication, which potentially restricts the user base.
+Moreover, model compilation adds unnecessary computational overhead for standard applications.
+To overcome these limitations, the `pema` package includes pre-compiled stock models with opinionated default options.
 At the time of writing, these include random effects and three-level meta-regression with and without an intercept.
@@
 Researchers who wish to construct a model that is currently out of scope of `brma()` are referred to `rstan` instead [@rstan].
-As a starting point, the `rstan` source code for the stock models included with `pema` is available in `pema:::stanmodels`.
-We welcome contributions of additional models.
+As a starting point, the `rstan` source code for the stock models included with `pema` can be accessed by running `pema:::stanmodels`.
+We welcome user contributions of additional models.
 
@@
 a formula interface, corresponding to base-R functions like `lm()`,
-in which the user provides a model `formula` that references variables in a `data` argument.
+which allows the user to specify a model `formula` that references variables in a `data` argument.
 The second interface is more amenable to machine learning applications,
@@
 As mentioned before, the R-implementation of BRMA has several options that can be customized.
-The most important option relates to the choice of priors f the regression coefficients.
-At the time of writing, `brma()` supports two priors for regression coefficients: the LASSO and the regularized horseshoe.
+The most important option relates to the choice of priors for the regression coefficients.
+At the time of writing, `brma()` supports two priors for regression coefficients: the LASSO and the regularizing horseshoe.
 A prior is selected using the `method` argument;
@@
 Parameters `df_global` and `scale_global` control global shrinkage that influences all coefficients similarly.
-The regularized horseshoe applies additional regularization to very large coefficients,
+The regularizing horseshoe applies additional regularization to very large coefficients,
 which is governed by parameters `df_slab` and `scale_slab`.
@@
 
-Another important decision is whether or not to standardize parameters.
+As explained before, standardization is an important step in Bayesian regularized meta-analysis.
 By default, `brma()` standardizes the predictor matrix,
@@
 
-The present simulation study set out to validate the BRMA algorithm.
-As a benchmark for comparison, we used restricted maximum likelihood meta-regression,
-which is the standard in the field.
+We performed a simulation study to validate the BRMA algorithm.
+As a benchmark for comparison, we used random effects meta-regression with restricted maximum likelihood estimation [RMA, @viechtbauerConductingMetaanalysesMetafor2010],
+which is the current state-of-the-art in the field.
 We evaluated the algorithms' predictive performance in new data, 
-<!-- examining its predictive performance in new data, its sensitivity and specificity in variable selection, and its bias and variance in recovering population parameters. -->
-<!-- their ability to perform variable selection, -->
-and their ability to recover population parameters. 
-Our research questions are whether BRMA offers a performance advantage over state-of-the-art random effects meta-analysis using restricted maximum likelihood [RMA, @viechtbauerConductingMetaanalysesMetafor2010] in terms of any of these indicators,
-and which prior (regularized horseshoe versus LASSO) is to be preferred.
+ability to perform variable selection,
+and ability to recover population parameters.
+Our research questions are whether BRMA offers a performance advantage over RMA in terms of any of these indicators,
+and which prior (regularizing horseshoe versus LASSO) is to be preferred.
 All analysis code is available in a version-controlled repository at <https://github.com/cjvanlissa/pema>.
@@
 
-Predictive performance reflects how well the algorithm is able to predict data not used to estimate the model parameters, in other words, it indicates the generalizability of the model.
-To compute it, for each iteration of the simulation both a training dataset and a testing dataset are generated.
-The model is estimated on the training data, which has a varying number of cases according to the simulation conditions.
-Predictive performance is then operationalized as the explained variance in the testing data, $R^2_{test}$.
-The testing data has 100 cases in all simulation conditions.
-The $R^2_{test}$ reflects the fraction of variance in the testing data explained by the model,
-relative to the mean.
-Note that the mean of the training data, not of the testing data, is used as a benchmark.
-The resulting metric $R_{test}^{2}$ is expressed by the following equation:
-
+<span id = "rsquared">Our primary performance indicator was predictive performance,
+a measure of model generalizability.
+To compute it, for each iteration of the simulation,
+both a training data set and a testing data set are generated from the same known population model.
+The number of cases in the training data vary according to the design factors of the simulation study.
+The number of cases in the testing data set was 100 for all replications.
+The models under evaluation (BRMA, RMA) are estimated on the training data,
+and used to predict cases in the testing data.
+Predictive performance was operationalized as the model's explained variance in the testing data, $R^2_{test}$, which is calculated as follows:
 $$
@@
 $$
-
-With $k$ being the number of studies in the testing dataset, $\hat{y}_{i-test}$ being the predicted effect size for study $i$, and $\bar{y}_{train}$ being the mean of the training dataset.
-
-The algorithms' ability to perform variable selection was evaluated by sensitivity and specificity.
+Where $k$ is the number of studies in the testing data set, $\hat{y}_{i-test}$ is the predicted effect size for study $i$, and $\bar{y}_{train}$ is the mean of the training data.
+The $R^2_{test}$ differs from the familiar $R^2$ metric:
+$R^2$ describes the proportion of variance a model explains in the training data, and it always increases as the model becomes more complex.
+By contrast, $R^2_{test}$ reflects the explained variance in the testing data.
+Remember that BRMA was developed to reduce the risk of overfitting meta-regression models.
+The $R^2_{test}$ is a useful metric to detect overfitting,
+which causes it to decrease, or even become negative.
+</span>
+
+The algorithm's ability to perform variable selection was evaluated by estimating sensitivity and specificity.
 Sensitivity $P$ is the ability to select true positives, or the probability that a variable is selected, $S = 1$, given that it has a non-zero population effect: $P = p(S = 1||\beta| >0)$.
@@
 
+## Missing data
+
 Any iterative algorithm is susceptible to convergence problems.
@@
 We were thus able to use all iterations of the BRMA algorithms,
-although there may be some that failed to converge, which will likely have poor performance.
-When the RMA algorithm fails to converge, however, it terminates with an error.
-To handle this contingency, we automated some of the steps recommended [on the `metafor` website](https://www.metafor-project.org/doku.php/tips:convergence_problems_rma).
-Nevertheless, `r out$missing` replications of the RMA algorithm failed to converge.
-All of these were characterized by low number of cases ($k \leq 40$) and high effect sizes $\beta \geq .5$.
-These cases were omitted from further analysis.
+although some may have failed to converge, which would negatively impact BRMA's performance.
+When the RMA algorithm fails to converge, however,
+terminates with an error.
+<!-- To handle this contingency, we automated some of the steps recommended [on the `metafor` website](https://www.metafor-project.org/doku.php/tips:convergence_problems_rma). -->
+<!-- This means that, in case of convergence  -->
+The RMA algorithm failed to converge in `r out$missing` cases.
+These cases were all characterized by low number of cases ($k \leq 40$) and high effect sizes $\beta \geq .5$.
+They were omitted from further analysis.
 
@@
 
-Within data sets, the BRMA with a horseshoe prior had the highest predictive performance `r round(whichhi[1]*100)`% of the time, followed by RMA, `r round(whichhi[3]*100)`%, and finally BRMA with a LASSO prior, `r round(whichhi[2]*100)`%.
-Results indicated that the overall $R^2_{test}$ was highest for BRMA with a horseshoe prior and lowest for RMA, see Table \@ref(tab:tabr2).
+Within data sets, the BRMA with a horseshoe prior had the highest predictive performance $R^2_{test}$ `r round(whichhi[1]*100)`% of the time, followed by RMA, `r round(whichhi[3]*100)`%, and finally BRMA with a LASSO prior, `r round(whichhi[2]*100)`%.
+Across data sets, the average $R^2_{test}$ was highest for BRMA with a horseshoe prior and lowest for RMA, see Table \@ref(tab:tabr2).
 This difference was driven in part by the fact that explained variance was somewhat higher for the BRMA models when the true effect was non-zero (i.e., in the presence of a population effect),
@@
 Evidently, predictive performance increased most for the HS algorithm when the effect size increased above zero.
-As noted previously, predictive performance of RMA was most negative (negative explained variance) when the effect size was zero.
+As previously noted, predictive performance of RMA was the most negative when the effect size was zero.
+This means that RMA's explained variance in new data was below zero, a clear indication of overfitting.
 The HS algorithm furthermore had the consistently highest predictive performance regardless of number of irrelevant moderators or number of cases in the training data, and was relatively less affected by increases in the number of irrelevant moderators (panel b) or in the number of training cases (panel c).
@@
 
-To determine the extent to which the algorithms could perform variable selection correctly, the sensitivity to true positives $P$ and specificity to true negatives $N$ were calculated.
-Only simulation conditions with $\beta > 0$ were used, such that the effect of the first moderator was always positive in the population and could be used to calculate $P$,
-and the effect of the second moderator was always zero in the population and could be used to calculate $N$.
-Additionally, overall accuracy can be computed, which reflects the trade off between sensitivity and specificity.
-As the base rate of true positives and true negatives is equal in this simulation, overall accuracy is simply given by $Acc = (P+N)/2$.
-
-As the regularized algorithms shrink all coefficients towards zero, it is unsurprising that sensitivity was highest for the un-regularized algorithm RMA, followed by HS and LASSO, `r truepos`.
-By contrast, specificity was higher for the regularized algorithms, `r trueneg`.
+To determine the extent to which the algorithms could perform variable selection correctly,
+we calculated sensitivity $P$,
+the ability to detect a true population effect,
+and specificity $N$,
+the ability to correctly estimate a null-effect at zero.
+We used all simulation conditions with $\beta > 0$,
+such that the population effect of the first moderator was always positive and that of the second moderator was always zero,
+and calculated $P$ from the effect of the first moderator,
+and $N$ from the effect of the second moderator.
+Finally, we computed overall accuracy as $Acc = (P+N)/2$,
+which reflects the trade off between sensitivity and specificity.
+
+As the regularizing algorithms shrink all coefficients towards zero,
+it is unsurprising that sensitivity was highest for RMA,
+followed by HS and LASSO, `r truepos`.
+By contrast, specificity was higher for the regularizing algorithms, `r trueneg`.
 Overall accuracy was approximately equal for RMA and HS, and was lower for LASSO, `r proboveral`.
@@
 We also computed this effect size for the difference between algorithms in the number of true positives by design factor.
-```{r tabcramerp, results= "asis", eval = TRUE}
-tabselect <- readRDS("selected.RData")
-rownames(tabselect) <- NULL
-names(tabselect) <- gsub("(?<!vs)\\.", " ", names(tabselect), perl = TRUE)
-apa_table(tabselect, caption = "Effect size (Cramer's V) of design factors, and of the difference between algorithms, on sensitivity (P).", digits = 2, escape = FALSE)#, longtable = TRUE)
-# Interpretation for main effects indicates whether the effect was uniformly positive or negative or other, and for interactions, whether it is a spreading or crossover interaction.
-```
-```{r figsensitivity, fig.cap="Sensitivity by design factors for the HS (circle, solid line), LASSO(triangle, dotted line) and RMA (square, dashed line) algorithms."}
-knitr::include_graphics("sensitivity.png")
-```
-```{r tabcramern, results= "asis", eval = TRUE}
-tabselectn <- readRDS("notselected.RData")
-rownames(tabselectn) <- NULL
-names(tabselectn) = gsub("(?<!vs)\\.", " ", names(tabselectn), perl = TRUE)
-apa_table(tabselectn, caption = "Effect size (Cramer's V) of design factors, and of the difference between algorithms, on specificity (N).", digits = 2, escape = FALSE)#, longtable = TRUE)
-```
-```{r figspecificity, fig.cap="Specificity by design factors for the HS (circle, solid line), LASSO(triangle, dotted line) and RMA (square, dashed line) algorithms."}
-knitr::include_graphics("specificity.png")
-```
 Differences in sensitivity between the algorithms were near-zero for HS and LASSO.
@@
 Across all design factors, RMA had the highest sensitivity, followed by HS and then LASSO.
-
 For specificity, differences in sensitivity between HS and LASSO were largest for the number of noise moderators $M$, followed by the effect size $\beta$, number of studies $k$, and residual heterogeneity $\tau^2$.
@@
 Conversely, a greater number of noise moderators $M$ had a positive effect on specificity for BRMA, but a negative effect for RMA.
+```{r tabcramerp, results= "asis", eval = TRUE}
+tabselect <- readRDS("selected.RData")
+rownames(tabselect) <- NULL
+names(tabselect) <- gsub("(?<!vs)\\.", " ", names(tabselect), perl = TRUE)
+apa_table(tabselect, caption = "Effect size (Cramer's V) of design factors, and of the difference between algorithms, on sensitivity (P).", digits = 2, escape = FALSE)#, longtable = TRUE)
+# Interpretation for main effects indicates whether the effect was uniformly positive or negative or other, and for interactions, whether it is a spreading or crossover interaction.
+```
+```{r figsensitivity, fig.cap="Sensitivity by design factors for the HS (circle, solid line), LASSO(triangle, dotted line) and RMA (square, dashed line) algorithms."}
+knitr::include_graphics("sensitivity.png")
+```
+```{r tabcramern, results= "asis", eval = TRUE}
+tabselectn <- readRDS("notselected.RData")
+rownames(tabselectn) <- NULL
+names(tabselectn) = gsub("(?<!vs)\\.", " ", names(tabselectn), perl = TRUE)
+apa_table(tabselectn, caption = "Effect size (Cramer's V) of design factors, and of the difference between algorithms, on specificity (N).", digits = 2, escape = FALSE)#, longtable = TRUE)
+```
+```{r figspecificity, fig.cap="Specificity by design factors for the HS (circle, solid line), LASSO(triangle, dotted line) and RMA (square, dashed line) algorithms."}
+knitr::include_graphics("specificity.png")
+```
 
@@
 then the bias $B$ and variance $V$ of this estimate can be computed as the mean and variance of the difference between $\hat{b}$ and $\beta$ across simulation conditions, respectively.
-Across all simulation conditions, HS had the lowest bias for $\tau^2$, $B_{HS} `r report(out[["tau2_bias"]][["hs_tau2"]])`$, 
+For the estimated regression coefficients,
+HS had the greatest (negative) bias across simulation conditions, $B_{HS} `r report(out[["beta_bias"]][["hs_beta1"]])`$, 
+followed by LASSO, $B_{LASSO} `r report(out[["beta_bias"]][["lasso_beta1"]])`$.
+Surprisingly, RMA also had negatively biased estimates, $B_{RMA} `r report(out[["beta_bias"]][["rma_beta1"]])`$.
+The effect of the design factors on the bias in estimated $\beta$ was evaluated using ANOVAs.
+Table \@ref(tab:tabbeta) reports the effect size $\eta^{2}$ of simulation conditions on $\hat{b}-\beta$.
+The skewness of moderator variables had the largest effect on bias in estimated $\beta$ for all algorithms.
+This was mainly because the algorithms overestimated $\tau^{2}$ most when the data-generating model contained cubic terms.
+Simulating data with a cubic model violates the model's assumption of linearity, which biases the estimated parameters.
+No differences between algorithms in the effect of design factors were observed.
+
+The variance of parameter estimates cannot be calculated on a case-by-case basis.
+Instead, it is calculated across replications for each simulation condition.
+Across simulation conditions, parameters estimated via HS had the lowest variance, $V_{HS} `r report(out[["beta_variance"]][["hs_beta1"]])`$, followed by LASSO, $B_{LASSO} `r report(out[["beta_variance"]][["lasso_beta1"]])`$,
+and then RMA, $B_{RMA} `r report(out[["beta_variance"]][["rma_beta1"]])`$.
+Online [Supplemental Table S1]() provides an overview of the effect size of design factors on variance of the regression coefficients.
+Notably, the differences between algorithms are very small;
+the largest effect sizes were observed for the difference between HS and RMA in the effects of effect size, sample size, and model, all with $\eta^2 < 0.01$.
+
+```{r tabbeta, results= "asis", eval = TRUE}
+tabbeta <- readRDS("table_beta.RData")
+tabbeta$Factor <- gsub("\\$(omega|beta|beta)", "\\$\\\\\\1", tabbeta$Factor)
+tabbeta <- tabbeta[, c(ncol(tabbeta), 2:(ncol(tabbeta)-1))]
+apa_table(tabbeta, caption = "Effect size of design factors on bias in beta squared for the different algorithms, and of the difference between algorithms.", digits = 2, escape = FALSE, col.names = gsub("(?<!vs)\\.", " ", names(tabbeta), perl = TRUE))
+```
+
+Across all simulation conditions, HS had the lowest bias for the residual heterogeneity $\tau^2$,
+$B_{HS} `r report(out[["tau2_bias"]][["hs_tau2"]])`$,
 followed by RMA, $B_{RMA} `r report(out[["tau2_bias"]][["rma_tau2"]])`$,
 and then LASSO, $B_{LASSO} `r report(out[["tau2_bias"]][["lasso_tau2"]])`$.
-Note that all algorithms yielded positively biased estimates. 
-The LASSO estimates of $\tau^2$ had the lowest variance, $V_{LASSO} `r report(out[["tau2_variance"]][["lasso_tau2"]])`$, 
-followed by HS, $V_{HS} `r report(out[["tau2_variance"]][["hs_tau2"]])`$,
-and then RMA, $B_{RMA} `r report(out[["tau2_variance"]][["rma_tau2"]])`$.
-The effect of the design factors on the bias in $\tau^2$ was evaluated using ANOVAs.
+Note that all algorithms yielded positively biased estimates. The effect of the design factors on the bias in $\tau^2$ was evaluated using ANOVAs.
 Table \@ref(tab:tabtau2) reports the effect size $\eta^{2}$ of simulation conditions on $\hat{t^2}-\tau^2$.
@@
 
-For the estimated regression coefficient, HS had the greatest (negative) bias across simulation conditions, $B_{HS} `r report(out[["beta_bias"]][["hs_beta1"]])`$, 
-followed by LASSO, $B_{LASSO} `r report(out[["beta_bias"]][["lasso_beta1"]])`$,
-and then RMA, $B_{RMA} `r report(out[["beta_bias"]][["rma_beta1"]])`$.
-Note that all algorithms - including RMA - provided, on average, negatively biased estimates. 
-Across simulation conditions, HS had the lowest variance, $V_{HS} `r report(out[["beta_variance"]][["hs_beta1"]])`$, followed by LASSO, $B_{LASSO} `r report(out[["beta_variance"]][["lasso_beta1"]])`$,
-and then RMA, $B_{RMA} `r report(out[["beta_variance"]][["rma_beta1"]])`$.
-The effect of the design factors on the bias in estimated $\beta$ was evaluated using ANOVAs.
-Table \@ref(tab:tabbeta) reports the effect size $\eta^{2}$ of simulation conditions on $\hat{b}-\beta$.
-The skewness of moderator variables had the largest effect on bias in estimated $\beta$ for all algorithms.
-Note, however, that this is likely due to the fact that the data simulated with a cubic model are analyzed with a linear model, and thus,  
-was the estimated model.
-This was mainly because the algorithms overestimated $\tau^{2}$ most when the model contained cubic terms.
-No differences between algorithms in the effect of design factors were observed.
-
-```{r tabbeta, results= "asis", eval = TRUE}
-tabbeta <- readRDS("table_beta.RData")
-tabbeta$Factor <- gsub("\\$(omega|beta|beta)", "\\$\\\\\\1", tabbeta$Factor)
-tabbeta <- tabbeta[, c(ncol(tabbeta), 2:(ncol(tabbeta)-1))]
-apa_table(tabbeta, caption = "Effect size of design factors on bias in beta squared for the different algorithms, and of the difference between algorithms.", digits = 2, escape = FALSE, col.names = gsub("(?<!vs)\\.", " ", names(tabbeta), perl = TRUE))
-```
+The variance of the residual heterogeneity was calculated across replications for each simulation condition.
+The LASSO estimates of $\tau^2$ had the lowest variance, $V_{LASSO} `r report(out[["tau2_variance"]][["lasso_tau2"]])`$, 
+followed by HS, $V_{HS} `r report(out[["tau2_variance"]][["hs_tau2"]])`$,
+and then RMA, $B_{RMA} `r report(out[["tau2_variance"]][["rma_tau2"]])`$.
+Online [Supplemental Table S2]() provides an overview of the effect size of design factors on variance of the residual heterogeneity.
+All differences between algorithms were small, $\eta^2 \leq 0.002$.
 
@@
 
-In this application, we will work with the `pema::bonapersona` data [@BonapersonaEtal2019].
+In this application, we will work with the `bonapersona` data [@BonapersonaEtal2019].
 This meta-analysis of over 400 experiments investigated the effects of early life adversity on cognitive performance in rodents.
@@
 See the `pema` package documentation (help and vignettes) for further examples.
-<!-- We focus specifically on how to choose the different hyperparameters of the regularized horseshoe prior. -->
+<!-- We focus specifically on how to choose the different hyperparameters of the regularizing horseshoe prior. -->
 
@@
 Increasing the degrees of freedom (`df_global` and `df_slab`) results in thinner tails, which applies more regularization.
-<!-- One advantage of the regularized horseshoe prior is its ability to define the prior in terms of the expected number of nonzero coefficients, using the argument `relevant_pars`. -->
+<!-- One advantage of the regularizing horseshoe prior is its ability to define the prior in terms of the expected number of nonzero coefficients, using the argument `relevant_pars`. -->
 <!-- This argument in turn influences the other hyperparameters. -->
@@
 with the different MCMC chains mixing together.
-<!-- Note that there are many auxiliary parameters used for the regularized horseshoe prior.
+<!-- Note that there are many auxiliary parameters used for the regularizing horseshoe prior.
 No information on these parameters is returned in the `brma` fitobject, however, once the fitobject is transformed into a Stan object for plotting, these parameters are included.
@@
 non-parametric methods like random forest meta-analysis may be preferable over linear models [@vanlissaSmallSampleMetaanalyses2020].
+
+<span id = "sensitivityanalysis">All simulations were conducted with default settings for the model's prior distributions.
+Our results suggest that these defaults are suitable for a wide range of situations, including when model assumptions are violated.
+However, bear in mind that model parameters are influenced by the prior distribution.
+It is good practice to perform sensitivity analysis to determine how sensitive the model results and inferences are to different prior specifications. 
+Performing sensitivity analyses is particularly important when the sample is small,
+as in this case, the prior is more influential.</span>
 
@@
 Thirdly, there may be pragmatic reasons for preferring BRMA over RMA.
-For example, if a dataset is small, or the number of moderators is high relative to the number of cases,
+For example, if a data set is small, or the number of moderators is high relative to the number of cases,
 RMA models may be empirically under-identified.

### 2022-11-23 paper/sara-responses.rmd
add supplemental tables

---
  title: Pema - Comments revision 1
created: 2022-10-24 09:30
tags: Pema
---

  Associate Editor Comments to Author:

  Associate Editor  
Comments to the Author:  
  The authors introduce their implementation of a regularisation approach for estimation and variable selection in meta-regression, which seems a timely contribution given the danger of overfitting. Some more detail or elaboration would be helpful in some places.  
I am sorry the review took quite a while.  
Besides the two reviewers' comments I only have a few points to add:

- please consider whether the title is appropriate, or whether (something like) "Selecting..." or "Selection of..." might be better.

  Thank you for this suggestion. We have now changed the title to: "Selecting relevant moderators using Bayesian regularized meta-regression"

- in abstract and Introduction, please consider being more concrete here: it might be good to mention here already that this is about penalisation/LASSO/horseshoe priors in order to give the reader a better idea.

  We have added the following two sentences to the abstract to make it more concrete:
  "BRMA relies on the use of Bayesian 
  shrinkage priors to pull coefficients towards zero thereby avoiding overfitting." and
  "The algorithm has been implemented in the R-package 
  `pema`  (which stands for penalized meta-analysis) with the lasso and horseshoe priors."

- on p.16 (Section "design factors"):  
what were the total numbers of variables (or "noise moderators")?

- regarding the 3rd comment by Reviewer 1: in the context of variable selection, the so-called "penalized complexity priors" (here: exponential priors for the heterogeneity standard deviation) might play a role.

Reviewers' Comments to Author:

  Reviewer: 1

Comments to the Author  
The manuscript provides an interesting approach based on regularization to selection of covariates in meta-regression, when the number of covariates is relevant. The Authors focus on a Bayesian strategy.  
Although I found the topic interesting, the study needs some additional investigations and the text needs to be substantially modified in order to provide a clear and exhaustive picture of the proposal.  
My comments and questions are listed below.

1) The introduction is too long in terms of explanation of the meta-regression and selection of covariates problems, with many repetitions. For example, end of page 4 and beginning of page 5 include many repetitions about between-study heterogeneity. Other parts, instead, require a substantially deeper explanation.   
* Which theories useful for variable selection do you refer to in page 5 ? The description is extremely vague.   
* The topic of the study is variable selection from a Bayesian point of view: but the description is so short. Just a few lines about the novelty of the paper in page 6, with no clear description of the proposal and with the reference to pema package without even the explanation of the name of the package.

We have added the following sentence to clarify the idea behind the Bayesian approach:
  "By specifying a particular type of prior with a peak at zero (a so-called shrinkage prior), regression coefficients for the moderators are pulled towards zero resulting in a penalized solution. We have implemented two popular shrinkage priors, the lasso and horseshoe priors in the function `brma()` in the R-package `pema` (which stands for penalized meta-analysis)."
We have not included more information in this section to avoid repetition with the "Statistical underpinnings" section.

2) Statistical underpinnings  
* Again, I found a lot of repetitions in the text.  
* Probably, in (1) you mean \theta and not \Theta? As you have \theta int the text. Why do you use theta and not beta, as you do for the meta-regression model in (7)? The notation would be simplified and would be more consistent.  
* The sentence in lines 132-133 is not clear.

3) Meta-regression.  
* line 147: probably the explanation of the error term should be anticipated where the error term appears for the first time.  
* line 152: “to estimate this model “ has a preferable statistical sound than “to solve this model”  
* lines 163- 166 describe some features of regularization….but regularization is introduced later, from line 167.

4) Regularized regression + Bayesian estimation  
I found both the sections very short and lacking of many details.   
* what about the existing literature using lasso for meta-regression?

  Ik weet zo niet naar welke literatuur wordt gerefereerd. Heb wel twee theses gevonden na een snelle search: https://www.proquest.com/openview/8a4d0bcf42eb7cdbf622135d4093bfb9/1?pq-origsite=gscholar&cbl=18750; https://studenttheses.uu.nl/handle/20.500.12932/36196. En er is zoiets als een meta-lasso: https://onlinelibrary.wiley.com/doi/abs/10.1111/biom.12213?casa_token=zY5wxOkhXtcAAAAA:uCyxxTtb4S9mlHlfnVEkcJl_UFtFePOnInB3aG_GwdUZouUm9717rteq_ar1-8sW_mAQ3ruJsndIYX4

* In addition, I expected some references about the theory of LASSO given the relevance of the instrument in the literature.

We agree and have included the original LASSO reference (Tibshirani, 1996) when first discussing the LASSO penalty.

Caspar: vanaf hier heb ik niks meer aangepast in het manuscript zelf, maar ik doe wel voorstellen voor zinnen die eventueel zo kunnen worden overgenomen.

* line 183-184: “other penalties exist”: ok, so discuss about, indicate advantages and disadvantages of the other solutions; why do you not focus on them in the study? If you do not, just explain why.

"Note that the LASSO penalty is but one example of a shrinkage penalty; other penalties exist such as the ridge (Hoerl & Kennard, 1970) and elastic net (Zou & Hastie, 2005). In this study, however, we focus on the LASSO penalty due to its popularity in both the classical and Bayesian penalization literature."

* Bayesian estimation: I think that some additional methodological details and additional explanations about priors and their comparison to the classical LASSO would help the reader.

In the suggested new text below, I have also changed "regularizing prior" to "shrinkage prior" to be consistent with the literature. If you are ok with this change, we should change this throughout the manuscript. Also, the text below now has a small overlap with the implementation section (the part about selecting moderators.) I would still include more details on the selection in the implementation part as well, but perhaps shorten that a bit if this text is used earlier.

"One alternative to the use of a penalty is Bayesian estimation with a shrinkage prior.
Whereas classical, frequentist estimation relies solely on the data at hand,
Bayesian estimation combines information from the data with a *prior distribution*.
The prior distribution is a probability distribution that reflects expectations about likely parameter values.
This prior is updated with the likelihood of the data to form a posterior distribution,
which reflects expectations about likely parameter values after having seen the data.

A shrinkage prior distribution reflects the expectation that not all regression coefficients are substantial enough to be included in the model.
There are many different shrinkage prior distributions [@vanErpOberskiMulder2019].
Some of these can result in exactly the same solutions as frequentist penalized methods.
For example, applying independent double exponential (i.e., Laplace) priors to regression coefficients results in posterior modes that are equal to the classical LASSO estimates [@ParkCasella2008]. However, there are some notable differences between the classical LASSO penalty and its Bayesian implementation through a double exponential shrinkage prior. First of all, whereas the tuning parameter $\lambda$ in the classical framework is usually determined using cross-validation, a similar parameter is present in the Bayesian framework as a hyperparameter of the shrinkage prior. Instead of using cross-validation, a hyperprior can be specified for this parameter which will then be estimated simultaneously with the model based on the data. Second, whereas the classical LASSO can set small estimated coefficients to zero, thereby performing automatic variable selection, the Bayesian implementation results in a full posterior distribution. The advantage of this posterior distribution is that it results in uncertainty estimates in the form of the posterior standard deviation. The disadvantage of this posterior distribution is that its usual summary statistics, the posterior mean and median, do not automatically set small coefficients to zero and thus a post-hoc selection mechanism is needed, for example using the credible intervals (i.e., the Bayesian equivalent of the confidence interval). Third, classical penalized regression approaches rely on optimization while the Bayesian framework generally relies on Markov Chain Monte Carlo (MCMC) sampling to obtain the posterior distribution. As a result, Bayesian estimation tends to be slower compared to classical estimation.

In addition to shrinkage priors that have equivalent penalties in the classical framework, other prior distributions have been developed specifically for the purpose of providing good shrinkage properties,
meaning that the prior pulls small regression coefficients towards zero,
while leaving larger regression coefficients mostly unaffected. 
A popular prior in this regard is the horseshoe prior [@CarvalhoPolsonScott2010].
It has heavier tails than the LASSO prior,
which means that it does not shrink (and therefore bias) substantial coefficients as much.""

* Why details relevant for the Bayesian estimation are included in the “Implementation” section? I mean lasso prior and horseshoe prior, that is, details useful to understand the methodology.

Het alternatief zou zijn om de prior equations naar de estimation sectie te verplaatsen, maar het nadeel daarvan is dat je dan pas bij implementatie verwijst naar de hyperparameters. Dit lijkt me niet wenselijk. Of we moeten de implementatie sectie in zijn geheel opnemen in de estimation sectie. Daar kan ik wel mee leven.

* Can you comment about the choice of the numerical values in the priors at the end of page 11?

  As mentioned in the text (lines ...), we have chosen these default settings such that they are reasonable in most applications. However, we also recommend the user to perform a prior sensitivity analysis to compare the effect of different hyperparameters on the results.

* line 221: “this extension”: which one?

  Change to: "The regularized horseshoe is an extension of the horseshoe that is..."

* line 225: “This is accomplished by..” Why?

  By having the scale of the global shrinkage parameter $\lambda^2_0$ depend on the prior guess of the number of relevant moderators $p_0$, we include prior information.

* line 240: “values are reasonable in most applications” Why? Can you prove this?

  These choices are based on our own experience. In addition, we have noticed that in general the choices for the hyperparameters do not influence the results substantially. However, because we cannot prove this for all situations, we recommend the user to perform a prior sensitivity analysis.

* lines 244-251 seems to be pertinent to the methodology of the proposal not to implementation.

  This is now included in the estimation (see text above).

More in general, I do not like to see a mixture of methodology and R code. I think I would be more useful for  the reader to have sections describing the proposed approach and the underlying methodology (something that is not present at the emano) and then having an appendix about the code.

Ik ben het hier niet mee eens en denk dat het voor de lezer juist fijner is om direct de methode aan de code te kunnen koppelen, maar als jij het liever splitst Caspar kan ik daar ook mee leven. Wel denk ik dat het onderscheid "Bayesian estimation" en "implementation" duidelijker kan, zoals de reviewer hierboven ook aangeeft. Ik denk dat de toevoeging aan estimation zoals hierboven daar al bij helpt.

* line 278: “x==0” could be substituted by “x is equal to 0” as this is a text, not a source code.

Mee eens.

5) Intercept.  
I don’t think it is so relevant to deserve a section. Why not inserting a line in the section devoted to the code?

Deze sectie is inderdaad wel redelijk uitgebreid. Zit er eigenlijk een woordenlimiet aan het paper?

6) Performance indicators, Design factors, Predictive performance  
* You split the data in training set and test set, for each iteration. So, how do you account for the variability associated to the choice of the test set (as done for example in cross-validation)?

  Dit doen we niet, denk ik? Maar: dit is ook niet haalbaar in een simulatie. Om bv. 10-fold cross-validation toe te passen duurt iedere replicatie zoveel langer gegeven de hele MCMC procedure. Maar ik denk dat dit niet uitmaakt omdat we enkel de methoden relatief t.o.v. elkaar willen vergelijken en we gebruiken overal slechts 1 test set. Als de reviewer dit echt een probleem vind, kunnen we altijd in een volgende ronde 1 conditie bekijken waarin we wel cross-validatie toepassen.

* I’m surprised by the large number fo linea devoted to the explanation of such a basic indicator like R2. In addition, it is well known to be optimistic, and thus the adjusted version I usually preferable. Why don’t you evaluate the method using other indicators, such as the adjusted r2, AIC, or BIC?

Hier hetzelfde punt als hierboven: we willen enkel de methoden met elkaar vergelijken dus als we een optimistische maat overal gebruiken, lijkt me dat niet zo'n probleem. Eli en ik hebben ook even gekeken naar de formule voor de adjusted R2, die verschilt enkel van R2 door n en p, dus we zouden die nog post-hoc kunnen berekenen maar dan zou je geen andere resultaten verwachten. Alhoewel ik me nu wel een beetje afvraag of p dan het totale aantal predictoren is of na selectie, want in het laatste geval maakt het natuurlijk wel uit. Maar in dat geval lijkt de adjusted r-squared voor de Bayesiaanse methoden ook weer heel afhankelijk van de manier van selecteren wat een afzonderlijke 2e stap is en dus niet inherent aan de Bayesian lasso of horseshoe zelf.

* line 344: I suppose you mean the estimate of sensitivity and specificity.  
* line 368: 100 datasets only? Probably, there is a typo, as 100 is the number of datasets included in the test set, if I’m not wrong. In any case, 100 is a very low number of replicates for a simulation study, I suggest to increase at least to the common value equal to 1,000.

  Niet haalbaar met Bayesiaanse simulaties. Of nou ja: wel haalbaar, maar praktisch erg onhandig. Misschien hier het totaal aantal replicaties noemen met een indicatie over hoe lang het zou duren? Eventueel zouden we nog kunnen overwegen om 1 conditie met 1000 replicaties te doen om te zien of de resultaten robuust zijn.

* line 385: do you mean “Table” 1?  
* line 405: “the” most negative?

7) Ability to recover….  
* lines 449-452 are not necessary as bias and variance are known concepts. However, in Tables I can see only bias, and not information about variance.  
*lines 469-470: there is a white space

8) Example  
* Could you please avoid writing pema::bonapersona and use instead dataset titled bonapersona in the R pema package? This is not a list of lines code, but a text.  
* you have 440 experiments in the dataset: do you mean 440 study included in the meta-regression? If so, the number is much. Larger than the scenarios evaluated in the simulations.

  Het waren > 200 publicaties met daarin > 400 studies.

Finally, There are many typos and inconsistencies throughout the text (e.g., data set and dataset, random effect and randoms-effects, …).

Laten we voor het herindienen allemaal het manuscript nog even uitgebreid checken. Caspar, als jij een timeline kunt geven dan plan ik hier alvast wat tijd voor in (ik ga een erg drukke periode in namelijk).

Reviewer: 2

Comments to the Author  
The authors investigated selection of moderators for the meta-regression, which is especially useful to explain the sources of heterogeneity between trials. They proposed the use of regularizing priors for meta-regression within a Bayesian framework. They shared publicly available R package "pema" which relies on rstan, which helps practitioners to use the proposed methods. I think the contribution of the paper and R package is important. However, I have some comments.

### Major points

1) I think it is important to note some limitations of meta-regression. For example, the use of moderators might "break" the randomization, when the studies analyzed are randomized controlled trials. This is because it is not possible to randomize patients to one moderator, see Thompson and Higgins (2002) section 3 for further discussion of limitations of meta-regression of clinical trials.

   Ik weet hier weinig vanaf, maar lijkt me goed om toe te voegen als dit inderdaad zo is.

2) Important references are missing, in which the use of regularization or penalization approaches for the meta-analysis were investigated, although not the same purpose as in the current paper. For example, in Chung et al (2013) regularizing prior was used for the heterogeneity parameter to avoid boundary estimates, and in Günhan et al (2020) regularizing priors were used for the heterogeneity parameter and treatment effect parameter to deal with data sparsity. Finally and most importantly, Röver et al (2021) reviewed different use of regularizing priors and provided some guidance. Note that in the mentioned references, the term of weakly informative priors are used instead of regularizing priors (also see an earlier reference by Gelman (2006) in a hierarchical model context). Mention of these publications and relationship to the present paper can help the reader.

Thank you for pointing out these relevant references. We have included the reference to Chung et al. (2013), Gelman (2006) and Rover et al. (2021) in the new section on the prior for $\tau$ (see the next comment). In addition we have added the following section on page ... to be more explicit about the terminology of different types of priors:

Suggest to add this paragraph in the section on Bayesian estimation after "which reflects expectations about likely parameter values after having seen the data." Note: if included, this should be updated in the text from a previous comment to reviewer 1 as well. Also here it is relevant whether we use "regularizing" or "shrinkage" priors and should mention the definite choice explicitly.

"As a result, the posterior distribution is a compromise between the likelihood of the data and the prior distribution. The influence of either the data or the prior is determined by the sample size as well as the informativeness of the prior distribution. The larger the sample size, the more influential the likelihood of the data will be. Similarly, as the prior distribution becomes more informative, i.e., more peaked, it will exert more influence on the results. Priors can thus be placed on a continuum from "non-informative" to "highly informative". Weakly informative or regularizing priors are often used in situations when there is some prior information available, for example regarding the boundaries of the parameter space or, as is the case here, regarding the existence of parameters equal to zero. Throughout this manuscript, we will use the term "shrinkage prior" to refer to the weakly informative or regularizing prior that holds the prior knowledge that some coefficients are equal to zero and should therefore be shrunken towards zero."

3) An important part of Bayesian random-effects meta-analysis is the specification of the prior for the heterogeneity parameter tau. Can you include more specifications on the prior choice for tau and influence of the choice to the results (if there is any).

The specification of the prior for the heterogeneity parameter tau is indeed important. Since this standard deviation is at the higher (study) level, there is less information available in the data to inform the posterior meaning that the prior will have a greater influence. It is well known that careless specification of this prior can influence the results unwarrantedly. We have included this important point on page ... as follows:

Suggest to include the text below in the implementation section:

"In addition to the prior on the regression coefficients, the Bayesian analysis requires the specification of a prior on the between study heterogeneity parameter $\tau$. `brma()` uses a half-student's t distribution with 3 degrees of freedom and a scale equal to 2.5 for $\tau$. This is the default prior used in the `brms` package and is considered a general, robust default prior for higher level variances (Gelman, 2006). Note, however, that other choices are possible. For example, Chung, Rabe-Hesketh & Choi (2013) recommend a gamma prior in combination with posterior mode estimation for $\tau$. Moreover, when prior information regarding possible values for $\tau$ is available, an informative prior can be specified as was done in Gronau et al. (2017). Given that the heterogeneity parameter $\tau$ is a higher-level parameter in the model, there is less information available in the data to inform its posterior meaning that the prior will generally be more influential for this parameter and thus requires careful specification. See Rover et al. (2021) for an overview and guidance on how to specify weakly informative priors for this parameter."

Chung Y, Rabe-Hesketh S, Choi IH. Avoiding zero between-study variance estimates in random-effects meta-analysis. Stat Med. 2013;32(23):4071-4089.

Gelman A. Prior distributions for variance parameters in hierarchical models. Bayesian Anal. 2006;1(3):515-534. [https://doi.org/10.1214/06-BA117A](https://doi.org/10.1214/06-BA117A "https://doi.org/10.1214/06-BA117A").

Gronau, Q. F., Van Erp, S., Heck, D. W., Cesario, J., Jonas, K. J., & Wagenmakers, E. J. (2017). A Bayesian model-averaged meta-analysis of the power pose effect with informed and default priors: The case of felt power. _Comprehensive Results in Social Psychology_, _2_(1), 123-138.

Röver, C, Bender, R, Dias, S, et al. On weakly informative prior distributions for the heterogeneity parameter in Bayesian random-effects meta-analysis. Res Syn Meth. 2021; 12: 448– 474. [https://doi.org/10.1002/jrsm.1475](https://doi.org/10.1002/jrsm.1475 "https://doi.org/10.1002/jrsm.1475")

4) In the abstract and in the main text, it states "We present a simulation study to validate the performance of BRMA relative to state-of-the-art meta-regression (RMA)". What does RMA refer to here, is it "Random effect Meta-Analysis using REML"? If yes, I think the term random-effect meta-analysis (or meta-regression) using RMLE is more clear than state-of-the-art meta-analysis (or meta-regression).

### Minor points  
 Line 385: "see 1": I think Table is missing

# References  
1) Thompson SG, Higgins JPT. How should meta-regression analyses be undertaken and interpreted?. Stat Med. 2002;21:1559-1573.  
2) Chung Y, Rabe-Hesketh S, Choi IH. Avoiding zero between-study variance estimates in random-effects meta-analysis. Stat Med. 2013;32(23):4071-4089.  
3) Günhan, BK, Röver, C, Friede, T. Random-effects meta-analysis of few studies involving rare events. Res Syn Meth. 2020; 11: 74– 90. [https://doi.org/10.1002/jrsm.1370](https://doi.org/10.1002/jrsm.1370 "https://doi.org/10.1002/jrsm.1370")  
4) Röver, C, Bender, R, Dias, S, et al. On weakly informative prior distributions for the heterogeneity parameter in Bayesian random-effects meta-analysis. Res Syn Meth. 2021; 12: 448– 474. [https://doi.org/10.1002/jrsm.1475](https://doi.org/10.1002/jrsm.1475 "https://doi.org/10.1002/jrsm.1475")  
5) Gelman A. Prior distributions for variance parameters in hierarchical models. Bayesian Anal. 2006;1(3):515-534. [https://doi.org/10.1214/06-BA117A](https://doi.org/10.1214/06-BA117A "https://doi.org/10.1214/06-BA117A").

### 2022-11-23 simulatie_2021/Analysis Sim2021_3.R

@@ -444,6 +444,58 @@ names(table_tau2)[2:4]<-c("HS", "LASSO", "RMA")
 saveRDS(table_tau2, "paper/table_tau2.RData")
 write.csv(table_tau2, file =  "paper/table_tau2.csv", row.names = FALSE)
 
+# Variance of tau2 --------------------------------------------------------
+
+tau_var <- tau2
+tau_var <- tau_var[ , lapply(.SD, var), by=conditions, .SDcols = measure.vars]
+
+yvars <- measure.vars
+anovas<-lapply(yvars, function(yvar){
+  form<-paste(yvar, '~', paste(conditions, collapse = " + "))
+  #form<-paste(yvar, '~(', paste(unlist(conditions[-lc]), "+", collapse = ' '), conditions[lc], ") ^ 2") #the ^2 signifies that we want all possible effects up until interactions
+  thisaov<-aov(as.formula(form), data=tau_var)
+  thisetasq<-EtaSq(thisaov)[ , 2]
+  list(thisaov, thisetasq)
+})
+
+
+# Anova for the difference ------------------------------------------------
+
+comps <- expand.grid(yvars, yvars)
+comps <- comps[!comps$Var1 == comps$Var2, ]
+comps <- t(apply(comps, 1, sort))
+comps <- comps[!duplicated(comps), ]
+diffanovas <- sapply(1:nrow(comps), function(i){
+  form<-as.formula(paste("tauhat", '~ algo * (', paste(conditions, collapse = "+"),")")) #the ^2 signifies that we want all possible effects up until interactions
+  tmp <- tau_var
+  tmp <- tmp[, .SD, .SDcols = c(conditions, comps[i, , drop = TRUE])]
+  names(tmp) <- gsub("^(.+?)_tau1", "tauhat_\\1", names(tmp))
+  tmp = melt(tmp, id.vars = names(tmp)[1:7],
+             measure.vars = names(tmp)[8:9],
+             variable.name = "algo",
+             value.name = "tauhat")
+  thisaov<-aov(form, data=tmp) #change data according to dataframe you are using
+  thisetasq<-EtaSq(thisaov)[ , 2]
+  thisetasq <- thisetasq[startsWith(names(thisetasq), "algo")]
+  thisetasq
+})
+colnames(diffanovas) <- paste0(gsub("_.+$", "", toupper(comps[,1])), " vs. ", gsub("_.+$", "", toupper(comps[,2])))
[…]

### 2022-11-28 paper/action_letter.Rmd
update 2022-11-28 13:44:48

@@
 class       : "draft"
-bibliography      : ["r-references.bib", "references.bib",
-                     "sara-references.bib", "eli-references.bib", "metaforest.bib"]
+bibliography      : ["meta-analysis.bib"]
 output      : papaja::revision_letter_pdf
@@
 library(revise)
+library(tidySEM)
+out <- readRDS("output.RData")
 read_manuscript("manuscript.Rmd")
+
 ```
@@
 
-In addressing all comments below, we have added detail and elaboration in many places. We hope that this addresses this comment.
+We have rewritten all sections of the paper and restructured some of them.
+Furthermore, in addressing all reviewer comments (see below), we have added detail and elaboration in many places.
+We hope that this addresses this comment.
 
@@
 We see now that we did not report clearly enough how many design factors there were and what they were.
-Apparently, it was also not sufficiently clear that "noise moderators" are not the same as "design factors".
 To address this comment and avoid confusion, we have rewritten this paragraph as follows:
@@
 
-To address this comment, we have made the following changes:
-
-1) We have rewritten the opening paragraph to clearly state the problem addressed in this paper, and the proposed solution:
+To address this comment, we have rewritten the opening paragraph to clearly state the problem addressed in this paper, and the proposed solution:
 
@@
 
-\WorkInProgress
-
 \RC{Statistical underpinnings: Again, I found a lot of repetitions in the text.}
 
-\WorkInProgress
+We have merged several sections to avoid repetition in the text.
 
@@
 
-\WorkInProgress
+We have attempted to clarify this sentence as follows:
+
+`r get_revision("informationdistribution")`
 
@@
 
-\WorkInProgress
+To address this comment, we have moved the explanation of the "error term" to the paragraph where it is first discussed.
 
@@
 
-\WorkInProgress
+We have made the suggested change.
 
@@
 
-\WorkInProgress
+To address this comment, we have moved this paragraph about regularization into the section on regularized regression.
 
@@
 
-\WorkInProgress
+Our aim is to provide a high-level conceptual introduction of the method's underpinnings,
+not to replicate the many excellent technical publications that already exist on these methods. 
+To address this comment, we have edited all technical sections for greater clarity and detail. Additionally, we explicitly direct the reader to appropriate introductory texts that go more in depth:
+
+`r get_revision("reftibshirani")`
+
+And:
+
+`r get_revision("refmcelreath")`
 
@@
 
-\WorkInProgress
+We were not aware of any existing literature at the time of writing;
+most likely because several such papers were only published after we wrote our draft - but we thank the Reviewer for encouraging us to search the literature again.
+Based on our findings, we now include the following paragraph:
+
+`r get_revision("earlierpapers")`
 
@@
 
-\WorkInProgress
+To address this comment, we now cite the following theoretical paper:
+
+`r get_revision("reftibshirani")`
 
@@
 
-\WorkInProgress
+We respectfully feel that indicating advantages and disadvantages of other penalties is out of scope for the present paper.
+The only reason we explain the LASSO penalty is to explain how regularization works.
+Since we ultimately do not use a frequentist solution with shrinkage penalties, there is little point to explaining other penalties in detail.
+
+To address this comment, we now clarify why we explain the LASSO penalty:
+
+`r get_revision("whylasso")`
 
@@
 
-\WorkInProgress
+We now explain this as follows:
+
+`r get_revision("defaultvalues")`
+
+Note that the results of our simulation study again validate the fact that these are sensible defaults.
 
@@
 
-We intended to explain that the regularizing horseshoe prior is an extension of the (normal) horseshoe prior. This was insufficiently clear.
-To address this comment, we have written the following section:
+We recognize that this choice of words was confusing.
+The regularizing horseshoe prior is an extension of the horseshoe prior.
+To address this comment, we now explain this in the text:
 
@@
 
-To address this comment, we have made a stricter separation between methodology and code. 
-All references to code are now relegated to the Implementation section.
+We see that a stricter separation of methodology and code could aid readability.
+Therefore, we have addressed this comment by relegating all code to the Implementation section.
 
-We do believe that there are advantages to having code in the paper and not in an appendix, as the intended readership for this paper consists of those who wish to conduct a Bayesian regularized meta-analysis.
-We hope that the current approach is an acceptable compromise.
+We do believe that there are advantages to having code in the paper and not in an appendix,
+as the intended readership for this paper consists of those who wish to conduct a Bayesian regularized meta-analysis.
+For this purpose, it is important that readers understand how to translate the methodological principles to a model specified in the `pema` package.
+We hope that the current revision strikes a reasonable compromise.
 
@@
 
-This section is important because omitting the intercept from the model has very different implications for penalized Bayesian meta-regression than for frequentist models (where the model is equivalent, regardless of whether the intercept is included or not).
+This section is important because omitting the intercept from the model has very different implications for regularized meta-regression than for non-regularized models.
 
@@
 
-`get_revision("intercept")`
+`r get_revision("intercept")`
 
@@
 We respectfully believe that this comment is based on a misunderstanding of the procedure.
-We do not split a finite sample into a training and testing set - 
-we simulate data for both sets from the same known data generating model.
-Each sample from this model is independent and identically distributed (IID).
-The distinction between training and testing is thus arbitrary.
+The Reviewer's comment seems to suggest that we split a finite sample into a training and testing set. This is not the case.
+
+Instead, we simulate both data sets from the same known data generating model.
+Each sample from this model is thus independent and identically distributed (IID).
+The distinction between training and testing is arbitrary.
 This is different from real data analyses, where the available dataset is finite, and training and testing data are drawn from that finite dataset - thus violating the assumption of IID.
@@
 We respectfully feel that it is important to define how we operationalized each outcome metric, and why we use it.
-Unfortunately, we now realize that our explanation was not sufficiently clear.
-To address this comment, we have rewritten the explanation of our outcome metric, $R^2_{test}$.
-We hope that this revised explanation clarifies that this is **not** the basic indicator R2, but rather, a different type of R2 that is suitable for assessing overfitting:
+In fact, it seems that our explanation was not sufficiently clear,
+because the outcome metric is not the basic indicator R2,
+as the Reviewer has apparently understood,
+but rather, a different type of R2 that is suitable for assessing overfitting.
+
+To address this comment, we have tried to explain the outcome metric, $R^2_{test}$ more clearly:
 
@@
 
-Additionally,
-the reason we do not use AIC or BIC is because these are comparative fit indices, only suitable for comparing a set of models; we have only a single model and AIC or BIC do not speak to the absolute fit of a single model.
+With regard to the Reviewer's suggestion to use AIC or BIC:
+the reason we do not use these is because they are comparative fit indices, only suitable for comparing a set of models; we have only a single model and AIC or BIC do not speak to the absolute fit of a single model.
 
-The reason we do not use adjusted $R^2$ is because it is an approximation of $R^2_{test}$ but calculated on the training sample data.
-Since we simulate data from a known true model,
-we do not need to *estimate* $R^2_{test}$ - we can *calculate* it directly, based on a new sample.
+The reason we do not use adjusted $R^2$ is because it is an approximation of $R^2_{test}$ that can be calculated on the training data.
+Since we can simulate testing data from a known model,
+we do not need to *estimate* $R^2_{test}$ - we can *calculate* it directly.
 
@@
 
-As these simulations are very computationally demanding,
-and increasing the number of replications adds only marginal accuracy gains, we did indeed use 100 replications.
-However, as per the Reviewer's request, we have increased this to 1000.
+As reported, we used 100 replications per simulation condition because these simulations are very computationally demanding,
+and increasing the number of replications adds only marginal accuracy gains.
+In total, we thus simulated 194.400 cases.
+Many of the analyses marginalize over some design factors,
+thus we always have a very large sample size.
+We do not see an urgent need to increase the number of replications,
+but we defer to the Editor in this matter.
 
@@
 
-We corrected this, and slightly rephrased the sentence for clarity.
+We corrected this, and have rephrased the sentence for clarity.
 
@@
 
-To address this comment, we now describe the results in the text, and provide the requested tables as online Supplements.
+To address this comment, we now describe the results in the text, and provide the requested tables as online Supplements:
+
+`r get_revision("variancebeta")`
+
+And:
+
+`r get_revision("variancetau")`
 
@@
 This means we can make the examples reproducible, requiring only the `pema` package.
-We feel that it adds a lot to the paper to present a reproducible real-data example based on a novel dataset.
+We feel that it adds a lot to the paper to present a reproducible real-data example based on a novel data set.
 To address this comment,
@@
 
-\WorkInProgress
+`r get_revision("sample400")`
 
@@
 
-\WorkInProgress
+We have proofread and spell checked the manuscript, and corrected all mistakes found.
 
@@
 
-\WorkInProgress
+We agree with the Reviewer that there are important limitations to meta-regression, and Thompson & Higgins provide an excellent analysis thereof.
+<!-- Limitations -->
+<!-- i) multicolinearity -->
+<!-- ii) ecological fallacy -->
+<!-- iii) restriction of range -->
+<!-- iv) multicolinearity -->
+<!-- v) something specific to clinical trials?? -->
+<!-- vi) data availability -->
+<!-- vii) small sample size, limited generalizability -->
+<!-- PITFALLS -->
+<!-- i) curse of dimensionality: small sample size, multicolinearity -->
+<!-- ii) overfitting -->
+<!-- iii) variable selection -->
+<!-- iv) variable selection -->
+Most of the limitations and pitfalls they discuss come down to two fundamental points which are already addressed throughout our paper: 1) the curse of dimensionality and its implications for multicolinearity (limitations i, iv, vii and pitfalls i, ii, iii, and iv), and 2) the ecological fallacy (limitation ii and iv).
+They further address three singular points which cannot be attributed to the two fundamental points:
+Limitation iii relates to the problem of restriction of range in moderators (which we do not address),
+Limitation vi relates to limited data availability (which we address in our discussion of missing data),
+and Limitation v makes a point about regression to the mean in RCTs that we fail to grasp.
+
+Since our method is a statistical solution to point 1),
+we devote most attention to it.
+We also acknowledge most of the other points.
+However, we respectfully feel that it is out of scope for the present paper to devote further attention to limitations of meta-regression that our method does *not* address;
+especially since Thompson & Higgins already did so.
+
+To address this comment, we have referenced the Thompson & Higgins paper in several places, and we have added the following sentences to our Recommendations for Applied Researchers:
+
+`r get_revision("metareglimits")`
 
@@
 
-We thank the Reviewer for suggesting these references, which had eluded our literature search.
+First of all, we thank the Reviewer for suggesting these references, which had eluded our literature search.
+We now cite them in relevant places in the manuscript.
 
-We agree that the use of weakly informative priors for heterogeneity parameters was insufficiently discussed in the previous version of our manuscript, and have now added a paragraph on that topic (see our response to the next comment).
+Second of all, we agree that the use of weakly informative priors for heterogeneity parameters was insufficiently discussed in the previous version of our manuscript, and have now added a paragraph on that topic (see our response to the next comment).
 
-However, it is important to note that the use of weakly informative priors (WIP) for heterogeneity parameters serves a categorically different purpose than the use of regularizing priors for regression coefficients - even if the term "regularization" has been used for both in prior literature.
+Third of all, we feel that it is important to stress that the use of weakly informative priors (WIP) for heterogeneity parameters serves a categorically different purpose than the use of regularizing priors for regression coefficients - even if the term "regularization" has been used for both in prior literature.
 The purpose of WIP for heterogeneity parameters is to aid model convergence and avoid boundary estimates.
@@
 We believe that the newly added paragraph sufficiently clarifies these distinct uses of "regularization" (see response to next comment).
-
-Thank you for pointing out these relevant references.
-We have included the reference to Chung et al.
-(2013), Gelman (2006) and Rover et al.
-(2021) in the new section on the prior for $\tau$ (see the next comment).
-In addition we have added the following section on page ...
-to be more explicit about the terminology of different types of priors:
-
-Suggest to add this paragraph in the section on Bayesian estimation after "which reflects expectations about likely parameter values after having seen the data." Note: if included, this should be updated in the text from a previous comment to reviewer 1 as well.
-Also here it is relevant whether we use "regularizing" or "shrinkage" priors and should mention the definite choice explicitly.
-
-"As a result, the posterior distribution is a compromise between the likelihood of the data and the prior distribution.
-The influence of either the data or the prior is determined by the sample size as well as the informativeness of the prior distribution.
-The larger the sample size, the more influential the likelihood of the data will be.
-Similarly, as the prior distribution becomes more informative, i.e., more peaked, it will exert more influence on the results.
-Priors can thus be placed on a continuum from "non-informative" to "highly informative".
-Weakly informative or regularizing priors are often used in situations when there is some prior information available, for example regarding the boundaries of the parameter space or, as is the case here, regarding the existence of parameters equal to zero.
-Throughout this manuscript, we will use the term "shrinkage prior" to refer to the weakly informative or regularizing prior that holds the prior knowledge that some coefficients are equal to zero and should therefore be shrunken towards zero."
-
-\WorkInProgress
 
@@
 `r get_revision("tauprior")`
-
-Chung Y, Rabe-Hesketh S, Choi IH. Avoiding zero between-study variance estimates in random-effects meta-analysis. Stat Med. 2013;32(23):4071-4089.
-
-Gelman A.
-Prior distributions for variance parameters in hierarchical models.
-Bayesian Anal.
-2006;1(3):515-534. [https://doi.org/10.1214/06-BA117A](https://doi.org/10.1214/06-BA117A "https://doi.org/10.1214/06-BA117A").
-
-Gronau, Q.
-F., Van Erp, S., Heck, D.
-W., Cesario, J., Jonas, K.
-J., & Wagenmakers, E.
-J.
-(2017).
-A Bayesian model-averaged meta-analysis of the power pose effect with informed and default priors: The case of felt power. _Comprehensive Results in Social Psychology_, _2_(1), 123-138.
-
-Röver, C, Bender, R, Dias, S, et al.
-On weakly informative prior distributions for the heterogeneity parameter in Bayesian random-effects meta-analysis.
-Res Syn Meth.
-2021; 12: 448– 474. [https://doi.org/10.1002/jrsm.1475](https://doi.org/10.1002/jrsm.1475 "https://doi.org/10.1002/jrsm.1475")
 
@@
 
-# References
-1) Thompson SG, Higgins JPT. How should meta-regression analyses be undertaken and interpreted?. Stat Med. 2002;21:1559-1573.
-2) Chung Y, Rabe-Hesketh S, Choi IH. Avoiding zero between-study variance estimates in random-effects meta-analysis. Stat Med. 2013;32(23):4071-4089.
-3) Günhan, BK, Röver, C, Friede, T. Random-effects meta-analysis of few studies involving rare events. Res Syn Meth. 2020; 11: 74– 90. https://doi.org/10.1002/jrsm.1370
-4) Röver, C, Bender, R, Dias, S, et al.
-On weakly informative prior distributions for the heterogeneity parameter in Bayesian random-effects meta-analysis.
-Res Syn Meth.
-2021; 12: 448– 474.
-https://doi.org/10.1002/jrsm.1475
-5) Gelman A. Prior distributions for variance parameters in hierarchical models. Bayesian Anal. 2006;1(3):515-534. https://doi.org/10.1214/06-BA117A.
-
 \newpage

### 2022-11-28 paper/manuscript.Rmd
update 2022-11-28 13:44:48

@@
   - name: "Caspar J. Van Lissa"
-    affiliation: "1,2"
+    affiliation: "1"
     corresponding: yes
-    address: "Padualaan 14, 3584CH Utrecht, The Netherlands"
-    email: "c.j.vanlissa@uu.nl"
+    address: "Professor Cobbenhagenlaan 125, 5037 DB Tilburg, The Netherlands"
+    email: "c.j.vanlissa@tilburguniversity.edu"
     role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
@@
   - name: "Sara van Erp"
-    affiliation: "1"
+    affiliation: "2"
     role:
@@
   - name: "Eli-Boaz Clapper"
-    affiliation: "1"
+    affiliation: "2"
     role:
@@
   - id            : "1"
+    institution   : "Tilburg University, dept. Methodology & Statistics"
+  - id            : "2"
     institution   : "Utrecht University, dept. Methodology & Statistics"
-  - id            : "2"
-    institution   : "Open Science Community Utrecht"
 
@@
   meta-regression can be used to account for potentially relevant between-studies differences.
-  A key challenge is that the number of these potential moderators is often high
+  A key challenge is that the number of candidate moderators is often high
   relative to the number of studies.
-  This introduces a risk of overfitting and finding spurious results.
-  To overcome this challenge,
-  [we introduce Bayesian Regularized Meta-Analysis (BRMA),
+  This introduces risks of overfitting, spurious results, and model non-convergence.
+  To overcome these challenges,
+  <span id = "lassoabstract">we introduce Bayesian Regularized
+  Meta-Analysis (BRMA),
   which selects relevant moderators from a larger set of candidates
   by shrinking small regression coefficients towards zero
-  with regularizing (LASSO or horseshoe) priors.]{#lassoabstract}
+  with regularizing (LASSO or horseshoe) priors.</span>
   This method is suitable when there are many potential moderators,
@@
   moderators,
-  but the overall proportion of Type I and Type II errors was
+  while the overall proportion of Type I and Type II errors was
   equivalent to RMA.
@@
 
-bibliography      : ["r-references.bib", "references.bib",
-                     "sara-references.bib", "eli-references.bib", "metaforest.bib"]
+bibliography      : ["meta-analysis.bib"]
 
@@
 set.seed(42)
-knitr::opts_chunk$set(cache.extra = knitr::rand_seed, warning = FALSE)
+knitr::opts_chunk$set(cache.extra = knitr::rand_seed, warning = FALSE, message = FALSE)
 ```
@@
 Accounting for between-studies heterogeneity thus poses a non-trivial challenge to classic meta-analytic methods.
-The present study introduces a novel method that overcomes this challenge by imposing Bayesian regularizing (LASSO and horseshoe) priors on the regression coefficients.
+The risk of arriving at false-positive conclusions
+when there are many potential moderators is so ubiquitous that it was referred to as the "primary pitfall" in meta-regression [@thompsonHowShouldMetaregression2002].
+The present study introduces a novel method to overcome this pitfall by imposing Bayesian regularizing (LASSO and regularizing horseshoe) priors on the regression coefficients.
 These priors shrink the effect of irrelevant predictors towards zero while leaving important predictors relatively unaffected.
@@
 identifying a smaller subset of relevant moderators from the larger set of candidate moderators [@hastieElementsStatisticalLearning2009].
-<span id = "theory">One way to perform variable selection is by relying on theory,
-and selecting only moderators that should theoretically have an impact on effect size.
+<span id = "theory">Prior authors have stressed the need to perform variable selection in meta-regression,
+for example, by limiting the number of moderators considered [@thompsonHowShouldMetaregression2002].
+This does not resolve the problem, however,
+as failing to consider a moderator does not mean that it is irrelevant.
+Instead, moderators ought to be selected based on their theoretical or empirical relevance for the studied effect.
+
+One approach to is to select variables on theoretical grounds.
 An important caveat is that theories that describe phenomena at the level of individual units of analysis do not necessarily generalize to the study level.
@@
 generalizing inferences across levels of analysis [@jargowskyEcologicalFallacy2004].
-The implications of the ecological fallacy for interpreting the *results* of meta-regression have been discussed elsewhere [@bakerUnderstandingHeterogeneityMetaanalysis2009]:
-For example, meta-regression may find a significant positive effect of average sample age on treatment efficacy,
-even if age is uncorrelated with treatment effect within each study.
-A similar problem arises when using individual level theory to select study level moderators:
+The implications of the ecological fallacy for interpreting the *results* of meta-regression are well-known [@bakerUnderstandingHeterogeneityMetaanalysis2009; @thompsonHowShouldMetaregression2002]:
+For example, meta-regression may find a significant positive effect of average sample age on the effect size of a randomized controlled trial,
+even if age is uncorrelated with treatment efficacy within each study.
+Less well-known is that the same problem applies when using individual level theory to select study level moderators:
 If theory states that an individual's age influences their susceptibility to treatment,
 that does not imply that average sample age will be a relevant moderator of study-level treatment effect in meta-regression.
-For an example of study level theory,
-consider the *decline effect*:
+One rare example of study level theory is the *decline effect*:
 effect sizes in any given tranche of the literature tend to diminish over time [@schoolerUnpublishedResultsHide2011].
@@
 theory has limited utility for variable selection.</span>
-
-An alternative solution is to rely on statistical methods for variable selection.
+A further complication is that theoretically relevant variables might not be reported in many published papers,
+which may be one reason why moderator analyses are rarely executed as planned [@thompsonHowShouldMetaregression2002]
+
+An alternative solution is data-driven variable selection using appropriate statistical techniques.
 This is a focal issue in the discipline of machine learning [@hastieElementsStatisticalLearning2009].
-There is precedent for the use of machine learning to perform variable selection in meta-analysis [@vanlissaSmallSampleMetaanalyses2020].
-This prior work used the non-parametric *random forest* algorithm to perform variable selection.
-One limitation of random forests is that non-parametric models are harder to interpret,
-particularly when the readership is accustomed to linear models that describe the effect of each moderator with a single parameter.
-
-In linear models, variable selection can be accomplished via a statistical method called  *regularization*.
+There is precedent for the use of machine learning for variable selection in meta-analysis [@vanlissaSmallSampleMetaanalyses2020].
+This prior work used the non-parametric *random forest* algorithm.
+A limitation of random forests is that its results are harder to interpret than linear models,
+which describe the effect of each moderator with a single parameter.
+The present study instead uses *regularization*,
+which is a method for variable selection in linear models.
 Regularization shrinks small model parameters towards zero,
@@
 This manuscript discusses two shrinkage priors,
-the LASSO and horseshoe prior.</span>
+the LASSO and regularizing horseshoe prior.</span>
 
@@
 that each observed effect size $T_i$ is an estimate of an underlying true population effect size $\beta_0$ [@hedgesFixedRandomeffectsModels1998].
-This assumption is appropriate when meta-analyzing close replication studies [@higginsReevaluationRandomeffectsMetaanalysis2009].
+This assumption is appropriate when meta-analyzing close replication studies [@higginsReevaluationRandomeffectsMetaanalysis2009a].
 The only cause of heterogeneity in observed effect sizes is presumed to be sampling error, $v_i$, which is treated as known, and computed as the square of the standard error of the effect size.
@@
 and thus follow a normal distribution with mean $\beta_0$ and variance $\tau^{2}$ [@hedgesFixedRandomeffectsModels1998].
-This assumption is appropriate when studies are conceptually similar but differ in small random ways [@higginsReevaluationRandomeffectsMetaanalysis2009]. 
+This assumption is appropriate when studies are conceptually similar but differ in small random ways [@higginsReevaluationRandomeffectsMetaanalysis2009a]. 
 The observed effect sizes are thus given by:
@@
 \end{align}
+In this model, the error term $\zeta_{i}$ represents between-studies heterogeneity, with variance $\tau^2$.
 As in the fixed effect model,
 studies with smaller sampling errors are assigned more weight.
-However, to account for the fact that all studies now provide some information about different regions of the distribution of true effect sizes,
-the weights are attenuated in proportion to the spread of that distribution.
-The random effects weights are thus given by $w_{i} =  \frac{1}{v_i + \hat{\tau}^2}$.
+<span id = "informationdistribution">In contrast to the fixed effect model, the random effects model assumes that all studies provide some information about the underlying distribution of true effect sizes.
+Fixed effect weights would discount the information smaller studies provide about the scale of this distribution, which is represented by it's variance $\tau^2$.
+To overcome this limitation, the weights are attenuated in proportion to the variance.
+The random effects weights are thus given by $w_{i} =  \frac{1}{v_i + \hat{\tau}^2}$.</span>
 Whereas sampling error is still treated as known,
@@
 and $\beta_{1\ldots p}$ their regression coefficients.
-Note that $\beta_0$ represents the intercept of the distribution of true effect sizes after controlling for the moderators
-and the error term $\zeta_{i}$ represents residual unexplained between-studies heterogeneity.
+Note that $\beta_0$ now represents the intercept of the distribution of true effect sizes after controlling for the moderators.
 This is a mixed-effects model; the intercept and effects of moderators are treated as fixed and the residual heterogeneity as random [@lopez-lopezEstimationPredictivePower2014]:
 \begin{align}
-T_i &= \beta_{0}+ \beta_{1}x_{1}+ \beta_{2}x_{2} + \ldots + \beta_{p}x_{p} + \zeta_{i} + \epsilon_i\\
+T_i &= \beta_{0}+ \beta_{1}x_{1}+ \beta_{2}x_{2} + \ldots + \beta_{p}x_{p} + \zeta_{i} + \epsilon_i
 \end{align}
 
-<!--The topic of estimating the residual heterogeneity is a highly discussed one (Veroniki et al., 2016; Viechtbauer \& López-López, 2015; Panityakul et al., 2013).
-The ability of the estimators to predict the residual heterogeneity is influenced by different factors, such as the number of studies (Guolo \& Varin, 2017; Panityakul et al., 2013; Hardy \& Thompson, 1996) included and the sample size of the individual studies (Panityakul et al., 2013).
-A third, and obvious factor, that is classified as relevant to model performance is heterogeneity among studies being meta-analysed (Kontopantelis \& Reeves, 2011; Jackson \& White, 2018).
-Coverage from models degrades when the residual heterogeneity increases, mostly when the amount of studies is small (Brockwell \& Gorden, 2001).
-Considering that all models their performance is linked to the accuracy of the estimate.
-According to Sidik \& Jonkman (2007), it is generally the case that the larger true between-study variance is, the more biased the estimate can be, which diminishes the performance of the method.-->
-Numerous methods have been proposed to estimate meta-regression models,
-the most common of which is restricted maximum likelihood [REML, @pattersonRecoveryInterblockInformation1971].
-REML is an iterative method, which means that it repeatedly performs the same calculations and updates the estimated parameters until their estimates stabilize.
-This estimator has low bias, which means that the average values of the parameters are close to their true values [@panityakulEstimatingResidualHeterogeneity2013].
-However, this bias comes at the cost of higher variance, which means that the estimated values of a population parameter vary more from one sample to the next. 
-An estimator with low bias and high variance produces results that generalize less well to new data than an estimator with high bias and low variance.
+### Regularized regression
+
+Meta-regression models are most commonly estimated using weighted least squares,
+with weights determined according to the aforementioned random effects model,
+where residual heterogeneity is estimated using restricted maximum likelihood [@pattersonRecoveryInterblockInformation1971; @viechtbauerBiasEfficiencyMetaAnalytic2005].
+This approach, henceforth referred to as RMA, has low bias, which means that, across hypothetical replications of a study, the average values of model parameters are close to their true population values [@panityakulEstimatingResidualHeterogeneity2013].
+Low bias comes at the cost of higher variance, however,
+which means that the estimated values of population parameters vary more from one hypothetical replication to the next.
 This phenomenon is known as the *bias-variance trade-off*.
-Regularization increases bias to reduce variance.
-A disadvantage of this trade-off is that model parameters can no longer be interpreted as straightforwardly as OLS regression coefficients.
-An advantage is that the resulting model is more generalizable and makes better predictions for new data [see @hastieElementsStatisticalLearning2009].
-
-### Regularized regression
-
-Ordinary least squares regression (OLS) estimates the model parameters by minimizing the Residual Sum of Squares (RSS) of the dependent variable.
-The resulting parameter estimates perfectly describe linear relations in the present data set, but generalize less well to new data:
-$$
+In general, an estimator with low bias and high variance produces results that generalize less well to new data than an estimator with high bias and low variance.
+Regularized approaches to regression intentionally increase bias in order to reduce variance.
+This is a sensible approach in the context of small samples, which are common in meta-analyses,
+because small samples incur a high risk of overfitting,
+and typically have relatively high levels of multicollinearity,
+due to the higher probability that extreme values on one moderator coincide with extreme values on another.
+In such cases, regularized regression reduces the risk of overfitting and increase generalizability of the results [see @hastieElementsStatisticalLearning2009].
+
+<span id = "reftibshirani">To understand how regularized regression introduces bias, consider a comparison between ordinary least squares regression and LASSO regression [for a more elaborate introduction, see @tibshiraniRegressionShrinkageSelection2011].</span>
+Ordinary least squares regression (OLS) estimates model parameters by minimizing the Residual Sum of Squares (RSS) of the outcome variable, given by the formula below.
+In this equation, $n$ is the number of participants; $y_i$ is the outcome variable, and $x$ is one of $p$ predictor variables.
+\begin{align}
 RSS=\sum_{i=1}^{n}(y_{i} - \beta_{0} - \sum_{j=1}^{p}\beta_{j}x_{ij})^2
-$$
+\end{align}
+The resulting parameter estimates perfectly describe linear relations in the present data set, but generalize less well to new data.
 Regularized regression biases parameter estimates towards zero by adding a penalty term to the RSS.
-As an example, we will discuss the most common penalty: the sum of the absolute regression coefficients, also known as the the L1- or LASSO penalty [@hastieElementsStatisticalLearning2009].
-Note that other penalties exist.
+Most common is the LASSO penalty, which consists of the sum of the absolute regression coefficients, or the L1 norm [@hastieElementsStatisticalLearning2009].
 As the LASSO penalty is a function of the regression coefficients, it increases when they get bigger.
 This incentivizes the optimizer to keep the regression coefficients as small as possible.
-Note that the amount of regularization can be controlled by multiplying the penalty by a tuning parameter, $\lambda$.
+The amount of regularization can be controlled by multiplying the penalty by a tuning parameter, $\lambda$.
 If $\lambda$ is zero, the shrinkage penalty has no impact.
@@
 The LASSO penalized residual sum of squares is given by:
-$$
+\begin{align}
 PRSS= RSS + \lambda \sum_{j=1}^{p}|\beta_{j}|
-$$
+\end{align}
+<span id = "whylasso">Note that many other regularizing penalties exist.
+This introduction focuses on the LASSO penalty because it is most ubiquitous, easy to understand,
+and has an analogue in Bayesian estimation,
+as explained in the next section.</span>
+
+<span id = "earlierpapers">Some seminal studies have applied the LASSO to perform moderator selection in meta-regression [@rosettieCosteffectivenessHPVVaccination2021; @sebriNaturalResourcesIncome2021; @requiaGlobalAssociationAir2018].
+This suggests that others have recognized its potential for exploring heterogeneity when the number of moderators is relatively high to the number of studies.
+However, these existing publications have taken a two-step approach, whereby moderators are first selected using LASSO regression,
+and selected moderators are then included in meta-regression analysis.
+This approach is fraught; firstly, because of known problems of inference after variable selection [@zhangInferenceVariableSelection1992].
+As the moderators included in the second step are based on an exploratory first step,
+their parameters are not valid for inference.
+Secondly, although the LASSO model in the first step accounts for potential multicollinearity by including all colinear variables but restricting the size of their coefficients,
+the meta-regression in the second step no longer does so.
+A three-step extension of the two-step approach exists
+that uses principles from the causal inference literature to overcome these limitations [@belloniInferenceTreatmentEffects2014].
+BRMA, by contrast, overcomes these limitations by introducing a one-step approach that performs inference within the penalized framework.</span>
 
@@
 The prior distribution is updated with the likelihood of the data to form a posterior distribution,
-which reflects expectations about likely parameter values after having seen the data [for an extensive introduction, see @mcelreathStatisticalRethinkingBayesian2020].
+which reflects expectations about likely parameter values after having seen the data.
+<span id = "refmcelreath">For a more extensive introduction to Bayesian estimation, see @mcelreathStatisticalRethinkingBayesian2020.</span>
 
 A regularizing prior distribution shrinks small coefficients towards zero by assigning high probability mass to near-zero values.
-There are many different regularizing prior distributions [@vanErpOberskiMulder2019].
-Some of these regularizing priors are analogous to specific frequentist methods.
+There are many different regularizing prior distributions,
+some of which are analogous to specific frequentist methods [@vanErpOberskiMulder2019].
 For example, a double exponential prior (hereafter: LASSO prior) results in posterior distributions whose modes are identical to the estimates from LASSO-penalized regression [@ParkCasella2008].
-There are some notable differences between the frequentist LASSO penalty and its Bayesian counterpart, the LASSO prior.
-First, the frequentist LASSO penalty has a tuning parameter $\lambda$, whose value is usually chosen via cross-validation.
-In the Bayesian approach, an analogous role is fulfilled by a hyperparameter of the shrinkage prior.
-Instead of using cross-validation, the value of this hyperparameter can be estimated from the data.
+Both the the frequentist LASSO penalty and the Bayesian LASSO prior have a tuning parameter $\lambda$ that controls the amount of regularization.
+In frequentist LASSO, its value is usually chosen via cross-validation [@hastieElementsStatisticalLearning2009]. 
+In the Bayesian approach, by contrast,
+its value can be optimized during model estimation.
 
@@
 which means that it does not shrink (and therefore bias) substantial coefficients as much.
-One remaining limitation of the horseshoe prior is that it is difficult to specify a prior that ensures a sufficiently sparse solution.
-The regularizing horseshoe was introduced to overcome this limitation;
-it uses information about the expected number of parameters to determine an appropriate shrinkage prior  [@PiironenVehtari2017b].</span></span>
+One limitation of the horseshoe prior is that it is difficult to specify a prior that ensures a sufficiently sparse solution.
+The regularizing horseshoe was introduced to overcome this limitation [@PiironenVehtari2017b].</span></span>
 
@@
 The LASSO prior is given by:
-$$
-\beta_{j} \sim \text{DE}(0, \frac{s}{\lambda})
-$$
-where DE denotes the double exponential distribution with a location equal to 0 and a scale determined by a global scale parameter $s$ and an inverse-tuning parameter $\lambda$.
-In the present study, the global scale parameter is set to 1,
-and the inverse-tuning parameter is assigned a $\chi^2$ prior distribution with 1 degree of freedom.
-Its value is thus optimized during model estimation.
-
-The regularizing horseshoe prior [@PiironenVehtari2017b] is given by:
-$$
-\begin{aligned}
-\beta_{j} &\sim N(0, \tilde{\tau}_j^2\lambda) \text{, with } \tilde{\tau}_j^2 = \frac{c^2 \tau_j^2}{c^2 + \lambda^2 \tau_j^2}\\
+\begin{align}
+\beta_{j} &\sim \text{DE}(0, \frac{s}{\lambda})\\ (\#eq:lasso)
+\lambda &\sim \chi^2(0, \nu_1)
+\end{align}
+where DE denotes the double exponential distribution centered around zero,
+with a scale determined by a global scale parameter $s$ that is multiplied by the inverse of tuning parameter $\lambda$.
+Increasing the scale parameter extends the prior to cover more extreme values.
+The inverse tuning parameter is estimated from the data 
+by assigning it a $\chi^2$ prior distribution with mean zero and degrees of freedom $\nu_1$ [@vanErpOberskiMulder2019].
+Increasing the degrees of freedom assigns greater probability mass to extreme values, resulting in less regularization.
+The present study used default values for the prior parameters,
+$s = 1$, $\nu_1 = 1$, as suggested by @vanErpOberskiMulder2019.
+
+The regularizing horseshoe prior combines global and local shrinkage of the regression coefficients with a finite slab that curtails the occurrence of very extreme values [@PiironenVehtari2017b].
+For regression coefficients $\beta_j$, for $j \in [1\ldots p]$ where $p$ is the total number of moderators,
+the regularizing horseshoe prior is given by:
+\begin{align}
+\beta_{j} &\sim N(0, \tilde{\tau}_j^2\lambda) \text{, with}\\ (\#eq:hs)
+\tilde{\tau}_j^2 &= \frac{c^2 \tau_j^2}{c^2 + \lambda^2 \tau_j^2}\\
 \lambda &\sim \text{student-}t^+(\nu_1, 0, \lambda^2_0)\\
@@
 c^2 &\sim \Gamma^{-1}(\frac{\nu_3}{2}, \frac{\nu_3 s^2}{2})
-\end{aligned}
-$$
-where $N$ denotes the normal distribution, student-$t^+$ denotes the half-t distribution and $\Gamma^{-1}$ denotes the inverse Gamma distribution. 
-In this formula, $\lambda^2_0$ is a global scale parameter that affects the overall shrinkage of the prior, with smaller values resulting in more shrinkage.
-In the present study, we assume a default value of $\lambda^2_0 = 1$.
+\end{align}
+Note that global shrinkage parameters, which are not subscripted, affect all regression coefficients.
+Local parameters are indicated by subscript $_j$, and affect each individual regression coefficient separately.
+In these equations, $N$ denotes the normal distribution,
+student-$t^+$ denotes the positive half of a t distribution,
+and $\Gamma^{-1}$ denotes the inverse Gamma distribution. 
+In this formula, $\lambda$ controls the overall scale of the priors for all regression coefficients,
+where larger values for the global scale parameter $\lambda^2_0$ widen the rande of values covered by the priors.
+The global degrees of freedom $\nu_1$ control the overall thickness of the tails,
+with higher values resulting in thinner tails, which assigning less probability mass to extreme values.
+Lighter tails can aid model convergence when the model is weakly identified; for example, when there are more moderators than observations.
+The prior $\tau_j$ controls the local shrinkage of specific regression coefficients;
+its scale is fixed, but its degrees of freedom $\nu_2$ control the incidence of extreme values in a similar way as $\nu_1$.
+A finite "slab" applies additional regularization to very large coefficients,
+which provides greater numerical stability of the model.
+This slab is governed by a degrees of freedom parameter $\nu_3$ and a scale parameter $s$.
+As before, increasing $\nu_3$ assigns less probability mass to extreme values.
+Increasing $s$ increases the range of values covered by the slab.
 
 <span id = "expectedmods">An attractive property of this shrinkage prior is that it can incorporate prior information regarding the expected number of relevant moderators.
-This is accomplished by having the scale of the global shrinkage parameter $\lambda^2_0$ depend on the expected number of relevant moderators $p_0$.
-The shrinkage parameter is then given by $\lambda^2_0 = \frac{p_0}{p-p_0}{\frac{\sigma}{\sqrt{n}}}$, where $p$ represents the total number of moderators, $\sigma$ is the residual standard deviation and $n$ equals the number of observations.</span>
+This is accomplished by calculating the scale of the global shrinkage parameter $\lambda^2_0$ based on the expected number of relevant moderators $p_{rel}$.
+The shrinkage parameter is then given by $\lambda^2_0 = \frac{p_{rel}}{p-p_{rel}}{\frac{\sigma}{\sqrt{n}}}$,
+where $\sigma$ is the residual standard deviation and $n$ equals the number of observations.</span>
+The present study used default values for the prior parameters, as
+proposed by its authors: $\lambda^2_0 = 1$, $\nu_1 = 1$, $\nu_2 = 1$, $\nu_3 = 4$, and $s = 2$ [@PiironenVehtari2017b].
+<!-- Check if s should be 2! -->
 <!-- SvE: nu twijfel ik toch weer of dit helemaal goed gaat.
@@
 -->
-The thickness of the tails is controlled by two degrees of freedom parameters, $\nu_1$ and $\nu_2$.
-In this study, we assume default values of 1 for these parameters.
-Increasing these degrees of freedom parameters results in a prior with lighter tails,
-which is, strictly speaking, no longer a horseshoe prior.
-However, in cases where the model is weakly identified, for example when there are more moderators than observations, these lighter tails can aid model convergence. 
-<span id = "thisextension">The regularizing horseshoe differs from the standard horseshoe by the addition of a finite "slab", which is governed by a degrees of freedom parameter ($\nu_3$, set to 4) and a scale parameter ($s$, set to 1).
-This slab ensures at least some regularization of large coefficients and as a consequence,
-results in greater numerical stability of the model parameters.</span>
 
@@
 [@gelmanPriorDistributionsVariance2006]:
-the half-Student's t distribution with large variance, $df = 3, scale = 2.5$.
+a half-Student's t distribution with large variance, 
+$\text{student-}t^+(3, 0, 2.5)$.
 Note that other relevant weakly informative priors have been discussed in the literature,
@@
 They thus differ from weakly informative priors,
-which merely guide the estimator towards possible values (e.g., by excluding negative values for the variance),
-or restrict it to plausible values to aid model convergence.
+which restrict the estimator towards possible values (e.g., by excluding negative values for the variance),
+or guide it towards plausible values to aid model convergence.
 BRMA takes a pragmatic approach to Bayesian analysis,
@@
 
-<!-- Eli? -->
-<!-- * Eli, kan jij het algemene principe van standardization hier uitleggen, met een paar referenties?
-In de volgende paragraaf over intercepts moet ook nog een referentie, over wel/niet standaardizeren van dummies.-->
-<!-- * In BRMA werk het als volgt: -->
-<!--     + By default, all variables are normalized. -->
-<!--     + The penalized model (without an intercept) is estimated on the normalized data -->
-<!--     + The intercept is then restored to the original scale by applying  -->
-<!--     $b_0 = b_{0z} - \mathbf{b}_z\frac{\bar{\mathbf{x}}}{\mathbf{s}_x}$ -->
-<!--     Where b_0 is the intercept, b_0z is the intercept for the normalized predictors, b_z is the vector of     regression coefficients for the normalized predictors, bar x is the vector of means of X, and s_x is the vector of standard deviations of x -->
-<!--     + The regression coefficients are restored to the original scale by applying  -->
-<!--     $\mathbf{b} = \mathbf{b}_z\mathbf{s}_x$ -->
-<!-- * Leg vervolgens uit dat mensen dummies misschien niet willen standaardizeren -->
-<!-- * Gebruikers kunnen de default standaardization overschrijven door een aantal van de variabelen handmatig te standaardizeren, en de vector met means en vector met SDs handmatig mee te geven via het argument `standardize = list(center = meanvec, scale = sdvec)`.
-Als ze een bepaalde variabele NIET willen standaardizeren moeten ze voor die variabele mean= 0 en sd= 1 meegeven.
--->
-
-Penalized regression analyses typically require the scales of predictors to be equivalent [@tibshirani1996].
-This is because regularization penalizes coefficients equally, without regard for their scale.
+As explained in Formula \@ref(eq:),
+regularization penalizes all coefficients equally,
+without regard for their scale.
 If variables are on different scales,
@@
 variables with smaller standard deviations are biased more strongly towards zero [@lee2015note].
-To clarify, a regression parameter $\beta$ can be interpreted as the expected increase in outcome $y$ for a one unit increase in predictor $x$.
-If the scale of predictor $x$ is increased by a factor 10, its regression coefficient is reduced by a factor 10.
-Standardization is a widely used method for equalizing predictor scales,
-in which the mean of all predictors is set to 0 and their standard deviation is set to 1 [@gelman2008scaling].
-BRMA performs standardization by default.
-
-After standardization, the estimated parameters can be restored to their original scales.
+If the scale of predictor $x$ is increased by a factor 10,
+its regression coefficient is reduced by a factor 10,
+bringing it closer to zero where it will be more affected by penalization.
+Standardization is a widely used method for equalizing predictor scales [@gelmanScalingRegressionInputs2008a].
+Standardization is a linear transformation that sets the mean of all predictors to 0 and their standard deviation to 1.
+Like most other regularizing methods,
+BRMA performs standardization by default [@tibshirani1996].
+After parameters are estimated using standardized variables,
+they can be restored to their original scales.
 For the intercept, the transformation is:
@@
 $$
+
 Note that standardization is not always necessary or desirable.
-If predictors are already on equivalent scales,
-standardization does not make scales more equal, nor the penalization more fair.
-<!--Alternatively, if the goal of a study is to compare results to prior findings based on unstandardized predictors, standardization would make penalization unequal across studies.-->
-
+Standardization is not necessary if predictors are already on equivalent scales,
+in which case penalization already affects them all equally.
 There are additional considerations regarding standardization of categorical predictors [@alkharusi2012categorical].
@@
 Extending this example to the multivariate case further complicates the problem [@wissmann2007role].
-
 The appropriate solution depends on the research goals;
@@
 However, if the primary goal is interpretation of the coefficients,
-they should not be [@gelman2008scaling].
-A related challenge is that, whereas various coding schemes for categorical predictors are equivalent in OLS regression, this is not the case in penalized regression.
-The choice of coding affects model fit and interpretation of the coefficients [@chiquet2016coding; @detmer2020note].
+they should not be [@gelmanScalingRegressionInputs2008a].
+A related challenge is that, whereas various coding schemes for categorical predictors are equivalent in standard linear regression,
+in penalized regression,
+the coding scheme does affect model fit and interpretation of the coefficients [@chiquet2016coding; @detmer2020note].
 
@@
 The regression coefficients of the dummy variables, $b_{1\ldots c}$, indicate the difference between the expected values of the reference category and of the category represented by the dummy.
-This so-called *regression specification* is useful when there is a meaningful reference category.
+This is useful when there is a meaningful reference category.
 For example, imagine a study on the effectiveness of interventions for specific phobia with two interventions: Treatment as usual, and a novel intervention.
@@
 and dummy-code the new contender.
-The intercept $b_0$ then represents the effect size of treatment as usual,
+The intercept $b_0$ then represents the average effect size of treatment as usual,
 and the effect of the dummy $b_1$ indicates whether the newly developed intervention has a significantly different effect size from treatment as usual.
@@
 For example, imagine a study on the effectiveness of one intervention for specific phobia in two continents.
-In this case, it makes more sense to estimate the average effect in both continents - in other words, to conduct a multi-group analysis.
+In this case, it makes more sense to estimate the average effect for all continents separately - in other words, to conduct a multi-group analysis.
 This is achieved by removing the intercept, and including all $c$ dummy variables.
-This so-called *ANOVA specification* of a model estimates a mean for all dummy-coded categories.
-In the context of standard linear regression, the regression specification and ANOVA specification are equivalent.
-This is not the case in regularized regression, however, because shrinkage may affect the intercept differently from the dummy variables.
+In the context of standard linear regression, both approaches are equivalent,
+but in regularized regression, shrinkage affects the intercept differently from the dummy variables.
 Consequently, a reasoned choice must be made about whether to include an intercept or not.</span>
@@
 
-We implemented BRMA in the function `brma()` in the statistical programming language R [@R-base],
-in the package `pema`, short for *pe*nalized *m*eta *a*nalysis [@R-pema].
-The `brma()` function aims to make Bayesian regularized regression readily available via a user-friendly interface.
-R-users can install the package from CRAN, by running `install.packages("pema")`.
-Non-R-users can use BRMA via a graphical user interface by selecting the menu option "Penalized Meta-Analysis" in the free, open source statistical program JASP [@JASP2022], see Figure \@ref(fig:figjasp).
+To facilitate adoption of the BRMA method in applied research,
+we have implemented it in two software packages.
+First, in the statistical programming language R [@rcoreteamLanguageEnvironmentStatistical2022].
+R-users can install the package `pema`,
+short for *pe*nalized *m*eta *a*nalysis, from CRAN by running `install.packages("pema")`.
+Second, non-R-users can use BRMA via a graphical interface in the free, open source statistical program JASP [@JASP2022] via the menu option "Penalized Meta-Analysis", see Figure \@ref(fig:figjasp).
 
@@
 
-For estimation, `brma()` depends on Stan, a probabilistic programming language that uses Hamiltonian Monte Carlo to sample from the posterior distribution [@StanManual].
+For estimation, `brma()` depends on Stan, a probabilistic programming language that uses Hamiltonian Monte Carlo to sample from the posterior distribution [@rstan].
 Stan is written in C++, and thus computationally efficient, but custom models must be compiled prior to estimation.
@@
 the `prior` argument is used to specify custom values for the prior hyperparameters (see Statistical underpinnings).
-The lasso prior uses Laplace priors, whose scale is determined by the `scale` parameter multiplied with a scale parameter,
-which in turn is assigned a chi-square prior distribution with `df` degrees of freedom.
-Increasing `df` allows for larger values for the inverse-tuning parameter, leading to less shrinkage.
-
-The horseshoe prior has several shrinkage parameters,
-all assigned Student's t prior distributions with parameters `df` and `scale`.
-The `df` parameter controls the thickness of the tails,
-with higher values corresponding to thinner tails, which assign less probability mass to extreme values.
-The `scale` parameter controls how wide the prior is;
-smaller values assign most probability mass to values near zero, thus resulting in more regularization.
-The parameters `df` and `scale` are local shrinkage parameters, enabling flexible shrinkage of separate regression coefficients.
-Parameters `df_global` and `scale_global` control global shrinkage that influences all coefficients similarly.
-The regularizing horseshoe applies additional regularization to very large coefficients,
-which is governed by parameters `df_slab` and `scale_slab`.
-This additional regularization ensures at least some shrinkage of large coefficients to avoid any sampling problems.
-When prior information regarding the expected number of relevant moderators is available,
-this information can be incorporated via the `relevant_pars` argument.
-The `scale_global` argument is then ignored and instead calculated based on `relevant_pars`.
-
-As explained before, standardization is an important step in Bayesian regularized meta-analysis.
+The parameters of the LASSO prior are explained in Equation \@ref(eq:lasso),
+and those of the regularizing horseshoe in Equation \@ref(eq:hs).
+Table \@ref(tab:tabprior) provides an overview of the arguments that can be passed to `prior` to control these parameters,
+along with a rudimentary description of the effect of increasing the value of each parameter.
+<!-- The default values in this table correspond to the values used for the present simulation study, and are based on prior research [@vanErpOberskiMulder2019; @PiironenVehtari2017a]. -->
+
+```{r tabprior, results='asis', eval = TRUE}
+tab <- read.csv("prior_table.csv", stringsAsFactors = FALSE)
+tab$Argument <- gsub("^`(.+?)`$", "\\\\texttt\\{\\1\\}", tab$Argument)
+papaja::apa_table(tab, escape = FALSE, caption = "Prior parameters and corresponding arguments, along with their default values and the effect of increasing their values.")
+```
+
+Standardization is an important step in Bayesian regularized meta-analysis,
+as explained before.
 By default, `brma()` standardizes the predictor matrix,
@@
 This can be accomplished using the argument `standardize = list(center = means, scale = sds)`.
-This approach can also be used to select predictors that **should not** be standardized:
-For these predictors,
+For predictors that should not be standardized,
 simply pass a mean of 0 and a standard deviation of 1;
@@
 Our research questions are whether BRMA offers a performance advantage over RMA in terms of any of these indicators,
-and which prior (regularizing horseshoe versus LASSO) is to be preferred.
+and which prior (LASSO versus regularizing horseshoe) is to be preferred.
+<span id = "defaultvalues">For both Bayesian priors, we used default values proposed in prior literature, see Table \@ref(tab:tabprior).
+Default values for the LASSO prior were based on @vanErpOberskiMulder2019,
+and default values for the regularizing horseshoe prior were based on @PiironenVehtari2017a.</span>
 All analysis code is available in a version-controlled repository at <https://github.com/cjvanlissa/pema>.
@@
 The number of cases in the training data vary according to the design factors of the simulation study.
-The number of cases in the testing data set was 100 for all replications.
-The models under evaluation (BRMA, RMA) are estimated on the training data,
+The number of cases in the testing data set was always 100.
+The models under evaluation (BRMA, RMA) were estimated on the training data,
 and used to predict cases in the testing data.
-Predictive performance was operationalized as the model's explained variance in the testing data, $R^2_{test}$, which is calculated as follows:
+Predictive performance was operationalized as the model's explained variance in the testing data, $R^2_{test}$, calculated as follows:
 $$
-R_{test}^{2} = 1- \frac{\sum_{i=1}^{k}(y_{i-test}-\hat{y}_{i-test})^{2}}{\sum_{i=1}^{k}(y_{i-test}-\bar{y}_{train})^{2}}
+R_{test}^{2} = 1- \frac{\sum_{i=1}^{k}(y_{i,test}-\hat{y}_{i,test})^{2}}{\sum_{i=1}^{k}(y_{i,test}-\bar{y}_{train})^{2}}
 $$
@@
 The ability to recover population parameters $\beta$ and $\tau^2$ was examined in terms of bias and variance of these estimates.
-The bias is given by the mean deviation of the estimate from the population value,
-and the variance is given by the variance of this deviation.
+The bias is given by the deviation of the estimate from the known population value,
+and the variance is given by the variance of this deviation across replications of the same simulation conditions.
 
@@
 The fourth design factor was the population effect size $\beta$ in the aforementioned models, with $\beta \in (0, .2, .5, .8)$. 
-Fifth, we manipulated the residual heterogeneity $\tau^2$ in the aforementioned models, with $\tau^{2} \in (.01, .04, .1)$.
+Fifth, we manipulated the residual heterogeneity $\tau^2$ in the aforementioned models, with $\tau^{2} \in (.01, .04, .10)$.
 According to a review of 705 published psychological meta-analyses (Van Erp et al., 2017),
@@
 <!-- This means that, in case of convergence  -->
-The RMA algorithm failed to converge in `r out$missing` cases.
-These cases were all characterized by low number of cases ($k \leq 40$) and high effect sizes $\beta \geq .5$.
+The RMA algorithm failed to converge in `r out$missing` replications,
+all characterized by low number of cases ($k \leq 40$) and high effect sizes $\beta \geq .5$.
 They were omitted from further analysis.
@@
 The difference between the two BRMA algorithms and RMA were largest for the design factor effect size $\beta$, followed by the model and number of studies $k$.
-Across all design factors, RMA had the highest sensitivity, followed by HS and then LASSO.
 For specificity, differences in sensitivity between HS and LASSO were largest for the number of noise moderators $M$, followed by the effect size $\beta$, number of studies $k$, and residual heterogeneity $\tau^2$.
 The difference between the two BRMA algorithms and RMA were largest for the design factor number of studies $k$, followed by the model, the number of noise moderators $M$, and the effect size $\beta$.
-Across all design factors, HS had the highest specificity, followed by LASSO and then RMA.
 Also note that the association between design factors and specificity was not monotonously positive or negative across algorithms.
@@
 If the value of the regression coefficient as estimated by one of the algorithms is $\hat{b}$,
-then the bias $B$ and variance $V$ of this estimate can be computed as the mean and variance of the difference between $\hat{b}$ and $\beta$ across simulation conditions, respectively.
+then the bias $B$ and variance $V$ of this estimate can be computed as $\hat{b}-\beta$,
+and as the variance of $\hat{b}$ across replications of the simulation for each unique combination of design factors, respectively.
 For the estimated regression coefficients,
@@
 The effect of the design factors on the bias in estimated $\beta$ was evaluated using ANOVAs.
-Table \@ref(tab:tabbeta) reports the effect size $\eta^{2}$ of simulation conditions on $\hat{b}-\beta$.
+Table \@ref(tab:tabbeta) reports the effect size $\eta^{2}$ of simulation conditions on the bias.
 The skewness of moderator variables had the largest effect on bias in estimated $\beta$ for all algorithms.
@@
 
-The variance of parameter estimates cannot be calculated on a case-by-case basis.
+<span id = "variancebeta">The variance of parameter estimates cannot be calculated on a case-by-case basis.
 Instead, it is calculated across replications for each simulation condition.
-Across simulation conditions, parameters estimated via HS had the lowest variance, $V_{HS} `r report(out[["beta_variance"]][["hs_beta1"]])`$, followed by LASSO, $B_{LASSO} `r report(out[["beta_variance"]][["lasso_beta1"]])`$,
-and then RMA, $B_{RMA} `r report(out[["beta_variance"]][["rma_beta1"]])`$.
+Across simulation conditions, parameters estimated via HS had the lowest variance, $V_{HS} `r report(out[["beta_variance"]][["hs_beta1"]])`$, followed by LASSO, $V_{LASSO} `r report(out[["beta_variance"]][["lasso_beta1"]])`$,
+and then RMA, $V_{RMA} `r report(out[["beta_variance"]][["rma_beta1"]])`$.
 Online [Supplemental Table S1]() provides an overview of the effect size of design factors on variance of the regression coefficients.
 Notably, the differences between algorithms are very small;
-the largest effect sizes were observed for the difference between HS and RMA in the effects of effect size, sample size, and model, all with $\eta^2 < 0.01$.
+the largest effect sizes were observed for the difference between HS and RMA in the effects of effect size, sample size, and model, all with $\eta^2 < 0.01$.</span>
 
@@
 
-The variance of the residual heterogeneity was calculated across replications for each simulation condition.
+<span id = "variancetau">The variance of the residual heterogeneity was calculated across replications for each simulation condition.
 The LASSO estimates of $\tau^2$ had the lowest variance, $V_{LASSO} `r report(out[["tau2_variance"]][["lasso_tau2"]])`$, 
 followed by HS, $V_{HS} `r report(out[["tau2_variance"]][["hs_tau2"]])`$,
-and then RMA, $B_{RMA} `r report(out[["tau2_variance"]][["rma_tau2"]])`$.
+and then RMA, $V_{RMA} `r report(out[["tau2_variance"]][["rma_tau2"]])`$.
 Online [Supplemental Table S2]() provides an overview of the effect size of design factors on variance of the residual heterogeneity.
-All differences between algorithms were small, $\eta^2 \leq 0.002$.
+All differences between algorithms were small, $\eta^2 \leq 0.002$.</span>
 
@@
 
-In this application, we will work with the `bonapersona` data [@BonapersonaEtal2019].
-This meta-analysis of over 400 experiments investigated the effects of early life adversity on cognitive performance in rodents.
-This example uses a small subset of the more than 30 moderators.
+This example uses the `bonapersona` data, which were included in the `pema` package with permission of the author [@bonapersonaBehavioralPhenotypeEarly2019].
+<span id = "sample400">This meta-analysis of over 400 experiments investigated the effects of early life adversity on cognitive performance in rodents.
+Note that the sample is much larger than the maximum used to validate BRMA in our simulation study.
+As larger samples provide greater statistical power,
+it should also be valid for this sample.</span>
+For illustrative purposes, we use a smaller subset of the more than 30 moderators.
 See the `pema` package documentation (help and vignettes) for further examples.
@@
 
-```{r exdata, eval = TRUE}
+```{r exdata, eval = FALSE, echo = TRUE}
 # Load relevant packages
 library(pema)
+library(mice)
+library(rstan)
+library(ggplot2)
 # Select data to analyze
-df <- bonapersona[ , c("yi", "vi", "mTimeLength", "year", "model", "ageWeek")] 
-# Impute missings
-df$ageWeek[is.na(df$ageWeek)] <- median(df$ageWeek, na.rm = TRUE)
-```
-
-Our simulation study shows good performance with default hyperparameters.
-However, experienced users may want to customize the prior.
-Visualizing the prior can be helpful in this process.
-This is accomplished using the interactive application visualization application available through `shiny_prior()`.
-The user can plot the prior distributions resulting from different sets of hyperparameters and compare them.
-Increasing the values of the scale parameters (`scale_global` and `hs_scale_slab`) results in a more spread out prior, which applies less regularization.
-Increasing the degrees of freedom (`df_global` and `df_slab`) results in thinner tails, which applies more regularization.
+df <- bonapersona[ , c("yi", "vi", "mTimeLength",
+                       "year", "model", "ageWeek")] 
+# Multiple imputation for missing values
+df <- mice(df)
+```
+```{r, eval = run_everything, echo = FALSE}
+# Load relevant packages
+library(pema)
+library(mice)
+library(rstan)
+library(ggplot2)
+# Select data to analyze
+df <- bonapersona[ , c("yi", "vi", "mTimeLength",
+                       "year", "model", "ageWeek")] 
+# Multiple imputation for missing values
+df <- mice(df)
+saveRDS(df, "df_imputed.RData")
+```
+```{r, eval = !run_everything, echo = FALSE}
+# Load relevant packages
+library(pema)
+library(mice)
+library(rstan)
+library(ggplot2)
+df <- readRDS("df_imputed.RData")
+```
+<!-- Our simulation study shows good performance with default hyperparameters. -->
+<!-- However, experienced users may want to customize the prior. -->
+<!-- Visualizing the prior can be helpful in this process. -->
+<!-- This is accomplished using the interactive application visualization application available through `shiny_prior()`. -->
+<!-- The user can plot the prior distributions resulting from different sets of hyperparameters and compare them. -->
+<!-- Increasing the values of the scale parameters (`scale_global` and `hs_scale_slab`) results in a more spread out prior, which applies less regularization. -->
+<!-- Increasing the degrees of freedom (`df_global` and `df_slab`) results in thinner tails, which applies more regularization. -->
 <!-- One advantage of the regularizing horseshoe prior is its ability to define the prior in terms of the expected number of nonzero coefficients, using the argument `relevant_pars`. -->
@@
 
-As no prior is specified, this example uses a horseshoe prior with default hyperparameters.
-To see the default values, open the function documentation using `?brma`.
-
+First, we estimate a model with all default settings.
+Based on the results of the present simulation study, the regularizing horseshoe is the default prior.
+To see all default values, open the function documentation using `?brma`.
+The use of a random seed makes this example reproducible:
 ```{r exmodel1, echo = TRUE, eval = FALSE}
-fit <- brma(yi ~ ., data = df, vi = "vi")
+fit <- brma(yi ~ ., data = df, vi = "vi", seed = 1)
 ```
 ```{r, echo = FALSE, eval = run_everything}
-fit <- brma(yi ~ ., data = df, vi = "vi")
+fit <- brma(yi ~ ., data = df, vi = "vi", seed = 1)
 saveRDS(fit, "fit.RData")
@@
 ```
-
-By running `summary(fit)`, we obtain the posterior mean, standard deviation, and quantiles of the model parameters (see Table \@ref(tab:tabsumex)).
+Running `summary(fit)` returns the posterior mean, standard deviation, and quantiles of the model parameters (see Table \@ref(tab:tabsumex)).
 Use the posterior mean or median (50% quantile) and 95% credible interval (2.5% - 97.5%) to perform inference on model parameters.
@@
 given the prior and observed data.
-In this example, however, there are no moderators for which the 95\% CI excludes zero.
+In this example, there are no moderators for which the 95\% CI excludes zero.
+The residual heterogeneity, however, does exceed zero.
+The `brma()` function builds upon the `rstan` package,
+and its output is backwards compatible.
+A `brma` model can be converted to a `stanfit` object via `as.stan(fit)`.
+This makes it possible to benefit from the many existing convenience functions for `rstan` models.
+For example, it is possible to get a HPDI interval for the residual heterogeneity by running `bayestestR::hdi(as.stan(fit), parameters = "tau2")`.
+There are also many plotting functions for `stanfit` objects;
+for example, one can plot the model parameters using `plot(as.stan(fit), plotfun = "dens", pars = c("Intercept", "year"))`.
+
+Before interpreting the results, however,
+it is important to assess model convergence.
+If any indication of non-convergence is detected during estimation,
+a warning will be printed.
+The example returns the warning that there were 331 divergent transitions,
+and suggests increasing the number of iteractions (increasing the argument `iter` beyond its default value of 2000).
+Divergent transitions can result in biased estimates.
+If the number of divergences is small and there are no further indications of non-convergence, however,
+the posterior distribution is often good enough to safely interpret the results.
+We can examine two parameter-specific indicators of convergence
+by ascertaining that the number of "unique" samples from the posterior `n_eff` for each parameter is sufficiently high,
+and that the different chains of the estimator have mixed properly, as indicated by `Rhat` close to 1.
+The number of effective (independent) MCMC samples should be high relative to the total number of samples (in this case, 4000, as we used 2000 iterations on a dual-core processor).
+If the effective sample size is less than 10% of the total,
+there may be a problem - which is not the case here.
+The `Rhat` is a version of the potential scale reduction factor,
+which represents the ratio of between- and within-chain variance [@GelmanRubin1992].
+If the chains mixed well, the `Rhat` should be close to 1.
+Both `n_eff` and `Rhat` indicate convergence in this example.
+Additional convergence diagnostics are obtained by running `check_hmc_diagnostics(as.stan(fit))`.
+Convergence can also be assessed visually using the function `traceplot(as.stan(fit), pars = c("Intercept", "year"))`,
+which provides trace plots for the MCMC draws.
+If the model converged, the traces of the different chains should mix well (i.e., overlap) and look like "fat caterpillars".
 
@@
 ```
-Many additional convenience functions exist for `rstan` models,
-which become available by converting a `brma` model object to a `stanfit` object,
-using the function `as.stan(fit)`.
-This makes it possible to plot the model parameters instead of tabulating them,
-using the `plot()` function.
-For example, one can obtain posterior density plots for parameters using `plot(as.stan(fit), plotfun = "dens", pars = c("Intercept", "year"))`.
-
+<!-- , see Figure \@ref(fig:figexres) -->
 ```{r exres, eval = FALSE, echo = FALSE}
@@
 ```
-```{r, eval = FALSE, echo = FALSE, fig.cap="Visual presentation of model parameters for the applied example."}
+```{r figexres, eval = FALSE, echo = FALSE, fig.cap="Visual presentation of model parameters for the applied example."}
 knitr::include_graphics("plot_es.png")
 ```
-
-It is good practice to assess model convergence.
-For example, the analysis above returns a warning about "divergent transitions".
-Converting to a `stanfit` object also facilitates convergence diagnostics;
-for example, using the function `check_hmc_diagnostics(as.stan(fit))`.
-Additionally, the MCMC draws can be visualized using `traceplot(as.stan(fit), pars = c("Intercept", "year"))`.
-The traces of a converged model look like "fat caterpillars",
-with the different MCMC chains mixing together.
 <!-- Note that there are many auxiliary parameters used for the regularizing horseshoe prior.
@@
 
-The model summary also offers convergence diagnostics.
-For example, the column `Rhat` provides information on the split $\hat{R}$,
-a version of the potential scale reduction factor [PSRF, @GelmanRubin1992].
-Values close to 1 indicate convergence.
-In addition, the column `n_eff` provides information on the number of effective (independent) MCMC samples, which should be high relative to the total number of samples (in this case, 4000).
-In this example, all `Rhat` values are close to 1.
-The effective number of MCMC samples is relatively small compared to the total number of MCMC samples.
-An often used heuristic is to consider ratios smaller than 0.1 as problematic.
-<!-- Even though this is not the case here, consider increasing the number of MCMC iterations. -->
-<!-- These diagnostics can be easily visualized using the `bayesplot` package: -->
-Both statistics indicate convergence in this example.
-
-As mentioned before, this analysis results in a warning message about divergent transitions.
-Divergent transitions can result in biased estimates.
-However, the posterior distribution is often good enough to safely interpret the results if the number of divergences is small and there are no further indications of non-convergence.
-In some cases, divergent transitions may be resolved by increasing the degrees of freedom of the prior.
-Increasing both `df_global` and `df_slab` to 5 results in fewer divergences for this example,
-but does not otherwise influence the substantive interpretation of the results.
-It is prudent to perform similar sensitivity analyses to determine whether results are robust to different priors.
-
-```{r exmodel2, eval = FALSE, echo = F}
-fit2 <- brma(yi ~ .,
-             data = df,
-             vi = "vi",
-             prior = c(df = 5, df_global = 5, df_slab = 4,
-                       scale_global = 1, scale_slab = 1,
-                       relevant_pars = NULL))
+As explained in the section on Bayesian estimation,
+model convergence can be aided by increasing the amount of regularization of the prior, for example, by increasing some of the `df` parameters (see code below).
+In this example, increasing both `df` and `df_slab` to 5 results in only 96 divergences, compared to the original 331.
+This can be verified by running `summary(fit2)`.
+In general, it is prudent to perform similar sensitivity analyses to determine how robust the results are to different priors.
+For a visual inspection of the difference in posterior distributions,
+use the function `plot_sensitivity()`, see Figure \@ref(fig:figsens).
+
+```{r exmodel2, eval = FALSE, echo = TRUE}
+fit2 <- brma(yi ~ ., data = df, vi = "vi",
+             prior = c("df_global" = 5, "df" = 5),
+             seed = 1)
+plot_sensitivity(fit, fit2) + coord_cartesian(xlim = c(-3, 3))
 ```
 ```{r, echo = FALSE, eval = FALSE}
-fit2 <- brma(yi ~ .,
-                data = df,
-                vi = "vi",
-                prior = c(df = 5, df_global = 5, df_slab = 4, scale_global = 1, scale_slab = 1, relevant_pars = NULL))
+fit2 <- brma(yi ~ ., data = df, vi = "vi",
+             prior = c("df_global" = 5, "df" = 5),
+             seed = 1)
 saveRDS(fit2, "fit2.RData")
-```
-```{r, echo = FALSE, eval = FALSE}
-fit2 <- readRDS("fit2.RData")
+p <- plot_sensitivity(fit, fit2) + coord_cartesian(xlim = c(-3, 3))
+ggsave("plot_sensitivity.png", p, device = "png", units = "mm", width = 105, height = 60)
+```
+```{r figsens, echo = FALSE, eval = TRUE, fig.cap="A rudimentary visual check for sensitivity to different priors."}
+knitr::include_graphics("plot_sensitivity.png")
 ```
@@
 <!-- one can run the model with a different prior. -->
-<!-- In this example, we vary the expected number of relevant moderators `relevant_pars`.  -->
+<!-- In this example, we vary the expected number of relevant moderators `relevant_pars`, all other prior parameters are equal to their default values: -->
 
 ```{r expriorsens, eval = FALSE, echo = FALSE}
-fit3 <- brma(yi ~ .,
-                data = datdum,
+fit_sens <- brma(yi ~ .,
+                data = df,
                 vi = "vi",
-                method = "hs",
-                standardize = FALSE,
-                prior = c(df = 1, df_global = 1, df_slab = 4, scale_global = 1, scale_slab = 1, relevant_pars = 1),
-                mute_stan = FALSE)
-
+                prior = c(df = 1, df_global = 5,
+                          df_slab = 5, scale_global = 1,
+                          scale_slab = 1, relevant_pars = NULL))
+```
+
+```{r echo = FALSE, eval = FALSE}
 fit4 <- brma(yi ~ .,
@@
                 standardize = FALSE,
-                prior = c(df = 1, df_global = 1, df_slab = 4, scale_global = 1, scale_slab = 1, relevant_pars = 3),
+                prior = c(df = 1, df_global = 5, df_slab = 5, scale_global = 1, scale_slab = 1, relevant_pars = NULL),
                 mute_stan = FALSE)
@@
 df3 <- df.fun(fit3, prior = "hs with p0 = 1")
-df4 <- df.fun(fit4, prior = "hs with p0 = 3")
+df2 <- df.fun(fit2, prior = "hs with p0 = 4")
 df5 <- df.fun(fit5, prior = "hs with p0 = 6")
 
-df <- rbind.data.frame(df1, df3, df4, df5)
-df$par <- as.factor(df$par)
-plotdat <- filter(df, !par %in% c("Intercept", "tau2"))
+df_plot <- rbind.data.frame(df1, df3, df2)
+df_plot$par <- as.factor(df_plot$par)
+plotdat <- filter(df_plot, !par %in% c("Intercept", "tau2"))
 
@@
 This study presented a novel algorithm to select relevant moderators that can explain heterogeneity in meta-analyses, using Bayesian shrinkage priors. 
-The simulation study validated the performance of two versions of the new BRMA algorithm, relative to state-of-the-art meta-regression (RMA).
+A simulation study validated the performance of two versions of the BRMA algorithm, with a regularizing horseshoe prior and LASSO prior, relative to state-of-the-art meta-regression with restricted maximum likelihood estimation (RMA).
 Our analyses examined the algorithms' predictive performance, which is a measure of generalizability,
 their ability to perform variable selection,
-and their ability to recover population parameters.
+and ability to recover population parameters.
 Our research questions were whether BRMA offers a performance advantage over RMA in terms of any of these indicators,
@@
 Results indicated that the BRMA algorithms had higher predictive performance than RMA in the presence of relevant moderators.
-In the absence of relevant moderators, RMA produced overfit models; in other words, its models generalized poorly to new data.
-The predictive performance of the BRMA algorithms also suffered less than that of RMA in the presence of more irrelevant moderators.
+In the absence of relevant moderators, BRMA showed less evidence of overfitting than RMA models.
+In these cases, RMA models had, on average, negative predictive performance, which suggests that these models generalize poorly to new data.
+In the presence of an increasing number of irrelevant moderators, the BRMA algorithms' predictive performance also suffered less than that of RMA.
 The BRMA algorithms were also more efficient, in the sense that they achieved greater predictive performance when the number of studies in the training data was low.
@@
 
-With regard to variable selection, results indicated that the penalized BRMA algorithms had lower sensitivity: they were less able to select relevant moderators than RMA.
-Conversely, the BRMA algorithms had better specificity: they were better able to reject irrelevant moderators than RMA.
-These results are unsurprising because the BRMA algorithms shrink all regression coefficients towards zero.
-This diminishes their ability to detect true effects and aids their ability to reject irrelevant moderators.
-Importantly however, the overall accuracy was approximately equal for RMA and BRMA with a horseshoe prior.
+With regard to variable selection, on the one hand, results indicated that the penalized BRMA algorithms had lower sensitivity:
+they were less able to select relevant moderators than RMA.
+On the other hand, the BRMA algorithms had higher specificity:
+they were better able to reject irrelevant moderators than RMA.
+Importantly, the overall accuracy was approximately equal for RMA and BRMA with a horseshoe prior.
 This means that the total number of Type I and Type II errors will be approximately the same when choosing between these two methods - but there is a tradeoff between sensitivity and specificity.
-Applied researchers must consider whether sensitivity or specificity is more important in the context of their research.
-When meta-analyzing a heterogeneous body of literature, with many between-study differences that could be coded as moderators, BRMA may be preferred due to its greater ability to retain only relevant moderators.
-Conversely, when meta-analyzing a highly curated body of literature with a small number of theoretically relevant moderators, un-penalized RMA might be preferred.
+Applied researchers must consider which is more important in the context of their research.
+When meta-analyzing a heterogeneous body of literature with many between-study differences, BRMA may be preferred due to its greater ability to exclude irrelevant moderators.
+Conversely, when meta-analyzing a highly curated body of literature with a small number of theoretically relevant moderators,
+RMA might be preferred.
 
@@
 we observed that BRMA with a horseshoe prior had the greatest bias towards zero across simulation conditions, followed by LASSO, and then RMA.
-Note that all algorithms provided, on average, negatively biased estimates.
-The variance of the estimates followed the opposite pattern.
-This illustrates the bias-variance trade-off,
-of which the BRMA algorithms' greater predictive performance is a direct consequence.
-
-With regard to residual heterogeneity, we observed that BRMA with a horseshoe prior had the lowest bias.
+Surprisingly, all algorithms - including RMA - provided, on average, negatively biased estimates.
+The variance of the estimates followed the opposite pattern,
+which illustrates the bias-variance trade-off.
+With regard to residual heterogeneity, BRMA with a horseshoe prior had the lowest bias.
 The BRMA algorithms also had lower variance.
@@
 
-We examined the effect of several violations of model assumptions, including simulating data from a cubic model.
-In applied research, it is often not known what the true shape of the association between a moderator and effect size is.
+We examined the effect of violations of the assumption of linearity by simulating data from a cubic model.
+In applied research, the true shape of the association between a moderator and effect size is typically unknown.
 Thus, model misspecification is likely to occur.
@@
 For example, researchers could add polynomials of continuous variables with suspected non-linear effects, or interactions between predictors.
-If nothing is known about the shape of the associations between moderators and effect size,
-non-parametric methods like random forest meta-analysis may be preferable over linear models [@vanlissaSmallSampleMetaanalyses2020].
-
-<span id = "sensitivityanalysis">All simulations were conducted with default settings for the model's prior distributions.
+Another possible solution is to resort to non-parametric methods like random forest meta-analysis, which intrinsically accommodates non-linear effects and interactions [@vanlissaSmallSampleMetaanalyses2020].
+
+<span id = "sensitivityanalysis">All simulations were conducted with default settings for the model's prior distributions, based on prior research [@vanErpOberskiMulder2019; @PiironenVehtari2017b].
 Our results suggest that these defaults are suitable for a wide range of situations, including when model assumptions are violated.
@@
 Another strength is that the present simulation study used realistic estimates of $\tau^2$,
-based on data from 705 published psychological meta-analyses (Van Erp et al., 2017).
-Another strength is that the BRMA algorithms have been made available in a FAIR (Findable, Accessible, Interoperable and Reusable) repository: an R-package published on the "Comprehensive R Archive Network".
+based on data from 705 published psychological meta-analyses [@vanerpEstimatesBetweenStudyHeterogeneity2017].
+Another strength is that the BRMA algorithms have been implemented in FAIR software (Findable, Accessible, Interoperable and Reusable): the R-package is published on the "Comprehensive R Archive Network", and the source code is hosted on GitHub.
 Thanks to the use of compiled code, the BRMA algorithm is computationally relatively inexpensive.
@@
 To facilitate further exploration and follow-up research,
-we have made all simulation data and analysis code for the present study available online.
-This code can also be used to conduct Monte Carlo power analyses for applied research.
+all simulation data and analysis code are available online.
+This code can also be adapted to conduct Monte Carlo power analyses for applied research.
 A second limitation is that the present study did not examine the effect of multicollinear predictors.
-Regularizing estimators typically have an advantage over OLS regression in the presence of multicollinearity;
+Regularizing estimators ought to have an advantage over OLS regression in the presence of multicollinearity [@hiltRidgeComputerProgram1977];
 future research ought to examine whether this advantage extends to BRMA.
@@
 The BRMA algorithm can accommodate dependent data by means of three-level multilevel analysis.
-To our knowledge, there are no reasons to expect that dependent data would result in a different pattern of findings than we found for independent data, but future research is required to ascertain this.
+To our knowledge, there is no reason to expect that dependent data would result in a different pattern of findings than we found for independent data, but future research is required to ascertain this.
 A final limitation of the current implementation is that it relies on 95% credible intervals to select relevant moderators.
@@
 
-BRMA aims to address the challenge that arises when meta-analyzing heterogeneous bodies of literature, with few studies relative to the number of moderators.
-BRMA can be used to identify relevant moderators when it is not known beforehand which moderators are responsible for between-studies differences in observed effect sizes.
-To facilitate adoption of this method in applied research, we have published the function `brma()` in the R package `pema`.
-Here, we offer several recommendations for its use.
-The first recommendation precedes analysis, and relates to
-the design of the meta-analysis.
-When the search for moderators is exploratory,
-researchers ought to be inclusive, but focus on moderators that are expected to be
-relevant, including theoretically relevant moderators, as well as moderators pertaining
-to the sample, methods, instruments, study quality, and publication type.
-In our experience, many applied researchers code such study characteristics anyway, but omit
-them from their analyses for lack of statistical power.
-Moderators can be continuous or categorical.
-Missing data must be accounted for.
-The best way to do so is by retrieving the missing information, by contacting authors or comparing different publications on the same data.
-If missing data remains, users can either use a single imputation method
-or supply multiple imputed data to the `data` argument (see function documentation).
-The effect sizes and their variances must be computed using suitable methods;
-note that many such methods are available in the R package `metafor` [@viechtbauerConductingMetaanalysesMetafor2010].
-With regard to data analysis, we recommend the use of a horseshoe prior by default,
-because it demonstrated the best predictive performance and most attractive trade-off between sensitivity and specificity in our simulations.
-When estimating the model, it is important to ascertain that the algorithm has converged before interpreting the results.
-Stan, the computational back-end of `brma()`, returns warnings and errors if there are any indications of non-convergence.
-Additionally, users can obtain trace plots as described in the illustrative example.
-
-When reporting results, researchers should substantiate their decision to explore heterogeneity on both subjective and objective grounds.
-The former can be achieved by simply ascertaining that the body of literature
-to be meta-analyzed appears to be heterogeneous;
-the same rationale commonly used to support the use of random effects meta-analysis (Higgins et al., 2009).
-The latter can be accomplished by conducting a random effects meta-analysis without any moderators,
-and reporting the estimated $\tau^2$.
-Note that significant heterogeneity does not constitute
-sufficient grounds, for deciding to explore ignore heterogeneity, for two reasons:
-Firstly, because data-driven decisions render any analysis (partly) exploratory, and increase the risk of results that generalize poorly (i.e., are overfit).
-The second reason is that tests for heterogeneity are often underpowered when the number of studies is low, and overpowered when it is high, thus limiting their usefulness (see Higgins & Thompson, 2002).
-As when conducting RMA meta-analysis, researchers should report both the estimated effect of moderators and residual heterogeneity.
-Regression coefficients can be interpreted as usual, but it is recommended that researchers acknowledge that they are biased towards zero.
-If all moderators are centered, the model intercept can be interpreted as the overall effect size at average levels of the moderators.
-Note that, as BRMA is a Bayesian method, credible intervals or highest posterior density intervals should be used for inference, instead of p-values.
+<span id = "metareglimits">Before conducting meta-regression,
+researchers should be aware of its limitations [see @thompsonHowShouldMetaregression2002].
+These can be subdivided into four categories: 1) the curse of dimensionality and its corrolary implications for multicolinearity; 2) the ecological fallacy; 3) limited information on moderator variables, including missing data and restrictions of range.
+BRMA seeks to address the first of these limitations,
+because the problems that arise from meta-analyzing small and heterogeneous bodies of literature are so ubiquitous that they have been referred to as the primary pitfall in meta-regression [@thompsonHowShouldMetaregression2002].
+Nonetheless, all applicable limitations should be acknowledged in the resulting publication.</span>
+
+With regard to the planning and design of a BRMA meta-analysis, consider explicitly mentioning the intended use of BRMA in a preregistered analysis protocol - either as primary analysis technique, or as a contingency in the case of model non-convergence or multicollinearity.
+Note that BRMA is suitable for both confirmatory hypothesis tests and for exploratory analyses to ensure that no important effects were missed.
+Both approaches can be included in a preregistration [see @vanlissaComplementingPreregisteredConfirmatory2022].
+With regard to data extraction,
+it is important to strike a balance between inclusiveness and selectivity when coding moderators [@thompsonHowShouldMetaregression2002].
+Moderators may include theoretically relevant factors and methodological ones, such as sample demographics, methods, instruments, study quality, and publication type.
+A key challenge is that moderators may not always be reported.
+The best way to handle missing data is by recovering the relevant information
+by contacting authors or comparing different publications on the same data.
+If data remains missing, users can use multiple imputation, which is a best practice for handling missingness (see Applied example).
+Finally, effect sizes and their variances must be computed using suitable methods;
+many of which are available in the R package `metafor` [@viechtbauerConductingMetaanalysesMetafor2010].
+
+In the Introduction, researchers should substantiate the decision to explore heterogeneity
+One valid reason is prima facie heterogeneity of the body of research [@higginsReevaluationRandomeffectsMetaanalysis2009a].
+Another reason is the presence of theoretically relevant moderators [@thompsonHowShouldMetaregression2002].
+Less convincing is the practice of exploring heterogeneity only when $\tau^2$ is significant,
+for two reasons:
+Firstly, because data-driven analysis decisions increase the risk of spurious findings [@zhangInferenceVariableSelection1992].
+Secondly, because tests for heterogeneity are often underpowered when the number of studies is low, and overpowered when it is high, thus limiting their usefulness [@higginsQuantifyingHeterogeneityMetaanalysis2002].
+
+With regard to data analysis,
+our simulation study indicates that a horseshoe prior is a suitable default.
+Before interpreting model parameters, one must ascertain that the algorithm has converged.
+Additionally, authors may consider performing a sensitivity analysis to examine whether findings are robust to different prior specifications.
+With regard to reporting results,
+researchers should report both the estimated effect of moderators and residual heterogeneity.
+In interpreting the regression coefficients,
+it should be explicitly acknowledged that regularization was used, and the parameters may thus be biased.
+The use of standardization and inclusion of an intercept should be reported and substantiated.
+As BRMA is a Bayesian method, inference is based on probability intervals instead of p-values.
 The null hypothesis is rejected if such intervals exclude zero.
-As both types of intervals performed identically in the present study,
-we suggest using credible intervals, which are computationally less expensive.
-
-Finally, with regard to publication, we highly recommend making the data and code for the meta-analysis publicly available.
+The present study compared credible intervals and HDPI intervals.
+Both performed identically for inference on regression coefficients.
+By default, `brma()` reports credible intervals - but HDPI intervals might be preferable for residual heterogeneity (which has a non-normal posterior distribution).
+
+With regard to publication, we highly recommend making the data and code for the meta-analysis publicly available.
 One way to do this is by creating a reproducible research repository,
-for example, using the Workflow for Reproducible Code in Science [WORCS, @vanlissaWORCSWorkflowOpen2020].
+for example, using the Workflow for Reproducible Code in Science [WORCS, @vanlissaWORCSWorkflowOpen2021].
 Transparency allows readers and reviewers to verify that methods were correctly applied,
-which should inspire greater confidence in the results.
+which bolsters confidence in the results.
 Others can easily perform sensitivity analyses by changing the analysis code.
 Sharing data allows the meta-analysis to be updated in the future,
-which increases the reuse value of the data.
+which increases its reuse value.
 Finally, sharing the model object (or code to reproduce it) allows others to obtain predictions for the expected effect size of a new study on the same topic.
-This prediction can be used to conduct power analysis for future research.
+These predictions can be used to conduct power analysis for future research.
 To this end, researchers can simply enter their planned
@@
 Several trade-offs must be considered to decide what method is most appropriate.
-Firstly, the fact that BRMA has high predictive performance compared to RMA suggests that it is particularly suitable when a researcher intends to obtain results that will generalize beyond the sample at hand,
-and is willing to accept some bias in parameter estimates.
-Conversely, RMA might be more suitable when the goal is to describe the sample at hand in an unbiased manner,
+Firstly, BRMA has higher predictive performance than RMA,
+which implies that it is more suitable when a researcher intends to generalize beyond the sample at hand.
+Conversely, RMA is be more suitable when the goal is to describe the sample at hand in an unbiased manner,
 with less concern for generalizability to future studies.
-Secondly, the fact that BRMA has high specificity compared to RMA suggests that it is more suitable when a researcher seeks to eliminate irrelevant moderators at the cost of increasing the Type II error rate.
-Conversely, RMA might be more suitable when the researcher seeks to identify relevant moderators, at the cost of increasing the Type I error rate.
-If many moderators have been coded, and many of them are expected to be irrelevant, then BRMA may thus be preferable.
+Secondly, BRMA trades off higher specificity for lower sensitivity compared to RMA,
+which suggests that it is more suitable when a researcher seeks to eliminate irrelevant moderators, at the cost of an increased Type II error rate.
+RMA might be more suitable when the researcher seeks to identify relevant moderators, at the cost of a greater Type I error rate.
+If many moderators are expected to be irrelevant,
+then BRMA may thus be preferable.
 Thirdly, there may be pragmatic reasons for preferring BRMA over RMA.
@@
 RMA models may be empirically under-identified.
-This can be indicated by convergence problems.
+This can result in convergence problems.
 In such cases, Bayesian estimation may converge on a solution where frequentist estimation does not [@kohliFittingLinearLinearPiecewise2015].
@@
 BRMA may have an advantage here, because the regularizing priors restrict variance.
-If multicollinearity is observed, researchers might thus prefer BRMA over RMA.
+If multicollinearity is observed or suspected, BRMA might be preferred.
 
@@
 Most applied researchers are familiar with the linear model, and it can easily accommodate predictor variables of any measurement level, interaction terms, and non-linear effects.
-Adoption of this new method may be further facilitated by the availability of the user-friendly R package `pema`.
+Adoption of this new method is facilitated by the availability of user-friendly software in `R` and `JASP`.
 
@@
 * The present study introduces Bayesian Regularized Meta-Analysis (BRMA), an algorithm that applies regularization to identify relevant moderators from a larger number of candidates.
-* The algorithm is made available in a user-friendly R-package, `pema`, which is published on CRAN.
+* The algorithm is available via the R-package `pema` on CRAN, and via a user-friendly graphical interface in JASP.
 * Readers across fields can use this method to account for between-studies heterogeneity in meta-analysis, without concern that models may be underfit or underpowered.

### 2022-11-28 R/brma.R

@@ -19,8 +19,8 @@
 #' a factor. This column will be removed from the data prior to analysis.
 #' See \code{Details} for more information about analyzing dependent data.
 #' @param method Character, indicating the type of regularizing prior to use.
-#' Supports one of \code{c("lasso", "hs")}, see Details. Defaults to
-#' \code{"lasso"}.
+#' Supports one of \code{c("hs", "lasso")}, see Details. Defaults to
+#' \code{"hs"}.
 #' @param standardize Either a logical argument or a list. If `standardize` is
 #' logical, it controls whether all predictors are standardized prior to
 #' analysis or not. Parameter estimates are restored to the predictors' original
@@ -159,7 +159,7 @@ brma.formula <-
            standardize = TRUE,
            prior = switch(method,
                           "lasso" = c(df = 1, scale = 1),
-                          "hs" = c(df = 1, df_global = 1, df_slab = 4, scale_global = 1, scale_slab = 1, relevant_pars = NULL)),
+                          "hs" = c(df = 1, df_global = 1, df_slab = 4, scale_global = 1, scale_slab = 2, relevant_pars = NULL)),
            mute_stan = TRUE,
            #prior_only = FALSE,
            ...) {
@@ -223,7 +223,7 @@ brma.formula <-
       standardize <- standardize[c("center", "scale")]
     }
 
-    cl[names(cl) %in% c("formula", "data", "method")] <- NULL
+    cl[names(cl) %in% c("formula", "data")] <- NULL
     cl[[1L]] <- str2lang("pema::brma")
     cl[["x"]] <- X
     cl[["y"]] <- Y
@@ -251,9 +251,10 @@ brma.default <-
            y,
            vi,
            study = NULL,
+           method = "hs",
+           standardize,
            prior,
            mute_stan = TRUE,
-           standardize,
            intercept,
            #prior_only = FALSE,
            ...) {
@@ -271,24 +272,36 @@ brma.default <-
       foroutput <- NULL
     }
     # Check validity of prior
-    method <- "invalid"
     if(is.null(ncol(X))) stop("Object 'X' must be a matrix.")
     if(dim(X)[2] == 0) stop("The function 'brma()' performs moderator selection, but this model does not include any moderators.")
-    if(all(c("df", "df_global", "df_slab", "scale_slab") %in% names(prior))){
-      if("par_ratio" %in% names(prior)){
-        message("Prior element 'par_ratio' is deprecated and will be ignored. Use 'relevant_pars' instead.")
-      }
[…]

### 2022-11-28 R/plot_sensitivity.R

@@ -1,0 +1,80 @@
+#' @title Plot posterior distributions for BRMA models
+#' @description To perform a rudimentary sensitivity analysis,
+#' plot the posterior distributions of multiple BRMA models
+#' and compare them visually.
+#' @param ... Objects of class `brma`. If the argument `model_names`
+#' is `NULL`, the names of these objects are used to label the plot.
+#' @param parameters Optional character vector with the names of
+#' parameters that exist in the models in `...`,
+#' Default: `NULL`.
+#' @param model_names Optional character vector with the names used
+#' to label the models in `...`, Default: `NULL`
+#' @return An object of class `ggplot`
+#' @examples
+#' plot_sensitivity(samples = list(
+#' data.frame(Parameter = "b",
+#' Value = rnorm(10),
+#' Model = "M1"),
+#' data.frame(Parameter = "b",
+#' Value = rnorm(10, mean = 2),
+#' Model = "M2")),
+#' parameters = "b")
+#' @export
+#' @importFrom ggplot2 ggplot
+#' @importFrom ggridges geom_density_ridges
+plot_sensitivity <- function(..., parameters = NULL, model_names = NULL){
+  models <- list(...)
+  UseMethod("plot_sensitivity", models[[1]])
+}
+
+#' @method plot_sensitivity brma
+#' @export
+plot_sensitivity.brma <- function(..., parameters = NULL, model_names = NULL){
+  if(is.null(model_names)){
+    model_names <- as.list(match.call())
+    model_names <- model_names[-c(1L, which(names(model_names) %in% c("parameters")))]
+    model_names <- sapply(model_names, deparse)
+  }
+
+  if(!all(sapply(models, inherits, what = "brma"))){
+    stop("Argument 'models' must be a named list of brma models.")
+  }
+  names(models) <- model_names
+  dfs <- lapply(names(models), function(m){
+    sim <- models[[m]]$fit@sim
+
+    row_int <- which(sim$fnames_oi == "Intercept")
+    row_beta <- which(startsWith(sim$fnames_oi, "betas"))
+    row_tau <- which(startsWith(sim$fnames_oi, "tau2"))
+    keepthese <- c(row_int, row_beta, row_tau)
+    samps <- sapply(keepthese, .extract_samples, sim = sim)
+    namz <- rownames(models[[m]]$coefficients)
[…]

### 2022-11-28 simulatie_2021/functions for simulation/model_accuracy.R

@@ -34,7 +34,7 @@ model_accuracy <-
         }
       },
       rma.uni = {
-        if (is.null(newdata)) {
+        if (is.null(newdata) | nrow(models$b) == 1) {
           predicted	  <- predict(fit)$pred
           if (length(predicted) == 1) {
             predicted <- rep(predicted, length(observed))

### 2022-11-28 simulatie_2021/Simulatie 2021_3.R
update 2022-11-28 18:23:04

@@ -1,0 +1,929 @@
+# Load packages
+packagenames <- c('pema', 'metaforest', 'parallel', 'sn', 'rstan', 'bayestestR', 'foreach', 'glmnet')
+lapply(packagenames, library, character.only = TRUE)
+
+# Check package versions
+# Which packages require correct versions and which versions are they?--------------------------------------------------
+versions <- c(
+  compareVersion(as.character(packageVersion("metaforest")), "0.1.3"),
+  compareVersion(as.character(packageVersion("pema")), "0.1.0.9000"),
+  compareVersion(as.character(packageVersion("rstan")), "2.21.2"))
+if(!all(versions > -1)) stop("Using the incorrect version of one or more packages.")
+
+# Load simulation functions from source -----------------------------------
+source("./simulatie_2021/functions for simulation/simulate_smd.R") #this function is necessary to load as it seems to be
+#different than the function simulate_smd in pema.
+source("./simulatie_2021/functions for simulation/model_accuracy.R")
+
+#set conditions for simulation
+hyper_parameters<-list(
+  #Number of datasets per condition
+  ndataset=1,
+  #Number of studies per dataset, normally distributed with mean n and sd n/3
+  k_train=c(20, 40, 100),
+  #Average n per study (k)
+  mean_n=c(40, 80, 160),
+  #Effect size
+  es = c(0, .2, .5, .8),
+  #Residual heterogeneity
+  tau2=c(0, .04, .1),
+  # Slant parameter alpha
+  alpha_tau = c(0),
+  alpha_mod = c(0, 2, 10),
+  #Study-level moderators
+  moderators= c(1, 2, 5),
+  model = c("es * x[, 1]",
+            "es * x[, 1] + es * (x[, 1] ^ 2) + es * (x[, 1] ^ 3)"),
+  distribution = "sn"
+)
+
+# Create grid with simulation parameters and save it
+summarydata <- expand.grid(hyper_parameters, stringsAsFactors = FALSE)
+
+# Add moderators so there's always sufficient predictors
+summarydata$moderators <-  summarydata$moderators + 1
+saveRDS(summarydata, file = "summarydata.RData")
+
+library(doSNOW)
+
+set.seed(78326)
+library(foreach)
[…]

### 2022-11-29 paper/action_letter.Rmd
update 2022-11-29 11:41:05

@@
 thus we always have a very large sample size.
-We do not see an urgent need to increase the number of replications,
+
+We have calculated the runtime required to conduct 1,000 replications per condition,
+and this amounts to 8160 computer-hours, or 340 days on a single core.
+This is exceptionally expensive and environmentally unfriendly,
+and the marginal gains are minimal.
+We thus strongly prefer to keep the number of replications at 100,
 but we defer to the Editor in this matter.

### 2022-12-01 paper/manuscript.Rmd
final corrections

@@
 ---
-title             : "Select relevant moderators using Bayesian regularized meta-regression"
+title             : "Selecting relevant moderators with Bayesian regularized meta-regression"
 shorttitle        : "BAYESIAN REGULARIZED META-REGRESSION"
@@
 
-One approach to is to select variables on theoretical grounds.
+One approach is to select variables on theoretical grounds.
 An important caveat is that theories that describe phenomena at the level of individual units of analysis do not necessarily generalize to the study level.
@@
 <span id = "informationdistribution">In contrast to the fixed effect model, the random effects model assumes that all studies provide some information about the underlying distribution of true effect sizes.
-Fixed effect weights would discount the information smaller studies provide about the scale of this distribution, which is represented by it's variance $\tau^2$.
+Fixed effect weights would discount the information smaller studies provide about the scale of this distribution, which is represented by its variance $\tau^2$.
 To overcome this limitation, the weights are attenuated in proportion to the variance.
@@
 
-As explained in Formula \@ref(eq:),
+As explained earlier,
 regularization penalizes all coefficients equally,
@@
 When the RMA algorithm fails to converge, however,
-terminates with an error.
+it terminates with an error.
 <!-- To handle this contingency, we automated some of the steps recommended [on the `metafor` website](https://www.metafor-project.org/doku.php/tips:convergence_problems_rma). -->
@@
 The example returns the warning that there were 331 divergent transitions,
-and suggests increasing the number of iteractions (increasing the argument `iter` beyond its default value of 2000).
+and suggests increasing the number of iterctions (increasing the argument `iter` beyond its default value of 2000).
 Divergent transitions can result in biased estimates.
@@
 
-In the Introduction, researchers should substantiate the decision to explore heterogeneity
+In the Introduction, researchers should substantiate the decision to explore heterogeneity.
 One valid reason is prima facie heterogeneity of the body of research [@higginsReevaluationRandomeffectsMetaanalysis2009a].
@@
 which implies that it is more suitable when a researcher intends to generalize beyond the sample at hand.
-Conversely, RMA is be more suitable when the goal is to describe the sample at hand in an unbiased manner,
+Conversely, RMA is more suitable when the goal is to describe the sample at hand in an unbiased manner,
 with less concern for generalizability to future studies.

### 2022-12-01 paper/manuscript.Rmd
final corrections ammend; iterations

@@
 The example returns the warning that there were 331 divergent transitions,
-and suggests increasing the number of iterctions (increasing the argument `iter` beyond its default value of 2000).
+and suggests increasing the number of iterations (increasing the argument `iter` beyond its default value of 2000).
 Divergent transitions can result in biased estimates.

### 2022-12-05 paper/manuscript.Rmd
update 2022-12-02 06:43:24
changed "regularizing horseshoe" to "regularized horseshoe" throughout

@@
 when there are many potential moderators is so ubiquitous that it was referred to as the "primary pitfall" in meta-regression [@thompsonHowShouldMetaregression2002].
-The present study introduces a novel method to overcome this pitfall by imposing Bayesian regularizing (LASSO and regularizing horseshoe) priors on the regression coefficients.
+The present study introduces a novel method to overcome this pitfall by imposing Bayesian regularizing (LASSO and regularized horseshoe) priors on the regression coefficients.
 These priors shrink the effect of irrelevant predictors towards zero while leaving important predictors relatively unaffected.
@@
 This manuscript discusses two shrinkage priors,
-the LASSO and regularizing horseshoe prior.</span>
+the LASSO and regularized horseshoe prior.</span>
 
@@
 \begin{align}
-PRSS= RSS + \lambda \sum_{j=1}^{p}|\beta_{j}|
+PRSS= RSS + \lambda \sum_{j=1}^{p}|\beta_{j}| (\#eq:prss)
 \end{align}
@@
 One limitation of the horseshoe prior is that it is difficult to specify a prior that ensures a sufficiently sparse solution.
-The regularizing horseshoe was introduced to overcome this limitation [@PiironenVehtari2017b].</span></span>
-
-The BRMA method introduced here offers both LASSO and regularizing horseshoe priors.
+The regularized horseshoe was introduced to overcome this limitation [@PiironenVehtari2017b].</span></span>
+
+The BRMA method introduced here offers both LASSO and regularized horseshoe priors.
 The LASSO prior is given by:
@@
 
-The regularizing horseshoe prior combines global and local shrinkage of the regression coefficients with a finite slab that curtails the occurrence of very extreme values [@PiironenVehtari2017b].
+The regularized horseshoe prior combines global and local shrinkage of the regression coefficients with a finite slab that curtails the occurrence of very extreme values [@PiironenVehtari2017b].
 For regression coefficients $\beta_j$, for $j \in [1\ldots p]$ where $p$ is the total number of moderators,
-the regularizing horseshoe prior is given by:
+the regularized horseshoe prior is given by:
 \begin{align}
@@
 
-As explained earlier,
+As explained in Formula \@ref(eq:prss),
 regularization penalizes all coefficients equally,
@@
 The most important option relates to the choice of priors for the regression coefficients.
-At the time of writing, `brma()` supports two priors for regression coefficients: the LASSO and the regularizing horseshoe.
+At the time of writing, `brma()` supports two priors for regression coefficients: the LASSO and the regularized horseshoe.
 A prior is selected using the `method` argument;
@@
 The parameters of the LASSO prior are explained in Equation \@ref(eq:lasso),
-and those of the regularizing horseshoe in Equation \@ref(eq:hs).
+and those of the regularized horseshoe in Equation \@ref(eq:hs).
 Table \@ref(tab:tabprior) provides an overview of the arguments that can be passed to `prior` to control these parameters,
@@
 Our research questions are whether BRMA offers a performance advantage over RMA in terms of any of these indicators,
-and which prior (LASSO versus regularizing horseshoe) is to be preferred.
+and which prior (LASSO versus regularized horseshoe) is to be preferred.
 <span id = "defaultvalues">For both Bayesian priors, we used default values proposed in prior literature, see Table \@ref(tab:tabprior).
 Default values for the LASSO prior were based on @vanErpOberskiMulder2019,
-and default values for the regularizing horseshoe prior were based on @PiironenVehtari2017a.</span>
+and default values for the regularized horseshoe prior were based on @PiironenVehtari2017a.</span>
 All analysis code is available in a version-controlled repository at <https://github.com/cjvanlissa/pema>.
@@
 First, we estimate a model with all default settings.
-Based on the results of the present simulation study, the regularizing horseshoe is the default prior.
+Based on the results of the present simulation study, the regularized horseshoe is the default prior.
 To see all default values, open the function documentation using `?brma`.
@@
 This study presented a novel algorithm to select relevant moderators that can explain heterogeneity in meta-analyses, using Bayesian shrinkage priors. 
-A simulation study validated the performance of two versions of the BRMA algorithm, with a regularizing horseshoe prior and LASSO prior, relative to state-of-the-art meta-regression with restricted maximum likelihood estimation (RMA).
+A simulation study validated the performance of two versions of the BRMA algorithm, with a regularized horseshoe prior and LASSO prior, relative to state-of-the-art meta-regression with restricted maximum likelihood estimation (RMA).
 Our analyses examined the algorithms' predictive performance, which is a measure of generalizability,

### 2022-12-05 paper/manuscript.Rmd
fixed typos

@@
 their parameters are not valid for inference.
-Secondly, although the LASSO model in the first step accounts for potential multicollinearity by including all colinear variables but restricting the size of their coefficients,
+Secondly, although the LASSO model in the first step accounts for potential multicollinearity by including all collinear variables but restricting the size of their coefficients,
 the meta-regression in the second step no longer does so.
@@
 For example, a double exponential prior (hereafter: LASSO prior) results in posterior distributions whose modes are identical to the estimates from LASSO-penalized regression [@ParkCasella2008].
-Both the the frequentist LASSO penalty and the Bayesian LASSO prior have a tuning parameter $\lambda$ that controls the amount of regularization.
+Both the frequentist LASSO penalty and the Bayesian LASSO prior have a tuning parameter $\lambda$ that controls the amount of regularization.
 In frequentist LASSO, its value is usually chosen via cross-validation [@hastieElementsStatisticalLearning2009]. 

### 2022-12-05 paper/manuscript.Rmd
adapted horseshoe section

@@
 In the Bayesian approach, by contrast,
-its value can be optimized during model estimation.
+its value can be estimated during model estimation.
 
@@
 which means that it does not shrink (and therefore bias) substantial coefficients as much.
-One limitation of the horseshoe prior is that it is difficult to specify a prior that ensures a sufficiently sparse solution.
-The regularized horseshoe was introduced to overcome this limitation [@PiironenVehtari2017b].</span></span>
+Two limitations of the horseshoe prior are 1) it lacks a formal way to include prior information regarding the degree of sparsity; and 2) it does not regularize coefficients far from zero.
+While the second problem is often considered a strength of the horseshoe prior, it can result in convergence issues when parameters are weakly identified.
+The regularized horseshoe was introduced to overcome these limitations [@PiironenVehtari2017b].</span></span>
 

### 2022-12-05 paper/manuscript.Rmd
fixed typos

@@
 By contrast, $R^2_{test}$ reflects the explained variance in the testing data.
-Remember that BRMA was developed to reduce the risk of overfitting meta-regression models.
+Recall that BRMA was developed to reduce the risk of overfitting meta-regression models.
 The $R^2_{test}$ is a useful metric to detect overfitting,
@@
 However, bear in mind that model parameters are influenced by the prior distribution.
-It is good practice to perform sensitivity analysis to determine how sensitive the model results and inferences are to different prior specifications. 
+It is good practice to perform a sensitivity analysis to determine how sensitive the model results and inferences are to different prior specifications. 
 Performing sensitivity analyses is particularly important when the sample is small,

### 2022-12-05 paper/action_letter.Rmd
fixed typos

@@
 We recognize that this choice of words was confusing.
-The regularizing horseshoe prior is an extension of the horseshoe prior.
+The regularized horseshoe prior is an extension of the horseshoe prior.
 To address this comment, we now explain this in the text:
@@
 We thank the Reviewer for pointing this out;
-a fragment of a sentance was cut here.
+a fragment of a sentence was cut here.
 We restored the original text.

### 2022-12-05 paper/manuscript.Rmd
fixed typos

@@
 This phenomenon is known as the *bias-variance trade-off*.
-In general, an estimator with low bias and high variance produces results that generalize less well to new data than an estimator with high bias and low variance.
+In general, an estimator with low bias and high variance produces results that generalize worse to new data than an estimator with high bias and low variance.
 Regularized approaches to regression intentionally increase bias in order to reduce variance.
@@
 \end{align}
-The resulting parameter estimates perfectly describe linear relations in the present data set, but generalize less well to new data.
+The resulting parameter estimates perfectly describe linear relations in the present data set, but do not generalize well to new data.
 Regularized regression biases parameter estimates towards zero by adding a penalty term to the RSS.

### 2022-12-05 paper/manuscript.Rmd
fix description lasso

@@
 \beta_{j} &\sim \text{DE}(0, \frac{s}{\lambda})\\ (\#eq:lasso)
-\lambda &\sim \chi^2(0, \nu_1)
+\frac{1}{lambda} &\sim \chi^2(0, \nu_1)
 \end{align}
@@
 The inverse tuning parameter is estimated from the data 
-by assigning it a $\chi^2$ prior distribution with mean zero and degrees of freedom $\nu_1$ [@vanErpOberskiMulder2019].
+by assigning it a $\chi^2$ prior distribution with mean zero and degrees of freedom $\nu_1$.
 Increasing the degrees of freedom assigns greater probability mass to extreme values, resulting in less regularization.
 The present study used default values for the prior parameters,
-$s = 1$, $\nu_1 = 1$, as suggested by @vanErpOberskiMulder2019.
+$s = 1$, $\nu_1 = 1$, which are the same defaults as used in `brms` [@R-brms_a].
 

### 2022-12-05 paper/manuscript.Rmd
fixed typo

@@
 In this formula, $\lambda$ controls the overall scale of the priors for all regression coefficients,
-where larger values for the global scale parameter $\lambda^2_0$ widen the rande of values covered by the priors.
+where larger values for the global scale parameter $\lambda^2_0$ widen the range of values covered by the priors.
 The global degrees of freedom $\nu_1$ control the overall thickness of the tails,

### 2022-12-05 paper/manuscript.Rmd
acknowledge brms
corrected defaults origin

@@
 Moreover, model compilation adds unnecessary computational overhead for standard applications.
-To overcome these limitations, the `pema` package includes pre-compiled stock models with opinionated default options.
+To overcome these limitations, the `pema` package includes pre-compiled stock models with opinionated default options. These models have been created using the `brms` package [@R-brms_a].
 At the time of writing, these include random effects and three-level meta-regression with and without an intercept.
@@
 <span id = "defaultvalues">For both Bayesian priors, we used default values proposed in prior literature, see Table \@ref(tab:tabprior).
-Default values for the LASSO prior were based on @vanErpOberskiMulder2019,
+Default values for the LASSO prior were based on the defaults used in @R-brms_a,
 and default values for the regularized horseshoe prior were based on @PiironenVehtari2017a.</span>

### 2022-12-07 paper/action_letter.Rmd
update 2022-12-07 15:57:04

@@
 We recognize that this choice of words was confusing.
-The regularized horseshoe prior is an extension of the horseshoe prior.
+The regularizing horseshoe prior is an extension of the horseshoe prior.
 To address this comment, we now explain this in the text:
@@
 <!-- Limitations -->
-<!-- i) multicolinearity -->
+<!-- i) multicollinearity -->
 <!-- ii) ecological fallacy -->
 <!-- iii) restriction of range -->
-<!-- iv) multicolinearity -->
+<!-- iv) multicollinearity -->
 <!-- v) something specific to clinical trials?? -->
@@
 <!-- PITFALLS -->
-<!-- i) curse of dimensionality: small sample size, multicolinearity -->
+<!-- i) curse of dimensionality: small sample size, multicollinearity -->
 <!-- ii) overfitting -->
@@
 <!-- iv) variable selection -->
-Most of the limitations and pitfalls they discuss come down to two fundamental points which are already addressed throughout our paper: 1) the curse of dimensionality and its implications for multicolinearity (limitations i, iv, vii and pitfalls i, ii, iii, and iv), and 2) the ecological fallacy (limitation ii and iv).
+Most of the limitations and pitfalls they discuss come down to two fundamental points which are already addressed throughout our paper: 1) the curse of dimensionality and its implications for multicollinearity (limitations i, iv, vii and pitfalls i, ii, iii, and iv), and 2) the ecological fallacy (limitation ii and iv).
 They further address three singular points which cannot be attributed to the two fundamental points:

### 2022-12-07 paper/manuscript.Rmd
update 2022-12-07 15:57:04

--- 2022-12-05 paper/manuscript.Rmd
@@
 This phenomenon is known as the *bias-variance trade-off*.
-In general, an estimator with low bias and high variance produces results that generalize worse to new data than an estimator with high bias and low variance.
+In general, an estimator with low bias and high variance produces results that generalize less well to new data than an estimator with high bias and low variance.
 Regularized approaches to regression intentionally increase bias in order to reduce variance.
@@
 \end{align}
-The resulting parameter estimates perfectly describe linear relations in the present data set, but do not generalize well to new data.
+The resulting parameter estimates perfectly describe linear relations in the present data set, but generalize less well to new data.
 Regularized regression biases parameter estimates towards zero by adding a penalty term to the RSS.
@@
 In the Bayesian approach, by contrast,
-its value can be estimated during model estimation.
+a diffuse hyperprior can be used to optimize its value during model estimation [@ParkCasella2008].
 
@@
 \beta_{j} &\sim \text{DE}(0, \frac{s}{\lambda})\\ (\#eq:lasso)
-\frac{1}{lambda} &\sim \chi^2(0, \nu_1)
+\frac{1}{\lambda} &\sim \chi^2(0, \nu_1)
 \end{align}
@@
 The inverse tuning parameter is estimated from the data 
-by assigning it a $\chi^2$ prior distribution with mean zero and degrees of freedom $\nu_1$.
+by assigning it a diffuse hyperprior:
+a $\chi^2$ prior distribution with mean zero and degrees of freedom $\nu_1$ [@ParkCasella2008].
 Increasing the degrees of freedom assigns greater probability mass to extreme values, resulting in less regularization.
 The present study used default values for the prior parameters,
-$s = 1$, $\nu_1 = 1$, which are the same defaults as used in `brms` [@R-brms_a].
+$s = 1$, $\nu_1 = 1$, were chosen as a diffuse hyperprior [@ParkCasella2008].
 
@@
 <span id = "defaultvalues">For both Bayesian priors, we used default values proposed in prior literature, see Table \@ref(tab:tabprior).
-Default values for the LASSO prior were based on @vanErpOberskiMulder2019,
+Default values for the LASSO prior were based on @ParkCasella2008,
 and default values for the regularized horseshoe prior were based on @PiironenVehtari2017a.</span>
@@
 See the `pema` package documentation (help and vignettes) for further examples.
-<!-- We focus specifically on how to choose the different hyperparameters of the regularizing horseshoe prior. -->
+<!-- We focus specifically on how to choose the different hyperparameters of the regularized horseshoe prior. -->
 
@@
 <!-- Increasing the degrees of freedom (`df_global` and `df_slab`) results in thinner tails, which applies more regularization. -->
-<!-- One advantage of the regularizing horseshoe prior is its ability to define the prior in terms of the expected number of nonzero coefficients, using the argument `relevant_pars`. -->
+<!-- One advantage of the regularized horseshoe prior is its ability to define the prior in terms of the expected number of nonzero coefficients, using the argument `relevant_pars`. -->
 <!-- This argument in turn influences the other hyperparameters. -->
@@
 ```
-<!-- Note that there are many auxiliary parameters used for the regularizing horseshoe prior.
+<!-- Note that there are many auxiliary parameters used for the regularized horseshoe prior.
 No information on these parameters is returned in the `brma` fitobject, however, once the fitobject is transformed into a Stan object for plotting, these parameters are included.
@@
 
-<span id = "sensitivityanalysis">All simulations were conducted with default settings for the model's prior distributions, based on prior research [@vanErpOberskiMulder2019; @PiironenVehtari2017b].
+<span id = "sensitivityanalysis">All simulations were conducted with default settings for the model's prior distributions, based on prior research [@ParkCasella2008; @PiironenVehtari2017b].
 Our results suggest that these defaults are suitable for a wide range of situations, including when model assumptions are violated.
@@
 researchers should be aware of its limitations [see @thompsonHowShouldMetaregression2002].
-These can be subdivided into four categories: 1) the curse of dimensionality and its corrolary implications for multicolinearity; 2) the ecological fallacy; 3) limited information on moderator variables, including missing data and restrictions of range.
+These can be subdivided into four categories: 1) the curse of dimensionality and its corrolary implications for multicollinearity; 2) the ecological fallacy; 3) limited information on moderator variables, including missing data and restrictions of range.
 BRMA seeks to address the first of these limitations,

### 2022-12-07 dev/pma.R

@@ -3,12 +3,24 @@ library(metafor)
 library(glmnet)
 ntau <- 10
 
-
-df <- pema::simulate_smd(k_train = 1000, es = 2)
+sim_out <- matrix(FALSE, nrow = 200, ncol = 2)
+for(i in 1:200){
+set.seed(i)
+df <- pema::simulate_smd(k_train = 100, es = .5, tau2 = .5)
 
 df_train <- df$training
+y = df_train$yi
+vi = df_train$vi
+x = X = model.matrix(~., df_train[, -c(1:2)])
 
-pma <- function(x, y, vi, ntau = 10, ...){
+# df_train <- curry[, -c(1:2)]
+# df_train <- df_train[complete.cases(df_train), ]
+#
+# y = df_train$d
+# vi = df_train$vi
+# x = X = model.matrix(~., df_train[, -c(1:4)])
+
+#pma <- function(x, y, vi, ntau = 10, ...){
   mf_nomod <- rma(y, vi)
   tau2_max <- mf_nomod$tau2
   mf_allmod <- rma(yi = y, vi = vi, mods = x)
@@ -21,15 +33,24 @@ pma <- function(x, y, vi, ntau = 10, ...){
     wts <- 1/(df_train$vi + tau_seq[i])
     res[[i]] <- cv.glmnet(x = X, y = y, weights = wts, foldid = res[[1]]$foldid)
   }
-  err_min <- sapply(res, function(i){min(i$cvm)})
-  tau2_cv <- tau_seq[which.min(err_min)]
-  list(
-    rma = mf_nomod,
-    lasso = res[[which.min(err_min)]],
-    tau2_cv = tau2_cv
-  )
-}
+#   err_min <- sapply(res, function(i){min(i$cvm)})
+#   tau2_cv <- tau_seq[which.min(err_min)]
+#   list(
+#     rma = mf_nomod,
+#     lasso = res[[which.min(err_min)]],
+#     tau2_cv = tau2_cv
+#   )
+# }
+#tmp <- cv.glmnet(x = X, y = y, foldid = res[[1]]$foldid)
+err_min <- sapply(res, function(i){min(i$cvm)})
+sim_out[i, 1] <- all(sign(diff(err_min)) == 1)
+sim_out[i, 2] <- tau_seq[1] == 0
 
+}
+#}
+plot(1:ntau, err_min)
+min(tmp$cvm)
+which.min(err_min)
[…]

### 2023-02-01 paper/manuscript.Rmd
incorporate changes for publication

@@
 classoption       : "man"
+csl               : american-medical-association.csl
 knit: worcs::cite_essential
@@
 ```{r setup, include = FALSE}
+# Change the variable `run_everything` to TRUE to reproduce all analyses,
+# including computer-intensive ones
 run_everything <- FALSE
@@
 and default values for the regularized horseshoe prior were based on @PiironenVehtari2017a.</span>
-All analysis code is available in a version-controlled repository at <https://github.com/cjvanlissa/pema>.
+The simulation code is available in a version-controlled repository at <https://github.com/cjvanlissa/pema>, in the directory `pema/simulatie_2021`.
 
@@
 
+# Data Availability Statement
+
+All analysis code is available in a version-controlled repository at <https://github.com/cjvanlissa/pema>.
+The directory `paper` contains the source code of this manuscript, 
+and the directory `simulatie_2021` contains the simulation source code.
+
 \newpage

### 2023-02-09 paper/manuscript.Rmd
add results files for knitting

@@
 Suspected causes of systematic heterogeneity can either be used as exclusion criteria,
-or controlled for using *meta-regression* [see @lopez-lopezEstimationPredictivePower2014].
+or controlled for using *meta-regression* [@lopez-lopezEstimationPredictivePower2014].
 The latter approach provides an opportunity to learn which factors impact the effect size
@@
 due to the higher probability that extreme values on one moderator coincide with extreme values on another.
-In such cases, regularized regression reduces the risk of overfitting and increase generalizability of the results [see @hastieElementsStatisticalLearning2009].
-
-<span id = "reftibshirani">To understand how regularized regression introduces bias, consider a comparison between ordinary least squares regression and LASSO regression [for a more elaborate introduction, see @tibshiraniRegressionShrinkageSelection2011].</span>
+In such cases, regularized regression reduces the risk of overfitting and increase generalizability of the results [@hastieElementsStatisticalLearning2009].
+
+<span id = "reftibshirani">To understand how regularized regression introduces bias, consider a comparison between ordinary least squares regression and LASSO regression; for a more elaborate introduction, see [@tibshiraniRegressionShrinkageSelection2011].</span>
 Ordinary least squares regression (OLS) estimates model parameters by minimizing the Residual Sum of Squares (RSS) of the outcome variable, given by the formula below.
@@
 We performed a simulation study to validate the BRMA algorithm.
-As a benchmark for comparison, we used random effects meta-regression with restricted maximum likelihood estimation [RMA, @viechtbauerConductingMetaanalysesMetafor2010],
+As a benchmark for comparison, we used random effects meta-regression with restricted maximum likelihood estimation (RMA) [@viechtbauerConductingMetaanalysesMetafor2010],
 which is the current state-of-the-art in the field.
@@
 <span id = "metareglimits">Before conducting meta-regression,
-researchers should be aware of its limitations [see @thompsonHowShouldMetaregression2002].
+researchers should be aware of its limitations [@thompsonHowShouldMetaregression2002].
 These can be subdivided into four categories: 1) the curse of dimensionality and its corrolary implications for multicollinearity; 2) the ecological fallacy; 3) limited information on moderator variables, including missing data and restrictions of range.
@@
 Note that BRMA is suitable for both confirmatory hypothesis tests and for exploratory analyses to ensure that no important effects were missed.
-Both approaches can be included in a preregistration [see @vanlissaComplementingPreregisteredConfirmatory2022].
+Both approaches can be included in a preregistration [@vanlissaComplementingPreregisteredConfirmatory2022].
 With regard to data extraction,
@@
 One way to do this is by creating a reproducible research repository,
-for example, using the Workflow for Reproducible Code in Science [WORCS, @vanlissaWORCSWorkflowOpen2021].
+for example, using the Workflow for Reproducible Code in Science (WORCS) [@vanlissaWORCSWorkflowOpen2021].
 Transparency allows readers and reviewers to verify that methods were correctly applied,

### 2023-02-15 paper/manuscript.Rmd
final revisions for publication

@@
 ```{r figr2, fig.cap="Predictive R2 for BRMA with horseshoe (HS) and LASSO prior, and RMA. Plots are sorted by largest performance difference between BRMA and RMA."}
-knitr::include_graphics("r2.png")
+knitr::include_graphics("r2.pdf")
 ```
@@
 ```{r figsensitivity, fig.cap="Sensitivity by design factors for the HS (circle, solid line), LASSO(triangle, dotted line) and RMA (square, dashed line) algorithms."}
-knitr::include_graphics("sensitivity.png")
+knitr::include_graphics("sensitivity.pdf")
 ```
@@
 ```{r figspecificity, fig.cap="Specificity by design factors for the HS (circle, solid line), LASSO(triangle, dotted line) and RMA (square, dashed line) algorithms."}
-knitr::include_graphics("specificity.png")
+knitr::include_graphics("specificity.pdf")
 ```
@@
 library(rstan)
-library(ggplot2)
 # Select data to analyze
@@
 library(rstan)
-library(ggplot2)
 df <- readRDS("df_imputed.RData")
@@
 ggsave("plot_es.png", p, device = "png", width = 4, height = 3, dpi = 300, scale = 1.5)
+ggsave("plot_es.pdf", p, device = "pdf", width = 4, height = 3, dpi = 300, scale = 1.5)
 ```
 ```{r figexres, eval = FALSE, echo = FALSE, fig.cap="Visual presentation of model parameters for the applied example."}
-knitr::include_graphics("plot_es.png")
+knitr::include_graphics("plot_es.pdf")
 ```
@@
 For a visual inspection of the difference in posterior distributions,
-use the function `plot_sensitivity()`, see Figure \@ref(fig:figsens).
+use the function `plot_sensitivity()`.
 
@@
              seed = 1)
-plot_sensitivity(fit, fit2) + coord_cartesian(xlim = c(-3, 3))
+plot_sensitivity(fit, fit2)
 ```
@@
 ggsave("plot_sensitivity.png", p, device = "png", units = "mm", width = 105, height = 60)
-```
-```{r figsens, echo = FALSE, eval = TRUE, fig.cap="A rudimentary visual check for sensitivity to different priors."}
-knitr::include_graphics("plot_sensitivity.png")
+ggsave("plot_sensitivity.pdf", p, device = "pdf", units = "mm", width = 105, height = 60)
+```
+```{r figsens, echo = FALSE, eval = FALSE, fig.cap="A rudimentary visual check for sensitivity to different priors."}
+knitr::include_graphics("plot_sensitivity.pdf")
 ```

### 2023-02-15 simulatie_2021/Analysis Sim2021_3.R

@@ -158,7 +158,7 @@ table_anova$Factor<-table.names
 
 saveRDS(table_anova, "paper/anova.RData")
 write.csv(table_anova, file =  "paper/anova.csv", row.names = FALSE)
-
+usethis::use_git_ignore("!anova.csv")
 # plotthese <- table_anova$condition[table_anova$Interpretation == "crossover"]
 # p <- lapply(1:length(plotthese), function(i){
 #   x = plotthese[i]
@@ -190,6 +190,8 @@ p[[1]] <- p[[1]] + theme(legend.position = c(.7, .22), legend.title = element_bl
 plot_other <- do.call(plot_grid, c(p, list(labels = NULL, ncol = 2))) # "auto"
 #ggsave("paper/other_effects.png", plot = plot_other, device = "png", height = 210, width =  297, units = "mm", scale = 2.5)
 ggsave("paper/r2.png", plot = plot_other, device = "png", width = 210, height =  297, units = "mm", scale = 2.5)
+
+ggsave("paper/r2.pdf", plot = plot_other, device = "pdf", width = 210, height =  297, units = "mm", scale = 2.5)
 
 # How often each highest?
 df_hi <- dat
@@ -224,7 +226,7 @@ colnames(cis) <- paste("CI ", c("HS", "LASSO", "RMA"))
 tab <- cbind(r2mean, cis, r2sd)
 tab <- data.frame(ES = c("Overall", "ES = 0", "ES != 0"), tab, check.names = F)
 write.csv(tab, "paper/r2.csv", row.names = F)
-
+usethis::use_git_ignore("!r2.csv")
 
 #---End R2---------------------------------------------------------------------------
 
@@ -304,9 +306,10 @@ tab_select2$Interpretation <- int_main
 
 saveRDS(tab_select, "paper/selected.RData")
 write.csv(tab_select, file =  "paper/selected.csv", row.names = FALSE)
+usethis::use_git_ignore("selected.csv")
 saveRDS(tab_select2, "paper/notselected.RData")
 write.csv(tab_select2, file =  "paper/notselected.csv", row.names = FALSE)
-
+usethis::use_git_ignore("notselected.csv")
 
 p <- lapply(1:length(conditions), function(i){
   x = plotthese[i]
@@ -332,6 +335,8 @@ p[[1]] <- p[[1]] + theme(legend.position = c(.7, .22), legend.title = element_bl
[…]

### 2023-02-21 README.Rmd
update doi

@@
 
-# pema: Penalized Meta-Analysis <!--a href='https://osf.io/zcvbs/'><img src='https://github.com/cjvanlissa/pema/raw/master/docs/pema_icon.png' align="right" height="139" /></a-->
+# pema: Penalized Meta-Analysis <!--a href='https://doi.org/10.1002/jrsm.1628'><img src='https://github.com/cjvanlissa/pema/raw/master/docs/pema_icon.png' align="right" height="139" /></a-->
 
@@
 [![CRAN RStudio mirror downloads](https://cranlogs.r-pkg.org/badges/grand-total/pema?color=blue)](https://r-pkg.org/pkg/pema)
-[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
+[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://lifecycle.r-lib.org/articles/stages.html#stable)
 [![R-CMD-check](https://github.com/cjvanlissa/pema/workflows/R-CMD-check/badge.svg)](https://github.com/cjvanlissa/pema/actions)
@@
 <!-- [![CII Best Practices](https://bestpractices.coreinfrastructure.org/projects/3969/badge)](https://bestpractices.coreinfrastructure.org/projects/3969) -->
-<!--[![DOI](http://joss.theoj.org/papers/10.21105/joss.00978/status.svg)](https://doi.org/10.21105/joss.00978)-->
 
@@
 
-<!-- ## Where do I start? -->
+## Where do I start?
 
-<!-- For most users, the recommended starting point is to [read the paper](https://osf.io/zcvbs/), currently in press in [Data Science](https://content.iospress.com/journals/data-science/Pre-press/Pre-press), -->
-<!-- which introduces the pema workflow, explains the underlying tools, and illustrates how the `pema` package can be used to create a new project that follows the workflow. -->
+For most users, the recommended starting point is to [read the paper](https://doi.org/10.1002/jrsm.1628) published in **Research Synthesis Methods**,
+which introduces the method, validates it, and provides a tutorial example.
 
@@
 
-The `pema` validation paper is currently in preprint stage.
-The code and results of the validation study are publicly available.
-You can cite `pema` using the following citation (please use the same citation for either the package, or the paper); consider updating that citation once the preprint is published:
+You can cite `pema` using the following citation (please use the same citation for either the package, or the paper):
 
-> Van Lissa, C. J., & van Erp, S. (2021, December 9). Select relevant moderators using Bayesian regularized meta-regression. Retrieved from psyarxiv.com/6phs5
+> Van Lissa, C. J., van Erp, S., & Clapper, E. B. (2023). Selecting relevant moderators with Bayesian regularized meta-regression. *Research Synthesis Methods*. https://doi.org/10.1002/jrsm.1628
 

### 2023-02-21 R/brma.R

@@ -99,9 +99,9 @@
 #'   coefficients to avoid any sampling problems.}
 #' }
 #' @references
-#' Van Lissa, C. J., & van Erp, S. (2021, December 9). Select relevant
+#' Van Lissa, C. J., Van Erp, S., & Clapper, E. B. (2023). Selecting relevant
 #' moderators using Bayesian regularized meta-regression.
-#' \doi{10.31234/osf.io/6phs5}
+#' \doi{10.1002/jrsm.1628}
 
 #' Park, T., & Casella, G. (2008). The Bayesian Lasso. Journal of the American
 #' Statistical Association, 103(482), 681–686. \doi{10.1198/016214508000000337}

### 2023-02-21 R/pema-package.R

@@ -12,9 +12,10 @@
 #' @importFrom rstan sampling
 #'
 #' @references
-#' Van Lissa, C. J., & van Erp, S. (2021, December 9). Select relevant
-#' moderators using Bayesian regularized meta-regression.
-#' \doi{10.31234/osf.io/6phs5}
+#' Van Lissa, C. J., van Erp, S., & Clapper, E. B. (2023).
+#' Selecting relevant moderators with Bayesian regularized
+#' meta-regression. Research Synthesis Methods.
+#' \doi{10.1002/jrsm.1628}
 #'
 #' Stan Development Team (NA). RStan: the R interface to Stan. R package version
 #' 2.26.2. \url{https://mc-stan.org}

### 2023-02-23 paper/manuscript.Rmd
update paper

@@
 authornote: |
-  This is a preprint paper, generated from Git Commit # `r substr(gert::git_commit_id(),1,7)`. This work was funded by a NWO Veni Grant (NWO Grant Number VI.Veni.191G.090), awarded to the lead author.
+  This is the peer reviewed version of the following article: [Van Lissa, C.
+J., van Erp, S., & Clapper, E.
+B.
+(2023).
+Selecting relevant moderators with Bayesian regularized meta‐regression.
+Research Synthesis Methods.
+DOI:10.1002/jrsm.1628].
+This paper was generated from Git Commit # `r substr(gert::git_commit_id(),1,7)`.
+This work was funded by a NWO Veni Grant (NWO Grant Number VI.Veni.191G.090), awarded to the lead author.
 

### 2023-02-23 R/plot_sensitivity.R
update 2023-02-23 10:32:01

@@ -73,7 +73,7 @@ plot_sensitivity.default <- function(..., parameters = NULL, model_names = NULL)
   if(!any(par_exists)) stop("Requested 'parameters' do not exist in any of the models provided.")
   parameters <- parameters[par_exists]
   df_plot <- df_plot[df_plot$Parameter %in% parameters, , drop = FALSE]
-  ggplot2::ggplot(df_plot, aes(x = Value, y = Parameter, colour = Model)) +
+  ggplot2::ggplot(df_plot, aes(x = .data[["Value"]], y = .data[["Parameter"]], colour = .data[["Model"]])) +
     ggridges::geom_density_ridges(scale = 1, alpha = 0) +
     theme_bw() +
     theme(axis.title = element_blank())

### 2023-02-23 R/pma_wrappers.R

@@ -1,103 +1,47 @@
-#' Conduct LASSO penalized Meta-Analysis
-#'
-#' This function conducts Bayesian regularized meta-regression (Van Lissa & Van
-#' Erp, 2021). It uses the \code{stan} function
-#' [rstan::sampling] to fit the model. A lasso or horseshoe prior is used to
-#' shrink the regression coefficients of irrelevant moderators towards zero.
-#' See Details.
-#' @param formula An object of class `formula` (or one that can be coerced to
-#' that class), see \code{\link[stats]{lm}}.
-#' @param data Either a `data.frame` containing the variables in the model,
-#' see \code{\link[stats]{lm}}, or a `list` of multiple imputed `data.frame`s,
-#' or an object returned by \code{\link[mice]{mice}}.
-#' @param vi Character. Name of the column in the \code{data} that
-#' contains the variances of the effect sizes. This column will be removed from
-#' the data prior to analysis. Defaults to \code{"vi"}.
-#' @param study Character. Name of the column in the
-#' \code{data} that contains the study id. Use this when the data includes
-#' multiple effect sizes per study. This column can be a vector of integers, or
-#' a factor. This column will be removed from the data prior to analysis.
-#' See \code{Details} for more information about analyzing dependent data.
-#' @param ntau Numeric, the numer of `tau2` values to try during
-#' cross-validation.
-# @details The Bayesian regularized meta-analysis algorithm (Van Lissa & Van
-# Erp, 2021) penalizes meta-regression coefficients either via the
-# lasso prior (Park & Casella, 2008) or the regularized horseshoe prior
-# (Piironen & Vehtari, 2017).
-# \describe{
-#   \item{lasso}{ The Bayesian equivalent of the lasso penalty is obtained when
-#   placing independent Laplace (i.e., double exponential) priors on the
-#   regression coefficients centered around zero. The scale of the Laplace
-#   priors is determined by a global scale parameter \code{scale}, which
-#   defaults to 1 and an inverse-tuning parameter \eqn{\frac{1}{\lambda}}
-#   which is given a chi-square prior governed by a degrees of freedom
-#   parameter \code{df} (defaults to 1). If \code{standardize = TRUE},
-#   shrinkage will
-#   affect all coefficients equally and it is not necessary to adapt the
-#   \code{scale} parameter. Increasing the \code{df} parameter will allow
[…]

### 2023-02-23 R/plot_sensitivity.R
remove ggridges dependency

@@ -21,7 +21,6 @@
 #' parameters = "b")
 #' @export
 #' @importFrom ggplot2 ggplot
-#' @importFrom ggridges geom_density_ridges
 plot_sensitivity <- function(..., parameters = NULL, model_names = NULL){
   models <- list(...)
   UseMethod("plot_sensitivity", models[[1]])
@@ -68,13 +67,27 @@ plot_sensitivity.brma <- function(..., parameters = NULL, model_names = NULL){
 #' @export
 plot_sensitivity.default <- function(..., parameters = NULL, model_names = NULL){
   dots <- list(...)
-  df_plot <- do.call(rbind, dots[["samples"]])
+  plotlist <- lapply(dots[["samples"]], function(i){
+    par_exists <- parameters %in% i$Parameter
+    if(!any(par_exists)) return(NULL)
+    do.call(rbind, lapply(parameters[par_exists], function(p){
+      densdat <- density(i$Value[i$Parameter == p])
+      data.frame(x = densdat$x, y = densdat$y, Parameter = p, Model = i$Model[1])
+    }))
+  })
+  df_plot <- do.call(rbind, plotlist)
   par_exists <- parameters %in% df_plot$Parameter
   if(!any(par_exists)) stop("Requested 'parameters' do not exist in any of the models provided.")
   parameters <- parameters[par_exists]
   df_plot <- df_plot[df_plot$Parameter %in% parameters, , drop = FALSE]
-  ggplot2::ggplot(df_plot, aes(x = .data[["Value"]], y = .data[["Parameter"]], colour = .data[["Model"]])) +
-    ggridges::geom_density_ridges(scale = 1, alpha = 0) +
+  df_plot$Parameter <- factor(df_plot$Parameter)
+  divby <- tapply(df_plot$y, df_plot$Parameter, max, na.rm = TRUE)
+  df_plot$y <- df_plot$y/ divby[df_plot$Parameter]
+  df_plot$y <- df_plot$y + as.integer(df_plot$Parameter)
+  df_plot$grp <- paste0(df_plot$Parameter, df_plot$Model)
+  ggplot2::ggplot(df_plot, aes(x = .data[["x"]], y = .data[["y"]], colour = .data[["Model"]], group = .data[["grp"]])) +
+    ggplot2::geom_path() +
     theme_bw() +
-    theme(axis.title = element_blank())
[…]

### 2023-03-14 README.Rmd
prepare for cran

@@
 [![CRAN status](https://www.r-pkg.org/badges/version/pema)](https://CRAN.R-project.org/package=pema)
-[![CRAN RStudio mirror downloads](https://cranlogs.r-pkg.org/badges/grand-total/pema?color=blue)](https://r-pkg.org/pkg/pema)
+[![CRAN RStudio mirror downloads](https://cranlogs.r-pkg.org/badges/grand-total/pema?color=blue)](https://cran.rstudio.com/web/packages/pema/index.html)
 [![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://lifecycle.r-lib.org/articles/stages.html#stable)

### 2023-03-16 README.Rmd
fix urls for CRAN

--- 2023-02-21 README.Rmd
@@
 
-# pema: Penalized Meta-Analysis <!--a href='https://doi.org/10.1002/jrsm.1628'><img src='https://github.com/cjvanlissa/pema/raw/master/docs/pema_icon.png' align="right" height="139" /></a-->
+# pema: Penalized Meta-Analysis <!--a href='https://doi.org/10.31234/osf.io/6phs5'><img src='https://github.com/cjvanlissa/pema/raw/master/docs/pema_icon.png' align="right" height="139" /></a-->
 
 [![CRAN status](https://www.r-pkg.org/badges/version/pema)](https://CRAN.R-project.org/package=pema)
-[![CRAN RStudio mirror downloads](https://cranlogs.r-pkg.org/badges/grand-total/pema?color=blue)](https://r-pkg.org/pkg/pema)
+[![CRAN RStudio mirror downloads](https://cranlogs.r-pkg.org/badges/grand-total/pema?color=blue)](https://cran.r-project.org/package=pema)
 [![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://lifecycle.r-lib.org/articles/stages.html#stable)
@@
 
-For most users, the recommended starting point is to [read the paper](https://doi.org/10.1002/jrsm.1628) published in **Research Synthesis Methods**,
+For most users, the recommended starting point is to [read the paper](https://doi.org/10.31234/osf.io/6phs5) published in **Research Synthesis Methods**,
 which introduces the method, validates it, and provides a tutorial example.
@@
 
-> Van Lissa, C. J., van Erp, S., & Clapper, E. B. (2023). Selecting relevant moderators with Bayesian regularized meta-regression. *Research Synthesis Methods*. https://doi.org/10.1002/jrsm.1628
+> Van Lissa, C. J., van Erp, S., & Clapper, E. B. (2023). Selecting relevant moderators with Bayesian regularized meta-regression. *Research Synthesis Methods*. https://doi.org/10.31234/osf.io/6phs5
 

### 2025-08-06 R/check_workshop_data.R
try to fix failing check

@@ -68,7 +68,10 @@ check_dependencies <- function (packages = "metaforest")
 #' check_workshop_data(fukkink_lont)
 #' @rdname check_workshop_data
 #' @export
-check_workshop_data <- function(df){
+check_workshop_data <- function(df = NULL){
+  if(is.null(df)){
+    df <- curry
+  }
   no_errors <- TRUE
   has_dep <- no_errors & check_dependencies(packages = c("pema", "metaforest", "ranger"))
 

### 2025-08-06 R/check_workshop_data.R
update 2025-08-06 20:45:57.094429

@@ -65,12 +65,12 @@ check_dependencies <- function (packages = "metaforest")
 #' @return Invisibly returns a logical TRUE/FALSE, indicating whether all checks
 #' have passed.
 #' @examples
-#' check_workshop_data(fukkink_lont)
+#' check_workshop_data(bonapersona)
 #' @rdname check_workshop_data
 #' @export
 check_workshop_data <- function(df = NULL){
   if(is.null(df)){
-    df <- curry
+    df <- pema::bonapersona
   }
   no_errors <- TRUE
   has_dep <- no_errors & check_dependencies(packages = c("pema", "metaforest", "ranger"))
